% Insert into Section~\ref{sec:projective-rigidity}, after the opening
% paragraph and before \subsection{Two-point comparison}.

\subsection{Branch exhaustion}
\label{subsec:branch-exhaustion}

The clean rebuild uses only two local obstruction branches: the completed
scalar two-point branch and the four-point full-quartet branch.  This is
an architectural reduction relative to the archived finite-core taxonomy,
and it must be stated as an explicit input until proved.  One-center data
are same-point normalization and whitening data; no one-point obstruction
projection is defined.  The archived three-point lifted/projective branch
is not imported as an active branch of the present rebuild.  The
\(N\)-point construction of Section~\ref{sec:n-point-odd-moment-cancellation}
is scalar moment aggregation of the two-point channel, not a separate
projection arity.

\begin{hypothesis}[Branch exhaustion]
\label{hyp:branch-exhaustion}
Every admissible off-line packet produced by the branch-entry construction
is excluded by at least one of the two active local obstruction branches:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=*]
\item the two-point scalar branch of
      Theorem~\ref{thm:two-point-rigidity}; or
\item the four-point full-quartet branch of
      Theorem~\ref{thm:four-point-rigidity}.
\end{enumerate}
Equivalently, there is no residual admissible off-line packet whose only
local obstruction would require a separate one-point, three-point, or
\(N\)-point projection branch outside the two branches above.
\end{hypothesis}

\begin{remark}[Status of Hypothesis~\ref{hyp:branch-exhaustion}]
\label{rem:branch-exhaustion-status}
Hypothesis~\ref{hyp:branch-exhaustion} is the clean rebuild's replacement
for importing the archived finite-core arity taxonomy wholesale.  It is
not a consequence of the two-point projection
\(\Pi_\trans\) alone and should not be treated as proved by
Sections~\ref{sec:transverse-projection}--\ref{sec:actual-zeta-transverse-suppression}.
If a later argument imports archived three-point lifted/projective
geometry, that import must either prove Hypothesis~\ref{hyp:branch-exhaustion}
or state a separate three-point branch explicitly.
\end{remark}
