\documentclass[11pt,a4paper]{amsart}

% =============================================================================
% Clean rebuild scaffold.
%
% Status convention: every unproven leaf is followed by a Gap remark via the
% `wip' theorem environment, carrying a `rem:wip-<name>' label so the gap is
% individually addressable from anywhere in the file.  Status is binary: a
% result is proved iff no `wip' remark is attached to it.  All bookkeeping
% (what is missing, where v1 prose lives, dependencies) lives in the body
% of that remark; nothing tracking-related is kept outside the .tex.
%
% The original large draft `proof_of_rh.tex' stays in place as a quarry from
% which prose may be migrated, after restatement and refereeing, into the
% present file; see Appendix~\ref{app:archive-map}.
% =============================================================================

\usepackage{amsmath,amssymb,amsthm,mathtools,bm,mathrsfs}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\pdfstringdefDisableCommands{%
  \def\Omega{Omega}%
  \def\Phi{Phi}%
  \def\PsiCal{Psi}%
  \def\RH{RH}%
  \def\corr{corr}%
  \def\toy{toy}%
  \def\val{val}%
  \def\aut{aut}%
  \def\jet{jet}%
  \def\far{far}%
  \def\est{est}%
  \def\rem{rem}%
  \def\sym{sym}%
  \def\curv{curv}%
  \def\tail{tail}%
  \def\mix{mix}%
  \def\core{core}%
  \def\aux{aux}%
  \def\out{out}%
  \def\pair{pair}%
  \def\lin{lin}%
  \def\new{new}%
}
\usepackage{enumitem}
\usepackage[expansion=false]{microtype}
\usepackage[margin=1in]{geometry}

\numberwithin{equation}{section}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{hypothesis}[theorem]{Hypothesis}

\title{A local obstruction proof of the Riemann hypothesis}

\author{John Shields}
\thanks{Preprint, clean rebuild draft.}
\date{May 2026}

\subjclass[2020]{11M26 (primary), 11M06, 11M50 (secondary)}
\keywords{Riemann hypothesis, zeta function, critical line, phase kernel,
  jet normalization, jet-Gram block, odd-moment cancellation,
  source-energy supply}

% Frozen namespace, identical to proof_of_rh.tex.
\newcommand{\RH}{\mathrm{RH}}
\newcommand{\z}{\zeta}
\newcommand{\Om}{\Omega}
\newcommand{\Ph}{\Phi}
\newcommand{\Del}{\Delta}
\newcommand{\Aut}{\mathrm{aut}}
\newcommand{\sym}{\mathrm{sym}}
\newcommand{\loc}{\mathrm{loc}}
\newcommand{\sm}{\mathrm{sm}}
\newcommand{\far}{\mathrm{far}}
\newcommand{\est}{\mathrm{est}}
\newcommand{\rem}{\mathrm{rem}}
\newcommand{\toy}{\mathrm{toy}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\corr}{\mathrm{corr}}
\newcommand{\main}{\mathrm{main}}
\newcommand{\err}{\mathrm{err}}
\newcommand{\jet}{\mathrm{jet}}
\newcommand{\bg}{\mathrm{bg}}
\newcommand{\curv}{\mathrm{curv}}
\newcommand{\tail}{\mathrm{tail}}
\newcommand{\mix}{\mathrm{mix}}
\newcommand{\core}{\mathrm{core}}
\newcommand{\aux}{\mathrm{aux}}
\newcommand{\out}{\mathrm{out}}
\newcommand{\pair}{\mathrm{pair}}
\newcommand{\lin}{\mathrm{lin}}
\newcommand{\new}{\mathrm{new}}
\newcommand{\off}{\mathrm{off}}
\newcommand{\odd}{\mathrm{odd}}
\newcommand{\amp}{\mathrm{amp}}
\newcommand{\actual}{\mathrm{actual}}
\newcommand{\can}{\mathrm{can}}
\newcommand{\source}{\mathrm{source}}
\newcommand{\base}{\mathrm{base}}
\newcommand{\wh}{\mathrm{wh}}
\newcommand{\phys}{\mathrm{phys}}
\newcommand{\quot}{\mathrm{quot}}
\newcommand{\Qabs}{\mathcal Q^{\mathrm{abs}}}
\newcommand{\F}{\mathrm{F}}
\newcommand{\RePart}{\operatorname{Re}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\sgn}{\operatorname{sgn}}
% Two additions used in this rebuild but absent from proof_of_rh.tex.
\newcommand{\op}{\mathrm{op}}
\newcommand{\trans}{\mathrm{trans}}

% Skeleton-only environment: marks an unproven leaf as a remark titled
% `Gap'.  Each occurrence carries a `rem:wip-<name>' label so gaps are
% individually addressable.  Removed at journal time.
\newtheorem{wip}[theorem]{Gap}

% Section-level status indicators.  Each axis has its own macro so it
% can be read and edited independently in the source.  `\status{VALUE}'
% is the underlying pill renderer.  The three computational axes
% (sympy, sim, lean) take an optional path argument that points to the
% verification artefact; if given, it is rendered next to the pill.
% Allowed values per axis:
%
%   \statuspaper{<value>}            LIVE | FINITE AUDIT | ARCHIVED |
%                                    SUPERSEDED | NO-GO | DIAGNOSTIC
%   \statusmig{<value>}              not-started | in-progress |
%                                    partial | migrated | n/a
%                                    (migration from proof_of_rh.tex;
%                                     n/a for rebuild-original
%                                     sections)
%   \statusreferee{<value>}          not-started | in-progress |
%                                    passed | failed
%   \statussympy[<path>]{<value>}    n/a | not-started | partial |
%                                    verified
%                                    (symbolic/formula verification;
%                                     <path> points to sympy script)
%   \statussim[<path>]{<value>}      n/a | not-started | partial |
%                                    verified
%                                    (numerical simulation; <path>
%                                     points to simulation script)
%   \statuslean[<path>]{<value>}     n/a | not-started | in-progress |
%                                    formalized
%                                    (Lean formalization; <path>
%                                     points to Lean source)
%
% Removed at journal time.
\newcommand{\status}[1]{\textbf{\scriptsize[#1]}}
\newcommand{\statuspaper}[1]{\textsf{\footnotesize paper:}\,\status{#1}}
\newcommand{\statusmig}[1]{\textsf{\footnotesize v1:}\,\status{#1}}
\newcommand{\statusreferee}[1]{\textsf{\footnotesize referee:}\,\status{#1}}
\newcommand{\statussympy}[2][\relax]{%
  \textsf{\footnotesize sympy:}\,\status{#2}%
  \ifx\relax#1\else\,\textsf{\scriptsize\texttt{#1}}\fi%
}
\newcommand{\statussim}[2][\relax]{%
  \textsf{\footnotesize sim:}\,\status{#2}%
  \ifx\relax#1\else\,\textsf{\scriptsize\texttt{#1}}\fi%
}
\newcommand{\statuslean}[2][\relax]{%
  \textsf{\footnotesize lean:}\,\status{#2}%
  \ifx\relax#1\else\,\textsf{\scriptsize\texttt{#1}}\fi%
}

\begin{document}

\begin{abstract}
We present a local-geometric obstruction proof of the Riemann hypothesis.
The two-by-two jet-normalized blocks of the phase kernel of \(\zeta\) at
one or two centers form a finite-dimensional comparison object: a
hypothetical off-line zero forces a transverse mode that the actual zeta
phase, after a single fixed value-gauge quotient, suppresses at a strictly
larger polynomial exponent in the local scale.  Two-point and four-point
comparisons of this object aggregate over heights via \(N\)-point
odd-moment cancellation to yield an unconditional zero-free strip around
the critical line, hence the Riemann hypothesis.  A self-contained final
section provides an optional source-energy supply
available to the two-point and four-point comparisons if their standalone
forms prove insufficient.
\end{abstract}

\maketitle

\tableofcontents

\newpage

% =============================================================================
\section{Introduction}
\label{sec:introduction}
\statuspaper{LIVE}\quad
\statusmig{n/a}\quad
\statusreferee{not-started}\quad
\statussympy{n/a}\quad
\statussim{n/a}\quad
\statuslean{not-started}
\par\medskip

The Riemann hypothesis, originating in Riemann's 1859 memoir
\cite{Riemann1859}, asserts that every nontrivial zero of \(\zeta(s)\) lies
on the critical line \(\RePart s = \tfrac12\); see
\cite{Bombieri2000,Conrey2003,Edwards2001,Titchmarsh1986} for surveys.  The
proof presented in this paper proceeds by a local-geometric obstruction.
For each height \(\gamma\) we work on a smooth window \(I_T\) centered at
\(T=\gamma\) of width comparable to \(1/Q(\gamma)\), where \(Q\) is a
scale parameter slowly growing with \(|\gamma|\).  On this window we fix a
real local phase \(\Ph\) for \(\zeta\) and study the phase kernel
\[
K_\Ph(x,y)=\frac{\sin\bigl(\Ph(x)-\Ph(y)\bigr)}{\pi(x-y)},
\qquad x\ne y,
\]
extended by removable singularity at \(x=y\).  The \(2\times 2\) blocks of
\(K_\Ph\) at one or two centers, transformed into the Gram-normalized
basis by a fixed elementary matrix \(P_h\), become explicit matrices
\(J(T)\) and \(N_{12}(T_1,T_2)\) whose entries are finite combinations of
\(q=\Ph'\), \(q'\), \(q''\), and \(\Del=\Ph(T_1)-\Ph(T_2)\).  All
subsequent estimates reduce to finite linear-algebraic manipulations of
these matrices.

A hypothetical off-line zero \(\rho=\beta+i\gamma\) with
\(\beta\ne\tfrac12\) forces a specific transverse mode in the
Gram-normalized jet space --- the toy mode --- which survives the
natural value/gauge quotient.  The actual zeta phase, under the same quotient,
cannot realize that mode: the transverse channel of the actual whitened
block is suppressed at a strictly larger polynomial exponent in \(Q\)
than the toy lower bound.  The clash is two-point at minimum and four-point in the full symmetry quartet
\(\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\), propagated across heights by
an \(N\)-point odd-moment cancellation.
Aggregation over the dyadic height ladder gives an unconditional
zero-free strip around the critical line; combined with standard
low-height verification of \(\RH\), this yields the Riemann hypothesis.

The argument is self-contained except for one optional input.  If either
the two-point or the four-point standalone closure proves insufficient,
the source-energy lower bound on the canonical source
curvature \(q''_\can=\partial_t^3 Z\), stated as
Hypothesis~\ref{hyp:source-energy-bound} in
Section~\ref{sec:source-energy-supply}, supplies the additional
polynomial-in-\(Q\) room required.

\subsection{Active dependency graph}
\label{subsec:active-dependency-graph}

The active spine of the argument is the chain
\[
\begin{aligned}
&\text{\S\ref{sec:local-kernel-and-jet-normalization}}
\;\longrightarrow\;
\text{\S\ref{sec:jet-limit-local-blocks}}
\;\longrightarrow\;
\text{\S\ref{sec:finite-scale-local-blocks-and-whitening}}\\
&\;\longrightarrow\;
\text{\S\ref{sec:toy-anomaly-and-transverse-obstruction},\
\S\ref{sec:transverse-projection},\
\S\ref{sec:actual-zeta-transverse-suppression}}\\
&\;\longrightarrow\;
\text{\S\ref{sec:projective-rigidity}}\\
&\;\longrightarrow\;
\text{\S\ref{sec:n-point-odd-moment-cancellation}}
\;\longrightarrow\;
\text{\S\ref{sec:aggregation-and-zero-free-strip}}
\;\longrightarrow\;
\text{\S\ref{sec:riemann-hypothesis}}.
\end{aligned}
\]
Section~\ref{sec:source-energy-supply} stands aside: it provides the
optional source-energy supply consumed by
Section~\ref{sec:projective-rigidity}
when their standalone forms are insufficient.  All cross-references to
Section~\ref{sec:source-energy-supply} from earlier sections are
forward references; that section is self-contained.

\subsection{Master conditional theorem}
\label{subsec:master-conditional}

\begin{theorem}[Master conditional]
\label{thm:master-conditional}
Assume the same-point and cross-block jet-limit identities
(Lemmas~\ref{lem:same-point-jet-limit}
and~\ref{lem:cross-block-jet-limit}); the finite-scale whitening loss
bound (Lemma~\ref{lem:whitening-loss}); the toy anomaly visibility lower
bound (Theorem~\ref{thm:toy-anomaly-visibility}); the two-point or
four-point actual-zeta transverse suppression upper bound
(Hypothesis~\ref{hyp:zeta-suppression-two-point} or
Hypothesis~\ref{hyp:zeta-suppression-four-point}); the corresponding
local rigidity theorem (Theorem~\ref{thm:two-point-rigidity} or
Theorem~\ref{thm:four-point-rigidity}); the branch-exhaustion input
(Hypothesis~\ref{hyp:branch-exhaustion}); the \(N\)-point odd-moment
cancellation (Lemma~\ref{lem:n-point-odd-moment-cancellation}); and the
aggregation step (Theorem~\ref{thm:zero-free-strip}).  Then every
nontrivial zero of \(\zeta\) satisfies \(\RePart s = \tfrac12\).
\end{theorem}

\begin{wip}\label{rem:wip-master-conditional}
The conditional statement is firm; its inputs are the section-level
results listed above.  The proof is short --- a composition of the
section-level results --- and is written out in
Section~\ref{sec:riemann-hypothesis}.
\end{wip}

\subsection{Notation and conventions}
\label{subsec:notation-and-conventions}

We use the symmetric pair convention \(T\pm h\) (rather than \(T\pm h/2\))
throughout.  The point-to-jet transform \(P_h\) of
\eqref{eq:point-to-jet-transform} is fixed by this choice.  The scale
parameter \(Q=Q(\gamma)\) is a fixed slowly growing function of the
height; all polynomial losses are stated as powers of \(Q\) with absolute
exponents.  For each height parameter \(T\), \(I_T\) denotes an
interval centered at \(T\) of length comparable to \(Q(T)^{-1}\):
there are fixed absolute constants \(0<c_I\le C_I<\infty\) such that
\[
        c_I Q(T)^{-1}\le |I_T|\le C_I Q(T)^{-1}.
\]
We also require \(I_T\subset[T/2,2T]\); high-height analysis takes
\(T\) sufficiently large that this inclusion is automatic.  The toy
polynomial-weight subdomain in
Section~\ref{sec:toy-anomaly-and-transverse-obstruction} uses the
slow-scale condition \(Q(T)=o(q(T))\), where \(q=\theta'\); when that
subdomain is not being invoked, the relevant lemmas state their window
hypotheses explicitly.  ``Retained packets'' refers to a polynomial-weight
sub-family of the local packets at height \(\gamma\) on which the
chart-regularity and Gram nondegeneracy hypotheses of
Definition~\ref{def:local-phase-chart} hold.

% =============================================================================
\section{Local kernel and jet normalization}
\label{sec:local-kernel-and-jet-normalization}
\statuspaper{LIVE}\quad
\statusmig{migrated}\quad
\statusreferee{in-progress}\quad
\statussympy[rh/sympy/sec-local-kernel-and-jet-normalization.py]{verified}\quad
\statussim[rh/simulation/sec-local-kernel-and-jet-normalization.py]{verified}\quad
\statuslean[rh/lean/RH/LocalKernelJetNormalization.lean]{in-progress}
\par\medskip

This section establishes the local geometric machinery used
throughout: the Riemann--Siegel phase chart \(\Ph_T = \theta\) on the
height window \(I_T\) of
\S\ref{subsec:notation-and-conventions}
(Definition~\ref{def:local-phase-chart}), the phase kernel \(K_\Ph\)
(Definition~\ref{def:phase-kernel}), and the Gram-normalized
point-to-jet transform \(P_h\) of
\eqref{eq:point-to-jet-transform}.

\subsection{The Riemann--Siegel phase chart}
\label{subsec:local-phase-chart}

\begin{definition}[Riemann--Siegel phase]
\label{def:riemann-siegel-phase}
Let \(L(z)\) be the unique holomorphic branch of \(\log\Gamma z\) on
\(\Re z>0\) for which \(L(x)=\log\Gamma(x)\in\mathbb R\) when \(x>0\).
For \(t>0\), define
\begin{equation}
\label{eq:theta-definition}
 \theta(t)
 := \Im L\!\left(\frac14+\frac{it}{2}\right)
    -\frac{t}{2}\log\pi,
\end{equation}
and \(Z(t):=e^{i\theta(t)}\zeta(1/2+it)\).  The functional equation
gives
\[
        \zeta\!\left(\tfrac12+it\right)
        =e^{-i\theta(t)}\,Z(t),
        \qquad Z(t)\in\mathbb R \text{ for } t>0.
\]
\end{definition}

\begin{remark}[Branch convention for the Riemann--Siegel phase]
\label{rem:theta-branch-convention}
The branch \(L\) in Definition~\ref{def:riemann-siegel-phase} is the
holomorphic logarithm of \(\Gamma\) on the half-plane \(\Re z>0\), not the
principal logarithm applied pointwise to \(\Gamma(z)\).  This branch exists
because \(\Gamma\) has no zeros or poles on \(\Re z>0\), and the half-plane
is simply connected; the normalization on \((0,\infty)\) fixes the additive
constant.  Any other holomorphic logarithm on a connected subdomain would
change \(\theta\) only by an additive constant \(2\pi k\), which leaves
\(q=\theta'\), the phase differences \(\theta(x)-\theta(y)\), and therefore
\(K_\theta\) unchanged.  A discontinuous branch, such as a principal-branch
representative with jumps, is not part of the definition and cannot be used
for derivative identities.
\end{remark}

\begin{lemma}[Differentiated theta asymptotics]
\label{lem:theta-derivative-asymptotics}
Uniformly for \(t\in I_T\),
\begin{align}
\label{eq:theta-derivative-asymptotics}
q(t):=\theta'(t)
&=\frac12\log\frac{t}{2\pi}-\frac{1}{48 t^2}+O(t^{-4}),\\
q'(t)=\theta''(t)
&=\frac{1}{2t}+O(t^{-3}),\\
q''(t)=\theta'''(t)
&=-\frac{1}{2t^2}+O(t^{-4}).
\end{align}
The constants in the \(O\)-terms are absolute.
\end{lemma}

\begin{proof}
Let \(z=1/4+it/2\).  The half-plane \(\Re z\ge 1/4\) lies in a fixed
Stirling sector.  By the differentiated form of Stirling's expansion,
after truncating \(L(z)\) at \(z^{-3}\) the remainder and its
\(t\)-derivatives up to order three are uniform in this sector, with
the corresponding differentiated powers of \(|z|\).  Taking imaginary
parts in \eqref{eq:theta-definition} gives the standard
Riemann--Siegel expansion
\[
\theta(t)=\frac{t}{2}\log\frac{t}{2\pi}-\frac{t}{2}-\frac{\pi}{8}
          +\frac{1}{48 t}+O(t^{-3}),
\]
with a remainder admitting three differentiations in \(t\) (needed for
\(q''=\theta'''\)).  Termwise differentiation gives
\(q(t)=\theta'(t)\); differentiating once and twice more gives \(q'(t)\)
and \(q''(t)\).  Since \(I_T\subset[T/2,2T]\), these estimates are
uniform on \(I_T\), with absolute constants.
\end{proof}

\begin{definition}[Local phase chart]
\label{def:local-phase-chart}
A retained high-height local phase chart is the interval \(I_T\)
together with the real smooth phase
\[
        \Ph_T(t):=\theta(t)\qquad (t\in I_T).
\]
When \(T\) is fixed by context, \(\Ph := \Ph_T\) and \(q := \Ph'\).
This is a specialized theta chart, not a general phase-chart axiom.
The chart conditions used downstream are:
\begin{enumerate}[label=\textup{(P\arabic*)},leftmargin=*]
\item \(\Ph_T = \theta\) on \(I_T\);
\item \(q(t)\ge 1\) on \(I_T\), after increasing the global lower-height
      cutoff if necessary.
\end{enumerate}
If \(Q(T)\ge 1\), then (P2) gives the polynomial-in-\(Q\) lower bound
\(q(t)\ge Q(T)^{-c_q}\) with \(c_q = 0\).  The uniform estimates
\(q(t)\asymp \log T\), \(q'(t)=O(T^{-1})\), and
\(q''(t)=O(T^{-2})\) on \(I_T\) are supplied by
Lemma~\ref{lem:theta-derivative-asymptotics}.
\end{definition}

\begin{lemma}[Phase-derivative lower bound]
\label{lem:phase-derivative-lower-bound}
Condition \textup{(P2)} of Definition~\ref{def:local-phase-chart}
holds for all sufficiently large \(T\).  More quantitatively, uniformly
on \(I_T\),
\[
        q(t)\ge \frac12\log\frac{T}{4\pi}-C\,T^{-2}
\]
for an absolute constant \(C\).
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:theta-derivative-asymptotics},
\(q(t)=\tfrac12\log(t/(2\pi))+O(t^{-2})\).  Since
\(t \in I_T \subset [T/2, 2T]\),
\(\log(t/(2\pi)) \ge \log(T/(4\pi))\), and the stated bound follows.
The right-hand side is eventually larger than \(1\).
\end{proof}

\begin{remark}[No \(\zeta\)-side regularity is used here]
\label{rem:chart-regularity-zeta-side}
The chart uses \(\zeta\) only through the identity
\(\zeta(1/2+it)=e^{-i\theta(t)}Z(t)\) and through the theta phase.
No lower bound on \(|Z|\), no zero-free condition in \(I_T\), and no
source-energy input is used in
Sections~\ref{sec:local-kernel-and-jet-normalization}--\ref{sec:jet-limit-local-blocks}.
Such conditions are imposed only in the later sections where
actual-zeta transverse suppression or source-energy transfer is
consumed.
\end{remark}

\subsection{The phase kernel}
\label{subsec:phase-kernel}

\begin{definition}[Phase kernel]
\label{def:phase-kernel}
For a real \(C^1\) phase \(\Ph\) on an interval \(I\),
\begin{equation}
\label{eq:phase-kernel}
K_\Ph(x,y)=
\begin{cases}
\dfrac{\sin\bigl(\Ph(x)-\Ph(y)\bigr)}{\pi(x-y)}, & x\ne y,\\[1.2ex]
\dfrac{q(x)}{\pi}, & x=y,
\end{cases}
\qquad q=\Ph'.
\end{equation}
\end{definition}

\begin{lemma}[Basic kernel properties]
\label{lem:phase-kernel-properties}
\(K_\Ph\) is real-valued and symmetric.  If \(\Ph\in C^1\), the
extension across the diagonal is continuous and
\[
        K_\Ph(T,T)=\frac{q(T)}{\pi}.
\]
If \(\Ph\in C^4\), the diagonal first and mixed second derivatives
exist and are given by
Lemma~\ref{lem:phase-kernel-diagonal-derivatives}.
\end{lemma}

\begin{proof}
For \(x\ne y\), symmetry follows from
\(\sin(\Ph(y)-\Ph(x))/(y-x) = \sin(\Ph(x)-\Ph(y))/(x-y)\).
Real-valuedness is immediate.  For joint continuity across the
diagonal, near any \(T\in I\) write
\[
        \Ph(x)-\Ph(y)=(x-y)A(x,y),\qquad
        A(x,y)=\int_0^1 q\bigl(y+\tau(x-y)\bigr)\,d\tau.
\]
The function \(A\) is continuous and \(A(T,T)=q(T)\).  For \(x\ne y\),
\[
        K_\Ph(x,y)
        =\frac{A(x,y)}{\pi}\,
          \frac{\sin\bigl((x-y)A(x,y)\bigr)}
               {(x-y)A(x,y)},
\]
with the last factor interpreted by its continuous value \(1\) at zero.
Hence \(K_\Ph(x,y)\to q(T)/\pi=K_\Ph(T,T)\) whenever
\((x,y)\to(T,T)\).
\end{proof}

\begin{lemma}[Off-diagonal kernel derivatives]
\label{lem:phase-kernel-derivatives}
For \(T_1\ne T_2\) with \(s=T_1-T_2\), \(\Del=\Ph(T_1)-\Ph(T_2)\),
\(q_j=q(T_j)\), and \(\Ph\in C^1\) near \(T_1, T_2\),
\begin{align*}
K_\Ph(T_1,T_2) &= \frac{\sin\Del}{\pi s},
&K_x(T_1,T_2) &= \frac{q_1\,s\cos\Del - \sin\Del}{\pi s^2},\\
K_y(T_1,T_2) &= \frac{\sin\Del - q_2\,s\cos\Del}{\pi s^2},
&K_{xy}(T_1,T_2)
&= \frac{(q_1+q_2)\,s\cos\Del + (q_1 q_2 s^2 - 2)\sin\Del}{\pi s^3}.
\end{align*}
\end{lemma}

\begin{proof}
Differentiate \(K_\Ph(x,y) = \sin(\Ph(x)-\Ph(y))/\pi(x-y)\) by the
quotient and chain rules, then evaluate at \((T_1, T_2)\).
\end{proof}

\begin{lemma}[Diagonal kernel derivatives]
\label{lem:phase-kernel-diagonal-derivatives}
If \(\Ph\in C^4\) near \(T\), then
\begin{equation}
\label{eq:diagonal-kernel-derivatives}
K_\Ph(T,T)=\frac{q(T)}{\pi},\qquad
K_x(T,T)=K_y(T,T)=\frac{q'(T)}{2\pi},
\end{equation}
\[
        K_{xy}(T,T)=\frac{q''(T)+2q(T)^3}{6\pi}.
\]
\end{lemma}

\begin{proof}
Set \(x=T+u\), \(y=T+v\), and write \(r=|u|+|v|\); derivatives below
are evaluated at \(T\).  Factor the phase difference as
\[
\Ph(T+u)-\Ph(T+v)=(u-v)A(u,v),\qquad
A(u,v)=\int_0^1 q\bigl(T+v+\tau(u-v)\bigr)\,d\tau,
\]
where the integral form extends continuously to \(u=v\).  Taylor
expansion of the integrand gives
\[
A(u,v)
= q+\frac{q'}2(u+v)+\frac{q''}{6}(u^2+uv+v^2)+O(r^3).
\]
For \(u\ne v\), and then by continuous extension to \(u=v\),
\(\Ph(T+u)-\Ph(T+v)=(u-v)A(u,v)=O(r)\) gives
\[
\frac{\sin(\Ph(T+u)-\Ph(T+v))}{u-v}
= A(u,v)-\frac{(u-v)^2}{6}A(u,v)^3+O(r^3).
\]
Keeping terms through total degree two gives
\[
K_\Ph(T+u,T+v)
= \frac1\pi\!\left[
 q + \frac{q'}{2}(u+v)
 + \!\left(\frac{q''}{6} - \frac{q^3}{6}\right)\!(u^2+v^2)
 + \!\left(\frac{q''}{6} + \frac{q^3}{3}\right)\!uv
 + O(r^3)\right].
\]
The coefficients of \(u\), \(v\), and \(uv\) are respectively
\(K_x(T,T)\), \(K_y(T,T)\), and \(K_{xy}(T,T)\), proving the claim.
\end{proof}

\subsection{Point-to-jet transform}
\label{subsec:point-to-jet-transform}

For symmetric pairs \(T\pm h\), define the Gram-normalized coalescing
even/odd transform
\begin{equation}
\label{eq:point-to-jet-transform}
P_h
=\frac1{\sqrt2}
\begin{pmatrix}
1 & 1\\[0.6ex]
-1/(2h) & 1/(2h)
\end{pmatrix}
=\diag(\sqrt 2, 1/\sqrt 2)\,
\begin{pmatrix}
1/2 & 1/2\\[0.6ex]
-1/(2h) & 1/(2h)
\end{pmatrix}.
\end{equation}
Thus \(P_h\) is the literal central value/derivative jet transform
followed by the fixed diagonal rescaling
\(\diag(\sqrt 2, 1/\sqrt 2)\); at the level of Gram blocks this induces
the corresponding diagonal congruence.  The value/derivative basis
produced by \(P_h\) is the \emph{Gram-normalized basis}.

With this convention,
\begin{equation}
\label{eq:same-point-as-kernel-derivatives}
J(T)=
\begin{pmatrix}
2K_\Ph(T,T) & \partial_y K_\Ph(T,T)\\[0.6ex]
\partial_x K_\Ph(T,T) & \tfrac12 \partial_{xy} K_\Ph(T,T)
\end{pmatrix},
\end{equation}
which is the same-point block computed explicitly in
Lemma~\ref{lem:same-point-jet-limit}.

\begin{remark}[Pair-separation convention]
\label{rem:pair-separation-convention}
The pair is \(T-h, T+h\), with separation \(2h\); the lower row of
\(P_h\) carries \(1/(2h)\).  Any formula imported from the alternative
\(T\pm h/2\) convention or from the literal-jet matrix with lower row
\((-1/h, 1/h)\) must be re-conjugated before use.
\end{remark}

\begin{remark}[Convention check]
\label{rem:normalization-audit}
With the literal central value/derivative transform at the pair
\(T\pm h\), the same-point limit would be
\[
\frac1\pi
\begin{pmatrix}
q(T) & \tfrac12 q'(T)\\[0.6ex]
\tfrac12 q'(T) & \tfrac16\bigl(q''(T)+2q(T)^3\bigr)
\end{pmatrix},
\]
related to \(J(T)\) by the diagonal congruence
\(\diag(\sqrt 2, 1/\sqrt 2)\) of \eqref{eq:point-to-jet-transform}; the
\((1,1)\) entry doubles and the \((2,2)\) entry is halved.  All
same-point blocks, cross-blocks, finite-scale blocks, whitening
matrices, and quotient covectors in this paper are read in the
Gram-normalized convention.
\end{remark}

% =============================================================================
\section{Jet-limit local blocks}
\label{sec:jet-limit-local-blocks}
\statuspaper{LIVE}\quad
\statusmig{migrated}\quad
\statusreferee{in-progress}\quad
\statussympy[rh/sympy/sec-jet-limit-local-blocks.py]{verified}\quad
\statussim[rh/simulation/sec-jet-limit-local-blocks.py]{verified}\quad
\statuslean[rh/lean/RH/JetLimitLocalBlocks.lean]{in-progress}
\par\medskip

From the phase kernel \(K_\Ph\) and the Gram-normalized transform
\(P_h\) of Section~\ref{sec:local-kernel-and-jet-normalization}, the
small-separation limits of \(K_\Ph\) at one and two centers produce
the same-point Gram block \(J(T)\)
(Lemma~\ref{lem:same-point-jet-limit}) and the cross-block
\(N_{12}(T_1,T_2)\) (Lemma~\ref{lem:cross-block-jet-limit}); for the
theta phase, \(J(T)\succ 0\) at sufficiently large height
(Lemma~\ref{lem:same-point-gram-positivity}).

\subsection{Same-point jet limit}
\label{subsec:same-point-jet-limit}

\begin{lemma}[Same-point jet limit]
\label{lem:same-point-jet-limit}
Assume \(\Ph\in C^5\) near \(T\).  Let
\[
A_h(T)=
\begin{pmatrix}
K_\Ph(T-h,T-h) & K_\Ph(T-h,T+h)\\
K_\Ph(T+h,T-h) & K_\Ph(T+h,T+h)
\end{pmatrix}
\]
with row and column order \((T-h, T+h)\).  Then
\[
        P_h\,A_h(T)\,P_h^\top \;=\; J(T) + O(h^2)
        \qquad (h\to 0),
\]
where the \(O(h^2)\) is entrywise, with a constant depending only on a
fixed neighborhood of \(T\) and on a local \(C^5\)-bound for \(\Ph\).  The
limiting block is
\begin{equation}
\label{eq:same-point-J}
J(T)=\frac1\pi
\begin{pmatrix}
2q(T) & \tfrac12 q'(T)\\[1ex]
\tfrac12 q'(T) & \tfrac1{12}\bigl(q''(T)+2q(T)^3\bigr)
\end{pmatrix}.
\end{equation}
\end{lemma}

\begin{proof}
Derivatives below are evaluated at \(T\).  Taylor expansion gives
\[
\Ph(T\pm h) = \Ph(T) \pm hq + \frac{h^2}{2}q'
            \pm \frac{h^3}{6}q'' + \frac{h^4}{24}q'''
            + O(h^5),
\]
so
\[
\Ph(T-h)-\Ph(T+h) = -2hq - \frac{h^3}{3}q'' + O(h^5).
\]
Using \(\sin z = z - z^3/6 + O(z^5)\),
\begin{equation}
\label{eq:A12-same-point-expansion}
K_\Ph(T-h, T+h)
= \frac{q}{\pi} + \frac{h^2}{6\pi}(q'' - 4q^3) + O(h^4).
\end{equation}
Also \(K_\Ph(T\pm h,T\pm h)=q(T\pm h)/\pi\), with
\[
q(T\pm h)=q\pm hq'+\frac{h^2}{2}q''
          \pm\frac{h^3}{6}q'''+O(h^4).
\]
The \(O(h^5)\) phase remainder and the \(O(h^4)\) \(q\)-remainder are
controlled by a local \(C^5\)-bound for \(\Ph\); after division by the
separation \(2h\), the off-diagonal kernel expansion has an \(O(h^4)\)
remainder, the order needed below since the \((2,2)\) jet entry
divides a second difference by \(h^2\).
For symmetric \(M\), conjugation by \eqref{eq:point-to-jet-transform}
gives
\begin{align*}
(P_h M P_h^\top)_{11} &= \tfrac12(M_{11}+2M_{12}+M_{22}),\\
(P_h M P_h^\top)_{12} &= \tfrac{1}{4h}(M_{22}-M_{11}),\\
(P_h M P_h^\top)_{22} &= \tfrac{1}{8h^2}(M_{11}-2M_{12}+M_{22}).
\end{align*}
Substituting \eqref{eq:A12-same-point-expansion} and the Taylor series
of \(q(T\pm h)\): the constant and odd terms cancel in the second
difference, while the first difference cancels its constant and even
terms.  The divisions by \(h\) and \(h^2\) therefore leave entrywise
\(O(h^2)\) remainders:
\begin{align*}
(P_h A_h P_h^\top)_{11} &= \frac{2q}{\pi} + O(h^2),\\
(P_h A_h P_h^\top)_{12} &= \frac{q'}{2\pi} + O(h^2),\\
(P_h A_h P_h^\top)_{22} &= \frac{q''+2q^3}{12\pi} + O(h^2),
\end{align*}
which is \eqref{eq:same-point-J}.
\end{proof}

\subsection{Cross-block jet limit}
\label{subsec:cross-block-jet-limit}

\begin{lemma}[Cross-block jet limit]
\label{lem:cross-block-jet-limit}
Assume \(\Ph\in C^5\) in neighborhoods of \(T_1\) and \(T_2\), let
\(T_1\ne T_2\), set
\[
        s = T_1 - T_2,
        \qquad \Del = \Ph(T_1)-\Ph(T_2),
        \qquad q_j = q(T_j),
\]
and assume \(0 < h < |s|/3\), with \(h\) also sufficiently small that
the four sampled points lie in the chosen neighborhoods of \(T_1\) and
\(T_2\).  Define
\[
C_h(T_1, T_2)=
\begin{pmatrix}
K_\Ph(T_1-h, T_2-h) & K_\Ph(T_1-h, T_2+h)\\
K_\Ph(T_1+h, T_2-h) & K_\Ph(T_1+h, T_2+h)
\end{pmatrix}
\]
with row order \((T_1-h, T_1+h)\) and column order \((T_2-h, T_2+h)\).
Then
\[
        P_h\,C_h(T_1, T_2)\,P_h^\top
        \;=\; \frac1\pi N_{12}(T_1, T_2) + O(h^2)
        \qquad (h\to 0),
\]
where the \(O(h^2)\) is entrywise for fixed \(T_1\ne T_2\); the implied
constant may depend on a finite power of \(|s|^{-1}\) and on local
\(C^5\)-bounds for \(\Ph\), but not on \(h\).  Here
\begin{equation}
\label{eq:cross-N12}
N_{12}=
\begin{pmatrix}
\dfrac{2\sin\Del}{s}
&
\dfrac{\sin\Del - q_2 s\cos\Del}{s^2}
\\[2.4ex]
\dfrac{q_1 s\cos\Del - \sin\Del}{s^2}
&
\dfrac{(q_1+q_2)s\cos\Del + (q_1 q_2 s^2 - 2)\sin\Del}{2s^3}
\end{pmatrix}.
\end{equation}
\end{lemma}

\begin{proof}
The kernel is smooth in a neighborhood of \((T_1, T_2)\), and the
hypothesis \(h<|s|/3\) gives
\(|s+u_1-u_2|\ge |s|/3\) for \(|u_1|,|u_2|\le h\), bounding the
Taylor remainder on the sampled square.  Write
\(K_{ab} = \partial_x^a \partial_y^b K_\Ph(T_1, T_2)\).  Taylor
expansion to total order four gives, uniformly for
\(u_1, u_2 \in \{-h, +h\}\),
\[
K_\Ph(T_1+u_1, T_2+u_2)
= \sum_{a+b\le 4}\frac{K_{ab}}{a!\,b!}\, u_1^a\, u_2^b + O_s(h^5).
\]
The subscript indicates that the constant may depend on a finite power
of \(|s|^{-1}\) and on local \(C^5\)-bounds for \(\Ph\) in the chosen
off-diagonal neighborhoods.  For a general \(2\times 2\) matrix \(M\),
\begin{align*}
(P_h M P_h^\top)_{11}
&= \tfrac12(M_{11} + M_{12} + M_{21} + M_{22}),\\
(P_h M P_h^\top)_{12}
&= \tfrac{1}{4h}(-M_{11} + M_{12} - M_{21} + M_{22}),\\
(P_h M P_h^\top)_{21}
&= \tfrac{1}{4h}(-M_{11} - M_{12} + M_{21} + M_{22}),\\
(P_h M P_h^\top)_{22}
&= \tfrac{1}{8h^2}(M_{11} - M_{12} - M_{21} + M_{22}).
\end{align*}
Equivalently, these four expressions apply the sign weights
\(1\), \(\sigma_2\), \(\sigma_1\), \(\sigma_1\sigma_2\) respectively to
the four samples with \(u_i = \sigma_i h\).  Parity selects the
required leading terms: the next surviving polynomial monomials in the
\((1,1)\) entry have total degree at least two, contributing \(O(h^2)\);
the \((1,2)\) and \((2,1)\) numerators select monomials with odd
degree in one variable, so after division by \(h\) the surviving
polynomial corrections are \(O(h^2)\); the \((2,2)\) numerator selects
monomials odd in both variables, and division by \(h^2\) again leaves
\(O(h^2)\).  The Taylor remainder \(O_s(h^5)\) per sample contributes
\(O_s(h^5)\) to the \((1,1)\) entry (no division), \(O_s(h^4)\) to the
off-diagonal entries (division by \(4h\)), and \(O_s(h^3)\) to the
\((2,2)\) entry (division by \(8h^2\)).  Hence
\[
(P_h C_h P_h^\top)_{11} = 2 K_{00} + O(h^2),\qquad
(P_h C_h P_h^\top)_{12} = K_{01} + O(h^2),
\]
\[
(P_h C_h P_h^\top)_{21} = K_{10} + O(h^2),\qquad
(P_h C_h P_h^\top)_{22} = \tfrac12 K_{11} + O(h^2).
\]
Substituting the off-diagonal derivative formulas of
Lemma~\ref{lem:phase-kernel-derivatives} gives \eqref{eq:cross-N12}.
\end{proof}

\begin{remark}[Fixed-separation scope]
\label{rem:cross-block-fixed-separation-scope}
Lemma~\ref{lem:cross-block-jet-limit} is an off-diagonal jet limit at
fixed separation.  It is not a collision expansion for \(T_1\to T_2\);
the constants are not asserted to be uniform as \(s=T_1-T_2\to 0\).
Any two-center blow-up or near-coalescence analysis must be derived
from a separate scaling argument, rather than by citing this lemma
with \(|s|\) comparable to \(h\).
\end{remark}

\subsection{Same-point Gram positivity}
\label{subsec:same-point-gram-positivity}

\begin{definition}[Same-point Gram determinant]
\label{def:same-point-gram-determinant}
\begin{equation}
\label{eq:same-point-gram-determinant}
D_J(T) \;:=\; 4\,q(T)^4 + 2\,q(T)\,q''(T) - 3\,q'(T)^2.
\end{equation}
\end{definition}

\begin{lemma}[Algebraic same-point Gram criterion]
\label{lem:algebraic-same-point-gram-criterion}
For \(J(T)\) of \eqref{eq:same-point-J},
\begin{equation}
\label{eq:J-trace-det}
\Tr J(T) = \frac{2 q(T)^3 + 24\,q(T) + q''(T)}{12\pi},\qquad
\det J(T) = \frac{D_J(T)}{12\pi^2}.
\end{equation}
Moreover,
\[
        J(T)\succ 0
        \quad\Longleftrightarrow\quad
        q(T) > 0 \quad\text{and}\quad D_J(T) > 0.
\]
\end{lemma}

\begin{proof}
The trace and determinant follow by direct computation from
\eqref{eq:same-point-J}.  Since \(J(T)\) is real symmetric,
Sylvester's criterion gives positive definiteness exactly when its
leading principal minor \(2q(T)/\pi\) and its determinant are
positive.
\end{proof}

\begin{lemma}[Same-point Gram positivity for the theta phase]
\label{lem:same-point-gram-positivity}
For \(\Ph_T = \theta\), and for all sufficiently large retained
heights, \(J(t)\) is positive definite uniformly for \(t\in I_T\).
More precisely,
\begin{equation}
\label{eq:lambda-min-asymptotic}
        \lambda_{\min}(J(t))
        = \frac{2 q(t)}{\pi}\,(1 + o_T(1))
        = \frac{1}{\pi}\,\log\frac{t}{2\pi}\,(1 + o_T(1))
        \qquad(t\in I_T),
\end{equation}
where the error is uniform on \(I_T\).  In particular this holds at the
center \(t=T\).  After increasing the lower-height cutoff if necessary,
\(\lambda_{\min}(J(t)) \ge 1\) uniformly on \(I_T\); hence the
polynomial-in-\(Q\) lower bound
\(\lambda_{\min}(J(t)) \ge Q(T)^{-C_J}\) holds with \(C_J = 0\)
whenever \(Q(T) \ge 1\).  The cutoff is qualitative; no explicit
numerical lower height is claimed here.
\end{lemma}

\begin{proof}
Let \(t\in I_T\).  By Lemma~\ref{lem:theta-derivative-asymptotics},
uniformly on \(I_T\),
\[
q(t) = \tfrac12 \log(t/(2\pi)) + O(t^{-2}),\qquad
q'(t) = O(t^{-1}),\qquad q''(t) = O(t^{-2}).
\]
Therefore, uniformly on \(I_T\),
\[
D_J(t) = 4\,q(t)^4 + O\!\bigl(q(t)\,t^{-2}\bigr) + O(t^{-2})
       = 4\,q(t)^4\,(1 + o_T(1)) > 0
\]
for sufficiently large \(T\), and \(q(t)>0\).  By
Lemma~\ref{lem:algebraic-same-point-gram-criterion},
\(J(t) \succ 0\).

Let \(0 < \lambda_1(t) \le \lambda_2(t)\) be the eigenvalues of
\(J(t)\).  Since \(\lambda_2(t) \le \Tr J(t)\),
\[
\lambda_1(t) = \frac{\det J(t)}{\lambda_2(t)}
          \ge \frac{\det J(t)}{\Tr J(t)}
          = \frac{D_J(t)}{\pi(2 q(t)^3 + 24\,q(t) + q''(t))}
          = \frac{2 q(t)}{\pi}\,(1 + o_T(1)),
\]
uniformly for \(t\in I_T\).  The Rayleigh quotient at \(e_1\) gives
\(\lambda_1(t) \le J_{11}(t) = 2 q(t)/\pi\), proving
\eqref{eq:lambda-min-asymptotic}.
\end{proof}

\begin{remark}[Scope of the positivity lemma]
\label{rem:scope-of-gram-positivity}
Lemma~\ref{lem:same-point-gram-positivity} is theta-specific.  For an
arbitrary real phase, the safe statement is only the algebraic
criterion \(q > 0\) and \(D_J > 0\).  This lemma does not prove any
lower bound for unrelated anisotropy functionals such as
\(q'' - 6q + 2q^3\), nor does it supply source-energy input of the
kind consumed in Section~\ref{sec:source-energy-supply}.
\end{remark}

% =============================================================================
\section{Finite-scale local blocks and whitening}
\label{sec:finite-scale-local-blocks-and-whitening}
\statuspaper{LIVE}\quad
\statusmig{migrated}\quad
\statusreferee{in-progress}\quad
\statussympy[rh/sympy/sec-finite-scale-local-blocks-and-whitening.py]{verified}\quad
\statussim[rh/simulation/sec-finite-scale-local-blocks-and-whitening.py]{verified}\quad
\statuslean{n/a}
\par\medskip

Around a midpoint \(m\) at finite separation \(s\), the same-point and
cross-block jets of Section~\ref{sec:jet-limit-local-blocks} give two
same-point Gram blocks \(G_{m,\pm}(s)\) and a mixed block \(N_m(s)\).
This section records the finite real-axis block package and the
whitening-factor loss used by later comparison arguments.

\begin{definition}[Finite packet domain]
\label{def:finite-packet-domain}
For a retained theta chart \(I_T\), set \(t_\pm = m\pm s/2\) and
\[
        \mathcal D_T
        :=\bigl\{(m,s)\in\mathbb R^2 : t_-\in I_T,\ t_+\in I_T\bigr\}.
\]
Write \(\mathcal D_T^\times := \{(m,s)\in\mathcal D_T : s\ne 0\}\).
The orientation convention is that rows correspond to the center
\(t_-\) and columns to the center \(t_+\).  In applications \(s>0\),
but allowing signed \(s\) makes the removable-singularity statement at
\(s=0\) precise.  Uniform estimates below are taken on
\(\mathcal D_T\), after the global lower-height cutoff has been
enlarged if necessary.
\end{definition}

\subsection{Finite same-point and mixed blocks}
\label{subsec:finite-same-point-and-mixed-blocks}

For \((m,s)\in\mathcal D_T\), write
\[
        t_\pm = m\pm s/2,
        \qquad q_\pm = q(t_\pm),
        \qquad \Del_m(s) = \Ph(t_-)-\Ph(t_+).
\]

\begin{definition}[Finite same-point and mixed blocks]
\label{def:finite-same-point-and-mixed-blocks}
For \((m,s)\in\mathcal D_T\), the finite same-point blocks are
\begin{equation}
\label{eq:Gpm}
G_{m,\pm}(s)
=\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \tfrac12 q'(t_\pm)\\[0.8ex]
\tfrac12 q'(t_\pm) & \tfrac1{12}\bigl(q''(t_\pm)+2q(t_\pm)^3\bigr)
\end{pmatrix}.
\end{equation}
For \(s\ne 0\), the finite mixed block is
\begin{equation}
\label{eq:Nm}
N_m(s)
=\frac1\pi
\begin{pmatrix}
-\dfrac{2\sin\Del_m(s)}{s}
&
\dfrac{\sin\Del_m(s)+q_+ s\cos\Del_m(s)}{s^2}
\\[2.4ex]
-\dfrac{\sin\Del_m(s)+q_- s\cos\Del_m(s)}{s^2}
&
\dfrac{(q_-+q_+)s\cos\Del_m(s)+(2-q_- q_+ s^2)\sin\Del_m(s)}{2s^3}
\end{pmatrix}.
\end{equation}
\end{definition}

\begin{lemma}[Exact finite-block interpretation]
\label{lem:finite-blocks-exact-interpretation}
For \((m,s)\in\mathcal D_T\),
\[
        G_{m,\pm}(s) = J(t_\pm).
\]
For \((m,s)\in\mathcal D_T^\times\), moreover,
\begin{equation}
\label{eq:Nm-kernel-derivative-form}
N_m(s)
=
\begin{pmatrix}
2K_\Ph(t_-,t_+) & \partial_y K_\Ph(t_-,t_+)\\[0.6ex]
\partial_x K_\Ph(t_-,t_+) & \tfrac12\partial_{xy}K_\Ph(t_-,t_+)
\end{pmatrix}.
\end{equation}
Equivalently, \(N_m(s) = \pi^{-1} N_{12}\) for the matrix \(N_{12}\) of
\eqref{eq:cross-N12} taken at \((T_1, T_2) = (t_-, t_+)\), with
\(s_{12} = T_1 - T_2 = -s\) absorbed into the displayed signs in
\eqref{eq:Nm}.
\end{lemma}

\begin{proof}
The identity \(G_{m,\pm}(s) = J(t_\pm)\) is immediate by comparing
\eqref{eq:Gpm} with \eqref{eq:same-point-J}.  For the mixed block,
apply the off-diagonal kernel-derivative formulas of
Lemma~\ref{lem:phase-kernel-derivatives} at
\((T_1, T_2) = (t_-, t_+)\); there \(s_{12} = t_- - t_+ = -s\),
\(q_1 = q_-\), \(q_2 = q_+\), and \(\Delta = \Del_m(s)\).
Substitution gives the four entries of
\eqref{eq:Nm-kernel-derivative-form}, which match \eqref{eq:Nm} entry
by entry.
\end{proof}

\begin{lemma}[Removable singularity of \(N_m(s)\)]
\label{lem:Nm-removable-singularity}
Let \(m\in I_T\).  If \(\Ph\in C^3\) on a neighborhood of \(m\), then,
as \(s\to 0\) with \((m,s)\in\mathcal D_T^\times\), the entries of
\(N_m(s)\) of \eqref{eq:Nm} extend continuously to \(s=0\) with
\begin{equation}
\label{eq:Nm-at-zero}
        N_m(0) = J(m)
        = \frac1\pi
        \begin{pmatrix}
        2q(m) & \tfrac12 q'(m)\\[0.8ex]
        \tfrac12 q'(m) & \tfrac1{12}\bigl(q''(m)+2q(m)^3\bigr)
        \end{pmatrix}.
\end{equation}
\end{lemma}

\begin{proof}
Write \(q = q(m)\), \(a = q'(m)\), \(b = q''(m)\).  Taylor expansion
about \(m\), using the symmetric points \(m\pm s/2\), gives
\[
        \Del_m(s)
        = \Ph(m-s/2)-\Ph(m+s/2)
        = -qs - \frac{b}{24}s^3 + o(s^3),
\]
\[
        q_+ = q + \frac{a}{2}s + \frac{b}{8}s^2 + o(s^2),
        \qquad
        q_- = q - \frac{a}{2}s + \frac{b}{8}s^2 + o(s^2).
\]
Hence
\[
        \sin\Del_m(s)
        = -qs + \!\left(\frac{q^3}{6}-\frac{b}{24}\right)\!s^3
          + o(s^3),
        \qquad
        \cos\Del_m(s) = 1 - \frac{q^2}{2}s^2 + o(s^2).
\]
Substituting into \eqref{eq:Nm} entry by entry,
\begin{align*}
        -\frac{2\sin\Del_m(s)}{s}
        &= 2q + o(1),\\
        \frac{\sin\Del_m(s)+q_+ s\cos\Del_m(s)}{s^2}
        &= \frac{a}{2} + o(1),\\
        -\frac{\sin\Del_m(s)+q_- s\cos\Del_m(s)}{s^2}
        &= \frac{a}{2} + o(1),\\
        \frac{(q_-+q_+)s\cos\Del_m(s)+(2-q_- q_+ s^2)\sin\Del_m(s)}{2s^3}
        &= \frac{b}{12}+\frac{q^3}{6}+o(1).
\end{align*}
The common factor \(1/\pi\) in \eqref{eq:Nm} gives
\eqref{eq:Nm-at-zero}.
\end{proof}

\begin{remark}[Coalescence is not the cross-block jet limit]
\label{rem:Nm-coalescence-not-cross-limit}
Lemma~\ref{lem:cross-block-jet-limit} is a fixed-center-separation
limit in the sampling parameter \(h\); its constants are not uniform
as \(s\to 0\) (Remark~\ref{rem:cross-block-fixed-separation-scope}).
Lemma~\ref{lem:Nm-removable-singularity} is a separate coalescence
statement in the center-separation parameter \(s\), proved by direct
Taylor expansion above.  From this point on, \(N_m(0)\) denotes the
continuous extension supplied by Lemma~\ref{lem:Nm-removable-singularity}.
\end{remark}

\subsection{Whitened finite block}
\label{subsec:whitened-finite-block}

\begin{definition}[Whitened finite block]
\label{def:whitened-finite-block}
For \((m,s)\in\mathcal D_T\), with \(N_m(0)\) understood by continuous
extension, whenever \(G_{m,-}(s)\) and \(G_{m,+}(s)\) are positive
definite, let \(G_{m,\pm}(s)^{-1/2}\) denote the positive definite
inverse square root and set
\begin{equation}
\label{eq:omega-finite}
\widehat\Om_\z(s;m)
:= G_{m,-}(s)^{-1/2}\,N_m(s)\,G_{m,+}(s)^{-1/2}.
\end{equation}
\end{definition}

\begin{corollary}[Coalescence: \(\widehat\Om_\z(0;m) = I_2\)]
\label{cor:omega-coalescence}
For every \(m\in I_T\) at sufficiently large height,
\(\widehat\Om_\z(s;m)\) extends continuously to \(s=0\), along
\((m,s)\in\mathcal D_T\), with \(\widehat\Om_\z(0;m) = I_2\).
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:same-point-gram-positivity}, \(J(m)\succ 0\) at
every midpoint \(m\in I_T\) at sufficiently large height.  By continuity,
\(G_{m,\pm}(s) = J(m\pm s/2)\) remain positive definite for all
sufficiently small \(|s|\) with \((m,s)\in\mathcal D_T\), and the map
\(G\mapsto G^{-1/2}\) is continuous on the positive definite cone.
Lemma~\ref{lem:Nm-removable-singularity} gives \(N_m(0) = J(m)\),
while \(G_{m,\pm}(0) = J(m)\) by
Lemma~\ref{lem:finite-blocks-exact-interpretation}.  Therefore
\(\widehat\Om_\z(0;m) = J(m)^{-1/2}\,J(m)\,J(m)^{-1/2} = I_2\).
\end{proof}

\subsection{Whitening loss}
\label{subsec:whitening-loss}

\begin{lemma}[Operator-norm bound for \(G_{m,\pm}^{-1/2}\)]
\label{lem:whitening-loss}
For \(\Ph_T = \theta\) on \(I_T\), after enlarging the global
lower-height cutoff if necessary, \(G_{m,\pm}(s)\) are positive
definite for every \((m,s)\in\mathcal D_T\), and there is a quantity
\(\varepsilon_T\to 0\), independent of \((m,s)\in\mathcal D_T\), such
that
\begin{equation}
\label{eq:whitening-loss-bound}
        \bigl\|G_{m,\pm}(s)^{-1/2}\bigr\|_{\op}
        \;\le\;
        \sqrt{\frac{\pi}{2\,q(t_\pm)}}\,(1+\varepsilon_T)
        \qquad (T\to\infty).
\end{equation}
After possibly enlarging the same lower-height cutoff,
\begin{equation}
\label{eq:whitening-loss-polynomial}
        \bigl\|G_{m,\pm}(s)^{-1/2}\bigr\|_{\op}
        \;\le\; Q(T)^{C_W}
\end{equation}
uniformly on \(\mathcal D_T\), with absolute exponent \(C_W = 0\)
whenever \(Q(T)\ge 1\).
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:finite-blocks-exact-interpretation},
\(G_{m,\pm}(s) = J(t_\pm)\); since \((m,s)\in\mathcal D_T\) implies
\(t_\pm\in I_T\subset[T/2, 2T]\), the theta-derivative estimates of
Lemma~\ref{lem:theta-derivative-asymptotics} are uniform at
\(t = t_\pm\).  The proof of Lemma~\ref{lem:same-point-gram-positivity}
then applies with \(T\) replaced by an arbitrary \(t\in I_T\), giving,
uniformly on \(I_T\),
\[
        \lambda_{\min}(J(t))
        = \frac{2q(t)}{\pi}\,(1 + o(1)).
\]
Equivalently, for some \(\delta_T\to 0\) independent of \(t\in I_T\),
\[
        \lambda_{\min}(J(t))
        \;\ge\; \frac{2q(t)}{\pi}\,(1-\delta_T).
\]
For large \(T\), \(1-\delta_T > 0\); the finite same-point blocks are
positive definite, and
\[
        \bigl\|G_{m,\pm}(s)^{-1/2}\bigr\|_{\op}
        = \lambda_{\min}(G_{m,\pm}(s))^{-1/2}
        \;\le\; \sqrt{\frac{\pi}{2\,q(t_\pm)}}\,(1-\delta_T)^{-1/2}.
\]
Absorbing \((1-\delta_T)^{-1/2}\) into \(1+\varepsilon_T\) gives
\eqref{eq:whitening-loss-bound}.

For the polynomial bound, the uniform asymptotic above together with
Lemma~\ref{lem:phase-derivative-lower-bound} gives
\(\lambda_{\min}(J(t))\to\infty\) uniformly for \(t\in I_T\); after
enlarging the lower-height cutoff,
\(\lambda_{\min}(J(t))\ge 1\) uniformly on \(I_T\).  Hence
\(\|G_{m,\pm}(s)^{-1/2}\|_{\op}\le 1\le Q(T)^0\) whenever
\(Q(T)\ge 1\), which is \eqref{eq:whitening-loss-polynomial} with
\(C_W = 0\).
\end{proof}

\begin{remark}[Scope of Lemma~\ref{lem:whitening-loss}]
\label{rem:whitening-loss-scope}
Lemma~\ref{lem:whitening-loss} controls only the real-axis same-point
whitening factors attached to the theta phase.  It does not prove
actual-zeta transverse suppression, does not supply source-energy
input, does not give a uniform bound on \(\widehat\Om_\z(s;m)\) itself
beyond the whitening-factor loss, and does not give complex-disk or
holomorphic whitening estimates.  Any stronger whitening statement
needed for a later complex-analytic argument must be introduced as a
separate input or proved in a separate section.
\end{remark}

\subsection{Two-sided whitening ledger}
\label{subsec:two-sided-whitening-ledger}

The one-sided estimate of Lemma~\ref{lem:whitening-loss} prevents
same-point whitening from enlarging upper bounds.  Lower bounds require a
separate ledger, because left and right multiplication by
\(G_{m,\pm}^{-1/2}\) can attenuate a nonzero matrix.  Define the whitening
map on \(2\times2\) real matrices by
\begin{equation}
\label{eq:whitening-map}
        \mathsf W_{m,s}(X)
        :=G_{m,-}(s)^{-1/2}\,X\,G_{m,+}(s)^{-1/2}.
\end{equation}

\begin{lemma}[Spectral size of the finite same-point blocks]
\label{lem:finite-same-point-spectral-size}
For \(\Ph_T=\theta\), uniformly for \((m,s)\in\mathcal D_T\),
\begin{align}
\label{eq:G-lambda-min-asymptotic}
\lambda_{\min}\bigl(G_{m,\pm}(s)\bigr)
&=\frac{2q(t_\pm)}{\pi}\,(1+o_T(1)),\\
\label{eq:G-lambda-max-asymptotic}
\lambda_{\max}\bigl(G_{m,\pm}(s)\bigr)
&=\frac{q(t_\pm)^3}{6\pi}\,(1+o_T(1)).
\end{align}
Consequently, after increasing the global lower-height cutoff, there are
absolute constants \(c,C>0\) such that, uniformly on \(\mathcal D_T\),
\begin{equation}
\label{eq:G-spectral-comparable}
        c\,q(t_\pm)
        \le \lambda_{\min}\bigl(G_{m,\pm}(s)\bigr)
        \le C\,q(t_\pm),
        \qquad
        c\,q(t_\pm)^3
        \le \lambda_{\max}\bigl(G_{m,\pm}(s)\bigr)
        \le C\,q(t_\pm)^3.
\end{equation}
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:finite-blocks-exact-interpretation},
\(G_{m,\pm}(s)=J(t_\pm)\).  Since \((m,s)\in\mathcal D_T\), both
\(t_\pm\in I_T\), and the theta derivative asymptotics of
Lemma~\ref{lem:theta-derivative-asymptotics} are uniform at these two
points.  The proof of Lemma~\ref{lem:same-point-gram-positivity} therefore
applies uniformly with \(T\) replaced by any \(t\in I_T\), giving
\eqref{eq:G-lambda-min-asymptotic}.

For the largest eigenvalue, use
\[
        \lambda_{\max}(J(t))
        =\Tr J(t)-\lambda_{\min}(J(t)).
\]
By \eqref{eq:J-trace-det}, uniformly for \(t\in I_T\),
\[
        \Tr J(t)
        =\frac{2q(t)^3+24q(t)+q''(t)}{12\pi}
        =\frac{q(t)^3}{6\pi}\,(1+o_T(1)),
\]
while \(\lambda_{\min}(J(t))=O(q(t))\).  Since \(q(t)\to\infty\)
uniformly on \(I_T\), the trace term of size \(q(t)^3\) dominates,
which gives \eqref{eq:G-lambda-max-asymptotic}.  The two-sided
comparability bounds \eqref{eq:G-spectral-comparable} follow by enlarging
the lower-height cutoff once more.
\end{proof}

\begin{lemma}[Two-sided whitening ledger]
\label{lem:two-sided-whitening-ledger}
For \(\Ph_T=\theta\), after increasing the global lower-height cutoff,
there are absolute constants \(c,C>0\) such that for every
\((m,s)\in\mathcal D_T\) and every real \(2\times2\) matrix \(X\),
\begin{equation}
\label{eq:two-sided-whitening-ledger}
        c\,\bigl(q(t_-)q(t_+)\bigr)^{-3/2}\,
        \|X\|_{\op}
        \le
        \|\mathsf W_{m,s}(X)\|_{\op}
        \le
        C\,\bigl(q(t_-)q(t_+)\bigr)^{-1/2}\,
        \|X\|_{\op}.
\end{equation}
In particular, the lower-bound attenuation of two-sided whitening is at
worst
\begin{equation}
\label{eq:two-sided-whitening-log-loss}
        \bigl(q(t_-)q(t_+)\bigr)^{-3/2}
        \asymp (\log T)^{-3}
\end{equation}
uniformly on \(\mathcal D_T\).
\end{lemma}

\begin{proof}
Let
\[
        A=G_{m,-}(s)^{-1/2},\qquad B=G_{m,+}(s)^{-1/2}.
\]
The upper bound follows from submultiplicativity:
\[
        \|AXB\|_{\op}
        \le \|A\|_{\op}\,\|X\|_{\op}\,\|B\|_{\op}
        = \lambda_{\min}(G_{m,-})^{-1/2}
          \lambda_{\min}(G_{m,+})^{-1/2}\,\|X\|_{\op}.
\]
Using the lower-eigenvalue estimate in
Lemma~\ref{lem:finite-same-point-spectral-size} gives the right-hand
inequality in \eqref{eq:two-sided-whitening-ledger}.

For the lower bound, write
\[
        X=A^{-1}(AXB)B^{-1}.
\]
Therefore
\[
        \|X\|_{\op}
        \le \|A^{-1}\|_{\op}\,\|AXB\|_{\op}\,\|B^{-1}\|_{\op}
        =\lambda_{\max}(G_{m,-})^{1/2}
         \lambda_{\max}(G_{m,+})^{1/2}\,\|AXB\|_{\op}.
\]
The upper-eigenvalue estimate in
Lemma~\ref{lem:finite-same-point-spectral-size} gives
\[
        \|AXB\|_{\op}
        \ge
        c\,\bigl(q(t_-)q(t_+)\bigr)^{-3/2}\,
        \|X\|_{\op},
\]
which is the left-hand inequality in
\eqref{eq:two-sided-whitening-ledger}.  Finally,
Lemma~\ref{lem:theta-derivative-asymptotics} gives
\(q(t_\pm)\asymp\log T\) uniformly on \(I_T\), and hence
\eqref{eq:two-sided-whitening-log-loss}.
\end{proof}

\begin{corollary}[Polynomial ledger form]
\label{cor:two-sided-whitening-polynomial-ledger}
Assume the packet scale has an upper phase-slope ledger
\begin{equation}
\label{eq:upper-phase-slope-ledger}
        q(t)\le Q(T)^{C_q^+}
        \qquad (t\in I_T)
\end{equation}
for some absolute exponent \(C_q^+\).  Then for all retained
\((m,s)\in\mathcal D_T\) and all real \(2\times2\) matrices \(X\),
\begin{equation}
\label{eq:two-sided-whitening-Q-ledger}
        \|\mathsf W_{m,s}(X)\|_{\op}
        \ge
        c\,Q(T)^{-3C_q^+}\,\|X\|_{\op},
\end{equation}
with an absolute constant \(c>0\).  Thus any pre-whitening lower bound
\(\|X\|_{\op}\ge Q(T)^{-A}\) becomes the post-whitening lower bound
\begin{equation}
\label{eq:pre-to-post-whitening-lower-bound}
        \|\mathsf W_{m,s}(X)\|_{\op}
        \ge c\,Q(T)^{-(A+3C_q^+)}.
\end{equation}
\end{corollary}

\begin{proof}
Combine the lower bound in Lemma~\ref{lem:two-sided-whitening-ledger} with
\eqref{eq:upper-phase-slope-ledger} at \(t_\pm\):
\[
        \bigl(q(t_-)q(t_+)\bigr)^{-3/2}
        \ge Q(T)^{-3C_q^+}.
\]
This gives \eqref{eq:two-sided-whitening-Q-ledger}; applying it to a
matrix satisfying \(\|X\|_{\op}\ge Q(T)^{-A}\) gives
\eqref{eq:pre-to-post-whitening-lower-bound}.
\end{proof}

\begin{remark}[When the ledger is consumed]
\label{rem:when-two-sided-whitening-ledger-is-consumed}
Lemma~\ref{lem:two-sided-whitening-ledger} is needed only when a toy,
source-side, or finite-algebraic lower bound is first proved in
unwhitened coordinates and then transported through
\(\mathsf W_{m,s}\).  If a visibility theorem is stated directly for the
already whitened block \(\widehat\Om_\z\), then no additional whitening
loss is charged.  The same caveat applies to any fixed finite-dimensional
norm other than \(\|\cdot\|_{\op}\): because all norms on \(M_2(\mathbb R)\)
are equivalent, the constants in the ledger change, but the powers of
\(q(t_\pm)\), \(\log T\), and \(Q(T)\) do not.
\end{remark}

% =============================================================================
\section{Toy anomaly and transverse obstruction}
\label{sec:toy-anomaly-and-transverse-obstruction}
\statuspaper{LIVE}\quad
\statusmig{migrated}\quad
\statusreferee{in-progress}\quad
\statussympy[rh/sympy/sec-toy-anomaly-and-transverse-obstruction.py]{verified}\quad
\statussim[rh/simulation/sec-toy-anomaly-and-transverse-obstruction.py]{verified}\quad
\statuslean{not-started}
\par\medskip

The toy phase \(\Ph_\toy\) defined below is a real-analytic visibility
model carrying an explicit even-\(u^2\) deformation of the linear
baseline, with \(u=\beta-\tfrac12\) the off-line displacement parameter.
Applying the finite-block package of
Section~\ref{sec:finite-scale-local-blocks-and-whitening} to
\(\Ph_\toy\) produces a toy whitened block
\(\widehat\Om_\toy(s;m,u,q_0)\).  The off-diagonal trace
\(\mathcal A_\toy\) of this block is identically zero on the on-line
baseline and has nonzero leading-\(u^2\) coefficient
\(F_\toy(d,q_0)\), where \(d=q_0\,s\) is the dimensionless local
separation.  As \(q_0\to\infty\), this coefficient converges uniformly
on compact \(d\)-intervals to a \(q_0\)-independent closed-form limit
\(F_{\infty}(d)\).  The gauge-fixing projection
\(\Pi_\trans\) of Section~\ref{sec:transverse-projection} is a separate
step; this section proves the scalar visibility input that such a
projection must preserve.

\subsection{Off-line toy phase}
\label{subsec:off-line-toy-phase}

\begin{definition}[Off-line toy phase]
\label{def:off-line-toy-phase}
Fix a height \(m_0\), a local frequency \(q_0>0\), and an off-line
displacement \(u\in\mathbb R\).  The off-line toy phase is the
real-analytic phase
\begin{equation}
\label{eq:toy-phase}
\Ph_\toy(t;u,m_0,q_0)
\;:=\;q_0\,(t-m_0)\;+\;u^2\,\bigl(1-\cos(q_0\,(t-m_0))\bigr),
\qquad t\in\mathbb R.
\end{equation}
The displacement is identified with the off-line real part by
\(u=\beta-\tfrac12\).  By construction \(\Ph_\toy\) depends on \(u\)
only through \(u^2\) and is \(C^\infty\) on \(\mathbb R\) for every
\((u,q_0)\).
\end{definition}

\begin{remark}[Toy frequency convention]
\label{rem:toy-frequency-convention}
The parameter \(q_0\) is part of the toy data.  When it matters, we
write
\[
        G_{\toy,\pm}(s;m,u,q_0),\qquad
        N_\toy(s;m,u,q_0),\qquad
        \widehat\Om_\toy(s;m,u,q_0).
\]
In Section~\ref{subsec:toy-retained-subdomain}, where the toy is placed
on a retained theta packet, the toy frequency is specialized to the
local theta slope \(q_0=q(m)\).  This convention is essential: the toy
visibility theorem is uniform in an abstract high-frequency parameter
\(q_0\), while the polynomial-weight subdomain chooses that parameter
from the actual retained packet.
\end{remark}

\begin{lemma}[Toy phase derivatives]
\label{lem:toy-phase-derivatives}
With \(\tau:=t-m_0\), the derivatives of \(\Ph_\toy\) are
\begin{equation}
\label{eq:toy-phase-derivatives}
q_\toy(\tau)
=q_0+u^2\,q_0\sin(q_0\tau),
\quad
q_\toy'(\tau)=u^2\,q_0^{\,2}\cos(q_0\tau),
\quad
q_\toy''(\tau)=-u^2\,q_0^{\,3}\sin(q_0\tau).
\end{equation}
At \(\tau=0\),
\(q_\toy(0)=q_0\), \(q_\toy'(0)=u^2 q_0^{\,2}\),
\(q_\toy''(0)=0\).  The toy phase is not the retained theta chart of
Definition~\ref{def:local-phase-chart}; it is used only as a model
phase.  Its positivity analogue is
\[
        q_\toy(\tau)\ge q_0(1-u^2),
\]
so the toy same-point blocks are safely in the positive-frequency regime
whenever \(|u|<1\) and \(q_0(1-u^2)>0\).
\end{lemma}

\begin{proof}
Direct differentiation of \eqref{eq:toy-phase}.  The lower bound
\(q_\toy\ge q_0(1-u^2)\) follows from \(|\sin|\le 1\).
\end{proof}

\begin{lemma}[Symmetric-centre splitting at scale \(s\)]
\label{lem:q-pm-split-at-centres}
With \(t_\pm=m_0\pm s/2\) and \(d:=q_0\,s\), the toy phase derivatives
at the symmetric centres satisfy
\begin{equation}
\label{eq:q-pm-symmetric-split}
q_\pm:=q_\toy(\pm s/2)\;=\;q_0\;\pm\;u^2\,q_0\sin(d/2),
\qquad
q_\pm'\;=\;u^2\,q_0^{\,2}\cos(d/2),
\end{equation}
\[
q_\pm''\;=\;\mp\,u^2\,q_0^{\,3}\sin(d/2).
\]
In particular \(q_+ - q_- = 2 u^2 q_0\sin(d/2)\),
\(q_+' = q_-'\), and \(q_+''+q_-'' = 0\).  The phase difference
\(\Del_m^\toy(s)\) at the symmetric pair is
\begin{equation}
\label{eq:toy-Delta}
\Del_m^\toy(s)\;:=\;\Ph_\toy(t_-)-\Ph_\toy(t_+)\;=\;-q_0\,s\;=\;-d
\end{equation}
(no \(u\)-dependence: the cosine is even at \(\pm s/2\)).
\end{lemma}

\begin{proof}
\eqref{eq:q-pm-symmetric-split} substitutes \(\tau=\pm s/2\) into
\eqref{eq:toy-phase-derivatives} and uses oddness of \(\sin\) and
evenness of \(\cos\).  For \eqref{eq:toy-Delta}, evaluate
\eqref{eq:toy-phase} at \(\tau=\pm s/2\):
\[
\Ph_\toy(\pm s/2)
=\pm\tfrac{q_0 s}{2}
+u^2\bigl(1-\cos(\mp d/2)\bigr)
=\pm\tfrac{q_0 s}{2}
+u^2\bigl(1-\cos(d/2)\bigr),
\]
and subtract.
\end{proof}

\subsection{Toy whitened block}
\label{subsec:toy-whitened-block}

\begin{definition}[Toy finite blocks]
\label{def:toy-finite-blocks}
For \((m,s)\in\mathcal D_T\), with \(t_\pm=m\pm s/2\), and for a
frequency parameter \(q_0>0\), evaluate the toy phase
\(\Ph_\toy(t;u,m_0,q_0)\) of Definition~\ref{def:off-line-toy-phase}
with centre \(m_0=m\).  Set
\begin{equation}
\label{eq:toy-G-N}
G_{\toy,\pm}(s;m,u,q_0)\;:=\;G_{m,\pm}(s)\big|_{\Ph=\Ph_\toy},
\qquad
N_\toy(s;m,u,q_0)\;:=\;N_m(s)\big|_{\Ph=\Ph_\toy}.
\end{equation}
Here the right-hand sides are the same-point and mixed blocks
\eqref{eq:Gpm}--\eqref{eq:Nm} of
Section~\ref{sec:finite-scale-local-blocks-and-whitening} evaluated
with \((q,q',q'',\Del_m)\) replaced by
\((q_\toy,q_\toy',q_\toy'',\Del_m^\toy)\) of
Lemmas~\ref{lem:toy-phase-derivatives}--\ref{lem:q-pm-split-at-centres}.
\end{definition}

\begin{definition}[Toy whitened block]
\label{def:toy-whitened-block}
For \((m,s)\in\mathcal D_T\), \(q_0>0\), and
\(G_{\toy,\pm}(s;m,u,q_0)\succ 0\), define
\begin{equation}
\label{eq:omega-toy}
\widehat\Om_\toy(s;m,u,q_0)
\;:=\;G_{\toy,-}(s;m,u,q_0)^{-1/2}\,N_\toy(s;m,u,q_0)\,G_{\toy,+}(s;m,u,q_0)^{-1/2}.
\end{equation}
The inverse square root is the unique positive definite one.
\end{definition}

\begin{lemma}[Toy block positivity]
\label{lem:toy-block-positivity}
Fix a compact interval \(D=[d_-,d_+]\subset(0,\infty)\).  There exist
\(u_G=u_G(D)\in(0,\tfrac12]\), \(Q_G(D)\ge1\), and \(c_G(D)>0\) such
that whenever \(d=q_0\,s\in D\), \(|u|\le u_G\), and \(q_0\ge Q_G(D)\),
\[
        G_{\toy,\pm}(s;m,u,q_0)\succ 0,
        \qquad
        \lambda_{\min}\bigl(G_{\toy,\pm}(s;m,u,q_0)\bigr)\;\ge\;c_G(D)\,q_0.
\]
In particular \(\|G_{\toy,\pm}(s;m,u,q_0)^{-1/2}\|_{\op}\le C_G(D)q_0^{-1/2}\)
on the same region.
\end{lemma}

\begin{proof}
Write \(r=u^2\), \(z=\sin(d/2)\), and \(c=\cos(d/2)\).  From
\eqref{eq:q-pm-symmetric-split}, after factoring out the powers of
\(q_0\), the normalized same-point determinant has the form
\[
q_0^{-4}D_J(t_\pm)
=
4(1\pm rz)^4 \mp 2rz(1\pm rz)-3r^2c^2.
\]
This expression converges uniformly to \(4\) as \(r\to0\), uniformly in
\(d\in D\).  Decrease \(u_G\), if necessary, so that
\(q_0^{-4}D_J(t_\pm)\ge 1\) and \(q_\pm\ge q_0/2\) for
\(|u|\le u_G\).  By Lemma~\ref{lem:algebraic-same-point-gram-criterion},
\(G_{\toy,\pm}\succ0\).  Also, on \(d\in D\) and \(|u|\le u_G\),
\(\Tr G_{\toy,\pm}\le C(D)q_0^3\).  Therefore
\[
\lambda_{\min}(G_{\toy,\pm})
\ge \frac{\det G_{\toy,\pm}}{\Tr G_{\toy,\pm}}
\ge c_G(D)q_0.
\]
After increasing \(Q_G(D)\), this holds throughout the retained
high-frequency region.  The inverse-square-root bound follows by taking
reciprocals and square roots.
\end{proof}

\subsection{Toy anomaly functional and leading expansion}
\label{subsec:toy-anomaly-functional}

\begin{definition}[Toy anomaly functional]
\label{def:toy-anomaly-functional}
For a real \(2\times 2\) matrix \(X=(x_{ij})\), the toy anomaly
functional is the off-diagonal trace
\begin{equation}
\label{eq:toy-anomaly-functional}
\mathcal A_\toy(X)\;:=\;x_{12}+x_{21}.
\end{equation}
\end{definition}

\begin{lemma}[Vanishing on the on-line baseline]
\label{lem:A-toy-baseline-vanishing}
At \(u=0\) the toy phase reduces to the linear baseline
\(\Ph_\toy(t;0,m,q_0)=q_0(t-m)\), and \(\widehat\Om_\toy(s;m,0,q_0)\) is
the constant-phase whitened block of the linear baseline.  In
particular
\begin{equation}
\label{eq:A-toy-baseline}
        \mathcal A_\toy\bigl(\widehat\Om_\toy(s;m,0,q_0)\bigr)\;=\;0
        \qquad\bigl((m,s)\in\mathcal D_T^\times\bigr).
\end{equation}
\end{lemma}

\begin{proof}
At \(u=0\), \eqref{eq:toy-phase-derivatives} gives \(q_\pm=q_0\) and
\(q_\pm'=q_\pm''=0\); by \eqref{eq:Gpm},
\(G_{\toy,\pm}(s;m,0)=(1/\pi)\diag(2q_0,q_0^{\,3}/6)\) is diagonal,
and \(G_{\toy,-}^{-1/2}=G_{\toy,+}^{-1/2}\) is the same diagonal
matrix.  By \eqref{eq:Nm} with \(q_+=q_-=q_0\),
\[
N_\toy(s;m,0,q_0)_{12}+N_\toy(s;m,0,q_0)_{21}
=\frac{(q_+-q_-)\cos\Del_m^\toy(s)}{\pi s}=0.
\]
Whitening by the diagonal \(G^{-1/2}\) preserves this off-diagonal
cancellation: \(\widehat\Om_{12}+\widehat\Om_{21}
=(G^{-1/2})_{11}(G^{-1/2})_{22}(N_{12}+N_{21})=0\).
\end{proof}

\begin{lemma}[Leading \(u^2\) expansion of the off-diagonal trace]
\label{lem:toy-anomaly-leading}
Fix a compact interval \(D=[d_-,d_+]\subset(0,\infty)\).  There exist
\(Q_1=Q_1(D)\ge1\), \(u_1=u_1(D)>0\), and a function
\(F_\toy:D\times[Q_1,\infty)\to\mathbb R\) such that for every
\(0<|u|<u_1\), every \(q_0\ge Q_1\), and every
\((m,s)\in\mathcal D_T^\times\) with \(d=q_0\,s\in D\),
\begin{equation}
\label{eq:toy-anomaly-leading}
\mathcal A_\toy\bigl(\widehat\Om_\toy(s;m,u,q_0)\bigr)
\;=\;u^2\,F_\toy(d,q_0)\;+\;u^4\,R_\toy(d,q_0,u),
\end{equation}
with \(|R_\toy(d,q_0,u)|\le C_R(D)\) uniformly on the region
\(\{|u|\le u_1,\,d\in D,\,q_0\ge Q_1(D)\}\).  The high-frequency limit
\begin{equation}
\label{eq:F-toy-asymptotic}
        F_{\infty}(d)\;:=\;\lim_{q_0\to\infty}F_\toy(d,q_0)
\end{equation}
exists, is reached uniformly on compact \(d\)-intervals, and admits
the explicit closed form
\begin{equation}
\label{eq:F-toy-closed-form}
\begin{aligned}
F_{\infty}(d)
\;&=\;\frac{\sqrt 3}{8\,d^{\,3}\,\sin(d/2)}\;\Bigl(
2\,d^{\,2}\cos d+5\,d^{\,2}\cos 2d-7\,d^{\,2}\\
&\qquad\qquad\qquad\quad
+6\,d\sin d-15\,d\sin 2d-12\cos 2d+12\Bigr).
\end{aligned}
\end{equation}
\(F_{\infty}\) is interpreted by removable continuation at the
apparent \(\sin(d/2)\)-poles \(d=2\pi k\), \(k\ge1\).  Its zero set in
\((0,\infty)\) is discrete.  On every compact subinterval
\(D\subset(0,\infty)\) avoiding the zeros of this continued function
there exist \(Q_0(D)\ge 1\) and
\(c_\toy(D)>0\) with
\begin{equation}
\label{eq:F-toy-lower-bound}
        \bigl|F_\toy(d,q_0)\bigr|\;\ge\;c_\toy(D)
        \qquad (d\in D,\;q_0\ge Q_0(D)).
\end{equation}
\end{lemma}

\begin{proof}
Each entry of \(G_{\toy,\pm}(s;m,u,q_0)\) and \(N_\toy(s;m,u,q_0)\) is a
real-analytic function of \(r:=u^2\) by \eqref{eq:toy-phase-derivatives}
and \eqref{eq:Gpm}--\eqref{eq:Nm}.  To make the uniformity in \(q_0\)
explicit after substituting \(s=d/q_0\), use the natural powers
\(q_0,q_0^2,q_0^3\) attached to the value/derivative coordinates:
\[
G_{11}=q_0\,g_{11},\quad G_{12}=q_0^2\,g_{12},\quad
G_{22}=q_0^3\,g_{22},
\]
and similarly
\[
N_{11}=q_0\,n_{11},\quad N_{12}=q_0^2\,n_{12},\quad
N_{21}=q_0^2\,n_{21},\quad N_{22}=q_0^3\,n_{22}.
\]
The coefficients \(g_{ij}\) and \(n_{ij}\) are real-analytic functions
of \((r,d,\eta)\), \(\eta=q_0^{-1}\), on
\([0,u_1^2]\times D\times[0,\eta_1]\), once \(u_1\) is small and
\(Q_1=\eta_1^{-1}\) is large.  By Lemma~\ref{lem:toy-block-positivity},
the normalized determinants of the \(G_{\toy,\pm}\) stay bounded away
from zero on this compact parameter set.  The explicit \(2\times2\)
positive-definite inverse-square-root formula therefore gives
\[
(G_{\toy,\pm}^{-1/2})_{11}=q_0^{-1/2}h_{11}^{\pm},\quad
(G_{\toy,\pm}^{-1/2})_{12}=q_0^{-3/2}h_{12}^{\pm},\quad
(G_{\toy,\pm}^{-1/2})_{22}=q_0^{-3/2}h_{22}^{\pm},
\]
where the \(h_{ij}^{\pm}\) are again real-analytic and uniformly bounded
on the same compact set.  Multiplying the three factors in
\(G_{\toy,-}^{-1/2}N_\toy G_{\toy,+}^{-1/2}\) shows that every entry of
\(\widehat\Om_\toy\), and in particular
\(\mathcal A_\toy(\widehat\Om_\toy)\), is real-analytic in \(r\) with
uniformly bounded Taylor coefficients.  Since the \(u^0\) coefficient
vanishes by Lemma~\ref{lem:A-toy-baseline-vanishing}, the leading
nonzero term is at order \(u^2\); call its coefficient
\(F_\toy(d,q_0)\).

Direct computation using the closed-form \(2\times 2\) SPD
inverse-square-root, applied to
\(G_{\toy,\pm}=G_{\toy,\pm}^{(0)}+u^2\,G_{\toy,\pm}^{(2)}+O(u^4)\) of
\eqref{eq:Gpm} with the toy substitutions of
\eqref{eq:q-pm-symmetric-split} and to \(N_\toy\) of
Definition~\ref{def:toy-finite-blocks}, yields an explicit expression
for \(F_\toy(d,q_0)\) in
\((\sin d,\cos d,\sin(d/2),\cos(d/2),q_0)\).  After choosing
\(Q_1(D)\) large enough, this expression is regular for
\(d\in D\), \(q_0\ge Q_1(D)\), has a finite \(q_0\to\infty\) limit
uniformly on \(D\), and the limiting expression is
\eqref{eq:F-toy-closed-form}.

The factor \(\sin(d/2)\) of the denominator of
\eqref{eq:F-toy-closed-form} vanishes at \(d=2\pi k\),
\(k\in\mathbb Z_{\ge 1}\); the trigonometric numerator vanishes at
the same points.  Expanding the numerator at each \(d=2\pi k\) shows a
factor of \(\sin(d/2)\), so the apparent poles are removable and
\(F_{\infty}\) extends real-analytically to \((0,\infty)\).  On any compact subinterval avoiding the zeros of
\(F_{\infty}\), the difference \(F_\toy(d,q_0)-F_{\infty}(d)\) is
\(O(1/q_0)\) uniformly; for \(q_0\) sufficiently large
\(|F_\toy(d,q_0)|\ge \tfrac12|F_{\infty}(d)|\), giving
\eqref{eq:F-toy-lower-bound}.  The remainder \(R_\toy\) is the \(u^4\)-and-higher part of this
real-analytic expansion.  The compactness of the normalized parameter
set and the uniform positive-definiteness just described give a
Cauchy-type bound for these coefficients, uniformly for \(d\in D\),
\(|u|\le u_1\), and \(q_0\ge Q_1(D)\), after decreasing \(u_1\) and
increasing \(Q_1(D)\) if necessary.
\end{proof}

\subsection{Toy retained subdomain and polynomial-weight density}
\label{subsec:toy-retained-subdomain}

\begin{definition}[Toy retained subdomain]
\label{def:toy-retained-subdomain}
Fix a compact interval \(D=[d_-,d_+]\subset(0,\infty)\) avoiding the
isolated zeros of \(F_{\infty}\) of
Lemma~\ref{lem:toy-anomaly-leading}.  The signed toy retained subdomain
at height \(T\) is
\begin{equation}
\label{eq:toy-retained-subdomain}
        \mathcal D_T^\toy(D)
        :=\bigl\{(m,s)\in\mathcal D_T^\times:
              q(m)\,|s|\in D\bigr\}.
\end{equation}
Thus the positive and negative separation branches are both retained.
The comparison estimates below are stated for the absolute scalar
functional \(|\mathcal A_\toy|\), so retaining both signs does not change
the toy lower bound; see Lemma~\ref{lem:toy-signed-separation-invariance}.
\end{definition}

\begin{lemma}[Polynomial-weight density of the toy retained subdomain]
\label{lem:toy-retained-density}
Let
\[
        q_T^-:=\inf_{m\in I_T}q(m),
        \qquad
        q_T^+:=\sup_{m\in I_T}q(m).
\]
Assume \(q_T^->0\) and
\begin{equation}
\label{eq:toy-density-height-hypothesis}
        \frac{d_+}{q_T^-}\le \frac{|I_T|}{4}.
\end{equation}
Then
\begin{equation}
\label{eq:toy-retained-density-exact}
        \frac{|\mathcal D_T^\toy(D)|}{|\mathcal D_T|}
        \ge
        \frac{d_+-d_-}{q_T^+\,|I_T|}.
\end{equation}
Consequently, if the retained windows satisfy
\begin{equation}
\label{eq:toy-window-comparability}
        |I_T|\le C_I Q(T)^{-1},
        \qquad
        q_T^+\le C_q q(T)
\end{equation}
with absolute constants \(C_I,C_q\), then
\begin{equation}
\label{eq:toy-retained-density}
        \frac{|\mathcal D_T^\toy(D)|}{|\mathcal D_T|}
        \ge
        \frac{d_+-d_-}{C_I C_q}\,\frac{Q(T)}{q(T)}.
\end{equation}
The height hypothesis \eqref{eq:toy-density-height-hypothesis} is
implied for all sufficiently large \(T\) in any scale regime with
\(|I_T|\ge c_I Q(T)^{-1}\), \(q_T^-\ge c_q q(T)\), and
\(Q(T)=o(q(T))\), with constants depending only on \(D,c_I,c_q\).
\end{lemma}

\begin{proof}
The finite packet domain is
\[
    \mathcal D_T
    =\bigl\{(m,s): |m-T|+|s|/2\le |I_T|/2\bigr\},
\]
a rotated square of area \(|\mathcal D_T|=|I_T|^2\).  Restrict to the
central slab
\[
        S_T:=\{m: |m-T|\le |I_T|/4\}.
\]
For \(m\in S_T\), the \(\mathcal D_T\)-constraint permits the full range
\[
        |s|\le |I_T|-2|m-T|.
\]
In particular it contains the smaller symmetric range
\(|s|\le |I_T|/4\).  By
\eqref{eq:toy-density-height-hypothesis},
\[
        \frac{d_+}{q(m)}\le \frac{d_+}{q_T^-}\le \frac{|I_T|}{4},
\]
so both intervals
\[
        \left[\frac{d_-}{q(m)},\frac{d_+}{q(m)}\right],
        \qquad
        -\left[\frac{d_+}{q(m)},\frac{d_-}{q(m)}\right]
\]
are contained in the allowed \(s\)-range.  Their combined length is
\(2(d_+-d_-)/q(m)\), which is at least \(2(d_+-d_-)/q_T^+\).  Therefore
\[
        |\mathcal D_T^\toy(D)|
        \ge \int_{S_T}\frac{2(d_+-d_-)}{q_T^+}\,dm
        =\frac{(d_+-d_-)|I_T|}{q_T^+}.
\]
Dividing by \(|\mathcal D_T|=|I_T|^2\) proves
\eqref{eq:toy-retained-density-exact}.  The estimate
\eqref{eq:toy-retained-density} follows immediately from
\eqref{eq:toy-window-comparability}.  Finally, if
\(|I_T|\ge c_IQ(T)^{-1}\) and \(q_T^-\ge c_q q(T)\), then
\eqref{eq:toy-density-height-hypothesis} follows from
\[
        \frac{d_+}{c_q q(T)}\le \frac{c_I}{4Q(T)},
        \quad\text{i.e.}\quad
        \frac{Q(T)}{q(T)}\le \frac{c_Ic_q}{4d_+},
\]
which holds eventually whenever \(Q(T)=o(q(T))\).
\end{proof}

\begin{lemma}[Signed-separation invariance of the scalar toy channel]
\label{lem:toy-signed-separation-invariance}
For the toy finite blocks of Definition~\ref{def:toy-finite-blocks}, with fixed
\(q_0>0\),
\[
        \widehat\Om_\toy(-s;m,u,q_0)=\widehat\Om_\toy(s;m,u,q_0)^\top
\]
whenever both sides are defined.  Consequently
\begin{equation}
\label{eq:toy-A-signed-invariance}
        \mathcal A_\toy(\widehat\Om_\toy(-s;m,u,q_0))
        =\mathcal A_\toy(\widehat\Om_\toy(s;m,u,q_0)).
\end{equation}
\end{lemma}

\begin{proof}
Changing \(s\) to \(-s\) swaps the two centers \(t_-\) and \(t_+\).
The same-point blocks therefore satisfy
\[
        G_{\toy,-}(-s;m,u,q_0)=G_{\toy,+}(s;m,u,q_0),\qquad
        G_{\toy,+}(-s;m,u,q_0)=G_{\toy,-}(s;m,u,q_0),
\]
and the mixed block satisfies
\(N_\toy(-s;m,u,q_0)=N_\toy(s;m,u,q_0)^\top\), by the symmetry of
\(K_\Phi\) and the row/column convention of
Definition~\ref{def:finite-same-point-and-mixed-blocks}.  Positive
definite inverse square roots commute with transposition for symmetric
matrices, so the displayed transpose identity for \(\widehat\Om_\toy\)
follows.  Since
\(\mathcal A_\toy(X)=X_{12}+X_{21}\) is invariant under transpose,
\eqref{eq:toy-A-signed-invariance} follows.
\end{proof}

\subsection{Toy anomaly visibility}
\label{subsec:toy-anomaly-visibility}

\begin{theorem}[Toy anomaly visibility]
\label{thm:toy-anomaly-visibility}
Let \(D\subset(0,\infty)\) be a compact interval avoiding the
isolated zeros of \(F_{\infty}\) of
Lemma~\ref{lem:toy-anomaly-leading}.  There are constants
\(Q_\toy(D)\ge1\) and \(u_\toy(D)>0\) such that, for every off-line
displacement \(u=\beta-\tfrac12\in\mathbb R\) with \(0<|u|\le u_\toy(D)\),
every \(q_0\ge Q_\toy(D)\), and every \((m,s)\in\mathcal D_T^\times\)
with \(d=q_0\,s\in D\), the toy
whitened block \(\widehat\Om_\toy(s;m,u,q_0)\) of
Definition~\ref{def:toy-whitened-block} satisfies
\begin{equation}
\label{eq:toy-anomaly-visibility-A}
        \bigl|\mathcal A_\toy\bigl(\widehat\Om_\toy(s;m,u,q_0)\bigr)\bigr|
        \;\ge\;
        \tfrac12\,c_\toy(D)\,u^2.
\end{equation}
The constant \(c_\toy(D)>0\) is the lower bound of
Lemma~\ref{lem:toy-anomaly-leading} and depends on \(D\) only.
On the polynomial-weight subset of midpoints and separations on which
\(d\in D\), the visibility exponent is \(A_\toy=0\): the lower bound
is \((c_\toy(D)/2)\,u^2\,Q^0\), independent of the height.
\end{theorem}

\begin{proof}
Choose \(Q_\toy(D)\ge\max\{Q_1(D),Q_G(D)\}\).  Let \(u_G(D)\) be the
smallness threshold from Lemma~\ref{lem:toy-block-positivity}.  Choose
\[
        u_\toy(D)\le \min\{u_1(D),u_G(D)\}
\]
small enough that both lemmas apply.  By
\eqref{eq:toy-anomaly-leading} and \eqref{eq:F-toy-lower-bound},
\[
\bigl|\mathcal A_\toy\bigl(\widehat\Om_\toy(s;m,u,q_0)\bigr)\bigr|
\;\ge\;
u^2\bigl(c_\toy(D)-u^2\,C_R(D)\bigr).
\]
Decreasing \(u_\toy(D)\) so that \(u_\toy(D)^{\,2}\,C_R(D)\le c_\toy(D)/2\) gives
\eqref{eq:toy-anomaly-visibility-A}.
\end{proof}

\begin{corollary}[Visibility on the polynomial-weight subdomain]
\label{cor:toy-visibility-polynomial-weight}
Fix \(D\) and the constants \(Q_\toy(D)\), \(u_\toy(D)\), \(c_\toy(D)\)
of Theorem~\ref{thm:toy-anomaly-visibility}.  Assume the height is large
enough that \(q_T^-\ge Q_\toy(D)\), where
\(q_T^-:=\inf_{m\in I_T}q(m)\).  On the toy retained subdomain we set
\(q_0=q(m)\).  Then for every \(0<|u|\le
u_\toy(D)\) and every \((m,s)\in\mathcal D_T^\toy(D)\),
\begin{equation}
\label{eq:toy-anomaly-visibility-on-subdomain}
        \bigl|\mathcal A_\toy(\widehat\Om_\toy(s;m,u,q(m)))\bigr|
        \ge \tfrac12 c_\toy(D)u^2.
\end{equation}
If, in addition, the hypotheses of Lemma~\ref{lem:toy-retained-density}
hold, then this lower bound holds on a subset of \(\mathcal D_T\) of
relative density at least the right-hand side of
\eqref{eq:toy-retained-density-exact}, and hence at least
\eqref{eq:toy-retained-density} under
\eqref{eq:toy-window-comparability}.
\end{corollary}

\begin{proof}
Let \((m,s)\in\mathcal D_T^\toy(D)\).  Then
\(d=q(m)|s|\in D\) and \(q_0=q(m)\ge q_T^-\ge Q_\toy(D)\).  If
\(s>0\), Theorem~\ref{thm:toy-anomaly-visibility} gives
\eqref{eq:toy-anomaly-visibility-on-subdomain}.  If \(s<0\), apply the
theorem to \(|s|\) and then use
Lemma~\ref{lem:toy-signed-separation-invariance}.  The density statement
is Lemma~\ref{lem:toy-retained-density}.
\end{proof}

\begin{remark}[Transverse projection deferred]
\label{rem:toy-Pi-trans-deferred}
The functional \(\mathcal A_\toy\) annihilates the on-line baseline
(Lemma~\ref{lem:A-toy-baseline-vanishing}).  The later projection
\(\Pi_\trans\) must be chosen so that this scalar functional descends to
or is represented on the retained transverse quotient.  Once
Section~\ref{sec:transverse-projection} proves that compatibility, the
visibility bound \eqref{eq:toy-anomaly-visibility-A} transfers to the
\(\Pi_\trans\)-projected comparison with the same exponent
\(A_\toy=0\).  This compatibility is not proved in the present section.
\end{remark}


\begin{remark}[Compatibility with the archived v1 toy matrix]
\label{rem:toy-phase-v1-compatibility}
The toy phase \eqref{eq:toy-phase} is a replacement toy for the clean
scalar-functional rebuild.  It is not the archived v1 matrix \(M(d)\),
and this section does not import the v1 calibration map
\(\Psi_{x,d}\) or the Frobenius pairings with \(A_{\val}\).  Consequently
this change is isolated for the present rebuild through
Sections~\ref{sec:transverse-projection}--\ref{sec:projective-rigidity},
where only the scalar functional \(\mathcal A_\toy\), the exponent
\(A_\toy=0\), and the lower bound \eqref{eq:toy-anomaly-visibility-A}
are consumed.  Any later attempt to import a v1 theorem that explicitly
uses \(M(d)\), \(\Phi_K(M(d))\), \(A_{\val}\), or \(\Psi_{x,d}\) must be
rederived for the present toy phase or kept in the archive.
\end{remark}

\begin{remark}[No uniform extension; polynomial-weight scope]
\label{rem:toy-anomaly-no-uniform-extension}
The visibility lower bound \eqref{eq:toy-anomaly-visibility-A} cannot be
extended to all of \(\mathcal D_T\).  At \(s=0\), the same coalescence
argument as Corollary~\ref{cor:omega-coalescence}, applied to the toy
finite blocks, gives \(\widehat\Om_\toy(0;m,u,q_0)=I_2\) for every \(u\).
Hence \(\mathcal A_\toy(\widehat\Om_\toy(0;m,u,q_0))=0\); no
\(u^2\)-lower bound can hold at the coalescence locus \(d=0\).  The
regimes \(d\to\infty\) and \(d\) approaching an isolated zero of
\(F_\infty\) are excluded by the compactness and avoidance hypotheses on
\(D\) in Definition~\ref{def:toy-retained-subdomain}.  The signed
polynomial-weight subdomain \(\mathcal D_T^\toy(D)\) carries the toy
visibility lower bound by
Corollary~\ref{cor:toy-visibility-polynomial-weight}; its relative
density is polynomial in \(Q\) by Lemma~\ref{lem:toy-retained-density}
and is the only density loss contributed by this replacement of the
impossible all-of-\(\mathcal D_T\) assertion.
\end{remark}

% =============================================================================
\section{Transverse projection}
\label{sec:transverse-projection}
\statuspaper{LIVE}\quad
\statusmig{migrated}\quad
\statusreferee{in-progress}\quad
\statussympy[rh/sympy/sec-transverse-projection.py]{verified}\quad
\statussim[rh/simulation/sec-transverse-projection.py]{verified}\quad
\statuslean{not-started}
\par\medskip

The scalar toy anomaly functional \(\mathcal A_\toy\) of
Definition~\ref{def:toy-anomaly-functional} fixes the two-point value
subspace as its kernel.  The transverse projection in this section is
the Hilbert--Schmidt orthogonal projection of the Gram-normalized
\(2\times2\) matrix space onto the one-dimensional complement of that
kernel.  This gives a canonical two-point \(\Pi_\trans\) compatible
with the scalar visibility lower bound of
Theorem~\ref{thm:toy-anomaly-visibility}.  The projection has
Hilbert--Schmidt operator norm one, contributes no polynomial loss,
and allows the actual-zeta two-point suppression statement of
Section~\ref{sec:actual-zeta-transverse-suppression} to be formulated
in the same scalar channel as the toy lower bound.  All occurrences of \(\Pi_\trans\) in this section are therefore
understood as two-point objects on \(M_2(\mathbb R)\).  This section does
not define the four-point projection \(\Pi_\trans^{(4)}\).

\subsection{Value subspace and transverse projection}
\label{subsec:transverse-projection-construction}

We work on \(M_{2}(\mathbb R)\) with the Hilbert--Schmidt inner product
\(
        \langle X,Y\rangle_{\mathrm{HS}}
        :=\operatorname{tr}(X^\top Y).
\)

\begin{definition}[Value subspace]
\label{def:value-subspace}
The two-point scalar value subspace is
\begin{equation}
\label{eq:V-val}
        \mathcal V_\val
        \;:=\;\bigl\{X\in M_{2}(\mathbb R):x_{12}+x_{21}=0\bigr\}
        \;=\;\ker\mathcal A_\toy.
\end{equation}
\end{definition}

\begin{lemma}[Explicit basis for \(\mathcal V_\val\)]
\label{lem:value-subspace-explicit-basis}
\(\mathcal V_\val\) is a three-dimensional subspace of
\(M_2(\mathbb R)\) with orthonormal basis
\begin{equation}
\label{eq:V-val-basis}
        e_{11}=\begin{pmatrix}1&0\\0&0\end{pmatrix},
        \qquad
        e_{22}=\begin{pmatrix}0&0\\0&1\end{pmatrix},
        \qquad
        e_{\mathrm{anti}}=\frac1{\sqrt2}
        \begin{pmatrix}0&1\\-1&0\end{pmatrix}.
\end{equation}
Its one-dimensional orthogonal complement is
\begin{equation}
\label{eq:V-val-perp-basis}
        \mathcal V_\val^\perp=\mathbb R\,e_\sym,
        \qquad
        e_\sym:=\frac1{\sqrt2}
        \begin{pmatrix}0&1\\1&0\end{pmatrix}.
\end{equation}
\end{lemma}

\begin{proof}
The four matrices \(e_{11},e_{22},e_{\mathrm{anti}},e_\sym\) form an
orthonormal basis of \(M_2(\mathbb R)\) by direct calculation.  The
first three have \(x_{12}+x_{21}=0\), so they lie in
\(\mathcal V_\val\).  The matrix \(e_\sym\) has
\(x_{12}+x_{21}=\sqrt2\ne 0\) and is orthogonal to the first three, so
it spans \(\mathcal V_\val^\perp\).
\end{proof}

\begin{remark}[Four-point projection not supplied here]
\label{rem:transverse-projection-four-point-not-supplied}
This section defines the two-center projection on \(M_2(\mathbb R)\).
The four-center projection \(\Pi_\trans^{(4)}\) appearing in
Hypothesis~\ref{hyp:zeta-suppression-four-point} and
Theorem~\ref{thm:four-point-rigidity} is a separate object.  No
four-point quotient, four-point value subspace, or four-point scalar
functional is proved in this section.
\end{remark}

\begin{definition}[Two-point transverse projection]
\label{def:two-point-transverse-projection}
The two-point transverse projection
\(\Pi_\trans:M_2(\mathbb R)\to M_2(\mathbb R)\) is the
Hilbert--Schmidt orthogonal projection onto
\(\mathcal V_\val^\perp\).  Equivalently,
\begin{equation}
\label{eq:Pi-trans-explicit}
        \Pi_\trans X
        \;=\;\frac{x_{12}+x_{21}}{2}
        \begin{pmatrix}0&1\\1&0\end{pmatrix}.
\end{equation}
\end{definition}

\begin{definition}[Two-point scalar transverse channel]
\label{def:two-point-scalar-transverse-channel}
For a real two-center whitened block \(X\in M_2(\mathbb R)\), define
\begin{equation}
\label{eq:two-point-scalar-channel}
        \mathcal A_2(X):=\mathcal A_\toy(\Pi_\trans X).
\end{equation}
Lemma~\ref{lem:transverse-projection-A-toy-compatibility} gives
\(\mathcal A_2(X)=\mathcal A_\toy(X)=x_{12}+x_{21}\).  Thus
\(\mathcal A_2\) is a scalar functional on two-point matrix
representatives, or equivalently on the quotient
\(M_2(\mathbb R)/\mathcal V_\val\) after choosing the
Hilbert--Schmidt orthogonal representative \(\Pi_\trans X\).
\end{definition}

\subsection{Properties of \(\Pi_\trans\)}
\label{subsec:transverse-projection-properties}

\begin{lemma}[Projection properties]
\label{lem:transverse-projection-properties}
The operator \(\Pi_\trans\) is idempotent, self-adjoint with respect
to the Hilbert--Schmidt inner product, has kernel exactly
\(\mathcal V_\val\), and, as an operator on
\((M_2(\mathbb R),\|\cdot\|_{\mathrm{HS}})\),
\begin{equation}
\label{eq:Pi-trans-norm}
        \|\Pi_\trans\|_{\op,\mathrm{HS}\to\mathrm{HS}}=1.
\end{equation}
\end{lemma}

\begin{proof}
Formula~\eqref{eq:Pi-trans-explicit} is the same as
\(\Pi_\trans X=\langle X,e_\sym\rangle_{\mathrm{HS}}\,e_\sym\).  Hence
\(\Pi_\trans\) is the Hilbert--Schmidt orthogonal projection onto the
nonzero subspace \(\mathbb R e_\sym\).  Idempotence,
self-adjointness, kernel \(\mathcal V_\val\), and operator norm one
follow immediately.
\end{proof}

\begin{lemma}[Quotient representative and scalar norm]
\label{lem:transverse-projection-quotient-representative}
For every \(X\in M_2(\mathbb R)\),
\begin{equation}
\label{eq:Pi-trans-representative}
        \Pi_\trans X=\frac{\mathcal A_\toy(X)}{\sqrt2}\,e_\sym,
        \qquad X-\Pi_\trans X\in\mathcal V_\val,
\end{equation}
and
\begin{equation}
\label{eq:Pi-trans-HS-norm-scalar}
        \|\Pi_\trans X\|_{\mathrm{HS}}^{\,2}
        =\frac{|\mathcal A_\toy(X)|^{\,2}}{2}.
\end{equation}
\end{lemma}

\begin{proof}
The representative identity follows from
\eqref{eq:Pi-trans-explicit} and
\(e_\sym=2^{-1/2}\bigl(\begin{smallmatrix}0&1\\1&0\end{smallmatrix}\bigr)\).
Applying \(\mathcal A_\toy\) to \(X-\Pi_\trans X\) gives zero by
Lemma~\ref{lem:transverse-projection-A-toy-compatibility}, so the
residual lies in \(\mathcal V_\val\).  The norm identity follows from
\(\|e_\sym\|_{\mathrm{HS}}=1\).
\end{proof}

\begin{lemma}[Scalar-channel compatibility]
\label{lem:transverse-projection-A-toy-compatibility}
For every \(X\in M_2(\mathbb R)\),
\begin{equation}
\label{eq:A-toy-pi-compat}
        \mathcal A_\toy(\Pi_\trans X)\;=\;\mathcal A_\toy(X).
\end{equation}
Consequently the toy visibility lower bound
\eqref{eq:toy-anomaly-visibility-A} is unchanged if the toy whitened
block is first replaced by its projected representative
\(\Pi_\trans\widehat\Om_\toy\).  No matrix-norm lower bound is
asserted; only the scalar channel
\(\mathcal A_2=\mathcal A_\toy\circ\Pi_\trans\) is transported.
\end{lemma}

\begin{proof}
By \eqref{eq:Pi-trans-explicit},
\((\Pi_\trans X)_{12}=(\Pi_\trans X)_{21}=(x_{12}+x_{21})/2\).
Therefore
\[
        \mathcal A_\toy(\Pi_\trans X)
        \;=\;\frac{x_{12}+x_{21}}{2}+\frac{x_{12}+x_{21}}{2}
        \;=\;x_{12}+x_{21}
        \;=\;\mathcal A_\toy(X).
\]
The final assertion follows by applying this equality to
\(X=\widehat\Om_\toy(s;m,u,q_0)\) inside the absolute value in
\eqref{eq:toy-anomaly-visibility-A}.
\end{proof}

\begin{lemma}[Two-point scalar quotient well-definedness]
\label{lem:A2-quotient-well-defined}
The scalar channel \(\mathcal A_2\) descends to the quotient
\(M_2(\mathbb R)/\mathcal V_\val\).  Equivalently, if
\(X-Y\in\mathcal V_\val\), then
\begin{equation}
\label{eq:A2-quotient-well-defined}
        \mathcal A_2(X)=\mathcal A_2(Y).
\end{equation}
Moreover, for every \(X\in M_2(\mathbb R)\),
\begin{equation}
\label{eq:A2-representative-identities}
        \mathcal A_2(X)
        =\mathcal A_\toy(\Pi_\trans X)
        =\mathcal A_\toy(X)
        =\sqrt2\,\langle X,e_\sym\rangle_{\mathrm{HS}}.
\end{equation}
\end{lemma}

\begin{proof}
If \(X-Y\in\mathcal V_\val=\ker\mathcal A_\toy\), then
\(\mathcal A_\toy(X)-\mathcal A_\toy(Y)=0\).  By
Definition~\ref{def:two-point-scalar-transverse-channel} and
Lemma~\ref{lem:transverse-projection-A-toy-compatibility},
\(\mathcal A_2=\mathcal A_\toy\) on matrix representatives; hence
\eqref{eq:A2-quotient-well-defined}.  The identities in
\eqref{eq:A2-representative-identities} follow from
Lemma~\ref{lem:transverse-projection-A-toy-compatibility} and
\(\langle X,e_\sym\rangle_{\mathrm{HS}}=(x_{12}+x_{21})/\sqrt2\).
\end{proof}

\subsection{Scope of the chosen projection}
\label{subsec:transverse-projection-scope}

\begin{remark}[No richer quotient is used in the scalar rebuild]
\label{rem:transverse-projection-no-richer-quotient}
The downstream two-point comparison consumes only the scalar
visibility \(|\mathcal A_2(\widehat\Om_\toy)|\) and the matching
actual-zeta scalar upper bound
\(|\mathcal A_2(\widehat\Om_\z)|\).  At this scalar level, the kernel
of \(\mathcal A_\toy\) is the complete value subspace.  The
orthogonal projection of
Definition~\ref{def:two-point-transverse-projection} gives the canonical
Hilbert--Schmidt representative of the quotient map
\(M_2(\mathbb R)\to M_2(\mathbb R)/\mathcal V_\val\), with no
polynomial loss.  Richer matrix-level quotient constructions from the
archived local-projective-rigidity machinery are not imported here;
cf.\ Remark~\ref{rem:toy-phase-v1-compatibility}.
\end{remark}

\begin{remark}[Residual gauge]
\label{rem:transverse-projection-residual-gauge}
The retained chart of Definition~\ref{def:local-phase-chart} pins
\(\Ph_T=\theta\).  Additive constants \(\Ph\mapsto\Ph+c\) leave
\(q,q',q''\), hence \(G_{m,\pm}\), \(N_m\), and \(\widehat\Om_\z\),
unchanged.  Affine-jet shifts \(\Ph\mapsto\Ph+at\) change \(q\) to
\(q+a\) and do not preserve the chart class.  Thus there is no
residual gauge action on the two-point matrix representatives beyond
the trivial additive-constant invariance.
\end{remark}

\begin{lemma}[Sufficient two-point projection input]
\label{lem:transverse-projection-sufficient}
The transverse projection \(\Pi_\trans\) and scalar channel
\(\mathcal A_2\) supply the two-point projection input required by
Section~\ref{sec:projective-rigidity}: the toy visibility lower bound
\eqref{eq:toy-anomaly-visibility-A} transports through
\(\Pi_\trans\) by
Lemma~\ref{lem:transverse-projection-A-toy-compatibility}, and the
Hilbert--Schmidt operator-norm bound
\eqref{eq:Pi-trans-norm} contributes no polynomial-in-\(Q\) loss.
The actual-zeta two-point upper bound must be stated in the same
scalar channel, namely as a bound for
\(|\mathcal A_2(\widehat\Om_\z(s;m))|\).
\end{lemma}

\begin{proof}
Combine Lemmas~\ref{lem:transverse-projection-properties},
\ref{lem:transverse-projection-quotient-representative},
\ref{lem:transverse-projection-A-toy-compatibility},
and~\ref{lem:A2-quotient-well-defined} with
Theorem~\ref{thm:toy-anomaly-visibility} and
Corollary~\ref{cor:toy-visibility-polynomial-weight}.
\end{proof}

% =============================================================================
\section{Actual-zeta transverse suppression}
\label{sec:actual-zeta-transverse-suppression}
\statuspaper{LIVE}\quad
\statusmig{not-started}\quad
\statusreferee{not-started}\quad
\statussympy{not-started}\quad
\statussim{not-started}\quad
\statuslean{not-started}
\par\medskip

The actual zeta phase \(\Ph\) defines two whitened blocks --- the
two-center block \(\widehat\Om_\z(s;m)\) and a four-center analogue
\(\widehat\Om_\z^{(4)}\) for the symmetric quartet --- on which the
actual-zeta transverse anomaly is suppressed at a strictly larger
polynomial exponent than the corresponding toy lower bound of
Theorem~\ref{thm:toy-anomaly-visibility}.  In the two-point case, the
transverse scalar channel is the one fixed in
Section~\ref{sec:transverse-projection}:
\[
        \mathcal A_2(X)
        \;:=\;\mathcal A_\toy(\Pi_\trans X)
        \;=\;\mathcal A_\toy(X).
\]
The equality is
Lemma~\ref{lem:transverse-projection-A-toy-compatibility}.  Thus
\(\Pi_\trans\) acts on the block before the scalar functional is
applied; the expression \(\Pi_\trans\mathcal A_2(X)\) is not used.

The two-point and four-point comparisons of
Section~\ref{sec:projective-rigidity} consume different forms of this
suppression, stated separately below.

\subsection{Two-point suppression}
\label{subsec:two-point-suppression}

\begin{hypothesis}[Two-point actual-zeta transverse suppression]
\label{hyp:zeta-suppression-two-point}
For the two-center packet associated with \(\rho\) and a symmetry
partner, after the gauge-fixed normalization of
Definition~\ref{def:local-phase-chart},
\begin{equation}
\label{eq:zeta-suppression-two-point-scalar}
        \bigl|\mathcal A_2\bigl(\widehat\Om_\z(s;m)\bigr)\bigr|
        \;\le\; Q^{-B_{\z,2}}
\end{equation}
for an absolute exponent \(B_{\z,2}>A_\toy\) on the retained
subfamily matched to the toy visibility theorem.  Equivalently, by
Lemma~\ref{lem:transverse-projection-A-toy-compatibility},
\[
        \bigl|\mathcal A_\toy\bigl(\Pi_\trans\widehat\Om_\z(s;m)\bigr)\bigr|
        \;=\;
        \bigl|\mathcal A_\toy\bigl(\widehat\Om_\z(s;m)\bigr)\bigr|
        \;\le\; Q^{-B_{\z,2}}.
\]
\end{hypothesis}

\begin{wip}\label{rem:wip-zeta-suppression-two-point}
The two-point case of the structural gap.  Consumed by
Theorem~\ref{thm:two-point-rigidity}.  Admissible proof routes:
\textup{(i)} a standalone route from the local jet-Gram geometry alone;
\textup{(ii)} an energy-supply route consuming the source bound
of Section~\ref{sec:source-energy-supply} via
Lemma~\ref{lem:source-energy-to-suppression}.  v1 prose to mine: the
odd holomorphic transverse channel and corrected finite-\(s\)
holomorphic whitening sections.
\end{wip}

\subsection{Four-point suppression}
\label{subsec:four-point-suppression}

\begin{hypothesis}[Four-point actual-zeta transverse suppression]
\label{hyp:zeta-suppression-four-point}
For the four-center packet associated with the symmetry quartet
\(\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\), let
\(\Pi_\trans^{(4)}\) be a four-point transverse projection and let
\(\mathcal A_{4,\trans}\) be the corresponding four-point transverse
functional, i.e.\ a scalar or finite-dimensional normed output after
the four-point projection has been applied.  Then
\begin{equation}
\label{eq:zeta-suppression-four-point-transverse}
        \bigl\|\mathcal A_{4,\trans}\bigl(\widehat\Om_\z^{(4)}\bigr)\bigr\|
        \;\le\; Q^{-B_{\z,4}}
\end{equation}
for an absolute exponent \(B_{\z,4}>A_\toy^{(4)}\) on the retained
four-point subfamily.
\end{hypothesis}

\begin{wip}\label{rem:wip-zeta-suppression-four-point}
The four-point case of the structural gap.  Consumed by
Theorem~\ref{thm:four-point-rigidity}.  Same admissible proof routes
as Hypothesis~\ref{hyp:zeta-suppression-two-point}.  The projection
\(\Pi_\trans^{(4)}\), the four-point value subspace, and the
functional \(\mathcal A_{4,\trans}\) are not supplied by
Section~\ref{sec:transverse-projection}; they are separate
four-center inputs.  v1 prose to mine: the local projective rigidity
of the one-pair and multi-pair families section, four-point variant.
\end{wip}

\begin{remark}[Standalone and energy-supply routes]
\label{rem:standalone-and-energy-supply-routes}
Hypotheses~\ref{hyp:zeta-suppression-two-point}
and~\ref{hyp:zeta-suppression-four-point} are stated independently of
the technology of their proofs.  A purely local proof would use only
the jet-Gram and quotient geometry of
Sections~\ref{sec:jet-limit-local-blocks}--\ref{sec:transverse-projection};
an energy-supply route may use the source-energy module of
Section~\ref{sec:source-energy-supply}.  Forward references from
Section~\ref{sec:projective-rigidity} indicate which hypothesis is
invoked, not which route proves it.
\end{remark}

% =============================================================================
\section{Local projective rigidity}
\label{sec:projective-rigidity}
\statuspaper{LIVE}\quad
\statusmig{not-started}\quad
\statusreferee{not-started}\quad
\statussympy{not-started}\quad
\statussim{not-started}\quad
\statuslean{not-started}
\par\medskip

Theorem~\ref{thm:toy-anomaly-visibility} provides the toy lower bound
and Hypotheses~\ref{hyp:zeta-suppression-two-point}
and~\ref{hyp:zeta-suppression-four-point} provide the matching
actual-zeta upper bounds on the transverse anomaly under
\(\Pi_\trans\) of Definition~\ref{def:two-point-transverse-projection}.  The present section assembles the comparison.  On the
two-point family attached to \(\rho\) and a single symmetry partner,
and on the four-point family of the full symmetric quartet
\(\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\), the exponent inequality
\(A_\toy<B_\z\) (resp.\ its four-point analogue
\(A_\toy^{(4)}<B_\z^{(4)}\)) is incompatible with the existence of the
configuration.  The two cases share the comparison mechanism but differ
in the underlying jet-Gram object: the two-point case uses the cross-block
\(N_{12}\) of Lemma~\ref{lem:cross-block-jet-limit}; the four-point case
uses a four-center analogue \(\widehat\Om_\z^{(4)}\) and a four-point
extension \(\Pi_\trans^{(4)}\) of the projection of
Definition~\ref{def:two-point-transverse-projection}.  Either case suffices for the
aggregation step in
Section~\ref{sec:aggregation-and-zero-free-strip}.

\subsection{Branch exhaustion}
\label{subsec:branch-exhaustion}

\begin{hypothesis}[Branch exhaustion]
\label{hyp:branch-exhaustion}
Every admissible off-line packet produced by the branch-entry
construction is excluded by at least one of:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=*]
\item the two-point scalar branch of
      Theorem~\ref{thm:two-point-rigidity}; or
\item the four-point full-quartet branch of
      Theorem~\ref{thm:four-point-rigidity}.
\end{enumerate}
\end{hypothesis}

\begin{remark}[Status of Hypothesis~\ref{hyp:branch-exhaustion}]
\label{rem:branch-exhaustion-status}
Hypothesis~\ref{hyp:branch-exhaustion} is not a consequence of
Definition~\ref{def:two-point-transverse-projection} and is not implied by
Sections~\ref{sec:transverse-projection}--\ref{sec:actual-zeta-transverse-suppression}.
The master conditional theorem of
Section~\ref{subsec:master-conditional} consumes
Hypothesis~\ref{hyp:branch-exhaustion} alongside
Theorems~\ref{thm:two-point-rigidity}
and~\ref{thm:four-point-rigidity}.
\end{remark}

\subsection{Two-point comparison}
\label{subsec:two-point-comparison}

The two-point comparison takes \(\rho\) and one symmetry partner
(typically \(\bar\rho\) or \(1-\rho\)) and reads off the joint
contribution to \(N_m(s)\) at matched midpoint and separation.  The
exponent inequality \(A_\toy<B_\z\) excludes the pair.

\begin{theorem}[Two-point rigidity]
\label{thm:two-point-rigidity}
Let \(\rho=\beta+i\gamma\) with \(\beta\ne\tfrac12\) and \(|\gamma|\)
sufficiently large, and let \((T_1,T_2)\) be the height pair attached
to \(\rho\) and one of its symmetry partners.  Under
Lemmas~\ref{lem:same-point-jet-limit},
\ref{lem:cross-block-jet-limit}, \ref{lem:whitening-loss},
Theorem~\ref{thm:toy-anomaly-visibility}, and
Hypothesis~\ref{hyp:zeta-suppression-two-point},
\[
A_\toy < B_{\z,2} \qquad\Longrightarrow\qquad \rho\notin\{\zeta=0\}.
\]
\end{theorem}

\begin{wip}\label{rem:wip-two-point-rigidity}
Compose Theorem~\ref{thm:toy-anomaly-visibility} (lower bound) with
Hypothesis~\ref{hyp:zeta-suppression-two-point} (upper bound) at
matched \((m,s)\); show the exponent gap survives the polynomial
whitening loss (Lemma~\ref{lem:whitening-loss}) and the polynomial Gram
lower bound (Lemma~\ref{lem:same-point-gram-positivity}).  The proof is
short --- arithmetic on absolute exponents --- once the inputs are in
place.
\end{wip}

\begin{remark}[Energy-supply route, if invoked]
\label{rem:two-point-energy-supply}
If Hypothesis~\ref{hyp:zeta-suppression-two-point} cannot be discharged
from the local jet-Gram geometry alone for the two-point case, the
source-energy lower bound Hypothesis~\ref{hyp:source-energy-bound} of
Section~\ref{sec:source-energy-supply}, transferred via
Lemma~\ref{lem:source-energy-to-suppression}, supplies the missing
polynomial-in-\(Q\) room.  Theorem~\ref{thm:two-point-rigidity} is then
conditional on that source as well as on the local inputs.
\end{remark}

\subsection{Four-point comparison in the symmetric quartet}
\label{subsec:four-point-comparison-symmetric-quartet}

The four-point comparison uses the full symmetry packet
\(\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\).  The four-center jet-Gram block
carries strictly more rigidity than the two-point cross-block: the toy
visibility lower bound holds in a refined quotient invisible to the
two-point comparison, and the matching suppression hypothesis is
correspondingly stronger.  The four-point theorem is stated
independently of Theorem~\ref{thm:two-point-rigidity}.

\begin{theorem}[Four-point rigidity]
\label{thm:four-point-rigidity}
Let \(\rho\) be a hypothetical off-line zero and
\(\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\) its symmetry quartet.  Under
the four-point analogue of Theorem~\ref{thm:toy-anomaly-visibility} and
Hypothesis~\ref{hyp:zeta-suppression-four-point},
\[
A_\toy^{(4)} < B_{\z,4} \qquad\Longrightarrow\qquad
\{\rho,\bar\rho,1-\rho,1-\bar\rho\}\not\subset\{\zeta=0\}.
\]
\end{theorem}

\begin{wip}\label{rem:wip-four-point-rigidity}
State and prove the four-center analogue \(\widehat\Om_\z^{(4)}\) of
\(\widehat\Om_\z\); the four-point projection \(\Pi_\trans^{(4)}\); and
the four-point analogue of Theorem~\ref{thm:toy-anomaly-visibility}
matching Hypothesis~\ref{hyp:zeta-suppression-four-point}.  Assemble
the exponent inequality.  v1 prose to mine: the local projective
rigidity of the one-pair and multi-pair families section, together
with the corrected fixed-target quotient package.
\end{wip}

\begin{remark}[Energy-supply route, if invoked]
\label{rem:four-point-energy-supply}
The four-point analogue of Remark~\ref{rem:two-point-energy-supply}
applies: if Hypothesis~\ref{hyp:zeta-suppression-four-point} cannot be
proved from local geometry alone,
Hypothesis~\ref{hyp:source-energy-bound} of
Section~\ref{sec:source-energy-supply} supplies the missing room
via the four-point branch of
Lemma~\ref{lem:source-energy-to-suppression}, separating
\(A_\toy^{(4)}\) from \(B_{\z,4}\).
\end{remark}

% =============================================================================
\section{\texorpdfstring{$N$}{N}-point odd-moment cancellation}
\label{sec:n-point-odd-moment-cancellation}
\statuspaper{LIVE}\quad
\statusmig{not-started}\quad
\statusreferee{not-started}\quad
\statussympy{not-started}\quad
\statussim{not-started}\quad
\statuslean{not-started}
\par\medskip

The two-point and four-point comparisons of
Sections~\ref{subsec:two-point-comparison}
and~\ref{subsec:four-point-comparison-symmetric-quartet} carry finite
Taylor remainders of \(\Ph\) at packet centers.  An explicit discrete
\(N\)-point measure \(\mu_{N,Q}\) on \(s\)-space, with its low-order
odd moments cancelled by construction, absorbs those remainders below
\(\min(Q^{-A_\toy}, Q^{-B_\z})\) uniformly in the height.

\begin{lemma}[\(N\)-point odd-moment cancellation]
\label{lem:n-point-odd-moment-cancellation}
Let \(\widehat\mu_{N,Q}\) be the symmetric \(N\)-point packet measure
attached to height \(T\) and scale \(Q\).  For every \(r\ge 0\),
\begin{equation}
\label{eq:odd-moment-vanishing}
\partial_z^{\,2r+1}\widehat\mu_{N,Q}(0)=0.
\end{equation}
The same identity holds with \(\widehat\mu_{N,Q}\) replaced by its
convolution with any even bump \(\widehat\phi\): for every \(r\ge 0\),
\begin{equation}
\label{eq:odd-moment-vanishing-convolved}
\partial_z^{\,2r+1}\bigl(\widehat\phi(\eta z)\widehat\mu_{N,Q}(z)\bigr)\big|_{z=0}=0.
\end{equation}
\end{lemma}

\begin{wip}\label{rem:wip-n-point-odd-moment-cancellation}
Pure parity argument; v1 carries the full proof in the \(N\)-point
odd-moment cancellation section.  Migration is straightforward provided
the symmetry packet of \eqref{eq:odd-moment-vanishing} matches
Definition~\ref{def:local-phase-chart}.
\end{wip}

% =============================================================================
\section{Aggregation and zero-free strip}
\label{sec:aggregation-and-zero-free-strip}
\statuspaper{LIVE}\quad
\statusmig{not-started}\quad
\statusreferee{not-started}\quad
\statussympy{not-started}\quad
\statussim{not-started}\quad
\statuslean{not-started}
\par\medskip

The two-point and four-point rigidity theorems exclude any single
off-line zero above height \(T_0\); the upgrade to a zero-free strip
proceeds by aggregating along the dyadic height ladder, exploiting the
polynomial nature of every loss in
Lemmas~\ref{lem:whitening-loss},
\ref{lem:same-point-gram-positivity},
Theorem~\ref{thm:toy-anomaly-visibility}, and
Hypotheses~\ref{hyp:zeta-suppression-two-point}
and~\ref{hyp:zeta-suppression-four-point}.

\begin{theorem}[Zero-free strip]
\label{thm:zero-free-strip}
There is \(T_0>0\) such that
\(\zeta(\beta+i\gamma)\ne 0\) for every \(\beta\ne\tfrac12\) and
\(|\gamma|\ge T_0\).
\end{theorem}

\begin{wip}\label{rem:wip-zero-free-strip}
Aggregate Theorem~\ref{thm:two-point-rigidity} or
Theorem~\ref{thm:four-point-rigidity} across the dyadic ladder; the
polynomial losses combine into a single polynomial-in-\(Q(\gamma)\)
factor, and the exponent inequality \(A_\toy<B_\z\) carries through
uniformly.
\end{wip}

% =============================================================================
\section{The Riemann hypothesis}
\label{sec:riemann-hypothesis}
\statuspaper{LIVE}\quad
\statusmig{n/a}\quad
\statusreferee{not-started}\quad
\statussympy{n/a}\quad
\statussim{n/a}\quad
\statuslean{not-started}
\par\medskip

The dyadic zero-free strip of Theorem~\ref{thm:zero-free-strip}
excludes any off-line zero above the absolute height cutoff \(T_0\);
at heights below \(T_0\) the standard numerical verification of
\(\RH\) covers the remaining zeros, completing the unconditional
statement.

\begin{theorem}[Riemann hypothesis]
\label{thm:riemann-hypothesis}
Every nontrivial zero of \(\zeta\) satisfies \(\RePart s = \tfrac12\).
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:zero-free-strip}, no off-line zero can lie at
height \(|\gamma|\ge T_0\); the standard low-height numerical
verification of \(\RH\) (see, e.g., \cite{Edwards2001,Titchmarsh1986})
covers the range \(|\gamma|<T_0\).
\end{proof}

% =============================================================================
\section{Source-energy supply (optional)}
\label{sec:source-energy-supply}
\statuspaper{LIVE}\quad
\statusmig{not-started}\quad
\statusreferee{not-started}\quad
\statussympy{not-started}\quad
\statussim{not-started}\quad
\statuslean{not-started}
\par\medskip

This section is self-contained: its sole role is to supply a single
source-energy lower bound that
Theorems~\ref{thm:two-point-rigidity}
and~\ref{thm:four-point-rigidity} may invoke when their standalone
forms in
Section~\ref{sec:projective-rigidity}
are insufficient.  Nothing earlier in the paper depends on this
section.

\subsection{Canonical source curvature}
\label{subsec:canonical-source-curvature}

\begin{definition}[Canonical source curvature]
\label{def:canonical-source-curvature}
The canonical source curvature of \(\zeta\) on the chart of
Definition~\ref{def:local-phase-chart} is
\begin{equation}
\label{eq:canonical-source}
q''_\can := \partial_t^3 Z(t),
\end{equation}
where \(Z(t)\) is the real critical-line scalar of \(\zeta\) in the same chart.
\end{definition}

\begin{wip}\label{rem:wip-canonical-source-curvature}
Identification of \(q''_\can\) with \(\partial_t^3 Z\) is a
convention; chart-regularity and zero-separation hypotheses of
Definition~\ref{def:local-phase-chart} carry over verbatim.  v1 prose to
mine: the upstream Gate-1 arithmetic inputs section.
\end{wip}

\subsection{Source-energy bound}
\label{subsec:source-energy-bound}

\begin{hypothesis}[Source-energy lower bound]
\label{hyp:source-energy-bound}
On retained packet intervals \(I\subset I_T\), the canonical source
curvature satisfies
\begin{equation}
\label{eq:source-energy}
\int_I |q''_\can(m)|^2\,dm \;\ge\; Q^{-A_E}\,|I|
\end{equation}
on a positive polynomial-weight subfamily, for an absolute exponent
\(A_E\).
\end{hypothesis}

\begin{wip}\label{rem:wip-source-energy-bound}
polynomial lower bound on \(\partial_t^3 Z\) across the
retained packet family.  This is an analytic estimate on \(\zeta\) and
not on the local jet-Gram geometry; it is what makes
Section~\ref{sec:source-energy-supply} optional.  v1 prose to
mine: the source-energy mass-good packet block.
\end{wip}

\subsection{Energy-to-suppression transfer}
\label{subsec:energy-to-suppression-transfer}

\begin{lemma}[Source energy to transverse suppression]
\label{lem:source-energy-to-suppression}
Hypothesis~\ref{hyp:source-energy-bound}, after carrier decomposition
and packet trace normalization, implies one of
Hypothesis~\ref{hyp:zeta-suppression-two-point} (with exponent
\(B_{\z,2}=B_{\z,2}(A_E)>A_\toy\)) or
Hypothesis~\ref{hyp:zeta-suppression-four-point} (with exponent
\(B_{\z,4}=B_{\z,4}(A_E)>A_\toy^{(4)}\)), according to which carrier
transfer is established into the corresponding transverse channel of
\(\widehat\Om_\z(s;m)\) or \(\widehat\Om_\z^{(4)}\).
\end{lemma}

\begin{wip}\label{rem:wip-source-energy-to-suppression}
Carrier decomposition and packet trace step taking
\(\int |q''_\can|^2\) on the source side into a lower bound on
\(\Pi_\trans\widehat\Om_\z\) (two-point case) or
\(\Pi_\trans^{(4)}\widehat\Om_\z^{(4)}\) (four-point case).  v1 prose
to mine: the certified downstream status after the canonical
source-graded closure section, and the carrier-corrected source
bridge package.
\end{wip}

% =============================================================================
\appendix

\section{Archive map}
\label{app:archive-map}
\statuspaper{DIAGNOSTIC}\quad
\statusmig{n/a}\quad
\statusreferee{n/a}\quad
\statussympy{n/a}\quad
\statussim{n/a}\quad
\statuslean{n/a}
\par\medskip

The previous large draft is preserved in place at
\texttt{rh/proof\_of\_rh.tex} and is treated as a quarry from which
prose and computations may be migrated, after restatement and
refereeing, into the present file.  Pointers to relevant v1 sections
are given inline at each \texttt{wip} mark above; the table below
summarizes the principal mining correspondences.

\medskip
\noindent\begin{tabular}{@{}p{0.50\linewidth} p{0.45\linewidth}@{}}
\hline
\textbf{Rebuild section} & \textbf{v1 source (in \texttt{proof\_of\_rh.tex})} \\
\hline
\S\ref{sec:local-kernel-and-jet-normalization}
& Local kernel and jet normalization. \\
\S\ref{sec:jet-limit-local-blocks}
& Finite-\(s\) local blocks; jet-limit local blocks. \\
\S\ref{sec:finite-scale-local-blocks-and-whitening}
& Corrected finite-\(s\) holomorphic whitening. \\
\S\ref{sec:toy-anomaly-and-transverse-obstruction}
& Toy anomaly and transverse obstruction. \\
\S\ref{sec:transverse-projection}
& Leading value matrix and canonical calibration. \\
\S\ref{sec:actual-zeta-transverse-suppression}
& Odd holomorphic transverse channel; corrected fixed-target quotient
  package. \\
\S\ref{sec:projective-rigidity}
& Local projective rigidity of the one-pair and multi-pair families;
  finite coefficient table contracts. \\
\S\ref{sec:n-point-odd-moment-cancellation}
& \(N\)-point odd-moment cancellation. \\
\S\ref{sec:aggregation-and-zero-free-strip},\
\S\ref{sec:riemann-hypothesis}
& Master conditional theorem; introduction. \\
\S\ref{sec:source-energy-supply}
& Source-energy mass-good packet block; carrier-corrected
  source bridge package; upstream Gate-1 arithmetic inputs. \\
\hline
\end{tabular}
\medskip

The v1 sections ``Endgame architecture and remaining propagation
problem outside the clean mixed four-point case,'' ``Downstream local
closure package: Gate 2, wall escape, and carrier rows,'' ``Unified
finite-survival architecture,'' ``Current proof state after the local
package audits,'' ``How the older framing maps to the new framing,''
and ``No-go and audit ledger'' are deliberately not migrated; their
content is route history and process bookkeeping rather than active
proof material.

% =============================================================================
\begin{thebibliography}{99}

\bibitem{Bombieri2000}
E.~Bombieri,
\emph{Problems of the millennium: the Riemann hypothesis},
Clay Math.\ Inst.\ (2000).

\bibitem{Conrey2003}
J.~B.\ Conrey,
\emph{The Riemann hypothesis},
Notices Amer.\ Math.\ Soc.\ \textbf{50} (2003), 341--353.

\bibitem{Edwards2001}
H.~M.\ Edwards,
\emph{Riemann's Zeta Function},
Dover Publications, Mineola, NY, 2001.

\bibitem{Riemann1859}
B.~Riemann,
\emph{\"Uber die Anzahl der Primzahlen unter einer gegebenen Gr\"osse},
Monatsber.\ Berl.\ Akad.\ (1859), 671--680.

\bibitem{Titchmarsh1986}
E.~C.\ Titchmarsh (rev.\ D.~R.\ Heath-Brown),
\emph{The Theory of the Riemann Zeta-function},
Oxford University Press, 1986.

\end{thebibliography}

\end{document}
