\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}

\title{An Abstract Odd-Projector Layer Extracted from the RH Draft}
\author{Working note in \texttt{grh/}}
\date{2026-04-23}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\begin{document}

\maketitle

\begin{abstract}
This note isolates the strongest source-light local statement that the current
RH draft appears to support. It is deliberately narrower than any GRH, ERH, or
Dirichlet portability claim. The theorem here stops at an odd holomorphic
transverse scalar and the universal \(N\)-point odd-moment projector. It does
not include the family-specific realization of that scalar, and it does not
include the later RH-specific endgame.
\end{abstract}

\section{Scope}

The current RH draft mixes a generic local phase package with a zeta-side
realization package. The safest common core is the odd-germ/projector layer.
This note records only that layer.

\section{Setup}

Fix a midpoint \(m\) and a microscopic variable \(s\). Suppose one is given:

\begin{enumerate}
\item a real critical-line phase \(\Phi\) with derivative \(q=\Phi'\);
\item same-point and mixed finite-\(s\) jet blocks
\[
G_{m,\pm}(s),\qquad N_m(s),
\]
defined and holomorphic on \(|s|<\rho_0/Q\);
\item positive-definite same-point blocks on that disk, so that the whitened
block
\[
\widehat\Omega(s;m)=G_{m,-}(s)^{-1/2}N_m(s)G_{m,+}(s)^{-1/2}
\]
is holomorphic there;
\item a real linear functional \(\Phi_K\) on the whitened block space such that
the extracted scalar
\[
H_m(s):=\Phi_K\bigl(\widehat\Omega(s;m)\bigr)
\]
is odd under symmetric placement;
\item a microscopic boundary estimate
\[
|H_m(s)|\le \frac{\mathcal B(m)}{Q^3}
\qquad\text{for } |s|=\rho_0/Q.
\]
\end{enumerate}

No family realization is assumed here beyond the existence of this package.

\section{Abstract theorem}

\begin{theorem}[Odd-germ projector layer]
Under the setup above:

\begin{enumerate}
\item \(H_m\) is odd and holomorphic on \(|s|<\rho_0/Q\);
\item if
\[
H_m(z/Q^2)=\sum_{r\ge 0} c_{2r+1}(m)\frac{z^{2r+1}}{Q^{2r+4}},
\]
then the coefficients satisfy Cauchy bounds of size \(\ll \mathcal B(m)\)
with constants depending only on \(\rho_0\);
\item for the universal coefficients \(a_j^{(N)}\) from the RH draft,
\[
\Xi^{(N)}(m):=\sum_{j=1}^N a_j^{(N)}H_m(j/Q^2)
\]
annihilates odd jets through order \(2N-3\).
\end{enumerate}
\end{theorem}

\begin{proof}
This is exactly the layer extracted by the follow-up attack in
\texttt{tasks/20260423-052540-attack-gap-local-package-portability/}.

Oddness is part of the setup. Holomorphy follows from the holomorphic block and
whitening hypotheses. The coefficient bounds are then immediate from Cauchy's
estimate on the microscopic disk. The final claim uses only the universal
odd-moment identities satisfied by the coefficients \(a_j^{(N)}\). No further
source-specific arithmetic input enters at this stage.
\end{proof}

\section{What is not included}

The theorem above does \emph{not} include:

\begin{enumerate}
\item a completed-\(L\) realization theorem producing the package in the setup;
\item the calibration comparison
\[
u^2\asymp \frac{x}{B}S(m),
\]
which needs extra family-specific hypotheses;
\item any RH-specific remote-incidence, provenance, or global propagation
argument;
\item any GRH- or ERH-style conclusion.
\end{enumerate}

\section{Conditional calibration layer}

The research cycle and its adversarial check indicate that calibration should
be treated separately.

To add calibration, one needs at least:

\begin{enumerate}
\item a realized value-channel derivative in the same family;
\item a real sign-compatible amplitude replacing \(S(m)\);
\item a nonzero toy pairing in the same channel;
\item a preserved corrected-whitening scale strong enough to keep the remainder
small in the calibration functional.
\end{enumerate}

So calibration is not part of the unconditional odd-projector theorem.

\section{Use}

This note is meant to separate two tasks that had been blurred together:

\begin{enumerate}
\item isolate the truly abstract local odd-germ / projector mechanism;
\item separately solve the realization problem for each target family.
\end{enumerate}

That separation is the safest route for later work on primitive Dirichlet
\(L\)-functions or the Ramanujan \(\tau\) \(L\)-function.

\section{Provenance}

This note was distilled from:

\begin{enumerate}
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/synthesis.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/local_package_theorem.md};
\item \texttt{tasks/20260423-052540-attack-gap-local-package-portability/reports/gap-local-package-routeA.md};
\item \texttt{tasks/20260423-052540-attack-gap-local-package-portability/reports/gap-local-package-routeB.md};
\item \texttt{tasks/20260423-052540-attack-gap-local-package-portability/reports/verifier-adversarial-local-package.md}.
\end{enumerate}

\end{document}
