\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}

\title{Candidate Paired Source-and-Slot Theorem for Primitive Dirichlet Characters}
\author{Working note in \texttt{grh/}}
\date{2026-04-23}

\begin{document}

\maketitle

\begin{abstract}
This note records the current best non-zeta theorem target identified in the
\texttt{grh/} program: an exact paired source-and-slot realization blueprint
for primitive Dirichlet characters. The target is conservative. It does not
claim a realized theorem. It isolates the exact paired object, the compact
source-package burden, the local-slot identification burden, and the immediate
downstream work that must remain deferred.
\end{abstract}

\section{The paired object}

For a primitive Dirichlet character \(\chi\), define the paired completed
object
\[
\Xi_\chi(s):=\Lambda(s,\chi)\Lambda(s,\overline\chi)
\]
and the strip-edge quotient
\[
\Phi_\chi^{\mathrm{pair}}(s):=\frac{\Xi_\chi(2s-1)}{\Xi_\chi(2s)}.
\]

This is the cleanest theorem-facing paired object from current scope alone. It
packages the contragredient pair into one self-dual scalar object and removes
the residual root-number asymmetry at the boundary phase level. If one chooses
to write an explicit boundary phase while keeping the fixed quotient and a
positive strip-edge source scalar, the sign-audited convention is:
\[
\Phi_\chi^{\mathrm{pair}}\!\left(\tfrac12+it\right)=e^{-2i\Theta_\chi^{\mathrm{pair}}(t)},
\qquad
q_\chi^{\mathrm{pair}}(t)=\Theta_\chi^{\mathrm{pair}\,\prime}(t).
\]
Equivalently, the positive zero-kernel contribution is carried by
\(-\frac12(\Phi_\chi^{\mathrm{pair}\,\prime}/
\Phi_\chi^{\mathrm{pair}})(\tfrac12+it)\). Using a positive exponent would
require defining \(q_\chi^{\mathrm{pair}}=-\Theta_\chi^{\mathrm{pair}\,\prime}\)
or replacing the quotient by its inverse.

\section{Why this object}

Three features motivate this choice.

\begin{enumerate}
\item It mirrors the zeta strip-edge quotient form directly.
\item Its boundary phase law is cleaner than the single-channel quotient law.
\item Conditional on an exact paired-source theorem, the one-zero strip-edge
kernel and its positivity are automatic upstairs.
\end{enumerate}

From current scope alone, this does not yet imply the exact local scalar used by
the manuscript's value channel.

\section{Candidate theorem}

The cleanest current theorem target is a two-stage statement.

\subsection*{Stage 1: paired source theorem}

On singularity-free compact intervals, prove a source theorem of the form
\[
q_\chi^{\mathrm{pair}}(t)=B_\chi^{\mathrm{pair}}(t)+S_\chi^{\mathrm{pair}}(t),
\]
where:

\begin{enumerate}
\item \(q_\chi^{\mathrm{pair}}\) is the phase derivative coming from
\(\Phi_\chi^{\mathrm{pair}}\);
\item \(B_\chi^{\mathrm{pair}}\) is one unified paired background term,
containing conductor/scaling, gamma derivatives, and any trivial-zero or pole
corrections;
\item \(S_\chi^{\mathrm{pair}}\) is the background-subtracted paired strip-edge
zero scalar.
\end{enumerate}

\subsection*{Stage 2: slot realization}

Prove that this exact paired scalar occupies the manuscript's local value slot:
\[
\Delta_\chi^{\mathrm{pair}}(m,\sigma)
=
S_\chi^{\mathrm{pair}}(m)
A_{\mathrm{val},\chi}^{\mathrm{pair}}(m,\sigma)
+
R_\chi^{\mathrm{pair}}(m,\sigma).
\]

Only after this second step does the paired scalar become the exact analogue of
the manuscript's \(S(m)\).

The safest theorem-facing patch order is therefore:

\begin{enumerate}
\item a compact-interval paired source-package blueprint;
\item exact paired local-slot identification.
\end{enumerate}

Even in Step 1, the theorem should stay narrow: unified paired background and
multiplicity are safest immediately after the theorem as explicit bookkeeping,
not overloaded into the theorem body.

\section{What becomes automatic after slot realization}

If the paired theorem yields the exact local slot above, then the manuscript's
existing local algebra already supplies the leading-channel interface. No second
coefficient theorem is needed beyond the slot-realization theorem itself.

\section{What remains after slot realization}

Even then, the following remain separate burdens:

\begin{enumerate}
\item remainder dominance in the calibrated value-channel subchain;
\item corrected odd/transverse realization;
\item denominator and whitening control;
\item boundary estimates for the odd scalar;
\item any variable-\(x\) or calibration-uniformity issues.
\end{enumerate}

So this note identifies the first non-zeta exact-source target, not the whole
portability theorem.

One further caution is now clear from the `grh/` work: the exact slot theorem
already needs a small local analytic admissibility package. In particular, the
theorem-facing statement should not pretend that the slot identity follows from
upstairs source data alone. It still needs the local symmetric normal form,
holomorphic whitening admissibility, and explicit same-point
positivity/nondegeneracy hypotheses in the paired family.

\section{Safe scope}

The strongest safe wording at present is:

\begin{quote}
From current scope alone, the paired source-and-slot theorem is the cleanest
first non-zeta exact-source target.
\end{quote}

It is not yet safe to call it the uniquely correct or fully realized non-zeta
theorem.

\section{Provenance}

This note is distilled from:

\begin{enumerate}
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/dirichlet\_paired\_source.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/paired\_slot\_realization.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/paired\_slot\_hypotheses.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/paired\_source\_package.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/paired\_proof\_plan.md};
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/paired\_value\_channel.md};
\item \texttt{tasks/20260423-141819-attack-gap-dirichlet-paired-source/reports/gap-dirichlet-paired-source-routeA.md};
\item \texttt{tasks/20260423-141819-attack-gap-dirichlet-paired-source/reports/gap-dirichlet-paired-source-routeB.md};
\item \texttt{tasks/20260423-143207-attack-gap-paired-object-candidate/reports/gap-paired-object-routeA.md};
\item \texttt{tasks/20260423-143207-attack-gap-paired-object-candidate/reports/gap-paired-object-routeB.md};
\item \texttt{tasks/20260423-144416-attack-gap-paired-quotient-properties/reports/gap-paired-quotient-routeA.md};
\item \texttt{tasks/20260423-144416-attack-gap-paired-quotient-properties/reports/gap-paired-quotient-routeB.md};
\item \texttt{tasks/20260423-184608-attack-gap-paired-background/reports/gap-paired-background-routeA.md};
\item \texttt{tasks/20260423-184608-attack-gap-paired-background/reports/gap-paired-background-routeB.md};
\item \texttt{tasks/20260423-194735-attack-gap-paired-slot-realization/reports/gap-paired-slot-routeA.md};
\item \texttt{tasks/20260423-194735-attack-gap-paired-slot-realization/reports/gap-paired-slot-routeB.md};
\item \texttt{tasks/20260423-194735-attack-gap-paired-slot-realization/reports/verifier-adversarial-paired-slot-realization.md}.
\end{enumerate}

\end{document}
