\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}

\title{A Positive Strip-Edge Kernel Extracted from the RH Draft}
\author{Working note in \texttt{grh/}}
\date{2026-04-23}

\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\begin{document}

\maketitle

\begin{abstract}
This note isolates a conservative theorem that is genuinely supported by the
current RH draft: each strip zero contributes a positive strip-edge kernel,
and omitted-zero tails built from these kernels admit the curvature bound used
in the manuscript once the stated shell-convergence hypotheses are imposed. The
note does not claim a fully normalized completed-function identity for the
phase derivative \(q\); that stronger source-level reading remains conditional
on a separate theorem.
\end{abstract}

\section{Single-zero kernel}

\begin{lemma}[Positive strip-edge kernel]
Let \(\rho=\beta+i\gamma\) with \(0\le \beta\le 1\). Define
\[
K_\rho(t):=\Re\left(\frac{1}{1+2it-\rho}-\frac{1}{2it-\rho}\right).
\]
Then for every real \(t\),
\[
K_\rho(t)=
\frac{1-\beta}{(1-\beta)^2+(2t-\gamma)^2}
+
\frac{\beta}{\beta^2+(2t-\gamma)^2},
\]
and in particular \(K_\rho(t)>0\).
\end{lemma}

\begin{proof}
Write
\[
\frac{1}{1+2it-\rho}=
\frac{1-\beta-i(2t-\gamma)}{(1-\beta)^2+(2t-\gamma)^2},
\qquad
\frac{1}{2it-\rho}=
\frac{-\beta-i(2t-\gamma)}{\beta^2+(2t-\gamma)^2}.
\]
Taking real parts and subtracting gives the displayed identity. Both summands
are nonnegative when \(0\le \beta\le 1\), and at least one is strictly
positive.
\end{proof}

\section{Summed tail layer}

Suppose now that one has an omitted-zero set and forms the strip-edge tail
\[
T_{\mathrm{far}}(t)=\sum_{\rho\notin \mathcal L} K_\rho(t).
\]

The manuscript uses this object under explicit local shell-convergence
hypotheses. In that setting, the single-zero kernel lemma feeds the curvature
bound.

\begin{lemma}[Conditional omitted-tail curvature]
Assume the omitted-zero shell sums converge strongly enough to justify termwise
differentiation up to order two, and let
\[
\Delta_\rho:=\operatorname{dist}(2I,\gamma_\rho)
\]
for a fixed real interval \(I\). Then on \(I\), each omitted zero satisfies
\[
|K_\rho''(t)|\ll \Delta_\rho^{-4},
\]
and therefore
\[
\sum_{\rho\notin \mathcal L}|K_\rho''(t)|
\ll
\sum_{\rho\notin \mathcal L}\Delta_\rho^{-4}.
\]
\end{lemma}

\begin{proof}
Each summand of \(K_\rho\) has the form
\[
g_a(u)=\frac{a}{a^2+u^2}
\qquad (a\in[0,1]).
\]
Direct differentiation shows \(|g_a''(u)|\ll |u|^{-4}\) away from \(u=0\).
Since omitted zeros satisfy \(|2t-\gamma_\rho|\ge \Delta_\rho\) on \(I\), the
bound follows termwise. Summation is justified by the stated convergence
hypothesis.
\end{proof}

\section{What this note does not claim}

This note stops deliberately before the stronger source-level statement. In
particular, it does \emph{not} claim from the current manuscript formulas alone
that
\[
q(t)=B_\zeta(t)+S(t)
\]
has already been proved as a fully normalized completed-log-derivative identity
with all gamma, pole, trivial-zero, and Hadamard bookkeeping supplied.

The safe statement is narrower:

\begin{enumerate}
\item the single-zero strip-edge kernel is positive;
\item the omitted-zero tail built from these kernels has the curvature bound used
in the manuscript once the local shell-convergence package is stated;
\item this isolates a positive strip-edge scalar candidate for later completed-
\(L\) generalization work.
\end{enumerate}

\section{Why this matters}

The GRH notes in \texttt{grh/} now separate three layers:

\begin{enumerate}
\item an unconditional odd-germ / odd-projector layer;
\item a candidate-object refinement saying the zeta scalar \(S(m)\) should be
viewed as a positive strip-edge zero kernel;
\item a still-missing completed-\(L\) realization theorem for Dirichlet or
Ramanujan-\(\tau\).
\end{enumerate}

This note belongs only to the second layer.

\section{Provenance}

This note was distilled from:

\begin{enumerate}
\item \texttt{grh/20260423-050630-research-team-grh-dirichlet-tau/notes/scattering_generalization.md};
\item \texttt{tasks/20260423-130548-attack-gap-scattering-generalization/reports/gap-scattering-generalization-routeA.md};
\item \texttt{tasks/20260423-130548-attack-gap-scattering-generalization/reports/gap-scattering-generalization-routeB.md};
\item \texttt{tasks/20260423-130548-attack-gap-scattering-generalization/reports/verifier-adversarial-scattering-generalization.md};
\item \texttt{tasks/20260423-131531-attack-gap-strip-edge-kernel/reports/gap-strip-edge-kernel-routeA.md};
\item \texttt{tasks/20260423-131531-attack-gap-strip-edge-kernel/reports/gap-strip-edge-kernel-routeB.md};
\item \texttt{tasks/20260423-131531-attack-gap-strip-edge-kernel/reports/verifier-adversarial-strip-edge-kernel.md}.
\end{enumerate}

\end{document}
