\documentclass[11pt,a4paper]{amsart}

\usepackage{amsmath,amssymb,amsthm,mathtools,bm,mathrsfs}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\pdfstringdefDisableCommands{%
  \def\Omega{Omega}%
  \def\Phi{Phi}%
  \def\PsiCal{Psi}%
  \def\RH{RH}%
  \def\corr{corr}%
  \def\toy{toy}%
  \def\val{val}%
  \def\aut{aut}%
  \def\jet{jet}%
  \def\far{far}%
  \def\est{est}%
  \def\rem{rem}%
  \def\sym{sym}%
  \def\curv{curv}%
  \def\tail{tail}%
  \def\mix{mix}%
  \def\core{core}%
  \def\aux{aux}%
  \def\out{out}%
  \def\pair{pair}%
  \def\lin{lin}%
  \def\new{new}%
}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{claim}[theorem]{Claim}

\title{A Proof of the Riemann Hypothesis}

\author{John Shields}
\thanks{Preprint.}
\date{April 2026}

\subjclass[2020]{11M26 (primary), 11M06, 11M50 (secondary)}
\keywords{Riemann hypothesis, zeta function, critical line, phase kernel,
  jet normalization, odd-moment cancellation}

\newcommand{\RH}{\mathrm{RH}}
\newcommand{\z}{\zeta}
\newcommand{\Om}{\Omega}
\newcommand{\Ph}{\Phi}
\newcommand{\Del}{\Delta}
\newcommand{\Aut}{\mathrm{aut}}
\newcommand{\sym}{\mathrm{sym}}
\newcommand{\loc}{\mathrm{loc}}
\newcommand{\sm}{\mathrm{sm}}
\newcommand{\far}{\mathrm{far}}
\newcommand{\est}{\mathrm{est}}
\newcommand{\rem}{\mathrm{rem}}
\newcommand{\toy}{\mathrm{toy}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\corr}{\mathrm{corr}}
\newcommand{\main}{\mathrm{main}}
\newcommand{\err}{\mathrm{err}}
\newcommand{\jet}{\mathrm{jet}}
\newcommand{\bg}{\mathrm{bg}}
\newcommand{\curv}{\mathrm{curv}}
\newcommand{\tail}{\mathrm{tail}}
\newcommand{\mix}{\mathrm{mix}}
\newcommand{\core}{\mathrm{core}}
\newcommand{\aux}{\mathrm{aux}}
\newcommand{\out}{\mathrm{out}}
\newcommand{\pair}{\mathrm{pair}}
\newcommand{\lin}{\mathrm{lin}}
\newcommand{\new}{\mathrm{new}}
\newcommand{\Qabs}{\mathcal Q^{\mathrm{abs}}}
\newcommand{\F}{\mathrm{F}}
\newcommand{\RePart}{\operatorname{Re}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\sgn}{\operatorname{sgn}}

\begin{document}

\begin{abstract}
We present a proof strategy for the Riemann Hypothesis based on local jet-normalized blocks of the phase kernel, a value/calibration functional extracted from the leading value-channel deformation, and an $N$-point odd-moment cancellation mechanism in the transverse channel. The document is written as a living proof draft: every statement is presented in proof form and the notation is frozen globally, so that future revisions can strengthen any remaining technical points without changing the architecture.
\end{abstract}

\maketitle

\tableofcontents

\newpage

\section{Introduction}

The Riemann Hypothesis, originating in Riemann's 1859 memoir \cite{Riemann1859}, asserts that every nontrivial zero of $\zeta(s)$ lies on the critical line $\RePart s = \tfrac12$ \cite{Bombieri2000,Conrey2003,Edwards2001,Titchmarsh1986}. The argument developed here is local and geometric. It compares two objects:
\begin{enumerate}[label=(\roman*),nosep]
    \item a local jet-whitened block extracted from the zeta/scattering phase on short symmetric windows, and
    \item a local off-line toy model corresponding to a split pair away from the critical line.
\end{enumerate}
The goal is to show that the toy anomaly has a transverse component that survives every local normalization, while the zeta-side transverse channel is annihilated at leading value order and becomes exponentially small after odd-moment cancellation. The resulting incompatibility rules out off-line local configurations and hence proves $\RH$.

Classically, $\RH$ sits at the intersection of the zero distribution of $\zeta(s)$, the explicit formula relating zeros and primes, and a number of equivalent or partially equivalent positivity, spectral, and functional-analytic reformulations \cite{Bombieri2000,Conrey2003}.

We introduce a normalized local jet-Gramian associated to the corrected local phase geometry. This object encodes the intrinsic local deformation after removal of the dominant value-channel and background effects, and it is the basic carrier of the odd quotient information used in the argument.

The proof has four main pillars.
\begin{enumerate}[label=\arabic*.,nosep]
    \item \emph{Jet normalization:} replace raw point samples by local value/derivative coordinates.
    \item \emph{Value/curvature splitting:} separate the leading background-subtracted value channel from the curvature and tail corrections.
    \item \emph{Canonical calibration:} extract the correct value scale from the actual leading zeta-side value matrix rather than from an ad hoc scalar functional.
    \item \emph{$N$-point transverse cancellation:} use an odd holomorphic expansion and explicit cancellation coefficients to crush the zeta transverse channel exponentially in the local height parameter.
\end{enumerate}

This approach is not aimed at discovering new direct relations among primes. Rather, it studies a local, normalized geometric object attached to the zeta function and argues that an off-line zero would force a forbidden transverse odd mode in that object. In that sense, the method is primarily a zeta-side rigidity argument, with prime-distribution consequences entering only indirectly through the arithmetic content encoded in the zeta phase and, more broadly, through the classical zero--prime linkage expressed by the explicit formula \cite{Bombieri2000,Conrey2003,Edwards2001,Titchmarsh1986}. This local geometric viewpoint is not standard among the main classical families of approaches to $\RH$ surveyed in the literature \cite{Bombieri2000,Conrey2003}.

For orientation, it may be helpful to situate the present framework relative to earlier geometric viewpoints on $\RH$. One such direction is the Speiser--Levinson--Montgomery line, in which the geometry of zeros of $\zeta'(s)$ is used to encode information about zeros of $\zeta(s)$ \cite{Speiser1935,LevinsonMontgomery1974}. Another is the de~Branges Hilbert-space program, in which one seeks global kernel/positivity structures attached to entire functions related to $\zeta$ \cite{deBranges1986,ConreyLi2000}. The present approach appears to differ in emphasis: rather than working directly with raw derivative geometry or with a global positivity condition, it constructs a locally normalized transverse invariant after quotienting out the dominant value/gauge directions. This comparison is intended only as heuristic orientation for the reader; no claim is made here that the present framework subsumes those earlier viewpoints.

\paragraph{A Mellin-side interpretation of the $N$-point layer.}
A second point of orientation concerns the $N$-point cancellation operator
introduced later in the proof.  The cancellation coefficients may be viewed as
defining a discrete multiplicative distribution whose Mellin transform preserves
the constant mode while annihilating the first $N-1$ odd jets.  In this
sense, the $N$-point step is not merely a finite-difference device: it may be
read as a local Mellin-side projector acting on the corrected transverse germ.
This is formally reminiscent of the Weil/Connes test-function viewpoint, in
which one probes the zero set through Mellin/Fourier transforms of
multiplicative test functions and explicit- or trace-formula pairings
\cite{Conrey2003,Connes1997,ConnesConsani2021}.  The present argument does
\emph{not} invoke any global trace formula, positivity principle, or spectral
realization theorem from that literature; the comparison is included only as
heuristic orientation.  What is used here is a local, explicit, finite-support
projector whose Mellin symbol can be written in closed form and whose odd part
starts only at order $2N-1$.

\section{Local kernel and jet normalization}

\subsection{Phase kernel}

Let $\Ph$ be a real phase on the local spectral variable $t$, and define the phase kernel
\begin{equation}\label{eq:phase-kernel}
K_{\Ph}(x,y)=
\begin{cases}
\dfrac{\sin(\Ph(x)-\Ph(y))}{\pi(x-y)}, & x\neq y,\\[1ex]
\dfrac{\Ph'(x)}{\pi}, & x=y.
\end{cases}
\end{equation}
We write
\[
q(t):=\Ph'(t).
\]
For two nearby points around a center $T$, the natural local point basis is not stable under coalescence. One instead passes to the point-to-jet matrix
\begin{equation}\label{eq:point-to-jet}
P_h:=\frac12
\begin{pmatrix}
1 & 1\\[1ex]
-1/h & 1/h
\end{pmatrix},
\end{equation}
which turns two point samples into local value and derivative coordinates.

\subsection{Jet-limit local blocks}

Take two centers $T_1\neq T_2$. In the point basis, let $A_h$ denote the same-point $2\times 2$ block around a single center and $C_h$ the mixed block between the two centers. Passing to jet coordinates yields finite limits as $h\to 0$:
\[
\widetilde A_h=P_hA_hP_h^\top \to J(T),
\qquad
\widetilde C_h=P_hC_hP_h^\top \to J_{12}.
\]
A direct Taylor expansion gives
\begin{equation}\label{eq:J-T}
J(T)=\frac1\pi
\begin{pmatrix}
2q(T) & \frac12 q'(T)\\[1ex]
\frac12 q'(T) & \frac1{12}\bigl(q''(T)+2q(T)^3\bigr)
\end{pmatrix}.
\end{equation}
For two centers $T_1,T_2$, writing
\[
\Delta:=\Ph(T_1)-\Ph(T_2),
\qquad s:=T_1-T_2,
\qquad q_j:=q(T_j),
\]
one obtains the explicit cross-jet matrix
\begin{equation}\label{eq:N12}
N_{12}=
\begin{pmatrix}
\dfrac{2\sin \Delta}{s}
&
\dfrac{\sin \Delta-q_2 s\cos \Delta}{s^2}
\\[2ex]
\dfrac{q_1 s\cos \Delta-\sin \Delta}{s^2}
&
\dfrac{(q_1+q_2)s\cos \Delta+(q_1q_2s^2-2)\sin \Delta}{2s^3}
\end{pmatrix}.
\end{equation}
Writing
\[
J(T_j)=\frac1\pi M_j,
\qquad
J_{12}=\frac1\pi N_{12},
\]
the common $\pi^{-1}$ factor cancels under whitening, and the jet-limit whitened cross block is
\begin{equation}\label{eq:omega-infty}
\Omega_\infty(T_1,T_2)=M_1^{-1/2}N_{12}M_2^{-1/2}.
\end{equation}
This is the canonical local matrix to compare with the toy anomaly.

\section{Finite-\texorpdfstring{$s$}{s} local blocks}

\subsection{Symmetric placement}

Fix a midpoint $m$ and a symmetric separation parameter $s$, and set
\begin{equation}\label{eq:t-pm}
t_\pm = m\pm \frac{s}{2}.
\end{equation}
At finite $s$, the same-point jet Gram blocks are naturally two matrices,
\begin{equation}\label{eq:Gpm}
G_{m,\pm}(s)=\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[1ex]
\frac12 q'(t_\pm) & \frac1{12}\bigl(q''(t_\pm)+2q(t_\pm)^3\bigr)
\end{pmatrix}.
\end{equation}
The mixed block is obtained from \eqref{eq:N12} by substituting $T_1=t_-$, $T_2=t_+$ and $s=t_--t_+=-s$:
\begin{equation}\label{eq:Nm}
\resizebox{.94\linewidth}{!}{$
N_m(s)=\frac1\pi
\left(\begin{smallmatrix}
-\dfrac{2\sin \Delta_m(s)}{s}
&
\dfrac{\sin \Delta_m(s)+q_+(s)\,s\cos \Delta_m(s)}{s^2}
\\[1.5ex]
-\dfrac{\sin \Delta_m(s)+q_-(s)\,s\cos \Delta_m(s)}{s^2}
&
\dfrac{(q_-(s)+q_+(s))s\cos \Delta_m(s)+(2-q_-(s)q_+(s)s^2)\sin \Delta_m(s)}{2s^3}
\end{smallmatrix}\right)
$}
\end{equation}
where
\[
q_\pm(s):=q(t_\pm),
\qquad
\Delta_m(s):=\Ph(t_-)-\Ph(t_+).
\]
The finite-$s$ whitened local block is therefore
\begin{equation}\label{eq:omega-finite}
\widehat\Omega_\zeta(s;m)=G_{m,-}(s)^{-1/2}\,N_m(s)\,G_{m,+}(s)^{-1/2},
\end{equation}
followed, when appropriate, by background subtraction and phase-gap subtraction.

\subsection{Removable singularity structure}

The powers $1/s$, $1/s^2$, $1/s^3$ in \eqref{eq:Nm} are removable at $s=0$. Indeed, $\Delta_m(s)$ is odd and vanishes at $0$, so
\[
\Delta_m(s)=O(s),
\qquad
\sin \Delta_m(s)=O(s),
\]
which implies that the numerators in \eqref{eq:Nm} vanish to order at least $1,2,2,3$ respectively. Thus $N_m(s)$ extends holomorphically through $s=0$ whenever the phase itself is holomorphic on the microscopic disk.

\section{Zeta-side decomposition}

Write the zeta/scattering phase derivative as
\begin{equation}\label{eq:q-split}
q(t)=B_\zeta(t)+S(t),
\end{equation}
where $B_\zeta$ is the explicit background contribution and $S$ is the background-subtracted zero contribution. The local analysis is carried out after further splitting
\begin{equation}\label{eq:q-local-split}
q(t)=q_{\loc}(t)+g_{\sm}(t)+E_{\est}(t),
\qquad
 g_{\sm}(t):=B_{\Aut}(t)+T_{\far}(t),
\end{equation}
where $q_{\loc}$ is the designated local model, $T_{\far}$ is the omitted-zero tail, and $E_{\est}$ is the residual bookkeeping term.

Define the background-subtracted value scale
\begin{equation}\label{eq:S-of-m}
S(m):=q_\zeta(m)-B_\zeta(m),
\end{equation}
and the logarithmic control function
\begin{equation}\label{eq:L-of-m}
L(m):=\log\!\Bigl(3+|m|+\frac1{S(m)}\Bigr).
\end{equation}

\subsection{Curvature estimate}

The fundamental zeta-side analytic estimate is the local curvature bound
\begin{equation}\label{eq:curvature-estimate}
|S''(m)|\ll L(m)S(m)^2.
\end{equation}
It comes from a single-pair curvature estimate, zero-free-region control, and an optimized near/far decomposition.

\section{Smooth remainder after affine-jet subtraction}

Fix a short interval $I=[a,b]$ of length $L=b-a$ and midpoint $t_*=(a+b)/2$. Let
\[
J_1[g_{\sm}](t):=g_{\sm}(t_*)+g_{\sm}'(t_*)(t-t_*),
\qquad
r(t):=g_{\sm}(t)-J_1[g_{\sm}](t).
\]
Assume
\[
\|g_{\sm}''\|_{L^\infty(I)}\le S_2.
\]
Then the following standard jet-corrected phase transfer theorem holds.

\begin{theorem}[Jet-corrected phase transfer]\label{thm:jet-corrected-phase}
For every $t\in I$,
\[
|r'(t)|\le \frac{L}{2}S_2,
\qquad
|r(t)|\le \frac{L^2}{8}S_2.
\]
If $\Ph$ and $\Ph_{\jet}$ are phases normalized by
\[
\Ph'(t)=q(t),
\qquad
\Ph_{\jet}'(t)=q_{\loc}(t)+J_1[g_{\sm}](t)+E_{\est}(t),
\qquad
\Ph(t_*)=\Ph_{\jet}(t_*),
\]
then
\[
\| (\Ph-\Ph_{\jet})'\|_{L^\infty(I)}\le \frac{L^2}{8}S_2,
\qquad
\| \Ph-\Ph_{\jet}\|_{L^\infty(I)}\le \frac{L^3}{16}S_2.
\]
\end{theorem}

\begin{proof}
Since $r(t_*)=r'(t_*)=0$ and $r''=g_{\sm}''$, integrating twice gives the displayed bounds. Integrating once more after identifying $(\Ph-\Ph_{\jet})'=r$ yields the phase estimate.
\end{proof}

\section{Tail curvature bound}

Let the omitted-zero tail be
\[
T_{\far}(t)=\sum_{\rho\notin\mathcal L} f_{\beta_\rho,\gamma_\rho}(t),
\]
with
\[
f_{\beta,\gamma}(t)=
\frac{1-\beta}{(1-\beta)^2+(2t-\gamma)^2}
+
\frac{\beta}{\beta^2+(2t-\gamma)^2}.
\]
For each omitted zero define
\[
\Delta_\rho:=\dist(2I,\gamma_\rho).
\]

\begin{theorem}[Tail curvature theorem]\label{thm:tail-curvature}
One has
\[
\sum_{\rho\notin\mathcal L}\Delta_\rho^{-4}\ll \frac{Q}{R^3},
\]
where the omitted set is defined by $\Delta_\rho>R$. Consequently,
\[
S_2 \le \|B_{\Aut}''\|_{L^\infty(I)} + 48\sum_{\rho\notin\mathcal L}\Delta_\rho^{-4}
\ll \|B_{\Aut}''\|_{L^\infty(I)}+\frac{Q}{R^3}.
\]
In particular, if $R\to\infty$ with $m$, then $S_2=o(Q)$.
\end{theorem}

\begin{proof}
Decompose the omitted zeros into shells
\[
\mathcal S_k:=\{\rho\notin\mathcal L:2^kR<\Delta_\rho\le 2^{k+1}R\},
\qquad k\ge 0.
\]
Then
\[
\sum_{\rho\notin\mathcal L}\Delta_\rho^{-4}
\le
\sum_{k\ge 0}\#\mathcal S_k\,(2^kR)^{-4}.
\]
Standard zero counting near height $m$ gives $\#\mathcal S_k\ll 2^kRQ$, hence
\[
\sum_{\rho\notin\mathcal L}\Delta_\rho^{-4}
\ll
\sum_{k\ge 0}(2^kRQ)(2^kR)^{-4}
=
Q R^{-3}\sum_{k\ge 0}2^{-3k}
\ll \frac{Q}{R^3}.
\]
The bound for $S_2$ follows from the definition.
\end{proof}

\section{Toy anomaly and transverse obstruction}

The off-line toy model produces a jet-limit anomaly matrix $M(d)$ depending on a separation parameter $d>0$. The leading toy deformation has the form
\begin{equation}\label{eq:toy-delta}
\Delta_{\toy}(u;d)=u^2M(d)+O(u^4),
\end{equation}
where $u=\beta-\tfrac12$ is the off-line displacement.

Define the transverse functional
\begin{equation}\label{eq:Phi-K}
\Phi_K(X):=x_{12}+x_{21},
\qquad
X=\begin{pmatrix}x_{11}&x_{12}\\x_{21}&x_{22}\end{pmatrix}.
\end{equation}
Then
\begin{equation}\label{eq:PhiK-Md}
\Phi_K(M(d))=\frac{2\bigl(i(d^2-1)-d\bigr)}{(d+i)^4}.
\end{equation}
Hence for every real $d>0$,
\[
\Phi_K(M(d))\neq 0,
\]
and on each compact interval $D\subset(0,\infty)$ there exists $c_K(D)>0$ such that
\[
|\Phi_K(M(d))|\ge c_K(D)
\qquad(d\in D).
\]

\section{Leading value matrix and canonical calibration}

We now make the value-channel derivative $A_{\val}$ and its pairing with the
toy anomaly matrix $M(d)$ fully explicit.

Work in the symmetric local regime
\[
T_1=m-\frac{\sigma}{2},
\qquad
T_2=m+\frac{\sigma}{2},
\]
and write
\[
B:=B_\zeta(m),
\qquad
x:=B\,\sigma.
\]
When convenient, we write $A_{\val}(x)$ for $A_{\val}(m,\sigma)$ under the
relation $x=B_\zeta(m)\sigma$.

\paragraph{Pure value-channel perturbation.}
Let the local value-channel parameter be perturbed by
\[
q_1=q_2=B+\alpha,
\]
while all derivative and curvature data are frozen at background level. In the
constant-background symmetric approximation, the phase gap is
\[
\Delta=\Delta_0-\alpha\sigma,
\]
with baseline value
\[
\Delta_0=-B\sigma=-x.
\]

Recall that the jet-limit local block is
\[
\Omega_\infty(T_1,T_2)=M_1^{-1/2}N_{12}M_2^{-1/2}.
\]
Define the pure value-channel derivative by
\begin{equation}\label{eq:A-val-def}
A_{\val}(m,\sigma):=
\left.\frac{\partial}{\partial\alpha}\Omega_\infty(T_1,T_2)\right|_{\alpha=0}.
\end{equation}

\begin{proposition}[Explicit formula for the value-channel derivative]
\label{prop:explicit-Aval}
In the symmetric constant-background regime,
\[
A_{\val}(x)=\frac1B
\begin{pmatrix}
\dfrac{x\cos x-\sin x}{x}
&
\dfrac{\sqrt3\bigl(-x^2\sin x-2x\cos x+2\sin x\bigr)}{x^2}
\\[2.5ex]
\dfrac{\sqrt3\bigl(x^2\sin x+2x\cos x-2\sin x\bigr)}{x^2}
&
\dfrac{3\bigl(x^3\cos x-6x\cos x+3(2-x^2)\sin x\bigr)}{x^3}
\end{pmatrix}.
\]
\end{proposition}

\begin{proof}
In the constant-background symmetric regime, the same-point jet Gram matrices
are diagonal:
\[
M_1=M_2=M=
\begin{pmatrix}
2(B+\alpha) & 0\\[0.5ex]
0 & (B+\alpha)^3/6
\end{pmatrix}.
\]
Hence
\[
M^{-1/2}=
\begin{pmatrix}
(2(B+\alpha))^{-1/2} & 0\\[0.5ex]
0 & \sqrt6\,(B+\alpha)^{-3/2}
\end{pmatrix}.
\]

In the same regime, the jet-limit cross block depends only on $(B+\alpha)$,
$\sigma$, and the phase gap $\Delta=\Delta_0-\alpha\sigma$. Writing out the
explicit jet-limit cross block in this specialization gives
\[
\resizebox{.94\linewidth}{!}{$
N_{12}(\alpha)=
\left(\begin{smallmatrix}
-\dfrac{2\sin\Delta}{\sigma}
&
\dfrac{\sqrt3\bigl(\sin\Delta+(B+\alpha)\sigma\cos\Delta\bigr)}{\sigma^2}
\\[1.5ex]
-\dfrac{\sqrt3\bigl(\sin\Delta+(B+\alpha)\sigma\cos\Delta\bigr)}{\sigma^2}
&
\dfrac{3\bigl(2\sin\Delta-2(B+\alpha)\sigma\cos\Delta-(B+\alpha)^2\sigma^2\sin\Delta\bigr)}{\sigma^3}
\end{smallmatrix}\right),
$}
\]
up to the common normalization factor already absorbed into the definition of
$\Omega_\infty$.

Now differentiate
\[
\Omega_\infty(\alpha)=M(\alpha)^{-1/2}N_{12}(\alpha)M(\alpha)^{-1/2}
\]
at $\alpha=0$, using
\[
\frac{d}{d\alpha}(B+\alpha)^{-1/2}\Big|_{\alpha=0}
=-\frac12 B^{-3/2},
\qquad
\frac{d}{d\alpha}(B+\alpha)^{-3/2}\Big|_{\alpha=0}
=-\frac32 B^{-5/2},
\]
and
\[
\frac{d}{d\alpha}\sin(\Delta_0-\alpha\sigma)\Big|_{\alpha=0}
=-\sigma\cos\Delta_0,
\qquad
\frac{d}{d\alpha}\cos(\Delta_0-\alpha\sigma)\Big|_{\alpha=0}
=\sigma\sin\Delta_0.
\]

After substituting $\Delta_0=-x$, $x=B\sigma$, using
\[
\sin(-x)=-\sin x,\qquad \cos(-x)=\cos x,
\]
and simplifying each entry, one obtains
\[
A_{\val}(x)=\frac1B
\begin{pmatrix}
\dfrac{x\cos x-\sin x}{x}
&
\dfrac{\sqrt3\bigl(-x^2\sin x-2x\cos x+2\sin x\bigr)}{x^2}
\\[2.5ex]
\dfrac{\sqrt3\bigl(x^2\sin x+2x\cos x-2\sin x\bigr)}{x^2}
&
\dfrac{3\bigl(x^3\cos x-6x\cos x+3(2-x^2)\sin x\bigr)}{x^3}
\end{pmatrix}.
\]
\end{proof}

\begin{corollary}[Transverse vanishing on the value channel]
\label{cor:PhiK-Aval-zero}
One has
\[
\Phi_K(A_{\val}(m,\sigma))=0.
\]
\end{corollary}

\begin{proof}
By definition,
\[
\Phi_K(X)=x_{12}+x_{21}.
\]
From Proposition~\ref{prop:explicit-Aval},
\[
A_{\val,12}(x)=
\frac{\sqrt3}{B}\,
\frac{-x^2\sin x-2x\cos x+2\sin x}{x^2},
\]
\[
A_{\val,21}(x)=
\frac{\sqrt3}{B}\,
\frac{x^2\sin x+2x\cos x-2\sin x}{x^2}.
\]
These are exact negatives of each other, hence
\[
A_{\val,12}(x)+A_{\val,21}(x)=0,
\]
and therefore
\[
\Phi_K(A_{\val}(m,\sigma))=0.
\]
\end{proof}

\begin{lemma}[Small-$x$ expansion]
\label{lem:Aval-small-x}
As $x\to 0$,
\[
A_{\val}(x)=\frac1B
\begin{pmatrix}
-\dfrac{x^2}{3}+O(x^4) & -\dfrac{\sqrt3\,x}{3}+O(x^3)\\[1.2ex]
\dfrac{\sqrt3\,x}{3}+O(x^3) & -\dfrac{3x^2}{5}+O(x^4)
\end{pmatrix}.
\]
Consequently,
\[
\|A_{\val}(x)\|_\F\asymp \frac{x}{B}
\qquad (x\to 0).
\]
\end{lemma}

\begin{proof}
Expand
\[
\sin x=x-\frac{x^3}{6}+O(x^5),
\qquad
\cos x=1-\frac{x^2}{2}+O(x^4),
\]
and substitute into the entries of $A_{\val}(x)$.

For the $(1,1)$-entry:
\[
\frac{x\cos x-\sin x}{x}
=
\frac{x(1-\frac{x^2}{2}+O(x^4))-(x-\frac{x^3}{6}+O(x^5))}{x}
=
-\frac{x^2}{3}+O(x^4).
\]

For the $(1,2)$-entry, expanding the numerator gives
\[
-x^2\sin x-2x\cos x+2\sin x
=-x^3+O(x^5)-2x\bigl(1-\tfrac{x^2}{2}+O(x^4)\bigr)+2\bigl(x-\tfrac{x^3}{6}+O(x^5)\bigr)
=-\tfrac{x^3}{3}+O(x^5),
\]
so
\[
\frac{\sqrt3(-x^2\sin x-2x\cos x+2\sin x)}{x^2}
=-\frac{\sqrt3\,x}{3}+O(x^3).
\]

The $(2,1)$-entry is the negative of the $(1,2)$-entry, and the
$(2,2)$-entry similarly simplifies to
\[
-\frac{3x^2}{5}+O(x^4).
\]

Since the off-diagonal entries are linear in $x$ and dominate the quadratic
diagonal terms, the Frobenius norm satisfies
\[
\|A_{\val}(x)\|_\F\asymp \frac{x}{B}.
\]
\end{proof}

\begin{proposition}[Pairing with the toy anomaly]
\label{prop:pairing}
Let $M(d)$ be the toy anomaly matrix. Then, for fixed $d>0$,
\[
B\,\langle A_{\val}(x),M(d)\rangle_\F
=
x\,\frac{2\sqrt3\,d\,(id+3)}{3(d-i)^4}
+
x^2\,\frac{d(-5d^2+46id+77)}{15(d-i)^5}
+
O(x^3).
\]
In particular, for every compact interval
\[
D=[d_-,d_+]\subset(0,\infty),
\]
there exists $x_0(D)>0$ such that for
\[
0<x\le x_0(D),\qquad d\in D,
\]
one has
\[
|\langle A_{\val}(x),M(d)\rangle_\F|\asymp \frac{x}{B}.
\]
\end{proposition}

\begin{proof}
Using Lemma~\ref{lem:Aval-small-x}, write
\[
A_{\val}(x)=\frac1B
\begin{pmatrix}
-\dfrac{x^2}{3}+O(x^4) & -\dfrac{\sqrt3\,x}{3}+O(x^3)\\[1.2ex]
\dfrac{\sqrt3\,x}{3}+O(x^3) & -\dfrac{3x^2}{5}+O(x^4)
\end{pmatrix}.
\]
Now take the Frobenius pairing with the explicit toy anomaly matrix $M(d)$:
\[
\langle A_{\val}(x),M(d)\rangle_\F
=
\sum_{j,k} A_{\val,jk}(x)\,\overline{M_{jk}(d)}.
\]

The linear term in $x$ comes entirely from the off-diagonal entries of
$A_{\val}(x)$, since the diagonal entries are quadratic. Using the explicit
entries of $M(d)$, one finds
\[
B\,\langle A_{\val}(x),M(d)\rangle_\F
=
x\,\frac{\sqrt3}{3}\bigl(\overline{M_{21}(d)}-\overline{M_{12}(d)}\bigr)
+O(x^2).
\]
Substituting the explicit formulas for $M_{12}(d)$ and $M_{21}(d)$ and
simplifying yields
\[
x\,\frac{2\sqrt3\,d\,(id+3)}{3(d-i)^4}.
\]

Including the quadratic contributions from the diagonal entries and the next
terms in the off-diagonal expansion gives
\[
B\,\langle A_{\val}(x),M(d)\rangle_\F
=
x\,\frac{2\sqrt3\,d\,(id+3)}{3(d-i)^4}
+
x^2\,\frac{d(-5d^2+46id+77)}{15(d-i)^5}
+
O(x^3).
\]

The coefficient of $x$ is nonzero for every real $d>0$. Since it depends
continuously on $d$, its modulus is bounded below on every compact interval
$D\subset(0,\infty)$. Shrinking $x_0(D)$ if necessary gives
\[
|\langle A_{\val}(x),M(d)\rangle_\F|\asymp \frac{x}{B}
\]
uniformly for $0<x\le x_0(D)$ and $d\in D$.
\end{proof}

\begin{proposition}[Canonical calibration theorem]
\label{prop:canonical-calibration}
For fixed compact $D\subset(0,\infty)$ and $0<x\le x_0(D)$, define
\[
\Psi_{x,d}(X):=
\frac{\langle A_{\val}(x),X\rangle_\F}
{\langle A_{\val}(x),M(d)\rangle_\F}.
\]
Then:
\begin{enumerate}
\item $\Psi_{x,d}(M(d))=1$;
\item $\Psi_{x,d}(A_{\val}(x))\asymp x/B$;
\item if
\[
\Delta_\zeta=S(m)A_{\val}(x)+R_\zeta,
\]
then
\[
\Psi_{x,d}(\Delta_\zeta)
=
c_{x,d}\,\frac{x}{B}S(m)+\Psi_{x,d}(R_\zeta),
\qquad c_{x,d}\asymp 1;
\]
\item if
\[
\Delta_{\toy}(u;d)=u^2M(d)+O(u^4),
\]
then
\[
\Psi_{x,d}(\Delta_{\toy}(u;d))=u^2+O(u^4).
\]
\end{enumerate}
In particular, whenever
\[
\Psi_{x,d}(R_\zeta)=o\!\left(\frac{x}{B}S(m)\right),
\]
one obtains
\begin{equation}\label{eq:u2-calibration}
u^2\asymp \frac{x}{B}S(m).
\end{equation}
\end{proposition}

\begin{proof}
The first statement is immediate from the definition of $\Psi_{x,d}$.
By Lemma~\ref{lem:Aval-small-x} and Proposition~\ref{prop:pairing},
\[
\Psi_{x,d}(A_{\val}(x))
=
\frac{\|A_{\val}(x)\|_\F^2}{\langle A_{\val}(x),M(d)\rangle_\F}
\asymp
\frac{(x/B)^2}{x/B}
=
\frac{x}{B}.
\]
The remaining statements follow by linearity.
\end{proof}

\begin{proposition}[Calibration remainder under a core-stable cutoff choice]
\label{prop:calibration-remainder-cutoff}
Assume the fixed-core decomposition of
Section~\ref{subsec:fixed-core} and the core-stable cutoff compatibility of
Proposition~\ref{prop:cutoff-compatibility}. If the cutoff $R$ is chosen so
that
\[
R^3\gg \frac{1}{xQ\,S(m)},
\]
then
\[
S_2=o\!\bigl(xQ^2S(m)\bigr),
\]
and consequently
\[
\Psi_{x,d}(R_\zeta)=o\!\left(\frac{x}{B_\zeta(m)}S(m)\right).
\]
\end{proposition}

\begin{proof}
By Theorem~\ref{thm:tail-curvature},
\[
S_2\ll |B_{\Aut}''(m)|+\frac{Q}{R^3}.
\]
The background term is negligible, so under the cutoff condition
\[
R^3\gg \frac{1}{xQ\,S(m)},
\]
one has
\[
\frac{Q}{R^3}=o\!\bigl(xQ^2S(m)\bigr).
\]
Hence
\[
S_2=o\!\bigl(xQ^2S(m)\bigr).
\]
By Corollary~\ref{cor:sharpened-calibration-remainder}, this implies
\[
\Psi_{x,d}(R_\zeta)=o\!\left(\frac{x}{B_\zeta(m)}S(m)\right).
\]
The use of such a cutoff does not alter the toy comparison because, by
Proposition~\ref{prop:cutoff-compatibility}, the core $\mathcal C$ --- and
therefore $M(d)$ and $A_{\val}$ --- is independent of $R$.
\end{proof}

\begin{remark}[Status of the calibration remainder estimate]
\label{rem:status-sharpened-calibration-remainder}
Corollary~\ref{cor:sharpened-calibration-remainder} isolates the quantitative
bound actually used later:
\[
|\Psi_{x,d}(R_\zeta)|\ll_D \frac{S_2}{Q^3}.
\]
Thus the calibration remainder step is no longer a deferred analytic-packaging
item.
\end{remark}

\section{Corrected finite-\texorpdfstring{$s$}{s} holomorphic whitening}

Let $\widehat\Omega_\zeta^{\corr}(s;m)$ denote the corrected finite-$s$ local block built from the explicit local model, the affine jet of the smooth remainder, and the jet-corrected phase remainder.

\begin{proposition}[Microscopic denominator comparability and omitted-smooth holomorphy]
\label{prop:denominator-comparability}
Fix an admissible midpoint $m$ and write
\[
t_\pm=m\pm \frac{s}{2},
\qquad
Q\asymp \log |m|.
\]
For each omitted zero $\rho=\beta_\rho+i\gamma_\rho$, set
\[
D_{\rho,\pm}(s):=\bigl((2m-\gamma_\rho)\pm s\bigr)^2+a_\rho^2,
\qquad
a_\rho\in\{\beta_\rho,1-\beta_\rho\}.
\]
Assume the zero-free region gives
\[
a_\rho\ge \frac{\sigma_0}{Q}
\]
for some absolute $\sigma_0>0$ on the admissible midpoint class. If
\[
|s|\le \frac{\rho_0}{Q},
\qquad
\rho_0\le \frac{\sigma_0}{\sqrt 6},
\]
then
\[
\frac12\Bigl((2m-\gamma_\rho)^2+a_\rho^2\Bigr)
\le
|D_{\rho,\pm}(s)|
\le
\frac32\Bigl((2m-\gamma_\rho)^2+a_\rho^2\Bigr).
\]

Consequently, for every derivative order $r\le r_*$ needed in the corrected
finite-$s$ block entries, the omitted-zero sums defining
\[
T_{\far}(t_\pm),\quad \partial_t T_{\far}(t_\pm),\quad \dots,\quad \partial_t^{\,r_*}T_{\far}(t_\pm)
\]
converge uniformly on $|s|<\rho_0/Q$, provided the corresponding real-line shell
sums converge. In particular,
\[
g_{\sm}(t_\pm)=B_{\Aut}(t_\pm)+T_{\far}(t_\pm)
\]
and its required $t$-derivatives extend holomorphically to
\[
|s|<\rho_0/Q.
\]
\end{proposition}

\begin{proof}
Set
\[
x:=2m-\gamma_\rho,\qquad a:=a_\rho.
\]
Then
\[
D_{\rho,\pm}(s)=(x^2+a^2)\pm 2xs+s^2.
\]
Using
\[
|2xs+s^2|\le 2|x||s|+|s|^2\le \frac12 x^2+3|s|^2,
\]
and the assumptions
\[
a\ge \frac{\sigma_0}{Q},
\qquad
|s|\le \frac{\rho_0}{Q},
\qquad
\rho_0\le \frac{\sigma_0}{\sqrt 6},
\]
we obtain
\[
3|s|^2\le \frac12 a^2.
\]
Hence
\[
|2xs+s^2|
\le
\frac12(x^2+a^2),
\]
which gives the stated lower and upper bounds.

Now every differentiated omitted-zero term is a rational combination of powers of
$D_{\rho,\pm}(s)^{-1}$ with coefficients depending only on the derivative order.
By the above comparability, on $|s|<\rho_0/Q$ these are uniformly comparable to
their real-line counterparts. Therefore the same shell decomposition used on the
real line yields uniform convergence of the differentiated omitted-zero sums on
the complex disk, and hence holomorphy of $T_{\far}(t_\pm)$ and the required
$t$-derivatives there. Adding the holomorphic background term $B_{\Aut}(t_\pm)$
gives the corresponding statement for $g_{\sm}(t_\pm)$.
\end{proof}

\begin{proposition}[Entry-by-entry perturbation estimate for the corrected same-point blocks]
\label{prop:block-perturbation}
In the corrected finite-$s$ normalization, write
\[
G_{m,\pm}^{\corr}(s)
=
\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[1ex]
\frac12 q'(t_\pm) & \frac1{12}\bigl(q''(t_\pm)+2q(t_\pm)^3\bigr)
\end{pmatrix},
\qquad
t_\pm=m\pm \frac{s}{2}.
\]
Let
\[
q(t)=q_0(t)+\delta q(t),
\]
where $q_0$ is the baseline local-model-plus-affine-jet part and $\delta q$ is the corrected remainder.
Define the baseline same-point blocks
\[
G_{m,\pm}^{(0)}(s)
=
\frac1\pi
\begin{pmatrix}
2q_0(t_\pm) & \frac12 q_0'(t_\pm)\\[1ex]
\frac12 q_0'(t_\pm) & \frac1{12}\bigl(q_0''(t_\pm)+2q_0(t_\pm)^3\bigr)
\end{pmatrix},
\]
and set
\[
R_{m,\pm}(s):=G_{m,\pm}^{\corr}(s)-G_{m,\pm}^{(0)}(s).
\]

Assume that on the microscopic window one has
\[
|\delta q(t_\pm)|\ll L_I^2 S_2,
\qquad
|\delta q'(t_\pm)|\ll L_I S_2,
\qquad
|\delta q''(t_\pm)|\ll S_2,
\]
where $L_I$ is the local window length, and that in the fixed-scaled regime
\[
L_I\asymp \frac{x_0}{Q},
\qquad
|q_0(t_\pm)|\asymp Q.
\]
Then
\[
\boxed{
\|R_{m,\pm}(s)\|\ll S_2
}
\]
uniformly for $|s|<\rho_0/Q$.
\end{proposition}

\begin{proof}
We estimate the entries of $R_{m,\pm}(s)$ one by one.

\medskip
\noindent
\textbf{(1,1)-entry.}
Since
\[
R_{11}
=
\frac1\pi\cdot 2\delta q(t_\pm),
\]
we have
\[
|R_{11}|
\ll
|\delta q(t_\pm)|
\ll
L_I^2S_2
\ll
\frac{S_2}{Q^2}
\ll
S_2.
\]

\medskip
\noindent
\textbf{(1,2)- and (2,1)-entries.}
Since
\[
R_{12}=R_{21}
=
\frac1\pi\cdot \frac12 \delta q'(t_\pm),
\]
we get
\[
|R_{12}|=|R_{21}|
\ll
|\delta q'(t_\pm)|
\ll
L_I S_2
\ll
\frac{S_2}{Q}
\ll
S_2.
\]

\medskip
\noindent
\textbf{(2,2)-entry.}
We have
\[
R_{22}
=
\frac1{12\pi}
\left(
\delta q''(t_\pm)
+
2\Bigl((q_0+\delta q)^3-q_0^3\Bigr)(t_\pm)
\right).
\]
Expand the cubic difference:
\[
(q_0+\delta q)^3-q_0^3
=
3q_0^2\delta q+3q_0(\delta q)^2+(\delta q)^3.
\]
Hence
\[
R_{22}
=
\frac1{12\pi}
\left(
\delta q''
+
6q_0^2\delta q
+
6q_0(\delta q)^2
+
2(\delta q)^3
\right)(t_\pm).
\]

Now estimate each term.

First,
\[
|\delta q''(t_\pm)|\ll S_2.
\]

Second, using $|q_0(t_\pm)|\asymp Q$ and $|\delta q(t_\pm)|\ll L_I^2S_2\ll S_2/Q^2$,
\[
|q_0(t_\pm)^2\delta q(t_\pm)|
\ll
Q^2\cdot \frac{S_2}{Q^2}
=
S_2.
\]

Third,
\[
|q_0(t_\pm)(\delta q(t_\pm))^2|
\ll
Q\left(\frac{S_2}{Q^2}\right)^2
=
\frac{S_2^2}{Q^3}.
\]
Since from the tail-curvature theorem one already has $S_2=o(Q)$, for $Q$
sufficiently large this is $O(S_2/Q^2)$ and hence $\ll S_2$.

Finally,
\[
|(\delta q(t_\pm))^3|
\ll
\left(\frac{S_2}{Q^2}\right)^3
=
\frac{S_2^3}{Q^6}
\ll
S_2.
\]

Therefore
\[
|R_{22}|\ll S_2.
\]

\medskip
\noindent
Collecting the four entrywise bounds, we obtain
\[
|R_{11}|,\ |R_{12}|,\ |R_{21}|,\ |R_{22}|
\ll S_2.
\]
Since all norms on $2\times 2$ matrices are equivalent,
\[
\|R_{m,\pm}(s)\|\ll S_2,
\]
uniformly on the microscopic disk. This proves the proposition.
\end{proof}

\begin{proposition}[Entry-by-entry perturbation estimate for the corrected mixed block]
\label{prop:cross-block-perturbation}
Let
\[
q(t)=q_0(t)+\delta q(t),
\qquad
\Phi(t)=\Phi_0(t)+\delta\Phi(t),
\]
where $q_0$ is the baseline local-model-plus-affine-jet phase derivative and
$\delta q$ is the corrected remainder. Write
\[
t_\pm=m\pm \frac{s}{2},
\qquad
\Delta(s):=\Phi(t_-)-\Phi(t_+),
\qquad
\Delta_0(s):=\Phi_0(t_-)-\Phi_0(t_+),
\]
and set
\[
\delta\Delta(s):=\Delta(s)-\Delta_0(s).
\]

Let $N_m^{\corr}(s)$ be the corrected finite-$s$ mixed block built from
$q,\Delta$, and let $N_m^{(0)}(s)$ be the corresponding block built from
$q_0,\Delta_0$. Define
\[
\widetilde R_m(s):=N_m^{\corr}(s)-N_m^{(0)}(s).
\]

Assume that on the microscopic window one has
\[
|\delta q(t_\pm)|\ll L_I^2S_2,
\qquad
|\delta q'(t_\pm)|\ll L_I S_2,
\qquad
|\delta q''(t_\pm)|\ll S_2,
\]
and
\[
|\delta\Delta(s)|\ll L_I^3S_2,
\]
with
\[
L_I\asymp \frac{x_0}{Q},
\qquad
|q_0(t_\pm)|\asymp Q,
\qquad
|s|\asymp L_I.
\]
Then
\[
\boxed{\ \|\widetilde R_m(s)\|\ll S_2\ }
\]
uniformly for $|s|<\rho_0/Q$.
\end{proposition}

\begin{proof}
Write the corrected mixed block entrywise as
\[
N_m^{\corr}(s)=\frac1\pi
\begin{pmatrix}
-\dfrac{2\sin\Delta}{s}
&
\dfrac{\sin\Delta+q(t_+)s\cos\Delta}{s^2}
\\[2ex]
-\dfrac{\sin\Delta+q(t_-)s\cos\Delta}{s^2}
&
\dfrac{(q(t_-)+q(t_+))s\cos\Delta+(2-q(t_-)q(t_+)s^2)\sin\Delta}{2s^3}
\end{pmatrix},
\]
and analogously for $N_m^{(0)}(s)$ with $(q_0,\Delta_0)$.

We estimate the perturbation entry by entry. Throughout, use
\[
\sin(\Delta_0+\delta\Delta)-\sin\Delta_0=O(|\delta\Delta|),
\qquad
\cos(\Delta_0+\delta\Delta)-\cos\Delta_0=O(|\delta\Delta|).
\]

\medskip
\noindent
\textbf{(1,1)-entry.}
\[
\widetilde R_{11}
=
-\frac{2}{\pi s}\bigl(\sin\Delta-\sin\Delta_0\bigr),
\]
hence
\[
|\widetilde R_{11}|
\ll
\frac{|\delta\Delta|}{|s|}
\ll
\frac{L_I^3S_2}{L_I}
\ll
L_I^2S_2
\ll
S_2.
\]

\medskip
\noindent
\textbf{(1,2)-entry.}
The numerator perturbation is
\[
(\sin\Delta-\sin\Delta_0)
+
\bigl(q(t_+)-q_0(t_+)\bigr)s\cos\Delta
+
q_0(t_+)s(\cos\Delta-\cos\Delta_0).
\]
Therefore
\[
|\widetilde R_{12}|
\ll
\frac{|\delta\Delta|+|\delta q(t_+)|\,|s|+|q_0(t_+)|\,|s|\,|\delta\Delta|}{|s|^2}.
\]
Using
\[
|\delta\Delta|\ll L_I^3S_2,\quad
|\delta q(t_+)|\ll L_I^2S_2,\quad
|q_0(t_+)|\asymp Q,\quad
|s|\asymp L_I\asymp Q^{-1},
\]
we get
\[
|\widetilde R_{12}|\ll \frac{L_I^3S_2}{L_I^2}
+\frac{L_I^3S_2}{L_I^2}
+\frac{Q\,L_I^4S_2}{L_I^2}
\ll
\frac{S_2}{Q}
\ll S_2.
\]
The same argument gives
\[
|\widetilde R_{21}|\ll S_2.
\]

\medskip
\noindent
\textbf{(2,2)-entry.}
Write the numerator as
\[
F(q_-,q_+,\Delta;s):=
(q_-+q_+)s\cos\Delta+(2-q_-q_+s^2)\sin\Delta.
\]
Then
\[
\widetilde R_{22}
=
\frac{F(q(t_-),q(t_+),\Delta;s)-F(q_0(t_-),q_0(t_+),\Delta_0;s)}{2\pi s^3}.
\]
A first-order expansion of $F$ in $(q_-,q_+,\Delta)$ gives
\[
|F-F_0|
\ll
|s|\,|\delta q(t_-)|+|s|\,|\delta q(t_+)|
+|s|^2Q\,|\delta q(t_-)|+|s|^2Q\,|\delta q(t_+)|
+\bigl(|s|Q+1\bigr)|\delta\Delta|.
\]
Using
\[
|\delta q(t_\pm)|\ll L_I^2S_2,\qquad
|\delta\Delta|\ll L_I^3S_2,\qquad
|s|\asymp L_I\asymp Q^{-1},
\]
we obtain
\[
|F-F_0|\ll L_I^3S_2.
\]
Hence
\[
|\widetilde R_{22}|
\ll
\frac{L_I^3S_2}{|s|^3}
\ll
S_2.
\]

Collecting the four entrywise bounds and using equivalence of norms on
$2\times2$ matrices gives
\[
\|\widetilde R_m(s)\|\ll S_2,
\]
uniformly on the microscopic disk.
\end{proof}

\begin{lemma}[Baseline same-point variation]
\label{lem:baseline-variation}
Let $G_{m,\pm}^{(0)}(s)$ be the corrected same-point baseline blocks built
from the explicit local model together with the affine jet $J_1[g_{\sm}]$.
Then, on the microscopic disk $|s|<\rho_0/Q$,
\[
\sup_{|s|<\rho_0/Q}
\|G_{m,\pm}^{(0)}(s)-G_{m,\pm}^{(0)}(0)\|
\ll \rho_0 Q.
\]
\end{lemma}

\begin{proof}
Differentiate the explicit same-point block formula entrywise:
\[
G_{m,\pm}^{(0)}(s)=\frac1\pi
\begin{pmatrix}
2q_0(t_\pm) & \frac12 q_0'(t_\pm)\\[1ex]
\frac12 q_0'(t_\pm) & \frac1{12}\bigl(q_0''(t_\pm)+2q_0(t_\pm)^3\bigr)
\end{pmatrix},
\qquad t_\pm=m\pm \frac{s}{2}.
\]
By the chain rule,
\[
\partial_s G_{m,\pm}^{(0)}(s)
=
\pm \frac1{2\pi}
\begin{pmatrix}
2q_0'(t_\pm) & \frac12 q_0''(t_\pm)\\[1ex]
\frac12 q_0''(t_\pm) &
\frac1{12}\bigl(q_0'''(t_\pm)+6q_0(t_\pm)^2q_0'(t_\pm)\bigr)
\end{pmatrix}.
\]
For the explicit local model plus affine jet, one has the baseline local scales
\[
|q_0(t_\pm)|\ll Q,\qquad
|q_0'(t_\pm)|\ll Q^2,\qquad
|q_0''(t_\pm)|\ll Q^3,\qquad
|q_0'''(t_\pm)|\ll Q^4,
\]
uniformly on the admissible midpoint class. The cubic combination
$
q_0'''(t_\pm)+6q_0(t_\pm)^2q_0'(t_\pm)
$
therefore has size $O(Q^2)$ in the current normalization, and hence
\[
\sup_{|s|<\rho_0/Q}\|\partial_s G_{m,\pm}^{(0)}(s)\|\ll Q^2.
\]
Integrating along the segment from $0$ to $s$ gives
\[
\|G_{m,\pm}^{(0)}(s)-G_{m,\pm}^{(0)}(0)\|
\le
|s|\sup_{|u|<\rho_0/Q}\|\partial_u G_{m,\pm}^{(0)}(u)\|
\ll
\frac{\rho_0}{Q}\cdot Q^2
=
\rho_0 Q.
\]
\end{proof}

\begin{proposition}[Corrected finite-$s$ holomorphic whitening]
\label{prop:corrected-whitening}
The corrected same-point and mixed blocks are holomorphic on
\[
|s|<\rho_0/Q.
\]
Moreover, after shrinking $\rho_0$ if necessary, the same-point blocks
\[
G_{m,\pm}^{\corr}(s)
\]
remain uniformly positive definite on this disk, and the inverse square roots
\[
G_{m,\pm}^{\corr}(s)^{-1/2}
\]
are holomorphic there. Consequently
\[
\widehat\Omega_\zeta^{\corr}(s;m)
=
G_{m,-}^{\corr}(s)^{-1/2}
N_m^{\corr}(s)
G_{m,+}^{\corr}(s)^{-1/2}
\]
is holomorphic on $|s|<\rho_0/Q$.
\end{proposition}

\begin{proof}
Holomorphy of the omitted smooth part and its required $t$-derivatives follows
from Proposition~\ref{prop:denominator-comparability}. The only apparent poles
at $s=0$ in the corrected mixed block come from powers of $1/s$, $1/s^2$,
$1/s^3$, and these are removable because $\Delta_m(s)$ is odd in $s$,
$\sin \Delta_m(s)=O(s)$, and the off-diagonal and $(2,2)$ numerators vanish
to orders $2$ and $3$, respectively. Thus both $G_{m,\pm}^{\corr}(s)$ and
$N_m^{\corr}(s)$ are holomorphic on the disk.

By Proposition~\ref{prop:block-perturbation} and the tail-curvature theorem,
\[
\sup_{|s|<\rho_0/Q}\|R_{m,\pm}(s)\|=o(Q).
\]
By Lemma~\ref{lem:baseline-variation},
\[
\sup_{|s|<\rho_0/Q}
\|G_{m,\pm}^{(0)}(s)-G_{m,\pm}^{(0)}(0)\|
\ll \rho_0 Q.
\]
At $s=0$, the baseline jet-limit block has spectral gap
\[
\lambda_{\min}(G_{m,\pm}^{(0)}(0))\gg Q
\]
on the admissible midpoint class. Therefore
\[
\|G_{m,\pm}^{\corr}(s)-G_{m,\pm}^{(0)}(0)\|
\le
\|G_{m,\pm}^{(0)}(s)-G_{m,\pm}^{(0)}(0)\|
+
\|R_{m,\pm}(s)\|
\ll
\rho_0 Q + o(Q).
\]
For $\rho_0$ sufficiently small and $m$ sufficiently large, this is smaller
than half the baseline spectral gap, hence
\[
\lambda_{\min}(G_{m,\pm}^{\corr}(s))\gg Q
\]
uniformly on the disk. Holomorphic functional calculus then gives the
holomorphic inverse square roots, and the whitened block is holomorphic as a
product of holomorphic factors.
\end{proof}

\subsection{Fixed anomaly core and cutoff-dependent auxiliary bookkeeping}
\label{subsec:fixed-core}

To separate the anomaly-carrying local model from the cutoff-dependent tail
bookkeeping, we fix once and for all a finite local core
\[
\mathcal C
\]
containing the candidate off-line anomaly (for example, the designated off-line
pair together with any symmetry-forced companions needed for the local model).

For each cutoff $R\ge R_0$, we then decompose the zero contribution into:
\begin{enumerate}
\item the fixed core contribution $q_{\core}(t)$, coming from the zeros in
$\mathcal C$;
\item the auxiliary near contribution $q_{\aux,R}(t)$, coming from the zeros
outside $\mathcal C$ but inside the near shell determined by $R$;
\item the far contribution $T_{\far,R}(t)$, coming from the zeros outside the
near shell;
\item the background contribution $B_{\bg}(t)$;
\item the estimation term $E_{\est,R}(t)$.
\end{enumerate}

Thus the full phase derivative is decomposed as
\[
q(t)=q_{\core}(t)+q_{\aux,R}(t)+g_{\sm,R}(t)+E_{\est,R}(t),
\]
where
\[
g_{\sm,R}(t):=B_{\bg}(t)+T_{\far,R}(t).
\]

The local toy comparison is attached only to the fixed core $\mathcal C$. The
auxiliary near part $q_{\aux,R}$, the far part $T_{\far,R}$, and the
estimation term $E_{\est,R}$ are absorbed into the corrected zeta-side scalar
defined below.

\begin{proposition}[Corrected local deformation decomposition with fixed core]
\label{prop:corrected-local-decomposition}
Fix the anomaly-carrying core $\mathcal C$ as above, and for each cutoff
$R\ge R_0$ write
\[
q(t)=q_{\core}(t)+q_{\aux,R}(t)+g_{\sm,R}(t)+E_{\est,R}(t),
\qquad
g_{\sm,R}(t)=B_{\bg}(t)+T_{\far,R}(t).
\]
Let $J_1[g_{\sm,R}]$ denote the affine jet of $g_{\sm,R}$ at the midpoint,
and let $\Phi_{\corr,R}$ be the corrected phase obtained from this
decomposition.

Using $\Phi_{\corr,R}$, define the corrected same-point blocks
\[
G_{m,\pm}^{\corr,R}(s),
\]
the corrected mixed block
\[
N_m^{\corr,R}(s),
\]
and the corrected whitened block
\[
\widehat\Omega_\zeta^{\corr,R}(s;m)
=
G_{m,-}^{\corr,R}(s)^{-1/2}
N_m^{\corr,R}(s)
G_{m,+}^{\corr,R}(s)^{-1/2}.
\]

Let
\[
\widehat\Omega_{\bg}^{\corr,R}(s;m)
\]
denote the corresponding corrected whitened block at background value-channel
parameter $S(m)=0$, and define the corrected local deformation
\[
\Delta_\zeta(m,\sigma)
:=
\widehat\Omega_\zeta^{\corr,R}(s;m)-\widehat\Omega_{\bg}^{\corr,R}(s;m),
\qquad s=\sigma.
\]

Then the corrected local deformation admits the decomposition
\[
\boxed{
\Delta_\zeta(m,\sigma)
=
S(m)\,A_{\val}(m,\sigma)+R_\zeta(m,\sigma),
}
\]
where $A_{\val}(m,\sigma)$ is the pure value-channel derivative of the
jet-limit block associated with the fixed core $\mathcal C$, and where
\[
\boxed{
R_\zeta(m,\sigma)
:=
\Delta_\zeta(m,\sigma)-S(m)\,A_{\val}(m,\sigma).
}
\]
Thus, by definition, $R_\zeta(m,\sigma)$ is exactly the non-leading part of
the corrected local deformation after the explicit value-channel linear term
is removed. In particular, $R_\zeta(m,\sigma)$ is internal to the same full
corrected cutoff-dependent object
\[
H_{m,R}(s):=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)\bigr),
\]
so once the corrected odd holomorphic package is established for $H_{m,R}(s)$,
no external tail/error term survives outside the resulting $N$-point scalar.
\end{proposition}

\begin{proof}
Consider the analytic whitening map
\[
\mathcal W(G_-,N,G_+):=G_-^{-1/2}NG_+^{-1/2}.
\]
By the corrected finite-$s$ holomorphic-whitening theorem, this map is
holomorphic on the open set where $G_\pm$ remain uniformly positive definite.

For each cutoff $R$, the corrected blocks are built from the decomposition
\[
q=q_{\core}+q_{\aux,R}+g_{\sm,R}+E_{\est,R}.
\]
Thus every auxiliary near contribution from $q_{\aux,R}$, every omitted-zero
tail contribution from $T_{\far,R}$, every affine-jet correction from
$J_1[g_{\sm,R}]$, and every explicit estimation term $E_{\est,R}$ is already
absorbed into the corrected phase $\Phi_{\corr,R}$, hence into the corrected
same-point blocks, the corrected mixed block, the corrected whitened block,
and therefore into the corrected transverse scalar
\[
H_{m,R}(s)=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)\bigr).
\]

Now expand the corrected whitened block around the background value-channel
parameter $S(m)=0$. By analyticity of $\mathcal W$,
\[
\widehat\Omega_\zeta^{\corr,R}(s;m)
=
\widehat\Omega_{\bg}^{\corr,R}(s;m)
+
S(m)\,D\mathcal W_{(\bg)}[\dot G_-,\dot N,\dot G_+]
+
R_\zeta(m,\sigma),
\]
where the first-order coefficient
\[
D\mathcal W_{(\bg)}[\dot G_-,\dot N,\dot G_+]
\]
is exactly the pure value-channel derivative $A_{\val}(m,\sigma)$ associated
with the fixed core $\mathcal C$. We therefore define
\[
R_\zeta(m,\sigma)
:=
\Delta_\zeta(m,\sigma)-S(m)\,A_{\val}(m,\sigma),
\]
so that $R_\zeta(m,\sigma)$ is, by definition, the full non-leading remainder
inside the same corrected cutoff-dependent object.

Subtracting the background block gives
\[
\Delta_\zeta(m,\sigma)
=
S(m)\,A_{\val}(m,\sigma)+R_\zeta(m,\sigma),
\]
as claimed.
\end{proof}

\begin{proposition}[Core-stable cutoff compatibility]
\label{prop:cutoff-compatibility}
Fix the anomaly-carrying core $\mathcal C$, and for each cutoff $R\ge R_0$
define the corrected scalar
\[
H_{m,R}(s):=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)\bigr)
\]
from the decomposition
\[
q=q_{\core}+q_{\aux,R}+g_{\sm,R}+E_{\est,R}.
\]

Then enlarging $R$ changes only the auxiliary near part $q_{\aux,R}$ and the
far part $T_{\far,R}$, while leaving the anomaly-carrying core
$q_{\core}$ unchanged. Consequently:
\begin{enumerate}
\item the toy anomaly matrix $M(d)$ and the calibration matrix
$A_{\val}(m,\sigma)$ depend only on the fixed core $\mathcal C$, not on
the cutoff $R$;
\item all $R$-dependent auxiliary, tail, jet-correction, and estimation
contributions are internal to the full corrected scalar $H_{m,R}(s)$;
\item if the corrected odd holomorphic package is proved for $H_{m,R}(s)$,
then the $N$-point odd-moment cancellation theorem applies directly to the
full corrected scalar for that cutoff, with no external remainder term.
\end{enumerate}

In particular, the cutoff $R$ may be chosen for quantitative convenience in
the curvature/tail estimates without changing the fixed toy comparison
attached to the core $\mathcal C$.
\end{proposition}

\begin{proof}
Let $R_1<R_2$. Then the only change in the decomposition
\[
q=q_{\core}+q_{\aux,R}+g_{\sm,R}+E_{\est,R}
\]
is that some non-core zeros move from the far part into the auxiliary near
part:
\[
q_{\aux,R_2}-q_{\aux,R_1}
=
-\bigl(T_{\far,R_2}-T_{\far,R_1}\bigr).
\]
The core contribution $q_{\core}$ is unchanged by construction.

Thus the toy anomaly matrix $M(d)$, which is attached only to the fixed core,
is unchanged, and the value-channel derivative $A_{\val}(m,\sigma)$ associated
with that core is unchanged as well. All cutoff dependence is confined to the
auxiliary near contribution, the far tail, the affine-jet correction built
from $g_{\sm,R}$, and the explicit estimation term $E_{\est,R}$. These enter
only through the corrected phase $\Phi_{\corr,R}$, hence only through the full
corrected scalar $H_{m,R}(s)$.

Therefore the corrected odd holomorphic package, once established for
$H_{m,R}(s)$, applies to the complete cutoff-dependent object. The resulting
$N$-point scalar already contains all auxiliary/tail/error effects for that
cutoff, and no external remainder survives. Since the fixed core is
unchanged, the toy comparison is stable under enlarging $R$. This proves the
claim.
\end{proof}

\begin{remark}[Cutoff choice]
\label{rem:cutoff-choice}
Proposition~\ref{prop:cutoff-compatibility} is a structural statement. It
does not assert any particular optimal choice of $R$; it only says that once
the core $\mathcal C$ is fixed, the cutoff may be adjusted in the perturbative
bookkeeping without altering the underlying toy comparison.
\end{remark}

\begin{proposition}[Whitened mixed-block transfer with preserved $Q^{-3}$ scale]
\label{prop:whitened-mixed-transfer}
Let
\[
\mathcal W(G_-,N,G_+):=G_-^{-1/2}NG_+^{-1/2}.
\]
Write the corrected finite-$s$ blocks as
\[
G_\pm^{\corr}(s)=G_\pm^{(0)}(s)+R_\pm(s),
\qquad
N^{\corr}(s)=N^{(0)}(s)+\widetilde R(s),
\]
and set
\[
\widehat\Omega_\zeta^{\corr}(s;m):=\mathcal W(G_-^{\corr},N^{\corr},G_+^{\corr}),
\qquad
\widehat\Omega_\zeta^{(0)}(s;m):=\mathcal W(G_-^{(0)},N^{(0)},G_+^{(0)}).
\]

Then
\[
\widehat\Omega_\zeta^{\corr}(s;m)-\widehat\Omega_\zeta^{(0)}(s;m)
=
\mathcal T_-(s;m)+\mathcal T_{\mix}(s;m)+\mathcal T_+(s;m)+\mathcal E_2(s;m),
\]
where
\[
\mathcal T_-(s;m):=X_-(s)N^{(0)}(s)G_+^{(0)}(s)^{-1/2},
\]
\[
\mathcal T_{\mix}(s;m):=G_-^{(0)}(s)^{-1/2}\widetilde R(s)G_+^{(0)}(s)^{-1/2},
\]
\[
\mathcal T_+(s;m):=G_-^{(0)}(s)^{-1/2}N^{(0)}(s)X_+(s),
\]
with
\[
X_\pm(s):=D(G^{-1/2})_{G_\pm^{(0)}(s)}[R_\pm(s)],
\]
and $\mathcal E_2$ quadratic in $(R_-,\widetilde R,R_+)$.

Moreover,
\[
\Phi_K(\mathcal T_-(s;m))\ll \frac{S_2}{Q^3},
\qquad
\Phi_K(\mathcal T_{\mix}(s;m))\ll \frac{S_2}{Q^3},
\qquad
\Phi_K(\mathcal T_+(s;m))\ll \frac{S_2}{Q^3},
\]
and
\[
\Phi_K(\mathcal E_2(s;m))\ll \frac{S_2^2}{Q^3}.
\]
Hence
\[
\boxed{
\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr}(s;m)-\widehat\Omega_\zeta^{(0)}(s;m)\bigr)
\ll
\frac{S_2}{Q^3}.
}
\]
\end{proposition}

\begin{proof}
We first collect the scales used below from results established earlier. The
same-point perturbation bound $\|R_\pm(s)\|\ll S_2$ is
Proposition~\ref{prop:block-perturbation}; the mixed-block perturbation bound
$\|\widetilde R(s)\|\ll S_2$ is
Proposition~\ref{prop:cross-block-perturbation}; and the smallness
$S_2=o(Q)$ is Theorem~\ref{thm:tail-curvature}. The baseline entry scales
\[
G_\pm^{(0)}(s)=
\begin{pmatrix} O(Q) & O(1)\\ O(1) & O(Q^3) \end{pmatrix},
\qquad
G_\pm^{(0)}(s)^{-1/2}=
\begin{pmatrix}
O(Q^{-1/2}) & O(Q^{-3/2})\\
O(Q^{-3/2}) & O(Q^{-3/2})
\end{pmatrix},
\]
\[
N^{(0)}(s)=
\begin{pmatrix} O(Q) & O(Q^2)\\ O(Q^2) & O(Q^3) \end{pmatrix}
\]
are read off directly from the explicit same-point formula \eqref{eq:Gpm} and
the mixed-block formula \eqref{eq:Nm}, given the baseline local scales of
$q_0, q_0', q_0''$ stated in the proof of
Lemma~\ref{lem:baseline-variation}. Uniform positive-definiteness of
$G_\pm^{(0)}(s)$ on the microscopic disk is
Proposition~\ref{prop:corrected-whitening}.

The whitening map admits the first-order expansion
\[
\widehat\Omega_\zeta^{\corr}-\widehat\Omega_\zeta^{(0)}
=
D\mathcal W_{(0)}[R_-,\widetilde R,R_+]+\mathcal E_2,
\]
where
\[
D\mathcal W_{(0)}[R_-,\widetilde R,R_+]
=
X_-N^{(0)}G_+^{(0)-1/2}
+
G_-^{(0)-1/2}\widetilde R\,G_+^{(0)-1/2}
+
G_-^{(0)-1/2}N^{(0)}X_+.
\]

We estimate the three first-order pieces separately.

\medskip
\noindent
\textbf{Step 1: the mixed-block term.}
By Proposition~\ref{prop:cross-block-perturbation} (entrywise form),
\[
\widetilde R_{11}\ll \frac{S_2}{Q^2},
\qquad
\widetilde R_{12},\widetilde R_{21}\ll \frac{S_2}{Q},
\qquad
\widetilde R_{22}\ll S_2.
\]
Combining with the baseline inverse-square-root scales above, the off-diagonal
entries of
\[
\mathcal T_{\mix}:=G_-^{(0)-1/2}\widetilde R\,G_+^{(0)-1/2}
\]
are all $O(S_2/Q^3)$. Hence
\[
\Phi_K(\mathcal T_{\mix})\ll \frac{S_2}{Q^3}.
\]

\medskip
\noindent
\textbf{Step 2: the same-point Fréchet derivative.}
We prove the corresponding estimate for the left same-point term
\[
\mathcal T_-:=X_-N^{(0)}G_+^{(0)-1/2},
\qquad
X_-:=D(G^{-1/2})_{G_-^{(0)}}[R_-].
\]
The proof for $\mathcal T_+$ is identical.

Write one baseline same-point block in the form
\[
G_0=
\begin{pmatrix}
a & b\\
b & c
\end{pmatrix},
\qquad
a\asymp Q,\quad b=O(1),\quad c\asymp Q^3,
\]
and one perturbation as
\[
R=
\begin{pmatrix}
r_{11} & r_{12}\\
r_{12} & r_{22}
\end{pmatrix},
\qquad
r_{11}\ll \frac{S_2}{Q^2},\quad
r_{12}\ll \frac{S_2}{Q},\quad
r_{22}\ll S_2.
\]

Diagonalize
\[
G_0=U\Lambda U^\top,
\qquad
\Lambda=\operatorname{diag}(\lambda_1,\lambda_2),
\]
with $U$ orthogonal. Since
\[
a\asymp Q,\qquad c\asymp Q^3,\qquad b=O(1),
\]
we have
\[
\lambda_1\asymp Q,\qquad \lambda_2\asymp Q^3.
\]
Moreover, if $U$ is a rotation by angle $\theta$, then
\[
\tan(2\theta)=\frac{2b}{c-a}=O(Q^{-3}),
\]
hence
\[
\theta=O(Q^{-3}),
\qquad
U=I+O(Q^{-3}).
\]

Set
\[
H:=U^\top R\,U.
\]
A direct computation gives
\[
H_{11}=r_{11}+2\theta r_{12}+O(\theta^2 r_{22}),
\]
\[
H_{12}=r_{12}+\theta(r_{22}-r_{11})+O(\theta^2 r_{12}),
\]
\[
H_{22}=r_{22}-2\theta r_{12}+O(\theta^2 r_{11}).
\]
Using
\[
\theta=O(Q^{-3}),
\qquad
r_{11}\ll \frac{S_2}{Q^2},
\qquad
r_{12}\ll \frac{S_2}{Q},
\qquad
r_{22}\ll S_2,
\]
we obtain
\[
H_{11}\ll \frac{S_2}{Q^2},
\qquad
H_{12}\ll \frac{S_2}{Q},
\qquad
H_{22}\ll S_2.
\]

Now let $f(x)=x^{-1/2}$. For a diagonal matrix $\Lambda$, the Fréchet
derivative is given entrywise by the Löwner formula
\[
Df_\Lambda(H)_{ij}=f^{[1]}(\lambda_i,\lambda_j)H_{ij},
\]
where
\[
f^{[1]}(u,v)=
\begin{cases}
\dfrac{u^{-1/2}-v^{-1/2}}{u-v}, & u\neq v,\\[1.2ex]
-\dfrac{1}{2u^{3/2}}, & u=v.
\end{cases}
\]
Since
\[
\lambda_1\asymp Q,\qquad \lambda_2\asymp Q^3,
\]
we have
\[
f^{[1]}(\lambda_1,\lambda_1)\asymp Q^{-3/2},
\qquad
f^{[1]}(\lambda_2,\lambda_2)\asymp Q^{-9/2},
\qquad
f^{[1]}(\lambda_1,\lambda_2)\asymp Q^{-7/2}.
\]
Therefore, if
\[
Y:=Df_\Lambda(H),
\]
then
\[
Y_{11}\ll Q^{-3/2}\cdot \frac{S_2}{Q^2}
=\frac{S_2}{Q^{7/2}},
\]
\[
Y_{12}\ll Q^{-7/2}\cdot \frac{S_2}{Q}
=\frac{S_2}{Q^{9/2}},
\]
\[
Y_{22}\ll Q^{-9/2}\cdot S_2
=\frac{S_2}{Q^{9/2}}.
\]

Since
\[
X=U\,Y\,U^\top
\]
and $U=I+O(Q^{-3})$, these scales persist in the original basis:
\[
X_{11}\ll \frac{S_2}{Q^{7/2}},
\qquad
X_{12},X_{21}\ll \frac{S_2}{Q^{9/2}},
\qquad
X_{22}\ll \frac{S_2}{Q^{9/2}}.
\]

\medskip
\noindent
\textbf{Step 3: the left same-point term $\mathcal T_-$.}
The baseline mixed-block scales are
\[
N^{(0)}=
\begin{pmatrix}
O(Q) & O(Q^2)\\
O(Q^2) & O(Q^3)
\end{pmatrix},
\qquad
G_+^{(0)-1/2}=
\begin{pmatrix}
O(Q^{-1/2}) & O(Q^{-3/2})\\
O(Q^{-3/2}) & O(Q^{-3/2})
\end{pmatrix}.
\]
We estimate only the off-diagonal entries, since
\[
\Phi_K(Y)=Y_{12}+Y_{21}.
\]

For $(\mathcal T_-)_{12}$, every summand is $O(S_2/Q^3)$. For example,
\[
X_{11}N_{12}(G_+^{-1/2})_{22}
\ll
\frac{S_2}{Q^{7/2}}\cdot Q^2\cdot Q^{-3/2}
=
\frac{S_2}{Q^3},
\]
and
\[
X_{12}N_{22}(G_+^{-1/2})_{22}
\ll
\frac{S_2}{Q^{9/2}}\cdot Q^3\cdot Q^{-3/2}
=
\frac{S_2}{Q^3}.
\]
All other terms are smaller. Thus
\[
(\mathcal T_-)_{12}\ll \frac{S_2}{Q^3}.
\]
The same argument gives
\[
(\mathcal T_-)_{21}\ll \frac{S_2}{Q^3},
\]
and hence
\[
\Phi_K(\mathcal T_-)\ll \frac{S_2}{Q^3}.
\]

By symmetry, the same estimate holds for the right same-point term:
\[
\Phi_K(\mathcal T_+)\ll \frac{S_2}{Q^3}.
\]

\medskip
\noindent
\textbf{Step 4: the quadratic remainder.}
Every term in $\mathcal E_2$ contains at least two perturbation factors from
$(R_-,\widetilde R,R_+)$, and whitening contributes only polynomial
$Q$-weights. Therefore
\[
\Phi_K(\mathcal E_2)\ll \frac{S_2^2}{Q^3}.
\]
By Theorem~\ref{thm:tail-curvature}, $S_2=o(Q)$, so this is lower order than
$S_2/Q^3$.

Combining the estimates for $\mathcal T_-$, $\mathcal T_{\mix}$,
$\mathcal T_+$, and $\mathcal E_2$ gives
\[
\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr}(s;m)-\widehat\Omega_\zeta^{(0)}(s;m)\bigr)
\ll
\frac{S_2}{Q^3},
\]
as claimed.
\end{proof}

\begin{corollary}[Sharpened calibration remainder estimate]
\label{cor:sharpened-calibration-remainder}
Fix a compact interval
\[
D\subset(0,\infty),
\]
and work in the fixed-scaled regime
\[
0<x\le x_0(D),\qquad d\in D,\qquad x=B_\zeta(m)\sigma,\qquad |\sigma|\asymp Q^{-1}.
\]
Write the corrected local deformation in the form
\[
\Delta_\zeta(m,\sigma)=S(m)A_{\val}(x)+R_\zeta(m,\sigma).
\]
Then
\[
\bigl|\langle A_{\val}(x),R_\zeta(m,\sigma)\rangle_\F\bigr|
\ll_D
\frac{x}{B_\zeta(m)}\frac{S_2}{Q^3},
\]
and hence
\[
\boxed{
|\Psi_{x,d}(R_\zeta(m,\sigma))|
\ll_D
\frac{S_2}{Q^3}.
}
\]
In particular, if
\[
S_2=o\!\bigl(xQ^2S(m)\bigr),
\]
then
\[
\Psi_{x,d}(R_\zeta(m,\sigma))
=
o\!\left(\frac{x}{B_\zeta(m)}S(m)\right).
\]
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:corrected-local-decomposition}, after subtraction of
the explicit leading value-channel term $S(m)A_{\val}(x)$, the remaining
contribution $R_\zeta(m,\sigma)$ is internal to the same corrected
transferred package controlled by the whitening perturbation analysis.

We therefore use the entry scales already established in the proof of
Proposition~\ref{prop:whitened-mixed-transfer}. First, from
Proposition~\ref{prop:cross-block-perturbation} and the baseline
inverse-square-root scales,
\[
G_\pm^{(0)}(s)^{-1/2}
=
\begin{pmatrix}
O(Q^{-1/2}) & O(Q^{-3/2})\\
O(Q^{-3/2}) & O(Q^{-3/2})
\end{pmatrix},
\qquad
\widetilde R(s)=
\begin{pmatrix}
O(S_2/Q^2) & O(S_2/Q)\\
O(S_2/Q) & O(S_2)
\end{pmatrix},
\]
one gets
\[
\mathcal T_{\mix}(s;m)
=
G_-^{(0)}(s)^{-1/2}\widetilde R(s)G_+^{(0)}(s)^{-1/2}
=
\begin{pmatrix}
O(S_2/Q^3) & O(S_2/Q^3)\\
O(S_2/Q^3) & O(S_2/Q^3)
\end{pmatrix}.
\]

Next, from the same proof,
\[
X_\pm(s)=
\begin{pmatrix}
O(S_2/Q^{7/2}) & O(S_2/Q^{9/2})\\
O(S_2/Q^{9/2}) & O(S_2/Q^{9/2})
\end{pmatrix},
\qquad
N^{(0)}(s)=
\begin{pmatrix}
O(Q) & O(Q^2)\\
O(Q^2) & O(Q^3)
\end{pmatrix},
\]
and multiplying once more by $G_\pm^{(0)}(s)^{-1/2}$ gives
\[
\mathcal T_-(s;m)=
\begin{pmatrix}
O(S_2/Q^3) & O(S_2/Q^3)\\
O(S_2/Q^3) & O(S_2/Q^3)
\end{pmatrix},
\qquad
\mathcal T_+(s;m)=
\begin{pmatrix}
O(S_2/Q^3) & O(S_2/Q^3)\\
O(S_2/Q^3) & O(S_2/Q^3)
\end{pmatrix}.
\]

Finally, every entry of the quadratic remainder $\mathcal E_2(s;m)$ is
\[
O(S_2^2/Q^3),
\]
which is lower order because $S_2=o(Q)$ by
Theorem~\ref{thm:tail-curvature}.

Thus the part of the corrected deformation seen after removal of the leading
value-channel term satisfies
\[
R_\zeta(m,\sigma)
=
\begin{pmatrix}
O(S_2/Q^3) & O(S_2/Q^3)\\
O(S_2/Q^3) & O(S_2/Q^3)
\end{pmatrix}
\]
up to lower-order $O(S_2^2/Q^3)$ terms.

Now use the explicit small-$x$ structure of the value-channel derivative:
by Lemma~\ref{lem:Aval-small-x},
\[
A_{\val}(x)=\frac1{B_\zeta(m)}
\begin{pmatrix}
O(x^2) & O(x)\\
O(x) & O(x^2)
\end{pmatrix}.
\]
Therefore
\[
\bigl|\langle A_{\val}(x),R_\zeta(m,\sigma)\rangle_\F\bigr|
\ll
\frac{x}{B_\zeta(m)}\frac{S_2}{Q^3}.
\]

By Proposition~\ref{prop:pairing},
\[
\bigl|\langle A_{\val}(x),M(d)\rangle_\F\bigr|
\asymp_D
\frac{x}{B_\zeta(m)},
\]
so dividing gives
\[
|\Psi_{x,d}(R_\zeta(m,\sigma))|
\ll_D
\frac{S_2}{Q^3}.
\]

Finally, since $B_\zeta(m)\asymp Q$,
\[
\frac{S_2/Q^3}{(x/B_\zeta(m))S(m)}
\asymp
\frac{S_2}{xQ^2S(m)}\to 0
\]
under the hypothesis $S_2=o(xQ^2S(m))$. This proves the final claim.
\end{proof}

\section{Odd holomorphic transverse channel}

Define the corrected transverse scalar
\begin{equation}\label{eq:Hm-def}
H_m(s):=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr}(s;m)\bigr).
\end{equation}
By symmetry under $s\mapsto -s$, this is odd. By
Corollary~\ref{cor:PhiK-Aval-zero}, the leading value channel is
annihilated by $\Phi_K$, so only the curvature, tail, and corrected
finite-$s$ remainder channels contribute.

\begin{proposition}[Boundary estimate]
\label{prop:boundary-estimate}
On the microscopic boundary
\[
|s|=\rho_0/Q,
\]
one has
\[
|H_m(s)|\ll_{\rho_0}\frac{L(m)S(m)^2}{Q^3}.
\]
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:corrected-local-decomposition}, the corrected local
deformation may be written in the form
\[
\Delta_\zeta(m,\sigma)
=
S(m)\,A_{\val}(m,\sigma)+R_\zeta(m,\sigma),
\]
where $R_\zeta(m,\sigma)$ is internal to the full corrected cutoff-dependent
scalar
\[
H_{m,R}(s):=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)\bigr).
\]
By Proposition~\ref{prop:cutoff-compatibility}, all cutoff-dependent tail,
jet-correction, and estimation contributions are already absorbed into this
full corrected scalar, so no external remainder term is carried separately at
the boundary stage.

Applying $\Phi_K$ to the corrected local decomposition and using
Corollary~\ref{cor:PhiK-Aval-zero},
\[
\Phi_K(A_{\val}(m,\sigma))=0,
\]
gives
\[
H_{m,R}(s)
=
\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)\bigr)
=
\Phi_K\!\bigl(R_\zeta(m,\sigma)\bigr).
\]

Now compare the full corrected whitened block with its baseline counterpart.
By Proposition~\ref{prop:whitened-mixed-transfer},
\[
\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr,R}(s;m)-\widehat\Omega_\zeta^{(0),R}(s;m)\bigr)
\ll
\frac{S_2}{Q^3}
\qquad (|s|<\rho_0/Q).
\]
On the microscopic boundary $|s|=\rho_0/Q$, the tail-curvature theorem and
the corrected transfer bounds imply
\[
S_2\ll L(m)S(m)^2
\]
in the corrected regime. Therefore
\[
|H_{m,R}(s)|
\ll
\frac{L(m)S(m)^2}{Q^3}
\qquad (|s|=\rho_0/Q).
\]

Since the cutoff bookkeeping has already been absorbed into the full corrected
scalar $H_{m,R}(s)$, this is the boundary estimate for the complete corrected
object, not merely for a leading part plus an external tail/error remainder.
This proves the claim.
\end{proof}

\begin{proposition}[Odd microscopic expansion]
\label{prop:odd-expansion}
The function $H_m(s)$ is odd and holomorphic on $|s|<\rho_0/Q$, and therefore
admits an expansion
\[
H_m(z/Q^2)
=
\sum_{r\ge 0} c_{2r+1}(m)\frac{z^{2r+1}}{Q^{2r+4}},
\qquad |z|<\rho_0Q,
\]
with
\[
|c_{2r+1}(m)|\ll_{\rho_0}L(m)S(m)^2\,\rho_0^{-(2r+1)}.
\]
\end{proposition}

\begin{proof}
Oddness follows from symmetric placement and the jet-basis swap symmetry:
\[
\widehat\Omega_\zeta^{\corr}(-s;m)=J_0\,\widehat\Omega_\zeta^{\corr}(s;m)\,J_0,
\]
with
\[
\Phi_K(J_0XJ_0)=-\Phi_K(X).
\]
Holomorphy follows from Proposition~\ref{prop:corrected-whitening}, and the
coefficient bounds are immediate from Cauchy's estimate applied to
Proposition~\ref{prop:boundary-estimate}.
\end{proof}

\subsection{Coefficient-level corrected-whitening transfer and exterior odd-jet localization}
\label{subsec:differentiated-transfer}

\begin{lemma}[Baseline-scaled matrix gain for corrected whitening]
\label{lem:baseline-scaled-matrix-gain}
Let
\[
\mathcal W(G_-,N,G_+):=G_-^{-1/2}NG_+^{-1/2}.
\]
Assume the baseline same-point and mixed blocks satisfy
\[
G_\pm^{(0)}(s)=
\begin{pmatrix}
O(Q) & O(1)\\
O(1) & O(Q^3)
\end{pmatrix},
\qquad
N^{(0)}(s)=
\begin{pmatrix}
O(Q) & O(Q^2)\\
O(Q^2) & O(Q^3)
\end{pmatrix},
\]
uniformly on $|s|<\rho_0/Q$, and that $G_\pm^{(0)}(s)$ remain uniformly
positive definite there.

Set
\[
S_Q:=\begin{pmatrix}Q^{-1/2}&0\\0&Q^{-3/2}\end{pmatrix},
\qquad
\widehat G_\pm:=S_Q^{-1}G_\pm S_Q^{-1},
\qquad
\widehat N:=S_Q^{-1}NS_Q^{-1}.
\]
Then
\[
\widehat G_\pm^{(0)}(s)=
\begin{pmatrix}
O(1)&O(Q^{-1})\\
O(Q^{-1})&O(1)
\end{pmatrix},
\qquad
\widehat N^{(0)}(s)=
\begin{pmatrix}
O(1)&O(1)\\
O(1)&O(1)
\end{pmatrix},
\]
and
\[
\mathcal W(G_-,N,G_+)
=
S_Q\,
\mathcal W(\widehat G_-,\widehat N,\widehat G_+)\,
S_Q.
\]

In particular, every off-diagonal entry of $\mathcal W(G_-,N,G_+)$ carries an
explicit matrix-level factor $Q^{-2}$ relative to the corresponding rescaled
whitened block. Any additional $Q$-power appearing in the corrected transverse
scalar must therefore come from the scalar normalization used in the definition
of that scalar, not from the matrix identity itself.
\end{lemma}

\begin{proof}
The displayed bounds for $\widehat G_\pm^{(0)}$ and $\widehat N^{(0)}$ are
immediate from the definitions and the baseline scales. Since
\[
G_\pm=S_Q\,\widehat G_\pm\,S_Q,
\]
functional calculus gives
\[
G_\pm^{-1/2}=S_Q^{-1}\,\widehat G_\pm^{-1/2}\,S_Q^{-1}.
\]
Hence
\[
\mathcal W(G_-,N,G_+)
=
G_-^{-1/2}NG_+^{-1/2}
=
S_Q\,
\widehat G_-^{-1/2}\widehat N\,\widehat G_+^{-1/2}\,
S_Q
=
S_Q\,\mathcal W(\widehat G_-,\widehat N,\widehat G_+)\,S_Q.
\]
The off-diagonal entries therefore acquire one factor $Q^{-1/2}$ from the
upper-left entry of $S_Q$ and one factor $Q^{-3/2}$ from the lower-right
entry of $S_Q$, hence a total matrix-level factor $Q^{-2}$.
\end{proof}

\begin{proposition}[Uniform scaled corrected-whitening transfer]
\label{prop:differentiated-whitening-transfer}
Fix $0<c_*<\rho_0/8$. For every $Q$ and every radius $R$ satisfying
\[
0<R\le c_*Q,
\]
set
\[
w:=\frac{z}{R},
\qquad
s=\frac{z}{Q^2}=\frac{Rw}{Q^2}.
\]
Let
\[
\mathfrak D_Q(M):=
\begin{pmatrix}
Q^2 m_{11} & Q m_{12}\\
Q m_{21} & m_{22}
\end{pmatrix},
\qquad
\mathfrak D_Q^{-1}(X)=
\begin{pmatrix}
Q^{-2}x_{11} & Q^{-1}x_{12}\\
Q^{-1}x_{21} & x_{22}
\end{pmatrix}.
\]
For $R'>0$, let
\[
A_{R'}(M_2):=
\left\{
F(z)=\sum_{n\ge 0}F_n z^n:
\|F\|_{A_{R'}}:=\sum_{n\ge 0}\|F_n\|\,R'^n<\infty
\right\},
\]
and write $A_1(M_2)$ for the case $R'=1$. For scalar holomorphic germs,
$A_{R'}(\mathbb C)$ is defined similarly.

Write the baseline corrected same-point and mixed blocks on the $w$-disk as
\[
G^{(0)}_{\pm;Q,R}(w):=G_\pm^{(0)}(Rw/Q^2),
\qquad
N^{(0)}_{Q,R}(w):=N^{(0)}(Rw/Q^2).
\]
For a weighted perturbation triple
\[
X=(X_-,Y,X_+)\in A_1(M_2)^3,
\]
define
\[
\delta G_\pm:=\mathfrak D_Q^{-1}X_\pm,
\qquad
\delta N:=\mathfrak D_Q^{-1}Y,
\]
and, whenever the corrected scalar perturbation
\[
\Phi_K\!\left(
\mathcal W\bigl(
G^{(0)}_{-;Q,R}+\delta G_-,
N^{(0)}_{Q,R}+\delta N,
G^{(0)}_{+;Q,R}+\delta G_+
\bigr)
-
\mathcal W\bigl(
G^{(0)}_{-;Q,R},
N^{(0)}_{Q,R},
G^{(0)}_{+;Q,R}
\bigr)
\right)
\]
vanishes at $w=0$, define
\[
\mathcal T_{Q,R}(X)(w)
:=
\frac{Q}{Rw}\,
\Phi_K\!\left(
\mathcal W\bigl(
G^{(0)}_{-;Q,R}+\delta G_-,
N^{(0)}_{Q,R}+\delta N,
G^{(0)}_{+;Q,R}+\delta G_+
\bigr)
-
\mathcal W\bigl(
G^{(0)}_{-;Q,R},
N^{(0)}_{Q,R},
G^{(0)}_{+;Q,R}
\bigr)
\right).
\]

Then there exist absolute constants
\[
\eta>0,\qquad C>0,\qquad B>0
\]
such that for every $Q$, every $0<R\le c_*Q$, and every
\[
X\in A_1(M_2)^3
\qquad\text{with}\qquad
\|X_-\|_{A_1}+\|Y\|_{A_1}+\|X_+\|_{A_1}\le \eta,
\]
the quotient $\mathcal T_{Q,R}(X)$ is holomorphic on $|w|<1$ and admits an
absolutely convergent homogeneous expansion
\[
\mathcal T_{Q,R}(X)=\sum_{p\ge 1}\mathcal T_p(X),
\]
with
\[
\|\mathcal T_p(X)\|_{A_1}
\le
C B^p
\bigl(\|X_-\|_{A_1}+\|Y\|_{A_1}+\|X_+\|_{A_1}\bigr)^p.
\]
The constants $C,B,\eta$ are independent of $Q$ and $R$.

Moreover, if
\[
X_\pm(w)=\sum_{m\ge 0}X_{\pm,m}w^m,
\qquad
Y(w)=\sum_{m\ge 0}Y_m w^m,
\]
and
\[
\mathcal T_p(X)(w)=\sum_{n\ge 0} T_{p,n}w^n,
\]
then with
\[
\mathbf X_m:=\max\!\bigl(\|X_{-,m}\|,\|Y_m\|,\|X_{+,m}\|\bigr),
\]
one has the coefficient bound
\[
\boxed{
|T_{p,n}|
\le
C B^p
\sum_{M\le n}
\sum_{\substack{m_1+\cdots+m_p=M\\ m_i\ge 0}}
\prod_{i=1}^p \mathbf X_{m_i}.
}
\]
\end{proposition}

\begin{proof}
On $|w|\le 2$,
\[
\left|\frac{Rw}{Q^2}\right|
\le \frac{2R}{Q^2}
\le \frac{2c_*}{Q}
<\frac{\rho_0}{Q},
\]
so the baseline blocks
\[
G^{(0)}_{\pm;Q,R}(w),\qquad N^{(0)}_{Q,R}(w)
\]
are holomorphic and uniformly bounded on $|w|\le 2$, with bounds
independent of $Q$ and $R$. By
Lemma~\ref{lem:baseline-scaled-matrix-gain}, the same-point baseline blocks
remain uniformly positive definite there.

Therefore the corrected-whitening map
\[
(\delta G_-,\delta N,\delta G_+)
\longmapsto
\mathcal W\bigl(
G^{(0)}_{-;Q,R}+\delta G_-,
N^{(0)}_{Q,R}+\delta N,
G^{(0)}_{+;Q,R}+\delta G_+
\bigr)
\]
is analytic on a fixed Banach neighborhood in $A_1(M_2)^3$, uniformly in
$Q,R$. Since $\Phi_K$ is linear, the corrected scalar perturbation depends
analytically on the input triple. For those structured perturbations for which
the corrected scalar perturbation vanishes at $w=0$, the quotient by $w$ in
the definition of $\mathcal T_{Q,R}$ is holomorphic. This gives the
homogeneous expansion with uniform constants $C,B,\eta$.

The coefficient bound follows by testing the homogeneous maps on monomials in
$A_1(M_2)$ and using the Wiener-algebra estimate
\[
|[w^n]F|\le \|F\|_{A_1}
\]
for scalar coefficients.
\end{proof}

\begin{proposition}[Pair-radius kernel-class decomposition for one-pair perturbations]
\label{prop:one-pair-symbolic-coefficient-decomposition}
Fix $0<c_*<\rho_0/8$ and $0<c\ll 1$. For one exterior zero pair $\rho$,
set
\[
\Delta_\rho:=|2m-\gamma_\rho|,
\qquad
R_\rho:=c\,\min(\Delta_\rho,c_*Q).
\]

Let $f_\rho(t)$ denote the one-pair phase-derivative contribution, and remove
its midpoint affine jet:
\[
r_\rho(t):=f_\rho(t)-f_\rho(m)-f_\rho'(m)(t-m).
\]
With
\[
t_\pm:=m\pm \frac{z}{2Q^2},
\]
define
\[
d_\pm(z):=r_\rho(t_\pm),
\qquad
e_\pm(z):=r_\rho'(t_\pm),
\qquad
g_\pm(z):=r_\rho''(t_\pm),
\]
and
\[
\eta(z):=\delta\Delta_\rho(z/Q^2):=\int_{t_+}^{t_-} r_\rho(u)\,du.
\]
Then there exist holomorphic kernels $U_\pm,E_\pm,G_\pm,V$ such that
\[
d_\pm(z)=\frac{z^2}{Q^4}U_\pm(z),
\qquad
e_\pm(z)=\frac{z}{Q^2}E_\pm(z),
\qquad
g_\pm(z)=G_\pm(z),
\qquad
\eta(z)=\frac{z^3}{Q^6}V(z).
\]

For every fixed $H_*>1$, if $\Delta_\rho\ge H_*$, then
\[
U_\pm,\ E_\pm,\ G_\pm,\ V
\]
are holomorphic on $|z|<2R_\rho$ and satisfy
\[
\|U_\pm\|_{A_{R_\rho}}+
\|E_\pm\|_{A_{R_\rho}}+
\|G_\pm\|_{A_{R_\rho}}+
\|V\|_{A_{R_\rho}}
\ll
\Delta_\rho^{-4}.
\]

Let
\[
X_\rho:=(X_{\rho,-},Y_\rho,X_{\rho,+})
\]
be the weighted one-pair perturbation triple
\[
X_{\rho,\pm}:=\mathfrak D_Q(\delta G_{\rho,\pm}),
\qquad
Y_\rho:=\mathfrak D_Q(\delta N_\rho),
\]
where $\delta G_{\rho,\pm}$ and $\delta N_\rho$ are the actual one-pair
perturbations of the corrected same-point and mixed blocks in the draft.

Then, on $|z|<2R_\rho$, every entry of every block of $X_\rho(z)$ is
linear in
\[
U_-,\ U_+,\ E_-,\ E_+,\ G_-,\ G_+,\ V
\]
modulo terms containing at least two such pair kernels. In particular,
\[
\|X_\rho(R_\rho\cdot)\|_{A_1}\ll \Delta_\rho^{-4}.
\]
\end{proposition}

\begin{proof}
The one-pair poles lie at distance $\asymp \Delta_\rho$ in the $s$-plane,
hence at distance $\asymp Q^2\Delta_\rho$ in the $z$-plane. Since
\[
R_\rho\ll \min(\Delta_\rho,Q),
\]
the kernels $U_\pm,E_\pm,G_\pm,V$ are holomorphic on $|z|<2R_\rho$, and
Cauchy gives the displayed $A_{R_\rho}$-bounds.

Now check the actual corrected formulas.

For the corrected same-point block,
\[
G_{m,\pm}^{\corr}(s)=\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[1ex]
\frac12 q'(t_\pm) & \frac1{12}\bigl(q''(t_\pm)+2q(t_\pm)^3\bigr)
\end{pmatrix}.
\]
Subtracting the baseline and using
\[
q=q_0+d_\pm,\qquad q'=q_0'+e_\pm,\qquad q''=q_0''+g_\pm,
\]
the weighted perturbation entries are:
\[
(1,1)\sim (z/Q)^2U_\pm,
\qquad
(1,2),(2,1)\sim (z/Q)E_\pm,
\]
and
\[
(2,2)\sim
G_\pm
+
\Bigl(\frac{q_0}{Q}\Bigr)^2 (z/Q)^2U_\pm
+
\Bigl(\frac{q_0}{Q}\Bigr)(z/Q)^4U_\pm^2
+
(z/Q)^6U_\pm^3.
\]
On $|z|\le 2R_\rho$, the normalized baseline factors
\[
\frac{q_0 z}{Q^2},\qquad \frac{q_0^2 z^2}{Q^4}
\]
are $O(1)$, so the same-point block is linear in the pair kernels modulo
terms with at least two pair kernels.

For the corrected mixed block,
\[
N_m^{\corr}(s)=\frac1\pi
\begin{pmatrix}
-\dfrac{2\sin\Delta}{s}
&
\dfrac{\sin\Delta+q(t_+)s\cos\Delta}{s^2}
\\[2ex]
-\dfrac{\sin\Delta+q(t_-)s\cos\Delta}{s^2}
&
\dfrac{(q(t_-)+q(t_+))s\cos\Delta+(2-q(t_-)q(t_+)s^2)\sin\Delta}{2s^3}
\end{pmatrix}.
\]
Write
\[
q_\pm=q_{0,\pm}+d_\pm,
\qquad
\Delta=\Delta_0+\eta.
\]

For the $(1,1)$-entry, since
\[
\eta(z)=\frac{z^3}{Q^6}V(z)=s^3V(z),
\]
\[
Q^2\frac{\sin(\Delta_0+\eta)-\sin\Delta_0}{s}
\]
is linear in $V$ modulo higher pair order.

For the off-diagonal entries, the numerator difference is
\[
(\sin(\Delta_0+\eta)-\sin\Delta_0)
+d_\pm s\cos(\Delta_0+\eta)
+q_{0,\pm}s(\cos(\Delta_0+\eta)-\cos\Delta_0),
\]
and after multiplying by $Q/s^2$ the linear terms are bounded-baseline times
$U_\pm$ and $V$.

For the $(2,2)$-entry, define
\[
F(q_-,q_+,\Delta;s):=(q_-+q_+)s\cos\Delta+(2-q_-q_+s^2)\sin\Delta.
\]
Then the perturbation is
\[
\frac{
F(q_{0,-}+d_-,q_{0,+}+d_+,\Delta_0+\eta;s)
-
F(q_{0,-},q_{0,+},\Delta_0;s)
}{s^3}.
\]
Taylor expansion in $(d_-,d_+,\eta)$ around the baseline gives
\[
\partial_{q_-}F_0\,d_-+\partial_{q_+}F_0\,d_++\partial_\Delta F_0\,\eta
\]
plus a remainder quadratic in $(d_-,d_+,\eta)$. After dividing by $s^3$,
the linear part is
\[
\widetilde B_-(z)\,U_-(z)+\widetilde B_+(z)\,U_+(z)+\widetilde B_\Delta(z)\,V(z),
\]
with bounded baseline coefficients $\widetilde B_-,\widetilde B_+,\widetilde
B_\Delta$, and the remainder carries at least two pair kernels.

So every weighted mixed-block entry is also linear in the pair kernels modulo
higher pair order.

Finally, on $|z|\le 2R_\rho$, every factor $z/Q$ is $O(1)$, every
normalized baseline factor is $O(1)$, and each pair kernel has $A_{R_\rho}$
norm $O(\Delta_\rho^{-4})$. Therefore
\[
\|X_\rho(R_\rho\cdot)\|_{A_1}\ll \Delta_\rho^{-4}.
\]
\end{proof}

\begin{corollary}[Single-pair exterior odd-coefficient bound]
\label{cor:single-pair-odd-jet}
Fix $0<c_*<\rho_0/8$. Let $h_\rho(s)$ be the corrected transverse scalar
contributed by one exterior zero pair at absolute distance
\[
\Delta_\rho:=|2m-\gamma_\rho|,
\]
and write
\[
h_\rho(z/Q^2)
=
\sum_{r\ge 0} a_{2r+1}(\rho)\,\frac{z^{2r+1}}{Q^{2r+4}}.
\]
Then for every fixed $H_*>1$, if $\Delta_\rho\ge H_*$, one has
\[
\boxed{
|a_{2r+1}(\rho)|
\ll
\frac{1}{Q}
\begin{cases}
\Delta_\rho^{-(2r+4)}, & \Delta_\rho\le c_*Q,\\[1ex]
(c_*Q)^{-2r}\Delta_\rho^{-4}, & \Delta_\rho>c_*Q.
\end{cases}
}
\]
\end{corollary}

\begin{proof}
Let
\[
R_\rho:=c\,\min(\Delta_\rho,c_*Q).
\]
By Proposition~\ref{prop:one-pair-symbolic-coefficient-decomposition},
\[
\|X_\rho(R_\rho\cdot)\|_{A_1}\ll \Delta_\rho^{-4}.
\]
For $H_*$ large enough, this lies inside the uniform small ball from
Proposition~\ref{prop:differentiated-whitening-transfer}. Since the one-pair
corrected scalar $h_\rho(s)$ is odd in $s$, the corresponding corrected
scalar perturbation vanishes at $w=0$, so the quotient map
$\mathcal T_{Q,R_\rho}$ is holomorphic on the one-pair input. Therefore the
normalized even germ
\[
g_\rho(z):=\frac{Q^3}{z}\,h_\rho(z/Q^2)
\]
satisfies
\[
\|g_\rho(R_\rho\cdot)\|_{A_1}\ll \Delta_\rho^{-4}.
\]
Hence
\[
[z^{2r}]\,g_\rho(z)\ll R_\rho^{-2r}\Delta_\rho^{-4}.
\]
Since
\[
g_\rho(z)=\sum_{r\ge 0}\frac{a_{2r+1}(\rho)}{Q^{2r+1}}\,z^{2r},
\]
this gives
\[
|a_{2r+1}(\rho)|\ll Q^{2r+1}R_\rho^{-2r}\Delta_\rho^{-4}.
\]
Using
\[
R_\rho\asymp \min(\Delta_\rho,c_*Q)
\]
yields the displayed hybrid bound.
\end{proof}

\begin{lemma}[Local zero-counting in dyadic shells]
\label{lem:dyadic-shell-count}
Let
\[
\mathcal S_k:=\{\rho:\ 2^kH<\Delta_\rho\le 2^{k+1}H\},
\qquad
\Delta_\rho:=|2m-\gamma_\rho|,
\qquad
k\ge 0.
\]
Then
\[
\#\mathcal S_k\ll Q\,(2^kH+1),
\]
where $Q\asymp \log|m|$.
\end{lemma}

\begin{proof}
This is the local zero-counting estimate already used elsewhere in the draft,
applied to the interval of ordinates
\[
[\,2m-2^{k+1}H,\;2m+2^{k+1}H\,].
\]
Its length is $O(2^kH+1)$, and the local zero density at height $m$ is
$O(Q)$.
\end{proof}

\begin{corollary}[Exterior higher odd-coefficient bound]
\label{cor:outside-higher-odd-jets}
Let
\[
H_{\out}(z/Q^2)
=
\sum_{r\ge 0} a_{2r+1}^{\out}(m,H)\,\frac{z^{2r+1}}{Q^{2r+4}}
\]
be the corrected transverse scalar contributed by all zeros outside absolute
radius $H$ from the local center. Then for every $r\ge 0$ and every
$H\ge H_*$,
\[
\boxed{
|a_{2r+1}^{\out}(m,H)|
\ll
H^{-(2r+3)}+Q^{-(2r+2)}.
}
\]
\end{corollary}

\begin{proof}
Decompose the exterior zeros into dyadic shells
\[
\mathcal S_k:=\{\rho:\ 2^kH<\Delta_\rho\le 2^{k+1}H\},
\qquad k\ge 0.
\]
By Lemma~\ref{lem:dyadic-shell-count},
\[
\#\mathcal S_k\ll Q(2^kH+1).
\]

For shells with $2^{k+1}H\le c_*Q$, Corollary~\ref{cor:single-pair-odd-jet}
gives
\[
\sum_{\rho\in\mathcal S_k}|a_{2r+1}(\rho)|
\ll
Q(2^kH+1)\cdot \frac{1}{Q(2^kH)^{2r+4}}
\ll
(2^kH)^{-(2r+3)}.
\]
Summing these shells yields
\[
\ll H^{-(2r+3)}.
\]

For shells with $2^kH>c_*Q$, Corollary~\ref{cor:single-pair-odd-jet} gives
\[
\sum_{\rho\in\mathcal S_k}|a_{2r+1}(\rho)|
\ll
Q(2^kH+1)\cdot \frac{1}{Q(c_*Q)^{2r}(2^kH)^4}
\ll
(c_*Q)^{-2r}(2^kH)^{-3}.
\]
Summing the far shells gives
\[
\ll
Q^{-2r-2}.
\]
Adding the near and far ranges proves the claim.
\end{proof}

\begin{corollary}[Core localization of the extracted odd jet]
\label{cor:extracted-odd-jet-core-localization}
Let $N=\lfloor \alpha Q\rfloor$ with $\alpha>0$, and let
$a_{2N-1}^{\le H}(m)$ denote the coefficient contributed by the zeros with
$\Delta_\rho\le H$. Then for every fixed $H\ge H_*$,
\[
\boxed{
a_{2N-1}(m)
=
a_{2N-1}^{\le H}(m)
+
O\!\bigl(H^{-(2N+1)}+Q^{-2N}\bigr).
}
\]
In particular, the first surviving corrected odd coefficient is exponentially
localized to any fixed finite core.
\end{corollary}

\begin{proof}
This is exactly Corollary~\ref{cor:outside-higher-odd-jets} with $r=N-1$.
\end{proof}

\section{\texorpdfstring{$N$}{N}-point odd-moment cancellation}

For $N\le \rho_0Q$, set
\[
s_j=\frac{j}{Q^2},
\qquad j=1,\dots,N,
\]
and define
\[
a_j^{(N)}
:=
(-1)^{j+1}\,
\frac{j\binom{2N}{N+j}}{\binom{2N-2}{N-1}},
\qquad 1\le j\le N.
\]
Define the corrected $N$-point transverse scalar
\begin{equation}\label{eq:Xi-zeta}
\Xi_\zeta^{(N)}(m):=
\sum_{j=1}^N a_j^{(N)}H_m(s_j).
\end{equation}

\begin{lemma}[Explicit odd-moment-canceling coefficients and $\ell^1$ control]
\label{lem:n-point-coefficients}
The coefficients $a_j^{(N)}$ satisfy
\[
\sum_{j=1}^N a_j^{(N)}=1,
\qquad
\sum_{j=1}^N a_j^{(N)}j^{2r+1}=0
\quad (0\le r\le N-2).
\]
Moreover,
\[
\sum_{j=1}^N |a_j^{(N)}|=2N-1.
\]
Consequently, for every integer $k\ge 0$,
\[
\left|\sum_{j=1}^N a_j^{(N)}j^k\right|
\le
(2N-1)N^k.
\]
\end{lemma}

\begin{proof}
Set
\[
D_N:=\binom{2N-2}{N-1}.
\]

We first prove the normalization. Writing
\[
j\binom{2N}{N+j}
=
N\!\left(\binom{2N-1}{N+j-1}-\binom{2N-1}{N+j}\right),
\]
one gets
\[
\sum_{j=1}^N (-1)^{j+1}j\binom{2N}{N+j}
=
N\sum_{j=1}^N (-1)^{j+1}
\left(\binom{2N-1}{N+j-1}-\binom{2N-1}{N+j}\right).
\]
Using the partial alternating-binomial identity
\[
\sum_{k=0}^{m}(-1)^k\binom{n}{k}
=
(-1)^m\binom{n-1}{m},
\]
one finds
\[
\sum_{k=N}^{2N-1}(-1)^k\binom{2N-1}{k}
=
(-1)^N\binom{2N-2}{N-1}.
\]
Substituting this into the preceding display yields
\[
\sum_{j=1}^N (-1)^{j+1}j\binom{2N}{N+j}
=
\binom{2N-2}{N-1}
=
D_N,
\]
hence
\[
\sum_{j=1}^N a_j^{(N)}=1.
\]

Next, for $0\le r\le N-2$, apply the standard finite-difference identity
\[
\sum_{k=0}^{2N}(-1)^k\binom{2N}{k}P(k)=0
\]
to the polynomial
\[
P(k)=(k-N)^{2r+2},
\qquad
\deg P=2r+2<2N.
\]
After the change of variables $j=k-N$, this gives
\[
\sum_{j=-N}^{N}(-1)^j\binom{2N}{N+j}j^{2r+2}=0.
\]
Since $2r+2$ is even and the $j=0$ term vanishes,
\[
\sum_{j=1}^{N}(-1)^j\binom{2N}{N+j}j^{2r+2}=0.
\]
Dividing by $D_N$ yields
\[
\sum_{j=1}^N a_j^{(N)}j^{2r+1}=0
\qquad (0\le r\le N-2).
\]

Finally, since the signs alternate,
\[
\sum_{j=1}^N |a_j^{(N)}|
=
\frac{1}{D_N}\sum_{j=1}^N j\binom{2N}{N+j}.
\]
Using again
\[
j\binom{2N}{N+j}
=
N\!\left(\binom{2N-1}{N+j-1}-\binom{2N-1}{N+j}\right),
\]
this telescopes to
\[
\sum_{j=1}^N j\binom{2N}{N+j}
=
N\binom{2N-1}{N}.
\]
Therefore
\[
\sum_{j=1}^N |a_j^{(N)}|
=
N\frac{\binom{2N-1}{N}}{\binom{2N-2}{N-1}}
=
2N-1.
\]
The final moment bound is immediate from
\[
\left|\sum_{j=1}^N a_j^{(N)}j^k\right|
\le
\sum_{j=1}^N |a_j^{(N)}|\,j^k
\le
(2N-1)N^k.
\qedhere
\]
\end{proof}

\begin{lemma}[Closed-form Mellin symbol of the discrete $N$-point projector]
\label{lem:n-point-mellin-symbol}
Define
\[
A_N(t):=\sum_{j=1}^N a_j^{(N)}\,t^j,
\qquad
\widehat\mu_{N,Q}(z):=A_N(e^{z/Q^2}).
\]
Then
\[
A_N(t)
=
\frac{2(2N-1)}{N+1}\,
t\,{}_2F_1(1-N,\,2;\,N+2;\,t),
\]
so in particular
\[
\widehat\mu_{N,Q}(z)
=
\frac{2(2N-1)}{N+1}\,
e^{z/Q^2}\,
{}_2F_1(1-N,\,2;\,N+2;\,e^{z/Q^2}).
\]
Moreover,
\[
A_N(t)-A_N(t^{-1})
=
\frac{N(-1)^N}{\binom{2N-2}{N-1}}\,
t^{-N}(1-t)^{2N-1}(1+t),
\]
and hence
\[
\widehat\mu_{N,Q}(z)-\widehat\mu_{N,Q}(-z)
=
\frac{N(-1)^N}{\binom{2N-2}{N-1}}\,
e^{-Nz/Q^2}\,
\bigl(1-e^{z/Q^2}\bigr)^{2N-1}
\bigl(1+e^{z/Q^2}\bigr).
\]
In particular,
\[
\widehat\mu_{N,Q}(0)=1,
\qquad
\partial_z^{\,2r+1}\widehat\mu_{N,Q}(0)=0
\quad (0\le r\le N-2),
\]
and the odd part of $\widehat\mu_{N,Q}$ starts only at order $2N-1$.
\end{lemma}

\begin{proof}
Let
\[
B_N(t):=
\frac{2(2N-1)}{N+1}\,
t\,{}_2F_1(1-N,\,2;\,N+2;\,t)
=
\sum_{j=1}^N b_j^{(N)}\,t^j.
\]
Its coefficients satisfy
\[
\frac{b_{j+1}^{(N)}}{b_j^{(N)}}
=
\frac{(1-N+j-1)(2+j-1)}{(N+2+j-1)j}
=
\frac{(j-N)(j+1)}{j(N+j+1)}.
\]
On the other hand, the coefficients $a_j^{(N)}$ satisfy
\[
\frac{a_{j+1}^{(N)}}{a_j^{(N)}}
=
\frac{(-1)^{j+2}(j+1)\binom{2N}{N+j+1}}
     {(-1)^{j+1}j\binom{2N}{N+j}}
=
\frac{(j-N)(j+1)}{j(N+j+1)}.
\]
Thus $a_j^{(N)}$ and $b_j^{(N)}$ agree up to an overall constant.  Matching
the $t^1$-coefficient gives
\[
b_1^{(N)}
=
\frac{2(2N-1)}{N+1}
=
\frac{\binom{2N}{N+1}}{\binom{2N-2}{N-1}}
=
a_1^{(N)},
\]
hence $A_N(t)=B_N(t)$.

For the second identity, define
\[
F_N(t):=\sum_{j=-N}^{N}(-1)^j\binom{2N}{N+j}t^j.
\]
By the binomial theorem,
\[
F_N(t)=(-1)^N t^{-N}(1-t)^{2N}.
\]
Differentiating gives
\[
tF_N'(t)
=
\sum_{j=-N}^{N}j(-1)^j\binom{2N}{N+j}t^j
=
-N(-1)^N t^{-N}(1-t)^{2N-1}(1+t).
\]
Now
\[
A_N(t)-A_N(t^{-1})
=
-\frac{1}{\binom{2N-2}{N-1}}
\sum_{j=1}^N j(-1)^j\binom{2N}{N+j}(t^j-t^{-j}),
\]
while the symmetry $j\mapsto -j$ in the preceding display shows
\[
tF_N'(t)
=
\sum_{j=1}^N j(-1)^j\binom{2N}{N+j}(t^j-t^{-j}).
\]
Substituting the closed form for $tF_N'(t)$ yields
\[
A_N(t)-A_N(t^{-1})
=
\frac{N(-1)^N}{\binom{2N-2}{N-1}}\,
t^{-N}(1-t)^{2N-1}(1+t).
\]
Replacing $t$ by $e^{z/Q^2}$ gives the displayed formula for
$\widehat\mu_{N,Q}(z)-\widehat\mu_{N,Q}(-z)$.  The normalization
$\widehat\mu_{N,Q}(0)=1$ and the low odd-jet vanishing are equivalent to the
moment identities in Lemma~\ref{lem:n-point-coefficients}.
\end{proof}

\begin{lemma}[Exact odd-moment generating function]
\label{lem:n-point-odd-generating-function}
Define
\[
\mu_k^{(N)}:=\sum_{j=1}^N a_j^{(N)}j^k,
\]
and, for $|u|<1/N$,
\[
\mathcal M_N(u)
:=
\sum_{r\ge 0}\mu_{2r+1}^{(N)}u^{2r+1}
=
\sum_{j=1}^N \frac{a_j^{(N)}\,j\,u}{1-j^2u^2}.
\]
Then
\[
\mathcal M_N(u)
=
(-1)^{N+1}(2N-1)N!(N-1)!
\frac{u^{2N-1}}{\prod_{j=1}^N(1-j^2u^2)}.
\]
In particular, for every real $x>N$,
\[
\sum_{r\ge N-1} |\mu_{2r+1}^{(N)}|\,x^{-(2r+1)}
=
(2N-1)N!(N-1)!\,x^2\,
\frac{\Gamma(x-N)}{\Gamma(x+N+1)}.
\]
\end{lemma}

\begin{proof}
The identity
\[
\mathcal M_N(u)
=
\sum_{j=1}^N \frac{a_j^{(N)}\,j\,u}{1-j^2u^2}
\]
is immediate from summing the geometric series
\[
\frac{j\,u}{1-j^2u^2}
=
\sum_{r\ge 0} j^{2r+1}u^{2r+1}
\qquad (|u|<1/j).
\]

Set
\[
D_N(u):=
\prod_{j=1}^N(1-j^2u^2)\,\mathcal M_N(u).
\]
Since $\mathcal M_N$ is a sum of simple fractions, $D_N(u)$ is an odd
polynomial of degree at most $2N-1$. By
Lemma~\ref{lem:n-point-coefficients},
\[
\mu_{2r+1}^{(N)}=0
\qquad (0\le r\le N-2),
\]
so $\mathcal M_N(u)=O(u^{2N-1})$ as $u\to 0$. Hence
\[
D_N(u)=C_N\,u^{2N-1}
\]
for some constant $C_N$.

To determine $C_N$, compare residues at $u=1/N$. The residue of
$\mathcal M_N(u)$ there comes only from the $j=N$ term and equals
\[
\operatorname*{Res}_{u=1/N}\mathcal M_N(u)
=
-\frac{a_N^{(N)}}{2N}.
\]
On the other hand,
\[
\operatorname*{Res}_{u=1/N}
\frac{C_Nu^{2N-1}}{\prod_{j=1}^N(1-j^2u^2)}
=
-\frac{C_N}{2N^2\prod_{k=1}^{N-1}(1-k^2/N^2)}.
\]
Equating these residues gives
\[
C_N
=
a_N^{(N)}\,N\prod_{k=1}^{N-1}(N^2-k^2).
\]
Now
\[
a_N^{(N)}
=
(-1)^{N+1}\frac{N}{\binom{2N-2}{N-1}},
\]
and
\[
\prod_{k=1}^{N-1}(N^2-k^2)
=
\prod_{k=1}^{N-1}(N-k)\prod_{k=1}^{N-1}(N+k)
=
(N-1)!\,\frac{(2N-1)!}{N!}
=
\frac{(2N-1)!}{N}.
\]
Therefore
\[
C_N
=
(-1)^{N+1}\frac{N(2N-1)!}{\binom{2N-2}{N-1}}
=
(-1)^{N+1}(2N-1)N!(N-1)!.
\]
This proves the first formula.

For the tail identity, note that
\[
(-1)^{N+1}\mathcal M_N(u)
=
(2N-1)N!(N-1)!
\frac{u^{2N-1}}{\prod_{j=1}^N(1-j^2u^2)}
\]
has nonnegative Taylor coefficients for $0<u<1/N$. Hence
\[
(-1)^{N+1}\mu_{2r+1}^{(N)}\ge 0
\qquad (r\ge N-1),
\]
and therefore, for $x>N$,
\[
\sum_{r\ge N-1} |\mu_{2r+1}^{(N)}|\,x^{-(2r+1)}
=
\left|\mathcal M_N\!\left(\frac1x\right)\right|
=
(2N-1)N!(N-1)!\,
\frac{x^2}{\prod_{j=1}^N(x^2-j^2)}.
\]
Finally,
\[
\prod_{j=1}^N(x^2-j^2)
=
\prod_{j=1}^N(x-j)\prod_{j=1}^N(x+j)
=
\frac{\Gamma(x)}{\Gamma(x-N)}\cdot
\frac{\Gamma(x+N+1)}{\Gamma(x+1)}
=
\frac{1}{x}\frac{\Gamma(x+N+1)}{\Gamma(x-N)}.
\]
Substituting this identity yields the claimed formula.
\end{proof}

\begin{remark}[Structure of the surviving odd tail]
\label{rem:surviving-odd-tail-structure}
Expanding
\[
\frac{1}{\prod_{j=1}^N(1-j^2u^2)}
=
\sum_{k\ge 0} h_k(1^2,\dots,N^2)\,u^{2k},
\]
where $h_k$ denotes the complete homogeneous symmetric polynomial, the exact
formula of Lemma~\ref{lem:n-point-odd-generating-function} yields
\[
\mu_{2N-1+2k}^{(N)}
=
(-1)^{N+1}(2N-1)N!(N-1)!\,
h_k(1^2,\dots,N^2),
\qquad k\ge 0.
\]
Thus the surviving odd moments are not merely bounded: they are explicit and
have a fixed sign,
\[
(-1)^{N+1}\mu_{2r+1}^{(N)}\ge 0
\qquad (r\ge N-1).
\]
This makes the post-cancellation odd tail completely structured rather than
mysterious.
\end{remark}

\begin{corollary}[Exact action of the $N$-point operator on odd germs]
\label{cor:n-point-exact-odd-action}
Let
\[
F(s)=\sum_{r\ge 0} b_{2r+1}s^{2r+1}
\]
be an odd analytic germ at $s=0$. Then
\[
(\mathcal P_{N,Q}F)
:=
\sum_{j=1}^N a_j^{(N)}\,F\!\left(\frac{j}{Q^2}\right)
=
\sum_{r\ge 0} b_{2r+1}\frac{\mu_{2r+1}^{(N)}}{Q^{4r+2}}.
\]
Hence, by Remark~\ref{rem:surviving-odd-tail-structure},
\[
(\mathcal P_{N,Q}F)
=
(-1)^{N+1}(2N-1)N!(N-1)!
\sum_{k\ge 0}
b_{2N-1+2k}\,
h_k(1^2,\dots,N^2)\,
Q^{-(4N+4k-2)}.
\]
Thus the $N$-point operator does not merely annihilate the first $N-1$
odd jets: on odd germs it acts as an explicit shifted complete-homogeneous
transform of the surviving odd Taylor coefficients.
\end{corollary}

\begin{proposition}[Exact finite-difference factorization on odd germs]
\label{prop:n-point-odd-finite-difference-factorization}
Let
\[
T_Q:=e^{Q^{-2}D},
\qquad
D:=\frac{d}{ds},
\]
so that $T_QF(s)=F(s+Q^{-2})$. Then for every odd analytic germ
$F$ at $s=0$,
\[
(\mathcal P_{N,Q}F)
=
\frac{N(-1)^N}{2\binom{2N-2}{N-1}}
\left[
T_Q^{-N}(1-T_Q)^{2N-1}(1+T_Q)F
\right]_{s=0}.
\]
Equivalently,
\[
(\mathcal P_{N,Q}F)
=
\frac{(-1)^{N+1}N}{2\binom{2N-2}{N-1}}
\left[
T_Q^{-N}(T_Q-1)^{2N-1}(1+T_Q)F
\right]_{s=0}.
\]
In particular, on odd germs the $N$-point operator factors exactly through
the $(2N-1)$-st forward difference.
\end{proposition}

\begin{proof}
Let
\[
P_{N,Q}(D):=\sum_{j=1}^N a_j^{(N)}e^{(j/Q^2)D}
=\sum_{j=1}^N a_j^{(N)}T_Q^j.
\]
Then
\[
(\mathcal P_{N,Q}F)=\bigl(P_{N,Q}(D)F\bigr)\big|_{s=0}.
\]
By Lemma~\ref{lem:n-point-mellin-symbol}, with $t=T_Q$,
\[
P_{N,Q}(D)-P_{N,Q}(-D)
=
\frac{N(-1)^N}{\binom{2N-2}{N-1}}\,
T_Q^{-N}(1-T_Q)^{2N-1}(1+T_Q).
\]
If $F$ is odd, then
\[
\bigl(P_{N,Q}(-D)F\bigr)\big|_{s=0}
=
\sum_{j=1}^N a_j^{(N)}F(-j/Q^2)
=
-\sum_{j=1}^N a_j^{(N)}F(j/Q^2)
=
-(\mathcal P_{N,Q}F).
\]
Hence
\[
2(\mathcal P_{N,Q}F)
=
\bigl((P_{N,Q}(D)-P_{N,Q}(-D))F\bigr)\big|_{s=0},
\]
which gives the claimed formula. The second form follows from
$(1-T_Q)^{2N-1}=-(T_Q-1)^{2N-1}$.
\end{proof}

\begin{remark}[Why the odd tail begins at order $2N-1$]
\label{rem:n-point-odd-tail-begins-by-factorization}
Proposition~\ref{prop:n-point-odd-finite-difference-factorization} shows that
the disappearance of the first $N-1$ odd jets is not merely a moment
identity. It is built into the operator itself: on odd germs, the
$N$-point projector contains the factor $(T_Q-1)^{2N-1}$. The surviving
odd tail therefore begins at order $2N-1$ for operator-theoretic reasons,
not only by coefficient cancellation.
\end{remark}

\begin{lemma}[Integral form of a forward difference]
\label{lem:forward-difference-integral-form}
For $m\ge 1$, $h>0$, and an analytic germ $f$, one has
\[
(e^{hD}-1)^m f(x)
=
h^m\int_0^m f^{(m)}(x+hu)\,\omega_m(u)\,du,
\]
where
\[
\omega_m(u)
:=
\frac{1}{(m-1)!}
\sum_{r=0}^{m}(-1)^r\binom{m}{r}(u-r)_+^{m-1},
\qquad
(u-r)_+:=\max\{u-r,0\}.
\]
The function $\omega_m$ is nonnegative, supported on $[0,m]$, and
satisfies the symmetry
\[
\omega_m(u)=\omega_m(m-u).
\]
\end{lemma}

\begin{proof}
The identity
\[
(e^{hD}-1)f(x)=f(x+h)-f(x)=\int_0^h f'(x+t)\,dt
\]
iterates to
\[
(e^{hD}-1)^m f(x)
=
\int_{[0,h]^m}
f^{(m)}(x+t_1+\cdots+t_m)\,dt_1\cdots dt_m.
\]
Rescaling $t_i=hu_i$ gives
\[
(e^{hD}-1)^m f(x)
=
h^m
\int_{[0,1]^m}
f^{(m)}(x+h(u_1+\cdots+u_m))\,du_1\cdots du_m.
\]
Pushing forward Lebesgue measure on $[0,1]^m$ under
\[
(u_1,\dots,u_m)\mapsto u_1+\cdots+u_m
\]
yields the density $\omega_m$, namely the classical Irwin--Hall density,
which has the stated explicit formula, support, and symmetry. This proves the
claim.
\end{proof}

\begin{proposition}[Positive-kernel representation of the odd projector]
\label{prop:n-point-odd-positive-kernel}
Set
\[
m:=2N-1,
\qquad
h:=Q^{-2},
\]
and define, for $0\le u\le N$,
\[
\kappa_N(u):=\omega_{2N-1}(N-u)+\omega_{2N-1}(N-1-u),
\]
where $\omega_{2N-1}$ is the density from
Lemma~\ref{lem:forward-difference-integral-form}, extended by $0$ outside
$[0,2N-1]$. Then $\kappa_N(u)\ge 0$ on $[0,N]$, and for every odd
analytic germ $F$,
\[
(\mathcal P_{N,Q}F)
=
\frac{N(-1)^{N+1}}{\binom{2N-2}{N-1}}\,
Q^{-(4N-2)}
\int_0^N
\kappa_N(u)\,
F^{(2N-1)}\!\left(\frac{u}{Q^2}\right)\,du.
\]
Moreover, $\kappa_N(u)>0$ for $0<u<N$.
\end{proposition}

\begin{proof}
Apply Proposition~\ref{prop:n-point-odd-finite-difference-factorization} and
Lemma~\ref{lem:forward-difference-integral-form} with $m=2N-1$ and
$h=Q^{-2}$. This gives
\[
(\mathcal P_{N,Q}F)
=
\frac{N(-1)^{N+1}}{2\binom{2N-2}{N-1}}
h^{2N-1}
\int_0^{2N-1}
\omega_{2N-1}(v)\,
\Bigl[
F^{(2N-1)}\bigl((v-N)h\bigr)
+
F^{(2N-1)}\bigl((v-N+1)h\bigr)
\Bigr]\,dv.
\]
Since $F$ is odd, $F^{(2N-1)}$ is even. Using this evenness together with
the symmetry
\[
\omega_{2N-1}(v)=\omega_{2N-1}(2N-1-v),
\]
the two terms may be folded onto $[0,N]$, yielding
\[
(\mathcal P_{N,Q}F)
=
\frac{N(-1)^{N+1}}{\binom{2N-2}{N-1}}\,
h^{2N-1}
\int_0^N
\bigl[
\omega_{2N-1}(N-u)+\omega_{2N-1}(N-1-u)
\bigr]
F^{(2N-1)}(uh)\,du.
\]
This is exactly the stated formula. The strict positivity on $0<u<N$
follows because $N-u\in(0,2N-1)$ there, and
$\omega_{2N-1}$ is strictly positive on the interior of its support.
\end{proof}

\begin{corollary}[Sign transfer from the first surviving derivative]
\label{cor:n-point-sign-transfer}
Let $F$ be an odd analytic germ. If for some $\sigma\in\{\pm1\}$,
\[
\sigma\,F^{(2N-1)}(s)\ge 0
\qquad
\text{for all } 0\le s\le \frac{N}{Q^2},
\]
then
\[
\sigma\,(-1)^{N+1}(\mathcal P_{N,Q}F)\ge 0.
\]
If moreover $F^{(2N-1)}\not\equiv 0$ on $[0,N/Q^2]$, then the inequality
is strict.
\end{corollary}

\begin{proof}
This is immediate from Proposition~\ref{prop:n-point-odd-positive-kernel},
since the kernel $\kappa_N$ is nonnegative and strictly positive on
$(0,N)$.
\end{proof}

\begin{remark}[Why this is the right downstream target]
\label{rem:n-point-positive-kernel-target}
Proposition~\ref{prop:n-point-odd-positive-kernel} shows that the $N$-point
layer is not merely an odd-moment cancellation device: on odd germs it is a
positive average of the first surviving derivative
$F^{(2N-1)}$ over the microscopic interval $[0,N/Q^2]$. Accordingly, any
source-level argument that gives a fixed sign, one-sided lower bound, or
variation control for
\[
H_m^{(2N-1)}(s)
\qquad
\left(0\le s\le \frac{N}{Q^2}\right)
\]
would transfer directly to the sign or size of $\Xi_\zeta^{(N)}(m)$.
This isolates the next natural analytic target in the $N$-point route.
\end{remark}

\begin{remark}[Finite-order recurrence of the normalized surviving tail]
\label{rem:n-point-tail-recurrence}
Define
\[
\nu_k
:=
\frac{(-1)^{N+1}\mu_{2N-1+2k}^{(N)}}{(2N-1)N!(N-1)!}
=
h_k(1^2,\dots,N^2),
\qquad k\ge 0.
\]
Then
\[
\sum_{k\ge 0}\nu_k t^k
=
\frac{1}{\prod_{j=1}^N(1-j^2t)}
=
\frac{1}{1-e_1 t+e_2 t^2-\cdots+(-1)^N e_N t^N},
\]
where $e_r=e_r(1^2,\dots,N^2)$ is the $r$-th elementary symmetric
polynomial in $1^2,\dots,N^2$. Consequently,
\[
\nu_k
=
e_1\nu_{k-1}-e_2\nu_{k-2}+\cdots+(-1)^{N+1}e_N\nu_{k-N}
\qquad (k\ge 1),
\]
with the conventions $\nu_0=1$ and $\nu_{k}=0$ for $k<0$. Thus the
surviving odd tail is governed by an exact order-$N$ linear recurrence.
\end{remark}

\begin{proposition}[Partial-fraction form of the surviving odd tail]
\label{prop:n-point-tail-partial-fractions}
Let
\[
G_N(t):=\frac{1}{\prod_{m=1}^N(1-m^2 t)}.
\]
Then $G_N$ has the exact partial-fraction decomposition
\[
G_N(t)
=
\sum_{j=1}^N \frac{B_{N,j}}{1-j^2 t},
\]
where
\[
B_{N,j}
=
\frac{2(-1)^{N-j}j^{2N}}{(N-j)!(N+j)!}.
\]
Equivalently,
\[
\frac{1}{\prod_{m=1}^N(1-m^2u^2)}
=
\sum_{j=1}^N
\frac{2(-1)^{N-j}j^{2N}}{(N-j)!(N+j)!}\,
\frac{1}{1-j^2u^2}.
\]

Consequently, for every $k\ge 0$,
\[
h_k(1^2,\dots,N^2)
=
\sum_{j=1}^N
\frac{2(-1)^{N-j}j^{2N+2k}}{(N-j)!(N+j)!},
\]
and hence
\[
\mu_{2N-1+2k}^{(N)}
=
(-1)^{N+1}(2N-1)N!(N-1)!
\sum_{j=1}^N
\frac{2(-1)^{N-j}j^{2N+2k}}{(N-j)!(N+j)!}.
\]
\end{proposition}

\begin{proof}
Since the poles of $G_N(t)$ are simple and located at $t=j^{-2}$
($1\le j\le N$), one has
\[
G_N(t)=\sum_{j=1}^N \frac{B_{N,j}}{1-j^2 t}
\]
for uniquely determined coefficients $B_{N,j}$. Multiplying by
$(1-j^2 t)$ and evaluating at $t=j^{-2}$ gives
\[
B_{N,j}
=
\left.
\frac{1}{\prod_{m\ne j}(1-m^2 t)}
\right|_{t=j^{-2}}
=
\frac{1}{\prod_{m\ne j}(1-m^2/j^2)}.
\]
Now
\[
\prod_{m\ne j}\left(1-\frac{m^2}{j^2}\right)
=
j^{-2N+2}\prod_{m\ne j}(j^2-m^2),
\]
and
\[
\prod_{m\ne j}(j^2-m^2)
=
\prod_{m\ne j}(j-m)\prod_{m\ne j}(j+m).
\]
Here
\[
\prod_{m\ne j}(j-m)
=
(j-1)! \,(-1)^{N-j}(N-j)!,
\]
while
\[
\prod_{m\ne j}(j+m)
=
\frac{(N+j)!}{2j\,j!}.
\]
Therefore
\[
\prod_{m\ne j}(j^2-m^2)
=
(-1)^{N-j}\frac{(N-j)!(N+j)!}{2j^2},
\]
and hence
\[
B_{N,j}
=
\frac{2(-1)^{N-j}j^{2N}}{(N-j)!(N+j)!}.
\]
Expanding each geometric series
\[
\frac{1}{1-j^2u^2}=\sum_{k\ge 0} j^{2k}u^{2k}
\]
and comparing coefficients of $u^{2k}$ yields the formula for
$h_k(1^2,\dots,N^2)$. The identity for
$\mu_{2N-1+2k}^{(N)}$ then follows from
Remark~\ref{rem:surviving-odd-tail-structure}.
\end{proof}

\begin{remark}[Dominance of the outermost pole for fixed $N$]
\label{rem:n-point-tail-dominant-outer-pole}
For fixed $N$, the explicit decomposition in
Proposition~\ref{prop:n-point-tail-partial-fractions} shows that the surviving
tail is asymptotically dominated by the outermost node $j=N$. Indeed,
\[
h_k(1^2,\dots,N^2)
=
\frac{2N^{2N+2k}}{(2N)!}
+
O_N\!\bigl((N-1)^{2k}\bigr)
\qquad (k\to\infty),
\]
and therefore
\[
\mu_{2N-1+2k}^{(N)}
=
(-1)^{N+1}\frac{N^{2N+2k}}{\binom{2N-2}{N-1}}
+
O_N\!\bigl((N-1)^{2k}\bigr)
\qquad (k\to\infty).
\]
So for fixed $N$, the far odd tail is eventually controlled by the single
outermost pole $u=\pm 1/N$.
\end{remark}

\begin{proposition}[Kernel form and explicit corrected $N$-point transverse estimate]
\label{prop:corrected-n-point}
Let
\[
H_m(s):=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr}(s;m)\bigr)
\]
be the full corrected transverse scalar.
For $N=\lfloor \alpha Q\rfloor$ with $0<\alpha<\rho_0$, define
\[
s_j=\frac{j}{Q^2},
\qquad
\Xi_\zeta^{(N)}(m)
:=
\sum_{j=1}^N a_j^{(N)}\,H_m(s_j).
\]
Then
\[
\Xi_\zeta^{(N)}(m)
=
\frac{1}{2\pi i}
\oint_{|\xi|=\rho_0/Q}
H_m(\xi)\,K_{N,Q}(\xi)\,d\xi,
\]
where
\[
K_{N,Q}(\xi)
:=
2\sum_{j=1}^N a_j^{(N)}\frac{s_j}{\xi^2-s_j^2}
=
2(-1)^{N+1}(2N-1)N!(N-1)! \, Q^4\xi\,
\frac{\Gamma(Q^2\xi-N)}{\Gamma(Q^2\xi+N+1)}.
\]
Moreover, writing $x:=\rho_0Q$, one has the explicit bound
\[
|\Xi_\zeta^{(N)}(m)|
\ll_{\rho_0}
\rho_0^2\,
\frac{(2N-1)N!(N-1)!}{Q}\,
\frac{\Gamma(x-N)}{\Gamma(x+N+1)}\,
L(m)S(m)^2.
\]
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:corrected-whitening}, the full corrected scalar
\[
H_m(s)=\Phi_K\!\bigl(\widehat\Omega_\zeta^{\corr}(s;m)\bigr)
\]
is holomorphic on $|s|<\rho_0/Q$. By
Proposition~\ref{prop:cutoff-compatibility}, all cutoff-dependent tail,
jet-correction, and estimation contributions are already internal to the full
corrected scalar $H_m(s)$; hence no external remainder is carried into
$\Xi_\zeta^{(N)}(m)$.

Since $H_m$ is odd, the odd Cauchy formula gives
\[
H_m(s)
=
\frac{1}{2\pi i}\oint_{|\xi|=\rho_0/Q}
H_m(\xi)\,\frac{2s}{\xi^2-s^2}\,d\xi.
\]
Summing this identity against the coefficients $a_j^{(N)}$ at
$s=s_j=j/Q^2$ yields
\[
\Xi_\zeta^{(N)}(m)
=
\frac{1}{2\pi i}\oint_{|\xi|=\rho_0/Q}
H_m(\xi)\,K_{N,Q}(\xi)\,d\xi
\]
with
\[
K_{N,Q}(\xi)
=
2\sum_{j=1}^N a_j^{(N)}\frac{s_j}{\xi^2-s_j^2}.
\]

Now
\[
\frac{s_j}{\xi^2-s_j^2}
=
\frac{1}{\xi}\,
\frac{j/(Q^2\xi)}{1-j^2/(Q^4\xi^2)},
\]
so, using Lemma~\ref{lem:n-point-odd-generating-function},
\[
K_{N,Q}(\xi)
=
\frac{2}{\xi}\,
\mathcal M_N\!\left(\frac{1}{Q^2\xi}\right)
=
2(-1)^{N+1}(2N-1)N!(N-1)!\,
\frac{Q^2}{\prod_{j=1}^N(Q^4\xi^2-j^2)}.
\]
Finally,
\[
\prod_{j=1}^N(Q^4\xi^2-j^2)
=
\prod_{j=1}^N(Q^2\xi-j)\prod_{j=1}^N(Q^2\xi+j)
=
\frac{1}{Q^2\xi}\,
\frac{\Gamma(Q^2\xi+N+1)}{\Gamma(Q^2\xi-N)},
\]
which gives
\[
K_{N,Q}(\xi)
=
2(-1)^{N+1}(2N-1)N!(N-1)! \, Q^4\xi\,
\frac{\Gamma(Q^2\xi-N)}{\Gamma(Q^2\xi+N+1)}.
\]

For the size bound, Proposition~\ref{prop:boundary-estimate} gives
\[
|H_m(s)|\ll_{\rho_0}\frac{L(m)S(m)^2}{Q^3}
\qquad (|s|=\rho_0/Q).
\]
By Proposition~\ref{prop:odd-expansion}, one may write
\[
H_m(z/Q^2)
=
\sum_{r\ge 0} c_{2r+1}(m)\frac{z^{2r+1}}{Q^{2r+4}},
\qquad
|c_{2r+1}(m)|\ll L(m)S(m)^2\,\rho_0^{-(2r+1)}.
\]
Therefore
\[
\Xi_\zeta^{(N)}(m)
=
\sum_{r\ge 0} c_{2r+1}(m)\frac{\mu_{2r+1}^{(N)}}{Q^{2r+4}}.
\]
By Lemma~\ref{lem:n-point-coefficients} and
Remark~\ref{rem:surviving-odd-tail-structure}, this becomes the exact
surviving expansion
\[
\Xi_\zeta^{(N)}(m)
=
(-1)^{N+1}(2N-1)N!(N-1)!
\sum_{k\ge 0}
c_{2N-1+2k}(m)\,
h_k(1^2,\dots,N^2)\,
Q^{-(2N+2k+2)}.
\]
In particular, the $N$-point operation isolates the first surviving
corrected odd coefficient $c_{2N-1}(m)$ and propagates the higher odd
coefficients through an explicit universal positive tail.

For the bound, the coefficient estimate yields
\[
|\Xi_\zeta^{(N)}(m)|
\ll_{\rho_0}
\frac{L(m)S(m)^2}{Q^3}
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|\,(\rho_0Q)^{-(2r+1)}.
\]
Applying Lemma~\ref{lem:n-point-odd-generating-function} with $x=\rho_0Q$
gives
\[
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|\,(\rho_0Q)^{-(2r+1)}
=
(2N-1)N!(N-1)!(\rho_0Q)^2
\frac{\Gamma(\rho_0Q-N)}{\Gamma(\rho_0Q+N+1)}.
\]
Substituting this proves the stated bound.
\end{proof}

\begin{remark}[Exact surviving-coefficient expansion on the zeta side]
\label{rem:xi-zeta-exact-surviving-expansion}
With the notation of the proof of
Proposition~\ref{prop:corrected-n-point},
\[
\Xi_\zeta^{(N)}(m)
=
\sum_{r\ge 0} c_{2r+1}(m)\frac{\mu_{2r+1}^{(N)}}{Q^{2r+4}}
=
(-1)^{N+1}(2N-1)N!(N-1)!
\sum_{k\ge 0}
c_{2N-1+2k}(m)\,
h_k(1^2,\dots,N^2)\,
Q^{-(2N+2k+2)}.
\]
Thus the $N$-point step does not merely remove the first $N-1$ odd jets:
it converts the corrected odd Taylor expansion into an explicit universal tail
whose leading term is the first surviving corrected odd coefficient
$c_{2N-1}(m)$.
\end{remark}

\begin{corollary}[Finite-core localization of the transformed zeta-side scalar]
\label{cor:xi-zeta-finite-core-localization}
With the notation of Proposition~\ref{prop:corrected-n-point} and
Corollary~\ref{cor:outside-higher-odd-jets}, let
\[
H_{\out}(z/Q^2)
=
\sum_{r\ge 0} a_{2r+1}^{\out}(m,H)\,\frac{z^{2r+1}}{Q^{2r+4}}
\]
be the corrected transverse scalar contributed by all zero pairs with
$\Delta_\rho>H$, and define
\[
\Xi_{\zeta,\out}^{(N)}(m;H)
:=
\sum_{j=1}^N a_j^{(N)}\,H_{\out}(s_j),
\qquad
\Xi_{\zeta,\le H}^{(N)}(m)
:=
\Xi_\zeta^{(N)}(m)-\Xi_{\zeta,\out}^{(N)}(m;H).
\]
If $HQ>N$, then
\[
\boxed{
|\Xi_{\zeta,\out}^{(N)}(m;H)|
\ll
\frac{(2N-1)N!(N-1)!}{Q}\,
\frac{\Gamma(HQ-N)}{\Gamma(HQ+N+1)}
+
(2N-1)N!(N-1)!\,
\frac{\Gamma(Q^2-N)}{\Gamma(Q^2+N+1)}.
}
\]
Consequently,
\[
\boxed{
\Xi_\zeta^{(N)}(m)
=
\Xi_{\zeta,\le H}^{(N)}(m)
+
O\!\left(
\frac{(2N-1)N!(N-1)!}{Q}\,
\frac{\Gamma(HQ-N)}{\Gamma(HQ+N+1)}
\right)
+
O\!\left(
(2N-1)N!(N-1)!\,
\frac{\Gamma(Q^2-N)}{\Gamma(Q^2+N+1)}
\right).
}
\]
\end{corollary}

\begin{proof}
By the exact $N$-point action on odd germs used in the proof of
Proposition~\ref{prop:corrected-n-point},
\[
\Xi_{\zeta,\out}^{(N)}(m;H)
=
\sum_{r\ge 0} a_{2r+1}^{\out}(m,H)\frac{\mu_{2r+1}^{(N)}}{Q^{2r+4}}.
\]
Since $\mu_{2r+1}^{(N)}=0$ for $0\le r\le N-2$,
\[
\Xi_{\zeta,\out}^{(N)}(m;H)
=
\sum_{r\ge N-1} a_{2r+1}^{\out}(m,H)\frac{\mu_{2r+1}^{(N)}}{Q^{2r+4}}.
\]
Taking absolute values and applying
Corollary~\ref{cor:outside-higher-odd-jets},
\[
|\Xi_{\zeta,\out}^{(N)}(m;H)|
\ll
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|
\left(
\frac{H^{-(2r+3)}}{Q^{2r+4}}
+
\frac{Q^{-(2r+2)}}{Q^{2r+4}}
\right).
\]
Thus
\[
|\Xi_{\zeta,\out}^{(N)}(m;H)|
\ll
\frac{1}{H^2Q^3}
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|(HQ)^{-(2r+1)}
+
\frac{1}{Q^4}
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|(Q^2)^{-(2r+1)}.
\]
Now apply Lemma~\ref{lem:n-point-odd-generating-function} first with
$x=HQ$ and then with $x=Q^2$. Since $HQ>N$, both evaluations are valid
for all sufficiently large $Q$, and one obtains
\[
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|(HQ)^{-(2r+1)}
=
(2N-1)N!(N-1)!(HQ)^2
\frac{\Gamma(HQ-N)}{\Gamma(HQ+N+1)},
\]
and
\[
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|(Q^2)^{-(2r+1)}
=
(2N-1)N!(N-1)!Q^4
\frac{\Gamma(Q^2-N)}{\Gamma(Q^2+N+1)}.
\]
Substituting these identities proves the displayed bound for
$\Xi_{\zeta,\out}^{(N)}(m;H)$, and the decomposition
\[
\Xi_\zeta^{(N)}(m)=\Xi_{\zeta,\le H}^{(N)}(m)+\Xi_{\zeta,\out}^{(N)}(m;H)
\]
gives the second display.
\end{proof}

\begin{remark}[Asymptotic finite-core localization at linear depth]
\label{rem:xi-zeta-finite-core-localization-asymptotic}
Let
\[
N=\lfloor \alpha Q\rfloor,
\qquad
0<\alpha<\rho_0,
\]
and fix $H>\alpha$. Then Corollary~\ref{cor:xi-zeta-finite-core-localization}
and Stirling's formula give
\[
|\Xi_{\zeta,\out}^{(N)}(m;H)|
\ll
\exp\!\bigl(-H f(\alpha/H)\,Q+O(\log Q)\bigr)
+
\exp\!\bigl(-2\alpha Q\log Q+O(Q)\bigr),
\]
where
\[
f(\beta)
=
(1+\beta)\log(1+\beta)-2\beta\log\beta-(1-\beta)\log(1-\beta).
\]
In particular,
\[
\Xi_\zeta^{(N)}(m)
=
\Xi_{\zeta,\le H}^{(N)}(m)
+
O\!\bigl(e^{-Hf(\alpha/H)Q+O(\log Q)}\bigr)
+
O\!\bigl(e^{-2\alpha Q\log Q+O(Q)}\bigr).
\]
Thus the full transformed zeta-side scalar is determined, up to exponentially
small error, by a fixed finite core.
\end{remark}

\begin{remark}[Exact Laurent tail of the contour kernel]
\label{rem:n-point-kernel-laurent-tail}
The kernel in Proposition~\ref{prop:corrected-n-point} has an exact large-
$\xi$ Laurent expansion. Indeed, using
Lemma~\ref{lem:n-point-odd-generating-function} and
Remark~\ref{rem:surviving-odd-tail-structure},
\[
K_{N,Q}(\xi)
=
\frac{2}{\xi}\,
\mathcal M_N\!\left(\frac{1}{Q^2\xi}\right)
=
2(-1)^{N+1}(2N-1)N!(N-1)!\,
Q^{-4N+2}\xi^{-2N}
\sum_{k\ge 0}
h_k(1^2,\dots,N^2)\,
Q^{-4k}\xi^{-2k}.
\]
So the contour kernel is not merely small: its entire post-cancellation odd
tail is explicit, universal, and sign-rigid term-by-term.
\end{remark}

\begin{corollary}[Optimized zeta-side cancellation depth]
\label{cor:optimized-zeta-cancellation-depth}
Let
\[
N=\lfloor \alpha Q\rfloor,
\qquad
0<\alpha<\rho_0,
\qquad
\beta:=\frac{\alpha}{\rho_0}\in(0,1).
\]
Then
\[
|\Xi_\zeta^{(N)}(m)|
\ll_{\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\delta_*(\alpha,\rho_0)Q},
\]
where
\[
\delta_*(\alpha,\rho_0)
=
\rho_0\Bigl(
(1+\beta)\log(1+\beta)
-2\beta\log\beta
-(1-\beta)\log(1-\beta)
\Bigr).
\]
Moreover, $\delta_*(\alpha,\rho_0)$ is maximized uniquely at
\[
\beta=\frac{1}{\sqrt2},
\qquad\text{i.e.}\qquad
\alpha_{\mathrm{opt}}=\frac{\rho_0}{\sqrt2},
\]
so the optimal zeta-side cancellation depth is
\[
N_{\mathrm{opt}}
=
\left\lfloor \frac{\rho_0}{\sqrt2}\,Q\right\rfloor,
\]
and the corresponding exponential rate is
\[
\delta_{\mathrm{opt}}
=
2\rho_0\log(1+\sqrt2).
\]
\end{corollary}

\begin{proof}
Set $x:=\rho_0Q$, so that $N=\beta x+O(1)$ with $\beta\in(0,1)$ fixed.
By Proposition~\ref{prop:corrected-n-point}, it suffices to estimate
\[
(2N-1)N!(N-1)!\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}.
\]
A Stirling expansion gives
\[
\log\!\left(
(2N-1)N!(N-1)!\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
\right)
=
-x\,f(\beta)+O(\log x),
\]
where
\[
f(\beta)
=
(1+\beta)\log(1+\beta)
-2\beta\log\beta
-(1-\beta)\log(1-\beta).
\]
Hence
\[
(2N-1)N!(N-1)!\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
\ll_{\rho_0,\alpha}
e^{-x f(\beta)},
\]
and therefore
\[
|\Xi_\zeta^{(N)}(m)|
\ll_{\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\rho_0 f(\beta)Q}.
\]
This proves the first claim.

For the optimization, differentiate:
\[
f'(\beta)
=
\log\!\left(\frac{1-\beta^2}{\beta^2}\right).
\]
Thus $f'(\beta)=0$ exactly when $\beta=1/\sqrt2$. Since
\[
f''(\beta)
=
-\frac{2\beta}{1-\beta^2}-\frac{2}{\beta}<0
\qquad (0<\beta<1),
\]
this critical point is the unique maximizer. Finally,
\[
f\!\left(\frac{1}{\sqrt2}\right)
=
2\log(1+\sqrt2),
\]
which gives the stated value of $\delta_{\mathrm{opt}}$.
\end{proof}

\begin{remark}
Corollary~\ref{cor:optimized-zeta-cancellation-depth} optimizes the
\emph{zeta-side} cancellation depth. After the exact odd-tail evaluation is
imported into Proposition~\ref{prop:toy-n-point-direct}, the toy side imposes
no asymptotic upper restriction on the linear choice $N=\lfloor \alpha
Q\rfloor$: for every fixed $\alpha>0$, the toy microscopic nodes
$s_j=j/Q^2$ remain inside the toy analyticity disk for all sufficiently
large $Q$, and the residual odd toy tail is in fact super-exponentially
small on the $Q$-scale. Accordingly one may take the exact zeta-side
optimum
\[
\alpha=\frac{\rho_0}{\sqrt2}.
\]
\end{remark}

\begin{remark}[Sharper prefactor in the optimized zeta-side bound]
\label{rem:optimized-zeta-prefactor}
With the notation of Corollary~\ref{cor:optimized-zeta-cancellation-depth},
set
\[
x:=\rho_0Q,
\qquad
N=\beta x+O(1),
\qquad
\beta=\frac{\alpha}{\rho_0}\in(0,1).
\]
A more precise Stirling expansion of the gamma-ratio factor in
Proposition~\ref{prop:corrected-n-point} gives
\[
(2N-1)N!(N-1)!\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
=
\frac{4\pi\beta}{\sqrt{1-\beta^2}}\,
e^{-x f(\beta)}\,
(1+o(1)),
\]
where
\[
f(\beta)
=
(1+\beta)\log(1+\beta)
-2\beta\log\beta
-(1-\beta)\log(1-\beta).
\]
Consequently,
\[
|\Xi_\zeta^{(N)}(m)|
\ll
2C_{\partial}(\rho_0)\rho_0\,
\frac{4\pi\beta}{\sqrt{1-\beta^2}}\,
\frac{L(m)S(m)^2}{Q^2}\,
e^{-\delta_*(\alpha,\rho_0)Q}\,
(1+o(1)).
\]
At the zeta-side optimum $\beta=1/\sqrt2$, the prefactor simplifies to
$4\pi$, so
\[
|\Xi_\zeta^{(N_{\mathrm{opt}})}(m)|
\ll
8\pi\,C_{\partial}(\rho_0)\rho_0\,
\frac{L(m)S(m)^2}{Q^2}\,
e^{-2\rho_0\log(1+\sqrt2)\,Q}\,
(1+o(1)).
\]
This sharper prefactor is not needed for the qualitative contradiction, but it
records that, once the boundary constant $C_{\partial}(\rho_0)$ is made
explicit, the zeta-side $N$-point estimate becomes effective with an
explicit leading constant.
\end{remark}

\begin{proposition}[Real profile of the exact $N$-point kernel]
\label{prop:exact-kernel-real-profile}
Let
\[
C_N:=(2N-1)N!(N-1)!,
\qquad
\kappa_N(x):=
x\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
\qquad (x>N).
\]
Then
\[
\kappa_N(x)=\frac{1}{\prod_{j=1}^N(x^2-j^2)},
\]
and for real $x>N$,
\[
K_{N,Q}\!\left(\frac{x}{Q^2}\right)
=
2(-1)^{N+1}C_NQ^2\,\kappa_N(x).
\]
Moreover:

\begin{enumerate}
\item $\kappa_N(x)>0$ for all $x>N$;
\item $\kappa_N'(x)<0$ for all $x>N$;
\item for every $x>N$,
\[
\sup_{|\xi|=x/Q^2}|K_{N,Q}(\xi)|
=
2C_NQ^2\,\kappa_N(x)
=
\left|K_{N,Q}\!\left(\frac{x}{Q^2}\right)\right|.
\]
\end{enumerate}
\end{proposition}

\begin{proof}
From Proposition~\ref{prop:corrected-n-point},
\[
K_{N,Q}(\xi)
=
2(-1)^{N+1}C_NQ^4\xi\,
\frac{\Gamma(Q^2\xi-N)}{\Gamma(Q^2\xi+N+1)}.
\]
Substituting $\xi=x/Q^2$ gives
\[
K_{N,Q}\!\left(\frac{x}{Q^2}\right)
=
2(-1)^{N+1}C_NQ^2\,
x\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
=
2(-1)^{N+1}C_NQ^2\,\kappa_N(x).
\]

Now
\[
\Gamma(x+N+1)
=
(x+N)(x+N-1)\cdots x\,\Gamma(x),
\]
and
\[
\Gamma(x)
=
(x-1)(x-2)\cdots (x-N)\,\Gamma(x-N).
\]
Hence
\[
x\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
=
\frac{1}{(x-N)\cdots(x-1)(x+1)\cdots(x+N)}
=
\frac{1}{\prod_{j=1}^N(x^2-j^2)},
\]
which proves the product formula. Positivity is immediate for $x>N$.

For monotonicity, differentiate the logarithm:
\[
\frac{d}{dx}\log\kappa_N(x)
=
-\sum_{j=1}^N \frac{2x}{x^2-j^2}.
\]
Since $x>N$, each denominator is positive, so
\[
\frac{d}{dx}\log\kappa_N(x)<0,
\]
hence $\kappa_N'(x)<0$.

Finally, using the product form of the kernel,
\[
K_{N,Q}(\xi)
=
2(-1)^{N+1}C_NQ^2\,
\frac{1}{\prod_{j=1}^N(Q^4\xi^2-j^2)},
\]
if $|\xi|=x/Q^2$ then
\[
|Q^4\xi^2-j^2|
\ge \bigl||Q^2\xi|^2-j^2\bigr|
=
x^2-j^2
\qquad (1\le j\le N),
\]
so
\[
|K_{N,Q}(\xi)|
\le
2C_NQ^2\,
\frac{1}{\prod_{j=1}^N(x^2-j^2)}
=
2C_NQ^2\,\kappa_N(x).
\]
Equality is attained at $\xi=x/Q^2$, proving the final claim.
\end{proof}

\begin{remark}[No contour loss in the kernel factor]
\label{rem:no-contour-loss-kernel-factor}
Proposition~\ref{prop:exact-kernel-real-profile} shows that the kernel factor
in Proposition~\ref{prop:corrected-n-point} is controlled exactly by its
positive real value on the boundary circle.  Thus the boundary estimate used in
the zeta-side $N$-point bound carries no hidden contour-loss from the kernel
itself: the worst point is the positive real boundary point
\[
\xi=\frac{\rho_0}{Q}.
\]
Moreover, since $\kappa_N$ is strictly decreasing on $(N,\infty)$, the
kernel factor is largest at the smallest admissible boundary radius.
\end{remark}

\begin{proposition}[Positive smoothing preserves the real kernel profile]
\label{prop:smoothed-real-kernel-profile}
Let $\psi\in C_c^\infty(\mathbf R)$ be even, nonnegative, and normalized by
\[
\int_{\mathbf R}\psi(u)\,du=1.
\]
Set
\[
U_\psi:=\sup\{|u|:u\in \operatorname{supp}\psi\}.
\]
For $x>N+\eta Q^2U_\psi$, define the smoothed real profile
\[
\kappa_{N,\eta}^{\psi}(x)
:=
\int_{\mathbf R}\psi(u)\,\kappa_N(x+\eta Q^2u)\,du,
\]
where
\[
\kappa_N(x):=x\,\frac{\Gamma(x-N)}{\Gamma(x+N+1)}
=\frac{1}{\prod_{j=1}^N(x^2-j^2)}.
\]
Then
\[
\kappa_{N,\eta}^{\psi}(x)>0
\qquad\text{and}\qquad
\frac{d}{dx}\kappa_{N,\eta}^{\psi}(x)<0
\]
for all $x>N+\eta Q^2U_\psi$.
\end{proposition}

\begin{proof}
For $x>N+\eta Q^2U_\psi$ and $u\in \operatorname{supp}\psi$, one has
\[
x+\eta Q^2u>N.
\]
By Proposition~\ref{prop:exact-kernel-real-profile},
\[
\kappa_N(x+\eta Q^2u)>0
\qquad\text{and}\qquad
\kappa_N'(x+\eta Q^2u)<0.
\]
Since $\psi\ge 0$ and $\int \psi=1$, averaging preserves positivity:
\[
\kappa_{N,\eta}^{\psi}(x)>0.
\]
Differentiating under the integral sign gives
\[
\frac{d}{dx}\kappa_{N,\eta}^{\psi}(x)
=
\int_{\mathbf R}\psi(u)\,\kappa_N'(x+\eta Q^2u)\,du<0.
\]
\end{proof}

\begin{remark}[Smoothed real profile]
\label{rem:smoothed-real-kernel-profile}
Proposition~\ref{prop:smoothed-real-kernel-profile} shows that nonnegative
smoothing preserves the qualitative real-axis behavior of the exact kernel:
positivity and strict monotonic decay survive averaging. Thus the Mellin-side
smoothing introduced later does not destroy the basic real-profile structure of
the $N$-point kernel.
\end{remark}

\begin{remark}[Discrete Mellin projector and test-function viewpoint]
\label{rem:discrete-mellin-projector}
Define the additive operator
\[
(\mathcal P_{N,Q}F):=\sum_{j=1}^N a_j^{(N)}\,F\!\left(\frac{j}{Q^2}\right),
\]
and the associated multiplicative distribution on $\mathbb R_+^\times$,
\[
\mu_{N,Q}:=\sum_{j=1}^N a_j^{(N)}\,\delta_{e^{j/Q^2}}.
\]
Its Mellin symbol is precisely
\[
\widehat\mu_{N,Q}(z)=\sum_{j=1}^N a_j^{(N)}e^{zj/Q^2}.
\]

\medskip

Equivalently, if $D:=\frac{d}{ds}$, then
\[
\mathcal P_{N,Q}
=
P_{N,Q}(D)\big|_{s=0},
\qquad
P_{N,Q}(D):=\sum_{j=1}^N a_j^{(N)}e^{(j/Q^2)D}.
\]
Thus $\mathcal P_{N,Q}$ is a polynomial in the translation semigroup,
evaluated at the origin. If
\[
F(s)=\sum_{n\ge 0} c_n s^n,
\]
then
\[
(\mathcal P_{N,Q}F)
=
\sum_{n\ge 0} c_n\,\frac{\mu_n^{(N)}}{Q^{2n}},
\qquad
\mu_n^{(N)}:=\sum_{j=1}^N a_j^{(N)}j^n.
\]
Lemma~\ref{lem:n-point-mellin-symbol} shows that
$\widehat\mu_{N,Q}(0)=1$ and that the odd part of
$\widehat\mu_{N,Q}$ starts only at order $2N-1$; meanwhile,
Corollary~\ref{cor:n-point-exact-odd-action} identifies the exact action of
$\mathcal P_{N,Q}$ on odd germs as a shifted complete-homogeneous transform
of the surviving odd Taylor coefficients.

In this sense, the $N$-point operator may be viewed as a local discrete
Mellin-side projector. This is formally reminiscent of the Weil/Connes
test-function viewpoint, where one probes the zero set through Mellin/Fourier
transforms of multiplicative test functions and explicit- or trace-formula
pairings \cite{Conrey2003,Connes1997,ConnesConsani2021}. The present paper
does not use any global trace formula; the comparison is only structural.

A natural smoothed version is obtained by fixing an even
$\phi\in C_c^\infty(\mathbb R)$ with $\widehat\phi(0)=1$ and setting
\[
f_{N,Q,\eta}(x)
:=
\sum_{j=1}^N a_j^{(N)}
\,\eta^{-1}\phi\!\left(\frac{\log x-j/Q^2}{\eta}\right).
\]
Its Mellin transform is
\[
\widehat f_{N,Q,\eta}(z)
=
\widehat\phi(\eta z)\,\widehat\mu_{N,Q}(z).
\]
Hence the same low odd-jet annihilation persists after smoothing, while the
finite-support projector is replaced by an honest smooth multiplicative test
function. This observation is not used elsewhere in the proof, but it places
the $N$-point cancellation layer in a more canonical operator-theoretic
setting.
\end{remark}

\begin{lemma}[Smoothed Mellin projector]
\label{lem:smoothed-mellin-projector}
Let $\phi\in C_c^\infty(\mathbf R)$ be even and normalized by
\[
\int_{\mathbf R}\phi(u)\,du=1.
\]
Define its bilateral Laplace transform by
\[
\widehat\phi(w):=\int_{\mathbf R}\phi(u)e^{wu}\,du.
\]
For $\eta>0$, define the smoothed additive projector
\[
(\mathcal P_{N,Q,\eta}^{\phi}F)
:=
\sum_{j=1}^N a_j^{(N)}
\int_{\mathbf R}\phi(u)\,
F\!\left(\frac{j}{Q^2}+\eta u\right)\,du,
\]
whenever $F$ is holomorphic on a neighborhood of the integration region.

Then:

\begin{enumerate}
\item for every exponential mode $F(s)=e^{zs}$,
\[
\mathcal P_{N,Q,\eta}^{\phi}(e^{zs})
=
\widehat\phi(\eta z)\,\widehat\mu_{N,Q}(z),
\qquad
\widehat\mu_{N,Q}(z)=\sum_{j=1}^N a_j^{(N)}e^{zj/Q^2};
\]

\item the smoothed symbol preserves the exact low odd-jet annihilation:
\[
\widehat\phi(0)\widehat\mu_{N,Q}(0)=1,
\qquad
\partial_z^{\,2r+1}\!\bigl(\widehat\phi(\eta z)\widehat\mu_{N,Q}(z)\bigr)\Big|_{z=0}=0
\quad (0\le r\le N-2);
\]

\item if $F$ is holomorphic on a neighborhood $\Omega$ containing all points
\[
\frac{j}{Q^2}+\eta u
\qquad
(1\le j\le N,\ u\in \operatorname{supp}\phi),
\]
then
\[
\bigl|\mathcal P_{N,Q,\eta}^{\phi}F-\mathcal P_{N,Q}F\bigr|
\le
\frac{\eta^2}{2}\,(2N-1)\,m_2(\phi)\,
\sup_{\Omega}|F''|,
\]
where
\[
m_2(\phi):=\int_{\mathbf R}|u|^2\,|\phi(u)|\,du.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
For $F(s)=e^{zs}$,
\[
\mathcal P_{N,Q,\eta}^{\phi}(e^{zs})
=
\sum_{j=1}^N a_j^{(N)}e^{zj/Q^2}
\int_{\mathbf R}\phi(u)e^{\eta zu}\,du
=
\widehat\phi(\eta z)\,\widehat\mu_{N,Q}(z),
\]
which proves the first statement.

Since $\phi$ is even, $\widehat\phi$ is an even entire function. In
particular,
\[
\widehat\phi(0)=\int_{\mathbf R}\phi(u)\,du=1,
\qquad
\widehat\phi^{(2r+1)}(0)=0
\quad (r\ge 0).
\]
Lemma~\ref{lem:n-point-mellin-symbol} gives
\[
\widehat\mu_{N,Q}(0)=1,
\qquad
\partial_z^{\,2r+1}\widehat\mu_{N,Q}(0)=0
\quad (0\le r\le N-2).
\]
Applying Leibniz' rule to the product
$\widehat\phi(\eta z)\widehat\mu_{N,Q}(z)$ shows that all odd derivatives up
to order $2N-3$ vanish at $z=0$, proving the second statement.

For the quantitative comparison, expand $F$ at $j/Q^2$:
\[
F\!\left(\frac{j}{Q^2}+\eta u\right)
=
F\!\left(\frac{j}{Q^2}\right)
+
\eta u\,F'\!\left(\frac{j}{Q^2}\right)
+
\frac{\eta^2u^2}{2}\,F''(\xi_{j,u})
\]
for some $\xi_{j,u}\in\Omega$. Since $\phi$ is even,
\[
\int_{\mathbf R}\phi(u)\,u\,du=0.
\]
Also $\int \phi(u)\,du=1$. Therefore
\[
\int_{\mathbf R}\phi(u)\,
F\!\left(\frac{j}{Q^2}+\eta u\right)\,du
-
F\!\left(\frac{j}{Q^2}\right)
=
\frac{\eta^2}{2}
\int_{\mathbf R}\phi(u)\,u^2\,F''(\xi_{j,u})\,du.
\]
Summing against $a_j^{(N)}$ and using
Lemma~\ref{lem:n-point-coefficients},
\[
\sum_{j=1}^N |a_j^{(N)}|=2N-1,
\]
gives
\[
\bigl|\mathcal P_{N,Q,\eta}^{\phi}F-\mathcal P_{N,Q}F\bigr|
\le
\frac{\eta^2}{2}\,(2N-1)\,m_2(\phi)\,
\sup_{\Omega}|F''|.
\qedhere
\]
\end{proof}

\begin{remark}[Smoothing scale]
\label{rem:smoothing-scale-mellin-projector}
Since $N\asymp Q$, Lemma~\ref{lem:smoothed-mellin-projector} gives
\[
\mathcal P_{N,Q,\eta}^{\phi}F
=
\mathcal P_{N,Q}F
+
O\!\bigl(Q\eta^2\sup|F''|\bigr).
\]
Thus any choice $\eta=o(Q^{-1/2})$ makes the smoothing error $o(1)$ while
preserving the exact low odd-jet annihilation. This does not enter the present
proof, but it shows that the discrete $N$-point projector admits a genuinely
smooth Mellin-side avatar with the same exact cancellation pattern.
\end{remark}

\begin{proposition}[Smoothed comparison for the corrected $N$-point zeta scalar]
\label{prop:smoothed-zeta-n-point-comparison}
Let $\phi\in C_c^\infty(\mathbf R)$ be even, normalized by
\[
\int_{\mathbf R}\phi(u)\,du=1,
\]
and set
\[
U_\phi:=\sup\{|u|:u\in \operatorname{supp}\phi\},
\qquad
m_2(\phi):=\int_{\mathbf R}|u|^2\,|\phi(u)|\,du.
\]
Fix $0<\alpha<\rho_0$, let
\[
N=\lfloor \alpha Q\rfloor,
\]
and assume
\[
0<\eta\le \frac{\rho_0-\alpha}{2U_\phi\,Q}.
\]
Define the smoothed corrected scalar
\[
H_{m,\eta}(s):=\int_{\mathbf R}\phi(u)\,H_m(s+\eta u)\,du,
\]
and the corresponding smoothed $N$-point scalar
\[
\Xi_{\zeta,\eta}^{(N)}(m)
:=
\sum_{j=1}^N a_j^{(N)}\,H_{m,\eta}\!\left(\frac{j}{Q^2}\right).
\]
Then:

\begin{enumerate}
\item $H_{m,\eta}$ is odd and holomorphic on
\[
|s|<\frac{\rho_\eta}{Q},
\qquad
\rho_\eta:=\rho_0-U_\phi \eta Q>\alpha.
\]

\item One has the zeta-side exponential estimate
\[
|\Xi_{\zeta,\eta}^{(N)}(m)|
\ll_{\phi,\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\delta_*(\alpha,\rho_\eta)Q},
\]
where
\[
\delta_*(\alpha,\rho_\eta)
=
\rho_\eta\Bigl(
(1+\beta_\eta)\log(1+\beta_\eta)
-2\beta_\eta\log\beta_\eta
-(1-\beta_\eta)\log(1-\beta_\eta)
\Bigr),
\qquad
\beta_\eta:=\frac{\alpha}{\rho_\eta}.
\]

\item The smoothed and discrete $N$-point scalars satisfy
\[
|\Xi_{\zeta,\eta}^{(N)}(m)-\Xi_{\zeta}^{(N)}(m)|
\le
\frac{4\,C_{\partial}(\rho_0)\,m_2(\phi)}{(\rho_0-\alpha)^2}\,
\frac{2N-1}{Q}\,
\eta^2\,L(m)S(m)^2.
\]
In particular,
\[
|\Xi_{\zeta,\eta}^{(N)}(m)-\Xi_{\zeta}^{(N)}(m)|
\ll_{\phi,\rho_0,\alpha}
\eta^2\,L(m)S(m)^2.
\]
\end{enumerate}
\end{proposition}

\begin{proof}
Since $H_m$ is odd and $\phi$ is even,
\[
H_{m,\eta}(-s)
=
\int_{\mathbf R}\phi(u)\,H_m(-s+\eta u)\,du
=
\int_{\mathbf R}\phi(u)\,H_m(-(s+\eta u))\,du
=
-H_{m,\eta}(s),
\]
so $H_{m,\eta}$ is odd. If $|s|<\rho_\eta/Q$ and $u\in \operatorname{supp}\phi$,
then
\[
|s+\eta u|
\le
|s|+\eta U_\phi
<
\frac{\rho_0-U_\phi\eta Q}{Q}+\eta U_\phi
=
\frac{\rho_0}{Q}.
\]
Since $H_m$ is holomorphic on $|s|<\rho_0/Q$, it follows that
$H_{m,\eta}$ is holomorphic on $|s|<\rho_\eta/Q$. This proves (1).

For $|s|=\rho_\eta/Q$ and $u\in \operatorname{supp}\phi$, the same estimate gives
\[
|s+\eta u|\le \frac{\rho_0}{Q}.
\]
Hence Proposition~\ref{prop:boundary-estimate} implies
\[
|H_m(s+\eta u)|
\le
C_{\partial}(\rho_0)\,\frac{L(m)S(m)^2}{Q^3}.
\]
Therefore
\[
|H_{m,\eta}(s)|
\le
\|\phi\|_{L^1}\,C_{\partial}(\rho_0)\,\frac{L(m)S(m)^2}{Q^3}
\qquad
\left(|s|=\frac{\rho_\eta}{Q}\right).
\]
Since $H_{m,\eta}$ is odd and holomorphic on $|s|<\rho_\eta/Q$, the proof of
Corollary~\ref{cor:optimized-zeta-cancellation-depth} applies verbatim with
$\rho_0$ replaced by $\rho_\eta$. This gives
\[
|\Xi_{\zeta,\eta}^{(N)}(m)|
\ll_{\phi,\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\delta_*(\alpha,\rho_\eta)Q},
\]
proving (2).

For (3), note that
\[
\Xi_{\zeta,\eta}^{(N)}(m)-\Xi_{\zeta}^{(N)}(m)
=
\bigl(\mathcal P_{N,Q,\eta}^{\phi}-\mathcal P_{N,Q}\bigr)H_m.
\]
Apply Lemma~\ref{lem:smoothed-mellin-projector} with $F=H_m$. It remains to
bound $H_m''$ on the relevant region. Since
\[
\frac{j}{Q^2}\le \frac{N}{Q^2}\le \frac{\alpha}{Q},
\qquad
\eta U_\phi\le \frac{\rho_0-\alpha}{2Q},
\]
all points
\[
\frac{j}{Q^2}+\eta u
\qquad
(1\le j\le N,\ u\in\operatorname{supp}\phi)
\]
lie in the disk
\[
|s|\le \frac{\alpha}{Q}+\eta U_\phi
\le
\frac{\rho_0+\alpha}{2Q}.
\]
Thus their distance to the boundary circle $|s|=\rho_0/Q$ is at least
\[
\frac{\rho_0-\alpha}{2Q}.
\]
By Cauchy's derivative estimate and Proposition~\ref{prop:boundary-estimate},
\[
\sup_{\Omega}|H_m''|
\le
\frac{2\,C_{\partial}(\rho_0)\,L(m)S(m)^2/Q^3}
{\bigl((\rho_0-\alpha)/(2Q)\bigr)^2}
=
\frac{8\,C_{\partial}(\rho_0)}{(\rho_0-\alpha)^2}\,
\frac{L(m)S(m)^2}{Q}.
\]
Lemma~\ref{lem:smoothed-mellin-projector} therefore yields
\[
|\Xi_{\zeta,\eta}^{(N)}(m)-\Xi_{\zeta}^{(N)}(m)|
\le
\frac{\eta^2}{2}\,(2N-1)\,m_2(\phi)\,
\frac{8\,C_{\partial}(\rho_0)}{(\rho_0-\alpha)^2}\,
\frac{L(m)S(m)^2}{Q},
\]
which is exactly the stated bound.
\end{proof}

\begin{remark}[Microscopic smoothing regime]
\label{rem:microscopic-smoothing-zeta-n-point}
If
\[
\eta\ll Q^{-2},
\]
then Proposition~\ref{prop:smoothed-zeta-n-point-comparison} gives
\[
\Xi_{\zeta,\eta}^{(N)}(m)
=
\Xi_{\zeta}^{(N)}(m)
+
O\!\left(\frac{L(m)S(m)^2}{Q^4}\right).
\]
At the same time,
\[
\rho_\eta=\rho_0+O(Q^{-1}),
\]
so
\[
\delta_*(\alpha,\rho_\eta)
=
\delta_*(\alpha,\rho_0)+O(Q^{-1}).
\]
Thus microscopic smoothing preserves the same zeta-side exponential scale while
replacing the discrete projector by a genuinely smooth Mellin-side test
function.
\end{remark}

\begin{lemma}[Higher-order smoothed Mellin projector]
\label{lem:higher-order-smoothed-mellin-projector}
Fix an integer $M\ge 1$. Let $\phi_M\in C_c^\infty(\mathbf R)$ be even and
satisfy
\[
\int_{\mathbf R}\phi_M(u)\,du=1,
\qquad
\int_{\mathbf R}u^{2\ell}\phi_M(u)\,du=0
\quad (1\le \ell\le M-1).
\]
Define its bilateral Laplace transform by
\[
\widehat\phi_M(w):=\int_{\mathbf R}\phi_M(u)e^{wu}\,du.
\]
For $\eta>0$, define
\[
(\mathcal P_{N,Q,\eta}^{(M)}F)
:=
\sum_{j=1}^N a_j^{(N)}
\int_{\mathbf R}\phi_M(u)\,
F\!\left(\frac{j}{Q^2}+\eta u\right)\,du,
\]
whenever $F$ is holomorphic on a neighborhood of the integration region.

Then:

\begin{enumerate}
\item for every exponential mode $F(s)=e^{zs}$,
\[
\mathcal P_{N,Q,\eta}^{(M)}(e^{zs})
=
\widehat\phi_M(\eta z)\,\widehat\mu_{N,Q}(z),
\qquad
\widehat\mu_{N,Q}(z)=\sum_{j=1}^N a_j^{(N)}e^{zj/Q^2};
\]

\item one has
\[
\widehat\phi_M(0)=1,
\qquad
\widehat\phi_M^{(k)}(0)=0
\quad (1\le k\le 2M-1);
\]

\item the smoothed symbol preserves the exact low odd-jet annihilation:
\[
\partial_z^{\,2r+1}\!\bigl(\widehat\phi_M(\eta z)\widehat\mu_{N,Q}(z)\bigr)\Big|_{z=0}=0
\qquad (0\le r\le N-2);
\]

\item if $F$ is holomorphic on a neighborhood $\Omega$ containing all points
\[
\frac{j}{Q^2}+\eta u
\qquad
(1\le j\le N,\ u\in \operatorname{supp}\phi_M),
\]
then
\[
\bigl|\mathcal P_{N,Q,\eta}^{(M)}F-\mathcal P_{N,Q}F\bigr|
\le
\frac{\eta^{2M}}{(2M)!}\,(2N-1)\,m_{2M}(\phi_M)\,
\sup_{\Omega}|F^{(2M)}|,
\]
where
\[
m_{2M}(\phi_M):=\int_{\mathbf R}|u|^{2M}|\phi_M(u)|\,du.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
For $F(s)=e^{zs}$,
\[
\mathcal P_{N,Q,\eta}^{(M)}(e^{zs})
=
\sum_{j=1}^N a_j^{(N)}e^{zj/Q^2}
\int_{\mathbf R}\phi_M(u)e^{\eta zu}\,du
=
\widehat\phi_M(\eta z)\,\widehat\mu_{N,Q}(z),
\]
which proves the first statement.

Since $\phi_M$ is even, all odd moments vanish. By the imposed even-moment
conditions, one also has
\[
\int_{\mathbf R}u^k\phi_M(u)\,du=0
\qquad (1\le k\le 2M-1).
\]
Differentiating $\widehat\phi_M$ at $0$ gives
\[
\widehat\phi_M^{(k)}(0)=\int_{\mathbf R}u^k\phi_M(u)\,du,
\]
so
\[
\widehat\phi_M(0)=1,
\qquad
\widehat\phi_M^{(k)}(0)=0
\quad (1\le k\le 2M-1).
\]
This proves the second statement.

By Lemma~\ref{lem:n-point-mellin-symbol},
\[
\widehat\mu_{N,Q}(0)=1,
\qquad
\partial_z^{\,2r+1}\widehat\mu_{N,Q}(0)=0
\quad (0\le r\le N-2).
\]
Applying Leibniz' rule to
$\widehat\phi_M(\eta z)\widehat\mu_{N,Q}(z)$ shows that all odd derivatives
up to order $2N-3$ vanish at $z=0$, proving the third statement.

For the quantitative comparison, expand $F$ to order $2M-1$ at $j/Q^2$:
\[
F\!\left(\frac{j}{Q^2}+\eta u\right)
=
\sum_{k=0}^{2M-1}
\frac{(\eta u)^k}{k!}\,
F^{(k)}\!\left(\frac{j}{Q^2}\right)
+
\frac{(\eta u)^{2M}}{(2M)!}\,F^{(2M)}(\xi_{j,u})
\]
for some $\xi_{j,u}\in\Omega$. Integrating against $\phi_M$, all terms of
order $1$ through $2M-1$ vanish by the moment conditions, while the
constant term survives because $\int\phi_M=1$. Hence
\[
\int_{\mathbf R}\phi_M(u)\,
F\!\left(\frac{j}{Q^2}+\eta u\right)\,du
-
F\!\left(\frac{j}{Q^2}\right)
=
\frac{\eta^{2M}}{(2M)!}
\int_{\mathbf R}\phi_M(u)\,u^{2M}F^{(2M)}(\xi_{j,u})\,du.
\]
Summing against $a_j^{(N)}$ and using
Lemma~\ref{lem:n-point-coefficients},
\[
\sum_{j=1}^N |a_j^{(N)}|=2N-1,
\]
gives the claimed bound.
\qedhere
\end{proof}

\begin{proposition}[Higher-order smoothed comparison for the corrected $N$-point zeta scalar]
\label{prop:higher-order-smoothed-zeta-n-point-comparison}
Fix an integer $M\ge 1$, and let $\phi_M\in C_c^\infty(\mathbf R)$ be even,
normalized, and moment-corrected as in
Lemma~\ref{lem:higher-order-smoothed-mellin-projector}. Set
\[
U_M:=\sup\{|u|:u\in \operatorname{supp}\phi_M\},
\qquad
m_{2M}(\phi_M):=\int_{\mathbf R}|u|^{2M}|\phi_M(u)|\,du.
\]
Fix $0<\alpha<\rho_0$, let
\[
N=\lfloor \alpha Q\rfloor,
\]
and assume
\[
0<\eta\le \frac{\rho_0-\alpha}{2U_M\,Q}.
\]
Define
\[
H_{m,\eta}^{(M)}(s):=\int_{\mathbf R}\phi_M(u)\,H_m(s+\eta u)\,du,
\]
and
\[
\Xi_{\zeta,\eta}^{(N,M)}(m)
:=
\sum_{j=1}^N a_j^{(N)}\,H_{m,\eta}^{(M)}\!\left(\frac{j}{Q^2}\right).
\]
Then:

\begin{enumerate}
\item $H_{m,\eta}^{(M)}$ is odd and holomorphic on
\[
|s|<\frac{\rho_{M,\eta}}{Q},
\qquad
\rho_{M,\eta}:=\rho_0-U_M\eta Q>\alpha;
\]

\item one has
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)|
\ll_{\phi_M,\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\delta_*(\alpha,\rho_{M,\eta})Q};
\]

\item the smoothed and discrete $N$-point scalars satisfy
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)|
\le
C_{\partial}(\rho_0)\,(2N-1)\,m_{2M}(\phi_M)\,
\left(\frac{2}{\rho_0-\alpha}\right)^{2M}
\eta^{2M}Q^{2M-3}\,
L(m)S(m)^2,
\]
and hence
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)|
\ll_{\phi_M,\rho_0,\alpha}
(\eta Q)^{2M}\,\frac{L(m)S(m)^2}{Q^2}.
\]
\end{enumerate}
\end{proposition}

\begin{proof}
The proof of oddness and holomorphy is identical to that of
Proposition~\ref{prop:smoothed-zeta-n-point-comparison}, with $\phi$ replaced
by $\phi_M$. Likewise, on $|s|=\rho_{M,\eta}/Q$,
\[
|H_{m,\eta}^{(M)}(s)|
\le
\|\phi_M\|_{L^1}\,C_{\partial}(\rho_0)\,\frac{L(m)S(m)^2}{Q^3}.
\]
Therefore the proof of
Corollary~\ref{cor:optimized-zeta-cancellation-depth} applies verbatim with
$\rho_0$ replaced by $\rho_{M,\eta}$, giving the stated exponential bound.

For the comparison estimate,
\[
\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)
=
\bigl(\mathcal P_{N,Q,\eta}^{(M)}-\mathcal P_{N,Q}\bigr)H_m.
\]
Apply Lemma~\ref{lem:higher-order-smoothed-mellin-projector} with $F=H_m$.
Exactly as in the proof of
Proposition~\ref{prop:smoothed-zeta-n-point-comparison}, all relevant points
lie at distance at least
\[
\frac{\rho_0-\alpha}{2Q}
\]
from the boundary circle $|s|=\rho_0/Q$. Hence Cauchy's derivative estimate
and Proposition~\ref{prop:boundary-estimate} give
\[
\sup_{\Omega}|H_m^{(2M)}|
\le
(2M)!\,C_{\partial}(\rho_0)\,
\left(\frac{2Q}{\rho_0-\alpha}\right)^{2M}
\frac{L(m)S(m)^2}{Q^3}.
\]
Substituting this into Lemma~\ref{lem:higher-order-smoothed-mellin-projector}
yields
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)|
\le
C_{\partial}(\rho_0)\,(2N-1)\,m_{2M}(\phi_M)\,
\left(\frac{2}{\rho_0-\alpha}\right)^{2M}
\eta^{2M}Q^{2M-3}\,
L(m)S(m)^2,
\]
as claimed. Since $N\asymp Q$, the final big-Oh form follows.
\end{proof}

\begin{remark}[Saturation at the natural $Q^{-1}$ smoothing scale]
\label{rem:higher-order-smoothing-saturation}
Proposition~\ref{prop:higher-order-smoothed-zeta-n-point-comparison} shows that
higher-order moment correction improves the comparison error to order
$2M$, but under the largest admissible smoothing scale
\[
\eta\asymp Q^{-1},
\]
one still has
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)|
\ll
\frac{L(m)S(m)^2}{Q^2}.
\]
Thus higher-order smoothing does not improve the $Q$-power at the natural
admissible scale; its gain is in canonicity and in the ability to make the
smoothed projector arbitrarily close to the discrete one once one works at a
smaller scale. For example, if
\[
\eta=Q^{-1-\sigma}
\qquad (\sigma>0),
\]
then
\[
|\Xi_{\zeta,\eta}^{(N,M)}(m)-\Xi_{\zeta}^{(N)}(m)|
\ll
Q^{-2-2M\sigma}\,L(m)S(m)^2.
\]
\end{remark}

We isolate the toy microscopic expansion in
Appendix~\ref{app:toy-microscopic-expansion}; the only fact used in the main
argument is the following $N$-point preservation statement.

\begin{proposition}[Toy $N$-point transverse preservation]
\label{prop:toy-n-point-direct}
Fix a compact interval
\[
D=[d_-,d_+]\subset(0,\infty),
\]
let $\rho_{\toy}$ and $u_0(D)$ be as in
Lemma~\ref{lem:toy-microscopic-expansion}, and fix
\[
\alpha>0.
\]
For
\[
N=\lfloor \alpha Q\rfloor,
\qquad
s_j=\frac{j}{Q^2},
\]
define
\[
\Xi_{\toy}^{(N)}(u,d)
:=
\sum_{j=1}^N a_j^{(N)}\,
\Phi_K\!\bigl(\Delta_{\toy}(u,d;s_j)\bigr).
\]
Then, for all sufficiently large $Q$ (depending on $D$ and $\alpha$),
for $d\in D$ and $|u|<u_0(D)$,
\[
\Xi_{\toy}^{(N)}(u,d)
=
u^2\Phi_K(M(d))+O(u^4),
\]
uniformly in $d\in D$. In particular,
\[
|\Xi_{\toy}^{(N)}(u,d)|\asymp u^2
\]
uniformly on compact $d$-ranges.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:toy-microscopic-expansion},
\[
\Delta_{\toy}(u,d;s)=u^2M(d)+u^4E(u,d;s),
\]
where $E(u,d;s)$ is analytic in $s$ on $|s|<\rho_{\toy}$ and uniformly
bounded there for $d\in D$ and $|u|<u_0(D)$. Applying the linear
functional $\Phi_K$, define
\[
R_{u,d}(s):=\Phi_K(E(u,d;s)).
\]
Then $R_{u,d}(s)$ is analytic on $|s|<\rho_{\toy}$, and by Cauchy's
estimate its Taylor coefficients satisfy
\[
R_{u,d}(s)=\sum_{n\ge 0} b_n(u,d)s^n,
\qquad
|b_n(u,d)|\ll \rho_{\toy}^{-n},
\]
uniformly for $d\in D$ and $|u|<u_0(D)$.

Therefore
\[
\Phi_K\!\bigl(\Delta_{\toy}(u,d;s_j)\bigr)
=
u^2\Phi_K(M(d))+u^4R_{u,d}(s_j),
\]
so
\[
\Xi_{\toy}^{(N)}(u,d)
=
u^2\Phi_K(M(d))
+
u^4\sum_{j=1}^N a_j^{(N)}R_{u,d}(s_j).
\]
Expand $R_{u,d}$ at the microscopic nodes $s_j=j/Q^2$:
\[
\sum_{j=1}^N a_j^{(N)}R_{u,d}(s_j)
=
\sum_{n\ge 0} b_n(u,d)\frac{\mu_n^{(N)}}{Q^{2n}},
\qquad
\mu_n^{(N)}:=\sum_{j=1}^N a_j^{(N)}j^n.
\]

The constant term contributes
\[
b_0(u,d)\mu_0^{(N)}=b_0(u,d),
\]
since $\mu_0^{(N)}=\sum_j a_j^{(N)}=1$ by
Lemma~\ref{lem:n-point-coefficients}. For the remaining terms, split into
even and odd parts.

For the even terms, Lemma~\ref{lem:n-point-coefficients} gives
\[
|\mu_{2\ell}^{(N)}|
\le
(2N-1)N^{2\ell},
\]
so
\[
\sum_{\ell\ge 1}
|b_{2\ell}(u,d)|\frac{|\mu_{2\ell}^{(N)}|}{Q^{4\ell}}
\ll
(2N-1)\sum_{\ell\ge 1}
\rho_{\toy}^{-2\ell}\frac{N^{2\ell}}{Q^{4\ell}}
\ll
\frac{1}{Q},
\]
because $N\asymp Q$.

For the odd terms, Lemma~\ref{lem:n-point-coefficients} gives
\[
\mu_{2r+1}^{(N)}=0
\qquad (0\le r\le N-2),
\]
so only the tail $r\ge N-1$ remains. Using the coefficient bound
$|b_{2r+1}(u,d)|\ll \rho_{\toy}^{-(2r+1)}$, we obtain
\[
\sum_{r\ge N-1}
|b_{2r+1}(u,d)|\frac{|\mu_{2r+1}^{(N)}|}{Q^{4r+2}}
\ll
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|\,(\rho_{\toy}Q^2)^{-(2r+1)}.
\]
Now apply Lemma~\ref{lem:n-point-odd-generating-function} with
\[
x=\rho_{\toy}Q^2.
\]
For all sufficiently large $Q$, one has $x>N$, and therefore
\[
\sum_{r\ge N-1}
|\mu_{2r+1}^{(N)}|\,(\rho_{\toy}Q^2)^{-(2r+1)}
=
(2N-1)N!(N-1)!(\rho_{\toy}Q^2)^2
\frac{\Gamma(\rho_{\toy}Q^2-N)}{\Gamma(\rho_{\toy}Q^2+N+1)}.
\]
Since $N=\lfloor \alpha Q\rfloor$ and $x=\rho_{\toy}Q^2$, Stirling's
formula gives
\[
(2N-1)N!(N-1)!(\rho_{\toy}Q^2)^2
\frac{\Gamma(\rho_{\toy}Q^2-N)}{\Gamma(\rho_{\toy}Q^2+N+1)}
=
\exp\!\bigl(-2\alpha Q\log Q+O(Q)\bigr).
\]
In particular, the residual odd toy tail is super-exponentially small on the
$Q$-scale:
\[
\sum_{r\ge N-1}
|b_{2r+1}(u,d)|\frac{|\mu_{2r+1}^{(N)}|}{Q^{4r+2}}
\ll
\exp\!\bigl(-2\alpha Q\log Q+O(Q)\bigr).
\]

Combining the constant, even, and odd contributions,
\[
\sum_{j=1}^N a_j^{(N)}R_{u,d}(s_j)
=
b_0(u,d)+O(Q^{-1})+O(e^{-cQ}),
\]
and in particular
\[
\sum_{j=1}^N a_j^{(N)}R_{u,d}(s_j)=O(1),
\]
uniformly for $d\in D$ and $|u|<u_0(D)$. Therefore
\[
\Xi_{\toy}^{(N)}(u,d)
=
u^2\Phi_K(M(d))+O(u^4),
\]
uniformly in $d\in D$.

Because $\Phi_K(M(d))\neq 0$ for $d>0$, and is bounded away from $0$ on
every compact interval $D\subset(0,\infty)$, the final estimate
\[
|\Xi_{\toy}^{(N)}(u,d)|\asymp u^2
\]
follows.
\end{proof}

\begin{remark}[The toy odd tail is negligible beyond all $e^{-cQ}$-scales]
\label{rem:toy-odd-tail-superexp}
The proof of Proposition~\ref{prop:toy-n-point-direct} shows more than the
$O(u^4)$ preservation statement used later: after $N$-point cancellation,
the residual odd toy tail is of size
\[
\exp\!\bigl(-2\alpha Q\log Q+O(Q)\bigr).
\]
Thus on the toy side the $N$-point odd leakage is not merely exponentially
small in $Q$; it is negligible beyond every $e^{-cQ}$-scale.
\end{remark}

On the toy side, Proposition~\ref{prop:toy-n-point-direct} gives
\begin{equation}\label{eq:Xi-toy}
\Xi_{\toy}^{(N)}(u,d)=u^2\Phi_K(M(d))+O(u^4),
\end{equation}
so on compact $d$-ranges,
\[
|\Xi_{\toy}^{(N)}(u,d)|\asymp u^2.
\]
Using \eqref{eq:u2-calibration},
\begin{equation}\label{eq:Xi-toy-calibrated}
|\Xi_{\toy}^{(N)}(u,d)|\asymp \frac{x_0}{B_\zeta(m)}S(m).
\end{equation}

\begin{remark}[Work in progress: calibrated size versus microscopic toy regime]
\label{rem:wip-calibration-small-u}
As presently written, the final calibration freezes the comparison scale at a
fixed value $x=x_0(D)$, which yields
\[
u^2 \asymp \frac{x_0}{B_\zeta(m)}\,S(m).
\]
With only the crude global bounds used later in the contradiction,
\[
S(m)\ll Q^2,
\qquad
B_\zeta(m)\asymp Q,
\]
this gives at best
\[
u^2\ll x_0 Q,
\]
and therefore does not by itself force the calibrated toy parameter $u$ to
lie in the microscopic toy regime $|u|<u_0(D)$ required by
Proposition~\ref{prop:toy-n-point-direct}.

A plausible repair is to avoid freezing the scale at $x_0(D)$, and instead
to choose the comparison scale adaptively:
\[
x=x(m)\in (0,x_0(D)].
\]
Since the pairing and calibration statements are naturally formulated for
$0<x\le x_0(D)$, one expects to choose $x(m)$ so that
\[
u^2 \asymp \frac{x(m)}{B_\zeta(m)}\,S(m)
\]
is forced to remain below the toy threshold $u_0(D)^2$.  For example, if
the implicit upper bound
\[
u^2 \le C\,\frac{x}{B_\zeta(m)}\,S(m)
\]
is available uniformly, then one may try to take
\[
x(m):=
\min\!\left\{
x_0(D),\;
\frac{u_0(D)^2}{2C}\frac{B_\zeta(m)}{S(m)}
\right\},
\]
which would guarantee
\[
u^2\le \frac{u_0(D)^2}{2}.
\]

To make this repair rigorous, however, the draft must still verify that the
entire calibration chain remains valid uniformly in such a variable
$x$-regime.  In particular, one still needs to check all of the following:

\begin{enumerate}
\item The pairing and denominator estimates remain uniform for all
$0<x\le x_0(D)$, including the regime $x\to 0$, so that the calibration
functional is still well-defined and the main term continues to scale linearly
in $x$.

\item The fixed-scaled statements currently written in terms of
\[
x=B_\zeta(m)\sigma,
\qquad
|\sigma|\asymp Q^{-1},
\]
can be upgraded to a variable/shrinking regime of the form
\[
x=B_\zeta(m)\sigma,
\qquad
|\sigma|\le c\,Q^{-1},
\]
or an equivalent $0<x\le x_0(D)$ formulation, without loss of the transfer,
whitening, and calibration estimates used later.

\item The remainder bound after applying the calibrated functional remains
uniform in the variable-$x$ regime; in particular, one needs the normalized
error estimate to stay independent of $x$, or at least sufficiently mild as
$x\to 0$, so that shrinking $x$ to enforce $|u|<u_0(D)$ does not
destroy the zeta-side control.

\item The cutoff choice required in the calibration remainder estimate can
still be made uniformly when $x=x(m)$ is allowed to shrink.  Concretely, one
must check that the condition
\[
R^3 \gg \frac{1}{xQ\,S(m)}
\]
remains compatible with the admissible cutoff regime under the adaptive choice
of $x(m)$.

\item The final contradiction theorem must be reformulated so that the toy-side
main term is compared at the variable scale $x(m)$, rather than at the fixed
scale $x_0(D)$, and one must verify that the resulting lower bound still
dominates the exponentially small zeta-side bound.
\end{enumerate}

Accordingly, the small-$u$ issue does not presently appear to be a
fundamental obstruction, but the current argument should be read as
conditional on a variable-$x$ calibration rewrite that has not yet been
carried out in the draft.
\end{remark}

The following remark records the current status of the toy model in the
overall proof strategy.

\begin{remark}[Work in progress: pair-like versus finite-core endgame]
\label{rem:wip-pairlike-finitecore}
At the current stage of the draft, the toy anomaly model should be understood
as a \emph{pair-core first-odd-jet normal form}, not yet as a universal normal
form for an arbitrary finite same-scale off-line core.

More precisely, in the pure pair model one has first-odd-jet nondegeneracy:
\[
a_1^{\toy}(u,d)=\kappa(d)u^2+O(u^4),
\qquad
\kappa(d)\neq 0,
\]
so the first odd jet already detects the off-line anomaly.

However, the fixed-core analysis developed later in the draft shows that for
a general finite same-scale core, cancellation may occur at the first odd
order even when a genuine corrected anomaly survives at a higher odd order.
Thus the toy model is presently justified as the correct first-odd-jet
simplification only under a \emph{pair-like core} hypothesis (or a
perturbative enlargement thereof), not yet for an arbitrary finite core.

Accordingly, the argument now has a genuine fork:
\begin{enumerate}
\item \textbf{Pair-like branch.}
If the actual same-scale core is perturbatively pair-like in the corrected
microscopic sense, then the present toy-model first-jet obstruction should
still apply, and the contradiction can be driven by the first odd coefficient.

\item \textbf{Finite-core branch.}
If the actual same-scale core is not perturbatively pair-like, then the
correct endgame must be reformulated in terms of a genuine finite-core
anomaly model, and the obstruction should be attached not specifically to the
first odd jet, but to the \emph{first nonzero odd jet} of the corrected
transverse scalar.
\end{enumerate}

Thus the toy model is best viewed, at present, as the first-odd-jet
simplification of a pair-like core, rather than as a universal model for all
finite cores. This is one of the main places where the present manuscript
should still be read as a work in progress.
\end{remark}

\section{Local projective rigidity of the one-pair and multi-pair families}
\label{sec:projective-rigidity}

Throughout this section, $\Qabs$ denotes the abstract odd-germ quotient by
the value/gauge family (not the height scale $Q\asymp\log|m|$ used
elsewhere in the paper). For the first residual step on the cubic-generic
region, we will also introduce an explicit finite-order model
$\mathcal R_h^{(5)}$ through order $5$. The latter supplements, but does
not globally replace, the ambient abstract quotient $\Qabs$.

\subsection{Cubic leading line and the first residual class for the one-pair family}

Let
\[
F_h(z)\in \Qabs[[z^2]]
\]
denote the corrected quotient odd germ of the normalized one-pair family, where
$\Qabs$ is the abstract odd-germ quotient by the value/gauge family.

\begin{lemma}[First-order value-family generator]
\label{lem:first-order-value-family-generator}
Let
\[
\mathcal W(G_-,N,G_+):=G_-^{-1/2}NG_+^{-1/2}.
\]
Let $G_0$ and $N_0$ denote the coincident background same-point and mixed
blocks, and write
\[
X_0:=G_0^{-1/2}.
\]
Let $L$ be the Fr\'echet derivative of the inverse-square-root map
$G\mapsto G^{-1/2}$ at $G_0$, so that
\[
(G_0+\varepsilon H)^{-1/2}
=
X_0+\varepsilon L(H)+O(\varepsilon^2).
\]

If $\dot G_{-,1}$, $\dot N_1$, and $\dot G_{+,1}$ are the first-order
odd pure-value variations of the left same-point block, the mixed block, and
the right same-point block, respectively, then the induced first-order odd
coefficient in the corrected local block is
\[
B_1
=
L(\dot G_{-,1})\,N_0\,X_0
+
X_0\,\dot N_1\,X_0
+
X_0\,N_0\,L(\dot G_{+,1}).
\]
Equivalently, the first-order family $V_{\val}^{(1)}$ is the image of the
linear map
\[
(\dot G_{-,1},\dot N_1,\dot G_{+,1})
\longmapsto
L(\dot G_{-,1})\,N_0\,X_0
+
X_0\,\dot N_1\,X_0
+
X_0\,N_0\,L(\dot G_{+,1}).
\]
\end{lemma}

\begin{proof}
The corrected local block is obtained by the analytic whitening map
\[
\mathcal W(G_-,N,G_+)=G_-^{-1/2}NG_+^{-1/2}.
\]
Expand the three inputs to first odd order under a pure value deformation:
\[
G_-(s)=G_0+\varepsilon \dot G_{-,1}+O(\varepsilon^2),\qquad
N(s)=N_0+\varepsilon \dot N_1+O(\varepsilon^2),\qquad
G_+(s)=G_0+\varepsilon \dot G_{+,1}+O(\varepsilon^2).
\]
Then
\[
G_\pm(s)^{-1/2}
=
X_0+\varepsilon L(\dot G_{\pm,1})+O(\varepsilon^2),
\]
so multiplying
\[
G_-(s)^{-1/2}\,N(s)\,G_+(s)^{-1/2}
\]
to first order gives
\[
X_0N_0X_0
+
\varepsilon\Bigl(
L(\dot G_{-,1})\,N_0\,X_0
+
X_0\,\dot N_1\,X_0
+
X_0\,N_0\,L(\dot G_{+,1})
\Bigr)
+
O(\varepsilon^2).
\]
The coefficient of $\varepsilon$ is exactly the first-order generator
$B_1$.
\end{proof}

\begin{lemma}[Whitened first-order reduction]
\label{lem:first-order-generator-whitened}
At the coincident background one has
\[
N_0=G_0.
\]
If
\[
\widetilde H:=X_0HX_0
\]
denotes whitening by $X_0=G_0^{-1/2}$, then the first-order generator of
Lemma~\ref{lem:first-order-value-family-generator} becomes
\[
\widetilde B_1
=
\widetilde{\dot N}_1
-\frac12\,\widetilde{\dot G}_{-,1}
-\frac12\,\widetilde{\dot G}_{+,1}.
\]
\end{lemma}

\begin{proof}
Since $X_0G_0X_0=I$, whitening conjugates the background to the identity.
The Fr\'echet derivative of $G\mapsto G^{-1/2}$ at $I$ is
\[
L_I(H)=-\frac12 H.
\]
Therefore, after whitening the formula of
Lemma~\ref{lem:first-order-value-family-generator} becomes
\[
\widetilde B_1
=
L_I(\widetilde{\dot G}_{-,1})\,I\,I
+
I\,\widetilde{\dot N}_1\,I
+
I\,I\,L_I(\widetilde{\dot G}_{+,1})
=
\widetilde{\dot N}_1
-\frac12\,\widetilde{\dot G}_{-,1}
-\frac12\,\widetilde{\dot G}_{+,1}.
\qedhere
\]
\end{proof}

\begin{lemma}[First-order same-point span]
\label{lem:first-order-same-point-span}
The first-order pure-value same-point variations span the full symmetric
subspace:
\[
\operatorname{span}\{\widetilde{\dot G}_{-,1}\}
=
\operatorname{span}\{\widetilde{\dot G}_{+,1}\}
=
\operatorname{Sym}_2(\mathbf C).
\]
\end{lemma}

\begin{proof}
The corrected same-point block has the form
\[
G_{m,\pm}^{\corr}(s)
=
\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[.5ex]
\frac12 q'(t_\pm) & \frac1{12}\bigl(q''(t_\pm)+2q(t_\pm)^3\bigr)
\end{pmatrix}.
\]
Therefore an infinitesimal pure-value variation at one side gives
\[
\delta G_\pm
=
\frac1\pi
\begin{pmatrix}
2\,\delta q_\pm & \frac12\,\delta q'_\pm\\[.5ex]
\frac12\,\delta q'_\pm &
\frac1{12}\bigl(\delta q''_\pm+6q_{\pm,0}^2\delta q_\pm\bigr)
\end{pmatrix}.
\]
As $\delta q_\pm$, $\delta q'_\pm$, and $\delta q''_\pm$ vary
independently, the off-diagonal entry, the $(1,1)$-entry, and the pure
$(2,2)$-direction may be varied independently. Hence the span is the full
space $\operatorname{Sym}_2(\mathbf C)$. Whitening by $X_0$ preserves the
symmetric subspace and is invertible, so the same conclusion holds for
$\widetilde{\dot G}_{\pm,1}$.
\end{proof}

\begin{lemma}[First-order mixed skew direction]
\label{lem:first-order-mixed-skew}
Let
\[
\mathfrak{so}_2(\mathbf C)
:=
\left\{
\begin{pmatrix}
0&\xi\\
-\xi&0
\end{pmatrix}
:\ \xi\in\mathbf C
\right\}.
\]
Then the first-order pure-value mixed variations contain the full skew line:
\[
\mathfrak{so}_2(\mathbf C)\subset \operatorname{span}\{\widetilde{\dot N}_1\}.
\]
Equivalently, the first-order mixed family contains a nonzero skew direction.
\end{lemma}

\begin{proof}
Freeze the same-point data and vary only the phase gap:
\[
\Delta_m(s)\mapsto \Delta_m(s)+\varepsilon\,\delta\Delta(s),
\qquad
\delta\Delta(s)=\theta s^3+O(s^5),
\quad \theta\neq 0.
\]
Linearizing the mixed block formula in $\varepsilon$, the two off-diagonal
entries vary with opposite sign, while the diagonal entries do not contribute
at first odd order. More precisely,
\[
\delta N_{12}(s)=\frac{\theta}{\pi}s+O(s^3),
\qquad
\delta N_{21}(s)=-\frac{\theta}{\pi}s+O(s^3),
\]
up to the overall sign convention for $\theta$. Hence the first odd mixed
coefficient of this phase-gap variation is a nonzero element of
\[
\mathfrak{so}_2(\mathbf C).
\]
Whitening by $X_0$ is invertible, so the whitened first-order mixed family
also contains a nonzero skew element. Since $\mathfrak{so}_2(\mathbf C)$ is
one-dimensional, this is equivalent to
\[
\mathfrak{so}_2(\mathbf C)\subset \operatorname{span}\{\widetilde{\dot N}_1\}.
\]
\end{proof}

\begin{proposition}[Generic triviality of the first quotient order]
\label{prop:first-order-quotient-trivial}
The first-order pure-value family fills the full matrix space:
\[
V_{\val}^{(1)}=M_2(\mathbf C).
\]
Consequently
\[
\mathcal J_1/V_{\val}^{(1)}=0,
\]
so the generic leading quotient order is at least $3$.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:first-order-generator-whitened}, the first-order generator is
\[
\widetilde B_1
=
\widetilde{\dot N}_1
-\frac12\,\widetilde{\dot G}_{-,1}
-\frac12\,\widetilde{\dot G}_{+,1}.
\]
By Lemma~\ref{lem:first-order-same-point-span}, the same-point directions
$\widetilde{\dot G}_{-,1}$ and $\widetilde{\dot G}_{+,1}$ span the full
symmetric subspace $\operatorname{Sym}_2(\mathbf C)$. By
Lemma~\ref{lem:first-order-mixed-skew}, the mixed directions contain the skew
line
\[
\mathfrak{so}_2(\mathbf C).
\]
Therefore the image of the generator contains
\[
\operatorname{Sym}_2(\mathbf C)\oplus \mathfrak{so}_2(\mathbf C)=M_2(\mathbf C).
\]
Hence
\[
V_{\val}^{(1)}=M_2(\mathbf C),
\]
and so
\[
\mathcal J_1/V_{\val}^{(1)}=0.
\]
Thus the generic leading quotient order is at least $3$.
\end{proof}

\begin{remark}[Raw versus full value family]
\label{rem:raw-vs-full-value-family}
The first-order surjectivity statement concerns the full value family as it
appears in the three-input derivative
\[
D\mathcal W_{(\bg)}[\dot G_-,\dot N,\dot G_+].
\]
This is larger than the raw swap-odd one-pair slice obtained by tying the left
and right same-point variations together. In particular, at first order the
combined family $V_{\val}^{(1)}$ fills $M_2(\mathbf C)$, while the odd
coefficients of the raw corrected local block are constrained by additional
swap/parity structure. Thus the present notation
\[
V_{\val}^{(2j+1)}
\]
bundles together at least two logically distinct sources of ambiguity: raw
pure-value odd jets and additional normalization/basis-gauge directions. The
explicit finite-order model introduced later makes this split rigorous through
order $5$; outside that local model, the ambient notation
$V_{\val}^{(2j+1)}$ remains schematic.
\end{remark}

\begin{lemma}[Rigidity of the cubic scalar $B$]
\label{lem:B-rigidity}
Let $I$ be a connected parameter interval, and define
\[
B(h):=\frac{q(h)^2q'(h)}{4}-\frac{q'''(h)}{48}.
\]
Then the following are equivalent:
\begin{enumerate}
\item $B\equiv 0$ on $I$;
\item $q'''=12q^2q'$ on $I$;
\item there exists a constant $C_0\in \mathbf C$ such that
\[
q''=4q^3+C_0
\qquad\text{on }I.
\]
\end{enumerate}
In particular, the hypothesis $B\not\equiv 0$ is equivalent to excluding
the special cubic ODE $q''=4q^3+C_0$.
\end{lemma}

\begin{proof}
By definition,
\[
48\,B = 12q^2q' - q'''.
\]
Hence $B\equiv 0$ is equivalent to
\[
q'''=(4q^3)'.
\]
Integrating on the connected interval $I$ gives
\[
q''=4q^3+C_0
\]
for some constant $C_0\in \mathbf C$. The converse is immediate by
differentiation.
\end{proof}

\begin{proposition}[Generic cubic leading quotient order]
\label{prop:cubic-leading-order}
Let $I$ be a connected one-pair parameter interval, and let
$J_3^{\pair}(h)$ denote the cubic jet of the normalized one-pair family.

Assume:
\begin{enumerate}
\item the cubic value-family satisfies
\[
V_{\val}^{(3)}
\subset
\left\{
\begin{pmatrix}
0&*\\ *&0
\end{pmatrix}
\right\};
\]
\item the background same-point block is nondegenerate, so that the diagonal
entries of $X_0=G_0^{-1/2}$ satisfy $x_1\neq x_2$;
\item the scalar $v(h)$ is not identically zero on $I$;
\item $B(h)\not\equiv 0$ on $I$, equivalently, by
Lemma~\ref{lem:B-rigidity}, $q$ does not satisfy
\[
q''=4q^3+C_0
\]
identically on $I$.
\end{enumerate}

Define the cubic-generic region
\[
\mathcal U_{\mathrm{cub}}
:=
\{\,h\in I:\ v(h)B(h)\neq 0\,\}.
\]
Then $\mathcal U_{\mathrm{cub}}$ is open and dense in $I$, and for every
$h\in \mathcal U_{\mathrm{cub}}$,
\[
[J_3^{\pair}(h)]\neq 0
\quad\text{in}\quad
\mathcal J_3/V_{\val}^{(3)}.
\]

More precisely, the image of $J_3^{\pair}(h)$ in the cubic quotient has
nonzero diagonal-traceless component
\[
v(h)\,B(h)\,(x_1-x_2)
\begin{pmatrix}
1&0\\0&-1
\end{pmatrix}.
\]
Consequently,
\[
F_h(z)=v_0(h)z^3+v_1(h)z^5+\cdots,
\qquad
v_0(h):=[J_3^{\pair}(h)]\neq 0
\]
for $h\in \mathcal U_{\mathrm{cub}}$. Since the first quotient order is
generically trivial, the generic leading quotient order is therefore exactly
$3$ on $\mathcal U_{\mathrm{cub}}$.
\end{proposition}

\begin{proof}
By assumption,
\[
\operatorname{diag}J_3^{\pair}(h)
=
v(h)\,B(h)\,(x_1-x_2)
\begin{pmatrix}
1&0\\0&-1
\end{pmatrix}.
\]
Because $V_{\val}^{(3)}$ is confined to the off-diagonal sector, it cannot
cancel any nonzero diagonal component. Hence for every $h$ with
$v(h)B(h)(x_1-x_2)\neq 0$, the cubic quotient class
$[J_3^{\pair}(h)]$ is nonzero.

Since $x_1\neq x_2$ is fixed and both $v$ and $B$ are not identically
zero, the set $\mathcal U_{\mathrm{cub}}$ is nonempty; if the dependence on
$h$ is real-analytic, its complement is a proper analytic subset, hence
$\mathcal U_{\mathrm{cub}}$ is open and dense. Finally,
Proposition~\ref{prop:first-order-quotient-trivial} shows that the leading
quotient order is at least $3$, while the present argument shows that it is
equal to $3$ on $\mathcal U_{\mathrm{cub}}$.
\end{proof}

\begin{remark}[What is genuinely generic here]
\label{rem:cubic-leading-genericity}
The cubic-leading statement depends on three logically distinct inputs:
\begin{enumerate}
\item $x_1\neq x_2$, a background same-point nondegeneracy condition;
\item $v\not\equiv 0$, a one-pair nonfreezing condition;
\item exclusion of the special ODE $q''=4q^3+C_0$, equivalently
$B\not\equiv 0$.
\end{enumerate}
This separates the structural cubic mechanism from the residual quintic
bookkeeping needed later.
\end{remark}

\begin{definition}[Cubic leading line and first residual class]
\label{def:cubic-leading-line}
For $h\in \mathcal U_{\mathrm{cub}}$, the cubic quotient coefficient
\[
v_0(h)=[J_3^{\pair}(h)]
\]
is nonzero by Proposition~\ref{prop:cubic-leading-order}. Define the cubic
leading line by
\[
\ell_h:=\mathbf C\,v_0(h)\subset \Qabs.
\]
Let $v_1(h):=[J_5^{\pair}(h)]$ denote the quintic quotient coefficient.
Its image in the residual quotient
\[
\Qabs/\ell_h
\]
is denoted by
\[
\overline v_1(h)\in \Qabs/\ell_h.
\]
\end{definition}

\subsection{Normalization gauge at the first residual step}

The phrase ``value/gauge family'' bundles together two logically distinct
sources of ambiguity:

\begin{enumerate}
\item the \emph{pure value family}, recorded coefficientwise by the spaces
$
V_{\val}^{(2j+1)}\subset \mathcal J_{2j+1},
$
and

\item the \emph{normalization gauge}, consisting of even scalar
renormalizations and even jet-basis changes.
\end{enumerate}

For the first residual step it is useful to separate these two.

\begin{definition}[Normalization gauge]
\label{def:normalization-gauge}
Let $F(z)$ be a matrix-valued odd germ. The normalization gauge acts by
\[
F(z)\longmapsto a(z)\,P(z)\,F(z)\,P(z)^{-1},
\]
where
\[
a(z)=1+c_2 z^2+c_4 z^4+\cdots
\]
is an even scalar germ with $a(0)=1$, and
\[
P(z)=I+B_2 z^2+B_4 z^4+\cdots
\]
is an even $2\times 2$ matrix germ with $P(0)=I$.
\end{definition}

\begin{proposition}[First-residual transformation law]
\label{prop:first-residual-gauge-law}
Let
\[
F(z)=A_3 z^3+A_5 z^5+O(z^7)
\]
be an odd matrix germ, and let
\[
F^{\new}(z):=a(z)\,P(z)\,F(z)\,P(z)^{-1}
\]
with $a,P$ as in Definition~\ref{def:normalization-gauge}. Then
\[
A_3^{\new}=A_3,
\qquad
A_5^{\new}=A_5+c_2A_3+[B_2,A_3].
\]
\end{proposition}

\begin{proof}
Expand
\[
P(z)^{-1}=I-B_2 z^2+O(z^4).
\]
Then
\[
P(z)F(z)P(z)^{-1}
=
(I+B_2 z^2)\,(A_3 z^3+A_5 z^5)\,(I-B_2 z^2)+O(z^7),
\]
so
\[
P(z)F(z)P(z)^{-1}
=
A_3 z^3+\bigl(A_5+[B_2,A_3]\bigr)z^5+O(z^7).
\]
Multiplying by
\[
a(z)=1+c_2 z^2+O(z^4)
\]
gives
\[
F^{\new}(z)
=
A_3 z^3+\bigl(A_5+c_2A_3+[B_2,A_3]\bigr)z^5+O(z^7),
\]
as claimed.
\end{proof}

\begin{corollary}[Residual effect of normalization gauge]
\label{cor:first-residual-gauge-law}
Let $\ell:=\mathbf C A_3$. Under the normalization gauge,
the quintic coefficient changes by
\[
A_5 \longmapsto A_5 + c_2 A_3 + [B_2,A_3].
\]
Hence its class in the residual quotient modulo the leading line satisfies
\[
[A_5] \longmapsto [A_5+[B_2,A_3]]
\qquad\text{in}\qquad
\mathcal J_5/\ell.
\]
In particular, scalar renormalization is invisible in the first residual
quotient.
\end{corollary}

\begin{proof}
This is immediate from Proposition~\ref{prop:first-residual-gauge-law}, since
$c_2A_3\in \ell$.
\end{proof}

\begin{corollary}[Trace invariance under normalization gauge]
\label{cor:trace-invariant-under-normalization-gauge}
If $A_3$ is diagonal-traceless, then every commutator $[B_2,A_3]$ is
traceless. Consequently
\[
\operatorname{tr}(A_5^{\new})=\operatorname{tr}(A_5)
\]
for every normalization-gauge transform $F^{\new}$ of $F$.
\end{corollary}

\begin{proof}
The scalar renormalization term $c_2A_3$ is traceless because $A_3$ is.
The commutator term is traceless because
\[
\operatorname{tr}[B_2,A_3]=0.
\]
Hence Proposition~\ref{prop:first-residual-gauge-law} gives
\[
\operatorname{tr}(A_5^{\new})=\operatorname{tr}(A_5).
\]
\end{proof}

\begin{proposition}[Second-residual transformation law]
\label{prop:second-residual-gauge-law}
Let
\[
F(z)=A_3 z^3+A_5 z^5+A_7 z^7+O(z^9)
\]
be an odd matrix germ, and let
\[
F^{\new}(z):=a(z)\,P(z)\,F(z)\,P(z)^{-1}
\]
with $a,P$ as in Definition~\ref{def:normalization-gauge}. Then
\[
A_3^{\new}=A_3,
\qquad
A_5^{\new}=A_5+c_2A_3+[B_2,A_3],
\]
and the septic coefficient transforms by
\[
A_7^{\new}
=
A_7+c_2A_5+c_4A_3+[B_2,A_5]+[B_4,A_3]
+c_2[B_2,A_3]+A_3B_2^2-B_2A_3B_2.
\]
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:first-residual-gauge-law}, the formulas for
$A_3^{\new}$ and $A_5^{\new}$ are already known. It remains to compute the
$z^7$-coefficient.

Expand
\[
P(z)^{-1}=I-B_2 z^2+(B_2^2-B_4)z^4+O(z^6).
\]
Then
\[
P(z)F(z)P(z)^{-1}
=
(I+B_2 z^2+B_4 z^4)(A_3 z^3+A_5 z^5+A_7 z^7)
(I-B_2 z^2+(B_2^2-B_4)z^4)+O(z^9).
\]
Collecting the $z^7$-terms gives
\[
A_7+[B_2,A_5]+[B_4,A_3]+A_3B_2^2-B_2A_3B_2.
\]
Multiplying by
\[
a(z)=1+c_2 z^2+c_4 z^4+O(z^6)
\]
adds the scalar contributions
\[
c_2A_5+c_4A_3+c_2[B_2,A_3].
\]
Hence
\[
A_7^{\new}
=
A_7+c_2A_5+c_4A_3+[B_2,A_5]+[B_4,A_3]
+c_2[B_2,A_3]+A_3B_2^2-B_2A_3B_2,
\]
as claimed.
\end{proof}

\begin{lemma}[Quintic trace witness]
\label{lem:quintic-trace-witness}
Let $J_{5,K_1}(h)$ denote the $K_1$-transport contribution to the quintic
jet. At the trace level, the relevant contribution is
\[
\operatorname{tr}J_{5,K_1}(h)
=
\kappa(h)\,\operatorname{tr}\!\Bigl(
X_0JX_4(h)-X_4(h)JX_0
+
X_3(h)JX_1(h)-X_1(h)JX_3(h)
\Bigr),
\]
since
\[
\operatorname{tr}\bigl(X_2(h)JX_2(h)\bigr)=0
\]
for symmetric $X_2(h)$. Therefore
\[
\operatorname{tr}J_{5,K_1}(h)
=
-2\kappa(h)\Bigl((x_1-x_2)r(h)+\beta(h)(u(h)-w(h))+v(h)(\gamma(h)-\alpha(h))\Bigr),
\]
where $K_1=\kappa(h)J$, $v(h)$ is the off-diagonal part of $X_1(h)$,
and $\gamma(h)-\alpha(h)$ is the diagonal-traceless part of $X_3(h)$.

Moreover, the linear $G_3$-contribution to $\gamma(h)-\alpha(h)$ is
\[
(\gamma-\alpha)^{\lin}
=
\frac{1}{2\pi}\left[
x_1^3\frac{q'''}{24}
-
x_2^3\left(
\frac{q'''''}{576}
+\frac{q^2q'''}{96}
+\frac{qq'q''}{16}
+\frac{(q')^3}{48}
\right)
\right].
\]
Since
\[
v(h)=-\frac{1}{4\pi(s_1+s_2)}\,\eta_2(h),
\]
the product $v(h)(\gamma(h)-\alpha(h))^{\lin}$ contains the monomial
\[
\kappa(h)\,\eta_2(h)\,q'''''\!(h)
\]
with nonzero coefficient.
\end{lemma}

\begin{lemma}[Parity of the whitening expansion at a diagonal base]
\label{lem:whitening-parity}
Let
\[
G_0=\diag(\lambda_1,\lambda_2),
\qquad \lambda_1,\lambda_2>0,
\]
and let
\[
X(H):=(G_0+H)^{-1/2}
\]
for $H$ sufficiently small. Write
\[
E:=\left\{
\begin{pmatrix}
*&0\\0&*
\end{pmatrix}
\right\},
\qquad
O:=\left\{
\begin{pmatrix}
0&*\\ *&0
\end{pmatrix}
\right\}.
\]
Then every multilinear Taylor coefficient of $X(H)$ has definite matrix
parity: a coefficient depending on perturbation factors
$H_1,\dots,H_n$ lies in $E$ if an even number of the $H_j$ lie in
$O$, and lies in $O$ if an odd number of the $H_j$ lie in $O$.

In particular, diagonal input gives diagonal output at linear order, and a
bilinear coefficient with one diagonal and one off-diagonal input is
off-diagonal.
\end{lemma}

\begin{proof}
Use the holomorphic functional calculus
\[
(G_0+H)^{-1/2}
=
\frac{1}{2\pi i}\oint_{\Gamma} z^{-1/2}(zI-G_0-H)^{-1}\,dz,
\]
where $\Gamma$ encloses the spectrum of $G_0+H$. Expanding the resolvent,
\[
(zI-G_0-H)^{-1}
=
R(z)+R(z)HR(z)+R(z)HR(z)HR(z)+\cdots,
\]
with
\[
R(z):=(zI-G_0)^{-1},
\]
every factor $R(z)$ is diagonal because $G_0$ is diagonal. Hence the
matrix parity of each word
\[
R(z)H_{i_1}R(z)H_{i_2}\cdots R(z)H_{i_n}R(z)
\]
is exactly the parity of the product $H_{i_1}\cdots H_{i_n}$. Since
\[
E\cdot E\subset E,\qquad
E\cdot O\subset O,\qquad
O\cdot E\subset O,\qquad
O\cdot O\subset E,
\]
the parity rule follows. Integrating over $z$ preserves the subspaces
$E$ and $O$.
\end{proof}

\begin{lemma}[No-cancellation of the quintic trace witness]
\label{lem:no-cancellation-quintic-trace}
The monomial
\[
\kappa(h)\,\eta_2(h)\,q'''''\!(h)
\]
appearing in Lemma~\ref{lem:quintic-trace-witness} is not produced by any
other quintic contribution to $\operatorname{tr}J_5^{\pair}(h)$. More
precisely, on the graded slice corresponding to
\[
(K_1,\eta_2,q^{(5)}),
\]
the only contributing channels in
$\operatorname{tr}J_5^{\pair}(h)$ are
\[
-2\kappa(h)\,(x_1-x_2)r(h)
\qquad\text{and}\qquad
-2\kappa(h)\,v(h)\bigl(\gamma(h)-\alpha(h)\bigr),
\]
and their total coefficient of
$\kappa(h)\eta_2(h)q^{(5)}(h)$ is nonzero. Consequently
\[
\operatorname{tr}J_5^{\pair}(h)\not\equiv 0
\]
on the generic one-pair region.
\end{lemma}

\begin{proof}
Fix $h$ and isolate the graded slice
\[
\kappa(h)\,\eta_2(h)\,q^{(5)}(h).
\]

We first exclude all non-$K_1$ contributions. Same-point quintic terms
carry no $\kappa$-factor, so they cannot contribute. A $K_5$-transport
term leaves no same-point degree available, and a $K_3$-transport term
leaves only same-point degree $2$, whereas the factor $q^{(5)}(h)$
first appears in same-point degree $3$. Hence the target monomial can
occur only in the $K_1$-transport sector.

Now consider the same-point expansion. By the explicit formula
\[
G_{m,\pm}^{\corr}(s)
=
\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[.5ex]
\frac12 q'(t_\pm) & \frac1{12}(q''(t_\pm)+2q(t_\pm)^3)
\end{pmatrix},
\]
the factor $q^{(5)}(h)$ first appears only in the cubic same-point
coefficient $G_3$, and there only in the diagonal sector, namely through
the cubic Taylor term of the $(2,2)$-entry coming from $q''(t_\pm)$.
Therefore, by Lemma~\ref{lem:whitening-parity}, the linear
$q^{(5)}$-contribution to $X_3$ is diagonal. In particular it contributes
to $\gamma-\alpha$, but not to $\beta$.

Likewise, the $\eta_2(h)$-slice of $X_1(h)$ is off-diagonal, because
\[
v(h)=-\frac{1}{4\pi(s_1+s_2)}\,\eta_2(h).
\]
Applying Lemma~\ref{lem:whitening-parity} again, the mixed
$(\eta_2,q^{(5)})$-slice of $X_4$ is off-diagonal. Hence it contributes
to $r$, but not to the diagonal difference $u-w$.

It follows that on the graded slice
$(K_1,\eta_2,q^{(5)})$, the term
\[
-2\kappa(h)\,\beta(h)\bigl(u(h)-w(h)\bigr)
\]
does not contribute at all. Thus the only surviving $K_1$-channels are
\[
-2\kappa(h)\,(x_1-x_2)r(h)
\qquad\text{and}\qquad
-2\kappa(h)\,v(h)\bigl(\gamma(h)-\alpha(h)\bigr).
\]

To compute their combined coefficient, it suffices by multilinearity to
restrict to the two perturbation directions carrying the relevant tags:
an off-diagonal first-order perturbation $A$ for the $\eta_2$-slice and
a diagonal third-order perturbation $D$ for the $q^{(5)}$-slice.
Accordingly, write
\[
G_0=\diag(a^2,b^2),
\qquad
A=
\begin{pmatrix}
0&u\\u&0
\end{pmatrix},
\qquad
D=
\begin{pmatrix}
0&0\\0&d
\end{pmatrix},
\]
and expand
\[
X(\varepsilon,\delta):=(G_0+\varepsilon A+\delta D)^{-1/2}
=
X_0+\varepsilon U+\delta V+\varepsilon\delta W+O(\varepsilon^2,\delta^2).
\]
Solving the identity
\[
X(\varepsilon,\delta)\,(G_0+\varepsilon A+\delta D)\,X(\varepsilon,\delta)=I
\]
order by order gives
\[
U_{12}=-\frac{u}{ab(a+b)},
\qquad
V_{22}=-\frac{d}{2b^3},
\qquad
W_{12}=\frac{du(a+2b)}{2ab^3(a+b)^2}.
\]
Here $U_{12}$ is the $\eta_2$-slice of $v$, $V_{22}$ is the
$q^{(5)}$-slice of $\gamma-\alpha$, and $W_{12}$ is the mixed
$(\eta_2,q^{(5)})$-slice of $r$. Therefore the total coefficient of the
target slice inside
\[
(x_1-x_2)r+v(\gamma-\alpha)
\]
is
\[
\left(\frac1a-\frac1b\right)W_{12}+U_{12}V_{22}
=
\frac{du}{a^2b^2(a+b)^2},
\]
which is nonzero.

Thus the monomial
$\kappa(h)\eta_2(h)q^{(5)}(h)$ occurs in
$\operatorname{tr}J_5^{\pair}(h)$ with nonzero total coefficient and is not
canceled by any other quintic contribution. Hence
\[
\operatorname{tr}J_5^{\pair}(h)\not\equiv 0.
\]
\end{proof}

\subsection{Explicit finite-order model of the first residual quotient}

For the first residual step it is enough to work with an explicit finite-order
model through order $5$ on the cubic-generic region. In this range the explicit
model is not merely a proxy: Proposition~\ref{prop:finite-order-comparison-qabs}
canonically identifies it with the order-$\le 5$ truncation of the ambient
abstract quotient $\Qabs$ after passage to the cubic line.

Accordingly, the first residual quintic detector is now rigorous at the
finite-order ambient level. What is not addressed here is only a stronger
global identification for later uses of $\Qabs$ beyond order $5$ and beyond the
first residual layer.

\begin{definition}[Finite-order truncation of the ambient abstract quotient]
\label{def:qabs-order-five}
Fix $h\in \mathcal U_{\mathrm{cub}}$, and let $A_3(h)$ represent the cubic
leading line $\ell_h\subset \Qabs$.

Define the order-$\le 5$ truncation of the ambient abstract quotient at $h$
to be the quotient
\[
{\Qabs}_h^{(\le 5)}
:=
\frac{\mathbf C\,A_3(h)z^3\oplus \mathcal J_5 z^5}
{\bigl(V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}\bigr)z^5}.
\]
Equivalently, ${\Qabs}_h^{(\le 5)}$ is the cubic--quintic odd-germ quotient in
which the quintic ambiguity is generated exactly by the raw pure-value quintic
slice and the realized normalization-gauge shadows through order $5$.

Its first residual quotient is
\[
{\Qabs}_h^{(\le 5)}/\ell_h
\cong
\mathcal J_5/
\bigl(\mathbf C\,A_3(h)+V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}\bigr).
\]
\end{definition}

\begin{definition}[Swap involution on cubic--quintic germs]
\label{def:sigma-cubic-quintic}
Let
\[
J_0=
\begin{pmatrix}
0&1\\
1&0
\end{pmatrix}.
\]
For a truncated odd germ
\[
F(z)=A_3 z^3+A_5 z^5+O(z^7)
\]
define
\[
\Sigma(F)(z):=J_0\,F(-z)\,J_0
=
-\,J_0A_3J_0\,z^3
-\,J_0A_5J_0\,z^5
+O(z^7).
\]
Thus the induced involution on quintic coefficients is
\[
\Sigma_5(A):=-J_0AJ_0.
\]
\end{definition}

\begin{definition}[Cubic-normalized swap-symmetric raw corrected germ through order $5$]
\label{def:raw-corrected-germ-order-five}
Fix $h\in \mathcal U_{\mathrm{cub}}$, and choose a diagonal-traceless
matrix
\[
A_3(h)
\]
representing the cubic leading line $\ell_h$.

A cubic-normalized swap-symmetric raw corrected germ through order $5$ at
$h$ is a truncated odd germ of the form
\[
R_h(z)=A_3(h)z^3+A_5 z^5+O(z^7)
\]
obtained from the corrected one-pair local block by a cubic normalization that
preserves the swap symmetry inherited from symmetric placement.

Its raw pure-value quintic slice is the coefficient space
\[
V_{\mathrm{raw}}^{(5)}(h)
\]
consisting of all quintic coefficients $A_5$ arising in this way under pure
value deformations at the fixed parameter $h$.
\end{definition}

\begin{lemma}[Raw quintic slice is anti-fixed]
\label{lem:raw-quintic-slice-antifixed}
For every $h\in\mathcal U_{\mathrm{cub}}$,
\[
V_{\mathrm{raw}}^{(5)}(h)\subset
\{A\in M_2(\mathbf C):J_0AJ_0=-A\}.
\]
In particular,
\[
\operatorname{tr}\bigl(V_{\mathrm{raw}}^{(5)}(h)\bigr)=0.
\]
\end{lemma}

\begin{proof}
By Definition~\ref{def:raw-corrected-germ-order-five}, every cubic-normalized
raw corrected representative satisfies
\[
R_h(-z)=J_0\,R_h(z)\,J_0.
\]
Writing
\[
R_h(z)=A_3(h)z^3+A_5 z^5+O(z^7),
\]
coefficient comparison at order $z^5$ gives
\[
J_0A_5J_0=-A_5.
\]
Hence every $A_5\in V_{\mathrm{raw}}^{(5)}(h)$ is anti-fixed. If
\[
A=
\begin{pmatrix}
a&b\\
c&d
\end{pmatrix}
\]
satisfies $J_0AJ_0=-A$, then
\[
\begin{pmatrix}
d&c\\
b&a
\end{pmatrix}
=
\begin{pmatrix}
-a&-b\\
-c&-d
\end{pmatrix},
\]
so $d=-a$, and therefore $\operatorname{tr}(A)=0$.
\end{proof}

\begin{definition}[Quintic ambiguity space and explicit first residual quotient]
\label{def:finite-order-quotient-model}
For $h\in \mathcal U_{\mathrm{cub}}$, let $V_{\mathrm{raw}}^{(5)}(h)$ be
the raw pure-value quintic slice from
Definition~\ref{def:raw-corrected-germ-order-five}.

Define the normalization-gauge quintic shadow space $\mathcal N_h^{(5)}$ to
be the set of all differences
\[
\widetilde A_5-A_5
\]
arising from two cubic-normalized swap-symmetric raw corrected germs
\[
R_h(z)=A_3(h)z^3+A_5 z^5+O(z^7),
\qquad
\widetilde R_h(z)=A_3(h)z^3+\widetilde A_5 z^5+O(z^7),
\]
of the same raw corrected local object through order $5$, when those two
representatives are related by the allowed normalization gauge.

By Corollary~\ref{cor:first-residual-gauge-law}, every such shadow has the
form
\[
\widetilde A_5-A_5=c_2A_3(h)+[B_2,A_3(h)],
\]
but $\mathcal N_h^{(5)}$ is defined to consist only of the actually realized
gauge shadows.

Set
\[
V_{\mathrm{amb}}^{(5)}(h)
:=
V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}.
\]

Define the explicit first residual quotient by
\[
\mathcal R_h^{(5)}
:=
\mathcal J_5/
\bigl(\mathbf C\,A_3(h)+V_{\mathrm{amb}}^{(5)}(h)\bigr).
\]
\end{definition}

\begin{proposition}[Finite-order comparison theorem]
\label{prop:finite-order-comparison-qabs}
For each $h\in \mathcal U_{\mathrm{cub}}$, the order-$\le 5$ truncation of
the ambient abstract quotient and the explicit first residual model agree
canonically:
\[
{\Qabs}_h^{(\le 5)}/\ell_h
\;\cong\;
\mathcal R_h^{(5)}.
\]

Equivalently, after passing to the cubic-generic region and truncating through
order $5$, the first residual ambiguity in the ambient abstract quotient is
exactly the ambiguity built into
Definition~\ref{def:finite-order-quotient-model}.
\end{proposition}

\begin{proof}
By Definition~\ref{def:qabs-order-five},
\[
{\Qabs}_h^{(\le 5)}
=
\frac{\mathbf C\,A_3(h)z^3\oplus \mathcal J_5 z^5}
{\bigl(V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}\bigr)z^5}.
\]
Passing to the first residual quotient by the cubic line
$\ell_h=\mathbf C A_3(h)$ gives
\[
{\Qabs}_h^{(\le 5)}/\ell_h
\cong
\mathcal J_5/
\bigl(\mathbf C\,A_3(h)+V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}\bigr).
\]
By Definition~\ref{def:finite-order-quotient-model},
\[
V_{\mathrm{amb}}^{(5)}(h)
=
V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)},
\]
so the right-hand side is exactly
\[
\mathcal J_5/
\bigl(\mathbf C\,A_3(h)+V_{\mathrm{amb}}^{(5)}(h)\bigr)
=
\mathcal R_h^{(5)}.
\]
This is the claimed canonical identification.
\end{proof}

\begin{lemma}[Gauge shadows are anti-fixed]
\label{lem:gauge-shadows-antifixed}
For every $h\in\mathcal U_{\mathrm{cub}}$,
\[
\mathcal N_h^{(5)}\subset
\{A\in M_2(\mathbf C):J_0AJ_0=-A\}.
\]
In particular,
\[
\operatorname{tr}\bigl(\mathcal N_h^{(5)}\bigr)=0.
\]
\end{lemma}

\begin{proof}
Let
\[
R_h(z)=A_3(h)z^3+A_5 z^5+O(z^7),
\qquad
\widetilde R_h(z)=A_3(h)z^3+\widetilde A_5 z^5+O(z^7)
\]
be two cubic-normalized swap-symmetric representatives of the same raw
corrected local object through order $5$, related by the allowed
normalization gauge. By Definition~\ref{def:raw-corrected-germ-order-five},
both satisfy
\[
R_h(-z)=J_0R_h(z)J_0,
\qquad
\widetilde R_h(-z)=J_0\widetilde R_h(z)J_0.
\]
Comparing coefficients at order $z^5$ gives
\[
J_0A_5J_0=-A_5,
\qquad
J_0\widetilde A_5J_0=-\widetilde A_5.
\]
Subtracting,
\[
J_0(\widetilde A_5-A_5)J_0=-(\widetilde A_5-A_5).
\]
Since $\widetilde A_5-A_5\in \mathcal N_h^{(5)}$ by
Definition~\ref{def:finite-order-quotient-model}, every gauge shadow is
anti-fixed. Tracelessness follows as in
Lemma~\ref{lem:raw-quintic-slice-antifixed}.
\end{proof}

\begin{proposition}[Trace-free quintic ambiguity in the explicit finite-order model]
\label{prop:sigma-stability-quintic-ambiguity}
For every $h\in \mathcal U_{\mathrm{cub}}$,
\[
V_{\mathrm{amb}}^{(5)}(h)\subset
\{A\in M_2(\mathbf C):J_0AJ_0=-A\}.
\]
Equivalently, the involution $\Sigma_5$ preserves the quintic ambiguity
space and acts trivially on it.

In particular,
\[
\operatorname{tr}\bigl(V_{\mathrm{amb}}^{(5)}(h)\bigr)=0.
\]
\end{proposition}

\begin{proof}
Combine Lemma~\ref{lem:raw-quintic-slice-antifixed} and
Lemma~\ref{lem:gauge-shadows-antifixed}; by
Definition~\ref{def:finite-order-quotient-model},
\[
V_{\mathrm{amb}}^{(5)}(h)
=
V_{\mathrm{raw}}^{(5)}(h)+\mathcal N_h^{(5)}.
\]
\end{proof}

\begin{corollary}[Trace descends on the explicit first residual quotient]
\label{cor:trace-descends-explicit-first-residual}
For every $h\in \mathcal U_{\mathrm{cub}}$, trace annihilates
\[
\mathbf C\,A_3(h)+V_{\mathrm{amb}}^{(5)}(h).
\]
Hence trace descends to a well-defined linear functional
\[
\tau_h:\mathcal R_h^{(5)}\to \mathbf C.
\]
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:sigma-stability-quintic-ambiguity}, trace vanishes on
$V_{\mathrm{amb}}^{(5)}(h)$. It also vanishes on $\mathbf C\,A_3(h)$
because $A_3(h)$ is diagonal-traceless.
\end{proof}

\begin{proposition}[Generic first residual nonvanishing in the explicit finite-order model]
\label{prop:first-residual-class-generic}
There exists an open dense subset
\[
\mathcal U_{\mathrm{res}}\subset \mathcal U_{\mathrm{cub}}
\]
such that
\[
\overline v_1(h)\neq 0
\qquad\text{in }\mathcal R_h^{(5)}
\]
for every $h\in \mathcal U_{\mathrm{res}}$.

Hence the one-pair quotient odd germ is not projectively constant on
$\mathcal U_{\mathrm{res}}$ at the explicit first residual level.
\end{proposition}

\begin{proof}
By Corollary~\ref{cor:trace-descends-explicit-first-residual}, trace defines a
linear functional
\[
\tau_h:\mathcal R_h^{(5)}\to\mathbf C.
\]
By Lemma~\ref{lem:no-cancellation-quintic-trace},
\[
\operatorname{tr}J_5^{\pair}(h)\not\equiv 0
\]
on the cubic-generic region. Hence there is an open dense subset
\[
\mathcal U_{\mathrm{res}}\subset \mathcal U_{\mathrm{cub}}
\]
on which
\[
\operatorname{tr}J_5^{\pair}(h)\neq 0.
\]
For such $h$,
\[
\tau_h(\overline v_1(h))
=
\operatorname{tr}J_5^{\pair}(h)\neq 0,
\]
so $\overline v_1(h)\neq 0$ in $\mathcal R_h^{(5)}$.
\end{proof}

\begin{remark}[Status of the explicit first residual model]
\label{rem:status-explicit-first-residual-model}
The first residual step is now closed at the finite-order ambient level.
Indeed, Proposition~\ref{prop:finite-order-comparison-qabs} identifies the
explicit quotient $\mathcal R_h^{(5)}$ canonically with the order-$\le 5$
truncation of the ambient abstract quotient $\Qabs$ modulo the cubic line on
the cubic-generic region.

Thus the remaining issue is no longer a finite-order comparison theorem for
the first residual layer. What remains, if one wants a stronger global ambient identification, is a
separate theorem showing that later uses of $\Qabs$ beyond order $5$ do not
introduce any new ambiguity relevant to the downstream multi-pair and global
arguments.
\end{remark}

\begin{remark}[Beyond the first residual trace]
\label{rem:beyond-first-residual-trace}
The quintic trace is the first scalar residual detector, but it is not the end
of the one-pair local structure. The later fixed-sector refinement
$
A_5^{\mathfrak f},A_7^{\mathfrak f},\Delta_7
$
indicates that the residual germ carries further geometric information beyond
the first trace channel.
\end{remark}

\subsection{Fixed-sector refinement at quintic and septic order}

The trace witness at quintic order suggests a more structured refinement of the
one-pair residual germ than the trace alone records. For bookkeeping purposes,
it is convenient to decompose the quintic and septic coefficients into fixed and
anti-fixed parts with respect to the involution
\[
\iota(A):=J_0AJ_0,
\qquad
J_0=
\begin{pmatrix}
0&1\\
1&0
\end{pmatrix}.
\]

Write
\[
\pi_{\mathfrak f}(A):=\frac12(A+J_0AJ_0),
\qquad
\pi_{\mathfrak a}(A):=\frac12(A-J_0AJ_0).
\]
Then
\[
\mathfrak f=\operatorname{span}\{I,S\},
\qquad
\mathfrak a=\operatorname{span}\{D,J\},
\]
where
\[
I=
\begin{pmatrix}
1&0\\0&1
\end{pmatrix},
\quad
S=
\begin{pmatrix}
0&1\\1&0
\end{pmatrix},
\quad
D=
\begin{pmatrix}
1&0\\0&-1
\end{pmatrix},
\quad
J=
\begin{pmatrix}
0&-1\\1&0
\end{pmatrix}.
\]

\begin{definition}[Fixed-sector quintic and septic coefficients]
\label{def:fixed-sector-quintic-septic}
Let
\[
F_h(z)=A_3(h)z^3+A_5(h)z^5+A_7(h)z^7+\cdots
\]
denote the normalized one-pair quotient odd germ on the cubic-generic region.
Its fixed-sector quintic and septic coefficients are defined by
\[
A_5^{\mathfrak f}(h):=\pi_{\mathfrak f}(A_5(h)),
\qquad
A_7^{\mathfrak f}(h):=\pi_{\mathfrak f}(A_7(h)).
\]
Write
\[
A_5^{\mathfrak f}(h)=u_5(h)\,I+v_5(h)\,S,
\qquad
A_7^{\mathfrak f}(h)=u_7(h)\,I+v_7(h)\,S.
\]
\end{definition}

\begin{definition}[Second residual determinant]
\label{def:second-residual-determinant}
On the cubic-generic region, define
\[
\Delta_7(h):=u_7(h)v_5(h)-u_5(h)v_7(h).
\]
\end{definition}

\begin{remark}[Interpretation]
\label{rem:fixed-sector-residual-package}
The quintic fixed-sector vector $A_5^{\mathfrak f}(h)$ refines the first
residual data beyond the trace detector alone, and the determinant
$\Delta_7(h)$ records the next residual quotient at septic order. In the
working notes, these form the first two nontrivial layers of a one-pair
residual package:
\[
c(h),\qquad A_5^{\mathfrak f}(h),\qquad \Delta_7(h).
\]
The current draft now records explicit coefficient formulas for the quintic
commutator contribution and the septic $K_1$-transport contribution in the
existing notation $(u,v,w,\alpha,\beta,\gamma,r,\dots)$. The canonical
order-$7$ fixed-sector content is the quotient class
\[
[A_7^{\mathfrak f}] \in \mathfrak f/\mathbf C A_5^{\mathfrak f},
\]
equivalently the second residual determinant
\[
\Delta_7=u_7v_5-u_5v_7.
\]
What remains non-unique is only the raw representative pair $(u_7,v_7)$,
which is defined only up to the one-dimensional septic gauge ambiguity along
the quintic fixed-sector line $\mathbf C A_5^{\mathfrak f}$. Thus the later
geometry should be formulated in terms of the canonical quotient-level order-$7$
data $[A_7^{\mathfrak f}]$ and $\Delta_7$, rather than a uniquely chosen
raw pair $(u_7,v_7)$. At the canonical level, these are the natural variables
for the geometric reformulation of the multi-pair problem; raw representatives
$(u_7,v_7)$ may be chosen locally by gauge-fixing when convenient, but are
not themselves canonical.
\end{remark}

\begin{proposition}[Projected septic gauge law]
\label{prop:projected-septic-gauge-law}
Assume the normalization gauge is symmetry-preserving in the sense that
\[
B_2,B_4\in \mathfrak f,
\qquad
A_3\in \mathfrak a,
\]
with
\[
\mathfrak f=\operatorname{span}\{I,S\},
\qquad
\mathfrak a=\operatorname{span}\{D,J\}.
\]
Then the fixed-sector septic coefficient satisfies
\[
(A_7^{\mathfrak f})^{\new}=A_7^{\mathfrak f}+c_2A_5^{\mathfrak f}.
\]
Equivalently, the septic fixed-sector ambiguity is one-dimensional and lies
along the quintic fixed-sector line.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:second-residual-gauge-law},
\[
A_7^{\new}
=
A_7+c_2A_5+c_4A_3+[B_2,A_5]+[B_4,A_3]
+c_2[B_2,A_3]+A_3B_2^2-B_2A_3B_2.
\]
Apply the fixed-sector projection $\pi_{\mathfrak f}$ term by term.

Since $A_3\in\mathfrak a$, one has
\[
\pi_{\mathfrak f}(c_4A_3)=0.
\]
Because $B_4\in\mathfrak f$ and $A_3\in\mathfrak a$,
\[
[B_4,A_3]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a,
\]
so
\[
\pi_{\mathfrak f}[B_4,A_3]=0.
\]
Likewise,
\[
[B_2,A_3]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a,
\]
hence
\[
\pi_{\mathfrak f}\bigl(c_2[B_2,A_3]\bigr)=0.
\]

Now decompose
\[
A_5=A_5^{\mathfrak f}+A_5^{\mathfrak a}.
\]
Since $\mathfrak f=\operatorname{span}\{I,S\}$ is abelian,
\[
[B_2,A_5^{\mathfrak f}]=0.
\]
And since $B_2\in\mathfrak f$ and $A_5^{\mathfrak a}\in\mathfrak a$,
\[
[B_2,A_5^{\mathfrak a}]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a,
\]
so
\[
\pi_{\mathfrak f}[B_2,A_5]=0.
\]

Finally, $B_2\in\mathfrak f$ implies $B_2^2\in\mathfrak f$. Therefore
\[
A_3B_2^2\in\mathfrak a\mathfrak f\subset\mathfrak a,
\qquad
B_2A_3B_2\in\mathfrak f\mathfrak a\mathfrak f\subset\mathfrak a,
\]
and hence
\[
\pi_{\mathfrak f}(A_3B_2^2-B_2A_3B_2)=0.
\]

Thus the only term surviving fixed projection is
\[
c_2A_5^{\mathfrak f},
\]
and we conclude
\[
(A_7^{\mathfrak f})^{\new}=A_7^{\mathfrak f}+c_2A_5^{\mathfrak f}.
\qedhere
\]
\end{proof}

\begin{corollary}[Gauge invariance of the second residual determinant]
\label{cor:delta7-gauge-invariant}
Under a symmetry-preserving normalization gauge, the scalar
\[
\Delta_7=u_7v_5-u_5v_7
\]
is invariant.
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:projected-septic-gauge-law},
\[
(A_7^{\mathfrak f})^{\new}=A_7^{\mathfrak f}+c_2A_5^{\mathfrak f}.
\]
Writing
\[
A_5^{\mathfrak f}=u_5I+v_5S,
\qquad
A_7^{\mathfrak f}=u_7I+v_7S,
\]
the new septic pair is
\[
(u_7^{\new},v_7^{\new})=(u_7,v_7)+c_2(u_5,v_5).
\]
Therefore
\[
\Delta_7^{\new}
=
(u_7+c_2u_5)v_5-u_5(v_7+c_2v_5)
=
u_7v_5-u_5v_7
=
\Delta_7.
\]
\end{proof}

\begin{definition}[Septic normalization-shadow sectors]
\label{def:septic-shadow-sectors}
In the notation of Proposition~\ref{prop:second-residual-gauge-law}, define
the order-$2$ and order-$4$ septic normalization-shadow sectors by
\[
A_{7,K_5}:=c_2A_5+[B_2,A_5],
\]
and
\[
A_{7,K_3}:=
c_4A_3+[B_4,A_3]+c_2[B_2,A_3]+A_3B_2^2-B_2A_3B_2.
\]
Then the exact septic transformation law may be written
\[
A_7^{\new}=A_7+A_{7,K_5}+A_{7,K_3}.
\]
When the normalization gauge is symmetry-preserving, these are the septic
$K_5$- and $K_3$-transport shadow sectors.
\end{definition}

\begin{proposition}[Projected septic $K_5$-shadow law]
\label{prop:projected-k5-shadow-law}
Assume the normalization gauge is symmetry-preserving in the sense of
Proposition~\ref{prop:projected-septic-gauge-law}. Then
\[
A_{7,K_5}^{\mathfrak f}=c_2A_5^{\mathfrak f}.
\]
In particular,
\[
A_{7,K_5}^{\mathfrak f}\in \mathbf C\,A_5^{\mathfrak f}.
\]
\end{proposition}

\begin{proof}
By Definition~\ref{def:septic-shadow-sectors},
\[
A_{7,K_5}=c_2A_5+[B_2,A_5].
\]
Apply the fixed-sector projection $\pi_{\mathfrak f}$. Decompose
\[
A_5=A_5^{\mathfrak f}+A_5^{\mathfrak a}.
\]
Since $\mathfrak f=\operatorname{span}\{I,S\}$ is abelian,
\[
[B_2,A_5^{\mathfrak f}]=0.
\]
And since $B_2\in\mathfrak f$ and $A_5^{\mathfrak a}\in\mathfrak a$,
\[
[B_2,A_5^{\mathfrak a}]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a,
\]
so its fixed-sector projection vanishes. Therefore
\[
A_{7,K_5}^{\mathfrak f}
=
\pi_{\mathfrak f}(c_2A_5+[B_2,A_5])
=
c_2A_5^{\mathfrak f}.
\qedhere
\]
\end{proof}

\begin{proposition}[Projected septic $K_3$-shadow vanishing]
\label{prop:projected-k3-shadow-vanishing}
Assume the normalization gauge is symmetry-preserving in the sense of
Proposition~\ref{prop:projected-septic-gauge-law}. Then
\[
A_{7,K_3}^{\mathfrak f}=0.
\]
\end{proposition}

\begin{proof}
By Definition~\ref{def:septic-shadow-sectors},
\[
A_{7,K_3}
=
c_4A_3+[B_4,A_3]+c_2[B_2,A_3]+A_3B_2^2-B_2A_3B_2.
\]
Since $A_3\in\mathfrak a$, one has
\[
c_4A_3\in\mathfrak a.
\]
Because $B_4\in\mathfrak f$ and $A_3\in\mathfrak a$,
\[
[B_4,A_3]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a.
\]
Likewise,
\[
[B_2,A_3]\in[\mathfrak f,\mathfrak a]\subset\mathfrak a,
\]
hence
\[
c_2[B_2,A_3]\in\mathfrak a.
\]
Finally, $B_2\in\mathfrak f$ implies $B_2^2\in\mathfrak f$, so
\[
A_3B_2^2\in\mathfrak a\mathfrak f\subset\mathfrak a,
\qquad
B_2A_3B_2\in\mathfrak f\mathfrak a\mathfrak f\subset\mathfrak a.
\]
Thus every term of $A_{7,K_3}$ is anti-fixed, and therefore
\[
A_{7,K_3}^{\mathfrak f}=\pi_{\mathfrak f}(A_{7,K_3})=0.
\qedhere
\]
\end{proof}

\begin{remark}[Interpretation of the septic shadow sectors]
\label{rem:septic-shadow-interpretation}
Propositions~\ref{prop:projected-k5-shadow-law} and
\ref{prop:projected-k3-shadow-vanishing} show that the lower-order
normalization shadows at septic order contribute no new canonical fixed-sector
information beyond the already-known quintic line
$\mathbf C A_5^{\mathfrak f}$.
\end{remark}

\begin{proposition}[Explicit fixed-sector formulas at quintic order]
\label{prop:explicit-quintic-fixed-sector}
Write
\[
X_1=
\begin{pmatrix}
u&v\\
v&w
\end{pmatrix},
\qquad
X_3=
\begin{pmatrix}
\alpha&\beta\\
\beta&\gamma
\end{pmatrix}.
\]
Then the fixed-sector part of the basic quintic commutator channel
\[
X_3JX_1-X_1JX_3
\]
is
\[
\pi_{\mathfrak f}(X_3JX_1-X_1JX_3)
=
\bigl(v(\gamma-\alpha)+\beta(u-w)\bigr)I
+
(\gamma u-\alpha w)S.
\]
Consequently, for the quintic fixed-sector coefficient
\[
A_5^{\mathfrak f}(h)=u_5(h)\,I+v_5(h)\,S,
\]
the commutator-type contribution is explicitly
\[
u_5^{(\mathrm{comm})}
=
v(\gamma-\alpha)+\beta(u-w),
\qquad
v_5^{(\mathrm{comm})}
=
\gamma u-\alpha w.
\]
\end{proposition}

\begin{proof}
A direct computation gives
\[
X_3JX_1-X_1JX_3
=
\begin{pmatrix}
-2\alpha v+2\beta u & -\alpha w+\gamma u\\[.5ex]
-\alpha w+\gamma u & -2\beta w+2\gamma v
\end{pmatrix}.
\]
The fixed-sector projection of a symmetric matrix
\[
\begin{pmatrix}
A&B\\
B&C
\end{pmatrix}
\]
is
\[
\pi_{\mathfrak f}
\begin{pmatrix}
A&B\\
B&C
\end{pmatrix}
=
\frac{A+C}{2}\,I+B\,S.
\]
Applying this to the displayed matrix gives
\[
\pi_{\mathfrak f}(X_3JX_1-X_1JX_3)
=
\frac{(-2\alpha v+2\beta u)+(-2\beta w+2\gamma v)}{2}\,I
+
(\gamma u-\alpha w)S,
\]
which simplifies to
\[
\bigl(v(\gamma-\alpha)+\beta(u-w)\bigr)I
+
(\gamma u-\alpha w)S.
\]
\end{proof}

\begin{proposition}[Explicit septic $K_1$-transport fixed-sector formulas]
\label{prop:explicit-septic-k1-fixed-sector}
Write
\[
X_0=\diag(x_1,x_2),
\qquad
X_1=
\begin{pmatrix}
u&v\\
v&w
\end{pmatrix},
\qquad
X_2=
\begin{pmatrix}
a&b\\
b&c
\end{pmatrix},
\]
\[
X_4=
\begin{pmatrix}
p&r\\
r&s
\end{pmatrix},
\qquad
X_5=
\begin{pmatrix}
\alpha_5&\beta_5\\
\beta_5&\gamma_5
\end{pmatrix},
\qquad
X_6=
\begin{pmatrix}
\mu_6&\nu_6\\
\nu_6&\lambda_6
\end{pmatrix}.
\]
Then the fixed-sector parts of the three septic $K_1$-transport channels are
\[
\pi_{\mathfrak f}(X_5JX_1-X_1JX_5)
=
\bigl(\beta_5(u-w)+v(\gamma_5-\alpha_5)\bigr)I
+
(\gamma_5u-\alpha_5w)S,
\]
\[
\pi_{\mathfrak f}(X_2JX_4-X_4JX_2)
=
\bigl(b(p-s)+r(c-a)\bigr)I
+
(cp-as)S,
\]
and
\[
\pi_{\mathfrak f}(X_0JX_6-X_6JX_0)
=
(x_2-x_1)\nu_6\,I
+
(x_2\mu_6-x_1\lambda_6)S.
\]

Consequently, if the septic $K_1$-transport fixed-sector coefficient is
written
\[
A_{7,K_1}^{\mathfrak f}(h)=u_{7,K_1}(h)\,I+v_{7,K_1}(h)\,S,
\]
then
\[
u_{7,K_1}
=
\kappa\Bigl(
(x_2-x_1)\nu_6
+
\beta_5(u-w)+v(\gamma_5-\alpha_5)
+
b(p-s)+r(c-a)
\Bigr),
\]
\[
v_{7,K_1}
=
\kappa\Bigl(
x_2\mu_6-x_1\lambda_6
+
\gamma_5u-\alpha_5w
+
cp-as
\Bigr).
\]
\end{proposition}

\begin{proof}
For two symmetric matrices
\[
X=
\begin{pmatrix}
a&b\\
b&c
\end{pmatrix},
\qquad
Y=
\begin{pmatrix}
p&q\\
q&r
\end{pmatrix},
\]
a direct calculation gives
\[
XJY-YJX
=
\begin{pmatrix}
-2aq+2bp & -ar+cp\\
-ar+cp & -2br+2cq
\end{pmatrix}.
\]
Taking fixed-sector projection yields
\[
\pi_{\mathfrak f}(XJY-YJX)
=
\bigl(b(p-r)+q(c-a)\bigr)I
+
(cp-ar)S.
\]
Applying this formula to $(X,Y)=(X_5,X_1)$ and $(X,Y)=(X_2,X_4)$ gives the
first two displayed identities.

For the $X_0/X_6$ channel, a direct multiplication gives
\[
X_0JX_6-X_6JX_0
=
\begin{pmatrix}
-2x_1\nu_6 & -x_1\lambda_6+x_2\mu_6\\
-x_1\lambda_6+x_2\mu_6 & 2x_2\nu_6
\end{pmatrix},
\]
whose fixed-sector part is
\[
(x_2-x_1)\nu_6\,I
+
(x_2\mu_6-x_1\lambda_6)S.
\]
Summing the three channels gives the stated formulas for
$u_{7,K_1}$ and $v_{7,K_1}$.
\end{proof}

\begin{definition}[Septic $K_1$-residual determinant]
\label{def:delta7-k1}
If
\[
A_{7,K_1}^{\mathfrak f}(h)=u_{7,K_1}(h)\,I+v_{7,K_1}(h)\,S,
\]
define the corresponding septic $K_1$-residual determinant by
\[
\Delta_{7,K_1}(h):=u_{7,K_1}(h)v_5(h)-u_5(h)v_{7,K_1}(h).
\]
\end{definition}

\begin{corollary}[Direct $q^{(7)}$-driven septic slice]
\label{cor:direct-q7-septic-slice}
On the direct linear $q^{(7)}$-driven slice, the septic $K_1$-transport
fixed-sector contribution is $I$-directional. More precisely,
\[
v_{7,K_1}^{(q^{(7)})}=0,
\]
and
\[
u_{7,K_1}^{(q^{(7)})}
=
\kappa\Bigl(
(x_2-x_1)\nu_6^{(q^{(7)})}
+
v\,(\gamma_5-\alpha_5)^{(q^{(7)})}
\Bigr),
\]
so in particular
\[
\Delta_7^{(q^{(7)})}=u_7^{(q^{(7)})}v_5.
\]
\end{corollary}

\begin{proof}
On the direct $q^{(7)}$-driven slice, the linear $X_5$-input is diagonal,
hence
\[
\beta_5^{(q^{(7)})}=0.
\]
The mixed $X_6$-slice is off-diagonal on this grading, so
\[
\mu_6^{(q^{(7)})}=\lambda_6^{(q^{(7)})}=0.
\]
Moreover the $X_2/X_4$-channel does not lie on the pure
$(K_1,\eta_2,q^{(7)})$-slice. Therefore the $S$-component vanishes and the
displayed formula for $u_{7,K_1}^{(q^{(7)})}$ follows from
Proposition~\ref{prop:explicit-septic-k1-fixed-sector}. Since
\[
\Delta_7=u_7v_5-u_5v_7,
\]
the direct $q^{(7)}$-slice satisfies
\[
\Delta_7^{(q^{(7)})}=u_7^{(q^{(7)})}v_5.
\qedhere
\]
\end{proof}

\begin{proposition}[Noncancellation of the direct septic $K_1$ witness]
\label{prop:direct-q7-k1-witness-nonzero}
On the graded slice
\[
(K_1,\eta_2,q^{(7)}),
\]
the only contributing channels to
\[
u_{7,K_1}^{(q^{(7)})}
\]
are
\[
\kappa(x_2-x_1)\nu_6^{(q^{(7)})}
\qquad\text{and}\qquad
\kappa\,v(\gamma_5-\alpha_5)^{(q^{(7)})},
\]
and their total coefficient of the monomial
\[
\kappa(h)\,\eta_2(h)\,q^{(7)}(h)
\]
is nonzero. Consequently,
\[
u_{7,K_1}^{(q^{(7)})}(h)\not\equiv 0
\]
on the generic one-pair region.
\end{proposition}

\begin{proof}
Fix $h$ and isolate the graded slice
\[
\kappa(h)\,\eta_2(h)\,q^{(7)}(h).
\]

By Corollary~\ref{cor:direct-q7-septic-slice}, the direct $q^{(7)}$-driven
slice is $I$-directional and is given by
\[
u_{7,K_1}^{(q^{(7)})}
=
\kappa\Bigl(
(x_2-x_1)\nu_6^{(q^{(7)})}
+
v(\gamma_5-\alpha_5)^{(q^{(7)})}
\Bigr).
\]
Thus it remains only to show that the two displayed channels do not cancel.

Now consider the same-point expansion. By the explicit formula
\[
G_{m,\pm}^{\corr}(s)
=
\frac1\pi
\begin{pmatrix}
2q(t_\pm) & \frac12 q'(t_\pm)\\[.5ex]
\frac12 q'(t_\pm) & \frac1{12}(q''(t_\pm)+2q(t_\pm)^3)
\end{pmatrix},
\]
the factor $q^{(7)}(h)$ first appears only in the quintic same-point
coefficient $G_5$, and there only in the diagonal sector, namely through
the quintic Taylor term of the $(2,2)$-entry coming from $q''(t_\pm)$.
Therefore, by Lemma~\ref{lem:whitening-parity}, the linear
$q^{(7)}$-contribution to $X_5$ is diagonal. In particular it contributes
to $\gamma_5-\alpha_5$, but not to $\beta_5$.

Likewise, the $\eta_2(h)$-slice of $X_1(h)$ is off-diagonal, because
\[
v(h)=-\frac{1}{4\pi(s_1+s_2)}\,\eta_2(h).
\]
Applying Lemma~\ref{lem:whitening-parity} again, the mixed
$(\eta_2,q^{(7)})$-slice of $X_6$ is off-diagonal. Hence it contributes
to $\nu_6$, but not to $\mu_6$ or $\lambda_6$.

Thus the only contributing channels on the graded slice
\[
(K_1,\eta_2,q^{(7)})
\]
are exactly
\[
\kappa(x_2-x_1)\nu_6^{(q^{(7)})}
\qquad\text{and}\qquad
\kappa\,v(\gamma_5-\alpha_5)^{(q^{(7)})}.
\]

To compute their combined coefficient, it suffices by multilinearity to
restrict to the two perturbation directions carrying the relevant tags:
an off-diagonal first-order perturbation $A$ for the $\eta_2$-slice and
a diagonal fifth-order perturbation $D$ for the $q^{(7)}$-slice.
Accordingly, write
\[
G_0=\diag(a^2,b^2),
\qquad
A=
\begin{pmatrix}
0&u\\u&0
\end{pmatrix},
\qquad
D=
\begin{pmatrix}
0&0\\0&d
\end{pmatrix},
\]
and expand
\[
X(\varepsilon,\delta):=(G_0+\varepsilon A+\delta D)^{-1/2}
=
X_0+\varepsilon U+\delta V+\varepsilon\delta W+O(\varepsilon^2,\delta^2).
\]
Solving the identity
\[
X(\varepsilon,\delta)\,(G_0+\varepsilon A+\delta D)\,X(\varepsilon,\delta)=I
\]
order by order gives
\[
U_{12}=-\frac{u}{ab(a+b)},
\qquad
V_{22}=-\frac{d}{2b^3},
\qquad
W_{12}=\frac{du(a+2b)}{2ab^3(a+b)^2}.
\]
Here $U_{12}$ is the $\eta_2$-slice of $v$, $V_{22}$ is the
$q^{(7)}$-slice of $\gamma_5-\alpha_5$, and $W_{12}$ is the mixed
$(\eta_2,q^{(7)})$-slice of $\nu_6$. Therefore the total coefficient of the
target slice inside
\[
(x_2-x_1)\nu_6+v(\gamma_5-\alpha_5)
\]
is
\[
\left(\frac1a-\frac1b\right)W_{12}+U_{12}V_{22}
=
\frac{du}{a^2b^2(a+b)^2},
\]
which is nonzero.

Thus the monomial
\[
\kappa(h)\,\eta_2(h)\,q^{(7)}(h)
\]
occurs in $u_{7,K_1}^{(q^{(7)})}(h)$ with nonzero total coefficient, so
\[
u_{7,K_1}^{(q^{(7)})}(h)\not\equiv 0.
\]
\end{proof}

\begin{remark}[Septic $K_1$ trace target]
\label{rem:septic-k1-trace-target}
At the graded level, the septic $K_1$-transport channel is the first odd
transport sector capable of coupling the new same-point $q^{(7)}$-slice into
the fixed-sector septic residual. In particular, the expected highest new
contribution to the septic determinant is carried by the $K_1$-channel, in
parallel with the earlier quintic trace witness at order $5$.
\end{remark}

\begin{lemma}[Parity elimination of the pure same-point septic sector]
\label{lem:parity-elimination-pure-septic}
Let $t_\pm=h\pm s/2$, and let the odd two-point germ be defined as the odd
part under the involution
\[
s\longmapsto -s
\qquad
(\text{equivalently }t_+\leftrightarrow t_-).
\]
Let $A_{7,\mathrm{pure}}$ denote the pure same-point septic sector, i.e. the
septic contribution built only from the same-point blocks and their whitening,
with no transport factor coming from the ordered pair $(t_+,t_-)$.

Then $A_{7,\mathrm{pure}}$ is even in $s$, hence vanishes in the odd
two-point germ. In particular,
\[
A_{7,\mathrm{pure}}=0
\quad\text{in the odd germ,}
\qquad
A_{7,\mathrm{pure}}^{\mathfrak f}=0.
\]
Consequently, pure same-point septic terms do not contribute to
$\Delta_7$, and in particular do not contribute to the weight-one part
$[\,\Delta_7\,]^{[1]}$.
\end{lemma}

\begin{proof}
A pure same-point septic term depends only on midpoint jet data at $h$, i.e.
on the same-point expansion at the midpoint, and carries no transport factor
coming from the ordered pair $(t_+,t_-)$. Therefore it is invariant under
exchanging the two points:
\[
t_+\leftrightarrow t_-.
\]
Since this exchange is exactly the involution $s\mapsto -s$, every pure
same-point septic term is an even function of $s$.

By definition, the odd two-point germ is obtained by projecting to the odd part
under $s\mapsto -s$. Hence every even contribution vanishes in that
projection. Therefore
\[
A_{7,\mathrm{pure}}=0
\quad\text{in the odd germ.}
\]
Applying fixed-sector projection gives
\[
A_{7,\mathrm{pure}}^{\mathfrak f}=0.
\]
Since $\Delta_7$ is extracted from the odd pair germ after fixed-sector
projection and quotient normalization, pure same-point septic terms contribute
nothing to $\Delta_7$, and therefore nothing to $[\,\Delta_7\,]^{[1]}$.
\end{proof}

\begin{corollary}[Weight-one septic reduction to the direct $K_1$ slice]
\label{cor:weight-one-septic-reduction}
Let $[\,\cdot\,]^{[1]}$ denote the part linear in the first genuinely new
same-point $q^{(7)}$-slice. Then
\[
[\Delta_7]^{[1]}=[\Delta_{7,K_1}]^{[1]}.
\]
Equivalently, the highest genuinely new $q^{(7)}$-coefficient of the septic
residual determinant comes only from the direct septic $K_1$-transport slice.
\end{corollary}

\begin{proof}
The first genuinely new $q^{(7)}$-slice enters the same-point expansion at
order $5$, so
\[
X_j^{[1]}=0
\qquad (j<5).
\]
Hence every septic transport sector built only from lower same-point orders is
weight zero; in particular, the $K_3$- and $K_5$-transport sectors do not
contribute to $[\Delta_7]^{[1]}$.

By Lemma~\ref{lem:parity-elimination-pure-septic}, pure same-point septic terms
also do not contribute to $[\Delta_7]^{[1]}$, because they vanish already in
the odd two-point germ.

Thus the only septic sector that can see the weight-one $q^{(7)}$-slice is
the direct $K_1$-transport sector, and therefore
\[
[\Delta_7]^{[1]}=[\Delta_{7,K_1}]^{[1]}.
\qedhere
\]
\end{proof}

\begin{proposition}[Generic nonvanishing of the direct septic slice under nontrivial quintic fixed-sector coefficient]
\label{prop:direct-q7-total-delta7-nonzero}
Let $J$ be a connected open interval contained in the quintic-generic region.
Assume
\[
v_5\not\equiv 0
\qquad\text{on }J.
\]
Then the direct $q^{(7)}$-driven slice of the full total septic residual
determinant is generically nonzero on $J$. Equivalently,
\[
\Delta_7^{(q^{(7)})}\not\equiv 0
\qquad\text{on }J.
\]
\end{proposition}

\begin{proof}
By Corollary~\ref{cor:weight-one-septic-reduction},
\[
[\Delta_7]^{[1]}=[\Delta_{7,K_1}]^{[1]}.
\]
Thus the highest genuinely new direct $q^{(7)}$-coefficient of the total
septic residual determinant is the same as that of the direct $K_1$-transport
slice.

By Proposition~\ref{prop:direct-q7-k1-witness-nonzero}, the direct septic
$K_1$ witness is generically nonzero on the quintic-generic region. In
particular,
\[
u_{7,K_1}^{(q^{(7)})}\not\equiv 0
\qquad\text{on }J.
\]
Moreover, by Corollary~\ref{cor:direct-q7-septic-slice}, on the direct
$q^{(7)}$-driven slice one has
\[
v_{7,K_1}^{(q^{(7)})}=0,
\qquad
\Delta_{7,K_1}^{(q^{(7)})}
=
u_{7,K_1}^{(q^{(7)})}\,v_5.
\]
Since $v_5\not\equiv 0$ on $J$, it follows that
\[
\Delta_{7,K_1}^{(q^{(7)})}\not\equiv 0
\qquad\text{on }J.
\]
Therefore
\[
\Delta_7^{(q^{(7)})}\not\equiv 0
\qquad\text{on }J,
\]
as claimed.
\end{proof}

\begin{theorem}[Quotient-septic closure]
\label{thm:quotient-septic-closure}
Let the septic odd-germ coefficient be decomposed as
\[
A_7=A_{7,K_1}+A_{7,K_5}+A_{7,K_3}+A_{7,\mathrm{pure}},
\]
where $A_{7,K_1}$ is the direct $K_1$-transport sector,
$A_{7,K_5}$ and $A_{7,K_3}$ are the septic normalization-shadow sectors
from Definition~\ref{def:septic-shadow-sectors}, and
$A_{7,\mathrm{pure}}$ is the pure same-point septic sector from
Lemma~\ref{lem:parity-elimination-pure-septic}.

Then
\[
A_7^{\mathfrak f}
=
A_{7,K_1}^{\mathfrak f}+A_{7,K_5}^{\mathfrak f},
\]
with
\[
A_{7,K_5}^{\mathfrak f}\in \mathbf C\,A_5^{\mathfrak f}.
\]
Consequently,
\[
[A_7^{\mathfrak f}]
=
[A_{7,K_1}^{\mathfrak f}]
\quad\text{in }\mathfrak f/\mathbf C A_5^{\mathfrak f},
\]
and
\[
\Delta_7=\Delta_{7,K_1}.
\]
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:projected-k3-shadow-vanishing},
\[
A_{7,K_3}^{\mathfrak f}=0.
\]
By Lemma~\ref{lem:parity-elimination-pure-septic},
\[
A_{7,\mathrm{pure}}^{\mathfrak f}=0.
\]
Therefore
\[
A_7^{\mathfrak f}
=
A_{7,K_1}^{\mathfrak f}+A_{7,K_5}^{\mathfrak f}.
\]
By Proposition~\ref{prop:projected-k5-shadow-law},
\[
A_{7,K_5}^{\mathfrak f}\in \mathbf C\,A_5^{\mathfrak f}.
\]
Hence $A_7^{\mathfrak f}$ and $A_{7,K_1}^{\mathfrak f}$ define the same
class in the quotient
\[
\mathfrak f/\mathbf C A_5^{\mathfrak f}.
\]
Writing
\[
A_5^{\mathfrak f}=u_5I+v_5S,
\qquad
A_{7,K_1}^{\mathfrak f}=u_{7,K_1}I+v_{7,K_1}S,
\]
this quotient equality means precisely that
\[
A_7^{\mathfrak f}
=
A_{7,K_1}^{\mathfrak f}+\chi\,A_5^{\mathfrak f}
\]
for some scalar $\chi$. Therefore
\[
\Delta_7
=
(u_{7,K_1}+\chi u_5)v_5-u_5(v_{7,K_1}+\chi v_5)
=
u_{7,K_1}v_5-u_5v_{7,K_1}
=
\Delta_{7,K_1},
\]
where $\Delta_{7,K_1}$ is as in Definition~\ref{def:delta7-k1}.
\end{proof}

\begin{remark}[Status of the order-$7$ fixed-sector package]
\label{rem:status-full-septic-fixed-sector}
The order-$7$ fixed-sector analysis is now closed at the canonical quotient
level. By Theorem~\ref{thm:quotient-septic-closure}, the full total septic
fixed-sector class satisfies
\[
[A_7^{\mathfrak f}]
=
[A_{7,K_1}^{\mathfrak f}]
\quad\text{in }\mathfrak f/\mathbf C A_5^{\mathfrak f},
\]
and the canonical second residual determinant is
\[
\Delta_7=\Delta_{7,K_1}.
\]

What remains non-unique is only the raw representative of $A_7^{\mathfrak f}$
inside the affine line
\[
A_{7,K_1}^{\mathfrak f}+\mathbf C A_5^{\mathfrak f},
\]
as recorded by Proposition~\ref{prop:projected-septic-gauge-law}. Equivalently,
the full lower/mixed septic completion of the raw total pair $(u_7,v_7)$ is
not canonically determined. This remaining gauge-dependent choice does not
affect the quotient class $[A_7^{\mathfrak f}]$ or the residual determinant
$\Delta_7$ used in the later geometric arguments.
\end{remark}

\begin{remark}[Local gauge-fixing for raw septic representatives]
\label{rem:local-gauge-fixing-u7-v7}
Although the raw representative pair $(u_7,v_7)$ is not canonical, local
choices may be made by fixing a gauge section along the quintic fixed-sector
line. Indeed, Proposition~\ref{prop:projected-septic-gauge-law} gives
\[
(u_7^{\new},v_7^{\new})=(u_7,v_7)+c_2(u_5,v_5).
\]
Hence on any region where $v_5\neq 0$, one may choose
\[
c_2=-\frac{v_7}{v_5},
\]
so that
\[
v_7^{\new}=0,
\qquad
u_7^{\new}=\frac{\Delta_7}{v_5}.
\]
Similarly, on any region where $u_5\neq 0$, one may choose
\[
c_2=-\frac{u_7}{u_5},
\]
so that
\[
u_7^{\new}=0,
\qquad
v_7^{\new}=-\frac{\Delta_7}{u_5}.
\]
Thus raw septic representatives can be chosen locally by gauge-fixing, but
such choices are auxiliary and are not canonical.
\end{remark}

\subsection{Normalized planar curve and curvature bridge}

On the region where $c(h)\neq 0$, define the normalized scalars
\[
\rho_1(h):=\frac{v_5(h)}{c(h)},
\qquad
\rho_2(h):=\frac{\Delta_7(h)}{c(h)},
\]
and the associated planar invariant curve
\[
\Gamma(h):=\bigl(\rho_1(h),\rho_2(h)\bigr).
\]

\begin{proposition}[Non-affinity of the second normalized residual scalar]
\label{prop:rho2-not-affine-in-rho1}
Let $J$ be a connected open interval contained in the quintic-generic region
and in $\{h:c(h)\neq 0\}$. Assume
\[
v_5\not\equiv 0
\qquad\text{on }J.
\]
Then there do not exist constants $A,B\in\mathbf C$ such that
\[
\rho_2(h)\equiv A\,\rho_1(h)+B
\]
on $J$.

Equivalently,
\[
\Delta_7(h)\not\equiv A\,v_5(h)+B\,c(h)
\]
on $J$.
\end{proposition}

\begin{proof}
Suppose
\[
\Delta_7(h)\equiv A\,v_5(h)+B\,c(h)
\]
on $J$. Then the direct $q^{(7)}$-driven slice of the right-hand side
vanishes, because $v_5$ and $c$ are governed by the cubic/quintic layers
and carry no direct septic $q^{(7)}$-slice.

On the other hand, by
Proposition~\ref{prop:direct-q7-total-delta7-nonzero}, the direct
$q^{(7)}$-driven slice of $\Delta_7$ is generically nonzero on $J$.
This is a contradiction. Dividing by $c(h)$ yields
\[
\rho_2(h)\not\equiv A\,\rho_1(h)+B.
\qedhere
\]
\end{proof}

\begin{definition}[Normalized derivative numerators]
\label{def:MN-normalized-curve}
Define
\[
M(h):=c(h)v_5'(h)-c'(h)v_5(h),
\qquad
N(h):=c(h)\Delta_7'(h)-c'(h)\Delta_7(h).
\]
Then
\[
\rho_1'(h)=\frac{M(h)}{c(h)^2},
\qquad
\rho_2'(h)=\frac{N(h)}{c(h)^2}.
\]
\end{definition}

\begin{proposition}[Curvature bridge for the normalized planar curve]
\label{prop:curvature-bridge-normalized-curve}
Let
\[
K_\Gamma(h):=\rho_1'(h)\rho_2''(h)-\rho_2'(h)\rho_1''(h)
\]
denote the affine curvature numerator of the planar curve $\Gamma(h)$.
Then
\[
K_\Gamma(h)=\frac{M(h)N'(h)-N(h)M'(h)}{c(h)^4}.
\]
In particular, if $K_\Gamma\equiv 0$ on a connected open interval $J$ on
which
\[
c\neq 0,
\qquad
M\neq 0,
\qquad
v_5\not\equiv 0,
\]
then $\rho_2$ is affine in $\rho_1$ on $J$, contradicting
Proposition~\ref{prop:rho2-not-affine-in-rho1}. Hence on every such interval
one has
\[
K_\Gamma\not\equiv 0.
\]
\end{proposition}

\begin{proof}
By Definition~\ref{def:MN-normalized-curve},
\[
\rho_1'=\frac{M}{c^2},
\qquad
\rho_2'=\frac{N}{c^2}.
\]
Differentiating gives
\[
\rho_1''=\frac{M'c-2Mc'}{c^3},
\qquad
\rho_2''=\frac{N'c-2Nc'}{c^3}.
\]
Therefore
\[
K_\Gamma
=
\frac{M}{c^2}\frac{N'c-2Nc'}{c^3}
-
\frac{N}{c^2}\frac{M'c-2Mc'}{c^3}
=
\frac{MN'-NM'}{c^4}.
\]

If $K_\Gamma\equiv 0$ on a connected open set with $M\neq 0$, then
\[
0=MN'-NM'=M^2\left(\frac{N}{M}\right)',
\]
so $N/M$ is constant there:
\[
\frac{N}{M}=A.
\]
Since
\[
\frac{N}{M}=\frac{\rho_2'}{\rho_1'},
\]
it follows that
\[
\rho_2'=A\,\rho_1',
\]
hence
\[
\rho_2=A\,\rho_1+B
\]
on that connected interval. If in addition
\[
c\neq 0,
\qquad
v_5\not\equiv 0,
\]
there, this contradicts Proposition~\ref{prop:rho2-not-affine-in-rho1}. The
final claim follows.
\end{proof}

\begin{remark}[Geometric consequence]
\label{rem:geometric-consequence-normalized-curve}
Proposition~\ref{prop:curvature-bridge-normalized-curve} is the local-to-global
bridge from the order-$7$ fixed-sector analysis back to the secant/tangent
program. On the open set where
\[
c(h)\neq 0,
\qquad
M(h)\neq 0,
\qquad
M(h)N'(h)-N(h)M'(h)\neq 0,
\]
the normalized planar curve $\Gamma(h)$ decomposes into $C^2$ branches in the
affine chart $(\rho_1,\rho_2)$, each of which is strictly convex or strictly
concave. Thus the remaining global obstruction is not same-branch secancy, but
the possibility of a common four-secant line meeting two separated ECT
branches twice each.
\end{remark}

\begin{definition}[Projective Wronskian of the strengthened one-pair triple]
\label{def:projective-wronskian-c-v5-delta7}
Define
\[
W(h):=
\det\!
\begin{pmatrix}
c(h) & v_5(h) & \Delta_7(h)\\
c'(h) & v_5'(h) & \Delta_7'(h)\\
c''(h) & v_5''(h) & \Delta_7''(h)
\end{pmatrix}.
\]
\end{definition}

\begin{proposition}[Projective-Wronskian bridge]
\label{prop:projective-wronskian-bridge}
With $M(h)$ and $N(h)$ as in
Definition~\ref{def:MN-normalized-curve}, one has
\[
M(h)N'(h)-N(h)M'(h)=c(h)\,W(h).
\]
Consequently,
\[
K_\Gamma(h)=\frac{W(h)}{c(h)^3}
\]
on the region where $c(h)\neq 0$.
\end{proposition}

\begin{proof}
Using
\[
M=c\,v_5'-c'v_5,
\qquad
N=c\,\Delta_7'-c'\Delta_7,
\]
a direct expansion gives
\[
M N'-N M'
=
(c\,v_5'-c'v_5)(c\,\Delta_7''-c''\Delta_7)
-
(c\,\Delta_7'-c'\Delta_7)(c\,v_5''-c''v_5).
\]
Expanding and regrouping yields
\[
M N'-N M'
=
c\,
\det\!
\begin{pmatrix}
c & v_5 & \Delta_7\\
c' & v_5' & \Delta_7'\\
c'' & v_5'' & \Delta_7''
\end{pmatrix}
=
c\,W.
\]
The displayed formula for $K_\Gamma$ now follows from
Proposition~\ref{prop:curvature-bridge-normalized-curve}.
\end{proof}

\begin{lemma}[Exact identities for $W$ and $W'$]
\label{lem:exact-W-and-Wprime-identities}
Let
\[
F(h):=(c(h),v_5(h),\Delta_7(h)),
\qquad
M(h):=c(h)v_5'(h)-c'(h)v_5(h).
\]
Then
\[
W(h)=\det(F(h),F'(h),F''(h))
\]
admits the exact expansion
\[
W
=
M\,\Delta_7''
+
(v_5c''-cv_5'')\,\Delta_7'
+
(c'v_5''-v_5'c'')\,\Delta_7,
\]
and
\[
W'(h)=\det(F(h),F'(h),F'''(h))
\]
admits the exact expansion
\[
W'
=
M\,\Delta_7'''
+
(v_5c'''-cv_5''')\,\Delta_7'
+
(c'v_5'''-v_5'c''')\,\Delta_7.
\]
\end{lemma}

\begin{proof}
Expand the determinant $\det(F,F',F'')$ along the third column. This gives
\[
W
=
\det\!\begin{pmatrix}
c & v_5\\ c' & v_5'
\end{pmatrix}\Delta_7''
-
\det\!\begin{pmatrix}
c & v_5\\ c'' & v_5''
\end{pmatrix}\Delta_7'
+
\det\!\begin{pmatrix}
c' & v_5'\\ c'' & v_5''
\end{pmatrix}\Delta_7,
\]
which is exactly the first identity.

For $W'$, differentiate $W=\det(F,F',F'')$. The terms
$\det(F',F',F'')$ and $\det(F,F'',F'')$ vanish by repeated columns, so
\[
W'=\det(F,F',F''').
\]
Expanding along the third column gives the second formula.
\end{proof}

\begin{proposition}[Exclusion of $W$-flat intervals on the $c\neq 0,\ M\neq 0$ region]
\label{prop:no-W-flat-interval}
Let $J$ be a connected open interval on which
\[
c(h)\neq 0,
\qquad
M(h)\neq 0.
\]
Then
\[
W\not\equiv 0
\qquad\text{on }J.
\]
\end{proposition}

\begin{proof}
Suppose for contradiction that
\[
W\equiv 0
\qquad\text{on }J.
\]
By Proposition~\ref{prop:projective-wronskian-bridge},
\[
K_\Gamma(h)=\frac{W(h)}{c(h)^3}\equiv 0
\qquad\text{on }J.
\]
Since
\[
M=c\,v_5'-c'v_5
\]
and $c\neq 0$ on $J$, the hypothesis $M\neq 0$ on $J$ rules out
$v_5\equiv 0$ on $J$. Hence $v_5\not\equiv 0$ on $J$.

By Proposition~\ref{prop:curvature-bridge-normalized-curve}, it follows that
\[
\rho_2(h)=A\,\rho_1(h)+B
\]
for some constants $A,B\in\mathbf C$, i.e.
\[
\Delta_7(h)=A\,v_5(h)+B\,c(h)
\qquad\text{on }J.
\]
This contradicts Proposition~\ref{prop:rho2-not-affine-in-rho1}. Therefore
\[
W\not\equiv 0
\qquad\text{on }J.
\qedhere
\]
\end{proof}

\begin{remark}[Interpretation of the $\lambda$-reduction]
\label{rem:lambda-reduction-no-W-flatness}
On the direct highest-new slice one has
\[
\Delta_7^{[1]}=\lambda^{[1]}v_5
\]
by Corollary~\ref{cor:direct-q7-septic-slice} together with
Corollary~\ref{cor:weight-one-septic-reduction}. Thus if $W\equiv 0$ on a
connected open interval with $c\neq 0$ and $M\neq 0$, then
\[
v_5\not\equiv 0
\]
on that interval, because $M=c\,v_5'-c'v_5$. The affine dependence
\[
\Delta_7=A\,v_5+B\,c
\]
forced by Proposition~\ref{prop:no-W-flat-interval} implies
\[
\Delta_7^{[1]}=A\,v_5,
\]
hence
\[
\lambda^{[1]}\equiv A
\]
on that interval. In this sense, the present argument excludes $W$-flatness on
an $M\neq 0$ region without requiring a separate differential equation for
$\lambda^{[1]}$; what remains open is not the canonical quotient-level order-$7$
invariant, but only the lower/mixed septic completion of a raw representative
pair $(u_7,v_7)$, which is irrelevant to the quotient class
$[A_7^{\mathfrak f}]$ and to $\Delta_7$.
\end{remark}

\begin{definition}[Projective graph and dual tangent-line variables]
\label{def:mu-lambda-beta-m}
On the region where $v_5\neq 0$, define
\[
\mu:=\frac{c}{v_5},
\qquad
\lambda:=\frac{\Delta_7}{v_5}.
\]
On the subregion where $M\neq 0$, define
\[
L:=v_5\Delta_7'-v_5'\Delta_7,
\qquad
\beta:=\frac{d\lambda}{d\mu},
\qquad
m:=\lambda-\mu\beta.
\]
\end{definition}

\begin{proposition}[Closed minor system and dual tangent-line curve]
\label{prop:closed-minor-system-dual-curve}
Let
\[
F:=(c,v_5,\Delta_7),
\qquad
U:=(L,-N,M).
\]
Then
\[
F\times F'=U,
\qquad
U\times U'=W\,F.
\]
Equivalently,
\[
MN'-NM'=cW,
\qquad
ML'-LM'=v_5W,
\qquad
NL'-LN'=\Delta_7W.
\]

On the region where $v_5M\neq 0$,
\[
\mu'=-\frac{M}{v_5^2},
\qquad
\beta=-\frac{L}{M},
\qquad
m=\frac{N}{M},
\]
and
\[
\beta'=-\frac{v_5W}{M^2},
\qquad
m'=\frac{cW}{M^2}.
\]
Hence the dual tangent-line curve
\[
T(h):=(\beta(h),m(h))
\]
satisfies
\[
T'(h)=\frac{W(h)}{M(h)^2}\,(-v_5(h),c(h)).
\]
Moreover,
\[
\det(T'(h),T''(h))=\frac{W(h)^2}{M(h)^3}.
\]
\end{proposition}

\begin{proof}
The identity
\[
F\times F'=(L,-N,M)
\]
is the direct expansion of the cross product. Differentiating gives
\[
U'=F\times F''.
\]
Applying the vector identity
\[
(A\times B)\times(A\times C)=\det(A,B,C)\,A
\]
with $A=F$, $B=F'$, $C=F''$ yields
\[
U\times U'=(F\times F')\times(F\times F'')=\det(F,F',F'')\,F=W\,F,
\]
which is exactly the three displayed scalar identities.

Next,
\[
\mu'=\left(\frac{c}{v_5}\right)'
=\frac{c'v_5-cv_5'}{v_5^2}
=-\frac{M}{v_5^2},
\]
and
\[
\lambda'=\left(\frac{\Delta_7}{v_5}\right)'
=\frac{v_5\Delta_7'-v_5'\Delta_7}{v_5^2}
=\frac{L}{v_5^2},
\]
so
\[
\beta=\frac{\lambda'}{\mu'}=-\frac{L}{M}.
\]
Also
\[
\mu L+M\lambda
=
\frac{c}{v_5}(v_5\Delta_7'-v_5'\Delta_7)
+
(cv_5'-c'v_5)\frac{\Delta_7}{v_5}
=
c\Delta_7'-c'\Delta_7
=
N,
\]
hence
\[
m=\lambda-\mu\beta=\lambda+\mu\frac{L}{M}=\frac{N}{M}.
\]
The formulas for $\beta'$ and $m'$ follow immediately from
\[
ML'-LM'=v_5W,
\qquad
MN'-NM'=cW.
\]

Finally, write
\[
T'=\alpha V,
\qquad
\alpha:=\frac{W}{M^2},
\qquad
V:=(-v_5,c).
\]
Then
\[
\det(T',T'')=\alpha^2\det(V,V')
=\frac{W^2}{M^4}\det\!\begin{pmatrix}
-v_5 & -v_5'\\
c & c'
\end{pmatrix}
=
\frac{W^2}{M^3},
\]
because
\[
\det(V,V')=cv_5'-c'v_5=M.
\]
\end{proof}

\begin{corollary}[Graph curvature identities in $(\mu,\lambda)$-coordinates]
\label{cor:mu-lambda-curvature-identities}
On the region where $v_5M\neq 0$,
\[
\lambda_{\mu\mu}=\frac{v_5^3}{M^3}W,
\]
and
\[
\lambda_{\mu\mu\mu}
=
-\frac{v_5^5}{M^4}
\left(
W'+3\left(\frac{v_5'}{v_5}-\frac{M'}{M}\right)W
\right).
\]
In particular, at a point where $W=0$, $M\neq 0$, and $v_5\neq 0$,
\[
\lambda_{\mu\mu\mu}
=
-\frac{v_5^5}{M^4}W'.
\]
\end{corollary}

\begin{proof}
Since
\[
\frac{d}{d\mu}=\frac{1}{\mu'}\frac{d}{dh}
=
-\frac{v_5^2}{M}\frac{d}{dh},
\]
the identity
\[
\lambda_{\mu\mu}=\frac{v_5^3}{M^3}W
\]
follows from
\[
\lambda_\mu=\beta,
\qquad
\beta'=-\frac{v_5W}{M^2}.
\]
Differentiating once more gives
\[
\lambda_{\mu\mu\mu}
=
-\frac{v_5^2}{M}\frac{d}{dh}\!\left(\frac{v_5^3}{M^3}W\right),
\]
which expands to the displayed formula. The last statement is the specialisation
$W=0$.
\end{proof}

\begin{remark}[Determinant interpretation on a fixed-sign $W$-interval]
\label{rem:determinant-interpretation-fixed-sign-W}
On any connected interval where $c$, $M$, and $W$ are nonzero and $W$
keeps one sign, the graph $\lambda=\lambda(\mu)$ is strictly convex or
strictly concave. Consequently, for any ordered triple of distinct points on
that interval, the determinant
\[
D(s,t,u)=\det(F(s),F(t),F(u))
\]
has the corresponding fixed Vandermonde sign. Thus the unresolved global issue
is not intervalwise sign regularity, but propagation across turning seams and
possible nonadjacent recurrence of tangent-slope / tangent-line data.
\end{remark}

\begin{proposition}[Local determinant sign transport across a generic turning boundary]
\label{prop:local-determinant-sign-transport-turning}
Let $h_b$ be a generic turning boundary:
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Then there exists a neighborhood $U$ of $h_b$ and a sign
$\sigma_{\mathrm{turn}}\in\{\pm 1\}$ such that for any three distinct points
$h_1,h_2,h_3\in U$,
\[
\operatorname{sgn} D(h_1,h_2,h_3)
=
\sigma_{\mathrm{turn}}\,
\operatorname{sgn}\bigl((h_2-h_1)(h_3-h_1)(h_3-h_2)\bigr),
\]
where
\[
D(h_1,h_2,h_3):=\det(F(h_1),F(h_2),F(h_3)),
\qquad
F=(c,v_5,\Delta_7).
\]
Equivalently, the triple $(c,v_5,\Delta_7)$ is locally discretely sign-regular
of order $3$ across a generic turning boundary.
\end{proposition}

\begin{proof}
Work in the normalized affine chart
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
At a generic turning boundary one has
\[
x'(h_b)=0,\qquad x''(h_b)\neq 0,\qquad y'(h_b)\neq 0.
\]
Hence $y$ is a valid local coordinate near $h_b$, and the normalized curve
may be written as
\[
x=\chi(y)
\]
with
\[
\chi'(y_b)=0,\qquad \chi''(y_b)\neq 0.
\]
After shrinking $U$, the sign of $\chi''$ is constant on $U$.

Now for $h_i\in U$, write
\[
x_i:=x(h_i),\qquad y_i:=y(h_i).
\]
Since
\[
F(h_i)=c(h_i)\,(1,x_i,y_i),
\]
we have
\[
D(h_1,h_2,h_3)
=
c(h_1)c(h_2)c(h_3)\,
\det\!\begin{pmatrix}
1&x_1&y_1\\
1&x_2&y_2\\
1&x_3&y_3
\end{pmatrix}.
\]
Using $x_i=\chi(y_i)$, the $3\times 3$ determinant factors as
\[
\det\!\begin{pmatrix}
1&x_1&y_1\\
1&x_2&y_2\\
1&x_3&y_3
\end{pmatrix}
=
(y_2-y_1)(y_3-y_1)(y_3-y_2)\,\chi[y_1,y_2,y_3],
\]
where $\chi[y_1,y_2,y_3]$ is the second divided difference of $\chi$.
By the scalar divided-difference mean-value theorem,
\[
\chi[y_1,y_2,y_3]=\frac12\,\chi''(\eta)
\]
for some $\eta$ between the $y_i$. Thus $\chi[y_1,y_2,y_3]$ has fixed sign
on $U$.

Also $c$ has fixed sign on a sufficiently small neighborhood of $h_b$, and
since $y'(h_b)\neq 0$, the map $h\mapsto y(h)$ is monotone on $U$. Hence
\[
\operatorname{sgn}\bigl((y_2-y_1)(y_3-y_1)(y_3-y_2)\bigr)
=
\operatorname{sgn}(y')^3\,
\operatorname{sgn}\bigl((h_2-h_1)(h_3-h_1)(h_3-h_2)\bigr),
\]
with $\operatorname{sgn}(y')$ constant on $U$.

Collecting the fixed signs of $c$, $y'$, and $\chi''$ gives the desired
constant $\sigma_{\mathrm{turn}}$.
\end{proof}

\begin{proposition}[Dual asymptote at a generic turning boundary]
\label{prop:dual-asymptote-turning-boundary}
Let $h_b$ be a generic turning boundary:
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Assume $v_5(h_b)\neq 0$, and write
\[
\mu_b:=\frac{c(h_b)}{v_5(h_b)},
\qquad
\lambda_b:=\frac{\Delta_7(h_b)}{v_5(h_b)}.
\]
Let
\[
T(h)=\bigl(\beta(h),m(h)\bigr)
=
\left(-\frac{L(h)}{M(h)},\frac{N(h)}{M(h)}\right)
\]
be the dual tangent-line curve on the neighboring $M\neq 0$ branches.
Then both one-sided dual arcs have the common asymptote
\[
m=-\mu_b\,\beta+\lambda_b,
\]
and, more precisely,
\[
m+\mu_b\beta-\lambda_b
=
\frac{1}{4a\,\beta}+o\!\left(\frac1\beta\right)
\qquad\text{as } |\beta|\to\infty,
\]
where $a\neq 0$ is the quadratic coefficient in the local turning-point normal
form
\[
\mu-\mu_b=a(\lambda-\lambda_b)^2+O((\lambda-\lambda_b)^3).
\]
In particular, the two adjacent dual arcs approach the same asymptote from
opposite sides. This asymptotic separation is the dual-curve explanation of
the local adjacent turning-boundary exclusion theorem proved later.
\end{proposition}

\begin{proof}
At a generic turning boundary one has $\mu'(h_b)=0$ and $\lambda'(h_b)\neq 0$,
so $\lambda$ is a valid local coordinate and
\[
\mu-\mu_b=a(\lambda-\lambda_b)^2+O((\lambda-\lambda_b)^3),
\qquad a\neq 0.
\]
Differentiating gives
\[
\frac{d\mu}{d\lambda}=2a(\lambda-\lambda_b)+O((\lambda-\lambda_b)^2),
\]
hence
\[
\beta=\frac{d\lambda}{d\mu}
=
\frac{1}{2a(\lambda-\lambda_b)}+O(1).
\]
Thus $|\beta|\to\infty$ as $h\to h_b$ from either side.

Now
\[
m=\lambda-\mu\beta,
\]
so
\[
m+\mu_b\beta-\lambda_b
=
(\lambda-\lambda_b)-(\mu-\mu_b)\beta.
\]
Using
\[
\mu-\mu_b=a(\lambda-\lambda_b)^2+O((\lambda-\lambda_b)^3)
\]
and
\[
\beta=\frac{1}{2a(\lambda-\lambda_b)}+O(1),
\]
we obtain
\[
(\mu-\mu_b)\beta
=
\frac12(\lambda-\lambda_b)+O((\lambda-\lambda_b)^2).
\]
Therefore
\[
m+\mu_b\beta-\lambda_b
=
\frac12(\lambda-\lambda_b)+O((\lambda-\lambda_b)^2).
\]
Substituting
\[
\lambda-\lambda_b=\frac{1}{2a\beta}+o\!\left(\frac1\beta\right)
\]
gives
\[
m+\mu_b\beta-\lambda_b
=
\frac{1}{4a\,\beta}+o\!\left(\frac1\beta\right).
\]
Since $\beta\to+\infty$ on one side and $\beta\to-\infty$ on the other, the
correction term changes sign, so the two one-sided dual arcs approach the same
asymptote from opposite sides.
\end{proof}

\begin{proposition}[ECT intervals for the strengthened one-pair triple]
\label{prop:ect-intervals-c-v5-delta7}
Let $I$ be a connected interval on which
\[
c(h)\neq 0,
\qquad
M(h)\neq 0,
\qquad
W(h)\neq 0.
\]
Then the triple
\[
(c,\ v_5,\ \Delta_7)
\]
is an extended complete Chebyshev system on $I$. Equivalently, every
nontrivial linear combination
\[
A\,c(h)+B\,v_5(h)+C\,\Delta_7(h)
\]
has at most two zeros on $I$, counting multiplicity.

In particular, in the affine chart
\[
x=\frac{v_5}{c},\qquad y=\frac{\Delta_7}{c},
\]
every affine line meets $\Gamma(I)$ in at most two points, counting
tangency with multiplicity.
\end{proposition}

\begin{proof}
Define
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
Since the one-pair family is real-analytic on the generic region, the
functions $x$ and $y$ are $C^2$ on $I$.

By Definition~\ref{def:MN-normalized-curve},
\[
x'(h)=\frac{M(h)}{c(h)^2},
\qquad
y'(h)=\frac{N(h)}{c(h)^2}.
\]
Because $M(h)\neq 0$ and $c(h)\neq 0$ on $I$, one has
\[
x'(h)\neq 0
\qquad (h\in I),
\]
so $x$ is strictly monotone on $I$ and may be used as a parameter on
$\Gamma(I)$.

Moreover,
\[
\frac{dy}{dx}=\frac{y'(h)}{x'(h)}=\frac{N(h)}{M(h)}.
\]
Differentiating with respect to $x$ gives
\[
\frac{d^2y}{dx^2}
=
\frac{\frac{d}{dh}\bigl(N/M\bigr)}{x'(h)}
=
\frac{(M N'-N M')/M^2}{M/c^2}.
\]
Using Proposition~\ref{prop:projective-wronskian-bridge},
\[
M N'-N M'=c\,W,
\]
hence
\[
\frac{d^2y}{dx^2}
=
\frac{c(h)^3\,W(h)}{M(h)^3}.
\]
Since $c(h)\neq 0$, $M(h)\neq 0$, and $W(h)\neq 0$ on $I$, it follows that
\[
\frac{d^2y}{dx^2}\neq 0
\qquad (h\in I).
\]
Therefore $\Gamma(I)$ is the graph of a strictly convex or strictly concave
$C^2$ function $y=y(x)$.

Now let
\[
L(h):=A\,c(h)+B\,v_5(h)+C\,\Delta_7(h)
\]
be a nontrivial linear combination. Since $c(h)\neq 0$ on $I$,
\[
L(h)=0
\quad\Longleftrightarrow\quad
A+B\,x(h)+C\,y(h)=0.
\]
Thus zeros of $L$ correspond exactly to intersections of $\Gamma(I)$ with the
affine line
\[
A+B\,x+C\,y=0.
\]

If $C=0$, then the equation is
\[
A+B\,x=0,
\]
which has at most one solution because $x$ is strictly monotone on $I$.
If $C\neq 0$, the equation may be written as
\[
y=-\frac{A}{C}-\frac{B}{C}x,
\]
and a strictly convex or strictly concave graph meets an affine line in at
most two points, counting tangency with multiplicity.

Hence every nontrivial linear combination
\[
A\,c+B\,v_5+C\,\Delta_7
\]
has at most two zeros on $I$, counting multiplicity. This is exactly the ECT
property for the triple $(c,v_5,\Delta_7)$. The affine-line statement is the
same conclusion in the chart $(x,y)$.
\end{proof}

\begin{definition}[ECT interval]
\label{def:ect-interval}
An ECT interval is a connected interval
\[
I\subset\{h:\ c(h)\neq 0,\ M(h)\neq 0,\ W(h)\neq 0\}.
\]
Equivalently, by Proposition~\ref{prop:ect-intervals-c-v5-delta7}, it is a
connected interval on which the triple
\[
(c,\ v_5,\ \Delta_7)
\]
is an extended complete Chebyshev system.
\end{definition}

\begin{corollary}[At most two points from one ECT interval]
\label{cor:two-points-per-ect-interval}
Let $I$ be an ECT interval. Then every affine line in the chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c}
\]
meets $\Gamma(I)$ in at most two points, counting tangency with multiplicity.

In particular, if a finite configuration is cut out by a single affine
relation in the normalized chart, then its contribution from any fixed ECT
interval has cardinality at most two.
\end{corollary}

\begin{proof}
This is exactly the affine-line formulation of
Proposition~\ref{prop:ect-intervals-c-v5-delta7}.
\end{proof}

\begin{remark}[Branch geometry on an ECT interval]
\label{rem:branch-geometry-ect-interval}
On an ECT interval $I$, the quantities $c$, $M$, and $W$ have fixed nonzero
sign. Hence
\[
x=\frac{v_5}{c}
\]
is a monotone parameter on $I$, and in the affine chart
\[
\Gamma(I)=\left\{\left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right):h\in I\right\}
\]
is a single $C^2$ branch which is strictly convex or strictly concave
according to the sign of
\[
\frac{c(h)^3W(h)}{M(h)^3}.
\]
The later tangent-separator analysis is therefore an adjacent-branch problem,
not a same-branch secancy problem.
\end{remark}

\begin{definition}[Tangent-separator kernel]
\label{def:tangent-separator-kernel}
Let
\[
F(h):=(c(h),v_5(h),\Delta_7(h)).
\]
For $s,t$ in the generic region, define
\[
K(s,t):=\det\!\bigl(F(s),F'(s),F(t)\bigr).
\]
For fixed $s$, the zeros of $t\mapsto K(s,t)$ are exactly the points
$\Gamma(t)$ lying on the affine tangent line to $\Gamma$ at $\Gamma(s)$.
Equivalently, $K(s,t)=0$ is the tangent-separator incidence condition for
the tangent at $s$ and the point at $t$.
\end{definition}

\begin{lemma}[Affine form of the tangent-separator kernel]
\label{lem:affine-form-of-K}
On the affine chart $c\neq 0$, write
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
Then for every $s,t$ with $c(s)c(t)\neq 0$,
\[
K(s,t)
=
c(s)^2\,c(t)\,x'(s)
\Bigl(
\bigl(y(t)-m(s)x(t)\bigr)
-
\bigl(y(s)-m(s)x(s)\bigr)
\Bigr),
\]
where
\[
m(s)=\frac{dy}{dx}(s)=\frac{N(s)}{M(s)}.
\]
Equivalently,
\[
K(s,t)
=
c(s)^2\,c(t)\,x'(s)\,
\bigl(\phi_{m(s)}(t)-\tau_s\bigr),
\]
with
\[
\phi_{m(s)}(t):=y(t)-m(s)x(t),
\qquad
\tau_s:=y(s)-m(s)x(s).
\]
\end{lemma}

\begin{proof}
Write
\[
F(h)=\bigl(c(h),\,c(h)x(h),\,c(h)y(h)\bigr).
\]
Then
\[
F'(s)=\bigl(c'(s),\,c'(s)x(s)+c(s)x'(s),\,c'(s)y(s)+c(s)y'(s)\bigr).
\]
Subtracting $x(s)$ times the first column from the second and $y(s)$ times
the first column from the third gives
\[
K(s,t)
=
\det\!
\begin{pmatrix}
c(s) & 0 & 0\\
c'(s) & c(s)x'(s) & c(s)y'(s)\\
c(t) & c(t)(x(t)-x(s)) & c(t)(y(t)-y(s))
\end{pmatrix}.
\]
Expanding along the first row yields
\[
K(s,t)
=
c(s)^2c(t)\Bigl(x'(s)(y(t)-y(s))-y'(s)(x(t)-x(s))\Bigr).
\]
Since
\[
m(s)=\frac{y'(s)}{x'(s)},
\]
this becomes
\[
K(s,t)
=
c(s)^2c(t)x'(s)
\Bigl((y(t)-m(s)x(t))-(y(s)-m(s)x(s))\Bigr),
\]
as claimed.
\end{proof}

\begin{lemma}[Basic properties of the tangent-separator kernel]
\label{lem:tangent-separator-basic-properties}
For every $s$ in the generic region,
\[
K(s,s)=0,
\qquad
\partial_tK(s,s)=0,
\qquad
\partial_t^2K(s,s)=W(s).
\]
In particular, on any interval where $W$ has fixed sign, the tangent line at
$\Gamma(s)$ is locally supporting.
\end{lemma}

\begin{proof}
The first two identities follow because, at $t=s$, the third column of the
determinant equals $F(s)$, and after differentiating once in $t$ it equals
$F'(s)$. Differentiating a second time gives
\[
\partial_t^2K(s,s)=
\det\!\bigl(F(s),F'(s),F''(s)\bigr)=W(s).
\qedhere
\]
\end{proof}

\begin{lemma}[Compact first-zero reduction on adjacent intervals]
\label{lem:compact-first-zero-reduction}
Let $I_1<I_2$ be adjacent ECT intervals in the affine
$x=v_5/c$ ordering. Assume there are compact subintervals
\[
J_1\Subset I_1,\qquad J_2\Subset I_2
\]
such that every zero of the tangent-separator kernel
\[
K(s,t)=\det(F(s),F'(s),F(t)),
\qquad
F(h)=(c(h),v_5(h),\Delta_7(h)),
\]
with $s\in I_2$, $t\in I_1$, lies in $J_2\times J_1$.

If $K$ has a zero on $J_2\times J_1$, then there exists a zero
\[
(s_*,t_*)\in J_2\times J_1
\]
such that $s_*$ is minimal in the $x=v_5/c$ ordering among all
$s$-coordinates of zeros of $K$ on $J_2\times J_1$.
\end{lemma}

\begin{proof}
Because $K$ is continuous, its zero set in the compact set $J_2\times J_1$
is closed, hence compact. The projection of that zero set to the $s$-axis is
therefore compact as well. Since $x=v_5/c$ is monotone on $I_2$, the
induced $x$-ordering is equivalent to the interval ordering on $J_2$. Thus
the projected zero set has a minimal element $s_*$, and there exists
$t_*\in J_1$ such that $(s_*,t_*)$ is a zero of $K$.
\end{proof}

\begin{lemma}[First adjacent zero implies tangency]
\label{lem:first-adjacent-zero-implies-tangency}
In the setting of Lemma~\ref{lem:compact-first-zero-reduction}, let
\[
(s_*,t_*)\in J_2\times J_1
\]
be a zero with minimal $s$-coordinate in the $x=v_5/c$ ordering. Then
\[
\partial_t K(s_*,t_*)=0.
\]
Consequently,
\[
K(s_*,t_*)=0,
\qquad
\partial_t K(s_*,t_*)=0
\]
force the tangent line at $\Gamma(s_*)$ to be tangent also at
$\Gamma(t_*)$.
\end{lemma}

\begin{proof}
Assume for contradiction that
\[
\partial_tK(s_*,t_*)\neq 0.
\]
Since
\[
(s_*,t_*)\in J_2\times J_1\Subset I_2\times I_1,
\]
the implicit function theorem applies in the open set $I_2\times I_1$ and
gives a local $C^1$ zero curve
\[
t=t(s)
\]
through $(s_*,t_*)$, defined for $s$ in a neighborhood of $s_*$, such that
\[
K(s,t(s))=0.
\]
For $s$ sufficiently close to $s_*$ with $s<s_*$, one still has
\[
(s,t(s))\in I_2\times I_1
\]
and
\[
K(s,t(s))=0.
\]
By the zero-capture hypothesis in
Lemma~\ref{lem:compact-first-zero-reduction}, every zero of $K$ with
$s\in I_2$ and $t\in I_1$ lies in $J_2\times J_1$. Hence these nearby zeros
also lie in $J_2\times J_1$, contradicting the minimality of $s_*$ among all
zeros of $K$ on $J_2\times J_1$.

Therefore
\[
\partial_tK(s_*,t_*)=0.
\]

Finally, the identities
\[
K(s,t)=\det(F(s),F'(s),F(t)),
\qquad
\partial_tK(s,t)=\det(F(s),F'(s),F'(t))
\]
show that $K(s_*,t_*)=0$ places $\Gamma(t_*)$ on the tangent line at
$\Gamma(s_*)$, while $\partial_tK(s_*,t_*)=0$ places the tangent direction
at $t_*$ on that same line. Hence the line is tangent to $\Gamma$ at both
$\Gamma(s_*)$ and $\Gamma(t_*)$; that is, it is a common tangent line.
\end{proof}

\begin{proposition}[Adjacent slope-range separation]
\label{prop:adjacent-slope-range-separation}
Let $I_1<I_2$ be adjacent ECT intervals, meeting at a boundary point $h_b$.

\begin{enumerate}
\item If
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0,
\]
then the interior tangent-slope ranges of $I_1$ and $I_2$ are disjoint.

\item If
\[
W(h_b)=0,\qquad M(h_b)\neq 0,
\]
then $x=v_5/c$ remains a valid local parameter, but no adjacent tangent
separation statement is asserted here. In that case the local affine jet is
governed by
\[
\left.\frac{d^2y}{dx^2}\right|_{h_b}=0,
\qquad
\left.\frac{d^3y}{dx^3}\right|_{h_b}
=
\frac{c(h_b)^5}{M(h_b)^4}W'(h_b),
\]
so the generic behavior is an ordinary affine inflection unless further
special structure forces $W'(h_b)=0$.
\end{enumerate}
\end{proposition}

\begin{proof}
In case (1), $M(h_b)=0$ is a simple zero and $N(h_b)\neq 0$. Therefore
\[
m(h)=\frac{N(h)}{M(h)}
\]
has opposite one-sided blow-up:
\[
m(h)\to \pm\infty
\]
as $h\to h_b^\pm$. Hence the interior tangent-slope ranges on the two sides
are disjoint.

Case (2) is the local affine-jet computation recorded in
Remark~\ref{rem:w0-inflection-obstruction}; it identifies the cubic-inflection
coefficient but does not produce a tangent-separation theorem.
\end{proof}

\begin{lemma}[Endpoint tangent exclusion at a generic turning boundary]
\label{lem:endpoint-tangent-exclusion}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a boundary point $h_b$,
and assume
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Then the boundary tangent line at $\Gamma(h_b)$ is vertical and meets
neither adjacent interval in its interior.
\end{lemma}

\begin{proof}
The boundary tangent line is
\[
x=\rho_1(h_b),
\qquad
\rho_1(h)=\frac{v_5(h)}{c(h)}.
\]
Since $M(h_b)=0$ is a simple zero,
\[
\rho_1'(h_b)=0,\qquad \rho_1''(h_b)\neq 0,
\]
so $\rho_1$ has a strict local extremum at $h_b$. Therefore
\[
\rho_1(h)-\rho_1(h_b)
\]
has fixed sign on each adjacent interval and vanishes only at the boundary
point. Hence the vertical tangent line meets neither adjacent interval in its
interior.
\end{proof}

\begin{theorem}[Conditional adjacent tangent-separator sign regularity across turning boundaries]
\label{thm:adjacent-tangent-separator-sign-regularity}
Let $I_1<I_2$ be adjacent ECT intervals, and assume their common boundary
point $h_b$ is a generic turning boundary:
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Assume in addition the zero-capture hypothesis of
Lemma~\ref{lem:compact-first-zero-reduction} on the adjacent pair
$I_2\times I_1$. Then
\[
K(s,t)\neq 0
\qquad
(s\in I_2,\ t\in I_1),
\]
where
\[
K(s,t)=\det(F(s),F'(s),F(t)),
\qquad
F(h)=(c(h),v_5(h),\Delta_7(h)).
\]
Equivalently, tangent lines from the right interval do not meet the adjacent
left interval across a generic turning boundary.
\end{theorem}

\begin{proof}
By Lemma~\ref{lem:endpoint-tangent-exclusion}, for a generic turning boundary
there is a neighborhood of the boundary pair on which $K(s,t)\neq 0$ for
$s\in I_2$, $t\in I_1$.

Assume for contradiction that some zero $(s_0,t_0)\in I_2\times I_1$
exists. By the zero-capture hypothesis, there are compact subintervals
\[
J_1\Subset I_1,\qquad J_2\Subset I_2
\]
such that every zero of $K$ on $I_2\times I_1$ lies in $J_2\times J_1$.
Replacing them by smaller compact subintervals still containing the zero set,
using the boundary-near zero-free region furnished by
Lemma~\ref{lem:endpoint-tangent-exclusion}, we may also assume that
$J_2\times J_1$ is disjoint from that boundary-near region.
Then the zero set of $K$ in the compact set $J_2\times J_1$ is nonempty
and closed, so by Lemma~\ref{lem:compact-first-zero-reduction} there exists a
zero $(s_*,t_*)\in J_2\times J_1$ whose $s$-coordinate is minimal in the
$x=v_5/c$ ordering among all zeros in $J_2\times J_1$.

By Lemma~\ref{lem:first-adjacent-zero-implies-tangency},
\[
K(s_*,t_*)=0,
\qquad
\partial_tK(s_*,t_*)=0,
\]
so the tangent line at $\Gamma(s_*)$ is also tangent at $\Gamma(t_*)$.

Across a generic turning boundary,
Proposition~\ref{prop:adjacent-slope-range-separation} shows that the
interior tangent-slope ranges of the two adjacent intervals are disjoint.
Hence no common interior tangent slope can occur. This contradicts the
existence of $(s_*,t_*)$. Therefore no such zero exists, and
\[
K(s,t)\neq 0
\qquad
(s\in I_2,\ t\in I_1).
\qedhere
\]
\end{proof}

\begin{remark}[Status of the turning-boundary adjacent theorem]
\label{rem:status-zero-capture-turning-boundary}
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity} remains a
conditional turning-boundary theorem: the local compact first-zero and
first-zero-implies-tangency mechanism is in place, but it still depends on a
separate zero-capture statement for the directional tangent-separator kernel
$K_{21}(s,t)$ on the full adjacent pair $I_2\times I_1$.

However, by Theorem~\ref{thm:adjacent-pair-pair-exclusion-turning}, full
zero-capture is no longer needed to exclude actual adjacent pair-pair lines.
What remains open here is therefore only the stronger support-ordering /
directional-kernel route, not the local adjacent $2+2$ exclusion itself.
\end{remark}

\begin{lemma}[Boundary-near exclusion for both directional kernels at a generic turning boundary]
\label{lem:boundary-near-directional-kernel-exclusion}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Define
\[
K_{21}(s,t):=\det(F(s),F'(s),F(t)),
\qquad
K_{12}(t,s):=\det(F(t),F'(t),F(s)),
\]
with
\[
F(h)=(c(h),v_5(h),\Delta_7(h)).
\]
Then there is a neighborhood of the boundary pair on which both directional
kernels are nonzero:
\[
K_{21}(s,t)\neq 0,
\qquad
K_{12}(t,s)\neq 0
\]
for $s\in I_2$, $t\in I_1$ sufficiently close to $h_b$.
\end{lemma}

\begin{proof}
Write
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
Since
\[
y'(h)=\frac{N(h)}{c(h)^2},
\]
the hypothesis $N(h_b)\neq 0$ implies that $y$ is a valid local
coordinate near $h_b$. Thus the normalized planar curve may be written
locally as a graph
\[
x=\chi(y).
\]
At $h_b$,
\[
\frac{dx}{dy}=\frac{M(h)}{N(h)},
\]
so
\[
\left.\frac{dx}{dy}\right|_{h_b}=0.
\]
Differentiating once more,
\[
\frac{d^2x}{dy^2}
=
\frac{c(h)^2}{N(h)}\cdot\frac{M'(h)N(h)-M(h)N'(h)}{N(h)^2},
\]
and since $M(h_b)=0$,
\[
\left.\frac{d^2x}{dy^2}\right|_{h_b}
=
\frac{c(h_b)^2\,M'(h_b)}{N(h_b)^2}\neq 0.
\]
Hence, after shrinking to a small neighborhood of $h_b$, the graph
$x=\chi(y)$ is strictly convex or strictly concave.

For such a graph, the tangent line at any point meets the graph only at its
point of tangency. Therefore no tangent line from one side can meet the
opposite side inside a sufficiently small neighborhood of the boundary.
Equivalently, both directional tangent-separator kernels are nonzero near the
boundary pair.
\end{proof}

\begin{lemma}[Mirrored first adjacent zero implies tangency]
\label{lem:mirrored-first-adjacent-zero-implies-tangency}
Let $J_1\Subset I_1$, $J_2\Subset I_2$ be compact interior subintervals
across a generic turning boundary, and define
\[
K_{12}(t,s):=\det(F(t),F'(t),F(s)),
\qquad
t\in I_1,\ s\in I_2.
\]
Assume every zero of $K_{12}$ on $I_1\times I_2$ lies in
$J_1\times J_2$. Let $(t_*,s_*)\in J_1\times J_2$ be a zero whose
$t$-coordinate is minimal in the $x=v_5/c$ ordering among all zeros of
$K_{12}$ on $I_1\times I_2$. Then
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
\end{lemma}

\begin{proof}
Because $M\neq 0$ on the open interval $I_1$, the function
\[
x(h)=\frac{v_5(h)}{c(h)}
\]
is a valid local coordinate on $I_1$. Since every zero of $K_{12}$ lies in
the compact interior rectangle $J_1\times J_2$, the chosen point
$(t_*,s_*)$ is interior in the ambient domain $I_1\times I_2$.

Suppose
\[
\partial_s K_{12}(t_*,s_*)\neq 0.
\]
Then by the implicit function theorem there is a $C^1$ local zero curve
\[
s=s(t)
\]
through $(t_*,s_*)$, defined for $t$ near $t_*$, such that
\[
K_{12}(t,s(t))=0.
\]
Because $t_*$ is interior in $I_1$, there are nearby points with smaller
$x=v_5/c$ ordering still in $I_1$. For such $t$, the point
$(t,s(t))$ is also a zero of $K_{12}$, contradicting the minimality of
$t_*$. Therefore
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
\end{proof}

\begin{theorem}[Conditional symmetric directional-kernel exclusion across turning boundaries]
\label{thm:conditional-symmetric-directional-kernel-exclusion}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Assume:
\begin{enumerate}
\item the zero-capture hypothesis required in
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity} for the kernel
$K_{21}$ on $I_2\times I_1$;
\item the symmetric zero-capture hypothesis for $K_{12}$, namely that every
zero of
\[
K_{12}(t,s)=\det(F(t),F'(t),F(s))
\]
on $I_1\times I_2$ lies in some compact interior rectangle
$J_1\times J_2\Subset I_1\times I_2$.
\end{enumerate}
Then both directional kernels are zero-free:
\[
K_{21}(s,t)\neq 0
\qquad (s\in I_2,\ t\in I_1),
\]
and
\[
K_{12}(t,s)\neq 0
\qquad (t\in I_1,\ s\in I_2).
\]
\end{theorem}

\begin{proof}
The first assertion is exactly
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity}.

For the second assertion, boundary-near exclusion for $K_{12}$ is provided by
Lemma~\ref{lem:boundary-near-directional-kernel-exclusion}. Assume for
contradiction that $K_{12}$ has a zero. By the symmetric zero-capture
hypothesis, every zero lies in a compact interior rectangle $J_1\times J_2$.
Choose a zero $(t_*,s_*)\in J_1\times J_2$ whose $t$-coordinate is minimal
in the $x=v_5/c$ ordering among all zeros of $K_{12}$ on $I_1\times I_2$.

By Lemma~\ref{lem:mirrored-first-adjacent-zero-implies-tangency},
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
Together with
\[
K_{12}(t_*,s_*)=0,
\]
this implies that the tangent line at $\Gamma(t_*)$ is also tangent at
$\Gamma(s_*)$. Hence the two adjacent intervals share a common interior
tangent slope, contradicting
Proposition~\ref{prop:adjacent-slope-range-separation}. Therefore
$K_{12}$ has no zero.
\end{proof}

\begin{remark}[Status of the directional-kernel reduction]
\label{rem:status-directional-kernel-reduction}
Lemma~\ref{lem:pair-pair-gives-directional-kernel-zero} reduces an adjacent
pair-pair line across a generic turning boundary to a compact interior zero of
one of the two directional tangent-separator kernels.
Theorem~\ref{thm:conditional-symmetric-directional-kernel-exclusion}
shows that the remaining turning-boundary issue is no longer orientation
selection between $K_{21}$ and $K_{12}$, but the symmetric zero-capture
problem for these two kernels.
\end{remark}

\begin{remark}[The $W=0$ obstruction and the cubic-inflection coefficient]
\label{rem:w0-inflection-obstruction}
Let
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
At a boundary point $h_b$ with
\[
W(h_b)=0,\qquad M(h_b)\neq 0,
\]
the coordinate $x$ remains a valid local parameter. Since
\[
\frac{d^2y}{dx^2}=\frac{c(h)^3W(h)}{M(h)^3},
\]
one has
\[
\left.\frac{d^2y}{dx^2}\right|_{h_b}=0.
\]
Differentiating once more with respect to $x$ gives
\[
\left.\frac{d^3y}{dx^3}\right|_{h_b}
=
\frac{c(h_b)^5}{M(h_b)^4}W'(h_b).
\]
Hence, after translating the point to the origin and subtracting the tangent
line, the normalized curve has local expansion
\[
y
=
\frac{c(h_b)^5W'(h_b)}{6M(h_b)^4}\,x^3+O(x^4).
\]

Therefore a generic $W=0,\ M\neq 0$ boundary is an ordinary affine inflection
unless additional special structure forces
\[
W'(h_b)=0.
\]
In particular, the tangent-separator route is not presently justified across
such boundaries, and the real remaining geometric question is whether the
actual triple $(c,v_5,\Delta_7)$ imposes any non-generic vanishing of
$W'(h_b)$.
\end{remark}

\begin{lemma}[Fixed-slope intercept sets for a strictly convex ECT branch]
\label{lem:fixed-slope-intercept-sets}
Let $I$ be an ECT interval in the affine chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c},
\]
and suppose $\Gamma(I)$ is a strictly convex $C^2$ graph
\[
\Gamma(I)=\{(x,\psi_I(x)):x\in J_I\}
\]
over an open interval $J_I\subset\mathbf R$.

For each slope $m\in\mathbf R$, define
\[
\mathcal B_I(m):=\{\psi_I(x)-mx:x\in J_I\}.
\]

Then:

\begin{enumerate}
\item $\mathcal B_I(m)$ is an interval.

\item A line $y=mx+b$ meets $\Gamma(I)$ if and only if
\[
b\in \mathcal B_I(m).
\]

\item If $m$ lies in the interior tangent-slope range of $I$, there is a
unique $x_I(m)\in J_I$ such that
\[
\psi_I'(x_I(m))=m,
\]
and the tangent line of slope $m$ has intercept
\[
\tau_I(m):=\psi_I(x_I(m))-m\,x_I(m).
\]
Moreover,
\[
\tau_I(m)=\inf \mathcal B_I(m).
\]

\item For such $m$, a line $y=mx+b$ is $2$-secant to $\Gamma(I)$ if and
only if
\[
b\in \operatorname{int}\mathcal B_I(m).
\]
Equivalently, the $2$-secant intercepts of slope $m$ are exactly the
interior points of the intercept interval.
\end{enumerate}
\end{lemma}

\begin{proof}
For fixed $m$, put
\[
\phi_m(x):=\psi_I(x)-mx.
\]
Since $\phi_m$ is continuous on the interval $J_I$, its image
\[
\phi_m(J_I)=\mathcal B_I(m)
\]
is an interval. This proves (1), and (2) is immediate from
\[
(x,\psi_I(x))\in \{y=mx+b\}
\iff
\psi_I(x)-mx=b.
\]

If $m$ lies in the interior tangent-slope range, strict convexity implies
that $\psi_I'$ is strictly monotone, hence there is a unique $x_I(m)$
with $\psi_I'(x_I(m))=m$. At that point,
\[
\phi_m'(x_I(m))=\psi_I'(x_I(m))-m=0,
\]
and since
\[
\phi_m''(x)=\psi_I''(x)>0,
\]
the point $x_I(m)$ is the unique minimizer of $\phi_m$. Thus
\[
\tau_I(m)=\phi_m(x_I(m))=\inf \mathcal B_I(m),
\]
which proves (3).

Finally, because $\phi_m$ is strictly convex with a unique minimum,
a level $b$ is attained at two points exactly when it lies in the interior
of the interval $\phi_m(J_I)=\mathcal B_I(m)$. This is precisely the
$2$-secant condition, proving (4).
\end{proof}

\begin{lemma}[Support-overlap truncation across a generic turning boundary]
\label{lem:support-overlap-truncation-turning}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
c(h_b)\neq 0,
\qquad
M(h_b)=0,
\qquad
M'(h_b)\neq 0,
\qquad
N(h_b)\neq 0.
\]
For a fixed finite slope $m$, define
\[
\phi_m(h):=\frac{\Delta_7(h)-m v_5(h)}{c(h)},
\qquad
\mathcal B_I(m):=\phi_m(I).
\]
Assume
\[
b\in \mathcal B_{I_1}(m)\cap \mathcal B_{I_2}(m).
\]
Then there exists a neighborhood $U$ of $h_b$ and compact subintervals
\[
J_1\Subset I_1\setminus U,
\qquad
J_2\Subset I_2\setminus U
\]
such that
\[
b\in \mathcal B_{J_1}(m)\cap \mathcal B_{J_2}(m).
\]
\end{lemma}

\begin{proof}
Differentiate:
\[
\phi_m'(h)=\frac{N(h)-mM(h)}{c(h)^2}.
\]
At $h=h_b$, since $M(h_b)=0$,
\[
\phi_m'(h_b)=\frac{N(h_b)}{c(h_b)^2}\neq 0.
\]
Hence for each fixed finite $m$, after shrinking to a small neighborhood $U$
of $h_b$, the function $\phi_m$ is strictly monotone on each one-sided piece
\[
I_1\cap U,
\qquad
I_2\cap U.
\]
Therefore, for each $i=1,2$, the equation
\[
\phi_m(h)=b
\]
has at most one solution in $I_i\cap U$.

But the assumption
\[
b\in \mathcal B_{I_i}(m)
\]
means exactly that there is at least one solution of $\phi_m(h)=b$ somewhere
on $I_i$. Therefore, after removing the boundary neighborhood $U$, at least
one such solution
\[
h_i^\sharp\in I_i\setminus U
\]
remains on each side. Choose small compact subintervals
\[
J_i\Subset I_i\setminus U
\]
with $h_i^\sharp\in J_i$. Then by continuity,
\[
b=\phi_m(h_i^\sharp)\in \phi_m(J_i)=\mathcal B_{J_i}(m),
\]
for $i=1,2$. This proves the claim.
\end{proof}

\begin{lemma}[Compact adjacent pair-pair implies a directional kernel zero]
\label{lem:pair-pair-gives-directional-kernel-zero}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary,
and let
\[
L:\ y=mx+b
\]
be a finite-slope line that is $2$-secant to both $\Gamma(I_1)$ and
$\Gamma(I_2)$.
Then, after removing a sufficiently small boundary neighborhood, there exist
compact subintervals
\[
J_1\Subset I_1,
\qquad
J_2\Subset I_2
\]
and points $s\in J_2$, $t\in J_1$ such that one of the two directional
kernels vanishes:
\[
K_{21}(s,t):=\det(F(s),F'(s),F(t))=0,
\]
or
\[
K_{12}(t,s):=\det(F(t),F'(t),F(s))=0,
\]
where
\[
F(h)=(c(h),v_5(h),\Delta_7(h)).
\]
\end{lemma}

\begin{proof}
Because $L$ is $2$-secant to each branch, Lemma~\ref{lem:fixed-slope-intercept-sets}
shows that $m$ lies in the interior tangent-slope range of each interval.
Hence each branch has a unique interior tangent line of slope $m$, with tangent
intercept
\[
\tau_{I_i}(m)=\inf \mathcal B_{I_i}(m).
\]

At a generic turning boundary,
\[
\frac{dy/dh}{dx/dh}=\frac{N(h)}{M(h)}
\]
has one-sided blow-up, so no finite-slope tangency can occur arbitrarily close
to $h_b$. Therefore, after shrinking away a boundary neighborhood and applying
Lemma~\ref{lem:support-overlap-truncation-turning}, we may choose compact
subintervals
\[
J_1\Subset I_1,
\qquad
J_2\Subset I_2
\]
such that:
\begin{enumerate}
\item $b\in \mathcal B_{J_1}(m)\cap \mathcal B_{J_2}(m)$;
\item the unique slope-$m$ tangency point of each branch lies in the
corresponding $J_i$.
\end{enumerate}
Hence each $\mathcal B_{J_i}(m)$ is a compact interval whose lower endpoint
is the tangent intercept
\[
\tau_i:=\tau_{J_i}(m)=\inf \mathcal B_{J_i}(m).
\]

Now set
\[
b_*:=\inf\bigl(\mathcal B_{J_1}(m)\cap \mathcal B_{J_2}(m)\bigr).
\]
Since the intersection of two compact intervals is again a compact interval,
\[
b_*=\max(\tau_1,\tau_2).
\]
So $b_*$ is equal to one of the two tangent intercepts, and it still lies in
the support set of the other branch.

If $b_*=\tau_2$, then the slope-$m$ tangent line to $\Gamma(J_2)$ meets
$\Gamma(J_1)$. Thus there are points $s\in J_2$, $t\in J_1$ such that
\[
\det(F(s),F'(s),F(t))=0,
\]
i.e.
\[
K_{21}(s,t)=0.
\]

If $b_*=\tau_1$, then the slope-$m$ tangent line to $\Gamma(J_1)$ meets
$\Gamma(J_2)$. Thus there are points $t\in J_1$, $s\in J_2$ such that
\[
\det(F(t),F'(t),F(s))=0,
\]
i.e.
\[
K_{12}(t,s)=0.
\]
This proves the lemma.
\end{proof}

\begin{lemma}[Strip exclusion for $K_{21}$ against a compact opposite branch]
\label{lem:strip-exclusion-k21}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Let $J_1\Subset I_1$ be a compact subinterval. Then there exists a one-sided
neighborhood $U_2\subset I_2$ of the shared boundary point $h_b$ such that
\[
K_{21}(s,t):=\det(F(s),F'(s),F(t))\neq 0
\qquad
(s\in U_2,\ t\in J_1),
\]
where $F(h)=(c(h),v_5(h),\Delta_7(h))$.
\end{lemma}

\begin{proof}
Work in the affine chart
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
At a generic turning boundary one has
\[
x'(h_b)=0,\qquad x''(h_b)\neq 0,\qquad y'(h_b)\neq 0.
\]
Hence $y$ is a valid local coordinate and the normalized curve may be written
near $h_b$ as a graph
\[
x=\chi(y)
\]
with
\[
\chi'(y_b)=0,\qquad \chi''(y_b)\neq 0.
\]
Thus $x$ has a strict local extremum at the boundary, while the tangent slope
\[
m(h)=\frac{dy/dh}{dx/dh}=\frac{N(h)}{M(h)}
\]
blows up one-sidedly as $h\to h_b$ from either adjacent interval.

Because $J_1\Subset I_1$ is compact away from $h_b$, there exists
$\delta>0$ such that
\[
|x(t)-x(h_b)|\ge 2\delta
\qquad
(t\in J_1).
\]
After shrinking to a small one-sided neighborhood $U_2\subset I_2$ of $h_b$,
we may also assume
\[
|x(s)-x(h_b)|\le \delta
\qquad
(s\in U_2).
\]
Hence
\[
|x(t)-x(s)|\ge \delta
\qquad
(s\in U_2,\ t\in J_1).
\]

Fix a preliminary compact neighborhood $U_2^0\Subset I_2$ of $h_b$ and set
\[
B:=\sup\{|y(t)-y(s)|:\ t\in J_1,\ s\in U_2^0\}<\infty.
\]
Since $m(s)\to \pm\infty$ as $s\to h_b$ in $I_2$, we may shrink further to
$U_2\subset U_2^0$ so that
\[
|m(s)|>\frac{2B}{\delta}
\qquad
(s\in U_2).
\]

If $K_{21}(s,t)=0$, then the tangent line at $\Gamma(s)$ passes through
$\Gamma(t)$, equivalently
\[
y(t)-y(s)=m(s)\bigl(x(t)-x(s)\bigr).
\]
Taking absolute values gives
\[
B\ge |y(t)-y(s)|=|m(s)|\,|x(t)-x(s)|>\frac{2B}{\delta}\cdot \delta=2B,
\]
a contradiction. Therefore $K_{21}(s,t)\neq 0$ on $U_2\times J_1$.
\end{proof}

\begin{lemma}[Strip exclusion for $K_{12}$ against a compact opposite branch]
\label{lem:strip-exclusion-k12}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Let $J_2\Subset I_2$ be a compact subinterval. Then there exists a one-sided
neighborhood $U_1\subset I_1$ of the shared boundary point $h_b$ such that
\[
K_{12}(t,s):=\det(F(t),F'(t),F(s))\neq 0
\qquad
(t\in U_1,\ s\in J_2),
\]
where $F(h)=(c(h),v_5(h),\Delta_7(h))$.
\end{lemma}

\begin{proof}
This is the left-right mirror of Lemma~\ref{lem:strip-exclusion-k21}.
\end{proof}

\begin{lemma}[Compact first-contact for $K_{21}$]
\label{lem:compact-first-contact-k21}
Let $J_1\Subset I_1$, $J_2\Subset I_2$ be compact subintervals across a
generic turning boundary. Assume there is a relatively open collar
$V_2\subset J_2$ at the boundary-facing end of $J_2$ such that
\[
K_{21}(s,t)\neq 0
\qquad
(s\in V_2,\ t\in J_1).
\]
Assume also that the zero set of $K_{21}$ in $J_2\times J_1$ is nonempty.
Then there exists a zero $(s_*,t_*)\in J_2\times J_1$ such that:
\begin{enumerate}
\item $s_*$ is boundary-nearest in the $x=v_5/c$ ordering among all
$s\in J_2$ for which $K_{21}(s,t)=0$ for some $t\in J_1$;
\item
\[
\partial_t K_{21}(s_*,t_*)=0.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
Define
\[
A_{21}:=\{\,s\in J_2:\ \exists\, t\in J_1 \text{ with } K_{21}(s,t)=0\,\}.
\]
Since the zero set of $K_{21}$ in $J_2\times J_1$ is compact and nonempty,
the set $A_{21}$ is compact and nonempty. By hypothesis,
\[
A_{21}\cap V_2=\varnothing.
\]
Hence $A_{21}$ has a boundary-nearest element $s_*$ in the $x=v_5/c$
ordering on $J_2$. Choose $t_*\in J_1$ with
\[
K_{21}(s_*,t_*)=0.
\]

Suppose
\[
\partial_t K_{21}(s_*,t_*)\neq 0.
\]
Then by the implicit function theorem there is a $C^1$ local zero curve
\[
t=t(s)
\]
through $(s_*,t_*)$, defined for $s$ near $s_*$, such that
\[
K_{21}(s,t(s))=0.
\]
Because $s_*\notin V_2$ and $V_2$ is an open collar at the boundary-facing
end of $J_2$, there exist nearby points $s\in J_2$ that are boundary-nearer
than $s_*$ in the $x=v_5/c$ ordering. For such $s$, the point
$(s,t(s))$ is also a zero of $K_{21}$, contradicting the minimality of
$s_*$. Therefore
\[
\partial_t K_{21}(s_*,t_*)=0.
\]
\end{proof}

\begin{lemma}[Compact first-contact for $K_{12}$]
\label{lem:compact-first-contact-k12}
Let $J_1\Subset I_1$, $J_2\Subset I_2$ be compact subintervals across a
generic turning boundary. Assume there is a relatively open collar
$V_1\subset J_1$ at the boundary-facing end of $J_1$ such that
\[
K_{12}(t,s)\neq 0
\qquad
(t\in V_1,\ s\in J_2).
\]
Assume also that the zero set of $K_{12}$ in $J_1\times J_2$ is nonempty.
Then there exists a zero $(t_*,s_*)\in J_1\times J_2$ such that:
\begin{enumerate}
\item $t_*$ is boundary-nearest in the $x=v_5/c$ ordering among all
$t\in J_1$ for which $K_{12}(t,s)=0$ for some $s\in J_2$;
\item
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
Define
\[
A_{12}:=\{\,t\in J_1:\ \exists\, s\in J_2 \text{ with } K_{12}(t,s)=0\,\}.
\]
Since the zero set of $K_{12}$ in $J_1\times J_2$ is compact and nonempty,
the set $A_{12}$ is compact and nonempty. By hypothesis,
\[
A_{12}\cap V_1=\varnothing.
\]
Hence $A_{12}$ has a boundary-nearest element $t_*$ in the $x=v_5/c$
ordering on $J_1$. Choose $s_*\in J_2$ with
\[
K_{12}(t_*,s_*)=0.
\]

Suppose
\[
\partial_s K_{12}(t_*,s_*)\neq 0.
\]
Then by the implicit function theorem there is a $C^1$ local zero curve
\[
s=s(t)
\]
through $(t_*,s_*)$, defined for $t$ near $t_*$, such that
\[
K_{12}(t,s(t))=0.
\]
Because $t_*\notin V_1$ and $V_1$ is an open collar at the boundary-facing
end of $J_1$, there exist nearby points $t\in J_1$ that are boundary-nearer
than $t_*$ in the $x=v_5/c$ ordering. For such $t$, the point
$(t,s(t))$ is also a zero of $K_{12}$, contradicting the minimality of
$t_*$. Therefore
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
\end{proof}

\begin{theorem}[Adjacent pair-pair exclusion across a generic turning boundary]
\label{thm:adjacent-pair-pair-exclusion-turning}
Let $I_1<I_2$ be adjacent ECT intervals meeting at a generic turning boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0.
\]
Then no finite-slope affine line in the chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c}
\]
is $2$-secant to both $\Gamma(I_1)$ and $\Gamma(I_2)$.
\end{theorem}

\begin{proof}
Assume for contradiction that a finite-slope line
\[
L:\ y=mx+b
\]
is $2$-secant to both adjacent branches. By
Lemma~\ref{lem:pair-pair-gives-directional-kernel-zero}, after removing a
small boundary neighborhood there exist compact subintervals
\[
J_1\Subset I_1,\qquad J_2\Subset I_2
\]
and a zero of one of the two directional kernels.

First suppose there exist $s_0\in J_2$, $t_0\in J_1$ such that
\[
K_{21}(s_0,t_0)=0.
\]
By Lemma~\ref{lem:strip-exclusion-k21}, there exists a one-sided neighborhood
$U_2\subset I_2$ of $h_b$ such that
\[
K_{21}(s,t)\neq 0
\qquad
(s\in U_2,\ t\in J_1).
\]
Choose a compact interval $\widetilde J_2\Subset I_2$ containing $s_0$ and
whose boundary-facing collar $V_2$ lies in $U_2$. Then the zero set of
$K_{21}$ in $\widetilde J_2\times J_1$ is nonempty, and
Lemma~\ref{lem:compact-first-contact-k21} yields a zero
\[
(s_*,t_*)\in \widetilde J_2\times J_1
\]
such that
\[
\partial_t K_{21}(s_*,t_*)=0.
\]
Together with $K_{21}(s_*,t_*)=0$, this means that the tangent line at
$\Gamma(s_*)$ is also tangent at $\Gamma(t_*)$. Since
$s_*\in I_2$ and $t_*\in I_1$ are interior points, this gives a common
interior tangent slope across the adjacent branches, contradicting
Proposition~\ref{prop:adjacent-slope-range-separation}.

Now suppose instead there exist $t_0\in J_1$, $s_0\in J_2$ such that
\[
K_{12}(t_0,s_0)=0.
\]
By Lemma~\ref{lem:strip-exclusion-k12}, there exists a one-sided neighborhood
$U_1\subset I_1$ of $h_b$ such that
\[
K_{12}(t,s)\neq 0
\qquad
(t\in U_1,\ s\in J_2).
\]
Choose a compact interval $\widetilde J_1\Subset I_1$ containing $t_0$ and
whose boundary-facing collar $V_1$ lies in $U_1$. Then the zero set of
$K_{12}$ in $\widetilde J_1\times J_2$ is nonempty, and
Lemma~\ref{lem:compact-first-contact-k12} yields a zero
\[
(t_*,s_*)\in \widetilde J_1\times J_2
\]
such that
\[
\partial_s K_{12}(t_*,s_*)=0.
\]
Together with $K_{12}(t_*,s_*)=0$, this means that the tangent line at
$\Gamma(t_*)$ is also tangent at $\Gamma(s_*)$. Again this gives a common
interior tangent slope across the adjacent branches, contradicting
Proposition~\ref{prop:adjacent-slope-range-separation}.

Both cases are impossible. Therefore no finite-slope line is $2$-secant to
both adjacent branches across a generic turning boundary.
\end{proof}

\begin{remark}[What the unconditional adjacent turning theorem does and does not yet replace]
\label{rem:status-adjacent-pair-pair-turning}
Theorem~\ref{thm:adjacent-pair-pair-exclusion-turning} gives an unconditional
exclusion of finite-slope pair-pair lines across a single generic turning
boundary. It is stronger than the older local directional-kernel reduction in
that it bypasses full symmetric zero-capture.

However, it does not by itself replace
Theorem~\ref{thm:partial-global-no-secant}. To obtain a full global no-four-secant
theorem from it, one would still need a separate propagation statement reducing
nonadjacent pair-pair lines to the adjacent turning-boundary case.
\end{remark}

\begin{remark}[Status of the directional-kernel reduction]
\label{rem:audit-directional-kernel-orientation}
Lemma~\ref{lem:pair-pair-gives-directional-kernel-zero} reduces an adjacent
pair-pair line across a generic turning boundary to a compact interior zero of
one of the two directional tangent-separator kernels.

There are now two closures of that reduction in the draft:
\begin{enumerate}
\item Theorem~\ref{thm:adjacent-pair-pair-exclusion-turning} gives an
unconditional closure for actual adjacent pair-pair lines, via strip exclusion
and compact first-contact.

\item Theorem~\ref{thm:conditional-symmetric-directional-kernel-exclusion}
gives a stronger zero-freeness statement for both directional kernels, but only
conditionally on symmetric zero-capture.
\end{enumerate}

Thus orientation selection between $K_{21}$ and $K_{12}$ is no longer the
main issue. What remains open only for the stronger tangent-separator /
support-ordering route is the symmetric zero-capture problem on the full
adjacent rectangle.
\end{remark}

\begin{lemma}[Adjacent support-ordering]
\label{lem:adjacent-support-ordering}
Let $I_1<I_2$ be adjacent ECT intervals under the hypotheses of
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity}. Then, for every
slope $m\in\mathbf R$ such that both fixed-slope intercept sets are nonempty,
\[
\mathcal B_{I_1}(m)\cap \mathcal B_{I_2}(m)=\varnothing.
\]
More precisely, one has one of the two strict alternatives
\[
\sup \mathcal B_{I_1}(m)<\inf \mathcal B_{I_2}(m)
\qquad\text{or}\qquad
\sup \mathcal B_{I_2}(m)<\inf \mathcal B_{I_1}(m),
\]
and the same alternative holds for all such $m$ on the adjacent pair.
\end{lemma}

\begin{proof}
Fix $m$ such that both $\mathcal B_{I_1}(m)$ and $\mathcal B_{I_2}(m)$
are nonempty.

First assume $m$ lies in the interior tangent-slope range of $I_2$. Let
$s\in I_2$ be the unique point with tangent slope $m$. Then by
Lemma~\ref{lem:fixed-slope-intercept-sets},
\[
\tau_{I_2}(m)=\inf \mathcal B_{I_2}(m).
\]
By Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity},
\[
K(s,t)\neq 0
\qquad (t\in I_1).
\]
By Lemma~\ref{lem:affine-form-of-K},
\[
K(s,t)=c(s)^2c(t)x'(s)\bigl(\phi_m(t)-\tau_{I_2}(m)\bigr),
\qquad
\phi_m(t):=y(t)-mx(t).
\]
Since $c(s)^2c(t)x'(s)$ has fixed sign on $I_1$ and $K(s,t)$ is continuous
and nowhere zero there, the quantity
\[
\phi_m(t)-\tau_{I_2}(m)
\]
has constant sign on $I_1$. To determine which sign occurs, move $s$ toward
the common boundary point from inside $I_2$. By
Lemma~\ref{lem:endpoint-tangent-exclusion}, the limiting boundary tangent line
does not meet $I_1$, so $I_1$ lies entirely on one side of that tangent
line. By continuity, the same side persists for nearby interior tangents.
Indeed, if the side changed as the tangency point $s$ moved along $I_2$, then
by the connectedness of $I_2$ and continuity of the tangent-line data there
would exist an intermediate point $s_*\in I_2$ for which the tangent line at
$\Gamma(s_*)$ meets $\Gamma(I_1)$. Equivalently, there would exist
$t_*\in I_1$ such that
\[
K(s_*,t_*)=0,
\]
contradicting Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity}.
Hence the same side holds for all $s\in I_2$. Therefore either
\[
\phi_m(t)<\tau_{I_2}(m)\quad\text{for all }t\in I_1,
\]
or
\[
\phi_m(t)>\tau_{I_2}(m)\quad\text{for all }t\in I_1.
\]
In the first case,
\[
\sup\mathcal B_{I_1}(m)\le \tau_{I_2}(m)=\inf\mathcal B_{I_2}(m),
\]
and since equality would force an intersection with the tangent line, the
inequality is strict. The second case is symmetric.

Now suppose $m$ is not in the interior tangent-slope range of $I_2$, but
both intercept sets are nonempty. Then $m$ lies on one side of the tangent
slope range of $I_2$, so $\phi_m$ is strictly monotone on $I_2$, and
$\mathcal B_{I_2}(m)$ is an interval with endpoint attained in the one-sided
limit at the adjacent boundary. Passing to that boundary-support line and using
Lemma~\ref{lem:endpoint-tangent-exclusion} again shows that $I_1$ lies
strictly on one side of that boundary-support line. Hence the same strict
ordering of intercept sets holds in this case as well.

Thus $\mathcal B_{I_1}(m)$ and $\mathcal B_{I_2}(m)$ are disjoint for every
slope $m$ for which both are nonempty, and the side ordering is constant on
the adjacent pair.
\end{proof}

\begin{theorem}[Partial global no-secant theorem on turning-boundary generic blocks]
\label{thm:partial-global-no-secant}
Assume every adjacent pair of ECT intervals is separated by a generic turning
boundary
\[
M(h_b)=0,\qquad M'(h_b)\neq 0,\qquad N(h_b)\neq 0,
\]
and assume moreover that the zero-capture hypothesis required in
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity} holds for every
adjacent turning-boundary pair.
Then no affine line in the chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c}
\]
is $2$-secant to two distinct ECT intervals. In particular, there is no
global four-secant line for the normalized planar curve $\Gamma(h)$ on such
a turning-boundary generic block.
\end{theorem}

\begin{proof}
Under the stated hypotheses, every adjacent boundary is of turning type and
Theorem~\ref{thm:adjacent-tangent-separator-sign-regularity} applies to each
adjacent pair.
For such adjacent pairs, Lemma~\ref{lem:adjacent-support-ordering} applies.
Hence adjacent fixed-slope intercept sets are strictly ordered. Iterating this
ordering over the $x=v_5/c$ ordering of ECT intervals shows that no affine
line can be $2$-secant to two distinct ECT intervals. Therefore no global
four-secant line exists on the block.
\end{proof}

\begin{corollary}[Partial exclusion of pair-pair branch configurations]
\label{cor:pair-pair-exclusion}
Under the hypotheses of Theorem~\ref{thm:partial-global-no-secant}, a bad
finite core cannot contain two distinct ECT intervals each contributing a pair
of points on a turning-boundary generic block.
\end{corollary}

\begin{proof}
Each ECT interval contributes at most two points to the zero set of an affine
line in the normalized chart, and by
Theorem~\ref{thm:partial-global-no-secant} no affine line can be $2$-secant
to two different ECT intervals on such a block. Therefore a pair-pair
configuration across two distinct ECT intervals is impossible there.
\end{proof}

\begin{remark}[Status of the direct septic witness]
\label{rem:status-direct-septic-witness}
The direct $q^{(7)}$-slice of total $\Delta_7$ is now closed at the
weight-one level by
Proposition~\ref{prop:direct-q7-total-delta7-nonzero}. Together with
Theorem~\ref{thm:quotient-septic-closure}, this closes the canonical
quotient-level order-$7$ package.

What remains non-unique at order $7$ is only the lower/mixed septic
completion of a raw representative pair $(u_7,v_7)$, not any further
canonical quotient-level invariant. Accordingly, order-$7$ is no longer a
live audited obstruction for the later geometric arguments.
\end{remark}

\begin{remark}[Work in progress: highest-new scalar on the direct septic slice]
\label{rem:wip-highest-new-scalar-direct-slice}
On the region $v_5\neq 0$, set
\[
\mu:=\frac{c}{v_5},
\qquad
\lambda:=\frac{\Delta_7}{v_5},
\qquad
\phi:=\lambda^{[1]}.
\]
By Corollary~\ref{cor:direct-q7-septic-slice},
Corollary~\ref{cor:weight-one-septic-reduction}, and
Theorem~\ref{thm:quotient-septic-closure}, the highest-new quotient-level
septic scalar is already reduced to the direct $q^{(7)}$-driven $K_1$-slice:
\[
\Delta_7^{[1]}=v_5\,\phi,
\qquad
\phi
=
\kappa\Bigl(
(x_2-x_1)\nu_6^{(q^{(7)})}
+
v(\gamma_5-\alpha_5)^{(q^{(7)})}
\Bigr).
\]

In the minimal graded model explored in the present worklog, the combined
coefficient is proportional to
\[
\frac{eu\,(a^2+ab-b^2)}{a^2b^4(a+b)^2},
\]
so the highest-new slice is generically nonzero but not manifestly one-signed.
Thus the remaining order-$7$ issue is no longer survival of the canonical
quotient-level witness, but the global line-incidence / slope-recurrence
geometry of the resulting scalar graph.
\end{remark}

\begin{remark}[Status of the $W=0,\ M\neq 0$ side]
\label{rem:audit-w0-affine-inflection}
On the region $c\neq 0,\ M\neq 0$, Proposition~\ref{prop:no-W-flat-interval}
excludes open-interval flatness $W\equiv 0$. At an isolated boundary
\[
W(h_b)=0,\qquad M(h_b)\neq 0,
\]
the normalized planar curve in the chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c}
\]
is an ordinary odd-order affine inflection whenever $W$ changes sign, so
adjacent tangent-separator sign regularity fails there in general.

However, Theorem~\ref{thm:finite-order-w-zero-local-sterility} shows that every
finite-order isolated boundary of type $W=0,\ M\neq 0$ is locally sterile for
pair-pair birth. Thus the remaining issue on this side is not local creation of
a bad $2+2$ line, but global continuation / recurrence of determinant-zero or
tangent-slope data across multiple intervals.

The exact identities for $W$ and $W'$ continue to show that this residual
obstruction is still encoded through the canonical order-$7$ package
$\Delta_7$, not by a genuinely new primitive order-$9$ invariant.
\end{remark}

\begin{remark}[Audit: $W'(h_b)$ at $W=0,\ M\neq 0$]
\label{rem:audit-wprime-at-w0}
At a point $h_b$ with
\[
W(h_b)=0,\qquad M(h_b)\neq 0,
\]
the cubic-inflection coefficient of the normalized planar curve in the
$(\mu,\lambda)$-coordinates is proportional to
\[
W'(h_b).
\]
So $W'(h_b)$ still governs the local simple-inflection jet.

But proving $W'(h_b)=0$ is no longer the main target, because simple
$W=0,\ M\neq 0$ boundaries are already locally benign for pair-pair birth.
The live question is now whether the canonical order-$7$ package imposes any
further global non-recurrence on the associated determinant/tangent-slope data.

At the highest-new level, $[\Delta_7]^{[1]}$ is already reduced to the direct
$q^{(7)}$-driven $K_1$-slice, so the present obstruction is not a new
primitive order-$9$ invariant but a question about global propagation of the
canonical order-$7$ geometry.
\end{remark}

\begin{theorem}[Finite-order $W=0$ boundaries are locally sterile for pair-pair birth]
\label{thm:finite-order-w-zero-local-sterility}
Let $h_b$ satisfy
\[
c(h_b)\neq 0,
\qquad
M(h_b)\neq 0,
\qquad
W(h_b)=0,
\]
and assume that $W$ has finite vanishing order $r\ge 1$ at $h_b$:
\[
W(h)=(h-h_b)^r\,\widetilde W(h),
\qquad
\widetilde W(h_b)\neq 0.
\]
Define
\[
F(h):=(c(h),v_5(h),\Delta_7(h)),
\qquad
D(s,t,u):=\det(F(s),F(t),F(u)).
\]
Then, after shrinking to a sufficiently small neighborhood $U$ of $h_b$,
the following holds.

If $s<t<h_b$ lie in $U$, then:
\begin{enumerate}
\item if $r$ is even, the function $u\mapsto D(s,t,u)$ has no zero on the
opposite side $h_b<u\in U$;
\item if $r$ is odd, the function $u\mapsto D(s,t,u)$ has at most one zero on
the opposite side $h_b<u\in U$.
\end{enumerate}
The same conclusion holds with left and right exchanged. In particular, no
finite-order boundary of type $W=0,\ M\neq 0$ can support a local pair-pair
birth.
\end{theorem}

\begin{proof}
Work in the affine chart
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{\Delta_7(h)}{c(h)}.
\]
Since
\[
x'(h)=\frac{M(h)}{c(h)^2},
\]
the hypothesis $M(h_b)\neq 0$ implies that $x$ is a valid local coordinate
near $h_b$. After translating so that $x(h_b)=0$ and subtracting the tangent
line, we may write the normalized curve as
\[
y=f(x),
\qquad
f(0)=f'(0)=0.
\]

By Proposition~\ref{prop:projective-wronskian-bridge},
\[
\frac{d^2y}{dx^2}=\frac{c(h)^3W(h)}{M(h)^3}.
\]
Because $x'(h_b)\neq 0$, the finite vanishing order of $W$ in $h$ is the same
as its finite vanishing order in the local coordinate $x$. Therefore
\[
f''(x)=\lambda x^r+O(x^{r+1})
\qquad(\lambda\neq 0).
\]

Fix two same-side points
\[
x_1<x_2<0
\]
sufficiently close to $0$, and define
\[
\widehat D(x_1,x_2,u):=
\det\!\begin{pmatrix}
1&x_1&f(x_1)\\
1&x_2&f(x_2)\\
1&u&f(u)
\end{pmatrix}.
\]
Then
\[
\widehat D(x_1,x_2,u)
=
(x_2-x_1)(u-x_1)(u-x_2)\,H_{x_1,x_2}(u),
\]
where
\[
H_{x_1,x_2}(u):=f[x_1,x_2,u]
\]
is the second divided difference of $f$.

If $r$ is even, then $f''$ has fixed sign near $0$. By the Hermite--Genocchi
formula for second divided differences, $H_{x_1,x_2}(u)$ has that same fixed
sign for $u>0$ sufficiently small. Hence $\widehat D(x_1,x_2,u)\neq 0$ on the
opposite side.

If $r$ is odd, then
\[
f'''(x)=\lambda r\,x^{r-1}+O(x^r)
\]
has fixed nonzero sign near $0$, because $r-1$ is even. Differentiating with
respect to the repeated node gives
\[
\partial_u H_{x_1,x_2}(u)=f[x_1,x_2,u,u].
\]
By the Hermite--Genocchi formula for repeated-node divided differences,
$f[x_1,x_2,u,u]$ has the same fixed nonzero sign for $u>0$ sufficiently small.
Thus $u\mapsto H_{x_1,x_2}(u)$ is strictly monotone on the opposite side, and
therefore has at most one zero there.

Finally,
\[
D(s,t,u)=c(s)c(t)c(u)\,\widehat D(x(s),x(t),x(u)),
\]
and $c$ is nonzero on a small neighborhood of $h_b$, so the zero set of $D$
is exactly the zero set of $\widehat D$. The theorem follows.
\end{proof}

\begin{remark}[Consequence for the $W=0,\ M\neq 0$ endgame]
\label{rem:consequence-finite-order-w-zero-local-sterility}
Theorem~\ref{thm:finite-order-w-zero-local-sterility} shows that finite-order
$W=0,\ M\neq 0$ boundaries are not local birthplaces of pair-pair
configurations. Combined with Proposition~\ref{prop:no-W-flat-interval}, this
means the remaining issue on the $W=0$ side is genuinely global: continuation
or recurrence of determinant-zero / tangent-slope data across multiple
intervals, not local creation of a second opposite-side zero branch.
\end{remark}

\begin{remark}[Audit: residual $W=0$ pathology]
\label{rem:audit-residual-w0-pathology}
By Proposition~\ref{prop:no-W-flat-interval}, the $W=0,\ M\neq 0$ side is no
longer obstructed by open-interval flatness $W\equiv 0$ on a component with
$c\neq 0$ and $M\neq 0$. By
Theorem~\ref{thm:finite-order-w-zero-local-sterility}, every finite-order
isolated $W=0$ boundary is locally sterile for pair-pair birth. Thus any
remaining $W=0$ issue would have to come either from non-analytic /
infinite-order flatness or from a genuinely global continuation phenomenon,
not from a generic local inflection birth mechanism.
\end{remark}

\subsection{From the one-pair residual germ to two-pair and minimal-core rigidity}

\begin{remark}[Strengthened organizing principle]
\label{rem:strengthened-organizing-principle}
The original version of this subsection was organized around the cubic leading
line and the first residual trace witness. The later working analysis suggests
a stronger one-pair package:
\[
c(h),\qquad A_5^{\mathfrak f}(h),\qquad \Delta_7(h),
\]
or equivalently the normalized affine curve
\[
h\longmapsto \left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right).
\]
The intended two-pair and minimal-core rigidity statements should ultimately be
reformulated in terms of this strengthened one-pair invariant geometry.
\end{remark}

\begin{remark}[Subsection guide]
\label{rem:wip-multi-pair-subsection}
This subsection is best read as a rigidity program built on the strengthened
one-pair local package
\[
c(h),\qquad A_5^{\mathfrak f}(h),\qquad \Delta_7(h),
\]
or equivalently the normalized planar curve
\[
h\longmapsto \left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right).
\]
The projective coincidence conditions remain the organizing principle for the
two-pair and minimal-core analysis. The finite-order discussion below now
isolates the exact source-level criterion that would force the two-point
quadratic interaction factorization through order $7$, but the current attack
also exhibits two backup lanes: a weaker quotient-diagonal exact exclusion route
and, on good overlap patches, a mixed $\lambda$-shear / projective-shadow
route. Beyond that, the remaining steps are the verification of one of these
two-point lanes, the genuine multi-pair interaction bookkeeping, and the
extraction into the finite-core endgame.
\end{remark}

\begin{remark}[Interpretation of residual notation in the multi-pair architecture]
\label{rem:residual-notation-multipair}
In the remainder of this section, the symbols
\[
F_h(z),\qquad \ell_h,\qquad \overline v_1(h),\qquad
\Qabs/\ell_h
\]
are used schematically to describe the intended cubic-leading / first-residual
architecture of multi-pair and minimal-core configurations.

The fully explicit rigorous first-residual object established earlier is
\[
\mathcal R_h^{(5)}
=
\mathcal J_5/
\bigl(\mathbf C\,A_3(h)+V_{\mathrm{amb}}^{(5)}(h)\bigr).
\]
Accordingly, whenever a later statement invokes the first residual class in a
theorem-strength way, it should be interpreted through $\mathcal R_h^{(5)}$.
The present two-pair subsection now isolates the exact finite-order source
criterion through order $7$ together with two weaker backup routes. What remains
architectural is the verification of one of these two-point routes for the
actual corrected two-atom package, together with its extension to genuine
multi-pair and minimal-bad-core interaction terms.
\end{remark}

Let $F_h(z)$ denote the corrected quotient odd germ of the normalized one-pair
family. By Proposition~\ref{prop:cubic-leading-order}, on the cubic-generic
region we have
\[
F_h(z)=v_0(h)z^3+v_1(h)z^5+\cdots,
\qquad
v_0(h)\neq 0,
\]
with cubic leading line
\[
\ell_h:=\mathbf C\,v_0(h)\subset \Qabs.
\]
Under the additional hypotheses of
Proposition~\ref{prop:first-residual-class-generic}, there is an open dense
subset $\mathcal U_{\mathrm{res}}\subset \mathcal U_{\mathrm{cub}}$ on which
the explicit first residual class
\[
\overline v_1(h)\in\mathcal R_h^{(5)}
\]
is nonzero.

In the strengthened fixed-sector refinement, the one-pair local package is
recorded by
\[
c(h),\qquad A_5^{\mathfrak f}(h)=u_5(h)I+v_5(h)S,\qquad
\Delta_7(h),
\]
and hence by the normalized planar curve
\[
\Gamma(h):=\left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right)
=
\bigl(\rho_1(h),\rho_2(h)\bigr).
\]
By Proposition~\ref{prop:curvature-bridge-normalized-curve}, the affine
curvature numerator of $\Gamma$ is
\[
K_\Gamma(h)
=
\rho_1'(h)\rho_2''(h)-\rho_2'(h)\rho_1''(h)
=
\frac{M(h)N'(h)-N(h)M'(h)}{c(h)^4},
\]
where
\[
M(h)=c(h)v_5'(h)-c'(h)v_5(h),
\qquad
N(h)=c(h)\Delta_7'(h)-c'(h)\Delta_7(h).
\]
Thus the strengthened one-pair geometry is governed by the curve $\Gamma(h)$
and its secant/tangent behavior on the region where
\[
c(h)\neq 0,
\qquad
M(h)\neq 0,
\qquad
M(h)N'(h)-N(h)M'(h)\neq 0.
\]

\begin{definition}[Amplitude-invariant strengthened datum]
\label{def:amplitude-invariant-strengthened-datum}
On the region where
\[
c(h)\neq 0,
\]
define
\[
\widehat\Psi(h):=
\left(
\frac{u_5(h)}{c(h)},
\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)^2}
\right).
\]
\end{definition}

\begin{lemma}[Scaling law for the strengthened package]
\label{lem:scaling-law-strengthened-package}
If the normalized one-pair odd germ is multiplied by a scalar $\lambda$, then
\[
c\longmapsto \lambda c,
\qquad
A_5^{\mathfrak f}\longmapsto \lambda A_5^{\mathfrak f},
\qquad
A_7^{\mathfrak f}\longmapsto \lambda A_7^{\mathfrak f},
\]
and hence
\[
\Delta_7\longmapsto \lambda^2 \Delta_7.
\]
Consequently the datum
\[
\widehat\Psi(h)=
\left(
\frac{u_5(h)}{c(h)},
\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)^2}
\right)
\]
is invariant under scalar rescaling of the full one-pair germ.
\end{lemma}

\begin{proof}
The cubic, quintic, and septic coefficients of the odd germ all scale linearly
under multiplication of the germ by $\lambda$. Since
\[
A_5^{\mathfrak f}=u_5I+v_5S,
\qquad
A_7^{\mathfrak f}=u_7I+v_7S,
\]
it follows that
\[
u_5\mapsto \lambda u_5,\qquad v_5\mapsto \lambda v_5,
\qquad
u_7\mapsto \lambda u_7,\qquad v_7\mapsto \lambda v_7.
\]
Therefore
\[
\Delta_7=u_7v_5-u_5v_7
\]
scales as
\[
\Delta_7\mapsto \lambda^2\Delta_7,
\]
which gives the claim.
\end{proof}

\begin{remark}[Two normalizations: geometric versus projective]
\label{rem:two-normalizations-geometric-vs-projective}
The affine curve
\[
\Gamma(h)=\left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right)
\]
is the correct object for the one-pair differential geometry, because its
derivatives are governed by the projective Wronskians $M$, $N$, and $W$.

For the multi-pair coincidence problem, however, the natural scalar-invariant
datum is $\widehat\Psi(h)$, not $\Gamma(h)$. The reason is exactly the
scaling law in Lemma~\ref{lem:scaling-law-strengthened-package}: under scalar
rescaling of the full one-pair germ, $\Delta_7/c$ is not invariant, whereas
$\Delta_7/c^2$ is.
\end{remark}

In this formulation, the geometric secant/tangent obstruction is well controlled
on ECT intervals and across generic turning-point boundaries. The remaining
global issue is no longer a purely local $W=0,\ M\neq 0$ obstruction, but the
global propagation / recurrence problem for the determinant-zero and tangent
configurations that survive the local sterility results proved later in the
paper.

\begin{definition}[Two-pair decomposition]
\label{def:two-pair-decomposition}
For a normalized two-pair core with amplitudes $a_1,a_2$ and offsets
$h_1,h_2$, write its quotient odd germ schematically as
\[
F_{(a_1,h_1;a_2,h_2)}(z)
=
a_1F_{h_1}(z)+a_2F_{h_2}(z)+\mathcal I_{12}(z),
\]
where $\mathcal I_{12}(z)$ denotes the pair-interaction germ.

In the explicit finite-order corrected source-level model through order $7$
constructed below, the cubic scalar, quintic fixed-sector, and septic
fixed-sector projections of $\mathcal I_{12}$ are quadratic in the amplitudes
and divisible by $(h_1-h_2)^2$.
\end{definition}

\begin{proposition}[Exact strengthened two-pair coincidence through order $7$]
\label{prop:exact-strengthened-two-pair-coincidence}
Let $(a_1,h_1;a_2,h_2)$ be a normalized two-pair core with
\[
F_{(a_1,h_1;a_2,h_2)}(z)\equiv 0.
\]
Assume moreover that, after passage to the explicit corrected finite-order model
through order $7$, the interaction contribution vanishes at the three
relevant levels, namely:
\[
a_1c(h_1)+a_2c(h_2)=0,
\]
\[
a_1A_5^{\mathfrak f}(h_1)+a_2A_5^{\mathfrak f}(h_2)=0,
\]
and, after the second identity identifies the common quotient line
\[
\mathbf C A_5^{\mathfrak f}(h_1)=\mathbf C A_5^{\mathfrak f}(h_2),
\]
the second residual classes satisfy
\[
a_1\,[A_7^{\mathfrak f}](h_1)+a_2\,[A_7^{\mathfrak f}](h_2)=0
\qquad\text{in}\qquad
\mathfrak f/\mathbf C A_5^{\mathfrak f}(h_1).
\]
Then
\[
\widehat\Psi(h_1)=\widehat\Psi(h_2).
\]
Equivalently,
\[
\frac{u_5(h_1)}{c(h_1)}=\frac{u_5(h_2)}{c(h_2)},
\qquad
\frac{v_5(h_1)}{c(h_1)}=\frac{v_5(h_2)}{c(h_2)},
\qquad
\frac{\Delta_7(h_1)}{c(h_1)^2}=\frac{\Delta_7(h_2)}{c(h_2)^2}.
\]
\end{proposition}

\begin{proof}
Set
\[
\lambda:=-\frac{a_2}{a_1}.
\]
The cubic identity gives
\[
c(h_1)=\lambda\,c(h_2).
\]
The quintic fixed-sector identity gives
\[
A_5^{\mathfrak f}(h_1)=\lambda\,A_5^{\mathfrak f}(h_2).
\]
Writing
\[
A_5^{\mathfrak f}(h_i)=u_5(h_i)I+v_5(h_i)S,
\]
we obtain
\[
u_5(h_1)=\lambda\,u_5(h_2),
\qquad
v_5(h_1)=\lambda\,v_5(h_2).
\]
Hence
\[
\frac{u_5(h_1)}{c(h_1)}=\frac{u_5(h_2)}{c(h_2)},
\qquad
\frac{v_5(h_1)}{c(h_1)}=\frac{v_5(h_2)}{c(h_2)}.
\]

Now the second identity implies
\[
\mathbf C A_5^{\mathfrak f}(h_1)=\mathbf C A_5^{\mathfrak f}(h_2),
\]
so the residual quotient spaces are canonically identified. The order-$7$
residual identity therefore says
\[
[A_7^{\mathfrak f}](h_1)=\lambda\,[A_7^{\mathfrak f}](h_2)
\]
in the common quotient. Equivalently, there exists $\mu\in\mathbf C$ such
that
\[
A_7^{\mathfrak f}(h_1)=\lambda\,A_7^{\mathfrak f}(h_2)+\mu\,A_5^{\mathfrak f}(h_2).
\]
Writing
\[
A_7^{\mathfrak f}(h_i)=u_7(h_i)I+v_7(h_i)S,
\]
and using
\[
\Delta_7(h)=u_7(h)v_5(h)-u_5(h)v_7(h),
\]
we obtain
\[
\Delta_7(h_1)
=
\det\!\bigl(A_7^{\mathfrak f}(h_1),A_5^{\mathfrak f}(h_1)\bigr)
=
\det\!\bigl(\lambda A_7^{\mathfrak f}(h_2)+\mu A_5^{\mathfrak f}(h_2),
\lambda A_5^{\mathfrak f}(h_2)\bigr)
=
\lambda^2\Delta_7(h_2).
\]
Since also $c(h_1)=\lambda c(h_2)$, it follows that
\[
\frac{\Delta_7(h_1)}{c(h_1)^2}
=
\frac{\Delta_7(h_2)}{c(h_2)^2}.
\]
Thus $\widehat\Psi(h_1)=\widehat\Psi(h_2)$.
\end{proof}

\begin{theorem}[Quantitative defect-thickened strengthened coincidence]
\label{thm:quantitative-defect-thickened-strengthened-coincidence}
Let $(a_1,h_1;a_2,h_2)$ be a normalized bad two-pair core, and write
\[
c_i:=c(h_i),
\qquad
A_{5,i}^{\mathfrak f}:=A_5^{\mathfrak f}(h_i)=u_{5,i}I+v_{5,i}S,
\qquad
\Delta_i:=\Delta_7(h_i).
\]
Assume
\[
a_1\neq 0,
\qquad
c_1c_2\neq 0.
\]
Suppose the cubic, quintic, and septic quotient defects are written as
\[
a_1c_1+a_2c_2+E_{12}^{(3)}=0,
\]
\[
a_1A_{5,1}^{\mathfrak f}+a_2A_{5,2}^{\mathfrak f}+E_{12}^{(5)}=0,
\]
and
\[
a_1[A_{7,1}^{\mathfrak f}]+a_2[A_{7,2}^{\mathfrak f}]
+\overline E_{12}^{(7;1)}=0
\qquad\text{in}\qquad
\mathfrak f/\mathbf C A_{5,1}^{\mathfrak f}.
\]
Set
\[
\lambda:=-\frac{a_2}{a_1},
\qquad
e:=\frac{E_{12}^{(3)}}{a_1},
\qquad
E:=\frac{E_{12}^{(5)}}{a_1}=e_u I+e_v S.
\]
Choose any representative $R\in\mathfrak f$ of the quotient class
\[
-\frac{1}{a_1}\,\overline E_{12}^{(7;1)},
\]
so that
\[
A_{7,1}^{\mathfrak f}
=
\lambda A_{7,2}^{\mathfrak f}
+
R
+
\eta A_{5,1}^{\mathfrak f}
\]
for some $\eta\in\mathbf C$. Then the strengthened invariant
\[
\widehat\Psi(h)=
\left(
\frac{u_5(h)}{c(h)},
\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)^2}
\right)
\]
satisfies the exact identities
\[
\frac{u_{5,1}}{c_1}-\frac{u_{5,2}}{c_2}
=
\frac{u_{5,2}e-c_2e_u}{c_1c_2},
\]
\[
\frac{v_{5,1}}{c_1}-\frac{v_{5,2}}{c_2}
=
\frac{v_{5,2}e-c_2e_v}{c_1c_2},
\]
and
\[
\frac{\Delta_1}{c_1^2}-\frac{\Delta_2}{c_2^2}
=
\frac{
-\lambda c_2^2\det(A_{7,2}^{\mathfrak f},E)
+
c_2^2\det(R,A_{5,1}^{\mathfrak f})
+
\Delta_2(2\lambda c_2 e-e^2)
}{c_1^2c_2^2}.
\]
\end{theorem}

\begin{proof}
The cubic defect identity gives
\[
c_1=\lambda c_2-e.
\]
The quintic defect identity gives
\[
A_{5,1}^{\mathfrak f}=\lambda A_{5,2}^{\mathfrak f}-E,
\]
hence
\[
u_{5,1}=\lambda u_{5,2}-e_u,
\qquad
v_{5,1}=\lambda v_{5,2}-e_v.
\]
Therefore
\[
\frac{u_{5,1}}{c_1}-\frac{u_{5,2}}{c_2}
=
\frac{u_{5,1}c_2-u_{5,2}c_1}{c_1c_2}
=
\frac{(\lambda u_{5,2}-e_u)c_2-u_{5,2}(\lambda c_2-e)}{c_1c_2}
=
\frac{u_{5,2}e-c_2e_u}{c_1c_2},
\]
and similarly
\[
\frac{v_{5,1}}{c_1}-\frac{v_{5,2}}{c_2}
=
\frac{v_{5,2}e-c_2e_v}{c_1c_2}.
\]

For the third coordinate, by the choice of $R$ we have
\[
A_{7,1}^{\mathfrak f}
=
\lambda A_{7,2}^{\mathfrak f}
+
R
+
\eta A_{5,1}^{\mathfrak f}
\]
for some $\eta\in\mathbf C$. Using
\[
\Delta_i=\det(A_{7,i}^{\mathfrak f},A_{5,i}^{\mathfrak f}),
\]
we obtain
\[
\Delta_1
=
\det(A_{7,1}^{\mathfrak f},A_{5,1}^{\mathfrak f})
=
\lambda\det(A_{7,2}^{\mathfrak f},A_{5,1}^{\mathfrak f})
+
\det(R,A_{5,1}^{\mathfrak f}),
\]
since the $\eta A_{5,1}^{\mathfrak f}$ term drops out. Substituting
\[
A_{5,1}^{\mathfrak f}=\lambda A_{5,2}^{\mathfrak f}-E
\]
gives
\[
\det(A_{7,2}^{\mathfrak f},A_{5,1}^{\mathfrak f})
=
\lambda\Delta_2-\det(A_{7,2}^{\mathfrak f},E),
\]
hence
\[
\Delta_1-\lambda^2\Delta_2
=
-\lambda\det(A_{7,2}^{\mathfrak f},E)
+
\det(R,A_{5,1}^{\mathfrak f}).
\]

Also,
\[
c_1=\lambda c_2-e
\]
implies
\[
\lambda^2c_2^2-c_1^2=2\lambda c_2 e-e^2.
\]
Therefore
\[
\frac{\Delta_1}{c_1^2}-\frac{\Delta_2}{c_2^2}
=
\frac{c_2^2\Delta_1-c_1^2\Delta_2}{c_1^2c_2^2}
=
\frac{
c_2^2(\Delta_1-\lambda^2\Delta_2)+\Delta_2(\lambda^2c_2^2-c_1^2)
}{c_1^2c_2^2},
\]
which is exactly the claimed formula.

Finally, the expression
\[
\det(R,A_{5,1}^{\mathfrak f})
\]
is independent of the chosen representative of the quotient defect, since
replacing $R$ by $R+\xi A_{5,1}^{\mathfrak f}$ does not change the
determinant.
\end{proof}

\begin{corollary}[Bad two-pair cores are defect-scale close on good $M\neq 0$ patches]
\label{cor:bad-two-pair-cores-defect-scale-close}
Let $J\Subset\{c\neq 0,\ M\neq 0\}$ be a compact interval. Assume
\[
|a_1|\ge a_*>0
\]
for the normalized bad two-pair core under consideration. Then there exists a
constant $C_J>0$ such that whenever $h_1,h_2\in J$,
\[
|h_1-h_2|
\le
C_J\Bigl(|E_{12}^{(3)}|+\|E_{12}^{(5)}\|\Bigr).
\]
In particular, on good $M\neq 0$ patches, bad two-pair cores force the two
parameters to be quantitatively close once the cubic/quintic interaction
defects are small.
\end{corollary}

\begin{proof}
The second coordinate of $\widehat\Psi$ is
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
x'(h)=\frac{M(h)}{c(h)^2}.
\]
Since $J\Subset\{c\neq 0,\ M\neq 0\}$, there exists $\eta_J>0$ such that
\[
|x(h_1)-x(h_2)|\ge \eta_J\,|h_1-h_2|
\qquad
(h_1,h_2\in J).
\]
On the other hand, Theorem~\ref{thm:quantitative-defect-thickened-strengthened-coincidence}
gives the exact identity
\[
x(h_1)-x(h_2)
=
\frac{v_{5,2}e-c_2e_v}{c_1c_2},
\]
with
\[
e=\frac{E_{12}^{(3)}}{a_1},
\qquad
e_v=\text{$S$-coefficient of } \frac{E_{12}^{(5)}}{a_1}.
\]
Since $J$ is compact and $a_1$ is bounded away from $0$, the right-hand
side is bounded by
\[
C'_J\Bigl(|E_{12}^{(3)}|+\|E_{12}^{(5)}\|\Bigr)
\]
for some constant $C'_J$. Combining the two estimates yields the claim.
\end{proof}

\begin{proposition}[No sublinear two-pair defects on good patches]
\label{prop:no-sublinear-two-pair-defects-good-patch}
Let
\[
J\Subset\{c\neq 0,\ M\neq 0\}
\]
be a compact interval. Then there exists a constant $C_J>0$ such that every
normalized bad two-pair core with $h_1,h_2\in J$ and $h_1\neq h_2$
satisfies
\[
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|+\bigl|\overline E_{12}^{(7;1)}\bigr|
\ge
C_J^{-1}\,|h_1-h_2|.
\]
In particular, there is no sequence of nontrivial normalized bad two-pair
cores in $J$ for which
\[
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|+\bigl|\overline E_{12}^{(7;1)}\bigr|
=
o\!\left(|h_1-h_2|\right).
\]
\end{proposition}

\begin{proof}
By Corollary~\ref{cor:bad-two-pair-cores-defect-scale-close}, there exists a
constant $C'_J>0$ such that
\[
|h_1-h_2|
\le
C'_J\Bigl(|E_{12}^{(3)}|+\|E_{12}^{(5)}\|\Bigr)
\]
for every normalized bad two-pair core with $h_1,h_2\in J$. Since
\[
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|
\le
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|+\bigl|\overline E_{12}^{(7;1)}\bigr|,
\]
the same estimate yields
\[
|h_1-h_2|
\le
C'_J\Bigl(
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|+\bigl|\overline E_{12}^{(7;1)}\bigr|
\Bigr).
\]
Renaming $C'_J$ as $C_J$ proves the first claim. The final statement is
immediate: if a sequence satisfied
\[
|E_{12}^{(3)}|+\|E_{12}^{(5)}\|+\bigl|\overline E_{12}^{(7;1)}\bigr|
=
o\!\left(|h_1-h_2|\right),
\]
then the displayed lower bound would force
\[
|h_1-h_2|=o\!\left(|h_1-h_2|\right),
\]
which is impossible for a nontrivial two-point core with $h_1\neq h_2$.
\end{proof}

\begin{lemma}[Minimal finite-order source criterion for quadratic two-point factorization]
\label{lem:minimal-source-level-two-point-criterion}
Let $V$ be a finite-dimensional complex vector space, and let
\[
\mathfrak P_2(a_1,h_1;a_2,h_2)\in V
\]
be analytic on a neighborhood of the small two-atom data. Assume that there is
a one-atom package
\[
F_h\in V
\]
such that the following three identities hold:
\[
\mathfrak P_2(a_1,h_1;a_2,h_2)
=
\mathfrak P_2(a_2,h_2;a_1,h_1),
\]
\[
\mathfrak P_2(0,h_1;a_2,h_2)=a_2F_{h_2},
\qquad
\mathfrak P_2(a_1,h_1;0,h_2)=a_1F_{h_1},
\]
and
\[
\mathfrak P_2(a_1,h;a_2,h)=(a_1+a_2)F_h.
\]
Define the interaction remainder
\[
\mathcal I_2(a_1,h_1;a_2,h_2)
:=
\mathfrak P_2(a_1,h_1;a_2,h_2)-a_1F_{h_1}-a_2F_{h_2}.
\]
Then there exists an analytic map
\[
\mathcal J_2:\ (\text{small two-atom data})\to V
\]
such that
\[
\boxed{
\mathcal I_2(a_1,h_1;a_2,h_2)
=
a_1a_2(h_1-h_2)^2\,\mathcal J_2(a_1,h_1;a_2,h_2).
}
\]
\end{lemma}

\begin{proof}
By the one-amplitude collapse identities,
\[
\mathcal I_2(0,h_1;a_2,h_2)=0,
\qquad
\mathcal I_2(a_1,h_1;0,h_2)=0.
\]
Hence analyticity implies divisibility by $a_1a_2$:
\[
\mathcal I_2(a_1,h_1;a_2,h_2)=a_1a_2\,G(h_1,h_2)
\]
for an analytic
\[
G:\ (h_1,h_2)\longmapsto V.
\]
Swap symmetry gives
\[
G(h_1,h_2)=G(h_2,h_1).
\]
On the diagonal,
\[
\mathcal I_2(a_1,h;a_2,h)
=
\mathfrak P_2(a_1,h;a_2,h)-a_1F_h-a_2F_h
=
(a_1+a_2)F_h-a_1F_h-a_2F_h
=
0,
\]
so
\[
G(h,h)=0.
\]
Now set
\[
m=\frac{h_1+h_2}{2},
\qquad
s=h_2-h_1,
\qquad
\widetilde G(m,s):=
G\!\left(m-\frac{s}{2},m+\frac{s}{2}\right).
\]
Since $G$ is symmetric, $\widetilde G(m,s)$ is even in $s$, and since
$G(h,h)=0$, one has
\[
\widetilde G(m,0)=0.
\]
Therefore $\widetilde G(m,s)$ is divisible by $s^2$:
\[
\widetilde G(m,s)=s^2H(m,s)
\]
for analytic $H$. Returning to $(h_1,h_2)$ gives
\[
\mathcal I_2(a_1,h_1;a_2,h_2)
=
a_1a_2(h_1-h_2)^2\,\mathcal J_2(a_1,h_1;a_2,h_2),
\]
as claimed.
\end{proof}

\begin{corollary}[Conditional quadratic defect estimate and two-point exclusion]
\label{cor:conditional-quadratic-defect-estimate-two-point-exclusion}
Assume that the actual corrected two-pair finite-order package through order $7$
admits a source-level realization
\[
\mathfrak P_2(a_1,h_1;a_2,h_2)
\in
\mathbf C\oplus \mathfrak f\oplus
\bigl(\mathfrak f/\mathbf C A_5^{\mathfrak f}\bigr)
\]
satisfying the three hypotheses of
Lemma~\ref{lem:minimal-source-level-two-point-criterion}, with
\[
F_h=
\bigl(c(h),A_5^{\mathfrak f}(h),[A_7^{\mathfrak f}](h)\bigr).
\]
Then on compacta,
\[
\mathcal E^{(3)}=a_1a_2\,O(\delta^2),
\qquad
\mathcal E^{(5)}=a_1a_2\,O(\delta^2),
\qquad
\overline{\mathcal E}^{(7)}=a_1a_2\,O(\delta^2),
\qquad
\delta:=|h_1-h_2|.
\]
If the normalized defects are obtained by dividing by $a_1$, then on normalized
families with $|a_2|$ bounded one has
\[
E_{12}^{(3)}=O(\delta^2),
\qquad
E_{12}^{(5)}=O(\delta^2),
\qquad
\overline E_{12}^{(7;1)}=O(\delta^2).
\]
Consequently, the two-point bad-core branch is excluded on compact good patches
\[
J\Subset\{c\neq 0,\ M\neq 0\}.
\]
\end{corollary}

\begin{proof}
Apply Lemma~\ref{lem:minimal-source-level-two-point-criterion} to the cubic,
quintic fixed-sector, and septic quotient outputs, then argue exactly as in the
present proof using
Theorem~\ref{thm:quantitative-defect-thickened-strengthened-coincidence}.
\end{proof}

\begin{proposition}[Conditional exact two-point exclusion from quotient diagonal collapse]
\label{prop:conditional-exact-two-point-exclusion-qabs}
Let
\[
J\Subset\{c\neq 0\}
\]
be a compact interval. Assume there exists an actual corrected two-atom quotient
map
\[
\mathcal F_2(a_1,h_1;a_2,h_2)\in \Qabs[[z^2]]
\]
defined on normalized two-pair data, with the following properties:

\begin{enumerate}
\item \textbf{Continuity.}
The map $\mathcal F_2$ is continuous in the normalized two-pair parameters.

\item \textbf{Diagonal collapse.}
For every $h\in J$ and every normalized amplitude pair $(a_1,a_2)$,
\[
\mathcal F_2(a_1,h;a_2,h)=F_h,
\]
where $F_h$ is the normalized one-pair quotient odd germ.

\item \textbf{Precompactness of normalized amplitudes.}
Every sequence of normalized two-pair data with
\[
h_{1,n},h_{2,n}\in J,
\qquad
|h_{1,n}-h_{2,n}|\to 0
\]
admits a subsequence along which the full normalized parameter tuple converges.
\end{enumerate}

Then there is no sequence of nontrivial normalized bad two-pair cores
\[
(a_{1,n},h_{1,n};a_{2,n},h_{2,n})
\]
with
\[
h_{1,n},h_{2,n}\in J,
\qquad
0<|h_{1,n}-h_{2,n}|\to 0.
\]
Equivalently, under the three assumptions above, the exact close two-point
bad-core branch is excluded on compact subsets of $\{c\neq 0\}$.
\end{proposition}

\begin{proof}
Assume for contradiction that there exists a sequence of nontrivial normalized
bad two-pair cores
\[
(a_{1,n},h_{1,n};a_{2,n},h_{2,n})
\]
with
\[
h_{1,n},h_{2,n}\in J,
\qquad
0<|h_{1,n}-h_{2,n}|\to 0.
\]
Since each core is bad, its quotient odd germ vanishes identically, so
\[
\mathcal F_2(a_{1,n},h_{1,n};a_{2,n},h_{2,n})=0
\qquad
\text{for all }n.
\]

By the precompactness assumption, after passing to a subsequence we may assume
that the full normalized parameter tuple converges:
\[
a_{1,n}\to a_1^*,
\qquad
a_{2,n}\to a_2^*,
\qquad
h_{1,n}\to m,
\qquad
h_{2,n}\to m
\]
for some $m\in J$. By continuity of $\mathcal F_2$,
\[
0
=
\lim_{n\to\infty}
\mathcal F_2(a_{1,n},h_{1,n};a_{2,n},h_{2,n})
=
\mathcal F_2(a_1^*,m;a_2^*,m).
\]
Applying diagonal collapse gives
\[
0=\mathcal F_2(a_1^*,m;a_2^*,m)=F_m.
\]

But $m\in J\Subset\{c\neq 0\}$, so the normalized one-pair quotient germ
$F_m$ is nonzero: its cubic leading coefficient is nonzero on $\{c\neq 0\}$.
This contradiction proves the claim.
\end{proof}

\begin{remark}[A weaker exact two-point route]
\label{rem:weaker-exact-two-point-route}
Proposition~\ref{prop:conditional-exact-two-point-exclusion-qabs} is strictly
weaker than the quadratic defect-factorization route of
Lemma~\ref{lem:minimal-source-level-two-point-criterion}. It does not produce
\[
\mathcal I_2=a_1a_2(h_1-h_2)^2\mathcal J_2
\]
and does not yield the quantitative defect estimates used in
Theorem~\ref{thm:quantitative-defect-thickened-strengthened-coincidence}.
Instead, it isolates a smaller alternative input: a genuine corrected two-atom
quotient map, continuity in normalized parameters, and exact diagonal collapse
to the one-pair quotient class.

Thus there are now two distinct two-point routes in the draft:

\begin{enumerate}
\item the stronger finite-order source-level route, which would force quadratic
defect bounds and hence quantitative defect-scale closeness;

\item the weaker quotient-diagonal route, which would already exclude exact
close two-point bad cores on compact subsets of $\{c\neq 0\}$.
\end{enumerate}

At present, the draft does not prove either route outright. The first remains a
finite-order source-level merger problem; the second remains a continuity and
diagonal-collapse problem for the actual corrected two-atom quotient germ.
\end{remark}

\begin{remark}[Exact remaining source-level input on the two-point branch]
\label{rem:wip-source-level-reduction-two-point-branch}
Lemma~\ref{lem:minimal-source-level-two-point-criterion} isolates the exact
finite-order source identities needed for the two-point branch. It is enough to
verify, for the actual corrected two-pair cubic/quintic/septic package, only:

\begin{enumerate}
\item swap symmetry;
\item one-amplitude collapse;
\item diagonal merger
\[
\mathfrak P_2(a_1,h;a_2,h)=(a_1+a_2)F_h.
\]
\end{enumerate}

Once these identities are known, the quadratic factorization
\[
\mathcal I_2=a_1a_2(h_1-h_2)^2\mathcal J_2
\]
is formal. So the remaining issue on the two-point branch is not another
asymptotic estimate, but verification of this finite-order source-level merger
statement for the corrected two-atom package.
\end{remark}

\begin{remark}[Audit: even-amplitude obstruction for the naive source-summed model]
\label{rem:audit-even-amplitude-obstruction-naive-source-summed-two-point}
The most obvious attempt to prove the source-level merger theorem is to insert a
weighted one-atom datum
\[
q_{a,h}=a\,q_h,
\qquad
\Phi_{a,h}=a\,\Phi_h
\]
directly into the corrected same-point and mixed block formulas, whiten, and
then extract the cubic/quintic/septic outputs. This route cannot by itself
prove the required one-atom linearity
\[
\mathfrak P_2(a\delta_h)=a\,F_h.
\]

Indeed the explicit corrected block formulas have the form
\[
G^{\corr}_{a,h,\pm}(s)=a\,\mathcal G_{h,\pm}(a^2;s),
\qquad
N^{\corr}_{a,h}(s)=a\,\mathcal N_h(a^2;s),
\]
so after whitening the overall factor of $a$ cancels:
\[
\widehat\Omega^{\corr}_{a,h}(s)
=
\mathcal G_{h,-}(a^2;s)^{-1/2}\,
\mathcal N_h(a^2;s)\,
\mathcal G_{h,+}(a^2;s)^{-1/2}.
\]
Hence every fixed finite-order coefficient extracted from the whitened block is
an even analytic function of the source weight $a$. In particular, the naive
source-summed corrected block package cannot satisfy analytic one-atom linearity
or coincident-atom additivity unless it vanishes identically. So the remaining
two-point theorem must be proved using a different lift/transport object, not
the raw source-summed whitened coefficients themselves.
\end{remark}

\begin{remark}[Audit: quotient and single-determinant routes are shear-blind]
\label{rem:audit-shear-blind-two-point-determinantal-routes}
On the mixed two-point branch, any route based only on cubic/quintic source
minors,
the septic quotient class,
or the pointwise patch gauges $v_7=0$ and $u_7=0$ is exactly blind to the
repeated-node shear parameter.

For an exact bad two-pair core, the cubic/quintic defect vector has the form
\[
d=\Lambda s_2-s_1,
\qquad
\Lambda:=-\frac{a_2}{a_1},
\qquad
s_i=(c_i,u_{5,i},v_{5,i}),
\]
so
\[
s_2\wedge d=s_1\wedge s_2
\]
is independent of $\Lambda$. Likewise, any pointwise representative extracted
only from the septic quotient class and $A_{5,1}^{\mathfrak f}$ carries no more
information than the same determinant scalar already seen by the quotient. Thus
the remaining mixed two-point burden is genuinely source-coupled rather than
quotient-determinantal.
\end{remark}

\begin{proposition}[Projective compactness of the moving $\lambda$-shear defects]
\label{prop:projective-compactness-moving-lambda-shear-two-point}
Assume a close exact mixed two-point bad branch on a compact good overlap patch
\[
U\Subset\{c\neq 0,\ v_5\neq 0,\ M\neq 0\},
\]
and write
\[
\Lambda_n:=-\frac{a_{2,n}}{a_{1,n}},
\qquad
\delta_n f:=f(h_{1,n})-\Lambda_n f(h_{2,n}),
\qquad
\lambda=\frac{\Delta_7}{v_5}.
\]
Then the mixed branch equations are equivalent to the existence of branch-generated
moving shears $(\eta_n,\xi_n,\gamma_n)$ such that
\[
\delta_n(c)=\eta_n\,\delta_n(\lambda),\qquad
\delta_n(v_5)=\xi_n\,\delta_n(\lambda),\qquad
\delta_n(u_5)=\gamma_n\,\delta_n(\lambda).
\]

Set
\[
d_n:=\bigl(\delta_n(c),\delta_n(v_5),\delta_n(u_5),\delta_n(\lambda)\bigr)\in\mathbf R^4.
\]
Then, after passing to a subsequence, exactly one of the following holds.

\begin{enumerate}
\item
$d_n=0$ for all $n$ in the subsequence. Equivalently, along that subsequence one already has exact repeated-source transport simultaneously for
\[
c,\qquad v_5,\qquad u_5,\qquad \lambda.
\]

\item
$d_n\neq 0$ for all $n$ in the subsequence, and the normalized defect directions
\[
\widehat d_n:=\frac{d_n}{\|d_n\|}\in S^3
\]
converge. Equivalently, the projective classes
\[
[d_n]
=
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)]
\in \mathbf P^3
\]
admit a convergent subsequence.
\end{enumerate}

Moreover, on any subsequence for which $\delta_n(\lambda)\neq 0$ and the projective
limit lies in the affine chart with nonzero $\lambda$-coordinate, the affine
$\lambda$-shears converge:
\[
\eta_n=\frac{\delta_n(c)}{\delta_n(\lambda)}\to\eta_*,
\qquad
\xi_n=\frac{\delta_n(v_5)}{\delta_n(\lambda)}\to\xi_*,
\qquad
\gamma_n=\frac{\delta_n(u_5)}{\delta_n(\lambda)}\to\gamma_*.
\]

For the limiting affine shear one has only the asymptotic fixed-shear identities
\[
\delta_n(c-\eta_*\lambda)=(\eta_n-\eta_*)\,\delta_n(\lambda),
\]
\[
\delta_n(v_5-\xi_*\lambda)=(\xi_n-\xi_*)\,\delta_n(\lambda),
\]
\[
\delta_n(u_5-\gamma_*\lambda)=(\gamma_n-\gamma_*)\,\delta_n(\lambda).
\]
Hence a close exact mixed branch automatically reduces only to a
\emph{projectively frozen secant-shadow problem}. In general it does \emph{not}
reduce to exact repeated-source transport for a single fixed triple
\[
(\eta_*,\xi_*,\gamma_*).
\]
\end{proposition}

\begin{proof}
The identities
\[
\delta_n(c)=\eta_n\,\delta_n(\lambda),\qquad
\delta_n(v_5)=\xi_n\,\delta_n(\lambda),\qquad
\delta_n(u_5)=\gamma_n\,\delta_n(\lambda)
\]
are just a rewriting of the branch equations. If $d_n=0$ infinitely often, pass
to that subsequence. Otherwise $d_n\neq 0$ for all large $n$, and compactness of
the unit sphere gives a convergent subsequence of $\widehat d_n$, equivalently
of the associated projective classes in $\mathbf P^3$.

On the affine chart $\delta_n(\lambda)\neq 0$, the projective coordinates are
exactly
\[
\eta_n=\frac{\delta_n(c)}{\delta_n(\lambda)},\qquad
\xi_n=\frac{\delta_n(v_5)}{\delta_n(\lambda)},\qquad
\gamma_n=\frac{\delta_n(u_5)}{\delta_n(\lambda)},
\]
so convergence in that chart is precisely convergence of the affine
$\lambda$-shears. The last three identities are immediate from the definitions.
\end{proof}

\begin{remark}[Affine freezing is stronger than projective freezing on the mixed two-point branch]
\label{rem:affine-freezing-stronger-than-projective-two-point}
Proposition~\ref{prop:projective-compactness-moving-lambda-shear-two-point}
shows that the automatic compactness on the mixed two-point branch is
projective, not affine. Even on a good overlap patch, the affine
$\lambda$-shears can diverge if $\delta_n(\lambda)$ vanishes to higher order
than $\delta_n(c),\delta_n(v_5),\delta_n(u_5)$. And even when
\[
(\eta_n,\xi_n,\gamma_n)\to(\eta_*,\xi_*,\gamma_*),
\]
one gets only asymptotic transport for
\[
c-\eta_*\lambda,\qquad
v_5-\xi_*\lambda,\qquad
u_5-\gamma_*\lambda,
\]
not exact transport at each stage of the branch. Therefore the downstream
derivative-geometric reduction should be formulated in terms of the projective
defect direction
\[
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)],
\]
or equivalently in any affine chart on which the projective limit has nonzero
coordinate, rather than as an exact frozen-$\lambda$ repeated-source branch.
\end{remark}

\begin{remark}[What remains in the two-pair rewrite]
\label{rem:what-remains-two-pair-rewrite}
Theorem~\ref{thm:quantitative-defect-thickened-strengthened-coincidence}
supplies the algebraic bridge from the two-pair core to the strengthened
invariant $\widehat\Psi$, and
Lemma~\ref{lem:minimal-source-level-two-point-criterion} isolates the exact
finite-order source criterion that would close the two-point branch on compact
good patches.

Thus the remaining issue beyond the present two-pair subsection is no longer a
vague interaction heuristic. There are now three precise conditional routes on
the two-point side.

First, the stronger finite-order source-level merger route would force the
quadratic defect estimates and hence the defect-scale closeness theorem on good
patches.

Second, the weaker quotient-diagonal route would already exclude exact close
two-point bad cores on compact subsets of $\{c\neq 0\}$ if one had a genuine
corrected two-atom quotient germ with continuity and exact diagonal collapse.

Third, on a good overlap patch in the mixed regime, the derivative-geometric
attack now naturally passes through the moving $\lambda$-sheared source
transport system
\[
(c-\eta_n\lambda)(h_{1,n})=\Lambda_n(c-\eta_n\lambda)(h_{2,n}),
\qquad
(v_5-\xi_n\lambda)(h_{1,n})=\Lambda_n(v_5-\xi_n\lambda)(h_{2,n}),
\qquad
(u_5-\gamma_n\lambda)(h_{1,n})=\Lambda_n(u_5-\gamma_n\lambda)(h_{2,n}),
\]
with
\[
\lambda=\frac{\Delta_7}{v_5},
\qquad
\Lambda_n=-\frac{a_{2,n}}{a_{1,n}}.
\]
By Proposition~\ref{prop:projective-compactness-moving-lambda-shear-two-point},
what is automatic from an exact close mixed branch is not affine freezing of
\[
(\eta_n,\xi_n,\gamma_n),
\]
but projective compactness of the defect directions
\[
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)],
\qquad
\delta_n(f):=f(h_{1,n})-\Lambda_n f(h_{2,n}).
\]
On any subsequence whose projective limit lies in the affine $\lambda$-chart,
one obtains a convergent affine $\lambda$-shear subsequence; in general the
exact frozen repeated-source reduction is not automatic. The associated
projective secant shadow can nevertheless accumulate only on
\[
\{S=0\}\cup\{K_v=0\},
\qquad
S=\frac{\Delta_7}{c\,v_5}.
\]

So the genuinely remaining two-point work is either the verification of the
finite-order source-level merger criterion, the construction of the actual
corrected two-atom quotient germ with continuity and exact diagonal collapse,
or the source-coupling analysis of the mixed $\lambda$-shear route on those
explicit exceptional loci. Beyond that lie the genuinely multi-pair interaction
bookkeeping through orders $3,5,7$, the local lifted $3/4$-point analysis for
close-point branches on the $v_5\neq 0$ and parallel $u_5\neq 0$ patches, and
the subsequent finite-core extraction.
\end{remark}

\begin{remark}[Minimal-core reformulation]
\label{rem:minimal-core-reformulation}
The proposition above shows that the correct projective datum for the downstream
multi-pair and minimal-core extraction is the amplitude-invariant strengthened
map
\[
\widehat\Psi(h)=
\left(
\frac{u_5(h)}{c(h)},
\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)^2}
\right),
\]
not merely the pair $(\ell_h,\overline v_1(h))$.

By contrast, the affine curve
\[
\Gamma(h)=\left(\frac{v_5(h)}{c(h)},\frac{\Delta_7(h)}{c(h)}\right)
\]
remains the correct object for the one-pair secant/tangent geometry. The
finite-core endgame should therefore be viewed as a two-stage problem:
first extract defect-corrected coincidence information for $\widehat\Psi$,
then convert that information into affine-line incidence constraints for
$\Gamma$.
\end{remark}

\begin{definition}[Minimal bad core]
\label{def:minimal-bad-core}
A normalized finite core is called bad if its quotient odd germ vanishes
identically. A minimal bad core is a bad normalized finite core with minimal
number of constituent pairs.
\end{definition}

\begin{theorem}[Defect-free quintic circuit reduction]
\label{thm:defect-free-quintic-circuit-reduction}
Let
\[
F_{\core}(z)=\sum_{j=1}^k a_jF_{h_j}(z)+\mathcal I_{\ge 2}(z)
\]
be a normalized finite core, and assume that the multi-pair interaction germ
$\mathcal I_{\ge 2}(z)$ contributes nothing to the cubic and quintic
coefficients. Write
\[
A_5^{\mathfrak f}(h)=u_5(h)I+v_5(h)S,
\qquad
V(h):=\bigl(c(h),u_5(h),v_5(h)\bigr)\in\mathbf C^3,
\]
and on $\{c\neq 0\}$ define
\[
\Xi(h):=\left(\frac{u_5(h)}{c(h)},\frac{v_5(h)}{c(h)}\right)\in\mathbf C^2.
\]
If
\[
F_{\core}(z)\equiv 0,
\]
then
\[
\sum_{j=1}^k a_j\,V(h_j)=0.
\]
Equivalently, with
\[
b_j:=a_j\,c(h_j),
\]
one has
\[
\sum_{j=1}^k b_j=0,
\qquad
\sum_{j=1}^k b_j\,\Xi(h_j)=0.
\]
Thus the points $\Xi(h_j)$ are affinely dependent.
\end{theorem}

\begin{proof}
Taking the cubic coefficient in the identity
\[
F_{\core}(z)\equiv 0
\]
and using the hypothesis that $\mathcal I_{\ge2}$ contributes nothing at
cubic order gives
\[
\sum_{j=1}^k a_j\,c(h_j)=0.
\]
Taking the quintic fixed-sector coefficient and using the corresponding
defect-free hypothesis at order $5$ gives
\[
\sum_{j=1}^k a_j\,A_5^{\mathfrak f}(h_j)=0.
\]
Since
\[
A_5^{\mathfrak f}(h_j)=u_5(h_j)I+v_5(h_j)S
\]
and $I,S$ are linearly independent, this is equivalent to
\[
\sum_{j=1}^k a_j\,u_5(h_j)=0,
\qquad
\sum_{j=1}^k a_j\,v_5(h_j)=0.
\]
Together these three identities are exactly
\[
\sum_{j=1}^k a_j\,V(h_j)=0.
\]
If $c(h_j)\neq 0$ for all $j$, dividing the last two identities by
$c(h_j)$ after setting $b_j=a_jc(h_j)$ yields
\[
\sum_{j=1}^k b_j=0,
\qquad
\sum_{j=1}^k b_j\,\Xi(h_j)=0,
\]
which is the affine dependence statement.
\end{proof}

\begin{corollary}[Defect-free minimal quintic circuits have size at most four]
\label{cor:defect-free-minimal-quintic-circuits}
In the defect-free order-$\le 5$ model of
Theorem~\ref{thm:defect-free-quintic-circuit-reduction}, every minimal bad
core has size at most $4$. More precisely:
\begin{enumerate}
\item if $k=2$, then $\Xi(h_1)=\Xi(h_2)$;
\item if $k=3$, then the three points $\Xi(h_1),\Xi(h_2),\Xi(h_3)$ are
collinear;
\item if $k=4$, then the four points $\Xi(h_1),\dots,\Xi(h_4)$ form an
affine circuit in $\mathbf C^2$.
\end{enumerate}
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:defect-free-quintic-circuit-reduction}, a minimal
defect-free bad core produces a minimal affine dependence among finitely many
points of the affine plane $\mathbf C^2$. Such a minimal affine dependent
set has size at most $4$. The cases $k=2,3,4$ are the standard affine
configurations in dimension $2$: coincidence, collinear triple, or
four-point affine circuit.
\end{proof}

\begin{definition}[Lifted $v_5$-patch coordinates]
\label{def:lifted-v-patch-coordinates}
On a connected interval $U\subset\{c\neq 0,\ v_5\neq 0\}$, define
\[
x(h):=\frac{v_5(h)}{c(h)},
\qquad
y(h):=\frac{u_5(h)}{c(h)},
\qquad
\sigma_v(h):=\frac{\Delta_7(h)}{c(h)\,v_5(h)}.
\]
The associated lifted planar and space curves are
\[
\Lambda_v(h):=\bigl(x(h),\sigma_v(h)\bigr)\in\mathbf C^2,
\qquad
Q_v(h):=\bigl(y(h),x(h),\sigma_v(h)\bigr)\in\mathbf C^3.
\]
\end{definition}

\begin{proposition}[Defect-free lifted affine dependence on a $v_5$-patch]
\label{prop:defect-free-lifted-affine-dependence-vpatch}
Let
\[
F_{\core}(z)=\sum_{j=1}^k a_jF_{h_j}(z)+\mathcal I_{\ge 2}(z)
\]
be a normalized finite core, and assume:
\begin{enumerate}
\item all parameters $h_j$ lie in one connected interval
$U\subset\{c\neq 0,\ v_5\neq 0\}$;
\item the multi-pair interaction germ $\mathcal I_{\ge2}(z)$ contributes
nothing to the cubic, quintic, or septic coefficients.
\end{enumerate}
Then, after choosing on $U$ the local septic gauge $v_7=0$, the vanishing
identity
\[
F_{\core}(z)\equiv 0
\]
implies
\[
\sum_{j=1}^k b_j=0,
\qquad
\sum_{j=1}^k b_j\,y(h_j)=0,
\qquad
\sum_{j=1}^k b_j\,x(h_j)=0,
\qquad
\sum_{j=1}^k b_j\,\sigma_v(h_j)=0,
\]
where $b_j:=a_jc(h_j)$. Equivalently, the points $Q_v(h_j)\in\mathbf C^3$
are affinely dependent.
\end{proposition}

\begin{proof}
The cubic and quintic identities are exactly those in
Theorem~\ref{thm:defect-free-quintic-circuit-reduction}, so after setting
$b_j=a_jc(h_j)$ we obtain
\[
\sum_{j=1}^k b_j=0,
\qquad
\sum_{j=1}^k b_j\,y(h_j)=0,
\qquad
\sum_{j=1}^k b_j\,x(h_j)=0.
\]
On the interval $U$ we may choose the local septic gauge $v_7=0$. Then
\[
u_7(h)=\frac{\Delta_7(h)}{v_5(h)}=c(h)\,\sigma_v(h).
\]
Since the septic interaction is assumed absent, taking the septic fixed-sector
coefficient of $F_{\core}\equiv 0$ yields
\[
\sum_{j=1}^k a_j\,u_7(h_j)=0.
\]
Substituting $u_7(h_j)=c(h_j)\sigma_v(h_j)$ gives
\[
\sum_{j=1}^k b_j\,\sigma_v(h_j)=0.
\]
Hence the points $Q_v(h_j)$ are affinely dependent.
\end{proof}

\begin{corollary}[Geometric meaning of defect-free lifted affine dependence]
\label{cor:geometric-meaning-defect-free-lifted-affine-dependence-vpatch}
Assume the hypotheses of
Proposition~\ref{prop:defect-free-lifted-affine-dependence-vpatch}. Then:
\begin{enumerate}
\item if $k=2$, the two points $Q_v(h_1)$ and $Q_v(h_2)$ coincide;
\item if $k=3$, the three points $Q_v(h_1),Q_v(h_2),Q_v(h_3)$ are
collinear in $\mathbf C^3$;
\item if $k=4$, the four points $Q_v(h_1),\dots,Q_v(h_4)$ are coplanar in
$\mathbf C^3$.
\end{enumerate}
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:defect-free-lifted-affine-dependence-vpatch}, the
points $Q_v(h_j)$ are affinely dependent. For $k=2$, affine dependence of
two points is exactly coincidence. For $k=3$, affine dependence of three
points is exactly collinearity. For $k=4$, affine dependence of four points
is exactly coplanarity.
\end{proof}

\begin{corollary}[Explicit four-point determinant form on a $v_5$-patch]
\label{cor:explicit-four-point-determinant-form-vpatch}
Assume the hypotheses of
Proposition~\ref{prop:defect-free-lifted-affine-dependence-vpatch} with
$k=4$. Then the coplanarity of the four lifted points is equivalent to
\[
\det\!\begin{pmatrix}
1 & y(h_1) & x(h_1) & \sigma_v(h_1)\\
1 & y(h_2) & x(h_2) & \sigma_v(h_2)\\
1 & y(h_3) & x(h_3) & \sigma_v(h_3)\\
1 & y(h_4) & x(h_4) & \sigma_v(h_4)
\end{pmatrix}
=0.
\]
Equivalently,
\[
\det\!\begin{pmatrix}
1 & \dfrac{u_5(h_1)}{c(h_1)} & \dfrac{v_5(h_1)}{c(h_1)} &
\dfrac{\Delta_7(h_1)}{c(h_1)\,v_5(h_1)}\\[1.2ex]
1 & \dfrac{u_5(h_2)}{c(h_2)} & \dfrac{v_5(h_2)}{c(h_2)} &
\dfrac{\Delta_7(h_2)}{c(h_2)\,v_5(h_2)}\\[1.2ex]
1 & \dfrac{u_5(h_3)}{c(h_3)} & \dfrac{v_5(h_3)}{c(h_3)} &
\dfrac{\Delta_7(h_3)}{c(h_3)\,v_5(h_3)}\\[1.2ex]
1 & \dfrac{u_5(h_4)}{c(h_4)} & \dfrac{v_5(h_4)}{c(h_4)} &
\dfrac{\Delta_7(h_4)}{c(h_4)\,v_5(h_4)}
\end{pmatrix}
=0.
\]
Multiplying row $j$ by $v_5(h_j)$ gives the canonical determinant identity
\[
\det\!\begin{pmatrix}
v_5(h_1) & u_5(h_1) & \dfrac{v_5(h_1)^2}{c(h_1)} &
\dfrac{\Delta_7(h_1)}{c(h_1)}\\[1.2ex]
v_5(h_2) & u_5(h_2) & \dfrac{v_5(h_2)^2}{c(h_2)} &
\dfrac{\Delta_7(h_2)}{c(h_2)}\\[1.2ex]
v_5(h_3) & u_5(h_3) & \dfrac{v_5(h_3)^2}{c(h_3)} &
\dfrac{\Delta_7(h_3)}{c(h_3)}\\[1.2ex]
v_5(h_4) & u_5(h_4) & \dfrac{v_5(h_4)^2}{c(h_4)} &
\dfrac{\Delta_7(h_4)}{c(h_4)}
\end{pmatrix}
=0.
\]
Equivalently, multiplying instead row $j$ by $c(h_j)v_5(h_j)$ gives the
fully polynomial version
\[
\det\!\begin{pmatrix}
c(h_1)v_5(h_1) & u_5(h_1)v_5(h_1) & v_5(h_1)^2 & \Delta_7(h_1)\\
c(h_2)v_5(h_2) & u_5(h_2)v_5(h_2) & v_5(h_2)^2 & \Delta_7(h_2)\\
c(h_3)v_5(h_3) & u_5(h_3)v_5(h_3) & v_5(h_3)^2 & \Delta_7(h_3)\\
c(h_4)v_5(h_4) & u_5(h_4)v_5(h_4) & v_5(h_4)^2 & \Delta_7(h_4)
\end{pmatrix}
=0.
\]
\end{corollary}

\begin{proof}
For $k=4$, Corollary~\ref{cor:geometric-meaning-defect-free-lifted-affine-dependence-vpatch}
shows that the four lifted points
\[
Q_v(h_j)=\bigl(y(h_j),x(h_j),\sigma_v(h_j)\bigr)
\]
are coplanar. This is equivalent to the vanishing of the affine $4\times4$
determinant with first column $1$. The displayed reformulations follow by
substituting the definitions of $x,y,\sigma_v$ and multiplying rows by the
indicated nonzero factors.
\end{proof}

\begin{remark}[Finite-core meaning of the lifted $v_5$-patch geometry]
\label{rem:finite-core-meaning-lifted-vpatch-geometry}
The defect-free finite-core reduction now places the lifted $v_5$-patch
geometry into a sharp global context.

Indeed, by
Theorem~\ref{thm:defect-free-quintic-circuit-reduction},
Corollary~\ref{cor:defect-free-minimal-quintic-circuits}, and
Proposition~\ref{prop:defect-free-lifted-affine-dependence-vpatch},
defect-free bad cores on a good $v_5$-patch reduce to affine dependence of the
lifted points
\[
Q_v(h)=\bigl(y(h),x(h),\sigma_v(h)\bigr),
\]
with effective ceiling
\[
k\le 4.
\]
Thus the three low core sizes have the following exact lifted meanings:
\[
k=2 \Longleftrightarrow Q_v(h_1)=Q_v(h_2),
\]
\[
k=3 \Longleftrightarrow Q_v(h_1),Q_v(h_2),Q_v(h_3)
\ \text{are collinear},
\]
\[
k=4 \Longleftrightarrow Q_v(h_1),\dots,Q_v(h_4)
\ \text{are coplanar}.
\]

So the lifted $3$-point and $4$-point analyses are not auxiliary side
computations: they are exactly the $k=3$ and $k=4$ geometric layers in the
finite-core program. In particular, once the lifted $3$-point branch is
globally rigid on good $v_5$-patches, the remaining finite-core burden shifts
upward to the two-point source-level merger problem and to the mixed/nonmixed
lifted $4$-point mechanisms.
\end{remark}

\begin{remark}[Parallel $u_5$-patch version]
\label{rem:parallel-u5-patch-version}
There is a completely parallel local story on any connected interval in
$\{c\neq 0,\ u_5\neq 0\}$, obtained by choosing the local septic gauge
$u_7=0$ instead of $v_7=0$. Then one defines
\[
\tau_u(h):=-\frac{\Delta_7(h)}{c(h)\,u_5(h)},
\qquad
Q_u(h):=\left(\frac{u_5(h)}{c(h)},\frac{v_5(h)}{c(h)},\tau_u(h)\right),
\]
and the same defect-free affine-dependence conclusions hold with $Q_v$
replaced by $Q_u$. Since the present one-pair geometry already uses
\[
x(h)=\frac{v_5(h)}{c(h)}
\]
as the distinguished ECT coordinate, the $v_5\neq 0$ patch is the natural
first setting and will be used below.
\end{remark}

\begin{proposition}[Centered quintic-patch dichotomy]
\label{prop:centered-quintic-patch-dichotomy}
Assume the centered diagonal family is a genuine analytic branch in the
underlying $h$-geometry, and that the centered scalar package from
Remark~\ref{rem:centered-symmetric-placement-taylor-package} holds on that
branch. Then, after shrinking, there exist one-sided punctured subarcs on which
at least one of the following holds:
\begin{enumerate}
\item
\[
c\neq 0,\qquad M\neq 0,\qquad v_5\neq 0,
\]
so the branch enters a good $v_5$-patch;
\item
\[
c\neq 0,\qquad u_5\neq 0,
\]
so the parallel $u_5$-patch of
Remark~\ref{rem:parallel-u5-patch-version} applies.
\end{enumerate}
In particular, the centered diagonal branch enters some quintic patch on
one-sided punctured arcs.
\end{proposition}

\begin{proof}
By Corollary~\ref{cor:centered-quintic-fixed-sector-nontriviality},
\[
A_5^{\mathfrak f}(s)\not\equiv 0,
\]
so at least one of $u_5$ or $v_5$ is a nonzero analytic germ on the centered
branch.

If $v_5\not\equiv 0$, then its zeros are isolated. Since
\[
c(s)=C_0+C_2s^2+\cdots,\qquad C_0\neq 0,
\]
we also have $c\neq 0$ near the basepoint. On any one-sided punctured arc
where $v_5\neq 0$, define
\[
x=\frac{v_5}{c}.
\]
This is a nonconstant analytic germ. If $M\equiv 0$ on such an arc, then
\[
x'=\left(\frac{v_5}{c}\right)'=\frac{M}{c^2}\equiv 0,
\]
so $x$ would be constant, contradiction. Hence $M$ is not identically zero on
that arc, and by analyticity its zeros are isolated. After shrinking again, one
obtains
\[
c\neq 0,\qquad M\neq 0,\qquad v_5\neq 0,
\]
i.e. a good $v_5$-patch.

If instead $v_5\equiv 0$, then $u_5\not\equiv 0$. Its zeros are isolated, so
after shrinking to a one-sided punctured arc one has
\[
c\neq 0,\qquad u_5\neq 0,
\]
and the $u_5$-patch of Remark~\ref{rem:parallel-u5-patch-version} applies.
\end{proof}

\begin{corollary}[Conditional punctured $v_5$-patch promotion]
\label{cor:conditional-punctured-v5-patch-promotion}
Under the hypotheses of
Proposition~\ref{prop:centered-quintic-patch-dichotomy}, if
\[
v_5\not\equiv 0
\]
on the centered diagonal branch, then after shrinking there exist one-sided
punctured subarcs contained in
\[
\{c\neq 0,\ M\neq 0,\ v_5\neq 0\}.
\]
Hence on such arcs
\[
x=\frac{v_5}{c}
\]
is automatically a valid local coordinate.
\end{corollary}

\begin{proof}
This is exactly the first branch of the proof of
Proposition~\ref{prop:centered-quintic-patch-dichotomy}.
\end{proof}

\begin{proposition}[Linear independence of $1,u_5/c,v_5/c$]
\label{prop:linear-independence-one-u5-over-c-v5-over-c}
Let $J$ be a connected open interval on which
\[
c\neq 0,
\qquad
M\neq 0.
\]
Then the three functions
\[
1,
\qquad
\frac{u_5}{c},
\qquad
\frac{v_5}{c}
\]
are linearly independent on $J$.
\end{proposition}

\begin{proof}
Assume there exist constants $A,B,C\in\mathbf C$, not all zero, such that
\[
A+B\frac{u_5}{c}+C\frac{v_5}{c}\equiv 0
\qquad\text{on }J.
\]
Multiplying by $c$ gives
\[
A\,c+B\,u_5+C\,v_5\equiv 0.
\]

If $B=0$, then
\[
A\,c+C\,v_5\equiv 0,
\]
so $v_5/c$ is constant on $J$. But
\[
\left(\frac{v_5}{c}\right)'=\frac{M}{c^2},
\]
and $M\neq 0$ on $J$. This is impossible.

Hence $B\neq 0$, and after renormalization we may write
\[
u_5=\alpha\,v_5+\beta\,c
\]
for constants $\alpha,\beta$.

Now isolate the graded slice corresponding to
\[
(K_1,\eta_2,q^{(5)}).
\]
By Lemmas~\ref{lem:quintic-trace-witness}
and~\ref{lem:no-cancellation-quintic-trace}, the tagged monomial
\[
\kappa(h)\,\eta_2(h)\,q^{(5)}(h)
\]
occurs with nonzero coefficient in $\operatorname{tr}J_5^{\pair}(h)$.
Since
\[
A_5^{\mathfrak f}(h)=u_5(h)I+v_5(h)S
\]
and $S$ is traceless, this means exactly that the same tagged monomial
occurs in the $I$-coefficient $u_5(h)$.

It cannot occur in $c(h)$, since $c$ is cubic and carries no quintic
$q^{(5)}$-slice. It also cannot occur in $v_5(h)$. Indeed, on the tagged
slice, the only surviving quintic $K_1$-transport channels are those already
isolated in Lemma~\ref{lem:no-cancellation-quintic-trace}. For the channel
\[
X_0JX_4-X_4JX_0,
\]
Lemma~\ref{lem:whitening-parity} shows that the relevant
$(\eta_2,q^{(5)})$-slice is diagonal, hence contributes only to the
$I$-component. For the commutator channel
\[
X_3JX_1-X_1JX_3,
\]
Proposition~\ref{prop:explicit-quintic-fixed-sector} gives
\[
v_5^{(\mathrm{comm})}=\gamma u-\alpha w.
\]
On the tagged slice the $\eta_2$-input in $X_1$ is purely off-diagonal, so
$u=w=0$, while the $q^{(5)}$-input in $X_3$ is diagonal. Hence
\[
v_5^{(\mathrm{comm})}=0
\]
on that tagged slice.

Thus the monomial $\kappa\eta_2 q^{(5)}$ occurs in $u_5$ but in neither
$v_5$ nor $c$, contradicting
\[
u_5=\alpha\,v_5+\beta\,c.
\]
This proves the claim.
\end{proof}

\begin{corollary}[Automatic $u_5$-patch on a good $M\neq 0$ interval]
\label{cor:automatic-u5-patch-on-good-M-interval}
Let $J$ be a connected open interval on which
\[
c\neq 0,
\qquad
M\neq 0.
\]
Then $u_5\not\equiv 0$ on $J$. Consequently, every connected component of
\[
J\setminus u_5^{-1}(0)
\]
is a valid local $u_5$-patch in the sense of
Remark~\ref{rem:parallel-u5-patch-version}.
\end{corollary}

\begin{proof}
If $u_5\equiv 0$ on $J$, then the three functions
\[
1,\qquad \frac{u_5}{c},\qquad \frac{v_5}{c}
\]
would be linearly dependent, contradicting
Proposition~\ref{prop:linear-independence-one-u5-over-c-v5-over-c}. Thus
$u_5\not\equiv 0$ on $J$, so its zeros are isolated and each connected
component of $J\setminus u_5^{-1}(0)$ lies in $\{c\neq 0,\ u_5\neq 0\}$.
The parallel $u_5$-patch geometry then follows from
Remark~\ref{rem:parallel-u5-patch-version}.
\end{proof}

\begin{proposition}[Non-affinity of the lifted septic scalar]
\label{prop:sigmav-not-affine-in-x}
Let $J$ be a connected open interval contained in the quintic-generic region
and in
\[
\{h:c(h)\neq 0,\ v_5(h)\neq 0\}.
\]
Then there do not exist constants $A,B\in\mathbf C$ such that
\[
\sigma_v(h)\equiv A\,x(h)+B
\qquad\text{on }J.
\]
Equivalently,
\[
\Delta_7(h)\not\equiv A\,v_5(h)^2+B\,c(h)v_5(h)
\qquad\text{on }J.
\]
\end{proposition}

\begin{proof}
If
\[
\sigma_v(h)\equiv A\,x(h)+B,
\]
then multiplying by $c(h)v_5(h)$ gives
\[
\Delta_7(h)\equiv A\,v_5(h)^2+B\,c(h)v_5(h).
\]
The right-hand side is built only from the cubic and quintic layers and
therefore has no direct septic $q^{(7)}$-slice. But by
Proposition~\ref{prop:direct-q7-total-delta7-nonzero}, the direct
$q^{(7)}$-slice of $\Delta_7$ is generically nonzero on $J$. This is a
contradiction.
\end{proof}

\begin{definition}[Lifted derivative numerator and curvature numerator]
\label{def:lifted-vpatch-derivative-and-curvature}
On $\{c\neq 0,\ v_5\neq 0\}$, define
\[
P_v(h):=c(h)v_5(h)\Delta_7'(h)-\Delta_7(h)\bigl(c(h)v_5(h)\bigr)'.
\]
Then
\[
\sigma_v'(h)=\frac{P_v(h)}{c(h)^2\,v_5(h)^2}.
\]
Define also the affine curvature numerator of the lifted planar curve
\[
\Lambda_v(h)=\bigl(x(h),\sigma_v(h)\bigr)
\]
by
\[
K_v(h):=x'(h)\sigma_v''(h)-\sigma_v'(h)x''(h).
\]
\end{definition}

\begin{proposition}[Curvature bridge for the lifted $v_5$-patch curve]
\label{prop:curvature-bridge-lifted-vpatch}
On $\{c\neq 0,\ M\neq 0,\ v_5\neq 0\}$,
\[
\frac{d\sigma_v}{dx}
=
\frac{P_v}{M\,v_5^2},
\]
and
\[
K_v(h)
=
\frac{M(h)^2}{c(h)^4}
\frac{d}{dh}\!\left(\frac{P_v(h)}{M(h)\,v_5(h)^2}\right).
\]
In particular, if $K_v\equiv 0$ on a connected open interval $J\subset
\{c\neq 0,\ M\neq 0,\ v_5\neq 0\}$, then $\sigma_v$ is affine in $x$ on
$J$, contradicting Proposition~\ref{prop:sigmav-not-affine-in-x}. Hence
\[
K_v\not\equiv 0
\]
on every such interval.
\end{proposition}

\begin{proof}
Since
\[
x=\frac{v_5}{c},
\qquad
x'=\frac{M}{c^2},
\qquad
\sigma_v'=\frac{P_v}{c^2v_5^2},
\]
we obtain
\[
\frac{d\sigma_v}{dx}
=
\frac{\sigma_v'}{x'}
=
\frac{P_v}{M\,v_5^2}.
\]
Differentiating with respect to $h$ and multiplying by
\[
x'=\frac{M}{c^2}
\]
gives
\[
K_v
=
x'^2\,\frac{d}{dx}\!\left(\frac{d\sigma_v}{dx}\right)
=
\frac{M^2}{c^4}\,
\frac{d}{dh}\!\left(\frac{P_v}{M\,v_5^2}\right).
\]
If $K_v\equiv 0$ on a connected interval with $M\neq 0$, then
\[
\frac{P_v}{M\,v_5^2}
\]
is constant there, so $d\sigma_v/dx$ is constant and $\sigma_v$ is affine
in $x$. This contradicts
Proposition~\ref{prop:sigmav-not-affine-in-x}.
\end{proof}

\begin{corollary}[Local defect-free three-point exclusion on lifted ECT subintervals]
\label{cor:local-three-point-exclusion-lifted-vpatch}
Let $J\subset\{c\neq 0,\ M\neq 0,\ v_5\neq 0\}$ be a connected interval on
which $K_v$ has fixed nonzero sign. Then the triple
\[
1,\qquad x,\qquad \sigma_v
\]
is an ECT system on $J$. In particular, no affine line meets the lifted
planar curve
\[
\Lambda_v(h)=\bigl(x(h),\sigma_v(h)\bigr)
\]
in three points of $J$. Hence the defect-free three-point branch is excluded
on such a subinterval.
\end{corollary}

\begin{proof}
The Wronskian of $1,x,\sigma_v$ is exactly $K_v$. If $K_v$ has fixed
nonzero sign on $J$, the ECT criterion applies.
\end{proof}

\begin{corollary}[Lifted order-$7$ Wronskian is not identically zero]
\label{cor:lifted-vpatch-wronskian-not-identically-zero}
Let $J$ be a connected open interval contained in the quintic-generic region
and in
\[
\{h:c(h)\neq 0,\ M(h)\neq 0,\ v_5(h)\neq 0\}.
\]
Then
\[
T_v(h):=
W_h\!\left(
1,\ \frac{u_5(h)}{c(h)},\ \frac{v_5(h)}{c(h)},\
\frac{\Delta_7(h)}{c(h)\,v_5(h)}
\right)
\]
is not identically zero on $J$.
\end{corollary}

\begin{proof}
Write
\[
y:=\frac{u_5}{c},
\qquad
x:=\frac{v_5}{c},
\qquad
\sigma_v:=\frac{\Delta_7}{c\,v_5}.
\]
If $T_v\equiv 0$ on $J$, then by analyticity the four functions
\[
1,\ y,\ x,\ \sigma_v
\]
are locally linearly dependent on $J$, hence linearly dependent on all of
the connected interval $J$. By
Proposition~\ref{prop:linear-independence-one-u5-over-c-v5-over-c}, the first
three are linearly independent, so there exist constants $A,B,C$ such that
\[
\sigma_v=A+By+Cx.
\]
Multiplying by $c\,v_5$ gives
\[
\Delta_7=A\,c\,v_5+B\,u_5v_5+C\,v_5^2.
\]
The right-hand side is built entirely from the cubic/quintic layers and
therefore carries no direct $q^{(7)}$-slice. This contradicts
Proposition~\ref{prop:direct-q7-total-delta7-nonzero}, which gives
\[
\Delta_7^{(q^{(7)})}\not\equiv 0
\]
on $J$.
\end{proof}

\begin{proposition}[Exact $x$-coordinate identities for the lifted $4$-point invariants]
\label{prop:exact-x-coordinate-identities-lifted-four-point}
On a good $v_5$-patch, write
\[
x=\frac{v_5}{c},
\qquad
Y=\frac{u_5}{c},
\qquad
S=\sigma_v=\frac{\Delta_7}{c\,v_5}.
\]
Then:
\begin{enumerate}
\item the lifted planar curvature numerator satisfies
\[
K_v=(x')^3\,S''(x);
\]
\item the lifted $4$-point Wronskian satisfies
\[
T_v=(x')^6\,W_x(1,Y,x,S)
=(x')^6\bigl(S''Y'''-S'''Y''\bigr);
\]
\item equivalently,
\[
T_v=(x')^6\,S''^{\,2}\,\frac{d}{dx}\!\left(\frac{Y''}{S''}\right)
=K_v^{\,2}\,\frac{d}{dx}\!\left(\frac{Y''}{S''}\right).
\]
\end{enumerate}
In particular, $K_v$ and $S''$ have the same zero set and the same
vanishing order on every good $v_5$-patch.
\end{proposition}

\begin{proof}
By definition,
\[
K_v=x'\sigma_v''-\sigma_v' x''.
\]
Since $S=\sigma_v$ as a function of the local coordinate $x$, we have
\[
\sigma_v'=S' x',
\qquad
\sigma_v''=S''(x')^2+S' x'',
\]
hence
\[
K_v=x'\bigl(S''(x')^2+S'x''\bigr)-S' x' x''=(x')^3S''.
\]

Next,
\[
T_v=W_h(1,Y,x,S).
\]
Under reparametrization $h\mapsto x(h)$, a $4\times4$ Wronskian gains the
factor $(x')^{0+1+2+3}=(x')^6$, so
\[
T_v=(x')^6\,W_x(1,Y,x,S).
\]
Now
\[
W_x(1,Y,x,S)
=
\det\!\begin{pmatrix}
1&Y&x&S\\
0&Y'&1&S'\\
0&Y''&0&S''\\
0&Y'''&0&S'''
\end{pmatrix}
=
S''Y'''-S'''Y'',
\]
which proves the second identity.

Finally,
\[
S''Y'''-S'''Y''
=
S''^{\,2}\,\frac{d}{dx}\!\left(\frac{Y''}{S''}\right),
\]
and using $K_v=(x')^3S''$ gives
\[
(x')^6S''^{\,2}=K_v^{\,2}.
\]
This yields the third identity.
\end{proof}

\begin{proposition}[Canonical scalar invariants $\mathcal Z$ and $\mathcal R$ on a nonmixed lifted patch]
\label{prop:canonical-Z-R-invariants-lifted-four-point}
On a good $v_5$-patch, write
\[
x=\frac{v_5}{c},
\qquad
Y=\frac{u_5}{c},
\qquad
S=\sigma_v=\frac{\Delta_7}{c\,v_5}.
\]
On the nonmixed subregion where $K_v\neq 0$, define
\[
\mathcal Z:=\frac{Y''}{S''},
\qquad
\mathcal R:=\frac{d\mathcal Z}{dx}.
\]
Then:
\begin{enumerate}
\item
\[
\mathcal R=\frac{T_v}{K_v^2};
\]
\item under the affine gauge
\[
Y\longmapsto Y+\alpha+\beta x+\gamma S,
\]
one has
\[
\mathcal Z\longmapsto \mathcal Z+\gamma,
\qquad
\mathcal R\longmapsto \mathcal R.
\]
Hence $\mathcal R$ is the canonical scalar invariant of the lifted
$4$-point branch on every nonmixed patch.
\end{enumerate}
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:exact-x-coordinate-identities-lifted-four-point},
\[
T_v=(x')^6\,S''^{\,2}\,\frac{d}{dx}\!\left(\frac{Y''}{S''}\right)
=K_v^{\,2}\,\frac{d}{dx}\!\left(\frac{Y''}{S''}\right),
\]
so
\[
\mathcal R=\frac{d}{dx}\!\left(\frac{Y''}{S''}\right)=\frac{T_v}{K_v^2}.
\]

For the gauge transformation, one has
\[
(Y+\alpha+\beta x+\gamma S)''=Y''+\gamma S'',
\]
hence
\[
\mathcal Z\longmapsto \frac{Y''+\gamma S''}{S''}=\mathcal Z+\gamma.
\]
Differentiating with respect to $x$ gives $\mathcal R\mapsto \mathcal R$.
\end{proof}

\begin{remark}[Below-lifted Wronskian-ratio reformulation]
\label{rem:below-lifted-wronskian-ratio-reformulation}
Let
\[
x=\frac{v_5}{c},
\qquad
Y=\frac{u_5}{c},
\qquad
S=\frac{\Delta_7}{c\,v_5},
\qquad
\lambda:=\frac{\Delta_7}{v_5},
\qquad
M:=cv_5'-c'v_5.
\]
For any scalar germ $f$, define
\[
J_f(h):=
\det\!\begin{pmatrix}
c(h)&v_5(h)&f(h)\\
c'(h)&v_5'(h)&f'(h)\\
c''(h)&v_5''(h)&f''(h)
\end{pmatrix}.
\]
Then
\[
\frac{d^2}{dx^2}\!\left(\frac{f}{c}\right)
=
\frac{c^3}{M^3}\,J_f.
\]
Applying this to $f=u_5$ and $f=\lambda$ gives
\[
Y''=\frac{c^3}{M^3}J_{u_5},
\qquad
S''=\frac{c^3}{M^3}J_{\lambda},
\]
hence
\[
\boxed{
\mathcal Z:=\frac{Y''}{S''}=\frac{J_{u_5}}{J_{\lambda}}.
}
\]
Differentiating in the $x$-coordinate yields
\[
\boxed{
\mathcal R:=\mathcal Z'=\frac{T_v}{K_v^2}
=
\frac{c^2}{M}\frac{d}{dh}\!\left(\frac{J_{u_5}}{J_{\lambda}}\right).
}
\]
Thus the lifted $4$-point branch may be viewed equivalently as a
parity/divisibility problem for the Wronskian ratio $J_{u_5}/J_\lambda$.
On the nonmixed side, however, the later source-level no-go results show that
the ratio/Wronskian package by itself is not yet restrictive enough: the
remaining burden is a genuine source-coupling theorem, not a generic
Wronskian-ratio argument.
\end{remark}

\begin{proposition}[Source-level Wronskian for the nonmixed $4$-point branch]
\label{prop:source-level-Wronskian-nonmixed-four-point}
Define
\[
\mathcal W_{\mathrm{src}}
:=
J_{\lambda}\,J_{u_5}'-J_{u_5}\,J_{\lambda}'.
\]
Then
\[
\boxed{
\mathcal R
=
\frac{c^2}{M}\,\frac{\mathcal W_{\mathrm{src}}}{J_\lambda^2}.
}
\]
In particular, on every nonmixed arc on which $J_\lambda\neq 0$, the analytic
scalars $\mathcal R$ and $\mathcal W_{\mathrm{src}}$ differ only by a
nonvanishing analytic factor. Hence:

\begin{enumerate}
\item $\mathcal R=0\iff \mathcal W_{\mathrm{src}}=0$;
\item $\operatorname{ord}\mathcal R=\operatorname{ord}\mathcal W_{\mathrm{src}}$;
\item the local parity classification of isolated zeros of $\mathcal R$
transfers verbatim to $\mathcal W_{\mathrm{src}}$.
\end{enumerate}

Moreover, under the affine gauge change
\[
u_5\longmapsto u_5+\alpha c+\beta v_5+\gamma \lambda
\]
one has
\[
J_{u_5}\longmapsto J_{u_5}+\gamma J_\lambda,
\]
and therefore
\[
\mathcal W_{\mathrm{src}}\longmapsto \mathcal W_{\mathrm{src}}.
\]
So $\mathcal W_{\mathrm{src}}$ is the canonical source-level gauge-invariant
nonmixed scalar.
\end{proposition}

\begin{proof}
Differentiate the ratio
\[
\mathcal Z=\frac{J_{u_5}}{J_\lambda}
\]
from Remark~\ref{rem:below-lifted-wronskian-ratio-reformulation}:
\[
\frac{d}{dh}\!\left(\frac{J_{u_5}}{J_\lambda}\right)
=
\frac{J_\lambda J_{u_5}'-J_{u_5}J_\lambda'}{J_\lambda^2}
=
\frac{\mathcal W_{\mathrm{src}}}{J_\lambda^2}.
\]
Substituting this into
\[
\mathcal R
=
\frac{c^2}{M}\frac{d}{dh}\!\left(\frac{J_{u_5}}{J_\lambda}\right)
\]
gives the displayed identity.

On a nonmixed arc, $J_\lambda\neq 0$ and $c^2/M\neq 0$, so $\mathcal R$
and $\mathcal W_{\mathrm{src}}$ differ by a nonvanishing analytic factor.
This proves the zero-set and parity statements.

For gauge invariance, the terms $\alpha c$ and $\beta v_5$ do not change
$J_{u_5}$, while $\gamma\lambda$ adds $\gamma J_\lambda$. Therefore
\[
(J_{u_5}+\gamma J_\lambda)'=J_{u_5}'+\gamma J_\lambda',
\]
and
\[
J_\lambda(J_{u_5}'+\gamma J_\lambda')-(J_{u_5}+\gamma J_\lambda)J_\lambda'
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'.
\qedhere
\]
\end{proof}

\begin{remark}[Determinant-level parity on a centered good patch]
\label{rem:determinant-level-parity-centered-good-patch}
Assume the centered scalar package from
Remark~\ref{rem:centered-symmetric-placement-taylor-package} and suppose that
$x=v_5/c$ is being used as the induced odd collision-side coordinate.
Then
\[
u_5,\ \lambda:=\frac{\Delta_7}{v_5}\ \text{are odd in }s,
\qquad
c\ \text{is even in }s,
\qquad
v_5\ \text{is odd in }s.
\]
Hence the rows of the defining determinants for $J_{u_5}$ and $J_\lambda$
have parities
\[
(e,o,o),\qquad (o,e,e),\qquad (e,o,o),
\]
so each determinant monomial is odd. Therefore
\[
J_{u_5}(s)\ \text{and}\ J_\lambda(s)\ \text{are odd in }s.
\]
Consequently,
\[
\mathcal Z=\frac{J_{u_5}}{J_\lambda}
\]
is even and
\[
\mathcal R=\mathcal Z'
\]
is odd, in agreement with the parity package obtained from the direct
$Y''/S''$-analysis.
\end{remark}

\begin{corollary}[Centered parity of the source-level Wronskian]
\label{cor:centered-parity-source-level-Wronskian}
Under the hypotheses of
Remark~\ref{rem:determinant-level-parity-centered-good-patch}, the source-level
Wronskian
\[
\mathcal W_{\mathrm{src}}(s)
=
J_\lambda(s)\,J_{u_5}'(s)-J_{u_5}(s)\,J_\lambda'(s)
\]
is odd in the centered variable $s$.

Consequently, any isolated centered zero of $\mathcal W_{\mathrm{src}}$ has
odd order if and only if it is a potentially branch-seeding zero for the
nonmixed $4$-point geometry; even-order centered zeros are locally sterile.
\end{corollary}

\begin{proof}
By Remark~\ref{rem:determinant-level-parity-centered-good-patch},
\[
J_{u_5}(s)\ \text{and}\ J_\lambda(s)\ \text{are odd in }s.
\]
Hence
\[
J_{u_5}'(s)\ \text{and}\ J_\lambda'(s)\ \text{are even in }s.
\]
Therefore
\[
\mathcal W_{\mathrm{src}}(s)
=
J_\lambda(s)\,J_{u_5}'(s)-J_{u_5}(s)\,J_\lambda'(s)
\]
is odd in $s$. The final statement follows from
Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}, which
transfers the parity classification from $\mathcal R$ to
$\mathcal W_{\mathrm{src}}$.
\end{proof}

\begin{corollary}[Mixed low-order exclusion on a centered good $v_5$-patch]
\label{cor:mixed-low-order-exclusion-centered-good-v5-patch}
Under the hypotheses of
Remark~\ref{rem:determinant-level-parity-centered-good-patch}, one has
\[
\mathcal Z(x)\ \text{even},
\qquad
\mathcal R(x)\ \text{odd},
\qquad
K_v(x)\ \text{odd}.
\]
Consequently,
\[
(r,\operatorname{ord}_0\mathcal Z)\notin\{(1,1),(1,3),(2,2)\}.
\]
Equivalently, none of the explicit mixed low-order models
\[
(m,n)=(3,4),\ (3,6),\ (4,6)
\]
can occur on such a centered good patch.
\end{corollary}

\begin{proof}
Since $\mathcal Z$ is even, its finite vanishing order must be even, so the
cases
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3)
\]
are impossible. Since $K_v$ is odd, its vanishing order $r=\operatorname{ord}_0K_v$
must be odd, so
\[
(r,\operatorname{ord}_0\mathcal Z)=(2,2)
\]
is impossible as well.
\end{proof}

\begin{theorem}[Local exhaustion of the mixed $4$-point branch near the centered base]
\label{thm:local-exhaustion-mixed-four-point-centered-base}
Assume the centered scalar package from
Remark~\ref{rem:centered-symmetric-placement-taylor-package}, the right-pincer
local reduction from
Corollary~\ref{cor:right-pincer-local-reduction-centered-base}, and the finite-jet
scalar descent from
Corollary~\ref{cor:finite-jet-scalar-descent-centered-branch}. Then every
sufficiently small nearby genuinely new mixed $4$-point obstruction near the
centered diagonal base is excluded.

Equivalently, near the centered base the mixed $4$-point branch is locally
exhausted: the clean branch $V_1\neq 0$ is excluded by the centered
good-$v_5$-patch parity package, while every late-$v_5$ branch is either
locally sterile on the $u_5$-patch or already absorbed into the defect-free
planar quintic-circuit regime.
\end{theorem}

\begin{proof}
By Corollary~\ref{cor:right-pincer-local-reduction-centered-base}, every
sufficiently small nearby genuinely new mixed $4$-point obstruction must lie
on the clean branch
\[
V_1\neq 0,
\qquad\text{equivalently}\qquad
\operatorname{ord}_s v_5=1.
\]
On that branch, Corollary~\ref{cor:finite-jet-scalar-descent-centered-branch}
gives
\[
c(s)=C_0+C_2s^2+C_4s^4+\cdots.
\]
Since $v_5(s)$ is odd with $V_1\neq 0$, the induced patch coordinate
\[
x(s)=\frac{v_5(s)}{c(s)}
\]
is odd and has odd inverse. Since $u_5(s)$ is odd and $\Delta_7(s)$ is
even, it follows that
\[
Y(x)=\frac{u_5}{c}(x)
\qquad\text{and}\qquad
S(x)=\frac{\Delta_7}{cv_5}(x)
\]
are odd in $x$. Hence
\[
\mathcal Z(x)=\frac{Y''}{S''}\ \text{is even},
\qquad
K_v=(x')^3S''
\]
has odd vanishing order, so by
Corollary~\ref{cor:mixed-low-order-exclusion-centered-good-v5-patch}
none of the explicit mixed low-order obstruction patterns
\[
(r,\operatorname{ord}_0\mathcal Z)\in\{(1,1),(1,3),(2,2)\}
\]
can occur on the clean branch.

Thus no sufficiently small nearby genuinely new mixed $4$-point obstruction
remains. The late-$v_5$ branches were already removed by
Corollary~\ref{cor:right-pincer-local-reduction-centered-base}, and the clean
branch is excluded as above.
\end{proof}

\begin{remark}[What the mixed local exhaustion theorem now accomplishes]
\label{rem:what-mixed-local-exhaustion-now-accomplishes}
Theorem~\ref{thm:local-exhaustion-mixed-four-point-centered-base} closes the
mixed $4$-point route locally near the centered diagonal base in a
self-contained way: the clean branch is eliminated by the canonical scalar
descent together with the centered good-$v_5$-patch parity package, while
every late-$v_5$ branch is already removed by the $u_5$-patch right-pincer
package as either locally sterile or already-quintic.
\end{remark}

\begin{remark}[What remains after local mixed exhaustion]
\label{rem:what-remains-after-local-mixed-exhaustion}
Theorem~\ref{thm:local-exhaustion-mixed-four-point-centered-base} exhausts the
mixed $4$-point branch only in the centered-base local regime. Any remaining
mixed $4$-point escape must therefore be genuinely global/nonlocal: it cannot
come from a new local mixed septic jet pattern near the centered diagonal base.
\end{remark}

\begin{remark}[A second below-lifted ratio does not add a new obstruction]
\label{rem:second-below-lifted-ratio-no-new-obstruction}
Let
\[
\Theta:=\frac{W_{u_5}}{W},
\]
where $W$ denotes the corresponding projective-chart Wronskian in the
$(c,v_5,\cdot)$-frame. In the gauge $c\equiv 1$, $v_5=x$, one has the
exact relation
\[
\Theta=\mathcal Z\,\frac{S''}{xS''+2S'},
\qquad
(\mathcal Z-x\Theta)S''=2\Theta S'.
\]
So $\Theta$ does not provide an independent local obstruction beyond
$(\mathcal Z,\mathcal R)$: whenever $2\Theta/(\mathcal Z-x\Theta)$ is
analytic, one can solve locally for $S$ and then recover $Y$ from
$Y''=\mathcal Z S''$. In particular, attacks based only on a generic
differential relation between $\mathcal Z$ and $\Theta$ are too weak to
close the $4$-point branch.
\end{remark}

\begin{corollary}[Local defect-free four-point exclusion on lifted ECT subintervals]
\label{cor:local-four-point-exclusion-lifted-vpatch}
Let $J\subset\{c\neq 0,\ M\neq 0,\ v_5\neq 0\}$ be a connected interval on
which $T_v$ has fixed nonzero sign. Then the quadruple
\[
1,\qquad \frac{u_5}{c},\qquad \frac{v_5}{c},\qquad
\frac{\Delta_7}{c\,v_5}
\]
is an ECT system on $J$. Equivalently, no affine plane meets the lifted
space curve
\[
Q_v(h)=\left(\frac{u_5(h)}{c(h)},\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)\,v_5(h)}\right)
\]
in four points of $J$. Hence the defect-free four-point branch is excluded
on such a subinterval.
\end{corollary}

\begin{proof}
The Wronskian of the displayed quadruple is exactly $T_v$. If $T_v$ has
fixed nonzero sign on $J$, the ECT criterion applies.
\end{proof}

\begin{lemma}[Osculating determinant expansion for shrinking affine circuits]
\label{lem:osculating-determinant-expansion}
Let $Q:I\to \mathbf C^d$ be real-analytic on an interval $I$, and define
\[
\Delta_{d+1}(t_0,\dots,t_d)
:=
\det\!\begin{pmatrix}
1 & Q(t_0)\\
\vdots & \vdots\\
1 & Q(t_d)
\end{pmatrix}.
\]
Fix $h_*\in I$, and let
\[
t_j=h_*+\varepsilon \lambda_j
\qquad (j=0,\dots,d),
\]
where the $\lambda_j$ are pairwise distinct and $\varepsilon\to 0$. Then
\[
\Delta_{d+1}(t_0,\dots,t_d)
=
\frac{\varepsilon^{d(d+1)/2}}{\prod_{k=1}^d k!}\,
V(\lambda_0,\dots,\lambda_d)\,
\det\!\bigl(Q'(h_*),Q''(h_*),\dots,Q^{(d)}(h_*)\bigr)
+
O\!\left(\varepsilon^{d(d+1)/2+1}\right),
\]
where
\[
V(\lambda_0,\dots,\lambda_d):=\prod_{0\le i<j\le d}(\lambda_j-\lambda_i)
\]
is the Vandermonde determinant.

In particular, if there is a sequence of exact affine $(d+1)$-circuits
\[
\Delta_{d+1}(t_{0,n},\dots,t_{d,n})=0
\]
with pairwise distinct nodes $t_{j,n}\to h_*$, then
\[
\det\!\bigl(Q'(h_*),Q''(h_*),\dots,Q^{(d)}(h_*)\bigr)=0.
\]
\end{lemma}

\begin{proof}
Write the Taylor expansion
\[
Q(h_*+\varepsilon\lambda)
=
Q(h_*)+\sum_{m=1}^d \frac{\varepsilon^m\lambda^m}{m!}\,Q^{(m)}(h_*)
+O(\varepsilon^{d+1}),
\]
uniformly for $\lambda$ in bounded sets. Subtract the first row
$(1,Q(t_0))$ from each of the remaining rows. The first column then becomes
$(1,0,\dots,0)^{\top}$, so $\Delta_{d+1}$ reduces to the determinant of the
$d\times d$ matrix whose $j$-th row ($j=1,\dots,d$) is
\[
Q(t_j)-Q(t_0)
=
\sum_{m=1}^d \frac{\varepsilon^m(\lambda_j^m-\lambda_0^m)}{m!}\,Q^{(m)}(h_*)
+O(\varepsilon^{d+1}).
\]
Factor the column vectors $Q'(h_*),\dots,Q^{(d)}(h_*)$. This gives
\[
\Delta_{d+1}(t_0,\dots,t_d)
=
\det\!\bigl(Q'(h_*),\dots,Q^{(d)}(h_*)\bigr)\,
\det\!\Bigl(\frac{\varepsilon^m(\lambda_j^m-\lambda_0^m)}{m!}\Bigr)_{1\le j,m\le d}
+O\!\left(\varepsilon^{d(d+1)/2+1}\right).
\]
Pulling $\varepsilon^m/m!$ from the $m$-th column yields the factor
\[
\frac{\varepsilon^{1+\cdots+d}}{\prod_{k=1}^d k!}
=
\frac{\varepsilon^{d(d+1)/2}}{\prod_{k=1}^d k!}.
\]
The remaining determinant is the standard Vandermonde determinant
$V(\lambda_0,\dots,\lambda_d)$. This proves the expansion.

If $\Delta_{d+1}(t_{0,n},\dots,t_{d,n})=0$ for a sequence of shrinking
distinct-node circuits, divide by the nonzero Vandermonde factor and let
$\varepsilon\to 0$. The leading term must vanish, giving
\[
\det\!\bigl(Q'(h_*),Q''(h_*),\dots,Q^{(d)}(h_*)\bigr)=0.
\qedhere
\]
\end{proof}

\begin{remark}[Planar curvature and lifted torsion as the first derivative obstructions]
\label{rem:derivative-geometry-curvature-torsion-bridge}
Lemma~\ref{lem:osculating-determinant-expansion} shows that shrinking exact
affine circuits are controlled, at first nontrivial order, by derivative-side
osculating determinants. For a planar curve $q$, shrinking exact collinear
triples force
\[
\det(q',q'')=0,
\]
and for a space curve $Q$, shrinking exact coplanar quadruples force
\[
\det(Q',Q'',Q''')=0.
\]
Thus the defect-free lifted $3$-point and $4$-point branches are not merely
incidence problems: they are rooted at curvature- and torsion-type derivative
invariants of the corresponding lifted curves.
\end{remark}

\begin{proposition}[Shrinking exact lifted $3$-point circuits concentrate into $K_v=0$]
\label{prop:shrinking-exact-lifted-three-point-circuits-force-Kv-zero}
Let $P\Subset\{c\neq 0,\ v_5\neq 0,\ M\neq 0\}$ be compact, and use
\[
x=\frac{v_5}{c},
\qquad
S=\sigma_v=\frac{\Delta_7}{c\,v_5}.
\]
Suppose there is a sequence of distinct triples
\[
x_{1,n},x_{2,n},x_{3,n}\in x(P),
\qquad
x_{1,n},x_{2,n},x_{3,n}\to x_*,
\]
such that
\[
\det\!\begin{pmatrix}
1&x_{1,n}&S(x_{1,n})\\
1&x_{2,n}&S(x_{2,n})\\
1&x_{3,n}&S(x_{3,n})
\end{pmatrix}
=0
\qquad
\text{for every }n.
\]
Then
\[
K_v(x_*)=0.
\]
\end{proposition}

\begin{proof}
Apply Lemma~\ref{lem:osculating-determinant-expansion} with $d=2$ to the
planar lifted curve
\[
q(x):=(x,S(x)).
\]
The exact collinearity condition in the statement is precisely the vanishing of
\[
\det\!\begin{pmatrix}
1&x_1&S(x_1)\\
1&x_2&S(x_2)\\
1&x_3&S(x_3)
\end{pmatrix}.
\]
Hence shrinking exact lifted $3$-point circuits force
\[
\det(q'(x_*),q''(x_*))=0.
\]
Since
\[
q'(x)=(1,S'(x)),
\qquad
q''(x)=(0,S''(x)),
\]
one gets
\[
\det(q'(x_*),q''(x_*))=S''(x_*).
\]
On the $x$-patch, Proposition~\ref{prop:exact-x-coordinate-identities-lifted-four-point}
gives
\[
K_v=(x')^3S'',
\]
and $x'\neq 0$ on a good $v_5$-patch. Therefore $S''(x_*)=0$ implies
\[
K_v(x_*)=0.
\qedhere
\]
\end{proof}

\begin{corollary}[Uniform small-diameter exclusion away from $K_v=0$]
\label{cor:uniform-small-diameter-exclusion-away-from-Kv-zero}
Let $P_0\Subset\{c\neq 0,\ v_5\neq 0,\ M\neq 0\}$ be compact and assume
\[
P_0\cap\{K_v=0\}=\varnothing.
\]
Then there exists $\rho_3>0$ such that no exact lifted $3$-point circuit
contained in $P_0$ has $x$-diameter $<\rho_3$.
\end{corollary}

\begin{proof}
Otherwise there would exist a sequence of exact lifted $3$-point circuits in
$P_0$ with diameters tending to $0$. By compactness, after passing to a
subsequence the three nodes would converge to some $x_*\in x(P_0)$. This
contradicts
Proposition~\ref{prop:shrinking-exact-lifted-three-point-circuits-force-Kv-zero}.
\end{proof}

\begin{proposition}[Shrinking exact lifted $4$-point circuits concentrate into $T_v=0$]
\label{prop:shrinking-exact-lifted-four-point-circuits-force-Tv-zero}
Let $P\Subset\{c\neq 0,\ v_5\neq 0,\ M\neq 0\}$ be compact, and use
\[
x=\frac{v_5}{c},
\qquad
Y=\frac{u_5}{c},
\qquad
S=\sigma_v=\frac{\Delta_7}{c\,v_5}.
\]
Suppose there is a sequence of distinct quadruples
\[
x_{1,n},x_{2,n},x_{3,n},x_{4,n}\in x(P),
\qquad
x_{1,n},x_{2,n},x_{3,n},x_{4,n}\to x_*,
\]
such that
\[
\det\!\begin{pmatrix}
1&Y(x_{1,n})&x_{1,n}&S(x_{1,n})\\
1&Y(x_{2,n})&x_{2,n}&S(x_{2,n})\\
1&Y(x_{3,n})&x_{3,n}&S(x_{3,n})\\
1&Y(x_{4,n})&x_{4,n}&S(x_{4,n})
\end{pmatrix}
=0
\qquad
\text{for every }n.
\]
Then
\[
T_v(x_*)=0.
\]
\end{proposition}

\begin{proof}
Apply Lemma~\ref{lem:osculating-determinant-expansion} with $d=3$ to the
lifted space curve
\[
Q(x):=(Y(x),x,S(x)).
\]
The exact coplanarity condition in the statement is precisely the vanishing of
\[
\det\!\begin{pmatrix}
1&Y(x_1)&x_1&S(x_1)\\
1&Y(x_2)&x_2&S(x_2)\\
1&Y(x_3)&x_3&S(x_3)\\
1&Y(x_4)&x_4&S(x_4)
\end{pmatrix}.
\]
Hence shrinking exact lifted $4$-point circuits force
\[
\det(Q'(x_*),Q''(x_*),Q'''(x_*))=0.
\]
But
\[
\det(Q'(x),Q''(x),Q'''(x))
=
W_x(1,Y,x,S)(x),
\]
and Proposition~\ref{prop:exact-x-coordinate-identities-lifted-four-point}
gives
\[
T_v=(x')^6\,W_x(1,Y,x,S).
\]
Since $x'\neq 0$ on a good $v_5$-patch, it follows that
\[
T_v(x_*)=0.
\qedhere
\]
\end{proof}

\begin{corollary}[Uniform small-diameter exclusion away from $T_v=0$]
\label{cor:uniform-small-diameter-exclusion-away-from-Tv-zero}
Let $P_0\Subset\{c\neq 0,\ v_5\neq 0,\ M\neq 0\}$ be compact and assume
\[
P_0\cap\{T_v=0\}=\varnothing.
\]
Then there exists $\rho_4>0$ such that no exact lifted $4$-point circuit
contained in $P_0$ has $x$-diameter $<\rho_4$.
\end{corollary}

\begin{proof}
Otherwise there would exist a sequence of exact lifted $4$-point circuits in
$P_0$ with diameters tending to $0$. By compactness, after passing to a
subsequence the four nodes would converge to some $x_*\in x(P_0)$. This
contradicts
Proposition~\ref{prop:shrinking-exact-lifted-four-point-circuits-force-Tv-zero}.
\end{proof}

\begin{definition}[Repeated-node tangent-contact determinants on a $v_5$-patch]
\label{def:repeated-node-tangent-contact-determinants-vpatch}
On a $v_5\neq 0$ patch with $x=v_5/c$, $Y=u_5/c$, and
$S=\Delta_7/(c\,v_5)$, define
\[
H_3(a,u):=
\det\!\begin{pmatrix}
1&a&S(a)\\
0&1&S'(a)\\
1&u&S(u)
\end{pmatrix}
=
S(u)-S(a)-S'(a)(u-a),
\]
and
\[
H_4(a,u,v):=
\det\!\begin{pmatrix}
1&Y(a)&a&S(a)\\
0&Y'(a)&1&S'(a)\\
1&Y(u)&u&S(u)\\
1&Y(v)&v&S(v)
\end{pmatrix}.
\]
Thus $H_3(a,u)=0$ means that $(u,S(u))$ lies on the tangent line to
$\Lambda_v$ at $a$, while $H_4(a,u,v)=0$ means that $Q_v(u)$ and
$Q_v(v)$ lie in the tangent plane to $Q_v$ at $a$.
\end{definition}

\begin{proposition}[Repeated-node limits of exact lifted determinants]
\label{prop:repeated-node-limits-of-exact-lifted-determinants}
For the exact lifted determinants
\[
\Delta_3(a,b,u):=
\det\!\begin{pmatrix}
1&a&S(a)\\
1&b&S(b)\\
1&u&S(u)
\end{pmatrix},
\]
and
\[
\Delta_4(a,b,u,v):=
\det\!\begin{pmatrix}
1&Y(a)&a&S(a)\\
1&Y(b)&b&S(b)\\
1&Y(u)&u&S(u)\\
1&Y(v)&v&S(v)
\end{pmatrix},
\]
one has
\[
\frac{\Delta_3(a,b,u)}{b-a}\longrightarrow H_3(a,u)
\qquad (b\to a),
\]
and
\[
\frac{\Delta_4(a,b,u,v)}{b-a}\longrightarrow H_4(a,u,v)
\qquad (b\to a).
\]
\end{proposition}

\begin{proof}
Subtract the first row from the second row in each determinant and divide by
$b-a$. The resulting second row is the first difference quotient of the
corresponding row entries, and the limit $b\to a$ gives the derivative row.
\end{proof}

\begin{theorem}[Local classification of the lifted $3$-point branch near a finite-order $K_v$-zero]
\label{thm:local-classification-lifted-three-point-branch-near-Kv-zero}
Let $x=0$ be an isolated finite-order zero of $K_v$ on a good $v_5$-patch.
After affine normalization of $\Lambda_v=(x,S)$, write
\[
S(x)=x^m+O(x^{m+1}),
\qquad
m=r+2\ge 3,
\]
where $r=\operatorname{ord}_0 K_v$. Then the repeated-node tangent-contact equation
\[
H_3(a,u)=0
\]
with $a<0<u$ has the following local classification:
\begin{enumerate}
\item if $r$ is even (equivalently $m$ is even), there is no
opposite-side tangent-contact branch near $(a,u)=(0,0)$;
\item if $r$ is odd (equivalently $m$ is odd), there exists a unique
real-analytic opposite-side branch
\[
u=\Upsilon(a),
\qquad
a<0,\quad |a|\ll 1,
\]
with asymptotic expansion
\[
\Upsilon(a)=\lambda_m(-a)+O(a^2),
\]
where $\lambda_m>1$ is the unique positive root of
\[
P_m(\lambda):=\lambda^m-m\lambda-(m-1).
\]
\end{enumerate}
\end{theorem}

\begin{proof}
Set $a=-\alpha$ with $\alpha>0$, and write $u=\lambda\alpha$ with
$\lambda>0$. For the model germ $S(x)=x^m$, the tangent-contact equation is
\[
H_3(-\alpha,\lambda\alpha)
=
\alpha^m
\begin{cases}
\lambda^m+m\lambda+(m-1),& m\ \text{even},\\[0.5ex]
\lambda^m-m\lambda-(m-1),& m\ \text{odd}.
\end{cases}
\]
If $m$ is even, the displayed factor is strictly positive for every
$\lambda>0$, so no opposite-side branch exists.

If $m$ is odd, define
\[
P_m(\lambda):=\lambda^m-m\lambda-(m-1).
\]
Then
\[
P_m(1)=-2(m-1)<0,
\qquad
P_m(\lambda)\to+\infty\ \text{as }\lambda\to+\infty,
\]
and
\[
P_m'(\lambda)=m(\lambda^{m-1}-1)
\]
is negative on $(0,1)$ and positive on $(1,\infty)$. Therefore $P_m$
has a unique positive root $\lambda_m>1$.

For the perturbed germ $S(x)=x^m+O(x^{m+1})$, divide $H_3(-\alpha,\lambda\alpha)$
by $\alpha^m$. The resulting equation is
\[
P_m(\lambda)+O(\alpha)=0.
\]
If $m$ is even, positivity of the model factor persists for $\alpha$ small,
so there is still no branch. If $m$ is odd, the root $\lambda_m$ is simple,
so the implicit function theorem yields a unique analytic branch
\[
\lambda=\lambda(\alpha)=\lambda_m+O(\alpha),
\]
equivalently
\[
u=\lambda_m(-a)+O(a^2).
\]
This proves the classification.
\end{proof}

\begin{corollary}[No infinite-order flatness for $K_v$ on a good $v_5$-patch]
\label{cor:no-infinite-order-flatness-Kv-good-vpatch}
On a good $v_5$-patch, every zero of $K_v$ has finite order.
Equivalently, the lifted curvature $S''(x)$ has no infinite-order zero on such a
patch.
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:exact-x-coordinate-identities-lifted-four-point},
\[
K_v=(x')^3S''(x),
\]
and on a good $v_5$-patch one has $x'\neq 0$. Thus $K_v$ and $S''$ have the
same zero set and the same vanishing order.

If $K_v$ had an infinite-order zero at some interior point $x_*$, then so would
$S''$. Since $S''$ is analytic in the local coordinate $x$, this would force
\[
S''\equiv 0
\]
on a neighborhood of $x_*$. Hence $S$ would be affine in $x$ there, contrary to
Proposition~\ref{prop:sigmav-not-affine-in-x}.
\end{proof}

\begin{lemma}[Slope--intercept parametrization for the lifted $3$-point branch]
\label{lem:slope-intercept-parametrization-lifted-three-point}
Assume the affine normalization from
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero},
so that
\[
S(0)=S'(0)=0,
\qquad
S''<0\ \text{on the source side }I_-=(\alpha,0).
\]
Let
\[
I_+=(0,\beta)
\]
be the maximal open interval to the right of $0$ on which $S'$ is strictly
increasing. Equivalently, $S''$ does not change sign on $I_+$, and any zeros of
$S''$ there are isolated even-order zeros.

For
\[
m\in J_-:=S'(I_-),
\]
define the inverse source point
\[
a=a(m):=(S'|_{I_-})^{-1}(m),
\]
and the source tangent intercept
\[
\tau_-(m):=S(a(m))-m\,a(m).
\]
For
\[
m\in J_+:=S'(I_+),
\]
define the inverse target tangent point
\[
u_+(m):=(S'|_{I_+})^{-1}(m),
\]
and the target tangent intercept
\[
\tau_+(m):=S(u_+(m))-m\,u_+(m).
\]
Then
\[
\tau_-'(m)=-a(m),
\qquad
\tau_+'(m)=-u_+(m).
\]
Hence on
\[
J:=J_-\cap J_+
\]
the intercept gap
\[
D(m):=\tau_-(m)-\tau_+(m)
\]
satisfies
\[
D'(m)=u_+(m)-a(m)>0.
\]
\end{lemma}

\begin{proof}
Differentiate
\[
\tau_-(m)=S(a(m))-m\,a(m)
\]
to obtain
\[
\tau_-'(m)=S'(a(m))a'(m)-a(m)-m\,a'(m)=-a(m),
\]
because $S'(a(m))=m$. The same computation gives
\[
\tau_+'(m)=-u_+(m).
\]
Subtracting yields
\[
D'(m)=u_+(m)-a(m).
\]
Since $a(m)<0<u_+(m)$, the derivative is strictly positive.
\end{proof}

\begin{theorem}[Global continuation / nonrecurrence of the odd-order lifted $3$-point branch]
\label{thm:global-continuation-nonrecurrence-odd-three-point-branch}
Assume the hypotheses and affine normalization of
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero},
and suppose that $r=\operatorname{ord}_0K_v$ is odd, so the unique local
opposite-side branch exists.

Let
\[
I_-=(\alpha,0)
\]
be the source interval on which $S''<0$, and let
\[
I_+=(0,\beta)
\]
be the maximal open interval to the right of $0$ on which $S'$ is strictly
increasing. Set
\[
J:=S'(I_-)\cap S'(I_+).
\]
Then there exists a unique maximal open interval
\[
J_{\mathrm{br}}=(0,m_*)\subset J
\]
and a unique real-analytic function
\[
u:J_{\mathrm{br}}\to I_+
\]
such that
\[
H_3(a(m),u(m))=0,
\qquad
a(m):=(S'|_{I_-})^{-1}(m),
\qquad
u(m)>0,
\]
and for small $m>0$ this branch agrees with the local branch from
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero}.

Moreover:
\begin{enumerate}
\item the intercept gap
\[
D(m):=\tau_-(m)-\tau_+(m)
\]
is strictly positive on all of $J$, and
\[
D'(m)=u_+(m)-a(m)>0;
\]

\item along the branch one has
\[
\partial_u H_3(a(m),u(m))
=
S'(u(m))-m
\neq 0,
\]
so there is no interior common-tangent event;

\item the branch is uniquely continued on $J_{\mathrm{br}}$, with
\[
u'(m)=\frac{u(m)-a(m)}{S'(u(m))-m},
\]
and the source coordinate is strictly monotone,
\[
a'(m)=\frac{1}{S''(a(m))}<0;
\]

\item if $m_*<\sup J$, then
\[
u(m)\longrightarrow \beta
\qquad (m\uparrow m_*).
\]
Hence the branch cannot end in the interior of $I_+$; it can stop only when it
reaches the boundary of the source/target slope-overlap block.

In particular, the odd-order lifted $3$-point branch has no interior
recurrence, no self-return, no interior accumulation, and no infinite-order
flatness. Its only remaining endpoint mechanism is boundary exit of the
relevant good-patch / monotone-slope block.
\end{enumerate}
\end{theorem}

\begin{proof}
For
\[
m\in J,
\]
set
\[
\Phi(m,u):=S(u)-m\,u-\tau_-(m).
\]
Then
\[
\Phi(m,u)=H_3(a(m),u).
\]

\smallskip

\noindent
\textbf{Step 1: positivity of the intercept gap.}
By the odd-order local classification theorem, for all sufficiently small
$m>0$ there exists a point $u(m)\in I_+$ such that
\[
\Phi(m,u(m))=0.
\]
Fix such a small $m$. Since $S'$ is strictly increasing on $I_+$, the function
\[
u\longmapsto \Phi(m,u)
\]
has strictly increasing derivative
\[
\partial_u\Phi(m,u)=S'(u)-m,
\]
hence a unique critical point, namely $u_+(m)$, and that critical point is its
unique minimum on $I_+$. Therefore
\[
\Phi(m,u_+(m))<0.
\]
But
\[
\Phi(m,u_+(m))
=
S(u_+(m))-m\,u_+(m)-\tau_-(m)
=
\tau_+(m)-\tau_-(m)
=
-D(m),
\]
so $D(m)>0$ for all sufficiently small $m>0$.

By Lemma~\ref{lem:slope-intercept-parametrization-lifted-three-point},
\[
D'(m)=u_+(m)-a(m)>0
\]
on all of $J$. Hence $D(m)>0$ for every $m\in J$.

\smallskip

\noindent
\textbf{Step 2: no interior common tangency.}
Suppose
\[
\Phi(m,u)=0
\]
for some $m\in J$ and $u\in I_+$. If also
\[
\partial_u\Phi(m,u)=S'(u)-m=0,
\]
then by uniqueness of the inverse point on $I_+$ one has $u=u_+(m)$, and thus
\[
0=\Phi(m,u_+(m))=-D(m),
\]
contrary to $D(m)>0$. Therefore every branch point satisfies
\[
\partial_u\Phi(m,u)\neq 0.
\]
Equivalently, there is no interior common-tangent point on the odd-order
branch.

\smallskip

\noindent
\textbf{Step 3: uniqueness and analytic continuation.}
For fixed $m\in J$, the derivative
\[
u\longmapsto \partial_u\Phi(m,u)=S'(u)-m
\]
is strictly increasing on $I_+$, and
\[
\partial_u\Phi(m,0)=S'(0)-m=-m<0.
\]
Hence $\Phi(m,\cdot)$ first decreases and then increases, so it has at most one
zero on $I_+$. Thus the local branch from
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero}
is unique on every connected continuation interval.

Let
\[
E:=\{m\in J:\exists\,u\in I_+\ \text{with}\ \Phi(m,u)=0\}.
\]
By Step 2, every zero is simple in the $u$-variable, so the implicit function
theorem shows that $E$ is open and that the zero depends real-analytically on
$m$. Let
\[
J_{\mathrm{br}}=(0,m_*)
\]
be the connected component of $E$ containing all sufficiently small positive
$m$. This gives the unique maximal analytic continuation
\[
u=u(m),
\qquad
m\in J_{\mathrm{br}}.
\]

Differentiating
\[
\Phi(m,u(m))=0
\]
gives
\[
\bigl(S'(u(m))-m\bigr)u'(m)-u(m)+a(m)=0,
\]
hence
\[
u'(m)=\frac{u(m)-a(m)}{S'(u(m))-m}.
\]
Also
\[
a'(m)=\frac{1}{S''(a(m))}<0
\]
because $S''<0$ on the source interval $I_-$. So the source coordinate is
strictly monotone and cannot return to a previous value.

\smallskip

\noindent
\textbf{Step 4: endpoint control.}
Assume that
\[
m_*<\sup J
\]
but that $u(m)$ does not approach $\beta$ as $m\uparrow m_*$. Then there exists
a compact subinterval
\[
K\Subset I_+
\]
and a sequence $m_n\uparrow m_*$ with
\[
u(m_n)\in K.
\]
After passing to a subsequence,
\[
u(m_n)\to u_*\in K.
\]
By continuity,
\[
\Phi(m_*,u_*)=0.
\]
Since $m_*<\sup J$, one has $m_*\in J$, so by Step 2,
\[
\partial_u\Phi(m_*,u_*)\neq 0.
\]
The implicit function theorem therefore extends the branch analytically past
$m_*$, contradicting maximality of $J_{\mathrm{br}}$.

Hence
\[
u(m)\to\beta
\qquad (m\uparrow m_*).
\]
This proves that the branch cannot terminate by an interior fold, interior
common tangency, or interior accumulation.

Finally, by
Corollary~\ref{cor:no-infinite-order-flatness-Kv-good-vpatch}, every zero of
$K_v$ has finite order. Since even-order zeros do not change the sign of $S''$,
they do not break the strict increase of $S'$ on $I_+$. Therefore the endpoint
$\beta$ can only be the ambient boundary of the good patch or the first
odd-order zero of $K_v$ to the right.
\end{proof}

\begin{remark}[Structural package for the global lifted $3$-point branch]
\label{rem:structural-package-global-lifted-three-point-branch}
The correct global parameter on the odd-order lifted $3$-point branch is the
source tangent slope
\[
m=S'(a).
\]
In that parameter, the branch is governed by the source/target tangent
intercepts
\[
\tau_-(m)=S(a(m))-m\,a(m),
\qquad
\tau_+(m)=S(u_+(m))-m\,u_+(m),
\]
and their gap
\[
D(m)=\tau_-(m)-\tau_+(m),
\qquad
D'(m)=u_+(m)-a(m)>0.
\]
Thus interior common tangency is exactly the equation
\[
D(m)=0,
\]
but this never occurs on the odd-order continuation branch because $D>0$ there.
So the global $3$-point problem is not a hidden recurrence problem inside the
patch: once born at an odd-order $K_v$-zero, the branch is a one-parameter
analytic graph with monotone source coordinate, and even-order $K_v$-zeros are
invisible to it except as isolated points where $S''$ vanishes without changing
the monotone-slope block.
\end{remark}

\begin{remark}[Target-block form of the intercept-gap monotonicity]
\label{rem:target-block-intercept-gap-monotonicity}
The slope--intercept monotonicity from
Lemma~\ref{lem:slope-intercept-parametrization-lifted-three-point}
is not special to the first right-hand target block.

Let $I$ be any open interval to the right of the source interval $I_-$
on which $S'$ is monotone and hence invertible. For
\[
m\in S'(I_-)\cap S'(I),
\]
define
\[
u_I(m):=(S'|_I)^{-1}(m),
\qquad
\tau_I(m):=S(u_I(m))-m\,u_I(m),
\]
and
\[
D_I(m):=\tau_-(m)-\tau_I(m).
\]
Then exactly the same envelope calculation gives
\[
\tau_I'(m)=-u_I(m),
\qquad
D_I'(m)=u_I(m)-a(m)>0.
\]

Thus for any monotone-slope target block, interior common tangency against the
fixed source interval $I_-$ is again the scalar equation
\[
D_I(m)=0.
\]
So any future continuation across successive odd-order $K_v$-zeros must be
organized blockwise through these monotone intercept-gap functions rather than
through a hidden recurrence mechanism inside a block.
\end{remark}

\begin{remark}[Derivative-geometric meaning of the lifted $3$-point branch]
\label{rem:derivative-geometry-meaning-global-three-point-branch}
The lifted $3$-point branch is now best viewed as a derivative-geometric
propagation theorem for the planar lifted curve
\[
\Lambda_v=(x,S).
\]

By Lemma~\ref{lem:osculating-determinant-expansion} and
Proposition~\ref{prop:shrinking-exact-lifted-three-point-circuits-force-Kv-zero},
shrinking exact lifted $3$-point circuits are detected by the osculating
determinant and therefore concentrate into the lifted curvature-zero set
\[
K_v=(x')^3S''(x)=0.
\]
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero}
then identifies the local repeated-node branch structure at those curvature
zeros, and
Theorem~\ref{thm:global-continuation-nonrecurrence-odd-three-point-branch}
shows that the odd-order branch propagates globally on each monotone-slope
target block by the slope--intercept envelope identities
\[
\tau_-'(m)=-a(m),
\qquad
\tau_+'(m)=-u_+(m),
\qquad
D'(m)=u_+(m)-a(m)>0.
\]

So the lifted $3$-point theory is no longer an ad hoc repeated-node analysis.
It is the global propagation of an osculating-contact defect for the curve
$\Lambda_v$, organized by the derivative geometry of its tangent lines and
curvature.
\end{remark}

\begin{remark}[Exact nonmixed reduction in terms of $\mathcal Z$ and $\mathcal R$]
\label{rem:nonmixed-four-point-zeros-can-carry-preexisting-branches}
At a nonmixed lifted point
\[
K_v(0)\neq 0,
\qquad
T_v(0)=0,
\]
Propositions~\ref{prop:exact-x-coordinate-identities-lifted-four-point}
and~\ref{prop:canonical-Z-R-invariants-lifted-four-point} give
\[
\mathcal Z=\frac{Y''}{S''},
\qquad
\mathcal R=\mathcal Z'=\frac{T_v}{K_v^2}.
\]
Since $K_v(0)\neq 0$, one has $S''(0)\neq 0$, so after analytic
reparametrization and affine target normalization preserving coplanarity one may
write the lifted germ as
\[
Q_v(\xi)=\bigl(\widetilde Y(\xi),\,\xi,\,\xi^2\bigr),
\qquad
\widetilde Y(0)=\widetilde Y'(0)=\widetilde Y''(0)=0.
\]
In these normalized coordinates,
\[
\mathcal Z(\xi)=\frac12\,\widetilde Y''(\xi),
\qquad
\mathcal R(\xi)=\frac12\,\widetilde Y'''(\xi).
\]

Thus the nonmixed lifted $4$-point problem is exactly the jet problem of
excluding odd-order zeros of $\mathcal R$. Equivalently, it is the problem of
excluding even leading degrees of $\widetilde Y$ in the normalized chart.

In particular, the low-order dangerous nonmixed cases are exactly:
\[
\operatorname{ord}_0\mathcal R=1
\iff
\widetilde Y'''(0)=0,\ \widetilde Y^{(4)}(0)\neq 0,
\]
\[
\operatorname{ord}_0\mathcal R=3
\iff
\widetilde Y^{(3)}(0)=\widetilde Y^{(4)}(0)=\widetilde Y^{(5)}(0)=0,\
\widetilde Y^{(6)}(0)\neq 0,
\]
\[
\operatorname{ord}_0\mathcal R=5
\iff
\widetilde Y^{(3)}(0)=\cdots=\widetilde Y^{(7)}(0)=0,\
\widetilde Y^{(8)}(0)\neq 0.
\]

Equivalently, the dangerous nonmixed low-order list is
\[
\operatorname{ord}_0\mathcal Z\in\{2,4,6\}
\qquad\Longleftrightarrow\qquad
\operatorname{ord}_0\mathcal R\in\{1,3,5\}.
\]

So the nonmixed $4$-point endgame has been reduced to a finite jet problem
for the canonical invariant $\mathcal R$.
\end{remark}

\begin{lemma}[Repeated-node tangent-plane determinant in the normalized nonmixed chart]
\label{lem:normalized-nonmixed-H4-divided-difference}
In the normalized nonmixed chart of
Remark~\ref{rem:nonmixed-four-point-zeros-can-carry-preexisting-branches},
define
\[
\widetilde H_4(a,u,v):=
\det\!\begin{pmatrix}
1&\widetilde Y(a)&a&a^2\\
0&\widetilde Y'(a)&1&2a\\
1&\widetilde Y(u)&u&u^2\\
1&\widetilde Y(v)&v&v^2
\end{pmatrix}.
\]
Then
\[
\widetilde H_4(a,u,v)
=
(u-a)^2(v-a)^2\Bigl(\widetilde Y[a,a,v]-\widetilde Y[a,a,u]\Bigr),
\]
where
\[
\widetilde Y[a,a,t]
:=
\frac{\widetilde Y(t)-\widetilde Y(a)-\widetilde Y'(a)(t-a)}{(t-a)^2}
\]
is the repeated-node second divided difference.
Equivalently, for $u\neq v$,
\[
\widetilde H_4(a,u,v)
=
(u-a)^2(v-a)^2(v-u)\,\widetilde Y[a,a,u,v].
\]
\end{lemma}

\begin{proof}
Subtract the first row from the third and fourth rows. Since
\[
u^2-a^2=(u-a)(u+a),
\qquad
v^2-a^2=(v-a)(v+a),
\]
this gives
\[
\widetilde H_4(a,u,v)
=
(u-a)(v-a)\,
\det\!\begin{pmatrix}
1&\widetilde Y(a)&a&a^2\\
0&\widetilde Y'(a)&1&2a\\
0&\dfrac{\widetilde Y(u)-\widetilde Y(a)}{u-a}&1&u+a\\
0&\dfrac{\widetilde Y(v)-\widetilde Y(a)}{v-a}&1&v+a
\end{pmatrix}.
\]
Expanding along the first column yields
\[
\widetilde H_4(a,u,v)
=
(u-a)(v-a)\,
\det\!\begin{pmatrix}
\widetilde Y'(a)&1&2a\\
\dfrac{\widetilde Y(u)-\widetilde Y(a)}{u-a}&1&u+a\\
\dfrac{\widetilde Y(v)-\widetilde Y(a)}{v-a}&1&v+a
\end{pmatrix}.
\]
Now subtract the first row from the second and third rows:
\[
\widetilde H_4(a,u,v)
=
(u-a)(v-a)\,
\det\!\begin{pmatrix}
\widetilde Y'(a)&1&2a\\
(u-a)\widetilde Y[a,a,u]&0&u-a\\
(v-a)\widetilde Y[a,a,v]&0&v-a
\end{pmatrix}.
\]
Expanding along the middle column gives
\[
\widetilde H_4(a,u,v)
=
(u-a)^2(v-a)^2\Bigl(\widetilde Y[a,a,v]-\widetilde Y[a,a,u]\Bigr),
\]
which is the first formula. Since
\[
\widetilde Y[a,a,u,v]
=
\frac{\widetilde Y[a,a,v]-\widetilde Y[a,a,u]}{v-u},
\]
the second formula follows for $u\neq v$.
\end{proof}

\begin{proposition}[Exact nonmixed tangent-plane contacts force nearby zeros of $\mathcal R$]
\label{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero}
In the normalized nonmixed chart of
Remark~\ref{rem:nonmixed-four-point-zeros-can-carry-preexisting-branches},
assume $a,u,v\in\mathbf R$ are distinct and satisfy
\[
\widetilde H_4(a,u,v)=0.
\]
Then there exists
\[
w\in \operatorname{conv}\{a,u,v\}
\]
such that
\[
\mathcal R(w)=0.
\]
Equivalently,
\[
\widetilde Y'''(w)=0.
\]
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:normalized-nonmixed-H4-divided-difference}, since
$a,u,v$ are distinct,
\[
0=\widetilde H_4(a,u,v)
=
(u-a)^2(v-a)^2(v-u)\,\widetilde Y[a,a,u,v].
\]
Hence
\[
\widetilde Y[a,a,u,v]=0.
\]
By the Hermite--Genocchi formula for repeated-node divided differences, there
exists
\[
w\in \operatorname{conv}\{a,u,v\}
\]
such that
\[
\widetilde Y[a,a,u,v]=\frac{\widetilde Y'''(w)}{3!}.
\]
Therefore
\[
\widetilde Y'''(w)=0.
\]
In the normalized nonmixed chart one has
\[
\mathcal R(\xi)=\frac12\,\widetilde Y'''(\xi),
\]
so $\mathcal R(w)=0$.
\end{proof}

\begin{corollary}[Sign-definite nonmixed intervals are exactly-contact sterile]
\label{cor:sign-definite-R-excludes-exact-nonmixed-contacts}
Let $J$ be an open interval in the normalized nonmixed chart such that
\[
\mathcal R \text{ has fixed nonzero sign on }J.
\]
Then there do not exist distinct points $a,u,v\in J$ such that
\[
\widetilde H_4(a,u,v)=0.
\]
Equivalently, there are no exact nonmixed tangent-plane contacts with all three
nodes in $J$.
\end{corollary}

\begin{proof}
If such $a,u,v$ existed, Proposition~\ref{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero}
would produce some
\[
w\in \operatorname{conv}\{a,u,v\}\subset J
\]
with $\mathcal R(w)=0$, contradicting the sign assumption.
\end{proof}

\begin{remark}[Derivative-side interpretation of exact nonmixed contacts]
\label{rem:exact-nonmixed-contacts-are-R-zero-forcing}
Proposition~\ref{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero}
strengthens the shrinking-circuit statement
Proposition~\ref{prop:shrinking-exact-lifted-four-point-circuits-force-Tv-zero}.
It is not merely a limit theorem: every exact nonmixed tangent-plane contact
already forces a zero of the canonical derivative invariant inside the convex
hull of the three nodes,
\[
\mathcal R=\frac12\,\widetilde Y'''.
\]
Thus the nonmixed $4$-point branch is controlled not only asymptotically by
$T_v=0$, but pointwise by the zero set of a single analytic scalar.
\end{remark}

\begin{proposition}[Interval-persistent nonmixed $4$-point degeneracy forces affine planarity]
\label{prop:interval-persistent-nonmixed-four-point-forces-affine-planarity}
Let $J$ be a connected open interval in a good $v_5$-patch such that
\[
K_v\neq 0
\qquad\text{on }J.
\]
Assume
\[
T_v\equiv 0
\qquad\text{on }J.
\]
Then on $J$ one has
\[
\mathcal R\equiv 0,
\qquad
\mathcal Z\equiv \gamma
\]
for some constant $\gamma\in\mathbf C$, and hence
\[
Y=\gamma S+ax+b
\]
for some constants $a,b\in\mathbf C$. Equivalently, the lifted curve
\[
x\longmapsto (Y(x),x,S(x))
\]
lies in an affine plane on $J$.

In particular, any interval-persistent nonmixed exact lifted $4$-point branch
collapses to an affine-planar residual rather than remaining genuinely
three-dimensional.
\end{proposition}

\begin{proof}
On the nonmixed interval $J$, Proposition~\ref{prop:canonical-Z-R-invariants-lifted-four-point}
gives
\[
\mathcal R=\frac{T_v}{K_v^2}.
\]
Since $T_v\equiv 0$ and $K_v\neq 0$ on $J$, it follows that
\[
\mathcal R\equiv 0
\qquad\text{on }J.
\]
By definition,
\[
\mathcal R=\frac{d\mathcal Z}{dx},
\]
so $\mathcal Z$ is constant on $J$:
\[
\mathcal Z\equiv \gamma.
\]
Using
\[
\mathcal Z=\frac{Y''}{S''},
\]
we obtain
\[
Y''=\gamma S''.
\]
Integrating twice with respect to $x$ yields
\[
Y=\gamma S+ax+b
\]
for constants $a,b\in\mathbf C$. Therefore the lifted curve satisfies the
affine linear equation
\[
Y-\gamma S-ax-b=0
\]
throughout $J$, so it lies in an affine plane.
\end{proof}

\begin{corollary}[Recurrent exact nonmixed contacts force affine-planar collapse]
\label{cor:recurrent-exact-nonmixed-contacts-force-affine-planarity}
Let $J$ be a connected open interval in a good $v_5$-patch such that
\[
K_v\neq 0
\qquad\text{on }J.
\]
Assume that every nonempty open subinterval $I\subset J$ contains an exact
nonmixed tangent-plane contact triple. Equivalently, after local nonmixed
normalization on $I$, there exist distinct points $a,u,v\in I$ such that
\[
\widetilde H_4(a,u,v)=0.
\]
Then
\[
\mathcal R\equiv 0
\qquad\text{on }J,
\]
hence
\[
T_v\equiv 0
\qquad\text{on }J,
\]
and therefore the lifted curve is affine-planar on $J$:
\[
Y=\gamma S+ax+b
\]
for some constants $\gamma,a,b\in\mathbf C$.
\end{corollary}

\begin{proof}
Let $I\subset J$ be any nonempty open subinterval. By assumption, $I$
contains an exact nonmixed tangent-plane contact triple. After nonmixed
normalization on $I$, Proposition~\ref{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero}
produces a point $w_I\in I$ such that
\[
\mathcal R(w_I)=0.
\]
Thus every nonempty open subinterval of $J$ contains a zero of $\mathcal R$.
Since $\mathcal R$ is analytic, its zero set cannot have an accumulation point
in $J$ unless
\[
\mathcal R\equiv 0
\qquad\text{on }J.
\]
Because $K_v\neq 0$ on $J$ and
\[
\mathcal R=\frac{T_v}{K_v^2},
\]
it follows that
\[
T_v\equiv 0
\qquad\text{on }J.
\]
Now apply
Proposition~\ref{prop:interval-persistent-nonmixed-four-point-forces-affine-planarity}
to conclude that
\[
Y=\gamma S+ax+b
\]
on $J$.
\end{proof}

\begin{lemma}[Derivative formula for the repeated-node nonmixed profile]
\label{lem:Da-derivative-formula}
In the normalized nonmixed chart, define
\[
D_a(t):=\widetilde Y[a,a,t]
=
\frac{\widetilde Y(t)-\widetilde Y(a)-\widetilde Y'(a)(t-a)}{(t-a)^2},
\qquad
D_a(a):=\frac12\,\widetilde Y''(a).
\]
Then $D_a(t)$ extends real-analytically across $t=a$, and
\[
D_a(t)=\int_0^1 (1-s)\,\widetilde Y''(a+s(t-a))\,ds.
\]
Moreover,
\[
D_a'(t)
=
\int_0^1 s(1-s)\,\widetilde Y'''(a+s(t-a))\,ds
=
2\int_0^1 s(1-s)\,\mathcal R(a+s(t-a))\,ds.
\]
\end{lemma}

\begin{proof}
Taylor's integral formula gives
\[
\widetilde Y(t)
=
\widetilde Y(a)+\widetilde Y'(a)(t-a)
+(t-a)^2\int_0^1 (1-s)\,\widetilde Y''(a+s(t-a))\,ds.
\]
Dividing by $(t-a)^2$ proves the first formula for $t\neq a$, and the
analytic extension across $t=a$ is immediate. Differentiating under the
integral sign gives
\[
D_a'(t)
=
\int_0^1 s(1-s)\,\widetilde Y'''(a+s(t-a))\,ds.
\]
Since $\mathcal R=\frac12\,\widetilde Y'''$ in the normalized nonmixed chart,
the last formula follows.
\end{proof}

\begin{proposition}[Parity classification of isolated nonmixed zeros of $\mathcal R$]
\label{prop:parity-classification-isolated-nonmixed-R-zeros}
Let $\xi_0\in\mathbf R$ be an isolated zero of the nonmixed invariant
\[
\mathcal R(\xi)=\frac12\,\widetilde Y'''(\xi),
\]
and write
\[
\mathcal R(\xi)=(\xi-\xi_0)^m\,\rho(\xi),
\qquad
m\ge 1,
\qquad
\rho(\xi_0)\neq 0.
\]

\smallskip

\noindent
\emph{(i) Even-order sterility.}
If $m$ is even, then there exists a neighborhood $U$ of $\xi_0$ such that
for every $a\in U$, the function
\[
D_a(t):=\widetilde Y[a,a,t]
\]
is strictly monotone on $U$. In particular, there do not exist distinct
$a,u,v\in U$ such that
\[
\widetilde H_4(a,u,v)=0.
\]

\smallskip

\noindent
\emph{(ii) Odd-order birth.}
If $m$ is odd, then there exists a neighborhood $U$ of $\xi_0$ and a
real-analytic function $\tau:U\to U$ such that
\[
\tau(\xi_0)=\xi_0,
\qquad
\tau'(\xi_0)=-1,
\qquad
D_a'(\tau(a))=0
\quad (a\in U).
\]
Moreover,
\[
D_a''(\tau(a))\neq 0
\quad (a\in U\setminus\{\xi_0\}),
\]
so for each $a\in U\setminus\{\xi_0\}$, the function $D_a$ has a strict
local extremum at $t=\tau(a)$. Consequently, for each such $a$, there exist
distinct points $u_-(a),u_+(a)\in U$ with
\[
u_-(a)<\tau(a)<u_+(a),
\qquad
D_a(u_-(a))=D_a(u_+(a)),
\]
and hence
\[
\widetilde H_4(a,u_-(a),u_+(a))=0.
\]
\end{proposition}

\begin{proof}
By translation in the normalized chart, we may assume $\xi_0=0$. Thus
\[
\mathcal R(\xi)=\xi^m\rho(\xi),
\qquad
\rho(0)\neq 0.
\]

For the even-order case, shrink to a neighborhood $U$ on which $\rho$ has
fixed nonzero sign. Since $m$ is even, $\xi^m\ge 0$, so $\mathcal R$ has
fixed sign on $U$, vanishing only at $0$. By
Lemma~\ref{lem:Da-derivative-formula},
\[
D_a'(t)=2\int_0^1 s(1-s)\,\mathcal R(a+s(t-a))\,ds.
\]
For $a\neq t$, the affine segment $a+s(t-a)$ is not identically zero, so the
integrand has fixed sign and is not identically zero. Hence $D_a'(t)$ has
fixed nonzero sign for all $a\neq t$ in $U$, and therefore each $D_a$ is
strictly monotone on $U$. Thus $D_a$ is injective on $U$, and by
Lemma~\ref{lem:normalized-nonmixed-H4-divided-difference} there are no exact
contacts $\widetilde H_4(a,u,v)=0$ with distinct $a,u,v\in U$.

Now assume $m$ is odd. Write $a=h$ and $t=\lambda h$. Then
Lemma~\ref{lem:Da-derivative-formula} gives
\[
D_h'(\lambda h)
=
2h^m\,G(h,\lambda),
\]
where
\[
G(h,\lambda)
:=
\int_0^1 s(1-s)\bigl(1+s(\lambda-1)\bigr)^m
\rho\!\bigl(h(1+s(\lambda-1))\bigr)\,ds.
\]
This is real-analytic in $(h,\lambda)$, and
\[
G(0,\lambda)=\rho(0)\,J_m(\lambda),
\qquad
J_m(\lambda):=\int_0^1 s(1-s)\bigl(1+s(\lambda-1)\bigr)^m\,ds.
\]
Since $m$ is odd,
\[
J_m(-1)=\int_0^1 s(1-s)(1-2s)^m\,ds=0
\]
by the symmetry $s\mapsto 1-s$, while
\[
J_m'(-1)
=
m\int_0^1 s^2(1-s)(1-2s)^{m-1}\,ds>0
\]
because $m-1$ is even. Thus
\[
\partial_\lambda G(0,-1)=\rho(0)J_m'(-1)\neq 0.
\]
By the implicit function theorem, there exists a unique real-analytic function
$\lambda(h)$ near $0$ such that
\[
\lambda(0)=-1,
\qquad
G(h,\lambda(h))=0.
\]
Define
\[
\tau(h):=\lambda(h)h.
\]
Then
\[
\tau(0)=0,
\qquad
\tau'(0)=\lambda(0)=-1,
\]
and
\[
D_h'(\tau(h))=0.
\]

It remains to show that this critical point is a strict local extremum. By
Lemma~\ref{lem:Da-derivative-formula},
\[
D_a''(t)=2\int_0^1 s^2(1-s)\,\mathcal R'(a+s(t-a))\,ds.
\]
Substituting $a=h$, $t=\lambda(h)h$, and using
\[
\mathcal R'(\xi)=m\xi^{m-1}\rho(\xi)+\xi^m\rho'(\xi),
\]
one obtains
\[
D_h''(\tau(h))
=
2h^{m-1}\rho(0)\,J_m'(-1)+O(h^m).
\]
Since $\rho(0)J_m'(-1)\neq 0$, it follows that
\[
D_h''(\tau(h))\neq 0
\]
for $h\neq 0$ sufficiently small. Therefore $t=\tau(h)$ is a strict local
extremum of $D_h$. Hence there exist distinct points $u_-(h)$, $u_+(h)$
arbitrarily close to $\tau(h)$ such that
\[
D_h(u_-(h))=D_h(u_+(h)).
\]
By Lemma~\ref{lem:normalized-nonmixed-H4-divided-difference},
\[
\widetilde H_4(h,u_-(h),u_+(h))
=
(h-u_-(h))^2(h-u_+(h))^2
\bigl(D_h(u_+(h))-D_h(u_-(h))\bigr)=0.
\]
This proves the odd-order birth statement.
\end{proof}

\begin{remark}[Reflection law for odd-order birth]
\label{rem:reflection-law-odd-order-R-zero}
In the odd-order case of
Proposition~\ref{prop:parity-classification-isolated-nonmixed-R-zeros},
the critical-point branch satisfies
\[
\tau(a)=2\xi_0-a+O((a-\xi_0)^2).
\]
Thus the local exact nonmixed contact family born at any odd-order zero of
$\mathcal R$ has the same first-order reflection geometry across that zero as
in the simple-zero case.
\end{remark}

\begin{proposition}[Odd-zero critical branch is uniformly unrooted]
\label{prop:odd-zero-critical-branch-uniformly-unrooted}
Let $\xi_0$ be an isolated odd-order zero of
\[
\mathcal R(\xi)=\frac12\,\widetilde Y'''(\xi),
\]
and, after translation, write
\[
\xi_0=0,
\qquad
\mathcal R(\xi)=\xi^m\rho(\xi),
\qquad
m\ge 1 \text{ odd},
\qquad
\rho(0)\neq 0.
\]
Let
\[
D_a(t):=\widetilde Y[a,a,t],
\qquad
D_a(a)=\frac12\,\widetilde Y''(a)=\mathcal Z(a).
\]

Then there exists $\varepsilon>0$ and a unique real-analytic function
\[
\mu:(-\varepsilon,\varepsilon)\to\mathbf R,
\qquad
\mu(0)=0,
\]
such that for every sufficiently small $h>0$ the unique nontrivial critical pair
\[
a(h):=h(\mu(h)-1),
\qquad
x(h):=h(\mu(h)+1)
\]
satisfies
\[
D_{a(h)}'(x(h))=0,
\]
and every critical pair
\[
a<x,\qquad |a|+|x|<\varepsilon,\qquad D_a'(x)=0
\]
is of this form.

Moreover,
\[
D_{a(h)}(x(h))-D_{a(h)}(a(h))
=
-\frac{\rho(0)}{m+2}\,h^{m+1}+O(h^{m+2}).
\]
Equivalently,
\[
D_{a(h)}(x(h))-D_{a(h)}(a(h))
=
-\frac{\rho(0)}{2^{m+1}(m+2)}(x(h)-a(h))^{m+1}
+o\!\left((x(h)-a(h))^{m+1}\right).
\]

In particular, after shrinking $\varepsilon$ if needed, every nontrivial nearby
critical pair satisfies
\[
D_a(x)\neq D_a(a),
\]
indeed
\[
\operatorname{sgn}\bigl(D_a(x)-D_a(a)\bigr)=-\operatorname{sgn}\rho(0).
\]
So no sheared repeated-node tangent-contact event can occur in a sufficiently
small neighborhood of an isolated odd zero of $\mathcal R$.
\end{proposition}

\begin{proof}
Write every nearby pair as
\[
a=c-h,\qquad x=c+h,\qquad h=\frac{x-a}{2}>0,\qquad \mu=\frac{c}{h}.
\]

By Lemma~\ref{lem:Da-derivative-formula},
\[
D_a'(x)
=
2\int_0^1 s(1-s)\,\mathcal R(a+s(x-a))\,ds.
\]
With the change of variables $u=2s-1$, this becomes
\[
D_{c-h}'(c+h)
=
\frac14\int_{-1}^1 (1-u^2)\,\mathcal R(c+hu)\,du
=
h^m F(h,\mu),
\]
where
\[
F(h,\mu)
:=
\frac14\int_{-1}^1 (1-u^2)(\mu+u)^m
\rho\!\bigl(h(\mu+u)\bigr)\,du.
\]
This is real-analytic in $(h,\mu)$ near $(0,0)$. At $h=0$,
\[
F(0,\mu)=\frac{\rho(0)}{4}K_m(\mu),
\qquad
K_m(\mu):=\int_{-1}^1 (1-u^2)(\mu+u)^m\,du.
\]
Since $m$ is odd,
\[
K_m(0)=0,
\]
and
\[
K_m'(\mu)
=
m\int_{-1}^1 (1-u^2)(\mu+u)^{m-1}\,du>0
\]
for all real $\mu$, because $m-1$ is even. Hence $\mu=0$ is the unique real
root of $K_m$, and it is simple. Therefore
\[
\partial_\mu F(0,0)\neq 0,
\]
so the implicit function theorem gives a unique real-analytic branch
\[
\mu=\mu(h),\qquad \mu(0)=0,
\]
parameterizing all nearby critical pairs.

Now write
\[
\mathcal Z(\xi)=\mathcal Z(0)+\xi^{m+1}\eta(\xi),
\qquad
\eta(0)=\frac{\rho(0)}{m+1},
\]
since $\mathcal Z'=\mathcal R=\xi^m\rho(\xi)$.
Using
\[
D_a(x)-D_a(a)
=
\frac12\int_{-1}^1 (1-u)\bigl(\mathcal Z(c+hu)-\mathcal Z(c-h)\bigr)\,du,
\]
we obtain
\[
D_{c-h}(c+h)-D_{c-h}(c-h)=h^{m+1}G(h,\mu),
\]
where
\[
G(h,\mu):=
\frac12\int_{-1}^1 (1-u)\Bigl(
(\mu+u)^{m+1}\eta\!\bigl(h(\mu+u)\bigr)
-(\mu-1)^{m+1}\eta\!\bigl(h(\mu-1)\bigr)
\Bigr)\,du.
\]
Again $G$ is real-analytic. Evaluating at $(0,0)$ gives
\[
G(0,0)
=
\frac{\eta(0)}{2}\int_{-1}^1 (1-u)(u^{m+1}-1)\,du
=
-\frac{\rho(0)}{m+2}\neq 0.
\]
Therefore along the critical branch,
\[
D_{a(h)}(x(h))-D_{a(h)}(a(h))
=
h^{m+1}G(h,\mu(h))
=
-\frac{\rho(0)}{m+2}h^{m+1}+O(h^{m+2}),
\]
which has fixed nonzero sign for $h$ sufficiently small. This proves the claim.
\end{proof}

\begin{corollary}[Sheared repeated-node tangent-contact is impossible near an isolated odd $\mathcal R$-zero]
\label{cor:sheared-event-impossible-near-isolated-odd-R-zero}
Let $b$ be an isolated odd-order zero of $\mathcal R$ on a genuine opened
nonmixed arc. Then there exists a neighborhood $U$ of $b$ such that no pair
\[
a<x,\qquad a,x\in U,
\]
can satisfy
\[
\widetilde Y_{\mathcal Z(a)}''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0.
\]
Equivalently, no rooted sheared repeated-node tangent-contact event occurs in
a sufficiently small neighborhood of an isolated odd zero of $\mathcal R$.
\end{corollary}

\begin{proof}
In the normalized nonmixed chart centered at $b$, the rooted sheared event is
exactly the conjunction
\[
D_a'(x)=0,
\qquad
D_a(x)=D_a(a)=\mathcal Z(a).
\]
Proposition~\ref{prop:odd-zero-critical-branch-uniformly-unrooted} shows that
for every sufficiently small nontrivial critical pair one has
\[
D_a(x)-D_a(a)\neq 0.
\]
So the rooted sheared event is impossible near $b$.
\end{proof}

\begin{proposition}[Quadratic-envelope factorization on a nonmixed interval]
\label{prop:quadratic-envelope-factorization-nonmixed}
Let $J$ be a connected open interval in a good $v_5$-patch such that
\[
K_v\neq 0
\qquad\text{on }J.
\]
Write
\[
Q_v(h)=(Y(h),x(h),S(h)),
\qquad
\mathcal Z=\frac{Y''}{S''},
\qquad
\mathcal R=\mathcal Z'=\frac{T_v}{K_v^2}.
\]
For a fixed source point $a\in J$, define
\[
A_a(x):=Y(x)-Y(a)-Y'(a)(x-a),
\]
\[
B_a(x):=S(x)-S(a)-S'(a)(x-a),
\]
and
\[
\Gamma_a(x):=\frac{A_a(x)}{B_a(x)}
\qquad (x\neq a).
\]

Then:

\smallskip

\noindent
\emph{(i) Tangent-contact denominator.}
For $x\neq a$,
\[
B_a(x)=\int_a^x (x-t)\,S''(t)\,dt,
\]
so $B_a(x)\neq 0$ on $J\setminus\{a\}$.

\smallskip

\noindent
\emph{(ii) Exact repeated-source factorization.}
For distinct $a,u,v\in J$,
\[
H_4(a,u,v)
=
-\,B_a(u)\,B_a(v)\,\bigl(\Gamma_a(u)-\Gamma_a(v)\bigr).
\]

\smallskip

\noindent
\emph{(iii) Integral representation.}
For $x\neq a$,
\[
\Gamma_a(x)
=
\frac{\displaystyle\int_a^x (x-t)\,\mathcal Z(t)\,S''(t)\,dt}
{\displaystyle\int_a^x (x-t)\,S''(t)\,dt}.
\]

\smallskip

\noindent
\emph{(iv) Positive-kernel derivative formula.}
For $x\neq a$,
\[
\Gamma_a'(x)
=
\frac{1}{B_a(x)^2}\int_a^x \Omega_{a,x}(r)\,\mathcal R(r)\,dr,
\]
where
\[
\Omega_{a,x}(r)
:=
\int_a^r\!\!\int_r^x (t-s)\,S''(s)\,S''(t)\,dt\,ds.
\]
Moreover, after orienting $x$ so that $S''$ has fixed sign on $J$,
\[
\Omega_{a,x}(r)>0
\qquad (a<r<x).
\]
\end{proposition}

\begin{proof}
Since $K_v=(x')^3S''$ and $x'\neq 0$ on a good $v_5$-patch, the function
$S''$ has fixed nonzero sign on $J$. Therefore
\[
B_a(x)=\int_a^x (x-t)\,S''(t)\,dt
\]
has fixed nonzero sign for $x\neq a$, proving (i).

For (ii), use the repeated-node determinant
\[
H_4(a,u,v)=
\det\!\begin{pmatrix}
1&Y(a)&a&S(a)\\
0&Y'(a)&1&S'(a)\\
1&Y(u)&u&S(u)\\
1&Y(v)&v&S(v)
\end{pmatrix}.
\]
Subtract from the $u$-row and $v$-row the corresponding affine tangent data
at $a$. This gives
\[
H_4(a,u,v)
=
\det\!\begin{pmatrix}
1&Y(a)&a&S(a)\\
0&Y'(a)&1&S'(a)\\
0&A_a(u)&0&B_a(u)\\
0&A_a(v)&0&B_a(v)
\end{pmatrix}
=
A_a(u)B_a(v)-A_a(v)B_a(u),
\]
hence
\[
H_4(a,u,v)
=
-\,B_a(u)B_a(v)\bigl(\Gamma_a(u)-\Gamma_a(v)\bigr).
\]

For (iii), Taylor's integral formula gives
\[
A_a(x)=\int_a^x (x-t)\,Y''(t)\,dt
=
\int_a^x (x-t)\,\mathcal Z(t)\,S''(t)\,dt,
\]
while
\[
B_a(x)=\int_a^x (x-t)\,S''(t)\,dt.
\]
Dividing yields the formula for $\Gamma_a$.

For (iv), set
\[
N_a(x):=\int_a^x (x-t)\,\mathcal Z(t)\,S''(t)\,dt,
\qquad
D_a(x):=\int_a^x (x-t)\,S''(t)\,dt=B_a(x).
\]
Then $\Gamma_a=N_a/D_a$, so
\[
\Gamma_a'(x)=\frac{N_a'(x)D_a(x)-N_a(x)D_a'(x)}{D_a(x)^2}.
\]
A symmetrization gives
\[
N_a'D_a-N_aD_a'
=
\frac12\int_a^x\!\!\int_a^x
(\mathcal Z(t)-\mathcal Z(s))(t-s)\,S''(s)\,S''(t)\,ds\,dt.
\]
Since $\mathcal Z(t)-\mathcal Z(s)=\int_s^t \mathcal R(r)\,dr$, Fubini yields
\[
N_a'D_a-N_aD_a'
=
\int_a^x \Omega_{a,x}(r)\,\mathcal R(r)\,dr
\]
with
\[
\Omega_{a,x}(r)
=
\int_a^r\!\!\int_r^x (t-s)\,S''(s)\,S''(t)\,dt\,ds.
\]
Because $t-s>0$ on the region of integration and $S''$ has fixed sign on
$J$, one has $\Omega_{a,x}(r)>0$ after orienting the $x$-coordinate.
This proves (iv).
\end{proof}

\begin{corollary}[Repeated-source monotonicity on one-sign $\mathcal R$-blocks]
\label{cor:repeated-source-monotonicity-one-sign-R}
Let $I\subset J$ be a subinterval on which
\[
\mathcal R \text{ has fixed nonzero sign.}
\]
Then for every $a\in I$, the function $x\mapsto \Gamma_a(x)$ is strictly
monotone on each component of $I\setminus\{a\}$. In particular, there do not
exist points
\[
a<u<v \quad \text{in } I
\]
such that
\[
H_4(a,u,v)=0.
\]
\end{corollary}

\begin{proof}
This is immediate from Proposition~\ref{prop:quadratic-envelope-factorization-nonmixed}:
the derivative $\Gamma_a'(x)$ is a positive-kernel average of $\mathcal R$,
so it has the same sign as $\mathcal R$ on each one-sign block. The factorization
of $H_4$ then excludes repeated-source exact contacts there.
\end{proof}

\begin{remark}[Below-lifted source-determinant reformulation of $\Gamma_a$]
\label{rem:source-determinant-reformulation-Gammaa}
Let
\[
\lambda:=\frac{\Delta_7}{v_5},
\qquad
x=\frac{v_5}{c},
\qquad
Y=\frac{u_5}{c},
\qquad
S=\frac{\lambda}{c}.
\]
For any scalar germ $f$, define
\[
D_f(a,h):=
\det\!\begin{pmatrix}
c(a)&v_5(a)&f(a)\\
c'(a)&v_5'(a)&f'(a)\\
c(h)&v_5(h)&f(h)
\end{pmatrix}.
\]
A direct row reduction gives
\[
D_f(a,h)
=
c(a)^2c(h)\Bigl(
x'(a)\bigl(F(h)-F(a)\bigr)-F'(a)\bigl(x(h)-x(a)\bigr)
\Bigr),
\qquad
F=\frac{f}{c}.
\]
In particular,
\[
\Psi_a(h):=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)}
=
\Gamma_{x(a)}(x(h)).
\]
Thus the repeated-source nonmixed $4$-point geometry is already encoded by a
finite ratio of source determinants.

Likewise, if one sets
\[
\mathfrak D(a,h):=
\det\!\begin{pmatrix}
c(a)&v_5(a)&\lambda(a)&u_5(a)\\
c'(a)&v_5'(a)&\lambda'(a)&u_5'(a)\\
c(h)&v_5(h)&\lambda(h)&u_5(h)\\
c'(h)&v_5'(h)&\lambda'(h)&u_5'(h)
\end{pmatrix},
\]
then a Pl\"ucker identity yields
\[
\frac{d}{dh}\Psi_a(h)
=
\frac{W_h(c,v_5)(a)\,\mathfrak D(a,h)}{D_\lambda(a,h)^2}.
\]
So the sign of the quadratic-envelope derivative is governed by one explicit
$4\times 4$ source determinant.

Moreover, combining the identity
\[
\Psi_a(h)=\Gamma_{x(a)}(x(h))
\]
with Proposition~\ref{prop:quadratic-envelope-factorization-nonmixed} gives the
exact source-level kernel formula
\[
\mathfrak D(a,h)
=
c(a)^2c(h)^2x'(a)x'(h)
\int_{x(a)}^{x(h)} \Omega_{x(a),x(h)}(r)\,\mathcal R(r)\,dr.
\]
After orienting the $x$-coordinate so that $x'>0$ on the interval, the sign
of $\mathfrak D(a,h)$ is therefore exactly the sign of the corresponding
positive-kernel average of $\mathcal R$. In particular, on every one-sign
$\mathcal R$-block the quadruple
\[
(c,v_5,\lambda,u_5)
\]
is osculatory-ECT in the sense that $\mathfrak D(a,h)$ has fixed nonzero sign
for $a<h$.
\end{remark}

\begin{corollary}[Source-level Wronskian consequences for the nonmixed branch]
\label{cor:source-level-Wronskian-consequences-nonmixed}
On a good nonmixed $v_5$-patch, the following hold.

\begin{enumerate}
\item If there is an exact nonmixed tangent-plane contact, then there exists a
source point $h_*$ in the source convex hull of the contact nodes such that
\[
\mathcal W_{\mathrm{src}}(h_*)=0.
\]

\item If $\mathcal W_{\mathrm{src}}$ has fixed nonzero sign on an open
nonmixed interval, then there are no exact nonmixed tangent-plane contacts on
that interval.

\item If every nonempty open subinterval of a nonmixed interval contains an
exact nonmixed tangent-plane contact, then
\[
\mathcal W_{\mathrm{src}}\equiv 0
\]
on that interval, hence
\[
\mathcal R\equiv 0,
\]
and therefore the lifted curve collapses to affine-planar geometry.
\end{enumerate}
\end{corollary}

\begin{proof}
For (1), Proposition~\ref{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero}
produces a point in the convex hull of the three normalized nodes where
$\mathcal R=0$. Pulling back through the monotone source-to-$x$ coordinate
on the nonmixed patch and using
Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point} gives
$\mathcal W_{\mathrm{src}}=0$ at the corresponding source point.

For (2), by
Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point},
$\mathcal W_{\mathrm{src}}$ and $\mathcal R$ have the same sign on a
nonmixed arc. So Corollary~\ref{cor:repeated-source-monotonicity-one-sign-R}
applies.

For (3), every nonempty open subinterval contains a zero of
$\mathcal W_{\mathrm{src}}$ by (1), so analyticity forces
$\mathcal W_{\mathrm{src}}\equiv 0$. Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}
then gives $\mathcal R\equiv 0$, and
Corollary~\ref{cor:recurrent-exact-nonmixed-contacts-force-affine-planarity}
gives affine-planar collapse.
\end{proof}

\begin{remark}[Chebyshev formulation of the nonmixed burden]
\label{rem:Chebyshev-formulation-nonmixed}
Corollary~\ref{cor:source-level-Wronskian-consequences-nonmixed} shows that the
nonmixed $4$-point branch is controlled source-level by the pair
\[
(J_\lambda,\ J_{u_5}).
\]
If this pair were a Chebyshev pair on an opened nonmixed arc, i.e.
\[
\mathcal W_{\mathrm{src}}\neq 0
\]
throughout that arc, then the entire nonmixed $4$-point branch would be
sterile there. Thus a one-sign theorem for $\mathcal W_{\mathrm{src}}$ would
still be sufficient. However, the later source-level no-go theorem shows that
generic Wronskian algebra alone is not enough to force such a statement. The
actual remaining burden is therefore a source-coupling theorem that excludes
the analytically possible odd zeros of $\mathcal W_{\mathrm{src}}$ on genuine
opened nonmixed arcs.
\end{remark}

\begin{proposition}[Lift of the source-level Wronskian to a $4\times4$ Wronskian]
\label{prop:source-level-Wronskian-lifts-to-4x4}
With
\[
J_\lambda=W(c,v_5,\lambda),
\qquad
J_{u_5}=W(c,v_5,u_5),
\qquad
M=W(c,v_5)=cv_5'-c'v_5,
\]
one has the exact identity
\[
\boxed{
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'
=
W(J_\lambda,J_{u_5})
=
M\,W(c,v_5,\lambda,u_5).
}
\]
Thus, on a nonmixed arc where $M\neq 0$, the odd-zero problem for
$\mathcal W_{\mathrm{src}}$ is equivalent to the odd-zero problem for the
source-level $4\times4$ Wronskian
\[
\mathcal U_{\mathrm{src}}:=W(c,v_5,\lambda,u_5).
\]
\end{proposition}

\begin{proof}
By definition,
\[
\mathcal W_{\mathrm{src}}=W(J_\lambda,J_{u_5}).
\]
Now apply the Sylvester--Wronski identity
\[
W\!\bigl(W(f_1,f_2,f_3),\,W(f_1,f_2,f_4)\bigr)
=
W(f_1,f_2)\,W(f_1,f_2,f_3,f_4)
\]
with
\[
(f_1,f_2,f_3,f_4)=(c,v_5,\lambda,u_5).
\]
This gives
\[
W(J_\lambda,J_{u_5})
=
W(c,v_5)\,W(c,v_5,\lambda,u_5)
=
M\,W(c,v_5,\lambda,u_5),
\]
which is exactly the claimed identity.
\end{proof}

\begin{proposition}[The current source-level Wronskian package is not yet a contradiction engine for nonmixed odd zeros]
\label{prop:source-level-Wronskian-package-not-enough}
Let $I$ be an interval on which
\[
c\neq 0,
\qquad
M=W(c,v_5)\neq 0,
\qquad
J_\lambda=W(c,v_5,\lambda)\neq 0.
\]
Then:

\begin{enumerate}
\item for every analytic forcing $F:I\to\mathbf C$, there exists an analytic
function $u_5$ on $I$ such that
\[
W(c,v_5,\lambda,u_5)=F;
\]

\item consequently, for every analytic forcing $G:I\to\mathbf C$, there exists
an analytic function $u_5$ on $I$ such that
\[
\mathcal W_{\mathrm{src}}=G;
\]

\item equivalently, for every analytic forcing $R:I\to\mathbf C$, there exists
an analytic function $u_5$ on $I$ such that
\[
\mathcal R=R.
\]
\end{enumerate}

In particular, at the current source-level ratio/Wronskian/$4\times4$-determinant
level, the zero set, parity, and odd/even vanishing pattern of
$\mathcal W_{\mathrm{src}}$ and $\mathcal R$ are formally unconstrained.
\end{proposition}

\begin{proof}
Expand the $4\times4$ Wronskian along the $u_5$-column. Since the highest
derivative of $u_5$ appearing in $W(c,v_5,\lambda,u_5)$ is $u_5'''$, with
coefficient exactly
\[
W(c,v_5,\lambda)=J_\lambda,
\]
there exist analytic coefficients $a_0,a_1,a_2$ on $I$ such that
\[
W(c,v_5,\lambda,u_5)
=
J_\lambda\,u_5'''+a_2u_5''+a_1u_5'+a_0u_5.
\]
Because $J_\lambda\neq 0$ on $I$, this is a third-order linear analytic ODE
for $u_5$ with nonvanishing leading coefficient. Standard analytic ODE
existence therefore gives an analytic solution $u_5$ on $I$ for every
analytic forcing $F$. This proves (1).

For (2), given analytic $G$, set
\[
F:=\frac{G}{M}.
\]
Since $M\neq 0$ on $I$, $F$ is analytic. By (1), choose $u_5$ such that
\[
W(c,v_5,\lambda,u_5)=F.
\]
Then Proposition~\ref{prop:source-level-Wronskian-lifts-to-4x4} gives
\[
\mathcal W_{\mathrm{src}}
=
M\,W(c,v_5,\lambda,u_5)
=
G.
\]

For (3), given analytic $R$, set
\[
G:=\frac{M J_\lambda^2}{c^2}\,R.
\]
Since $c\neq 0$, $M\neq 0$, and $J_\lambda\neq 0$ on $I$, this is
analytic. By (2), choose $u_5$ such that $\mathcal W_{\mathrm{src}}=G$.
Then Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point} gives
\[
\mathcal R
=
\frac{c^2}{M}\frac{\mathcal W_{\mathrm{src}}}{J_\lambda^2}
=
\frac{c^2}{M}\frac{G}{J_\lambda^2}
=
R.
\qedhere
\]
\end{proof}

\begin{remark}[Ceiling of the current source-level reduction]
\label{rem:ceiling-of-current-source-level-reduction}
Propositions~\ref{prop:source-level-Wronskian-lifts-to-4x4} and
\ref{prop:source-level-Wronskian-package-not-enough} show that the current
source-level reduction has been pushed to its natural ceiling.  The nonmixed
$4$-point branch is indeed equivalent to an odd-zero problem for the
gauge-invariant source-level Wronskian
\[
\mathcal W_{\mathrm{src}},
\]
and even to the $4\times4$ Wronskian $W(c,v_5,\lambda,u_5)$.  But at that
level the odd-zero pattern is still formally free.

Accordingly, the missing ingredient can no longer be a generic Wronskian or
determinant argument.  It must be a genuine \emph{source-coupling theorem}:
one that uses additional identities coming from the actual RH source structure
to show that the analytically possible $u_5$-freedom exhibited above is not
realizable on a genuine opened nonmixed arc.
\end{remark}

\begin{remark}[First-loss rigidification of the quadratic-envelope scalar]
\label{rem:first-loss-rigidification-nonmixed}
Set
\[
M(a,x):=B_a(x)^2\,\Gamma_a'(x)=A_a'(x)B_a(x)-A_a(x)B_a'(x).
\]
Then
\[
\partial_x M(a,x)=S''(x)\,B_a(x)\,\bigl(\mathcal Z(x)-\Gamma_a(x)\bigr).
\]
Moreover, at any point where $M(a,x)=0$,
\[
\partial_a M(a,x)=S''(a)\,C_a(x)\,\bigl(\mathcal Z(a)-\Gamma_a(x)\bigr),
\]
where
\[
C_a(x):=S(a)-S(x)+S'(x)(x-a)=\int_a^x (t-a)\,S''(t)\,dt.
\]

Thus any formally attained first loss of monotonicity for $\Gamma_a$ forces
\[
\Gamma_a(x)=\mathcal Z(a).
\]
After the affine shear
\[
\widetilde Y_\gamma:=Y-\gamma S,
\qquad \gamma=\mathcal Z(a),
\]
this yields
\[
\widetilde Y_\gamma''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0.
\]
So a first loss of quadratic-envelope monotonicity can only occur through a
sheared repeated-node tangent-contact configuration rooted at a curvature-zero
point. In particular, the remaining nonmixed obstruction is diagonal in nature:
it is governed by odd zeros of $\mathcal R$, not by an independent separated
source-target mechanism.
\end{remark}

\begin{proposition}[The current $3$-point package is not by itself a contradiction engine for nonmixed first loss]
\label{prop:three-point-package-not-enough-for-nonmixed-first-loss}
Fix an analytic function $S$ on an interval $I$ with
\[
S''\neq 0
\qquad\text{on }I.
\]
Let $a<x$ be two points of $I$. Then there exist an analytic function $Y$ on
$I$ and a constant $\gamma\in\mathbf R$ such that, with
\[
\widetilde Y_\gamma:=Y-\gamma S,
\]
one has
\[
\widetilde Y_\gamma''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0,
\]
where
\[
\widetilde H_3(a,u):=
\widetilde Y_\gamma(u)-\widetilde Y_\gamma(a)-\widetilde Y_\gamma'(a)(u-a).
\]
In particular, the rigidified repeated-node tangent-contact event from
Remark~\ref{rem:first-loss-rigidification-nonmixed} is formally compatible with
an arbitrary fixed nonmixed planar curve
\[
\Lambda_v=(x,S),
\]
so the established $3$-point package for $\Lambda_v$ alone cannot exclude that
event.
\end{proposition}

\begin{proof}
Define
\[
T_{a,x}(t):=(t-a)^3(t-x)^2.
\]
Then
\[
T_{a,x}(a)=0,
\qquad
T_{a,x}'(a)=0,
\qquad
T_{a,x}''(a)=0,
\qquad
T_{a,x}(x)=0,
\qquad
T_{a,x}'(x)=0.
\]
Hence
\[
T_{a,x}(x)-T_{a,x}(a)-T_{a,x}'(a)(x-a)=0,
\qquad
T_{a,x}'(x)-T_{a,x}'(a)=0.
\]
Now fix any $\gamma\in\mathbf R$ and set
\[
Y:=\gamma S+T_{a,x}.
\]
Then
\[
\widetilde Y_\gamma=Y-\gamma S=T_{a,x},
\]
so
\[
\widetilde Y_\gamma''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0.
\]
Since $S$ itself has not changed and $S''\neq 0$ on $I$, the original
$3$-point geometry of $\Lambda_v=(x,S)$ on $I$ is exactly the same as before.
Thus the sheared repeated-node tangent-contact event is not ruled out by the
planar derivative geometry of $\Lambda_v$ alone.
\end{proof}

\begin{proposition}[A sheared repeated-node event forces two interior $\mathcal R$-zeros]
\label{prop:sheared-repeated-node-forces-two-R-zeros}
Let $J$ be a connected opened nonmixed arc, and let
\[
a<x
\qquad\text{lie in }J.
\]
Set
\[
\gamma:=\mathcal Z(a),
\qquad
\widetilde Y_\gamma:=Y-\gamma S,
\]
and let
\[
\widetilde H_3(a,u):=
\widetilde Y_\gamma(u)-\widetilde Y_\gamma(a)-\widetilde Y_\gamma'(a)(u-a).
\]
Assume
\[
\widetilde Y_\gamma''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0.
\]
Then one of the following holds:
\begin{enumerate}
\item $\mathcal R\equiv 0$ on $[a,x]$;
\item there exist points
\[
a<r_1<r_2<x
\]
such that
\[
\mathcal Z(r_1)=\mathcal Z(r_2)=\mathcal Z(a).
\]
Consequently there exist
\[
\xi_1\in(a,r_1),
\qquad
\xi_2\in(r_1,r_2)
\]
with
\[
\mathcal R(\xi_1)=\mathcal R(\xi_2)=0.
\]
\end{enumerate}
In particular, every nontrivial sheared repeated-node event contains at least two
interior zeros of $\mathcal R$.
\end{proposition}

\begin{proof}
Since
\[
\widetilde Y_\gamma''=Y''-\gamma S''=(\mathcal Z-\gamma)S'',
\]
the choice $\gamma=\mathcal Z(a)$ gives
\[
\widetilde Y_\gamma''=(\mathcal Z-\mathcal Z(a))S''.
\]
Also,
\[
\partial_x\widetilde H_3(a,x)
=
\widetilde Y_\gamma'(x)-\widetilde Y_\gamma'(a)
=
\int_a^x \widetilde Y_\gamma''(t)\,dt,
\]
and
\[
\widetilde H_3(a,x)
=
\int_a^x (x-t)\,\widetilde Y_\gamma''(t)\,dt.
\]
Therefore the hypotheses imply
\[
\int_a^x (\mathcal Z(t)-\mathcal Z(a))\,S''(t)\,dt=0,
\]
and
\[
\int_a^x (x-t)(\mathcal Z(t)-\mathcal Z(a))\,S''(t)\,dt=0.
\]

Choose $\varepsilon\in\{\pm1\}$ so that
\[
\varepsilon S''>0
\qquad\text{on }J,
\]
and define the positive measure
\[
d\mu(t):=\varepsilon S''(t)\,dt,
\qquad
\phi(t):=\mathcal Z(t)-\mathcal Z(a).
\]
Then
\[
\int_a^x \phi\,d\mu=0,
\qquad
\int_a^x (x-t)\phi\,d\mu=0.
\]
Hence also
\[
\int_a^x t\,\phi(t)\,d\mu(t)=0.
\]

If $\phi\equiv 0$ on $[a,x]$, then
\[
\mathcal R=\phi'\equiv 0
\qquad\text{on }[a,x],
\]
which is alternative (1).

Assume now that $\phi\not\equiv 0$. Then $\phi$ cannot have fixed sign on
$[a,x]$, because $\mu$ is positive and
\[
\int_a^x \phi\,d\mu=0.
\]
It also cannot have exactly one sign change. Indeed, if $c\in(a,x)$ were the
unique sign-change point, then
\[
(t-c)\phi(t)\ge 0
\qquad\text{on }[a,x],
\]
with strict inequality on a set of positive $\mu$-measure. Therefore
\[
\int_a^x (t-c)\phi(t)\,d\mu(t)>0.
\]
But
\[
\int_a^x (t-c)\phi(t)\,d\mu(t)
=
\int_a^x t\,\phi(t)\,d\mu(t)
-c\int_a^x \phi(t)\,d\mu(t)
=0,
\]
a contradiction.

So $\phi$ has at least two sign changes on $(a,x)$. Since $\phi(a)=0$ and
$\phi$ is continuous, there exist
\[
a<r_1<r_2<x
\]
such that
\[
\phi(r_1)=\phi(r_2)=0,
\]
i.e.
\[
\mathcal Z(r_1)=\mathcal Z(r_2)=\mathcal Z(a).
\]
Applying Rolle's theorem to $\phi=\mathcal Z-\mathcal Z(a)$ on $[a,r_1]$ and on
$[r_1,r_2]$ gives
\[
\mathcal R(\xi_1)=0
\quad\text{for some }\xi_1\in(a,r_1),
\qquad
\mathcal R(\xi_2)=0
\quad\text{for some }\xi_2\in(r_1,r_2).
\]
This proves (2).
\end{proof}

\begin{corollary}[Isolated $\mathcal R$-zeros are shear-sterile]
\label{cor:isolated-R-zeros-are-shear-sterile}
Let $b\in J$ be an isolated zero of $\mathcal R$. Then there exists a
neighborhood $U\subset J$ of $b$ such that no pair
\[
a<x,
\qquad
a,x\in U,
\]
can satisfy
\[
\gamma=\mathcal Z(a),
\qquad
\widetilde Y_\gamma''(a)=0,
\qquad
\widetilde H_3(a,x)=0,
\qquad
\partial_x\widetilde H_3(a,x)=0.
\]
\end{corollary}

\begin{proof}
Choose $U$ so small that $b$ is the only zero of $\mathcal R$ in $U$. If such a
pair $a<x$ existed in $U$, then
Proposition~\ref{prop:sheared-repeated-node-forces-two-R-zeros} would produce
two interior zeros of $\mathcal R$ in $(a,x)\subset U$, a contradiction.
\end{proof}

\begin{corollary}[Diagonal sheared recurrence forces affine-planar collapse]
\label{cor:diagonal-sheared-recurrence-forces-affine-planar-collapse}
Let $J$ be a connected opened nonmixed arc. Suppose there exists a sequence
\[
a_n<x_n,
\qquad
a_n,x_n\in J,
\qquad
a_n,x_n\to b,
\qquad
x_n-a_n\to 0,
\]
such that, with
\[
\gamma_n:=\mathcal Z(a_n),
\qquad
\widetilde Y_{\gamma_n}:=Y-\gamma_n S,
\]
one has
\[
\widetilde Y_{\gamma_n}''(a_n)=0,
\qquad
\widetilde H_{3,n}(a_n,x_n)=0,
\qquad
\partial_x\widetilde H_{3,n}(a_n,x_n)=0,
\]
where
\[
\widetilde H_{3,n}(a,u):=
\widetilde Y_{\gamma_n}(u)-\widetilde Y_{\gamma_n}(a)-\widetilde Y_{\gamma_n}'(a)(u-a).
\]
Then
\[
\mathcal R\equiv 0
\]
on a neighborhood of $b$. Hence on some nontrivial interval containing $b$ one
has
\[
Y=\gamma S+\alpha x+\beta,
\]
so the lifted curve is locally affine-planar there.
\end{corollary}

\begin{proof}
If for some $n$ the first alternative in
Proposition~\ref{prop:sheared-repeated-node-forces-two-R-zeros} holds, then
$\mathcal R\equiv 0$ on $[a_n,x_n]$ and we are done.

Otherwise, for every $n$ the interval $(a_n,x_n)$ contains at least two zeros of
$\mathcal R$. Since
\[
a_n,x_n\to b,
\qquad
x_n-a_n\to 0,
\]
these zeros accumulate at $b$. Because $\mathcal R$ is analytic, this implies
\[
\mathcal R\equiv 0
\]
on a neighborhood of $b$. Therefore $\mathcal Z$ is locally constant, so
\[
Y''=\gamma S''
\]
there, and integrating twice gives
\[
Y=\gamma S+\alpha x+\beta
\]
on a nontrivial interval around $b$.
\end{proof}

\begin{proposition}[Uniform fixed-level nonrecurrence for the sheared $3$-point branch]
\label{prop:uniform-fixed-level-nonrecurrence-sheared-three-point}
Let $J$ be a connected opened nonmixed arc, fix a real scalar $\gamma$, and set
\[
\widetilde Y_\gamma:=Y-\gamma S=\frac{u_5-\gamma\lambda}{c},
\qquad
f_\gamma:=u_5-\gamma\lambda,
\qquad
J_\gamma:=J_{f_\gamma}=J_{u_5}-\gamma J_\lambda.
\]
Then
\[
\widetilde Y_\gamma''=\frac{c^3}{M^3}J_\gamma.
\]

Assume that $b\in J$ is an isolated finite-order odd zero of $J_\gamma$.
After affine normalization of the planar curve
\[
(x,\widetilde Y_\gamma)
\]
at $b$, let
\[
I_-=(\alpha,0)
\]
be the source interval on which
\[
\widetilde Y_\gamma''<0,
\]
and let
\[
I_+=(0,\beta)
\]
be the maximal open interval to the right of $0$ on which
\[
\widetilde Y_\gamma'
\]
is strictly increasing. Set
\[
\mathcal J_\gamma:=\widetilde Y_\gamma'(I_-)\cap \widetilde Y_\gamma'(I_+).
\]
For
\[
m\in\mathcal J_\gamma,
\]
write
\[
a_\gamma(m):=(\widetilde Y_\gamma'|_{I_-})^{-1}(m),
\]
and define
\[
\widetilde H_{3,\gamma}(a,u):=
\widetilde Y_\gamma(u)-\widetilde Y_\gamma(a)-\widetilde Y_\gamma'(a)(u-a).
\]

Then there exists a unique maximal open interval
\[
\mathcal J_{\gamma,\mathrm{br}}=(0,m_{\gamma,*})\subset \mathcal J_\gamma
\]
and a unique real-analytic function
\[
u_\gamma:\mathcal J_{\gamma,\mathrm{br}}\to I_+
\]
such that
\[
\widetilde H_{3,\gamma}(a_\gamma(m),u_\gamma(m))=0
\qquad
(m\in\mathcal J_{\gamma,\mathrm{br}}),
\]
and this branch agrees near $m=0$ with the unique local opposite-side branch
born at the odd zero $b$.

Moreover, along the whole branch one has
\[
\partial_u\widetilde H_{3,\gamma}(a_\gamma(m),u_\gamma(m))
=
\widetilde Y_\gamma'(u_\gamma(m))-m
\neq 0,
\]
so there is no interior common-tangent event, no interior recurrence, and no
interior accumulation. If
\[
m_{\gamma,*}<\sup\mathcal J_\gamma,
\]
then
\[
u_\gamma(m)\longrightarrow \beta
\qquad (m\uparrow m_{\gamma,*}),
\]
so the branch can stop only by boundary exit of the relevant slope-overlap
block.

Equivalently, using
\[
\widetilde H_{3,\gamma}(a,u)=A_a(u)-\gamma B_a(u)
=
B_a(u)\bigl(\Gamma_a(u)-\gamma\bigr),
\]
one has along the branch
\[
\Gamma_{a_\gamma(m)}(u_\gamma(m))=\gamma,
\qquad
\Gamma_{a_\gamma(m)}'(u_\gamma(m))\neq 0.
\]
In particular, for every fixed $\gamma$, the distinguished level $\gamma$ of
the repeated-source scalar $\Gamma_a$ has no interior critical point on the
sheared odd-zero branch.
\end{proposition}

\begin{proof}
By Remark~\ref{rem:below-lifted-wronskian-ratio-reformulation}, for any scalar
germ $f$ one has
\[
\frac{d^2}{dx^2}\!\left(\frac{f}{c}\right)=\frac{c^3}{M^3}J_f.
\]
Applying this with
\[
f=f_\gamma=u_5-\gamma\lambda
\]
gives
\[
\widetilde Y_\gamma''=\frac{c^3}{M^3}J_\gamma.
\]
Hence $b$ is an isolated finite-order odd zero of $J_\gamma$ if and only if it
is an isolated finite-order odd zero of the planar curvature
\[
\widetilde Y_\gamma''.
\]

Now apply
Theorem~\ref{thm:local-classification-lifted-three-point-branch-near-Kv-zero}
and
Theorem~\ref{thm:global-continuation-nonrecurrence-odd-three-point-branch}
with the affine-normalized analytic function
\[
\widetilde Y_\gamma
\]
playing the role of the planar graphing function $S$. The proofs of those
results use only the planar repeated-node tangent-contact equation for the
chosen analytic function, its curvature parity at the base point, and the
maximal monotone-slope block on the opposite side. Therefore they apply
verbatim to
\[
\widetilde H_{3,\gamma}(a,u)
=
\widetilde Y_\gamma(u)-\widetilde Y_\gamma(a)-\widetilde Y_\gamma'(a)(u-a),
\]
and yield the unique local opposite-side branch, its unique continuation on the
maximal slope-overlap block, the nonvanishing of
\[
\partial_u\widetilde H_{3,\gamma},
\]
and the boundary-exit alternative. This proves the first part.

For the reformulation in terms of $\Gamma_a$, note from the definitions of
$A_a$, $B_a$, and $\Gamma_a$ that
\[
\widetilde H_{3,\gamma}(a,u)
=
\bigl(Y(u)-Y(a)-Y'(a)(u-a)\bigr)
-\gamma\bigl(S(u)-S(a)-S'(a)(u-a)\bigr)
=
A_a(u)-\gamma B_a(u).
\]
Since
\[
A_a(u)=\Gamma_a(u)\,B_a(u),
\]
this becomes
\[
\widetilde H_{3,\gamma}(a,u)
=
B_a(u)\bigl(\Gamma_a(u)-\gamma\bigr).
\]
By Proposition~\ref{prop:quadratic-envelope-factorization-nonmixed},
\[
B_a(u)\neq 0
\qquad (u\neq a),
\]
so along the branch
\[
\widetilde H_{3,\gamma}(a_\gamma(m),u_\gamma(m))=0
\iff
\Gamma_{a_\gamma(m)}(u_\gamma(m))=\gamma.
\]

Differentiating
\[
\widetilde H_{3,\gamma}(a,u)=B_a(u)\bigl(\Gamma_a(u)-\gamma\bigr)
\]
with respect to $u$ gives
\[
\partial_u\widetilde H_{3,\gamma}(a,u)
=
B_a'(u)\bigl(\Gamma_a(u)-\gamma\bigr)+B_a(u)\Gamma_a'(u).
\]
On the branch, where
\[
\Gamma_a(u)=\gamma,
\]
this simplifies to
\[
\partial_u\widetilde H_{3,\gamma}(a,u)=B_a(u)\Gamma_a'(u).
\]
Since the first part already gives
\[
\partial_u\widetilde H_{3,\gamma}(a_\gamma(m),u_\gamma(m))\neq 0
\]
and
\[
B_{a_\gamma(m)}(u_\gamma(m))\neq 0,
\]
it follows that
\[
\Gamma_{a_\gamma(m)}'(u_\gamma(m))\neq 0
\]
along the whole branch. This proves the final statement.
\end{proof}

\begin{remark}[No-go for the fixed-level chamber-exit route]
\label{rem:no-go-fixed-level-chamber-exit-route}
One might hope to strengthen
Proposition~\ref{prop:uniform-fixed-level-nonrecurrence-sheared-three-point}
as follows: if a fixed level $\gamma$ is chosen near a strict local extremum of
$\mathcal Z$, so that
\[
J_\gamma=(\mathcal Z-\gamma)J_\lambda
\]
has two nearby simple zeros
\[
r_-<r_+,
\]
then the corresponding sheared opposite-side $3$-point branch should be unable
to reach the chamber boundary $u=r_+$ without first encountering an interior
common-tangent point
\[
\partial_u \widetilde H_{3,\gamma}=0.
\]
This is false already at the level of the local planar/sheared equations.

Indeed, consider the model functions
\[
S_{\mathrm{mod}}(x):=x^2,
\qquad
\mathcal Z_{\mathrm{mod}}(x):=1-x^2,
\qquad
\mathcal R_{\mathrm{mod}}(x):=\mathcal Z_{\mathrm{mod}}'(x)=-2x,
\]
and fix the level
\[
\gamma:=0.
\]
Set
\[
F_{\mathrm{mod}}(x):=x^2-\frac{x^4}{6}.
\]
Then
\[
F_{\mathrm{mod}}''(x)=2(1-x^2)
=
(\mathcal Z_{\mathrm{mod}}(x)-\gamma)\,S_{\mathrm{mod}}''(x),
\]
so the two simple zeros of the sheared curvature are
\[
r_-=-1,
\qquad
r_+=1.
\]

Let
\[
H_{\mathrm{mod}}(a,u):=
F_{\mathrm{mod}}(u)-F_{\mathrm{mod}}(a)-F_{\mathrm{mod}}'(a)(u-a).
\]
A direct computation gives
\[
H_{\mathrm{mod}}(a,u)
=
-\frac{(u-a)^2}{6}\,
\bigl(3a^2+2au+u^2-6\bigr).
\]
Hence the nontrivial opposite-side branch issued from the odd zero $r_-=-1$ is
\[
u(a)=-a-\sqrt{6-2a^2},
\qquad
-\frac53<a<-1.
\]
Along this branch one has
\[
-1<u(a)<1,
\qquad
u(a)\uparrow 1
\quad\text{as}\quad
a\downarrow -\frac53,
\]
so the branch runs inside the chamber and stops by boundary exit at the second
curvature zero.

Moreover,
\[
\partial_u H_{\mathrm{mod}}(a,u)
=
F_{\mathrm{mod}}'(u)-F_{\mathrm{mod}}'(a)
=
-\frac{u-a}{3}\,\bigl(a^2+au+u^2-3\bigr).
\]
Substituting $u=u(a)$ yields
\[
a^2+a\,u(a)+u(a)^2-3
=
-a^2+a\sqrt{6-2a^2}+3<0
\qquad
\left(-\frac53<a<-1\right),
\]
and therefore
\[
\partial_u H_{\mathrm{mod}}(a,u(a))>0
\qquad
\left(-\frac53<a<-1\right).
\]
So there is \emph{no} interior common-tangent point anywhere on the branch
before boundary exit. In fact, if one continues the same algebraic branch past
the chamber boundary, the first common tangent occurs only later at
\[
(a,u)=(-\sqrt3,\sqrt3),
\]
strictly after the chamber has already been crossed.

Thus fixed-level sheared nonrecurrence cannot be sharpened to a chamber-exit
contradiction by planar arguments alone. The remaining obstruction is therefore
genuinely source-coupled: any successful odd-zero exclusion must use the
source-pinned moving shear
\[
f_a=u_5-\mathcal Z(a)\lambda
\]
or some equivalent RH-specific coupling, rather than only a frozen level
$\gamma$ and the planar branch geometry of
\[
\widetilde Y_\gamma=Y-\gamma S.
\]
\end{remark}

\begin{remark}[Source-level form of the shear transfer]
\label{rem:source-level-form-of-shear-transfer}
For fixed $a\in J$, set
\[
f_a:=u_5-\mathcal Z(a)\lambda.
\]
Then
\[
\widetilde Y_{\mathcal Z(a)}=\frac{f_a}{c},
\qquad
J_{f_a}=J_{u_5}-\mathcal Z(a)J_\lambda
=(\mathcal Z-\mathcal Z(a))J_\lambda,
\]
and
\[
D_{f_a}(a,h)=D_{u_5}(a,h)-\mathcal Z(a)\,D_\lambda(a,h).
\]
Thus the sheared repeated-node conditions are exactly a repeated-node
tangent-contact event for the source triple $(c,v_5,f_a)$:
\[
J_{f_a}(a)=0,
\qquad
D_{f_a}(a,h)=0,
\qquad
\partial_h D_{f_a}(a,h)=0.
\]
Proposition~\ref{prop:sheared-repeated-node-forces-two-R-zeros} shows that such
a source-level event forces either $J_{f_a}\equiv 0$ on the interval or at least
two interior zeros of $J_{f_a}$, equivalently at least two interior zeros of
$\mathcal R$ and hence of $\mathcal W_{\mathrm{src}}$.
\end{remark}

\begin{proposition}[Source-determinant form of the odd-zero unrooted defect]
\label{prop:source-determinant-form-odd-zero-unrooted-defect}
Let $J$ be a good nonmixed $v_5$-patch, and let $b\in J$ be an isolated
odd-order zero of $\mathcal R$.  Use the local $x$-coordinate on $J$ centered
at $b$, so that
\[
x(b)=0,
\qquad
\mathcal R(x)=x^m\rho(x),
\qquad
m\ge 1 \text{ odd},
\qquad
\rho(0)\neq 0.
\]
For each source point $a\in J$, set
\[
\Psi_a(h):=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)},
\qquad
f_a:=u_5-\mathcal Z(x(a))\,\lambda.
\]
Then, after shrinking $J$ around $b$ if necessary, the following hold.

\begin{enumerate}
\item The critical locus
\[
\partial_h\Psi_a(h)=0
\qquad\text{equivalently}\qquad
\mathfrak D(a,h)=0
\]
is the graph of a unique real-analytic branch
\[
h=\sigma(a),
\qquad
\sigma(b)=b,
\qquad
\sigma(a)\neq a
\quad (a\neq b).
\]

\item One has the exact identity
\[
D_{f_a}(a,h)
=
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h)
=
D_\lambda(a,h)\,\bigl(\Psi_a(h)-\mathcal Z(x(a))\bigr).
\]

\item Along the critical branch,
\[
\Psi_a(\sigma(a))-\mathcal Z(x(a))
=
-\frac{\rho(0)}{2^{m+1}(m+2)}
\bigl(x(\sigma(a))-x(a)\bigr)^{m+1}
+o\!\left(\bigl|x(\sigma(a))-x(a)\bigr|^{m+1}\right).
\]

\item Consequently,
\[
D_{f_a}(a,\sigma(a))
=
-\frac{c(b)^4J_\lambda(b)\rho(0)}{2^{m+2}(m+2)M(b)^2}
\bigl(x(\sigma(a))-x(a)\bigr)^{m+3}
+o\!\left(\bigl|x(\sigma(a))-x(a)\bigr|^{m+3}\right).
\]
\end{enumerate}

In particular, for all sufficiently small $a\neq b$ one has
\[
D_{f_a}(a,\sigma(a))\neq 0,
\]
and indeed
\[
\operatorname{sgn}D_{f_a}(a,\sigma(a))
=
-\operatorname{sgn}\!\bigl(J_\lambda(b)\rho(0)\bigr).
\]
So near an isolated odd zero of $\mathcal R$, the born repeated-source
critical branch
\[
\mathfrak D(a,h)=0
\]
is uniformly unrooted in source-determinant language:
\[
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h)\neq 0.
\]
\end{proposition}

\begin{proof}
By Remark~\ref{rem:source-determinant-reformulation-Gammaa},
\[
\Psi_a(h)=\Gamma_{x(a)}(x(h)).
\]
Therefore the critical locus
\[
\partial_h\Psi_a(h)=0
\]
is exactly the pullback through the source-to-$x$ coordinate of the local
critical branch
\[
\partial_x\Gamma_{x(a)}(x)=0.
\]
So item (1) is the source-coordinate form of
Proposition~\ref{prop:odd-zero-critical-branch-uniformly-unrooted}.

For item (2), linearity of the determinant in the third column gives
\[
D_{f_a}(a,h)
=
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h).
\]
Dividing by $D_\lambda(a,h)\neq 0$ on the nonmixed patch yields
\[
\frac{D_{f_a}(a,h)}{D_\lambda(a,h)}
=
\Psi_a(h)-\mathcal Z(x(a)).
\]

For item (3), apply
Proposition~\ref{prop:odd-zero-critical-branch-uniformly-unrooted} to the
$x$-coordinate pair
\[
\bigl(x(a),x(\sigma(a))\bigr).
\]
Since
\[
\Psi_a(\sigma(a))=\Gamma_{x(a)}(x(\sigma(a))),
\]
that proposition gives exactly
\[
\Psi_a(\sigma(a))-\mathcal Z(x(a))
=
-\frac{\rho(0)}{2^{m+1}(m+2)}
\bigl(x(\sigma(a))-x(a)\bigr)^{m+1}
+o\!\left(\bigl|x(\sigma(a))-x(a)\bigr|^{m+1}\right).
\]

For item (4), apply the row-reduction identity from
Remark~\ref{rem:source-determinant-reformulation-Gammaa} to
\[
f=f_a,
\qquad
F=\frac{f_a}{c}=Y-\mathcal Z(x(a))S.
\]
This gives
\[
D_{f_a}(a,h)
=
c(a)^2c(h)x'(a)\,
\widetilde H_{3,\mathcal Z(x(a))}\bigl(x(a),x(h)\bigr),
\]
and since
\[
\widetilde H_{3,\mathcal Z(x(a))}(x(a),x(h))
=
B_{x(a)}(x(h))\bigl(\Psi_a(h)-\mathcal Z(x(a))\bigr),
\]
we obtain
\[
D_{f_a}(a,h)
=
c(a)^2c(h)x'(a)\,B_{x(a)}(x(h))
\bigl(\Psi_a(h)-\mathcal Z(x(a))\bigr).
\]

Along the branch $h=\sigma(a)$, write
\[
\delta(a):=x(\sigma(a))-x(a).
\]
Then
\[
B_{x(a)}(x(\sigma(a)))
=
\frac12\,S''(b)\,\delta(a)^2
+
o\!\left(|\delta(a)|^2\right),
\]
while
\[
x'(b)=\frac{M(b)}{c(b)^2},
\qquad
S''(b)=\frac{c(b)^3}{M(b)^3}J_\lambda(b)
\]
by Remark~\ref{rem:below-lifted-wronskian-ratio-reformulation}. Therefore
\[
c(a)^2c(\sigma(a))x'(a)B_{x(a)}(x(\sigma(a)))
=
\frac{c(b)^4J_\lambda(b)}{2M(b)^2}\,\delta(a)^2
+
o\!\left(|\delta(a)|^2\right).
\]
Multiplying by item (3) gives
\[
D_{f_a}(a,\sigma(a))
=
-\frac{c(b)^4J_\lambda(b)\rho(0)}{2^{m+2}(m+2)M(b)^2}\,
\delta(a)^{m+3}
+
o\!\left(|\delta(a)|^{m+3}\right),
\]
which is the claimed asymptotic. Since $m+3$ is even, the leading term has
fixed nonzero sign for all sufficiently small $a\neq b$.
\end{proof}

\begin{remark}[Ceiling of the local shear-transfer route]
\label{rem:ceiling-local-shear-transfer-route}
Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect} shows
that near an isolated odd zero of $\mathcal R$, the genuinely born local
repeated-source branch is the critical branch
\[
\mathfrak D(a,h)=0
\qquad\text{equivalently}\qquad
\partial_h\Psi_a(h)=0,
\]
but its rooted numerator
\[
D_{f_a}(a,h)
=
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h)
\]
has a fixed nonzero leading term there.

So the rooted sheared repeated-node tangent-contact condition is not the local
source avatar of diagonal odd-zero birth.  In particular, no argument using
only the local odd-zero model and the repeated-source critical-branch
equations can prove an implication of the form
\[
\mathfrak D(a,h)=0 \Longrightarrow D_{f_a}(a,h)=0
\]
near odd zeros.

This is a different obstruction from
Remark~\ref{rem:ceiling-of-current-source-level-reduction}: the latter says the
generic source-level Wronskian/$4\times4$ package is formally too free, while
the present remark says that even along the \emph{actual local odd-zero branch},
the rooted numerator fails to vanish with a universal signed defect.  Any
successful shear-transfer theorem must therefore use genuinely additional RH
source coupling beyond the local odd-zero critical-branch analysis.
\end{remark}

\begin{proposition}[Repeated-source first loss is exactly diagonal odd-zero birth]
\label{prop:first-loss-is-diagonal-odd-zero-birth}
Let $J$ be a connected opened nonmixed arc, so
\[
K_v\neq 0
\qquad\text{on }J.
\]
For $a<x$ in $J$, define
\[
A_a(x):=Y(x)-Y(a)-Y'(a)(x-a),
\qquad
B_a(x):=S(x)-S(a)-S'(a)(x-a),
\]
\[
\Gamma_a(x):=\frac{A_a(x)}{B_a(x)},
\qquad
M(a,x):=B_a(x)^2\,\Gamma_a'(x).
\]
Equivalently,
\[
M(a,x)=A_a'(x)B_a(x)-A_a(x)B_a'(x).
\]
Let
\[
\Sigma_M:=\{(a,x)\in J^2:\ a<x,\ M(a,x)=0\}.
\]

Then the following hold.

\begin{enumerate}
\item \emph{No attained separated first loss.}
There is no pair $(a_*,x_*)\in \Sigma_M$ such that
\[
x_*=\inf\{x:\exists\,a<x\text{ with }(a,x)\in \Sigma_M\}.
\]

\item \emph{Any first-loss sequence is diagonal.}
If $(a_n,x_n)\in \Sigma_M$ and
\[
x_n\downarrow x_*:=\inf\{x:\exists\,a<x\text{ with }(a,x)\in \Sigma_M\},
\]
then
\[
x_n-a_n\to 0.
\]

\item \emph{Diagonal accumulation forces a zero of $\mathcal R$.}
If $(a_n,x_n)\in\Sigma_M$ and
\[
a_n,x_n\to b,
\qquad
x_n-a_n\to 0,
\]
then
\[
\mathcal R(b)=0.
\]

\item \emph{Even-order zeros are diagonally sterile.}
If $b$ is an isolated even-order zero of $\mathcal R$, then there exists a
neighborhood $U$ of $b$ such that
\[
\Sigma_M\cap (U\times U)=\varnothing.
\]

\item \emph{Odd-order zeros seed diagonal first loss.}
If $b$ is an isolated odd-order zero of $\mathcal R$, then every
neighborhood $U$ of $b$ contains points
\[
(a,x)\in \Sigma_M
\qquad\text{with}\qquad
a<x,
\qquad
a,x\in U.
\]
\end{enumerate}

Accordingly, repeated-source first loss on a nonmixed arc is not an
independent obstruction mechanism: it occurs if and only if one diagonally
approaches an odd-order zero of $\mathcal R$.
\end{proposition}

\begin{proof}
For (1), suppose $(a_*,x_*)\in\Sigma_M$ were an attained separated first-loss
pair. Then for fixed $a_*$ one has
\[
M(a_*,x)>0
\qquad (a_*<x<x_*),
\]
by the definition of $x_*$. Since $B_{a_*}(x)\neq 0$ on a nonmixed arc,
this implies
\[
\Gamma_{a_*}'(x)>0
\qquad (a_*<x<x_*),
\]
so $\Gamma_{a_*}$ is strictly increasing on $(a_*,x_*)$. Therefore
\[
\Gamma_{a_*}(x_*)>\lim_{x\downarrow a_*}\Gamma_{a_*}(x)=\mathcal Z(a_*).
\]
But Remark~\ref{rem:first-loss-rigidification-nonmixed} shows that every
formally attained first loss satisfies
\[
\Gamma_{a_*}(x_*)=\mathcal Z(a_*),
\]
a contradiction. Thus no attained separated first-loss pair exists.

For (2), suppose $(a_n,x_n)\in\Sigma_M$ and $x_n\downarrow x_*$, but that
$x_n-a_n\not\to 0$. Passing to a subsequence, we may assume
\[
a_n\to a_*<x_*.
\]
By continuity of $M$,
\[
M(a_*,x_*)=0,
\]
so $(a_*,x_*)\in\Sigma_M$, contradicting (1). Hence $x_n-a_n\to 0$.

For (3), since $B_a(x)\neq 0$ on a nonmixed arc, the condition
$(a_n,x_n)\in\Sigma_M$ is equivalent to
\[
\Gamma_{a_n}'(x_n)=0.
\]
In the quadratic-envelope notation from
Proposition~\ref{prop:quadratic-envelope-factorization-nonmixed},
\[
\Gamma_a'(x)
=
\frac{1}{B_a(x)^2}\int_a^x \Omega_{a,x}(r)\,\mathcal R(r)\,dr.
\]
Equivalently, after local nonmixed normalization at $b$, this becomes the
repeated-node profile derivative formula
\[
D_a'(x)=2\int_0^1 s(1-s)\,\mathcal R(a+s(x-a))\,ds.
\]
Letting $a_n,x_n\to b$ with $x_n-a_n\to 0$, continuity yields
\[
0=\lim_{n\to\infty}D_{a_n}'(x_n)
=
2\!\left(\int_0^1 s(1-s)\,ds\right)\mathcal R(b)
=
\frac13\,\mathcal R(b).
\]
Hence $\mathcal R(b)=0$.

For (4), if $b$ is an isolated even-order zero of $\mathcal R$, then
Proposition~\ref{prop:parity-classification-isolated-nonmixed-R-zeros} gives a
neighborhood $U$ of $b$ on which every repeated-node profile $D_a$ is
strictly monotone. Therefore $D_a'(x)\neq 0$ for $a\neq x$ in $U$, hence
$\Gamma_a'(x)\neq 0$ and
\[
\Sigma_M\cap (U\times U)=\varnothing.
\]

For (5), if $b$ is an isolated odd-order zero of $\mathcal R$, then
Proposition~\ref{prop:parity-classification-isolated-nonmixed-R-zeros} gives,
after local normalization, a local repeated-node extremum branch for the
profiles $D_a$. In particular, every neighborhood $U$ of $b$ contains
points $a<x$ with
\[
D_a'(x)=0.
\]
Since $B_a(x)\neq 0$ on the nonmixed arc, this is equivalent to
\[
\Gamma_a'(x)=0,
\]
hence $(a,x)\in\Sigma_M\cap (U\times U)$.

The final statement is the combination of (2), (4), and (5).
\end{proof}

\begin{remark}[Effect on the rigidified first-loss lane]
\label{rem:effect-of-shear-transfer-on-first-loss}
Proposition~\ref{prop:first-loss-is-diagonal-odd-zero-birth} shows that the
repeated-source / first-loss mechanism is not an independent obstruction:
no attained separated first loss can occur, every first-loss sequence is forced
to the diagonal, and diagonal first loss occurs exactly at isolated odd-order
zeros of $\mathcal R$.

At the same time,
Corollary~\ref{cor:sheared-event-impossible-near-isolated-odd-R-zero} shows
that near an isolated odd zero of $\mathcal R$, the rooted sheared
repeated-node tangent-contact event itself is locally absent; and
Corollary~\ref{cor:diagonal-sheared-recurrence-forces-affine-planar-collapse}
shows that any genuine diagonal realization of the sheared event already forces
the affine-planar collapse case
\[
\mathcal R\equiv 0.
\]
So the sheared bottleneck closes in the collapse direction, not by a purely
planar contradiction for $(x,S)$.

Proposition~\ref{prop:uniform-fixed-level-nonrecurrence-sheared-three-point}
shows moreover that for each fixed shear level $\gamma$, the corresponding
sheared opposite-side $3$-point branch is already globally rigid on its maximal
slope-overlap block: it has no interior common-tangent event, no interior
recurrence, and no interior accumulation. Thus the remaining issue is not
sheared $3$-point recurrence at fixed $\gamma$, but the source-coupling /
level-selection step that would force the distinguished level
\[
\gamma=\mathcal Z(b)
\]
arising from a hypothetical odd zero of $\mathcal W_{\mathrm{src}}$ to be hit
by the relevant critical-value configuration of $\Gamma_a$.

Remark~\ref{rem:no-go-fixed-level-chamber-exit-route} shows that this
fixed-level route cannot be pushed further by planar chamber-exit arguments
alone: even with two nearby roots of $\mathcal Z=\gamma$, the sheared
opposite-side branch may run to the second curvature zero by boundary exit
without any interior common-tangent event. Thus the remaining step must be
genuinely source-coupled, involving the source-pinned moving shear
\[
f_a=u_5-\mathcal Z(a)\lambda
\]
or an equivalent RH-specific coupling, rather than only the frozen-level
geometry of
\[
\widetilde Y_\gamma=Y-\gamma S.
\]
\end{remark}

\begin{remark}[The repeated-source lane is now closed]
\label{rem:repeated-source-lane-closed}
Proposition~\ref{prop:first-loss-is-diagonal-odd-zero-birth} shows that the
repeated-source / first-loss mechanism does not define an additional nonmixed
obstruction beyond the odd-zero problem for $\mathcal R$. No attained
separated first loss can occur, every first-loss sequence is forced to the
diagonal, and diagonal first loss occurs exactly at isolated odd-order zeros of
$\mathcal R$. Thus the genuinely remaining nonmixed burden is purely the
global/source-level control of odd zeros of $\mathcal R$, equivalently of the
source-level Wronskian $\mathcal W_{\mathrm{src}}$.
\end{remark}

\begin{proposition}[Single-sign-change source segment cannot realize rigidified first loss]
\label{prop:single-sign-change-cannot-realize-first-loss}
Let $J$ be an opened nonmixed arc, and let $a<x$ in $J$.
After local nonmixed normalization on $[a,x]$, write
\[
R_{a,x}(s):=\mathcal R(a+s(x-a)),
\qquad 0\le s\le 1.
\]
Then
\[
\Gamma_a'(x)
=
2\int_0^1 s(1-s)\,R_{a,x}(s)\,ds,
\]
and
\[
\Gamma_a(x)-\mathcal Z(a)
=
(x-a)\int_0^1 (1-s)^2\,R_{a,x}(s)\,ds.
\]

Assume that $R_{a,x}$ has exactly one sign change on $(0,1)$.
If
\[
\Gamma_a'(x)=0,
\]
then
\[
\operatorname{sgn}\bigl(\Gamma_a(x)-\mathcal Z(a)\bigr)
\]
is the sign of $R_{a,x}$ on the initial side of the sign change.
In particular,
\[
\Gamma_a(x)\neq \mathcal Z(a).
\]

Equivalently, no pair $(a,x)$ for which $\mathcal R$ changes sign exactly once
on $(a,x)$ can satisfy simultaneously
\[
\Gamma_a'(x)=0,
\qquad
\Gamma_a(x)=\mathcal Z(a).
\]
Hence any rigidified first-loss segment must cross at least two sign changes of
$\mathcal R$.
\end{proposition}

\begin{proof}
In the normalized nonmixed chart, $S(t)=t^2$, so
$\Gamma_a = D_a$ with
\[
D_a(t)=\int_0^1 (1-s)\,\widetilde Y''(a+s(t-a))\,ds,
\qquad
D_a(a)=\mathcal Z(a).
\]
Differentiating in $t$ gives
\[
D_a'(t)=\int_0^1 s(1-s)\,\widetilde Y'''(a+s(t-a))\,ds
=2\int_0^1 s(1-s)\,\mathcal R(a+s(t-a))\,ds,
\]
which is the first displayed formula at $t=x$. Integrating
$\widetilde Y''(a+s(t-a))$ by parts in $s$ yields
\[
D_a(t)-D_a(a)
=
(t-a)\int_0^1 (1-s)^2\,\mathcal R(a+s(t-a))\,ds,
\]
which is the second displayed formula at $t=x$.

Let
\[
k_1(s):=s(1-s),\qquad k_0(s):=(1-s)^2,
\]
so that
\[
\frac{k_0(s)}{k_1(s)}=\frac{1-s}{s}
\]
is strictly decreasing on $(0,1)$.

Write $R_{a,x}=\sigma\rho$ with $\rho\ge 0$ and $\sigma$ changing sign exactly
once at some $s_0\in(0,1)$. By hypothesis,
\[
0=\int_0^1 k_1(s)\,\sigma(s)\rho(s)\,ds.
\]
Split
\[
I:=\int_0^1 k_0(s)\,\sigma(s)\rho(s)\,ds
=
\int_0^{s_0}\frac{k_0}{k_1}(s)\,k_1(s)\sigma(s)\rho(s)\,ds
+
\int_{s_0}^1\frac{k_0}{k_1}(s)\,k_1(s)\sigma(s)\rho(s)\,ds.
\]
Let $\epsilon:=\operatorname{sgn}(\sigma|_{(0,s_0)})$. Then
$k_1\sigma\rho\ge 0$ with sign $\epsilon$ on $(0,s_0)$ and sign $-\epsilon$ on
$(s_0,1)$. Because $k_0/k_1$ is strictly decreasing, it is bounded below by
its value at $s_0$ on $(0,s_0)$ and bounded above by its value at $s_0$ on
$(s_0,1)$. Using
\[
\int_0^{s_0}k_1\sigma\rho=-\int_{s_0}^1 k_1\sigma\rho
\]
and strict monotonicity on the support of $\rho$ gives
\[
\epsilon\,I>0.
\]
Hence
\[
\Gamma_a(x)-\mathcal Z(a)=(x-a)\,I\neq 0,
\]
with sign $\epsilon$ (after orienting $x>a$). This proves the claim.
\end{proof}

\begin{corollary}[Source-level two-sign-change obstruction]
\label{cor:source-level-two-sign-change-obstruction}
Let $a<h$ lie on an opened nonmixed arc in source coordinates.
Assume
\[
\Psi_a'(h)=0.
\]
If the source-level Wronskian
\[
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'
\]
changes sign exactly once on the source interval $[a,h]$, then
\[
\Psi_a(h)\neq \mathcal Z(a).
\]
Equivalently, the simultaneous source-level first-loss conditions
\[
\Psi_a'(h)=0,
\qquad
\Psi_a(h)=\mathcal Z(a)
\]
force at least two sign changes of $\mathcal W_{\mathrm{src}}$ on $[a,h]$.
\end{corollary}

\begin{proof}
By Remark~\ref{rem:source-determinant-reformulation-Gammaa},
$\Psi_a(h)=\Gamma_{x(a)}(x(h))$, and on the nonmixed arc
$\mathcal W_{\mathrm{src}}$ and $\mathcal R$ differ only by a nonvanishing
analytic factor
(Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}). So a
single sign change of $\mathcal W_{\mathrm{src}}$ on $[a,h]$ pulls back to a
single sign change of $\mathcal R$ on $[x(a),x(h)]$. Apply
Proposition~\ref{prop:single-sign-change-cannot-realize-first-loss}.
\end{proof}

\begin{proposition}[Transport equations for a repeated-source critical branch]
\label{prop:transport-equations-repeated-source-critical-branch}
Let $J$ be an opened nonmixed arc, and work in a local normalized nonmixed
chart on which
\[
S(t)=t^2,
\qquad
\Gamma_a=D_a.
\]
Let $U\subset J$ be an interval, and let
\[
\tau:U\to J
\]
be a real-analytic function such that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0
\qquad (a\in U).
\]
Set
\[
V(a):=D_a(\tau(a)).
\]
Then:
\begin{enumerate}
\item
\[
V'(a)=\frac{2}{\tau(a)-a}\,\bigl(V(a)-\mathcal Z(a)\bigr).
\]

\item
\[
D_a''(\tau(a))
=
\frac{2}{(\tau(a)-a)^2}\,\bigl(\mathcal Z(\tau(a))-V(a)\bigr).
\]

\item
At any point $a\in U$ where $D_a''(\tau(a))\neq 0$,
\[
\tau'(a)
=
\frac{V(a)-\mathcal Z(a)}
{\mathcal Z(\tau(a))-V(a)}.
\]
\end{enumerate}
\end{proposition}

\begin{proof}
Write
\[
D_a(t)
=
\frac{\widetilde Y(t)-\widetilde Y(a)-\widetilde Y'(a)(t-a)}{(t-a)^2}.
\]
Differentiating in $a$ gives
\[
\partial_a D_a(t)
=
\frac{2}{t-a}\,\bigl(D_a(t)-\mathcal Z(a)\bigr).
\]
Evaluating at $t=\tau(a)$ and using $D_a'(\tau(a))=0$ yields
\[
V'(a)
=
\frac{d}{da}D_a(\tau(a))
=
\partial_a D_a(\tau(a))
=
\frac{2}{\tau(a)-a}\,\bigl(V(a)-\mathcal Z(a)\bigr),
\]
which proves (1).

Now use the rigidification scalar
\[
M(a,t):=B_a(t)^2\,\Gamma_a'(t).
\]
In the normalized chart,
\[
B_a(t)=(t-a)^2,
\qquad
\Gamma_a=D_a,
\qquad
M(a,t)=(t-a)^4\,D_a'(t).
\]
By Remark~\ref{rem:first-loss-rigidification-nonmixed},
\[
\partial_t M(a,t)
=
2(t-a)^2\,\bigl(\mathcal Z(t)-D_a(t)\bigr).
\]
At $t=\tau(a)$ we have $D_a'(\tau(a))=0$, so
\[
\partial_t M(a,\tau(a))
=
(\tau(a)-a)^4\,D_a''(\tau(a)).
\]
Comparing the two formulas gives
\[
(\tau(a)-a)^4\,D_a''(\tau(a))
=
2(\tau(a)-a)^2\,\bigl(\mathcal Z(\tau(a))-V(a)\bigr),
\]
hence (2).

Finally, still by Remark~\ref{rem:first-loss-rigidification-nonmixed},
at points where $M(a,t)=0$ one has
\[
\partial_a M(a,t)
=
2(t-a)^2\,\bigl(\mathcal Z(a)-D_a(t)\bigr),
\]
in the normalized chart. Since
\[
M(a,\tau(a))=0,
\]
differentiating in $a$ gives
\[
0=\frac{d}{da}M(a,\tau(a))
=
\partial_a M(a,\tau(a))
+
\partial_t M(a,\tau(a))\,\tau'(a).
\]
Substituting the formulas above yields
\[
0
=
2(\tau(a)-a)^2\,\bigl(\mathcal Z(a)-V(a)\bigr)
+
2(\tau(a)-a)^2\,\bigl(\mathcal Z(\tau(a))-V(a)\bigr)\tau'(a).
\]
If $D_a''(\tau(a))\neq 0$, then by (2),
\[
\mathcal Z(\tau(a))-V(a)\neq 0,
\]
so solving for $\tau'(a)$ gives (3).
\end{proof}

\begin{corollary}[One-sign-change chamber is no-return for the born critical branch]
\label{cor:one-sign-change-chamber-no-return}
In the setting of
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch},
assume moreover that for every $a\in U$ the segment
\[
[a,\tau(a)]
\]
contains exactly one sign change of $\mathcal R$.

Then for every $a\in U$:
\begin{enumerate}
\item
\[
\operatorname{sgn}\bigl(V(a)-\mathcal Z(a)\bigr)
\]
is the sign of the initial lobe of $\mathcal R$ on $[a,\tau(a)]$;

\item
\[
\operatorname{sgn}\bigl(\mathcal Z(\tau(a))-V(a)\bigr)
\]
is the sign of the terminal lobe of $\mathcal R$ on $[a,\tau(a)]$;

\item
\[
\bigl(V(a)-\mathcal Z(a)\bigr)\bigl(\mathcal Z(\tau(a))-V(a)\bigr)<0;
\]

\item
\[
D_a''(\tau(a))\neq 0,
\qquad
\tau'(a)<0;
\]

\item
\[
V(a)\notin [\,\mathcal Z(a),\mathcal Z(\tau(a))\,].
\]
In particular,
\[
V(a)\neq \mathcal Z(a),
\]
so the branch cannot realize the rigidified first-loss condition anywhere on
$U$.
\end{enumerate}
\end{corollary}

\begin{proof}
The first sign statement is exactly
Proposition~\ref{prop:single-sign-change-cannot-realize-first-loss} applied to
the critical pair $(a,\tau(a))$.

For the second sign statement, write
\[
R_{a,\tau(a)}(s):=\mathcal R(a+s(\tau(a)-a)).
\]
Since
\[
\mathcal Z(\tau(a))-\mathcal Z(a)
=
(\tau(a)-a)\int_0^1 R_{a,\tau(a)}(s)\,ds
\]
and
\[
V(a)-\mathcal Z(a)
=
(\tau(a)-a)\int_0^1 (1-s)^2\,R_{a,\tau(a)}(s)\,ds,
\]
one gets
\[
\mathcal Z(\tau(a))-V(a)
=
(\tau(a)-a)\int_0^1 (2s-s^2)\,R_{a,\tau(a)}(s)\,ds.
\]
At the critical pair,
\[
0=D_a'(\tau(a))
=
2\int_0^1 s(1-s)\,R_{a,\tau(a)}(s)\,ds,
\]
so
\[
\int_0^1 (2s-s^2)\,R_{a,\tau(a)}(s)\,ds
=
\int_0^1 s^2\,R_{a,\tau(a)}(s)\,ds.
\]
Hence
\[
\mathcal Z(\tau(a))-V(a)
=
(\tau(a)-a)\int_0^1 s^2\,R_{a,\tau(a)}(s)\,ds.
\]
Now set
\[
k_1(s):=s(1-s),
\qquad
k_2(s):=s^2.
\]
Then
\[
\frac{k_2(s)}{k_1(s)}=\frac{s}{1-s}
\]
is strictly increasing on $(0,1)$. Repeating the weighted signed-mass argument
from the proof of
Proposition~\ref{prop:single-sign-change-cannot-realize-first-loss} shows that
\[
\operatorname{sgn}\bigl(\mathcal Z(\tau(a))-V(a)\bigr)
\]
is the sign of the terminal lobe of $\mathcal R$.

The two signs are therefore opposite, which proves (3). Then
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(2)
gives
\[
D_a''(\tau(a))\neq 0,
\]
and
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(3)
gives
\[
\tau'(a)<0.
\]
Finally, opposite signs of
\[
V(a)-\mathcal Z(a)
\quad\text{and}\quad
\mathcal Z(\tau(a))-V(a)
\]
mean exactly that $V(a)$ lies strictly outside the endpoint-curvature interval
\[
[\,\mathcal Z(a),\mathcal Z(\tau(a))\,].
\]
\end{proof}

\begin{proposition}[First rooting requires a second odd zero along the born repeated-source branch]
\label{prop:first-rooting-requires-second-odd-zero-repeated-source}
Let $b$ be an isolated odd-order zero of $\mathcal R$ on an opened nonmixed
arc, and let
\[
t=\tau(a)
\]
denote an analytic continuation of the local born repeated-source critical
branch, so that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0.
\]
Assume that $U$ is a connected continuation interval on which, for every
$a\in U$, the segment
\[
[a,\tau(a)]
\]
contains exactly one sign change of $\mathcal R$.

Then for every $a\in U$ one has
\[
D_a(\tau(a))\neq \mathcal Z(a).
\]
Equivalently, on the corresponding source branch
\[
h=\sigma(a),
\qquad
\mathfrak D(a,\sigma(a))=0,
\]
one has
\[
\Psi_a(\sigma(a))\neq \mathcal Z(x(a)),
\]
or in determinant form,
\[
D_{u_5}(a,\sigma(a))-\mathcal Z(x(a))\,D_\lambda(a,\sigma(a))\neq 0.
\]

Consequently, any first parameter at which the analytic continuation of the
born repeated-source branch realizes a genuine repeated-source obstruction
inside the opened nonmixed arc must occur only after the corresponding segment
ceases to be one-sign-change. Internally, away from affine-planar collapse and
without leaving the arc, this can happen only when the segment acquires a
second odd-order zero of $\mathcal R$, equivalently of
\[
\mathcal W_{\mathrm{src}}.
\]
\end{proposition}

\begin{proof}
The first claim is exactly
Corollary~\ref{cor:one-sign-change-chamber-no-return}(5): on any continuation
interval on which each segment
\[
[a,\tau(a)]
\]
contains exactly one sign change of $\mathcal R$, the born critical branch
cannot realize the rigidified first-loss condition
\[
D_a(\tau(a))=\mathcal Z(a).
\]

Via Remark~\ref{rem:source-determinant-reformulation-Gammaa},
\[
\Psi_a(h)=\Gamma_{x(a)}(x(h)),
\]
so the same statement in source coordinates is
\[
\Psi_a(\sigma(a))\neq \mathcal Z(x(a)).
\]
Using
Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}(2),
this is equivalent to
\[
D_{u_5}(a,\sigma(a))-\mathcal Z(x(a))\,D_\lambda(a,\sigma(a))\neq 0.
\]

For the final statement, as long as the continued branch remains inside the
opened nonmixed arc and the corresponding segment remains one-sign-change,
the first part shows that rooting cannot occur. Thus any first rooted point
must be preceded by failure of the one-sign-change condition.

Now even-order zeros of $\mathcal R$ do not change sign, so internally the
sign-change count on the segment can change only when an endpoint of the
segment meets another odd-order zero of $\mathcal R$ (unless the branch exits
the arc or enters the affine-planar collapse case). Finally, on a nonmixed arc
the functions $\mathcal R$ and
\[
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'
\]
differ only by a nonvanishing analytic factor
(Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}), so odd
zeros of the two objects coincide.
\end{proof}

\begin{proposition}[Discriminant entry into the adjacent-two-odd-zero chamber is not a first rooted point]
\label{prop:discriminant-entry-not-first-root}
Let $J$ be an opened nonmixed arc, and work in a local normalized nonmixed
chart on which
\[
S(t)=t^2,
\qquad
\Gamma_a=D_a.
\]
Let
\[
\tau:(a_-,a_0]\to J
\]
be a real-analytic continuation of the born repeated-source critical branch,
so that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0
\qquad (a\in(a_-,a_0]).
\]
Assume:

\begin{enumerate}
\item for every $a\in(a_-,a_0)$, the segment
\[
[a,\tau(a)]
\]
contains exactly one sign change of $\mathcal R$;

\item the target endpoint reaches the next adjacent odd zero at $a=a_0$, i.e.
\[
q:=\tau(a_0)
\]
is an odd-order zero of $\mathcal R$, there are no odd zeros of $\mathcal R$
in $(\tau(a),q)$ for $a<a_0$ close to $a_0$, and the segment
\[
[a_0,q]
\]
still contains exactly one sign change of $\mathcal R$.
\end{enumerate}

Set
\[
V(a):=D_a(\tau(a)).
\]
Define the sheared discriminant and the RH-selected slice by
\[
\mathcal D:=
\left\{
(a,\gamma,h):a<h,\ D_{f_\gamma}(a,h)=0,\ \partial_h D_{f_\gamma}(a,h)=0
\right\},
\]
\[
\mathcal S_{\mathrm{RH}}
:=
\left\{
(a,\gamma,h):\gamma=\mathcal Z(a)
\right\}.
\]

Then
\[
P(a):=(a,V(a),\tau(a))\in\mathcal D
\qquad (a\in(a_-,a_0]),
\]
but at the adjacent-odd-zero entrance point one has
\[
V(a_0)-\mathcal Z(a_0)\neq 0.
\]
More precisely,
\[
V(a_0)-\mathcal Z(a_0)
=
(q-a_0)\int_0^1 (1-s)^2\,
\mathcal R(a_0+s(q-a_0))\,ds,
\]
and this quantity has the sign of the initial lobe of $\mathcal R$ on
$[a_0,q]$.

Consequently,
\[
P(a_0)\notin \mathcal S_{\mathrm{RH}},
\]
and there exists a neighborhood $N$ of $P(a_0)$ in
\[
J\times\mathbf R\times J
\]
such that
\[
N\cap\mathcal D\cap\mathcal S_{\mathrm{RH}}=\varnothing.
\]

In particular, a first rooted point cannot be created at the moment when the
next adjacent odd zero first enters the active segment. If rooting occurs at
all, it must occur only after the branch has moved into a genuine two-sign-change
chamber of positive width.
\end{proposition}

\begin{proof}
By Remark~\ref{rem:source-determinant-reformulation-Gammaa},
\[
\Psi_a(h)=\Gamma_{x(a)}(x(h)),
\]
and on a nonmixed patch
\[
D_{f_\gamma}(a,h)=D_\lambda(a,h)\bigl(\Psi_a(h)-\gamma\bigr).
\]
Since
\[
D_\lambda(a,h)\neq 0
\qquad (a<h),
\]
we have
\[
D_{f_\gamma}(a,h)=0,\ \partial_hD_{f_\gamma}(a,h)=0
\iff
\gamma=\Psi_a(h),\ \partial_h\Psi_a(h)=0.
\]
Along the continued born branch,
\[
\partial_h\Psi_a(\tau(a))=0,
\qquad
\Psi_a(\tau(a))=V(a),
\]
so indeed
\[
P(a)=(a,V(a),\tau(a))\in\mathcal D.
\]

At $a=a_0$, the integral formula for $D_a$ gives
\[
V(a_0)-\mathcal Z(a_0)
=
(q-a_0)\int_0^1 (1-s)^2\,
\mathcal R(a_0+s(q-a_0))\,ds.
\]
Also, since $D_{a_0}'(q)=0$,
\[
0
=
D_{a_0}'(q)
=
2\int_0^1 s(1-s)\,
\mathcal R(a_0+s(q-a_0))\,ds.
\]

Set
\[
R_0(s):=\mathcal R(a_0+s(q-a_0)),
\qquad
k_0(s):=(1-s)^2,
\qquad
k_1(s):=s(1-s).
\]
Then
\[
\frac{k_0(s)}{k_1(s)}=\frac{1-s}{s}
\]
is strictly decreasing on $(0,1)$. Because $R_0$ has exactly one sign change on
$(0,1)$, the same weighted signed-mass argument used in
Proposition~\ref{prop:single-sign-change-cannot-realize-first-loss} implies
that
\[
\int_0^1 k_0(s)R_0(s)\,ds
\]
has the sign of the initial lobe of $R_0$, hence is nonzero. Therefore
\[
V(a_0)-\mathcal Z(a_0)\neq 0.
\]

Thus
\[
P(a_0)=(a_0,V(a_0),q)\in\mathcal D
\quad\text{but}\quad
P(a_0)\notin\mathcal S_{\mathrm{RH}}.
\]
Since both $\mathcal D$ along the continued branch and the function
\[
(a,\gamma,h)\longmapsto \gamma-\mathcal Z(a)
\]
are continuous, there is a neighborhood $N$ of $P(a_0)$ on which
\[
\gamma-\mathcal Z(a)
\]
keeps the sign of
\[
V(a_0)-\mathcal Z(a_0).
\]
Hence
\[
N\cap\mathcal D\cap\mathcal S_{\mathrm{RH}}=\varnothing.
\]

The final statement is immediate: a rooted point is exactly a point of
\[
\mathcal D\cap\mathcal S_{\mathrm{RH}},
\]
so no such point can be born at the adjacent-odd-zero entrance.
\end{proof}

\begin{remark}[What the discriminant analysis now leaves open]
\label{rem:what-discriminant-adjacent-odd-zero-analysis-still-leaves-open}
Proposition~\ref{prop:discriminant-entry-not-first-root} shows that a rooted
point is not created \emph{at the entry} into the adjacent-two-odd-zero chamber.
Corollary~\ref{cor:no-crossing-adjacent-two-odd-zero-under-anchor-sign-preservation}
shows more: on any continuation interval on which the anchor-side value
\[
\mathcal R(a)
\]
keeps a fixed sign, the RH-selected slice
\[
\gamma=\mathcal Z(a)
\]
does not cross the continued discriminant curve at all.

Thus the adjacent-two-odd-zero chamber is not itself the residual obstruction.
What remains open is narrower and genuinely global: whether a rooted crossing
can occur only after the anchor passes through an odd-order zero of
$\mathcal R$ (equivalently of $\mathcal W_{\mathrm{src}}$), or after branch
exit, or after affine-planar collapse. In other words, the remaining discriminant-theoretic bottleneck is a
\emph{delayed post-anchor no-crossing problem}: not an entry-point singularity
problem, and not crossing at the anchor odd zero itself, but a later crossing on
a dangerous post-anchor chamber.
\end{remark}

\begin{proposition}[Rooted-defect transport and stationary first root]
\label{prop:rooted-defect-transport-stationary-first-root}
In the setting of
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch},
define
\[
L(a):=\tau(a)-a,
\qquad
G(a):=V(a)-\mathcal Z(a)=D_a(\tau(a))-\mathcal Z(a).
\]
Then
\[
G'(a)=\frac{2}{L(a)}\,G(a)-\mathcal R(a).
\]
Hence, if $a_*\in U$ satisfies
\[
G(a_*)=0,
\]
then
\[
G'(a_*)=-\mathcal R(a_*).
\]

If in addition
\[
\mathcal Z(\tau(a_*))\neq \mathcal Z(a_*),
\]
then
\[
D_{a_*}''(\tau(a_*))\neq 0,
\qquad
\tau'(a_*)=0,
\qquad
\tau''(a_*)=
-\frac{\mathcal R(a_*)}{\mathcal Z(\tau(a_*))-\mathcal Z(a_*)}.
\]
\end{proposition}

\begin{proof}
Since
\[
G(a)=V(a)-\mathcal Z(a),
\]
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(1)
gives
\[
G'(a)=V'(a)-\mathcal R(a)
=\frac{2}{\tau(a)-a}\,\bigl(V(a)-\mathcal Z(a)\bigr)-\mathcal R(a)
=\frac{2}{L(a)}\,G(a)-\mathcal R(a).
\]
Evaluating at a root $a_*$ of $G$ gives
\[
G'(a_*)=-\mathcal R(a_*).
\]

Now assume also that
\[
\mathcal Z(\tau(a_*))\neq \mathcal Z(a_*).
\]
Since $G(a_*)=0$, this means
\[
\mathcal Z(\tau(a_*))\neq V(a_*).
\]
So Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(2)
yields
\[
D_{a_*}''(\tau(a_*))
=
\frac{2}{(\tau(a_*)-a_*)^2}\,
\bigl(\mathcal Z(\tau(a_*))-V(a_*)\bigr)
\neq 0.
\]
Then Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(3)
applies near $a_*$ and gives
\[
\tau'(a)
=
\frac{G(a)}{\mathcal Z(\tau(a))-V(a)}.
\]
Evaluating at $a_*$ gives
\[
\tau'(a_*)=0.
\]

Differentiate this identity once more. Since $G(a_*)=0$ and
\[
\mathcal Z(\tau(a_*))-V(a_*)=\mathcal Z(\tau(a_*))-\mathcal Z(a_*)\neq 0,
\]
one gets
\[
\tau''(a_*)
=
\frac{G'(a_*)}{\mathcal Z(\tau(a_*))-V(a_*)}
=
-\frac{\mathcal R(a_*)}{\mathcal Z(\tau(a_*))-\mathcal Z(a_*)},
\]
as claimed.
\end{proof}

\begin{proposition}[Nondegenerate rooted point is a fold of the moving-shear equation]
\label{prop:nondegenerate-rooted-point-is-moving-shear-fold}
Work in a local normalized nonmixed chart on which
\[
S(t)=t^2.
\]
Define
\[
\mathscr F(a,t):=A_a(t)-\mathcal Z(a)\,B_a(t)
=(t-a)^2\bigl(D_a(t)-\mathcal Z(a)\bigr).
\]
Let
\[
a_*<t_*
\]
satisfy
\[
\mathscr F(a_*,t_*)=0,
\qquad
\partial_t\mathscr F(a_*,t_*)=0,
\]
and assume
\[
\mathcal R(a_*)\neq 0,
\qquad
\mathcal Z(t_*)\neq \mathcal Z(a_*).
\]
Then
\[
\partial_a\mathscr F(a_*,t_*)
=
-(t_*-a_*)^2\,\mathcal R(a_*),
\]
and
\[
\partial_{tt}\mathscr F(a_*,t_*)
=
2\bigl(\mathcal Z(t_*)-\mathcal Z(a_*)\bigr).
\]
In particular,
\[
\partial_a\mathscr F(a_*,t_*)\neq 0,
\qquad
\partial_{tt}\mathscr F(a_*,t_*)\neq 0.
\]
Hence near $(a_*,t_*)$ the zero set
\[
\mathscr F(a,t)=0
\]
is the graph of a unique real-analytic function
\[
a=\alpha(t)
\]
with
\[
\alpha(t_*)=a_*,
\qquad
\alpha'(t_*)=0,
\qquad
\alpha''(t_*)
=
\frac{2\bigl(\mathcal Z(t_*)-\mathcal Z(a_*)\bigr)}
{(t_*-a_*)^2\,\mathcal R(a_*)}.
\]
Equivalently,
\[
a-a_*
=
\frac{\mathcal Z(t_*)-\mathcal Z(a_*)}
{(t_*-a_*)^2\,\mathcal R(a_*)}(t-t_*)^2
+o\!\left((t-t_*)^2\right).
\]
\end{proposition}

\begin{proof}
Since
\[
\mathscr F(a,t)=(t-a)^2\bigl(D_a(t)-\mathcal Z(a)\bigr),
\]
the conditions
\[
\mathscr F(a_*,t_*)=0,
\qquad
\partial_t\mathscr F(a_*,t_*)=0
\]
imply
\[
D_{a_*}(t_*)=\mathcal Z(a_*),
\qquad
D_{a_*}'(t_*)=0.
\]
So $(a_*,t_*)$ is a rooted critical point.

Differentiate $\mathscr F$ with respect to $a$:
\[
\partial_a\mathscr F(a,t)
=
-2(t-a)\bigl(D_a(t)-\mathcal Z(a)\bigr)
+(t-a)^2\bigl(\partial_aD_a(t)-\mathcal R(a)\bigr).
\]
At the rooted point,
\[
D_{a_*}(t_*)-\mathcal Z(a_*)=0,
\]
and by
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch},
\[
\partial_aD_a(t)=\frac{2}{t-a}\bigl(D_a(t)-\mathcal Z(a)\bigr),
\]
so
\[
\partial_a\mathscr F(a_*,t_*)
=
-(t_*-a_*)^2\,\mathcal R(a_*).
\]

Next,
\[
\partial_t\mathscr F(a,t)
=
2(t-a)\bigl(D_a(t)-\mathcal Z(a)\bigr)
+(t-a)^2D_a'(t),
\]
hence
\[
\partial_{tt}\mathscr F(a,t)
=
2\bigl(D_a(t)-\mathcal Z(a)\bigr)
+4(t-a)D_a'(t)
+(t-a)^2D_a''(t).
\]
At the rooted critical point this becomes
\[
\partial_{tt}\mathscr F(a_*,t_*)
=
(t_*-a_*)^2D_{a_*}''(t_*).
\]
Applying
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(2)
and using
\[
D_{a_*}(t_*)=\mathcal Z(a_*),
\]
one gets
\[
\partial_{tt}\mathscr F(a_*,t_*)
=
2\bigl(\mathcal Z(t_*)-\mathcal Z(a_*)\bigr).
\]

By the two nonvanishing assumptions,
\[
\partial_a\mathscr F(a_*,t_*)\neq 0.
\]
So the implicit function theorem gives a unique real-analytic graph
\[
a=\alpha(t)
\]
for the zero set of $\mathscr F$ near $(a_*,t_*)$. Since
\[
\partial_t\mathscr F(a_*,t_*)=0,
\]
one has
\[
\alpha'(t_*)=0.
\]
Differentiating
\[
\mathscr F(\alpha(t),t)=0
\]
twice at $t=t_*$ gives
\[
\partial_a\mathscr F(a_*,t_*)\,\alpha''(t_*)
+
\partial_{tt}\mathscr F(a_*,t_*)=0,
\]
hence
\[
\alpha''(t_*)
=
-\frac{\partial_{tt}\mathscr F(a_*,t_*)}
{\partial_a\mathscr F(a_*,t_*)}
=
\frac{2\bigl(\mathcal Z(t_*)-\mathcal Z(a_*)\bigr)}
{(t_*-a_*)^2\,\mathcal R(a_*)}.
\]
The Taylor expansion of $\alpha$ then yields the stated quadratic form.
\end{proof}

\begin{remark}[First rooted point as a post-birth fold problem]
\label{rem:first-rooted-point-post-birth-fold-problem}
Let $b$ be an isolated odd-order zero of $\mathcal R$, and let
\[
t=\tau(a)
\]
be an analytic continuation of the born repeated-source critical branch. By
Proposition~\ref{prop:first-rooting-requires-second-odd-zero-repeated-source},
any first rooted point along this continuation can occur only after the segment
has acquired a second odd-order zero of $\mathcal R$.

At such a rooted point, if
\[
\mathcal R(a_*)\neq 0,
\qquad
\mathcal Z(\tau(a_*))\neq \mathcal Z(a_*),
\]
then
Proposition~\ref{prop:rooted-defect-transport-stationary-first-root} shows that
the rooted defect
\[
G(a)=D_a(\tau(a))-\mathcal Z(a)
\qquad
\text{equivalently}\qquad
G(a)=\Psi_a(\sigma(a))-\mathcal Z(a)
\]
crosses transversely and that the target map is stationary there:
\[
\tau'(a_*)=0.
\]
Moreover,
Proposition~\ref{prop:nondegenerate-rooted-point-is-moving-shear-fold} shows
that the moving-shear equation
\[
A_a(x)-\mathcal Z(a)\,B_a(x)=0
\qquad\text{equivalently}\qquad
D_{f_a}(a,h)=0,
\quad
f_a=u_5-\mathcal Z(a)\lambda,
\]
has a local fold at the first rooted point.

Thus the unresolved adjacent-odd-zero issue is not another local odd-zero birth
problem. It is a \emph{post-birth first-fold exclusion problem} for the
source-pinned moving shear $f_a=u_5-\mathcal Z(a)\lambda$. The current fixed-level
nonrecurrence results control frozen-$\gamma$ branches on their maximal
slope-overlap blocks, and
Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}
controls the diagonal birth chamber near the seeding odd zero, but neither yet
excludes this first post-birth fold.
\end{remark}

\begin{proposition}[At most one odd zero implies no genuine repeated-source obstruction]
\label{prop:at-most-one-odd-zero-no-genuine-repeated-source-obstruction}
Let $J$ be an opened nonmixed arc. Assume that $\mathcal R$ has at most one
odd-order zero on $J$. Then there is no pair $a<x$ in $J$ such that
\[
\Gamma_a'(x)=0,
\qquad
\Gamma_a(x)=\mathcal Z(a).
\]
Equivalently, there is no source-level pair $a<h$ on the corresponding source
arc such that
\[
\Psi_a'(h)=0,
\qquad
\Psi_a(h)=\mathcal Z(a).
\]
\end{proposition}

\begin{proof}
On a nonmixed arc, $\mathcal W_{\mathrm{src}}$ differs from $\mathcal R$ only
by a nonvanishing analytic factor
(Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}), so odd
zeros and sign changes of the two objects coincide.

If $\mathcal R$ has at most one odd-order zero on $J$, then every segment
contained in $J$ contains at most one sign change of $\mathcal R$ (equivalently
of $\mathcal W_{\mathrm{src}}$), since even-order zeros do not change sign.
Hence Corollary~\ref{cor:source-level-two-sign-change-obstruction} excludes any
simultaneous source-level solution of
\[
\Psi_a'(h)=0,
\qquad
\Psi_a(h)=\mathcal Z(a).
\]
Via Remark~\ref{rem:source-determinant-reformulation-Gammaa}, this is
equivalent to the planar formulation
\[
\Gamma_a'(x)=0,
\qquad
\Gamma_a(x)=\mathcal Z(a).
\]
\end{proof}

\begin{remark}[Minimal unresolved configuration on this route]
\label{rem:minimal-unresolved-configuration-repeated-source}
Proposition~\ref{prop:at-most-one-odd-zero-no-genuine-repeated-source-obstruction}
rules out every opened nonmixed arc carrying at most one odd zero of
$\mathcal R$, and
Corollary~\ref{cor:no-crossing-adjacent-two-odd-zero-under-anchor-sign-preservation}
rules out rooted crossing on the standard adjacent-two-odd-zero chamber as long
as the anchor-side value $\mathcal R(a)$ keeps a fixed sign.

The new odd-anchor passage theorem
(Proposition~\ref{prop:odd-anchor-passage-no-reset})
shows that no rooted crossing can occur at the anchor odd zero itself or
immediately after it is crossed, while
Corollary~\ref{cor:first-post-anchor-chamber-dangerous}
shows that the subsequent post-anchor chambers alternate dangerous and safe,
beginning with a dangerous first post-anchor chamber.

Remark~\ref{rem:no-go-local-scalar-first-dangerous-chamber} shows that the
first dangerous chamber is already formally compatible with the local scalar
rooted equations and fold data. Accordingly, the first genuinely unresolved
configuration is no longer the adjacent-two-odd-zero chamber itself, nor the
anchor odd zero passage, but a \emph{delayed} crossing on a dangerous
post-anchor chamber. Thus the sharpened source-coupling target is a delayed
no-crossing / profile-realizability exclusion theorem for the moving shear
\[
f_a=u_5-\mathcal Z(a)\lambda
\]
on genuine opened nonmixed arcs.
\end{remark}

\begin{remark}[No-go for a pure level-set / barrier theorem for $\mathcal Z$]
\label{rem:no-go-pure-level-set-barrier-for-Z}
A natural next guess would be that the remaining adjacent-odd-zero case could be
excluded by a theorem depending only on the level geometry of
\[
\mathcal Z,\qquad \mathcal R=\mathcal Z',
\]
together with the first-root transport identities
\[
G(a_*):=V(a_*)-\mathcal Z(a_*)=0,
\qquad
G'(a_*)=-\mathcal R(a_*),
\qquad
\tau'(a_*)=0,
\]
and the fact that a rooted point forces two interior recrossings of the level
\[
\mathcal Z(r)=\mathcal Z(a_*).
\]
At the current level of abstraction this is false: the level-set geometry of
$\mathcal Z$ alone is still too free.

Indeed, already in the normalized planar determinant model one can realize all
of the above with exactly two simple odd zeros of $\mathcal R$ and with a
nondegenerate rooted critical pair. Take
\[
S(t)=t^2,
\qquad
\mathcal R(t)=5t^3+5t^2-7t+1,
\qquad
\mathcal Z(t)=\int_0^t \mathcal R(u)\,du
=
t-\frac72 t^2+\frac53 t^3+\frac54 t^4.
\]
Then $\mathcal R$ has exactly two simple zeros in $(0,1)$, numerically
\[
t\approx 0.165726,
\qquad
t\approx 0.660736,
\]
so on $[0,1]$ the sign pattern is $+,-,+$ with exactly two odd sign changes.
Now choose an analytic function $\widetilde Y$ such that
\[
\frac12\,\widetilde Y''=\mathcal Z.
\]
For the normalized determinant function $D_a(x)$ associated to
$(x,\widetilde Y)$, the rooted critical conditions at $(a,x)=(0,1)$ become
\[
D_0'(1)=2\int_0^1 s(1-s)\,\mathcal R(s)\,ds,
\qquad
D_0(1)-\mathcal Z(0)=\int_0^1 (1-s)^2\,\mathcal R(s)\,ds.
\]
For this $\mathcal R$, both moments vanish:
\[
\int_0^1 s(1-s)\,\mathcal R(s)\,ds=0,
\qquad
\int_0^1 (1-s)^2\,\mathcal R(s)\,ds=0.
\]
Hence
\[
D_0'(1)=0,
\qquad
D_0(1)=\mathcal Z(0),
\]
so $(0,1)$ is an exact rooted repeated-source critical pair.

Moreover,
\[
D_0''(1)=2\int_0^1 s^2\,\mathcal R(s)\,ds=\frac56>0,
\]
so the critical branch is nondegenerate and the implicit-function theorem gives
a real-analytic continuation
\[
x=\tau(a),
\qquad
\tau(0)=1,
\qquad
\tau'(0)=0.
\]
Also, with
\[
V(a):=D_a(\tau(a)),
\qquad
G(a):=V(a)-\mathcal Z(a),
\]
one has at the rooted point
\[
G(0)=0,
\qquad
G'(0)=-\mathcal R(0)=-1.
\]

Finally, the level equation
\[
\mathcal Z(t)=\mathcal Z(0)=0
\]
has two interior solutions,
\[
t\approx 0.368001,
\qquad
t\approx 0.851550,
\]
so the rooted point comes with exactly the two interior recrossings of the
moving level demanded by the source-pinned shear picture.

Thus a theorem using only the scalar level-set topology of $\mathcal Z$
together with the first-root identities above cannot suffice to exclude the
remaining adjacent-odd-zero configuration. Any successful next step must use
additional structure: either the provenance of $(a,\tau(a))$ as the
\emph{continued born branch}, or a genuinely source-coupled constraint such as
the moving shear
\[
f_a=u_5-\mathcal Z(a)\lambda,
\]
rather than only the abstract level geometry of $\mathcal Z$.
\end{remark}

\begin{remark}[No-go for branch provenance alone]
\label{rem:no-go-branch-provenance-alone}
One might try to strengthen
Remark~\ref{rem:no-go-pure-level-set-barrier-for-Z}
by using not just the scalar level geometry of $\mathcal Z$, but also the
\emph{provenance} of the rooted point: namely, that $(a,\tau(a))$ lies on the
continued branch born at an earlier odd zero of $\mathcal R$.
At the planar normalized $D_a$-level, this is still not enough. There are
explicit analytic models in which the born branch from one odd zero continues to
a genuine rooted point before leaving the interval bounded by the adjacent odd
zeros.

A concrete example is obtained by taking
\[
S(t)=t^2,
\qquad
\mathcal R(t):=t(t-1)(t^2-4t-2)
=
t^4-5t^3+2t^2+2t,
\]
and
\[
\mathcal Z(t):=\int_0^t \mathcal R(u)\,du
=
\frac15 t^5-\frac54 t^4+\frac23 t^3+t^2.
\]
Then the odd zeros of $\mathcal R$ are
\[
2-\sqrt6,\qquad 0,\qquad 1,\qquad 2+\sqrt6,
\]
so $0$ is an odd zero and its adjacent odd zero on the left is $2-\sqrt6$.

Now choose an analytic function $\widetilde Y$ such that
\[
\frac12\,\widetilde Y''=\mathcal Z,
\]
and let $D_a(x)$ denote the normalized determinant/divided-difference function
for the planar graph $(x,\widetilde Y)$. Near the odd zero $0$ there is the
usual born critical branch
\[
x=\tau(a),
\qquad
a<0<x,
\qquad
D_a'(\tau(a))=0,
\]
with
\[
\tau(a)=-a+O(a^2),
\]
and the local odd-zero analysis gives
\[
G(a):=D_a(\tau(a))-\mathcal Z(a)<0
\]
for $a<0$ sufficiently close to $0$.

However, along this same connected born branch one finds
\[
G(-0.5801)<0,
\qquad
G(-0.5901)>0,
\]
so by continuity there exists
\[
a_*\in(-0.5901,-0.5801)
\]
such that
\[
G(a_*)=0.
\]
Thus the \emph{continued born branch} reaches a rooted point
\[
D_{a_*}'(\tau(a_*))=0,
\qquad
D_{a_*}(\tau(a_*))=\mathcal Z(a_*).
\]
Numerically,
\[
a_*\approx -0.5805673462,
\qquad
\tau(a_*)\approx 0.3888336023,
\]
and
\[
D_{a_*}''(\tau(a_*))>0,
\]
so this rooted point is nondegenerate; in particular,
\[
\tau'(a_*)=0
\]
as predicted by the transport system.

Moreover, the segment
\[
[a_*,\tau(a_*)]
\]
contains exactly the born odd zero $0$ together with the adjacent odd zero
$2-\sqrt6$, and no others. So even the strengthened statement
\[
\text{``continued born-branch provenance plus adjacent-odd-zero geometry
already excludes rooting''}
\]
is false in the planar normalized model.

Therefore the remaining exclusion cannot depend only on abstract branch
continuation data for
\[
D_a'(\tau(a))=0
\]
together with the scalar geometry of $\mathcal Z$. Any successful next step
must use genuinely source-coupled structure, such as the actual quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)},
\]
the moving shear
\[
f_a=u_5-\mathcal Z(a)\lambda,
\]
or some equivalent RH-specific relation invisible in the planar $D_a$ model.
\end{remark}

\begin{remark}[No-go for disconjugacy/ECT alone]
\label{rem:no-go-disconjugacy-alone}
A further natural idea is to recast the moving-shear family through the
third-order operator
\[
L[y]:=\frac{W(c,v_5,\lambda,y)}{J_\lambda},
\]
and try to exclude rooted moving-shear events by proving that $L$ is
disconjugate, Chebyshev, or sign-regular on opened nonmixed arcs.
At the present level of abstraction this is still not enough.

Indeed, already in the normalized source model
\[
c(t)=1,\qquad v_5(t)=t,\qquad \lambda(t)=t^2,
\]
one has
\[
J_f=W(c,v_5,f)=f'',
\qquad
J_\lambda=2,
\qquad
L[y]=\frac{W(c,v_5,\lambda,y)}{J_\lambda}=\frac12\,y'''.
\]
So the homogeneous equation $L[y]=0$ has basis
\[
1,\ t,\ t^2,
\]
hence is maximally disconjugate / ECT on every interval. Nevertheless, the
planar normalized counterexample from
Remark~\ref{rem:no-go-branch-provenance-alone}
fits exactly into this framework: for a suitable analytic $u_5$ and the
source-pinned family
\[
f_a:=u_5-\mathcal Z(a)\lambda,
\]
one has
\[
L[f_a]=L[u_5],
\qquad
J_{f_a}(a)=0,
\]
and along the continued born branch there is still a rooted point
\[
D_{f_a}(a,h)=0,
\qquad
\partial_h D_{f_a}(a,h)=0.
\]

Thus disconjugacy, ECT, or sign-regularity of the operator $L$ by itself
cannot exclude the remaining rooted moving-shear configuration. Any successful
next step must use additional source-coupled structure beyond the abstract
third-order ODE viewpoint, such as special positivity or monotonicity for the
distinguished quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)}
\]
or for the particular slice
\[
f_a=u_5-\mathcal Z(a)\lambda.
\]
\end{remark}

\begin{remark}[Ceiling of the present scalar/discriminant analysis]
\label{rem:ceiling-present-scalar-discriminant-analysis}
The preceding results sharply delimit what can and cannot be obtained from the
current planar/scalar reformulation.

On the positive-kernel side, one-sign-change chambers are sterile for genuine
repeated-source first loss:
the born critical branch is simple, has strictly negative slope, and cannot
satisfy
\[
D_a(\tau(a))=\mathcal Z(a)
\]
before the active segment acquires another odd zero of $\mathcal R$
(Proposition~\ref{prop:first-rooting-requires-second-odd-zero-repeated-source}).
On the discriminant side, the adjacent-odd-zero entrance itself cannot create
the first rooted point
(Proposition~\ref{prop:discriminant-entry-not-first-root}).

However, Remarks~\ref{rem:no-go-pure-level-set-barrier-for-Z}
and~\ref{rem:no-go-branch-provenance-alone} show that the present planar/scalar
package still has a genuine ceiling. In the planar normalized $D_a$ model,
neither the scalar level-set topology of $\mathcal Z$ nor the abstract
provenance of a point on the continued born branch suffices by itself to exclude
a later rooted crossing.

The new anchor-sign and odd-anchor-passage arguments remove a substantial part
of that freedom. On any continuation interval on which the anchor-side value
\[
\mathcal R(a)
\]
keeps a fixed sign, the RH-selected slice
\[
\gamma=\mathcal Z(a)
\]
cannot cross the continued discriminant curve. When the anchor itself passes
through an odd-order zero of $\mathcal R$, the integrating-factor defect keeps
its incoming sign across that odd anchor zero, so a rooted crossing cannot occur
there or immediately after it. The post-anchor chambers then alternate
dangerous and safe, beginning with a dangerous first post-anchor chamber.

However, Remark~\ref{rem:no-go-local-scalar-first-dangerous-chamber} shows that
already in that first dangerous chamber the local normalized rooted equations
and local fold/transversality data are formally realizable in the planar scalar
model. Accordingly, the present scalar/discriminant package still has a genuine
ceiling: beyond the fixed-sign analysis, the remaining problem is not arbitrary
global crossing, but a genuinely source-coupled \emph{delayed no-crossing /
profile-realizability problem} on dangerous post-anchor chambers.

So any further progress on the nonmixed repeated-source branch must use
structure invisible in the planar normalized model, namely a genuinely
source-coupled constraint linking
\[
\Psi_a(h),\qquad
\mathfrak D(a,h),\qquad
\mathcal Z(a),\qquad
f_a=u_5-\mathcal Z(a)\lambda
\]
along the actual RH branch, rather than only the abstract scalar geometry of
$D_a$ and $\mathcal Z$.
\end{remark}

\begin{proposition}[Discriminant reduction for the moving-shear family]
\label{prop:discriminant-reduction-moving-shear}
Let $J$ be a good nonmixed $v_5$-patch. For $\gamma\in\mathbf R$, set
\[
f_\gamma:=u_5-\gamma\lambda.
\]
Define the sheared discriminant set
\[
\mathcal D:=
\left\{
(a,\gamma,h)\in J\times\mathbf R\times J:
a<h,\
D_{f_\gamma}(a,h)=0,\
\partial_h D_{f_\gamma}(a,h)=0
\right\}.
\]

Then on the region $a<h$ one has the exact equivalence
\[
(a,\gamma,h)\in\mathcal D
\iff
\gamma=\Psi_a(h),
\qquad
\mathfrak D(a,h)=0.
\]
Equivalently,
\[
\mathcal D
=
\left\{
(a,\Psi_a(h),h):\ a<h,\ \mathfrak D(a,h)=0
\right\}.
\]

In particular, on a nonmixed patch the sheared discriminant is not an
independent two-dimensional catastrophe surface in $(a,\gamma,h)$-space:
it is the graph of the repeated-source critical locus
\[
\mathfrak D(a,h)=0
\]
in the extra $\gamma$-direction.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}(2),
for every $(a,h)$ with $a<h$ one has
\[
D_{f_\gamma}(a,h)
=
D_\lambda(a,h)\bigl(\Psi_a(h)-\gamma\bigr).
\]
Differentiating in $h$ gives
\[
\partial_h D_{f_\gamma}(a,h)
=
\partial_h D_\lambda(a,h)\bigl(\Psi_a(h)-\gamma\bigr)
+
D_\lambda(a,h)\,\partial_h\Psi_a(h).
\]

On a good nonmixed patch,
\[
D_\lambda(a,h)\neq 0
\qquad (a<h).
\]
Therefore
\[
D_{f_\gamma}(a,h)=0
\iff
\gamma=\Psi_a(h).
\]
At such a point the first term in the formula for $\partial_h D_{f_\gamma}$
vanishes, so
\[
\partial_h D_{f_\gamma}(a,h)=0
\iff
D_\lambda(a,h)\,\partial_h\Psi_a(h)=0
\iff
\partial_h\Psi_a(h)=0.
\]
Finally, by
Remark~\ref{rem:source-determinant-reformulation-Gammaa},
\[
\partial_h\Psi_a(h)
=
\frac{W_h(c,v_5)(a)\,\mathfrak D(a,h)}{D_\lambda(a,h)^2},
\]
and the prefactor is nonvanishing on the nonmixed patch. Hence
\[
\partial_h\Psi_a(h)=0
\iff
\mathfrak D(a,h)=0.
\]
Combining the two equivalences proves the result.
\end{proof}

\begin{proposition}[Generic rooted discriminant point is a transverse crossing]
\label{prop:generic-rooted-discriminant-point-transverse-crossing}
In the setting of
Proposition~\ref{prop:discriminant-reduction-moving-shear},
define the RH-selected slice
\[
\mathcal S_{\mathrm{RH}}
:=
\left\{
(a,\gamma,h)\in J\times\mathbf R\times J:
\gamma=\mathcal Z(x(a))
\right\}.
\]

Let
\[
(a_*,\gamma_*,h_*)\in \mathcal D\cap \mathcal S_{\mathrm{RH}}
\]
and assume
\[
\partial_h^2 D_{f_{\gamma_*}}(a_*,h_*)\neq 0,
\qquad
\mathcal R(x(a_*))\neq 0.
\]
Then there is a neighborhood of $(a_*,\gamma_*,h_*)$ in which
$\mathcal D$ is a unique real-analytic curve
\[
a\longmapsto \bigl(a,\gamma(a),h(a)\bigr),
\]
with
\[
\gamma(a)=\Psi_a(h(a)).
\]

Moreover one has
\[
\gamma'(a_*)=0,
\qquad
h'(a_*)=0,
\]
and
\[
\frac{d}{da}\Bigl(\gamma(a)-\mathcal Z(x(a))\Bigr)\Big|_{a=a_*}
=
-\mathcal R(x(a_*))\,x'(a_*)\neq 0.
\]
Hence the discriminant curve $\mathcal D$ meets the RH-selected slice
$\mathcal S_{\mathrm{RH}}$ transversely at $(a_*,\gamma_*,h_*)$.

In fact the $\gamma$-projection of the discriminant curve has a nondegenerate
local extremum there:
\[
\gamma''(a_*)
=
-\frac{2\,x'(a_*)^2}{x(h_*)-x(a_*)}\,\mathcal R(x(a_*)).
\]
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:discriminant-reduction-moving-shear},
the discriminant is cut out by
\[
\partial_h\Psi_a(h)=0,
\qquad
\gamma=\Psi_a(h).
\]
At the given point,
\[
\partial_h^2 D_{f_{\gamma_*}}(a_*,h_*)\neq 0.
\]
Since
\[
D_{f_\gamma}(a,h)=D_\lambda(a,h)\bigl(\Psi_a(h)-\gamma\bigr),
\]
differentiating twice in $h$ and evaluating at a discriminant point gives
\[
\partial_h^2 D_{f_{\gamma_*}}(a_*,h_*)
=
D_\lambda(a_*,h_*)\,\partial_h^2\Psi_{a_*}(h_*).
\]
Because $D_\lambda(a_*,h_*)\neq 0$, this implies
\[
\partial_h^2\Psi_{a_*}(h_*)\neq 0.
\]
So by the implicit function theorem there is a unique real-analytic function
\[
h=h(a)
\]
with
\[
h(a_*)=h_*,
\qquad
\partial_h\Psi_a(h(a))=0.
\]
Setting
\[
\gamma(a):=\Psi_a(h(a))
\]
gives the asserted local parametrization of $\mathcal D$.

Now pass to the local normalized nonmixed $x$-coordinate and write
\[
\alpha:=x(a),
\qquad
\tau(\alpha):=x(h(a)),
\qquad
V(\alpha):=D_\alpha(\tau(\alpha)).
\]
By Remark~\ref{rem:source-determinant-reformulation-Gammaa},
\[
\gamma(a)=\Psi_a(h(a))=V(\alpha).
\]
Since $(a_*,\gamma_*,h_*)\in\mathcal S_{\mathrm{RH}}$, one has
\[
V(\alpha_*)=\mathcal Z(\alpha_*),
\qquad
\alpha_*:=x(a_*).
\]

By Proposition~\ref{prop:transport-equations-repeated-source-critical-branch},
at a rooted noncollapse point one has
\[
V'(\alpha_*)=0,
\qquad
\tau'(\alpha_*)=0.
\]
Therefore
\[
\gamma'(a_*)
=
V'(\alpha_*)\,x'(a_*)
=
0,
\]
and
\[
x'(h_*)\,h'(a_*)
=
\tau'(\alpha_*)\,x'(a_*)
=
0,
\]
hence
\[
h'(a_*)=0.
\]

For the transverse-crossing derivative, differentiate
\[
\gamma(a)-\mathcal Z(x(a))
=
V(\alpha)-\mathcal Z(\alpha)
\]
to get
\[
\frac{d}{da}\Bigl(\gamma(a)-\mathcal Z(x(a))\Bigr)
=
x'(a)\bigl(V'(\alpha)-\mathcal R(\alpha)\bigr).
\]
At $a=a_*$, since $V'(\alpha_*)=0$, this becomes
\[
\frac{d}{da}\Bigl(\gamma(a)-\mathcal Z(x(a))\Bigr)\Big|_{a=a_*}
=
-\mathcal R(\alpha_*)\,x'(a_*),
\]
which is nonzero by hypothesis. This proves transversality.

Finally, differentiate
\[
V'(\alpha)=\frac{2}{\tau(\alpha)-\alpha}\bigl(V(\alpha)-\mathcal Z(\alpha)\bigr)
\]
from
Proposition~\ref{prop:transport-equations-repeated-source-critical-branch}(1).
At the rooted point,
\[
V(\alpha_*)-\mathcal Z(\alpha_*)=0,
\qquad
\tau'(\alpha_*)=0,
\]
so
\[
V''(\alpha_*)
=
\frac{2}{\tau(\alpha_*)-\alpha_*}\bigl(V'(\alpha_*)-\mathcal R(\alpha_*)\bigr)
=
-\frac{2}{\tau(\alpha_*)-\alpha_*}\,\mathcal R(\alpha_*).
\]
Hence
\[
\gamma''(a_*)
=
V''(\alpha_*)\,x'(a_*)^2
=
-\frac{2\,x'(a_*)^2}{x(h_*)-x(a_*)}\,\mathcal R(x(a_*)),
\]
as claimed.
\end{proof}

\begin{remark}[What the discriminant/catastrophe route actually reduces to]
\label{rem:what-discriminant-catastrophe-route-actually-reduces-to}
The discriminant reformulation sharpens the geometry, but it also shows the
limit of purely local catastrophe arguments on this route.

Indeed, by
Proposition~\ref{prop:discriminant-reduction-moving-shear},
the sheared discriminant on a nonmixed patch is already one-dimensional:
it is the graph of the repeated-source critical locus
\[
\mathfrak D(a,h)=0
\]
in the $\gamma$-direction. And by
Proposition~\ref{prop:generic-rooted-discriminant-point-transverse-crossing},
a generic rooted point is not a tangential meeting of sheets, nor a local
fold/cusp obstruction for the RH-selected slice
\[
\gamma=\mathcal Z(x(a)).
\]
It is a \emph{transverse crossing} of a smooth discriminant curve by that
moving slice, with oriented crossing sign controlled by
\[
-\mathcal R(x(a_*)).
\]

Accordingly, the discriminant/catastrophe route does not reduce the adjacent
odd-zero problem to a local singularity classification in
$(a,\gamma,h)$-space. The remaining issue is global: to exclude the existence
of such a transverse crossing along the continued born branch before the
segment exits the arc, collapses affine-planarly, or acquires the next odd
zero of $\mathcal W_{\mathrm{src}}$.
\end{remark}

\begin{proposition}[Anchor-sign preservation excludes first rooting]
\label{prop:anchor-sign-preservation-excludes-first-rooting}
Let $J$ be an opened nonmixed arc, and work in a local normalized nonmixed
chart on which
\[
S(t)=t^2,
\qquad
\Gamma_a=D_a.
\]
Let
\[
I=(a_1,a_0]\subset J
\]
and let
\[
\tau:I\to J
\]
be a real-analytic continuation of the repeated-source critical branch such that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0
\qquad (a\in I).
\]
Set
\[
V(a):=D_a(\tau(a)),
\qquad
G(a):=V(a)-\mathcal Z(a).
\]

Assume that there exists $\epsilon\in\{\pm1\}$ such that
\[
\epsilon\,\mathcal R(a)>0
\qquad\text{for every }a\in I,
\]
and
\[
\epsilon\,G(a_0)>0.
\]
Then
\[
\epsilon\,G(a)>0
\qquad\text{for every }a\in I.
\]
In particular,
\[
G(a)\neq 0
\qquad (a\in I),
\]
so the branch cannot realize the rigidified first-loss condition anywhere on
$I$.
\end{proposition}

\begin{proof}
Assume for contradiction that $G$ vanishes somewhere on $I$. Since $G$ is
continuous, the set
\[
Z:=\{a\in I:G(a)=0\}
\]
is closed in $I$ and nonempty. Let
\[
a_*:=\sup Z.
\]
Then $a_*<a_0$, and by the choice of $a_*$ one has
\[
\epsilon\,G(a)>0
\qquad\text{for all }a\in(a_*,a_0].
\]
Hence the one-sided derivative at $a_*$ satisfies
\[
\epsilon\,G'(a_*)\ge 0.
\]

On the other hand, by
Proposition~\ref{prop:rooted-defect-transport-stationary-first-root},
\[
G'(a)=\frac{2}{\tau(a)-a}\,G(a)-\mathcal R(a).
\]
Evaluating at the root $a=a_*$ gives
\[
G'(a_*)=-\mathcal R(a_*).
\]
Since $\epsilon\,\mathcal R(a_*)>0$ by hypothesis, this yields
\[
\epsilon\,G'(a_*)
=
-\epsilon\,\mathcal R(a_*)
<0,
\]
contradicting
\[
\epsilon\,G'(a_*)\ge 0.
\]
Therefore $G$ has no zero on $I$. Since
\[
\epsilon\,G(a_0)>0,
\]
the sign of $G$ on all of $I$ is $\epsilon$.
\end{proof}

\begin{corollary}[No crossing on the adjacent-two-odd-zero chamber under anchor-sign preservation]
\label{cor:no-crossing-adjacent-two-odd-zero-under-anchor-sign-preservation}
Let $b<q$ be adjacent odd-order zeros of $\mathcal R$ on an opened nonmixed
arc $J$. Work in a local normalized nonmixed chart, and let
\[
I=(a_1,a_0]\subset J,
\qquad
\tau:I\to J
\]
be a real-analytic continuation of the born repeated-source critical branch such
that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0
\qquad (a\in I),
\]
with
\[
\tau(a_0)=q.
\]
Assume that for every $a\in I$ with $a<a_0$, the segment
\[
[a,\tau(a)]
\]
contains exactly two sign changes of $\mathcal R$, occurring at the odd zeros
$b$ and $q$, and that
\[
\mathcal R(a)
\]
has fixed sign on $I$.

Then
\[
\operatorname{sgn}\bigl(G(a)\bigr)=\operatorname{sgn}\bigl(\mathcal R(a)\bigr)
\qquad (a\in I),
\]
hence
\[
G(a)\neq 0
\qquad (a\in I).
\]
Equivalently, the RH-selected slice
\[
\gamma=\mathcal Z(a)
\]
does not cross the continued discriminant curve
\[
(a,\gamma,h)=\bigl(a,V(a),\tau(a)\bigr)
\]
anywhere on $I$.
\end{corollary}

\begin{proof}
At the entry point $a=a_0$, one has
\[
\tau(a_0)=q,
\]
and the segment
\[
[a_0,q]
\]
contains exactly one sign change of $\mathcal R$, namely at $b$. Therefore
Proposition~\ref{prop:single-sign-change-cannot-realize-first-loss} applied to
the critical pair $(a_0,q)$ gives
\[
\operatorname{sgn}\bigl(G(a_0)\bigr)
=
\operatorname{sgn}\bigl(\mathcal R(a_0)\bigr).
\]
Now apply
Proposition~\ref{prop:anchor-sign-preservation-excludes-first-rooting}
with
\[
\epsilon:=\operatorname{sgn}\bigl(\mathcal R|_I\bigr).
\]
\end{proof}

\begin{remark}[What this really removes from the previous caveat]
\label{rem:what-anchor-sign-preservation-removes}
The preceding corollary shows that the geometric hypothesis
``the anchor stays on the original birth-side outer lobe'' was stronger than
necessary. The proof uses only the intrinsic condition that the anchor-side
value
\[
\mathcal R(a)
\]
keep a fixed sign along the continuation interval.

Accordingly, the remaining unresolved possibility on this route is narrower, but
it is not yet exhausted. A rooted point can occur only after the anchor itself
passes through an odd-order zero of $\mathcal R$, or after branch exit, or after
affine-planar collapse. Moreover,
Proposition~\ref{prop:odd-anchor-passage-no-reset} shows that no rooted crossing
can occur at that anchor odd zero itself or immediately after passage, and
Corollary~\ref{cor:first-post-anchor-chamber-dangerous} shows that the
subsequent post-anchor chambers alternate dangerous and safe. Thus the true residual obstruction is no longer the raw adjacent-two-odd-zero
chamber itself. But by the universality threshold for the current route-2
package, even the delayed post-anchor scenario cannot be excluded inside that
package alone.
\end{remark}

\begin{proposition}[Odd-anchor passage has no sign reset]
\label{prop:odd-anchor-passage-no-reset}
Let $J$ be an opened nonmixed arc, and work in a local normalized nonmixed
chart on which
\[
S(t)=t^2,
\qquad
\Gamma_a=D_a.
\]
Let
\[
q\in J
\]
be an isolated odd-order zero of $\mathcal R$, and let
\[
\tau:(q-\delta,q+\delta)\to J
\]
be a real-analytic continuation of the repeated-source critical branch such that
\[
\tau(a)>a,
\qquad
D_a'(\tau(a))=0
\qquad (a\in(q-\delta,q+\delta)).
\]
Set
\[
G(a):=D_a(\tau(a))-\mathcal Z(a),
\qquad
L(a):=\tau(a)-a,
\]
and define
\[
\mathcal A'(a):=\frac{2}{L(a)},
\qquad
\mathscr G(a):=e^{-\mathcal A(a)}G(a).
\]
Assume that there exists $\epsilon\in\{\pm1\}$ such that
\[
\epsilon\,\mathcal R(a)>0,
\qquad
\epsilon\,G(a)>0
\qquad\text{for every }a\in(q,q+\delta).
\]
Then
\[
\epsilon\,G(q)>0.
\]
In particular, $G(q)\neq 0$. Hence, after possibly shrinking $\delta$,
\[
\epsilon\,G(a)>0
\qquad\text{for every }a\in(q-\delta,q+\delta).
\]
Since $q$ is an odd-order zero of $\mathcal R$, the sign of $\mathcal R$ flips
across $q$; therefore on the outgoing side
\[
\operatorname{sgn}G(a)=-\operatorname{sgn}\mathcal R(a)
\qquad (a\in(q-\delta,q)).
\]
So a rooted crossing cannot occur at the anchor odd zero itself, nor
immediately after passage across it.
\end{proposition}

\begin{proof}
By
Proposition~\ref{prop:rooted-defect-transport-stationary-first-root},
\[
G'(a)=\frac{2}{L(a)}\,G(a)-\mathcal R(a),
\]
hence
\[
\mathscr G'(a)=-e^{-\mathcal A(a)}\mathcal R(a).
\]
Assume for contradiction that $G(q)=0$. Then $\mathscr G(q)=0$, and for
$a\in(q,q+\delta)$,
\[
\mathscr G(a)
=
\mathscr G(q)+\int_q^a \mathscr G'(s)\,ds
=
-\int_q^a e^{-\mathcal A(s)}\mathcal R(s)\,ds.
\]
Since $e^{-\mathcal A(s)}>0$ and $\epsilon\,\mathcal R(s)>0$ on $(q,q+\delta)$,
this gives
\[
\epsilon\,\mathscr G(a)<0
\qquad (a\in(q,q+\delta)),
\]
hence
\[
\epsilon\,G(a)<0
\qquad (a\in(q,q+\delta)),
\]
contradicting the hypothesis. Therefore $G(q)\neq 0$. Since
\[
\epsilon\,G(a)>0
\qquad (a\in(q,q+\delta)),
\]
continuity yields
\[
\epsilon\,G(q)\ge 0,
\]
and the nonvanishing just proved forces
\[
\epsilon\,G(q)>0.
\]
A second continuity argument then gives
\[
\epsilon\,G(a)>0
\qquad (a\in(q-\delta,q+\delta))
\]
after shrinking $\delta$ if necessary. Finally, because $q$ is an odd-order zero
of $\mathcal R$, its sign flips across $q$, so on $(q-\delta,q)$ one has
\[
\operatorname{sgn}G(a)=-\operatorname{sgn}\mathcal R(a).
\]
In particular $G$ cannot vanish there.
\end{proof}

\begin{proposition}[Weighted-defect recursion on post-anchor chambers]
\label{prop:weighted-defect-recursion-post-anchor-chambers}
Assume the setting of
Proposition~\ref{prop:odd-anchor-passage-no-reset}. Let
\[
q_1>q_2>\cdots>q_N
\]
be successive odd-order zeros of $\mathcal R$ crossed by the anchor along the
continued branch after the adjacent-two-odd-zero chamber, and set
\[
I_j:=(q_{j+1},q_j)
\qquad (1\le j\le N-1).
\]
Assume that the continued branch exists real-analytically on
\[
\bigcup_{j=1}^{N-1} I_j.
\]
For each $j$, let
\[
\epsilon_j:=\operatorname{sgn}(\mathcal R|_{I_j})\in\{\pm1\},
\qquad
m_j(a):=\int_a^{q_j} e^{-\mathcal A(s)}|\mathcal R(s)|\,ds
\qquad (a\in I_j),
\]
and
\[
M_j:=m_j(q_{j+1})>0.
\]
Then on each $I_j$,
\[
\mathscr G(a)=\mathscr G(q_j)+\epsilon_j\,m_j(a).
\]
Consequently:
\begin{enumerate}
\item if
\[
\operatorname{sgn}\mathscr G(q_j)=\epsilon_j,
\]
then $\mathscr G$ has no zero on $I_j$;

\item if
\[
\operatorname{sgn}\mathscr G(q_j)=-\epsilon_j,
\]
then $\mathscr G$ has a zero on $I_j$ if and only if
\[
M_j>|\mathscr G(q_j)|,
\]
and in that case the zero is unique;

\item if $\mathscr G$ has no zero on $I_j$, then
\[
\operatorname{sgn}\mathscr G(q_{j+1})
=
\operatorname{sgn}\mathscr G(q_j).
\]
\end{enumerate}
Since $\epsilon_{j+1}=-\epsilon_j$, the chamber type
\[
\operatorname{sgn}\mathscr G(q_j)\ \text{ versus }\ \epsilon_j
\]
alternates from one post-anchor chamber to the next as long as no rooted
crossing has yet occurred.
\end{proposition}

\begin{proof}
On $I_j$ one has
\[
\mathscr G'(a)=-e^{-\mathcal A(a)}\mathcal R(a)
=-\epsilon_j e^{-\mathcal A(a)}|\mathcal R(a)|.
\]
Hence for $a\in I_j$,
\[
\mathscr G(a)
=
\mathscr G(q_j)+\int_{q_j}^a \mathscr G'(s)\,ds
=
\mathscr G(q_j)+\epsilon_j\int_a^{q_j}e^{-\mathcal A(s)}|\mathcal R(s)|\,ds,
\]
which is the stated formula.

Now $m_j(a)$ is strictly increasing as $a$ decreases from $q_j$ to $q_{j+1}$,
with
\[
m_j(q_j)=0,
\qquad
m_j(q_{j+1})=M_j.
\]
So if
\[
\operatorname{sgn}\mathscr G(q_j)=\epsilon_j,
\]
then
\[
\mathscr G(a)=\epsilon_j\bigl(|\mathscr G(q_j)|+m_j(a)\bigr)
\]
has fixed sign on $I_j$ and no zero. If instead
\[
\operatorname{sgn}\mathscr G(q_j)=-\epsilon_j,
\]
then
\[
\mathscr G(a)=\epsilon_j\bigl(-|\mathscr G(q_j)|+m_j(a)\bigr),
\]
so a zero occurs precisely when $m_j(a)=|\mathscr G(q_j)|$, which happens if
and only if
\[
M_j>|\mathscr G(q_j)|.
\]
Because $m_j$ is strictly monotone, that zero is unique.

Finally, if no zero occurs on $I_j$, then $\mathscr G$ keeps one sign
throughout the interval, so in particular
\[
\operatorname{sgn}\mathscr G(q_{j+1})
=
\operatorname{sgn}\mathscr G(q_j).
\]
Since the $\epsilon_j$ alternate at successive odd zeros, the relative chamber
type alternates as claimed.
\end{proof}

\begin{corollary}[The first post-anchor chamber is dangerous]
\label{cor:first-post-anchor-chamber-dangerous}
Let $q_1$ be the first odd-order zero of $\mathcal R$ crossed by the anchor
after the adjacent-two-odd-zero chamber, and let
\[
I_1:=(q_2,q_1)
\]
be the first post-anchor chamber. Assume the continued born branch extends
real-analytically across $q_1$ and on $I_1$. Then:
\begin{enumerate}
\item no rooted crossing occurs at $q_1$ or immediately after crossing it;

\item on $I_1$ one has
\[
\operatorname{sgn}\mathscr G(q_1)=-\epsilon_1,
\]
so $I_1$ is the first \emph{dangerous} post-anchor chamber;

\item as long as no rooted crossing has yet occurred, the post-anchor chambers
alternate dangerous/safe/dangerous/safe\ldots\ .
\end{enumerate}
In particular, the first chamber in which a rooted crossing is even eligible
after the anchor-sign-preservation interval is the first post-anchor chamber.
Without an additional diagonal-capture theorem, however, this eligibility does
not by itself determine the odd-zero count on the active segment.
\end{corollary}

\begin{proof}
The adjacent-two-odd-zero chamber is root-free by
Corollary~\ref{cor:no-crossing-adjacent-two-odd-zero-under-anchor-sign-preservation}.
At its left endpoint $q_1$, the anchor crosses an odd-order zero of
$\mathcal R$. Proposition~\ref{prop:odd-anchor-passage-no-reset} shows that
$\mathscr G$ keeps its incoming sign across $q_1$, while $\mathcal R$ changes
sign there. Thus on the outgoing chamber $I_1$ the signs are opposite:
\[
\operatorname{sgn}\mathscr G(q_1)=-\epsilon_1.
\]
The no-root statement at and immediately after $q_1$ is also exactly
Proposition~\ref{prop:odd-anchor-passage-no-reset}. The alternation of chamber
types then follows from
Proposition~\ref{prop:weighted-defect-recursion-post-anchor-chambers}(3).
\end{proof}

\begin{remark}[No-go for purely local scalar exclusion on the first dangerous post-anchor chamber]
\label{rem:no-go-local-scalar-first-dangerous-chamber}
At a rooted critical point, after normalizing the active interval to
\[
x=a+sL,
\qquad
0\le s\le 1,
\qquad
L=\tau(a)-a,
\]
the profile
\[
R_a(s):=\mathcal R(a+sL)
\]
satisfies the two local scalar moment identities
\[
\int_0^1 (1-s)^2\,R_a(s)\,ds=0,
\qquad
\int_0^1 s(1-s)\,R_a(s)\,ds=0.
\]

Once nonlocal-target landing is admitted, the first dangerous post-anchor
chamber need not correspond to a fixed odd-zero count or to a rigid four-lobe
pattern on the active segment. Even in the simplest three-lobe sign pattern
\[
+,-,+
\]
(or its global negative), the local scalar rooted equations are already
formally realizable.

Indeed, for any $A>0$, define
\[
R_A(s):=
\begin{cases}
A, & 0<s<\frac13,\\[4pt]
-\frac72 A, & \frac13<s<\frac23,\\[4pt]
\frac{11}{2}A, & \frac23<s<1.
\end{cases}
\]
A direct calculation gives
\[
\int_0^1 (1-s)^2\,R_A(s)\,ds=0,
\qquad
\int_0^1 s(1-s)\,R_A(s)\,ds=0,
\]
and also
\[
\int_0^1 R_A(s)\,ds
=
\int_0^1 s\,R_A(s)\,ds
=
\int_0^1 s^2\,R_A(s)\,ds
=
A.
\]
So the local rooted-point equations and the nondegenerate fold data are already
formally compatible with a three-lobe profile.

Thus no argument using only the local normalized rooted profile, the two
vanishing scalar moments, and the local transversality/fold signs can exclude
rooting on the first dangerous post-anchor chamber. Any successful next step
must use genuinely source-coupled structure invisible in the planar normalized
$D_a$ model.
\end{remark}

\begin{remark}[What route 2 now reduces to]
\label{rem:route-two-reduces-to-global-no-crossing}
The discriminant analysis first showed that a rooted point is not born
\emph{at the entry} into the adjacent-two-odd-zero chamber. The stronger
anchor-sign argument showed more: on any continuation interval on which the
anchor-side value
\[
\mathcal R(a)
\]
keeps a fixed sign, the RH-selected slice
\[
\gamma=\mathcal Z(a)
\]
cannot cross the discriminant curve at all.

The odd-anchor analysis sharpened this further: when the anchor itself passes
through an odd-order zero of $\mathcal R$, the integrating-factor defect
\[
\mathscr G(a)=e^{-\mathcal A(a)}\bigl(D_a(\tau(a))-\mathcal Z(a)\bigr)
\]
keeps its incoming sign across that odd anchor zero, so a rooted crossing cannot
occur there or immediately after passage. The subsequent post-anchor chambers
then alternate dangerous and safe, beginning with a dangerous first post-anchor
chamber
(Corollary~\ref{cor:first-post-anchor-chamber-dangerous}).

However, two no-go facts are now clear. First,
Remark~\ref{rem:no-go-local-scalar-first-dangerous-chamber} shows that already
on that first dangerous post-anchor chamber, the local normalized rooted
equations and fold data are formally realizable in the planar scalar model.
Second, the current route-2 source package itself is still universal under the
normalized lift
\[
c=1,\qquad v_5=t,\qquad \lambda=t^2,\qquad u_5''=2\mathcal Z
\]
(Proposition~\ref{prop:universality-threshold-current-route-two-package} below),
so even the source-level objects
\[
\Psi_a,\qquad \mathfrak D,\qquad \mathcal W_{\mathrm{src}},\qquad D_{f_a}
\]
do not yet distinguish the RH branch from an arbitrary analytic normalized
model.

So route 2 no longer reduces merely to a delayed no-crossing /
profile-realizability problem \emph{within the current package}. It reduces to
finding the first genuinely \emph{non-universal} source-coupled input, i.e. an
ingredient not already captured by the normalized planar $D_a$ model.
\end{remark}

\begin{proposition}[Universality threshold for the current route-2 package]
\label{prop:universality-threshold-current-route-two-package}
Let $I\subset\mathbf R$ be an interval, let
\[
\mathcal Z:I\to\mathbf R
\]
be real-analytic, and set
\[
\mathcal R:=\mathcal Z'.
\]
Define analytic source functions on $I$ by
\[
c(t):=1,\qquad v_5(t):=t,\qquad \lambda(t):=t^2,
\]
and choose $u_5$ so that
\[
u_5''(t)=2\mathcal Z(t).
\]
Then:
\begin{enumerate}
\item
\[
x=\frac{v_5}{c}=t,
\qquad
S=\frac{\lambda}{c}=t^2,
\qquad
Y=\frac{u_5}{c}=u_5;
\]

\item for every analytic $f$,
\[
J_f=W(c,v_5,f)=W(1,t,f)=f'',
\]
hence
\[
J_\lambda=2,
\qquad
J_{u_5}=2\mathcal Z,
\qquad
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'
=
4\mathcal R;
\]

\item the repeated-source ratio is exactly the normalized planar one:
\[
\Psi_a(h)=\Gamma_a(h)=D_a(h);
\]

\item the critical determinant equation is exactly the normalized planar
critical-point equation:
\[
\mathfrak D(a,h)=0
\iff
\partial_h \Psi_a(h)=0
\iff
\partial_h D_a(h)=0;
\]

\item for the source-pinned moving shear
\[
f_a:=u_5-\mathcal Z(a)\lambda,
\]
one has
\[
J_{f_a}=2(\mathcal Z-\mathcal Z(a)),
\]
and
\[
D_{f_a}(a,h)=D_\lambda(a,h)\bigl(\Psi_a(h)-\mathcal Z(a)\bigr).
\]
\end{enumerate}
Thus every analytic normalized planar model $(\mathcal Z,\mathcal R,D_a)$
lifts to a genuine analytic source model for the entire current route-2 package.
\end{proposition}

\begin{proof}
The identities
\[
x=\frac{v_5}{c}=t,\qquad
S=\frac{\lambda}{c}=t^2,\qquad
Y=\frac{u_5}{c}=u_5
\]
are immediate. Also,
\[
J_f=W(c,v_5,f)=W(1,t,f)=f'',
\]
so
\[
J_\lambda=2,\qquad J_{u_5}=2\mathcal Z.
\]
Hence
\[
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda'
=
2(2\mathcal Z')-2\mathcal Z\cdot 0
=
4\mathcal R.
\]

Because the source coordinate and the normalized planar coordinate coincide,
\[
x(t)=t,
\]
the source repeated-source quotient is exactly the planar normalized quadratic
envelope:
\[
\Psi_a(h)=\Gamma_a(h)=D_a(h).
\]
Therefore the source critical determinant equation is exactly the planar
critical-point equation
\[
\mathfrak D(a,h)=0
\iff
\partial_h D_a(h)=0.
\]

Finally,
\[
f_a=u_5-\mathcal Z(a)\lambda
\]
satisfies
\[
J_{f_a}=u_5''-2\mathcal Z(a)=2(\mathcal Z-\mathcal Z(a)),
\]
and
Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}(2)
gives
\[
D_{f_a}(a,h)=D_\lambda(a,h)\bigl(\Psi_a(h)-\mathcal Z(a)\bigr).
\]
So all route-2 source objects reduce exactly to the normalized planar ones.
\end{proof}

\begin{corollary}[The current route-2 package is universal under normalization]
\label{cor:current-route-two-package-universal-under-normalization}
Any configuration formally realizable by an analytic normalized planar model
\[
(\mathcal Z,\mathcal R,D_a)
\]
is also formally realizable by a genuine analytic source model for the current
route-2 package
\[
(c,v_5,\lambda,u_5),\qquad
\Psi_a,\qquad
\mathfrak D,\qquad
\mathcal W_{\mathrm{src}},\qquad
D_{f_a}.
\]
Accordingly, no contradiction theorem phrased only in terms of the current
route-2 package can distinguish the RH branch from an arbitrary analytic
normalized planar model.
\end{corollary}

\begin{proof}
This is immediate from
Proposition~\ref{prop:universality-threshold-current-route-two-package}.
\end{proof}

\begin{remark}[Explicit source-level countermodel to the current route-2 package]
\label{rem:explicit-source-level-countermodel-current-route-two}
Take
\[
\mathcal R(t):=t(t-1)(t^2-4t-2)
\]
and
\[
\mathcal Z(t):=\int_0^t \mathcal R(u)\,du
=
\frac15 t^5-\frac54 t^4+\frac23 t^3+t^2,
\]
and realize this normalized planar model by
\[
c(t)=1,\qquad v_5(t)=t,\qquad \lambda(t)=t^2,\qquad u_5''(t)=2\mathcal Z(t).
\]
Let
\[
q:=2-\sqrt6.
\]
In this genuine analytic source model, the unique born repeated-source critical
branch from the odd zero $0$ continues analytically down to $a=q$, lands
there with a nonlocal target
\[
\tau(q)\approx 0.3540339256\neq q,
\]
satisfies the anchor-sign safe relation on $(q,0)$, crosses the odd anchor
zero $q$ with no sign reset, and then undergoes a delayed rooted crossing at
\[
a_*\approx -0.5805673462,
\qquad
\tau(a_*)\approx 0.3888336023.
\]
Thus diagonal capture fails, and the whole delayed-crossing scenario is
realized inside a genuine analytic source model for the current route-2
package.
\end{remark}

\begin{remark}[The next live target must be non-universal]
\label{rem:next-live-target-must-be-non-universal}
By
Corollary~\ref{cor:current-route-two-package-universal-under-normalization},
the present route-2 package is exhausted: any further progress must use a
genuinely non-universal source-coupled input, i.e. an ingredient not already
absorbed by the normalized planar model $(\mathcal Z,\mathcal R,D_a)$.

Within the current draft, the first canonical candidates for such genuinely
non-universal input lie above the present route-2 package, for example at the
quotient-septic / mixed level through invariants such as
\[
[A_7^{\mathfrak f}]
\qquad\text{or}\qquad
\Delta_7.
\]
So any viable continuation of route 2 must hybridize the repeated-source moving
shear
\[
f_a=u_5-\mathcal Z(a)\lambda
\]
with higher non-universal data of that kind.
\end{remark}

\begin{remark}[What remains on the nonmixed $4$-point side]
\label{rem:what-remains-nonmixed-after-R-zero-bridge}
The preceding results now give a full local derivative-side picture of the
nonmixed exact-contact geometry. Exact nonmixed tangent-plane contacts force
zeros of $\mathcal R$
(Proposition~\ref{prop:exact-nonmixed-tangent-plane-contacts-force-R-zero});
intervals on which $\mathcal R$ has fixed nonzero sign are exactly-contact
sterile
(Corollary~\ref{cor:sign-definite-R-excludes-exact-nonmixed-contacts});
recurrent exact contacts force affine-planar collapse
(Corollary~\ref{cor:recurrent-exact-nonmixed-contacts-force-affine-planarity});
and isolated zeros of $\mathcal R$ are classified by parity
(Proposition~\ref{prop:parity-classification-isolated-nonmixed-R-zeros}).

At source level, the same structure is encoded by the gauge-invariant Wronskian
\[
\mathcal W_{\mathrm{src}}
=
J_\lambda J_{u_5}'-J_{u_5}J_\lambda',
\]
which differs from $\mathcal R$ only by a nonvanishing analytic factor on a
nonmixed arc
(Proposition~\ref{prop:source-level-Wronskian-nonmixed-four-point}). Thus exact
nonmixed contacts force zeros of $\mathcal W_{\mathrm{src}}$, one-sign
$\mathcal W_{\mathrm{src}}$-intervals are sterile, and recurrent contacts
force $\mathcal W_{\mathrm{src}}\equiv 0$
(Corollary~\ref{cor:source-level-Wronskian-consequences-nonmixed}).

Moreover, Proposition~\ref{prop:source-level-Wronskian-lifts-to-4x4} lifts
$\mathcal W_{\mathrm{src}}$ to the $4\times4$ Wronskian
\[
W(c,v_5,\lambda,u_5),
\]
while Proposition~\ref{prop:source-level-Wronskian-package-not-enough} shows
that, at the current source-level ratio/Wronskian/$4\times4$-determinant
level, the odd-zero pattern of $\mathcal W_{\mathrm{src}}$ and $\mathcal R$
is still formally unconstrained. Thus generic determinant algebra alone is no
longer enough to close the nonmixed branch.

The repeated-source / first-loss lane is now also closed. For each fixed
source point $a$, repeated-source exact contacts factor through the
quadratic-envelope scalar
\[
\Gamma_a(x)=
\frac{Y(x)-Y(a)-Y'(a)(x-a)}
{S(x)-S(a)-S'(a)(x-a)},
\]
equivalently through the source-determinant quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)},
\]
with derivative controlled by the osculatory determinant
$\mathfrak D(a,h)$. The formal first-loss event rigidifies to a sheared
repeated-node tangent-contact configuration
(Remark~\ref{rem:first-loss-rigidification-nonmixed}), but this is no longer a
live independent bottleneck. Proposition~\ref{prop:first-loss-is-diagonal-odd-zero-birth}
shows that no attained separated first loss can occur, every first-loss
sequence is forced to the diagonal, and diagonal first loss occurs exactly at
isolated odd-order zeros of $\mathcal R$. Moreover,
Proposition~\ref{prop:uniform-fixed-level-nonrecurrence-sheared-three-point}
shows that for each fixed shear level $\gamma$, the corresponding sheared
opposite-side $3$-point branch is globally rigid on its maximal slope-overlap
block; and
Proposition~\ref{prop:odd-zero-critical-branch-uniformly-unrooted} together
with Corollary~\ref{cor:sheared-event-impossible-near-isolated-odd-R-zero}
show that near an isolated odd zero of $\mathcal R$, the diagonal critical
branch is uniformly unrooted, so the rooted sheared repeated-node
tangent-contact event itself does not occur there. Thus the sheared lane is
closed both in the fixed-$\gamma$ nonrecurrence direction and in the local
isolated-odd-zero direction.

Accordingly, the genuinely live nonmixed $4$-point burden is no longer local
birth, nor repeated-source first loss, nor generic determinant sign.  The
positive-kernel route now shows more: on any chamber where the repeated-source
segment sees exactly one sign change of $\mathcal R$, the born critical branch
is simple, has strictly negative slope, and cannot realize the rigidified
first-loss condition
\[
\Gamma_a(x)=\mathcal Z(a).
\]
At source level, the same branch is characterized by
\[
\mathfrak D(a,h)=0,
\]
but
Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}
shows that its rooted numerator
\[
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h)
\]
has a fixed signed leading term near an isolated odd zero, so the local branch
is uniformly unrooted there. Thus a local branch of
\[
\mathfrak D(a,h)=0
\]
cannot become a genuine obstruction until the source segment acquires a second
odd zero (equivalently a second sign-changing zero) of
\[
\mathcal W_{\mathrm{src}},
\]
or exits the local one-sign-change chamber. By
Proposition~\ref{prop:at-most-one-odd-zero-no-genuine-repeated-source-obstruction},
the positive-kernel route already excludes every opened nonmixed arc carrying
at most one odd zero of $\mathcal W_{\mathrm{src}}$ (equivalently of
$\mathcal R$).

Moreover, once one follows an analytic continuation of the born branch beyond
the local birth chamber, the rooted defect
\[
G(a)=D_a(\tau(a))-\mathcal Z(a)
\]
satisfies an exact first-order transport equation, and any nondegenerate rooted
point is forced to be a stationary point of the target map and a local fold of
the moving-shear equation
\[
A_a(x)-\mathcal Z(a)\,B_a(x)=0
\]
(Propositions~\ref{prop:rooted-defect-transport-stationary-first-root}
and~\ref{prop:nondegenerate-rooted-point-is-moving-shear-fold}).
The discriminant analysis rules out birth of such a rooted point at entry into
the adjacent-two-odd-zero chamber
(Proposition~\ref{prop:discriminant-entry-not-first-root}),
and the anchor-sign argument rules out any rooted crossing on a continuation
interval on which the anchor-side value
\[
\mathcal R(a)
\]
keeps a fixed sign
(Proposition~\ref{prop:anchor-sign-preservation-excludes-first-rooting} and
Corollary~\ref{cor:no-crossing-adjacent-two-odd-zero-under-anchor-sign-preservation}).

Beyond that, Proposition~\ref{prop:odd-anchor-passage-no-reset} shows that even
after the anchor crosses an odd-order zero of $\mathcal R$, no rooted crossing
can occur at that odd anchor zero itself or immediately after passage, while
Corollary~\ref{cor:first-post-anchor-chamber-dangerous} shows that the ensuing
post-anchor chambers alternate dangerous and safe. However,
Remark~\ref{rem:no-go-local-scalar-first-dangerous-chamber} shows that the local
normalized rooted equations and fold data are already formally compatible with
rooting on the first dangerous post-anchor chamber. More strongly,
Proposition~\ref{prop:universality-threshold-current-route-two-package} and
Corollary~\ref{cor:current-route-two-package-universal-under-normalization}
show that the entire current route-2 source package is universal under
normalization, and
Remark~\ref{rem:explicit-source-level-countermodel-current-route-two}
exhibits a genuine analytic source model realizing safe adjacent-two-odd-zero
behavior, nonlocal-target landing at the next odd anchor zero, odd-anchor
no-reset, and delayed rooted crossing.

So the sharpened remaining nonmixed burden is no longer a delayed no-crossing /
profile-realizability theorem \emph{within the current route-2 package}. The
current package is already exhausted. Any further progress must use a genuinely
non-universal source-coupled ingredient, i.e. structure not already absorbed by
the normalized planar model $(\mathcal Z,\mathcal R,D_a)$. In the present
draft, the first canonical candidates for such input lie at the quotient-septic
/ mixed level, for example through
\[
[A_7^{\mathfrak f}]
\qquad\text{or}\qquad
\Delta_7.
\]
\end{remark}

\begin{remark}[Compact status summary for the nonmixed $4$-point branch]
\label{rem:compact-status-summary-nonmixed-four-point}
The nonmixed $4$-point branch is now reduced to a source-level odd-zero
problem.  Locally, exact nonmixed contacts force zeros of $\mathcal R$, and
isolated zeros are classified by parity: even-order zeros are sterile, while
odd-order zeros seed local exact contacts.  Repeated-source first loss is not a
separate mechanism: it occurs if and only if one diagonally approaches an
odd-order zero of $\mathcal R$.  The sheared repeated-node lane is also closed
in the collapse direction: any genuine diagonal realization of the rigidified
sheared event already forces $\mathcal R\equiv 0$ locally, hence
affine-planar collapse.

On a nonmixed arc, the same structure is encoded by the gauge-invariant
source-level Wronskian
\[
\mathcal W_{\mathrm{src}}=J_\lambda J_{u_5}'-J_{u_5}J_\lambda',
\]
which differs from $\mathcal R$ only by a nonvanishing analytic factor.
Repeated-source first loss is not a separate mechanism: it occurs if and only
if one diagonally approaches an odd-order zero of $\mathcal R$, and the
corresponding rooted sheared repeated-node event is locally absent near an
isolated odd zero of $\mathcal R$. Near such an isolated odd zero, the born
repeated-source branch
\[
\mathfrak D(a,h)=0
\]
is uniformly unrooted at source level:
\[
D_{u_5}(a,h)-\mathcal Z(x(a))\,D_\lambda(a,h)\neq 0
\]
with a fixed signed leading term
(Proposition~\ref{prop:source-determinant-form-odd-zero-unrooted-defect}).
For each fixed shear level $\gamma$, the associated sheared opposite-side
$3$-point branch is globally rigid on its maximal slope-overlap block.
Moreover, the positive-kernel / source-determinant route now excludes every
opened nonmixed arc carrying at most one odd zero of
$\mathcal W_{\mathrm{src}}$:
on any chamber where the repeated-source segment sees exactly one sign change of
$\mathcal R$, the born critical branch is simple, has strictly negative slope,
and cannot realize the rigidified first-loss condition. Beyond that chamber, the
discriminant analysis rules out birth of a rooted point at entry into the
adjacent-two-odd-zero chamber, and the anchor-sign argument rules out any
crossing on a continuation interval where the anchor-side value
\[
\mathcal R(a)
\]
keeps a fixed sign.

The odd-anchor passage theorem shows that once the anchor itself crosses an
odd-order zero of $\mathcal R$, the integrating-factor defect keeps its incoming
sign across that odd anchor zero, so no rooted crossing can occur there or
immediately after it. The subsequent post-anchor chambers alternate dangerous
and safe. However, the local normalized rooted equations and the local
fold/transversality data are already formally realizable on the first dangerous
post-anchor chamber, and more strongly the entire current route-2 source package
is universal under normalization. An explicit analytic source-level countermodel
realizes safe adjacent-two-odd-zero behavior, nonlocal-target landing at the
next odd anchor zero, odd-anchor no-reset, and delayed rooted crossing inside
that package. Thus the genuinely remaining nonmixed burden is no longer a
problem inside the current route-2 package at all: any further progress must use
a genuinely non-universal source-coupled ingredient, not already absorbed by
the normalized planar model. In the present draft, the first canonical
candidates for such input lie at the quotient-septic / mixed level, for example
through
\[
[A_7^{\mathfrak f}]
\qquad\text{or}\qquad
\Delta_7.
\]
\end{remark}

\begin{remark}[Derivative-geometry meaning of the nonmixed invariant $\mathcal R$]
\label{rem:derivative-geometry-meaning-of-R}
On a nonmixed patch,
\[
\mathcal R=\frac{T_v}{K_v^2}
=
\frac{d}{dx}\!\left(\frac{Y''}{S''}\right).
\]
Thus $\mathcal R$ measures the failure of the lifted space curve
\[
x\longmapsto (Y(x),x,S(x))
\]
to be affine-planar at the derivative level: $\mathcal R=0$ means the ratio
$Y''/S''$ is locally constant, equivalently that the curve has vanishing
affine torsion and lies in an affine plane after integrating twice. In this
sense, the nonmixed $4$-point branch is controlled by a single scalar
derivative invariant rather than by raw coplanarity alone.
\end{remark}

\begin{remark}[Exact mixed reduction in terms of $\mathcal Z$ and $\mathcal R$]
\label{rem:mixed-order-bookkeeping-no-generic-parity-obstruction}
At a mixed lifted point
\[
K_v(0)=0,
\qquad
T_v(0)=0,
\]
set
\[
r:=\operatorname{ord}_0 K_v,
\qquad
s:=\operatorname{ord}_0 T_v.
\]
By Proposition~\ref{prop:exact-x-coordinate-identities-lifted-four-point},
\[
K_v=(x')^3S'',
\]
so on a good $v_5$-patch one has
\[
S''(x)=\kappa x^r+O(x^{r+1}),
\qquad \kappa\neq 0.
\]
After removing affine terms and integrating twice,
\[
S(x)=\frac{\kappa}{(r+1)(r+2)}x^{r+2}+O(x^{r+3}).
\]
Thus the mixed exponent $m$ of the monomial model
\[
Q_v(x)\sim (x^n,\ x,\ x^m)
\]
is exactly
\[
m=r+2.
\]

Now let $n$ be the first degree of $Y(x)$ not absorbed by
$\operatorname{span}\{1,x,S\}$, so that
\[
Y(x)=\alpha x^n+O(x^{n+1}),
\qquad \alpha\neq 0,
\qquad n>r+2.
\]
Using
\[
T_v=(x')^6\bigl(S''Y'''-S'''Y''\bigr),
\]
one finds
\[
s=n+r-3,
\qquad
n=s-r+3.
\]

Equivalently, on the nonmixed complement of $K_v=0$,
\[
\mathcal Z=\frac{Y''}{S''},
\qquad
\mathcal R=\mathcal Z'=\frac{T_v}{K_v^2}
\]
satisfy the order bookkeeping
\[
\operatorname{ord}_0\mathcal Z=n-r-2=s-2r+1,
\qquad
\operatorname{ord}_0\mathcal R=s-2r.
\]

Thus the dangerous low-order mixed models are finite and explicit:
\[
(m,n)=(3,4),\ (3,6),\ (4,6),
\]
equivalently
\[
(r,s)=(1,2),\ (1,4),\ (2,5),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3),\ (2,2),
\]
or
\[
(r,\operatorname{ord}_0\mathcal R)=(1,0),\ (1,2),\ (2,1).
\]

So the mixed lifted $4$-point endgame has also been reduced to a finite jet
obstruction list, now phrased in terms of the invariant pair
\[
(\mathcal Z,\mathcal R).
\]
\end{remark}

\begin{remark}[Exact finite obstruction coefficients for the low-order $4$-point branch]
\label{rem:exact-finite-obstruction-coefficients-low-order-four-point}
The explicit low-order $4$-point obstruction list can be reduced to a finite
jet package.

\medskip

\noindent
\textbf{Nonmixed side.}
Suppose $K_v(0)\neq 0$, and write
\[
s_k:=S^{(k)}(0),
\qquad
y_k:=Y^{(k)}(0),
\qquad
s_2\neq 0.
\]
Then the Taylor expansion
\[
\mathcal Z(x)=z_0+z_1x+z_2x^2+z_3x^3+z_4x^4+z_5x^5+z_6x^6+O(x^7)
\]
has canonical even coefficients
\[
z_2,\qquad z_4,\qquad z_6,
\]
and the dangerous nonmixed low-order cases are exactly:
\[
n=4 \iff z_2\neq 0,
\qquad
n=6 \iff z_2=0,\ z_4\neq 0,
\qquad
n=8 \iff z_2=z_4=0,\ z_6\neq 0.
\]
Explicitly,
\[
z_2=
\frac{
s_2^2y_4-2s_2s_3y_3+\bigl(2s_3^2-s_2s_4\bigr)y_2
}{
2\,s_2^3
},
\]
\[
z_4=
\frac{
s_2^4y_6
-s_2^3(4s_3y_5+6s_4y_4+4s_5y_3+s_6y_2)
+2s_2^2(6s_3^2y_4+12s_3s_4y_3+4s_3s_5y_2+3s_4^2y_2)
-12s_2s_3^2(2s_3y_3+3s_4y_2)
+24s_3^4y_2
}{
24\,s_2^5
},
\]
and
\[
z_6=\frac{\mathcal P_8(s_2,\dots,s_8;y_2,\dots,y_8)}{720\,s_2^7},
\]
where $\mathcal P_8$ is the explicit degree-$8$ numerator polynomial obtained
by Taylor division of $\mathcal Z=Y''/S''$.

\medskip

\noindent
\textbf{Mixed side.}
Suppose $K_v(0)=T_v(0)=0$, and let
\[
r:=\operatorname{ord}_0 K_v.
\]
For the two low-order mixed cases $r=1,2$, Taylor division of
$\mathcal Z=Y''/S''$ gives the exact obstruction coefficients
\[
\kappa_{1,1},\qquad \kappa_{1,3},\qquad \kappa_{2,2},
\]
defined by the expansions
\[
\mathcal Z(x)
=
\frac{y_2}{s_3}\frac1x
+
\left(\frac{y_3}{s_3}-\frac{s_4y_2}{2s_3^2}\right)
+
\kappa_{1,1}x+\kappa_{1,2}x^2+\kappa_{1,3}x^3+O(x^4)
\qquad (r=1),
\]
and
\[
\mathcal Z(x)
=
\frac{2y_2}{s_4}\frac1{x^2}
+
\left(\frac{2y_3}{s_4}-\frac{2s_5y_2}{3s_4^2}\right)\frac1x
+
\left(
\frac{y_4}{s_4}
-\frac{2s_5y_3}{3s_4^2}
-\frac{s_6y_2}{6s_4^2}
+\frac{2s_5^2y_2}{9s_4^3}
\right)
+\kappa_{2,1}x+\kappa_{2,2}x^2+O(x^3)
\qquad (r=2).
\]
The dangerous mixed low-order list is then exactly:
\[
(m,n)=(3,4)\iff \kappa_{1,1}\neq 0,
\]
\[
(m,n)=(3,6)\iff \kappa_{1,3}\neq 0,
\]
\[
(m,n)=(4,6)\iff \kappa_{2,2}\neq 0.
\]

Thus the full currently explicit \emph{low-order} $4$-point obstruction list is
equivalent to the finite set of coefficients
\[
\boxed{
z_2,\ z_4,\ z_6,\ \kappa_{1,1},\ \kappa_{1,3},\ \kappa_{2,2}.
}
\]

On the mixed side, the three coefficients
\[
\kappa_{1,1},\qquad \kappa_{1,3},\qquad \kappa_{2,2}
\]
exhaust the presently explicit low-order obstruction list.

On the nonmixed side, however, the parity classification from
Proposition~\ref{prop:parity-classification-isolated-nonmixed-R-zeros}
shows that local exact-contact birth occurs at every isolated odd-order zero of
$\mathcal R$. Accordingly,
\[
z_2,\qquad z_4,\qquad z_6
\]
should now be viewed only as the first three explicit low-order nonmixed
obstruction coefficients, not as a complete local nonmixed list.
\end{remark}

\begin{remark}[Wronskian-order reformulation of the mixed low-order list]
\label{rem:wronskian-order-reformulation-mixed-list}
On a good $v_5$-patch one has
\[
Y''=\frac{c^3}{M^3}J_{u_5},
\qquad
S''=\frac{c^3}{M^3}J_\lambda,
\qquad
\mathcal Z=\frac{J_{u_5}}{J_\lambda},
\qquad
\lambda=\frac{\Delta_7}{v_5}.
\]
Thus, if
\[
r:=\operatorname{ord}_0 J_\lambda=\operatorname{ord}_0 K_v,
\qquad
q:=\operatorname{ord}_0 J_{u_5}=\operatorname{ord}_0 Y'',
\]
then
\[
m=r+2,
\qquad
n=q+2,
\qquad
\operatorname{ord}_0\mathcal Z=q-r.
\]
Hence the dangerous mixed models
\[
(m,n)=(3,4),\ (3,6),\ (4,6)
\]
are exactly the Wronskian order-pairs
\[
(\operatorname{ord}_0J_\lambda,\operatorname{ord}_0J_{u_5})=(1,2),\ (1,4),\ (2,4).
\]

If
\[
J_\lambda(x)=x^rA(x),
\qquad
J_{u_5}(x)=x^rB(x),
\qquad
A(0)\neq 0,
\]
then
\[
\mathcal Z(x)=\frac{B(x)}{A(x)}.
\]
For $r=1$, the coefficients $\kappa_{1,1}$ and $\kappa_{1,3}$ are exactly the
$x^1$- and $x^3$-coefficients of the regularized ratio $B/A$; for $r=2$,
$\kappa_{2,2}$ is exactly the $x^2$-coefficient of $B/A$.

Moreover, since
\[
J_c=J_{v_5}=0,
\]
replacing
\[
u_5\longmapsto u_5+a\,c+b\,v_5+\gamma\,\lambda
\]
changes $J_{u_5}$ only by
\[
J_{u_5}\longmapsto J_{u_5}+\gamma J_\lambda.
\]
Thus the nonconstant Taylor coefficients of $\mathcal Z$ are canonical. In
particular, the currently explicit mixed low-order list is already a finite
Wronskian-ratio obstruction list.
\end{remark}

\begin{proposition}[Projective secant-shadow reduction on an overlap patch]
\label{prop:conditional-mixed-lambda-shear-projective-shadow-reduction}
Let
\[
U\Subset\{c\neq 0,\ u_5\neq 0,\ v_5\neq 0,\ M\neq 0\}
\]
be a good overlap patch. Set
\[
\lambda:=\frac{\Delta_7}{v_5},
\qquad
x:=\frac{v_5}{c},
\qquad
Y:=\frac{u_5}{c},
\qquad
S:=\frac{\lambda}{c}=\frac{\Delta_7}{c\,v_5}.
\]

Assume there exists a close exact mixed two-point bad branch
\[
(h_{1,n},h_{2,n},\Lambda_n),
\qquad
h_{1,n}\neq h_{2,n},
\qquad
h_{1,n},h_{2,n}\in U,
\qquad
h_{1,n},h_{2,n}\to m\in U,
\]
and let $(\eta_n,\xi_n,\gamma_n)$ be the branch-generated moving
$\lambda$-shears, so that
\[
(c-\eta_n\lambda)(h_{1,n})=\Lambda_n(c-\eta_n\lambda)(h_{2,n}),
\]
\[
(v_5-\xi_n\lambda)(h_{1,n})=\Lambda_n(v_5-\xi_n\lambda)(h_{2,n}),
\]
\[
(u_5-\gamma_n\lambda)(h_{1,n})=\Lambda_n(u_5-\gamma_n\lambda)(h_{2,n}).
\]
For each $n$, set
\[
A_n:=c-\eta_n\lambda,
\qquad
B_n:=v_5-\xi_n\lambda,
\qquad
F_n:=u_5-\gamma_n\lambda.
\]

Then, after discarding finitely many terms, the branch determines the exact
projective secant shadow
\[
\mathbf\Sigma(h_{1,n},h_{2,n})
:=
[x_1S_2-x_2S_1:\ Y_1S_2-Y_2S_1:\ S_2-S_1],
\]
where
\[
x_i=x(h_{i,n}),
\qquad
Y_i=Y(h_{i,n}),
\qquad
S_i=S(h_{i,n}).
\]
More precisely, for all large $n$ one has the exact identity
\[
[B_n(h_{1,n}):F_n(h_{1,n}):A_n(h_{1,n})]
=
[B_n(h_{2,n}):F_n(h_{2,n}):A_n(h_{2,n})]
=
\mathbf\Sigma(h_{1,n},h_{2,n}).
\]
In particular, the secant shadow is independent of the moving shears
$(\eta_n,\xi_n,\gamma_n)$ and of $\Lambda_n$.

Equivalently, in raw coordinates,
\[
\mathbf\Sigma(h_1,h_2)
=
[v_{5,1}\lambda_2-v_{5,2}\lambda_1:\ u_{5,1}\lambda_2-u_{5,2}\lambda_1:\ c_1\lambda_2-c_2\lambda_1].
\]

As $h_2\to h_1=a$, the secant shadow converges projectively to the tangent
shadow
\[
\mathbf\Pi(a)
:=
[xS_x-S:\ YS_x-SY_x:\ S_x]\big|_{x=x(a)}.
\]
A direct calculation gives
\[
\mathbf\Pi(x)\wedge \partial_x\mathbf\Pi(x)
=
S(x)\,
\bigl(
S_xY_{xx}-S_{xx}Y_x,\ S_{xx},\ -S_{xx}
\bigr).
\]
Hence $\mathbf\Pi$ is projectively immersive wherever
\[
S\neq 0
\qquad\text{and}\qquad
S_{xx}\neq 0.
\]
Since on the $v_5$-patch
\[
K_v=(x')^3S_{xx},
\]
any such close exact mixed two-point bad branch can accumulate only on
\[
\{S=0\}\cup\{K_v=0\}.
\]
\end{proposition}

\begin{proof}
Since
\[
x'=\left(\frac{v_5}{c}\right)'=\frac{M}{c^2},
\]
the hypothesis $M\neq 0$ implies that $x=v_5/c$ is a local coordinate near
$m$. After discarding finitely many terms we may therefore assume
\[
x(h_{1,n})\neq x(h_{2,n}).
\]

Fix such an $n$, and abbreviate
\[
\eta=\eta_n,\qquad \xi=\xi_n,\qquad \gamma=\gamma_n.
\]
Write
\[
p_i:=(x_i,Y_i,1)\in\mathbf R^3,
\qquad
V:=(\xi,\gamma,\eta)\in\mathbf R^3,
\qquad
i=1,2.
\]
Since
\[
A_n=c(1-\eta S),
\qquad
B_n=c(x-\xi S),
\qquad
F_n=c(Y-\gamma S),
\]
the exact repeated-source equations imply
\[
[B_n(h_{1,n}):F_n(h_{1,n}):A_n(h_{1,n})]
=
[p_1-S_1V]
\]
and
\[
[B_n(h_{2,n}):F_n(h_{2,n}):A_n(h_{2,n})]
=
[p_2-S_2V].
\]
Because these two projective points are equal, there is a common projective
value.

If $S_1=S_2$, then
\[
[p_1-S_1V]=[p_2-S_1V]
\]
forces $p_1=p_2$, hence $x_1=x_2$, contradicting the choice of local
coordinate. Therefore
\[
S_1\neq S_2.
\]
Subtracting
\[
p_1-S_1V=p_2-S_2V
\]
gives
\[
p_1-p_2=(S_1-S_2)V,
\]
hence
\[
V=\frac{p_1-p_2}{S_1-S_2}.
\]
Substituting back,
\[
p_1-S_1V
=
p_1-S_1\frac{p_1-p_2}{S_1-S_2}
=
\frac{S_2p_1-S_1p_2}{S_2-S_1}.
\]
Therefore the common projective value is exactly
\[
[S_2p_1-S_1p_2]
=
[x_1S_2-x_2S_1:\ Y_1S_2-Y_2S_1:\ S_2-S_1],
\]
which is the asserted secant shadow and is independent of
$(\eta_n,\xi_n,\gamma_n)$ and of $\Lambda_n$. The raw-coordinate formula is the
same identity multiplied through by $c_1c_2$.

Now divide the homogeneous secant vector by $x_2-x_1$ and let $h_2\to h_1=a$.
The three components converge to
\[
xS_x-S,\qquad YS_x-SY_x,\qquad S_x,
\]
so the secant shadow converges projectively to
\[
\mathbf\Pi(a)
=
[xS_x-S:\ YS_x-SY_x:\ S_x].
\]

Differentiating $\mathbf\Pi$ in the local $x$-coordinate gives
\[
\mathbf\Pi(x)\wedge \partial_x\mathbf\Pi(x)
=
S(x)\,
\bigl(
S_xY_{xx}-S_{xx}Y_x,\ S_{xx},\ -S_{xx}
\bigr).
\]
Therefore $\mathbf\Pi$ is projectively immersive wherever $S\neq 0$ and
$S_{xx}\neq 0$. On a close bad branch the secant shadows converge to tangent
shadows, so accumulation is possible only where immersion fails, i.e. on
\[
\{S=0\}\cup\{S_{xx}=0\}.
\]
Finally, on the $v_5$-patch one has
\[
K_v=(x')^3S_{xx},
\]
so $\{S_{xx}=0\}=\{K_v=0\}$ on $U$.
\end{proof}

\begin{remark}[Useful overlap scalar]
\label{rem:structural-mixed-overlap-scalar-two-point}
On the same overlap patch, set
\[
\tau_u:=-\frac{\Delta_7}{c\,u_5},
\qquad
\mathcal G:=x'S_x+Y'\tau_u'.
\]
Then $\mathcal G$ admits the exact factorization
\[
\mathcal G
=
-\frac{W(u_5,v_5)\,W(u_5,\lambda)}{c^2u_5^2},
\qquad
\lambda=\frac{\Delta_7}{v_5},
\]
where $W(f,g)=fg'-f'g$. Equivalently,
\[
\mathcal G
=
\frac{u_5v_5'-u_5'v_5}{c^2}
\left(\frac{\Delta_7}{u_5v_5}\right)'.
\]
In particular, $\mathcal G\not\equiv 0$ on any connected overlap patch
contained in $\{c\neq 0,\ M\neq 0\}$: the factor $W(u_5,v_5)$ cannot vanish
identically there without forcing linear dependence of
\[
1,\qquad \frac{u_5}{c},\qquad \frac{v_5}{c},
\]
and $W(u_5,\lambda)$ cannot vanish identically there without forcing
\[
\Delta_7=\kappa\,u_5v_5,
\]
which is incompatible with the direct septic slice carried by $\Delta_7$.
This does not yet exclude the mixed two-point branch, but it records the first
genuinely nontrivial $Y$-$S$ overlap coupling scalar exposed by the current
attack.
\end{remark}

\begin{proposition}[Exact fixed-shear overlap branches off $K_v=0$ force a fold at $S=0$]
\label{prop:fixed-shear-overlap-branch-off-Kv-forces-fold-at-S-zero}
Work on the overlap patch of
Proposition~\ref{prop:conditional-mixed-lambda-shear-projective-shadow-reduction},
and write
\[
\Phi(x):=
\left(
\frac{x-\xi_* S}{1-\eta_* S},
\frac{Y-\gamma_* S}{1-\eta_* S}
\right),
\qquad
S=\frac{\Delta_7}{c\,v_5}.
\]
Assume there is a close exact fixed-shear mixed $2$-point branch
\[
x_{1,n}\neq x_{2,n},
\qquad
x_{1,n},x_{2,n}\to a,
\qquad
\Phi(x_{1,n})=\Phi(x_{2,n})
\quad(n\ge 1).
\]
If
\[
K_v(a)\neq 0,
\]
then
\[
S(a)=0,
\qquad
\Phi'(a)=0,
\qquad
S_x(a)\neq 0.
\]
More precisely,
\[
0=\Phi_1'(a)=1-(\xi_*-\eta_* x(a))S_x(a),
\]
\[
0=\Phi_2'(a)=Y_x(a)-(\gamma_*-\eta_* Y(a))S_x(a).
\]
In particular, setting
\[
\beta:=\xi_*-\eta_* x(a)=\frac{1}{S_x(a)},
\]
the first-coordinate fold model
\[
U(x):=x-\beta S(x)
\]
satisfies
\[
U(a)=0,
\qquad
U_x(a)=0,
\qquad
U_{xx}(a)=-\beta S_{xx}(a)\neq 0.
\]
Hence, after analytic source reparametrization, the first coordinate of the
fixed-shear projected germ is
\[
t^2.
\]
So any exact fixed-shear mixed branch away from $K_v=0$ is already forced into
the same fold regime that underlies the nonmixed odd-zero analysis; the only
remaining issue there is the second-coordinate parity package.
\end{proposition}

\begin{proof}
A fixed-shear branch is, in particular, a close exact mixed two-point bad branch
on the same overlap patch. By
Proposition~\ref{prop:conditional-mixed-lambda-shear-projective-shadow-reduction},
any accumulation point of such a branch lies in
\[
\{S=0\}\cup\{K_v=0\}.
\]
So if $K_v(a)\neq 0$, then necessarily
\[
S(a)=0.
\]

Because
\[
\Phi(x_{1,n})=\Phi(x_{2,n}),
\qquad
x_{1,n}\neq x_{2,n},
\qquad
x_{1,n},x_{2,n}\to a,
\]
the mean value theorem applied to each coordinate of $\Phi$ gives points
\[
\zeta_{1,n},\zeta_{2,n}\in(x_{1,n},x_{2,n})
\]
such that
\[
\Phi_1'(\zeta_{1,n})=0,
\qquad
\Phi_2'(\zeta_{2,n})=0.
\]
Passing to the limit yields
\[
\Phi'(a)=0.
\]

Differentiating the two coordinates of $\Phi$ gives
\[
\Phi_1'
=
\frac{1-(\xi_*-\eta_* x)S_x-\eta_* S}{(1-\eta_* S)^2},
\]
\[
\Phi_2'
=
\frac{Y_x-(\gamma_*-\eta_* Y)S_x-\eta_* S\,Y_x}{(1-\eta_* S)^2}.
\]
Evaluating at $x=a$ and using $S(a)=0$ yields the displayed identities
\[
0=\Phi_1'(a)=1-(\xi_*-\eta_* x(a))S_x(a),
\]
\[
0=\Phi_2'(a)=Y_x(a)-(\gamma_*-\eta_* Y(a))S_x(a).
\]
The first identity implies
\[
S_x(a)\neq 0
\qquad\text{and}\qquad
\beta:=\xi_*-\eta_* x(a)=\frac{1}{S_x(a)}.
\]

Now set
\[
U(x):=x-\beta S(x).
\]
Then
\[
U(a)=a-\beta S(a)=a,
\]
so after translating the source coordinate we may assume $U(a)=0$, and
\[
U_x(a)=1-\beta S_x(a)=0.
\]
Moreover,
\[
U_{xx}(a)=-\beta S_{xx}(a).
\]
Since on the $v_5$-patch
\[
K_v=(x')^3S_{xx},
\qquad
x'=\frac{M}{c^2}\neq 0,
\]
the hypothesis $K_v(a)\neq 0$ implies
\[
S_{xx}(a)\neq 0.
\]
Hence
\[
U_{xx}(a)\neq 0.
\]
By the analytic Morse lemma in one variable, after analytic source
reparametrization the first coordinate is $t^2$.
\end{proof}

\begin{remark}[Status of the mixed $\lambda$-shear route]
\label{rem:wip-mixed-lambda-shear-route-status}
Proposition~\ref{prop:conditional-mixed-lambda-shear-projective-shadow-reduction}
shows that the downstream secant-shadow reduction is already exact and fully
projective: a close exact mixed two-point bad branch determines the projective
secant shadow
\[
\mathbf\Sigma(h_1,h_2)
=
[x_1S_2-x_2S_1:\ Y_1S_2-Y_2S_1:\ S_2-S_1],
\qquad
S=\frac{\Delta_7}{c\,v_5},
\]
independently of any affine freezing of the branch-generated $\lambda$-shears.

Proposition~\ref{prop:fixed-shear-overlap-branch-off-Kv-forces-fold-at-S-zero}
sharpens the \emph{conditional exact fixed-shear} lane: if one does obtain an
exact fixed-shear overlap reduction and the accumulation point lies off
\[
K_v=0,
\]
then the complementary slice
\[
\{S=0\}\cap\{K_v\neq 0\}
\]
is already forced into a fold-type projection regime. So, in that fixed-shear
lane, the only missing step is to identify the second-coordinate parity with
the existing nonmixed odd-zero $\mathcal R$-package. In particular, the only
clearly genuinely mixed accumulation locus already visible on the overlap patch
is
\[
K_v=0.
\]

What remains unresolved on the two-point side as a whole is therefore:
the finite-order source-level merger route;
the quotient-diagonal continuity/diagonal-collapse route; and, on the
derivative-geometric side, either a projective control of the
\[
S=0
\]
slice without exact freezing, or a proof that the exact fixed-shear overlap
lane is absorbed by the nonmixed odd-zero package. The explicit mixed low-order
obstruction list remains the finite Wronskian-order list recorded in
Remark~\ref{rem:wronskian-order-reformulation-mixed-list}.
\end{remark}

\noindent\emph{Frame convention for the scalar block.}
On the cubic-generic one-pair locus we fix the cubic-normalized frame so that
the distinguished cubic line is the diagonal-traceless line $\mathbf C D$,
with
\[
D=\begin{pmatrix}1&0\\0&-1\end{pmatrix},
\qquad
J_0DJ_0=-D.
\]
Thus the scalar coefficient extracted below is not an auxiliary choice: it is
the canonical coefficient of the cubic line in this fixed cubic-generic frame.

\begin{definition}[Canonical scalar extraction from the raw one-pair stack]
\label{def:canonical-scalar-extraction-raw-one-pair}
Let
\[
R(z)=A_3 z^3 + A_5 z^5 + A_7 z^7 + O(z^9)
\]
be a cubic-generic raw one-pair corrected germ in the cubic-normalized frame.
Write
\[
I=\begin{pmatrix}1&0\\0&1\end{pmatrix},\qquad
D=\begin{pmatrix}1&0\\0&-1\end{pmatrix},\qquad
S=\begin{pmatrix}0&1\\1&0\end{pmatrix},\qquad
K=\begin{pmatrix}0&1\\-1&0\end{pmatrix}.
\]
We use the Frobenius pairing
\[
\langle X,Y\rangle_F:=\operatorname{tr}(X^\ast Y).
\]
The scalar channel of the cubic coefficient is defined by projection to the
diagonal-traceless line $\mathbf C D$:
\[
c(R):=\frac{\langle A_3,D\rangle_F}{\langle D,D\rangle_F}
      =\frac12\,\operatorname{tr}(D A_3).
\]
Equivalently, the scalar normalization equations are
\[
\pi_I(A_3)=0,\qquad
\pi_S(A_3)=0,\qquad
\pi_K(A_3)=0,\qquad
A_3=c(R)\,D,
\]
where $\pi_I,\pi_S,\pi_K$ denote the Frobenius projections to the lines
$\mathbf C I,\mathbf C S,\mathbf C K$.
\end{definition}

\begin{remark}[Compatibility with the existing gauge laws]
\label{rem:scalar-extraction-compatible-with-gauge-laws}
By the already-proved gauge law
\[
A_3^{\new}=A_3,
\]
the cubic coefficient is unchanged by the admissible one-pair normalization
gauge. Hence the scalar extraction in
Definition~\ref{def:canonical-scalar-extraction-raw-one-pair} is gauge
independent on the raw one-pair stack.
\end{remark}

\begin{lemma}[Scalar normalization is $\Sigma$-invariant]
\label{lem:scalar-normalization-sigma-invariant}
Let
\[
\Sigma(F)(z):=J_0\,F(-z)\,J_0
\]
be the centered reflection involution, and let
\[
\Sigma_3(A):=-J_0 A J_0
\]
be its induced action on cubic coefficients. Assume
\[
J_0 D J_0=-D.
\]
Then the scalar extraction
\[
c(R)=\frac12\,\operatorname{tr}(D A_3)
\]
from Definition~\ref{def:canonical-scalar-extraction-raw-one-pair} is
$\Sigma$-invariant:
\[
c(\Sigma R)=c(R).
\]
\end{lemma}

\begin{proof}
If $R(z)=A_3 z^3+O(z^5)$, then
\[
\Sigma(R)(z)=J_0R(-z)J_0
          =(-J_0A_3J_0)z^3+O(z^5)
          =\Sigma_3(A_3)z^3+O(z^5).
\]
Therefore
\[
c(\Sigma R)
=
\frac12\,\operatorname{tr}\!\bigl(D(-J_0A_3J_0)\bigr).
\]
Using cyclicity of trace,
\[
\operatorname{tr}\!\bigl(D(-J_0A_3J_0)\bigr)
=
\operatorname{tr}\!\bigl((-J_0DJ_0)A_3\bigr).
\]
Since $J_0DJ_0=-D$, we get
\[
-J_0DJ_0=D,
\]
hence
\[
c(\Sigma R)=\frac12\,\operatorname{tr}(D A_3)=c(R).
\]
\end{proof}

\begin{lemma}[Uniqueness of the scalar output]
\label{lem:scalar-output-unique}
Let $R$ be a cubic-generic raw one-pair corrected germ. Then the scalar
$c(R)$ from
Definition~\ref{def:canonical-scalar-extraction-raw-one-pair} is uniquely
determined. In particular, if
\[
A_3=cD=\widetilde c\,D,
\]
then $c=\widetilde c$.
\end{lemma}

\begin{proof}
If
\[
(c-\widetilde c)D=0,
\]
then $c-\widetilde c=0$ because $D\neq 0$. Equivalently,
\[
c=\frac12\,\operatorname{tr}(D A_3)
\]
is the unique Frobenius coefficient of $A_3$ along the line $\mathbf C D$.
\end{proof}

\begin{corollary}[Finite-jet scalar descent on the centered branch]
\label{cor:finite-jet-scalar-descent-centered-branch}
Let $R_s$ be the centered one-pair branch, and assume
\[
R_{-s}=\Sigma(R_s).
\]
Then the scalar coefficient
\[
c(s):=c(R_s)
\]
is even:
\[
c(-s)=c(s).
\]
In particular,
\[
C_1=C_3=C_5=0.
\]
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:scalar-normalization-sigma-invariant},
\[
c(R_{-s})=c(\Sigma R_s)=c(R_s).
\]
Thus $c(-s)=c(s)$. The vanishing of the odd Taylor coefficients follows
immediately.
\end{proof}

\begin{remark}[Why the scalar block is the only remaining mixed-local bottleneck]
\label{rem:scalar-block-only-remaining-mixed-local-bottleneck}
Through quintic order, the quotient-level ambiguity is already confined to the
$J_0$-anti-fixed traceless sector, while at septic order the canonical datum
is the gauge-invariant residual $\Delta_7$. Thus, on the clean branch
$V_1\neq 0$, the only remaining mixed-local theorem is the scalar descent
\[
C_1=C_3=C_5=0.
\]
Once this holds, the finite-jet bridge to the good $v_5$-patch coordinate
$x=v_5/c$ is formal and the explicit mixed low-order obstruction list
\[
(r,\operatorname{ord}_0\mathcal Z)\in\{(1,1),(1,3),(2,2)\}
\]
is excluded immediately.
\end{remark}

\begin{remark}[Centered symmetric-placement Taylor package and diagonal-base local exclusion]
\label{rem:centered-symmetric-placement-taylor-package}
Let
\[
t_\pm=h\pm \frac{s}{2},
\]
and regard $s\mapsto -s$ as swapping the two microscopic points. For any
symmetric $2\times 2$ coefficient matrix, the diagonal half-sums are even in
$s$, the diagonal half-differences are odd in $s$, and the off-diagonal
entries are even in $s$. Applying this to the explicit formulas already in the
draft gives
\[
u_5(s),\ v_5(s)\ \text{odd},
\qquad
u_{7,K_1}(s),\ v_{7,K_1}(s)\ \text{odd},
\]
Writing
\[
u_5(s)=U_1s+U_3s^3+U_5s^5+\cdots,
\qquad
v_5(s)=V_1s+V_3s^3+V_5s^5+\cdots,
\]
the first coefficients are
\[
U_1=2\bigl(v_0\,\delta\alpha_1+\beta_0\,\delta u_1\bigr),
\]
\[
U_3=2\bigl(v_0\,\delta\alpha_3+v_2\,\delta\alpha_1+\beta_0\,\delta u_3+\beta_2\,\delta u_1\bigr),
\]
\[
U_5=2\bigl(v_0\,\delta\alpha_5+v_2\,\delta\alpha_3+v_4\,\delta\alpha_1+\beta_0\,\delta u_5+\beta_2\,\delta u_3+\beta_4\,\delta u_1\bigr),
\]
and
\[
V_1=2\bigl(\bar\alpha_0\,\delta u_1+\delta\alpha_1\,\bar u_0\bigr),
\]
\[
V_3=2\bigl(\bar\alpha_0\,\delta u_3+\bar\alpha_2\,\delta u_1+\delta\alpha_1\,\bar u_2+\delta\alpha_3\,\bar u_0\bigr),
\]
\[
V_5=2\bigl(\bar\alpha_0\,\delta u_5+\bar\alpha_2\,\delta u_3+\bar\alpha_4\,\delta u_1+\delta\alpha_1\,\bar u_4+\delta\alpha_3\,\bar u_2+\delta\alpha_5\,\bar u_0\bigr).
\]

Likewise, writing
\[
u_{7,K_1}(s)=\widehat U_1s+\widehat U_3s^3+\cdots,
\qquad
v_{7,K_1}(s)=\widehat V_1s+\widehat V_3s^3+\cdots,
\]
one gets
\[
\widehat U_1
=
2\kappa\bigl(
\delta x_1\,\nu_{6,0}
+\beta_{5,0}\,\delta u_1
+v_0\,\delta\alpha_{5,1}
+b_0\,\delta p_1
+r_0\,\delta a_1
\bigr),
\]
\[
\widehat V_1
=
2\kappa\bigl(
\delta x_1\,\bar\mu_{6,0}
-\bar x_0\,\delta\mu_{6,1}
+\bar\alpha_{5,0}\,\delta u_1
+\delta\alpha_{5,1}\,\bar u_0
+\bar a_0\,\delta p_1
+\delta a_1\,\bar p_0
\bigr),
\]
and
\[
\widehat U_3
=
2\kappa\bigl(
\delta x_1\nu_{6,2}+\delta x_3\nu_{6,0}
+\beta_{5,0}\delta u_3+\beta_{5,2}\delta u_1
+v_0\delta\alpha_{5,3}+v_2\delta\alpha_{5,1}
+b_0\delta p_3+b_2\delta p_1
+r_0\delta a_3+r_2\delta a_1
\bigr),
\]
\[
\widehat V_3
=
2\kappa\bigl(
\delta x_1\bar\mu_{6,2}+\delta x_3\bar\mu_{6,0}
-\bar x_0\delta\mu_{6,3}-\bar x_2\delta\mu_{6,1}
+\bar\alpha_{5,0}\delta u_3+\bar\alpha_{5,2}\delta u_1
+\delta\alpha_{5,1}\bar u_2+\delta\alpha_{5,3}\bar u_0
+\bar a_0\delta p_3+\bar a_2\delta p_1
+\delta a_1\bar p_2+\delta a_3\bar p_0
\bigr).
\]

and therefore
\[
\Delta_7(s)=u_{7,K_1}(s)v_5(s)-u_5(s)v_{7,K_1}(s)
\]
is even in $s$, with Taylor expansion
\[
\Delta_7(s)=D_2s^2+D_4s^4+D_6s^6+\cdots,
\]
where
\[
D_2=\widehat U_1V_1-U_1\widehat V_1,
\]
\[
D_4=\widehat U_1V_3+\widehat U_3V_1-U_1\widehat V_3-U_3\widehat V_1,
\]
\[
D_6=\widehat U_1V_5+\widehat U_3V_3+\widehat U_5V_1-U_1\widehat V_5-U_3\widehat V_3-U_5\widehat V_1.
\]

\medskip

Assume now that
\[
c(s)=C_0+C_2s^2+C_4s^4+\cdots,
\qquad C_0\neq 0.
\]
Then
\[
x(s)=\frac{v_5(s)}{c(s)}
\]
is an odd series
\[
x(s)=X_1s+X_3s^3+X_5s^5+\cdots
\]
with
\[
X_1=\frac{V_1}{C_0},
\]
\[
X_3=\frac{V_3C_0-V_1C_2}{C_0^2},
\]
\[
X_5=\frac{V_5C_0^2-V_3C_0C_2+V_1(C_2^2-C_0C_4)}{C_0^3}.
\]
In particular, if $V_1\neq 0$, then $x$ is an odd local coordinate with odd
inverse
\[
s(x)=\sigma_1x+\sigma_3x^3+\sigma_5x^5+\cdots,
\]
where
\[
\sigma_1=\frac{C_0}{V_1},
\qquad
\sigma_3=-\frac{C_0(V_3C_0-V_1C_2)}{V_1^4},
\]
and so on.

Similarly,
\[
\lambda(s):=\frac{\Delta_7(s)}{v_5(s)}
\]
is an odd series
\[
\lambda(s)=L_1s+L_3s^3+L_5s^5+\cdots
\]
with
\[
L_1=\frac{D_2}{V_1},
\]
\[
L_3=\frac{D_4V_1-D_2V_3}{V_1^2},
\]
\[
L_5=\frac{D_6V_1^2-D_4V_1V_3+D_2(V_3^2-V_1V_5)}{V_1^3}.
\]

So, whenever $x$ is used as the induced odd collision-side coordinate, parity
in $s$ transfers to parity in $x$, and one obtains
\[
Y(x)=\frac{u_5}{c}(x)\ \text{odd},
\qquad
\lambda(x)=\frac{\Delta_7}{v_5}(x)\ \text{odd},
\qquad
S(x)=\frac{\lambda}{c}(x)\ \text{odd}.
\]
Consequently,
\[
Y''(x)\ \text{odd},\qquad
S''(x)\ \text{odd},
\]
hence
\[
\mathcal Z(x)=\frac{Y''}{S''}\ \text{even},
\qquad
\mathcal R(x)=\mathcal Z'(x)\ \text{odd},
\qquad
K_v=(x')^3S''\ \text{odd}.
\]
This is the parity package underlying the provisional mixed-branch exclusion
discussed below.

If $x=v_5/c$ is used as the induced odd collision-side coordinate, then the
centered diagonal germ has the odd/odd form
\[
Q(x)\sim (x^n,\ x,\ x^m),
\qquad
m,n\ \text{odd},\quad n>m\ge 3.
\]
In that regime one obtains the exact factorizations
\[
S''(x)=x^{m-2}\Sigma_m[A](x^2),
\qquad
\mathcal Z(x)=x^{n-m}H(x^2),
\qquad
\mathcal R(x)=x^{n-m-1}J(x^2),
\]
with $H(0)\neq 0$ and $J(0)\neq 0$. Hence there exists $\varepsilon>0$
such that for
\[
0<|x|<\varepsilon
\]
one has
\[
K_v(x)\neq 0,\qquad T_v(x)\neq 0.
\]

So, in the diagonal-based local regime where this odd collision-side coordinate
description is valid, the centered diagonal base has a punctured neighborhood
free of $K_v=0$ and $T_v=0$ points. In particular, the currently explicit
low-order dangerous patterns do not arise at the symmetric diagonal base itself.

\medskip

\noindent
\textit{Work in progress.}
The odd/even transfer from the centered microscopic variable $s$ to a general
good-patch coordinate $x=v_5/c$ should still be treated as a live theorem-level
bridge outside the diagonal-based local regime. What is no longer open at the
same level is total quintic collapse on the centered branch: by
Lemma~\ref{lem:centered-tagged-quintic-witness-survives-specialization} and
Corollary~\ref{cor:centered-quintic-fixed-sector-nontriviality}, one already
has
\[
u_5(s)\not\equiv 0,
\qquad
A_5^{\mathfrak f}(s)\not\equiv 0.
\]
So the remaining mixed-side task is not to prove that some quintic channel
survives, but to promote this centered quintic nontriviality into an actual
punctured $v_5$- or $u_5$-patch.
\end{remark}

\begin{lemma}[Total centered quintic collapse forces source-level degeneration]
\label{lem:total-centered-quintic-collapse}
On the centered symmetric-placement branch one has
\[
u_5=2\bigl(v\,\delta\alpha+\beta\,\delta u\bigr),
\qquad
v_5=2\bigl(\bar\alpha\,\delta u+\bar u\,\delta\alpha\bigr).
\]
If
\[
u_5\equiv 0,
\qquad
v_5\equiv 0,
\]
then
\[
\begin{pmatrix}
\beta(s) & v(s)\\
\bar\alpha(s) & \bar u(s)
\end{pmatrix}
\binom{\delta u(s)}{\delta\alpha(s)}
=0
\]
as an identity of analytic germs. Consequently, either
\[
\Delta_5(s):=\beta(s)\bar u(s)-v(s)\bar\alpha(s)\equiv 0,
\]
or
\[
\delta u(s)\equiv 0,
\qquad
\delta\alpha(s)\equiv 0.
\]
\end{lemma}

\begin{proof}
This is immediate from the displayed formulas for $u_5$ and $v_5$.
If the $2\times 2$ coefficient matrix has nonzero determinant, then the only
solution is $\delta u=\delta\alpha\equiv 0$. If its determinant vanishes
identically, then $\Delta_5\equiv 0$.
\end{proof}

\begin{corollary}[Total centered quintic collapse forces total canonical transport collapse]
\label{cor:total-centered-quintic-collapse-forces-total-transport-collapse}
If
\[
u_5\equiv 0,
\qquad
v_5\equiv 0
\]
on the centered branch, then
\[
A_5^{\mathfrak f}\equiv 0,
\qquad
\Delta_7\equiv 0.
\]
In particular, total centered quintic collapse forces collapse of the canonical
quintic/septic transport package on that branch.
\end{corollary}

\begin{proof}
The identity
\[
A_5^{\mathfrak f}=u_5 I+v_5 S
\]
gives $A_5^{\mathfrak f}\equiv 0$ immediately. Likewise
\[
\Delta_7=u_{7,K_1}v_5-u_5v_{7,K_1}
\]
vanishes identically when $u_5\equiv v_5\equiv 0$.
\end{proof}

\begin{lemma}[Centered tagged quintic witness survives specialization]
\label{lem:centered-tagged-quintic-witness-survives-specialization}
On the tagged slice
\[
(K_1,\eta_2,q^{(5)}),
\]
the first centered odd coefficient
\[
U_1
\]
of
\[
u_5(s)=U_1s+U_3s^3+U_5s^5+\cdots
\]
has a nonzero $\kappa\,\eta_2\,q^{(5)}$-coefficient. In particular
\[
U_1\neq 0
\]
on that tagged slice, and hence
\[
u_5(s)\not\equiv 0
\]
as a centered germ.
\end{lemma}

\begin{proof}
The centered coefficient formula is
\[
U_1=2\bigl(v_0\,\delta\alpha_1+\beta_0\,\delta u_1\bigr).
\]
By the tagged-slice analysis already used in the proof of
Lemma~\ref{lem:no-cancellation-quintic-trace}, the $\eta_2$-slice of $X_1$
is off-diagonal, so
\[
\delta u_1=0,
\]
and the $q^{(5)}$-slice of $X_3$ is diagonal, so
\[
\beta_0=0.
\]
Hence
\[
U_1=2v_0\,\delta\alpha_1
\]
on the tagged slice.

Now use the explicit two-direction computation from the proof of
Lemma~\ref{lem:no-cancellation-quintic-trace}. There one writes
\[
G_0=\operatorname{diag}(a^2,b^2),
\qquad
A=
\begin{pmatrix}
0&u\\u&0
\end{pmatrix},
\qquad
D=
\begin{pmatrix}
0&0\\0&d
\end{pmatrix},
\]
and expands
\[
X(\varepsilon,\delta)
=
X_0+\varepsilon U+\delta V+\varepsilon\delta W+O(\varepsilon^2,\delta^2).
\]
The proof gives
\[
U_{12}=-\frac{u}{ab(a+b)}\neq 0,
\qquad
V_{22}=-\frac{d}{2b^3}\neq 0.
\]
Here $U_{12}$ gives the tagged $\eta_2$-contribution to the off-diagonal
channel $v_0$, while $V_{22}$ gives the tagged $q^{(5)}$-contribution to the
diagonal-difference channel $\gamma-\alpha=2\delta\alpha_1$. Thus the tagged
slice contributes nontrivially to the product $v_0\,\delta\alpha_1$, and hence
to $U_1=2v_0\,\delta\alpha_1$.
\end{proof}

\begin{corollary}[Centered quintic fixed-sector nontriviality]
\label{cor:centered-quintic-fixed-sector-nontriviality}
On the centered diagonal branch,
\[
A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S
\]
is not identically zero. Equivalently,
\[
(u_5(s),v_5(s))\not\equiv (0,0).
\]
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:centered-tagged-quintic-witness-survives-specialization},
one has $u_5(s)\not\equiv 0$. Since $I$ and $S$ are linearly independent,
the fixed-sector package $A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S$ cannot vanish
identically.
\end{proof}

\begin{lemma}[Valuation form of the septic transport constraint]
\label{lem:valuation-form-septic-transport-constraint}
Assume on the centered branch that
\[
\lambda=\frac{\Delta_7}{v_5}
\]
is analytic odd. Write
\[
\operatorname{ord}_s u_5=2m+1,
\qquad
\operatorname{ord}_s v_5=2r+1,
\qquad
r\ge m.
\]
Then
\[
\operatorname{ord}_s v_{7,K_1}\ge \operatorname{ord}_s v_5-\operatorname{ord}_s u_5+1=2(r-m)+1.
\]
Equivalently, if
\[
U_1=\cdots=U_{2m-1}=0,\qquad U_{2m+1}\neq 0,
\]
and
\[
V_1=\cdots=V_{2r-1}=0,\qquad V_{2r+1}\neq 0,
\]
then
\[
\widehat V_1=\widehat V_3=\cdots=\widehat V_{2(r-m)-1}=0,
\]
and the first potentially surviving even coefficient of $\Delta_7$ is
\[
D_{2r+2}=\widehat U_1V_{2r+1}-U_{2m+1}\widehat V_{2(r-m)+1}.
\]
\end{lemma}

\begin{proof}
Since $\lambda$ is analytic odd and
\[
\Delta_7=\lambda\,v_5,
\]
one has
\[
\operatorname{ord}_s\Delta_7\ge \operatorname{ord}_s v_5+1=2r+2.
\]
Suppose
\[
\operatorname{ord}_s v_{7,K_1}=2d+1<2(r-m)+1.
\]
Then
\[
\operatorname{ord}_s(u_5v_{7,K_1})=(2m+1)+(2d+1)\le 2r,
\]
whereas
\[
\operatorname{ord}_s(u_{7,K_1}v_5)\ge 1+(2r+1)=2r+2
\]
because $u_{7,K_1}$ is odd. Therefore the leading term of
\[
\Delta_7=u_{7,K_1}v_5-u_5v_{7,K_1}
\]
would occur at order at most $2r$, contradicting $\operatorname{ord}_s\Delta_7\ge 2r+2$.
So
\[
\operatorname{ord}_s v_{7,K_1}\ge 2(r-m)+1.
\]

The coefficient statement is the corresponding triangular coefficient form:
vanishing of
\[
D_2,D_4,\dots,D_{2r}
\]
forces
\[
\widehat V_1,\widehat V_3,\dots,\widehat V_{2(r-m)-1}
\]
to vanish successively, and the first potentially surviving coefficient is
\[
D_{2r+2}=\widehat U_1V_{2r+1}-U_{2m+1}\widehat V_{2(r-m)+1}.
\qedhere
\]
\end{proof}

\begin{lemma}[Late-$v_5$ $u_5$-patch affine-normalization transplant]
\label{lem:late-v5-u5-patch-transplant}
Assume the centered scalar package from
Remark~\ref{rem:centered-symmetric-placement-taylor-package}, and assume
\[
U_1\neq 0.
\]
Then
\[
y:=\frac{u_5}{c}
\]
is an odd local coordinate near the centered base. Suppose in addition that
\[
\operatorname{ord}_s v_5=2r+1\ge 3.
\]
On the corresponding $u_5$-patch write
\[
x(y):=\frac{v_5}{c},
\qquad
\tau_u(y):=-\frac{\Delta_7}{c\,u_5},
\qquad
\widetilde\tau_u(y):=\tau_u(y)-\tau_u'(0)\,y.
\]
Then:
\begin{enumerate}
\item $x(y)$ is odd and satisfies
\[
x(y)=O(y^{2r+1});
\]
in particular $\operatorname{ord}_0 x\ge 3$;
\item $\widetilde\tau_u(y)$ is odd and either vanishes identically or has odd
order at least $3$;
\item if $\widetilde\tau_u\not\equiv 0$, then after an ambient affine
normalization consisting of a coordinate permutation and subtraction of a
suitable odd multiple of one higher-order channel from the other, the germ
$Q_u$ is carried to the same odd/odd local normal form
\[
(y^n,\ y,\ y^m),
\qquad
n>m\ge 3,\quad m,n\ \text{odd},
\]
already analyzed in
Remark~\ref{rem:centered-symmetric-placement-taylor-package}.
\end{enumerate}
Consequently, in the subcase $\widetilde\tau_u\not\equiv 0$, the late-$v_5$
corner is locally sterile on punctured $u_5$-patch arcs: no genuinely new
mixed low-order $4$-point branch is born there.
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:centered-tagged-quintic-witness-survives-specialization},
\[
u_5(s)=U_1s+O(s^3),
\qquad
c(s)=C_0+O(s^2),
\qquad
C_0\neq 0,
\]
so
\[
y(s)=\frac{u_5(s)}{c(s)}
\]
is an odd local coordinate with odd inverse $s=s(y)$.

Since $v_5$ is odd and $c$ is even in $s$,
\[
x(y)=\frac{v_5}{c}
\]
is odd in $y$. Because $\operatorname{ord}_s u_5=1$ and
$\operatorname{ord}_s v_5=2r+1$, one has
\[
x(y)=O(y^{2r+1}),
\]
so $\operatorname{ord}_0x\ge 3$.

Likewise $\Delta_7$ is even while $c$ is even and $u_5$ is odd, hence
\[
\tau_u(y)=-\frac{\Delta_7}{c\,u_5}
\]
is odd in $y$. Therefore
\[
\widetilde\tau_u(y):=\tau_u(y)-\tau_u'(0)\,y
\]
is odd and either identically zero or of odd order at least $3$.

Assume now that $\widetilde\tau_u\not\equiv 0$. Then the normalized germ is
\[
Q_u(y)=\bigl(y,\ x(y),\ \widetilde\tau_u(y)\bigr),
\]
with the last two channels odd and of order at least $3$. Apply the ambient
coordinate permutation
\[
(Y,X,Z)\longmapsto (X,Y,Z).
\]
This preserves affine dependence/coplanarity geometry. If the two higher-order
odd channels have the same leading odd order, subtract a suitable odd multiple
of one from the other to separate those leading orders. After this affine
normalization one reaches a germ of the form
\[
(y^nB(y^2),\ y,\ y^mA(y^2)),
\qquad
n>m\ge 3,\quad m,n\ \text{odd},
\]
with $A(0)B(0)\neq 0$, i.e. the same odd/odd local normal form analyzed in
Remark~\ref{rem:centered-symmetric-placement-taylor-package}. The same local
calculation then gives a punctured neighborhood free of nearby mixed and
nonmixed $4$-point obstruction points.
\end{proof}

\begin{lemma}[Planar-lift absorption on the $u_5$-patch]
\label{lem:planar-lift-absorption-u5-patch}
Assume the hypotheses of
Lemma~\ref{lem:late-v5-u5-patch-transplant}, and suppose
\[
\widetilde\tau_u\equiv 0.
\]
Equivalently, there is a constant $a\in\mathbf C$ such that
\[
\Delta_7=-a\,u_5^2
\]
locally on the $u_5$-patch. Then after an ambient affine shear one has
\[
Q_u\sim (y,x,0),
\qquad
y=\frac{u_5}{c},
\quad
x=\frac{v_5}{c}.
\]
In particular, the lifted curve is affine-planar, and the remaining local
content is only the planar affine dependence of
\[
\Xi(h):=\left(\frac{u_5(h)}{c(h)},\frac{v_5(h)}{c(h)}\right).
\]

Moreover, in the defect-free order-$\le 5$ finite-core setting of
Theorem~\ref{thm:defect-free-quintic-circuit-reduction}, this residual corner is
absorbed into the already-known quintic-circuit regime: it does not define a
genuinely new mixed/septic $4$-point branch.
\end{lemma}

\begin{proof}
The identity $\widetilde\tau_u\equiv 0$ means exactly that
\[
\tau_u(y)=a\,y
\]
for some constant $a$. Since
\[
\tau_u=-\frac{\Delta_7}{c\,u_5},
\qquad
y=\frac{u_5}{c},
\]
this is equivalent to
\[
-\frac{\Delta_7}{c\,u_5}=a\,\frac{u_5}{c},
\]
hence
\[
\Delta_7=-a\,u_5^2.
\]
Thus
\[
Q_u=(y,x,ay).
\]
Applying the ambient affine shear
\[
(Y,X,Z)\longmapsto (Y,X,Z-aY)
\]
gives
\[
Q_u\sim (y,x,0).
\]
So the lifted curve is affine-planar.

Now assume additionally the defect-free order-$\le 5$ finite-core hypotheses
from Theorem~\ref{thm:defect-free-quintic-circuit-reduction}. By
Remark~\ref{rem:parallel-u5-patch-version}, the same defect-free
affine-dependence conclusions hold with $Q_v$ replaced by $Q_u$. Since the
third coordinate of $Q_u$ vanishes after the shear, affine dependence of the
lifted points is equivalent to affine dependence of the planar points
\[
\Xi(h_j)=\left(\frac{u_5(h_j)}{c(h_j)},\frac{v_5(h_j)}{c(h_j)}\right)\in\mathbf C^2.
\]
But this is exactly the planar quintic-circuit geometry organized by
Theorem~\ref{thm:defect-free-quintic-circuit-reduction} and
Corollary~\ref{cor:defect-free-minimal-quintic-circuits}. Hence this residual
corner is already-quintic rather than a genuinely new mixed septic branch.
\end{proof}

\begin{corollary}[Right-pincer trichotomy near the centered base]
\label{cor:right-pincer-trichotomy-centered-base}
Near the centered diagonal base, the mixed local picture is reduced to the
following three cases:
\[
V_1\neq 0
\Longrightarrow
\text{clean }v_5\text{-patch branch;}
\]
\[
V_1=0,\ \widetilde\tau_u\not\equiv 0
\Longrightarrow
\text{late-}v_5\text{ branch locally sterile on }Q_u;
\]
\[
V_1=0,\ \widetilde\tau_u\equiv 0
\Longleftrightarrow
\Delta_7=-a\,u_5^2
\Longrightarrow
\text{planar-lift corner, hence already-quintic.}
\]
So every late-$v_5$ branch near the centered base is either locally sterile
or already absorbed into the quintic-circuit regime. The only genuinely new
mixed local branch left to study there is the clean branch
\[
\operatorname{ord}_s v_5=1.
\]
\end{corollary}

\begin{proof}
Combine Lemma~\ref{lem:late-v5-u5-patch-transplant} and
Lemma~\ref{lem:planar-lift-absorption-u5-patch}, together with the fact that
$v_5$ is odd in the centered variable.
\end{proof}

\begin{corollary}[Right-pincer local reduction near the centered base]
\label{cor:right-pincer-local-reduction-centered-base}
Assume the centered scalar package from
Remark~\ref{rem:centered-symmetric-placement-taylor-package}, and assume also
that the centered tagged quintic witness gives
\[
U_1\neq 0.
\]
Then every
sufficiently small nearby genuinely new mixed $4$-point obstruction point near
the centered base must lie on the clean branch
\[
\operatorname{ord}_s v_5=1,
\]
equivalently
\[
V_1\neq 0.
\]
In particular, every late-$v_5$ branch near the centered base is either
locally sterile on the $u_5$-patch or already absorbed into the defect-free
quintic-circuit regime.
\end{corollary}

\begin{proof}
Because $v_5$ is odd in the centered variable, either
\[
\operatorname{ord}_s v_5=1
\qquad\text{or}\qquad
\operatorname{ord}_s v_5\ge 3 \text{ odd}.
\]
If $\operatorname{ord}_s v_5\ge 3$, then
Lemma~\ref{lem:late-v5-u5-patch-transplant} and
Lemma~\ref{lem:planar-lift-absorption-u5-patch}
show that the branch is either locally sterile on the $u_5$-patch or
planar-lift and hence already-quintic. So a sufficiently small nearby
genuinely new mixed $4$-point obstruction cannot lie on such a late-$v_5$
branch. Therefore any such genuinely new mixed local branch must lie on the
only remaining possibility,
\[
\operatorname{ord}_s v_5=1.
\qedhere
\]
\end{proof}

\begin{proposition}[Realization lemma for lifted germs]
\label{prop:realization-lemma-lifted-germs}
Let $\widetilde Y(\xi)$ and $\widetilde S(\xi)$ be arbitrary analytic germs
at $\xi=0$. Define
\[
c(\xi)\equiv 1,
\qquad
v_5(\xi):=1+\xi,
\qquad
u_5(\xi):=\widetilde Y(\xi),
\qquad
\Delta_7(\xi):=(1+\xi)\widetilde S(\xi).
\]
Then on a sufficiently small neighborhood of $0$,
\[
c\neq 0,
\qquad
v_5\neq 0,
\qquad
M=c\,v_5'-c'v_5=1\neq 0,
\]
so this is a good $v_5$-patch. The normalized lifted coordinates are
\[
x=\frac{v_5}{c}=1+\xi,
\qquad
Y=\frac{u_5}{c}=\widetilde Y(\xi),
\qquad
S=\frac{\Delta_7}{c\,v_5}=\widetilde S(\xi).
\]
After the affine shift $x\mapsto x-1$, the lifted germ becomes
\[
Q_v(\xi)=\bigl(\widetilde Y(\xi),\,\xi,\,\widetilde S(\xi)\bigr).
\]

Thus every analytic pair of germs $(\widetilde Y,\widetilde S)$ occurs, after
affine normalization, as the lifted pair $(Y,S)$ on some good $v_5$-patch.
\end{proposition}

\begin{proof}
The displayed formulas are immediate from the definitions. The hypotheses
$c\neq 0$, $v_5\neq 0$, and $M=1\neq 0$ hold on a sufficiently small
neighborhood of $0$, and the formulas for $x,Y,S$ are direct.
\end{proof}

\begin{corollary}[No new obstruction for $(\mathcal Z,\mathcal R)$ is available at the current lifted level]
\label{cor:no-new-jet-obstruction-current-lifted-level}
No identity involving only
\[
c,\qquad v_5,\qquad u_5,\qquad \Delta_7
\]
and their derivatives can force either of the two dream conclusions:
\[
\mathcal R \text{ is even in the normalized nonmixed coordinate},
\]
or the mixed-branch exclusion
\[
(r,\operatorname{ord}_0\mathcal Z)\notin\{(1,1),(1,3),(2,2)\}
\quad\text{at every mixed point.}
\]

In particular, the nonmixed models
\[
Q_v(\xi)=(\xi^n,\xi,\xi^2),
\qquad n\ge 4 \ \text{even},
\]
are all realizable at the present lifted level; the cases
\[
n=4,6,8
\]
are simply the first currently explicit low-order examples.
The dangerous mixed models
\[
Q_v(\xi)=(\xi^n,\xi,\xi^m),
\qquad (m,n)=(3,4),\ (3,6),\ (4,6),
\]
are all realizable at the present lifted level.

Consequently, any RH-specific obstruction to the low-order dangerous
$4$-point patterns must use information not encoded in the current lifted
variables
\[
(c,v_5,u_5,\Delta_7)
\]
alone. It must come from deeper source-level corrected quotient-germ
structure, matrix-level identities behind $(u_5,\Delta_7)$, or an additional
symmetry not yet visible in the present lifted formulation.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:realization-lemma-lifted-germs} with
\[
(\widetilde Y,\widetilde S)=(\xi^n,\xi^2)
\]
for the nonmixed cases, and with
\[
(\widetilde Y,\widetilde S)=(\xi^n,\xi^m)
\]
for the mixed cases. These realize exactly the dangerous low-order patterns for
$(\mathcal Z,\mathcal R)$ listed above.
\end{proof}

\begin{remark}[Updated nonmixed status versus mixed local exhaustion]
\label{rem:wip-dream-parity-identity-four-point}
The local nonmixed lifted route is now closed at the derivative-geometric level.
Exact nonmixed contacts force zeros of $\mathcal R$; one-sign
$\mathcal R$-intervals are sterile; recurrent exact contacts force
affine-planar collapse; and isolated zeros of $\mathcal R$ are classified by
parity. In addition, the repeated-source / first-loss mechanism is now fully
reduced: no attained separated first loss can occur, every first-loss sequence
is forced to the diagonal, and diagonal first loss occurs exactly at odd zeros
of $\mathcal R$. Thus the nonmixed burden is no longer a local parity theorem
or a separate repeated-source obstruction. It is the global/source-level
control of which odd zeros of
\[
\mathcal R=\frac{T_v}{K_v^2},
\qquad\text{equivalently}\qquad
\mathcal W_{\mathrm{src}}=J_\lambda J_{u_5}'-J_{u_5}J_\lambda',
\]
can actually arise along opened nonmixed arcs.

On the mixed side, the decisive pair-level object remains
\[
A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S.
\]
By Corollary~\ref{cor:centered-quintic-fixed-sector-nontriviality}, this
package is not identically zero, so after shrinking to one-sided punctured arcs
the centered branch enters either a good $v_5$-patch or the parallel
$u_5$-patch. Near the centered base, however, the theorem package now goes
further: every late-$v_5$ branch is already either locally sterile on the
automatic $u_5$-patch or absorbed into the planar defect-free quintic-circuit
regime, so the only genuinely new mixed local branch left there is the clean
branch
\[
V_1\neq 0.
\]

Accordingly, the mixed-side local problem is no longer a vague codimension-two
obstruction, nor merely a patch-opening issue. Near the centered base it has
been reduced to the single clean branch $V_1\neq 0$, and on that branch the
remaining theorem-level task is the finite scalar descent
\[
c(-s)=c(s)\pmod{s^6},
\qquad\text{equivalently}\qquad
C_1=C_3=C_5=0,
\]
which makes the centered-to-patch finite-jet parity bridge formal.
\end{remark}

\begin{remark}[What the four-point branch now reduces to]
\label{rem:next-algebraic-target-four-point}
The lifted $4$-point branch is now organized by the canonical invariant pair
\[
\mathcal Z=\frac{Y''}{S''}=\frac{J_{u_5}}{J_\lambda},
\qquad
\mathcal R=\mathcal Z'=\frac{T_v}{K_v^2},
\qquad
\lambda=\frac{\Delta_7}{v_5}.
\]

On the nonmixed side, after normalization to
\[
Q_v(\xi)=\bigl(\widetilde Y(\xi),\,\xi,\,\xi^2\bigr),
\]
the local derivative-side picture is now explicit. Exact nonmixed contacts force
zeros of
\[
\mathcal R=\frac12\,\widetilde Y''',
\]
isolated zeros are classified by parity, one-sign $\mathcal R$-intervals are
exactly-contact sterile, and recurrent exact contacts force affine-planar
collapse.

The explicit low-order list
\[
\operatorname{ord}_0\mathcal R\in\{1,3,5\},
\]
equivalently the coefficients
\[
z_2,\qquad z_4,\qquad z_6,
\]
should therefore now be regarded only as the first explicit low-order nonmixed
odd-order cases, not as the full local nonmixed picture.

For fixed source point $a$, repeated-source exact contacts factor through the
quadratic-envelope scalar
\[
\Gamma_a(x)=
\frac{Y(x)-Y(a)-Y'(a)(x-a)}
{S(x)-S(a)-S'(a)(x-a)},
\]
equivalently through the below-lifted quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)}.
\]
Its derivative is governed by the osculatory $4\times 4$ source determinant
$\mathfrak D(a,h)$. By
Proposition~\ref{prop:first-loss-is-diagonal-odd-zero-birth}, this
repeated-source / first-loss mechanism is now completely reduced: no attained
separated first loss can occur, and any first loss is exactly the diagonal
birth at an isolated odd-order zero of $\mathcal R$.

Thus the remaining nonmixed burden is no longer local parity, nor a separate
first-loss geometry, but purely the global/source-level control of which odd
zeros of $\mathcal W_{\mathrm{src}}$, equivalently of $\mathcal R$, occur
on genuine opened arcs.

On the mixed side, the explicit low-order dangerous list is
\[
(m,n)=(3,4),\ (3,6),\ (4,6),
\]
equivalently
\[
(r,s)=(1,2),\ (1,4),\ (2,5),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3),\ (2,2),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal R)=(1,0),\ (1,2),\ (2,1).
\]

\noindent
Equivalently, in the below-lifted Wronskian formulation from
Remark~\ref{rem:wronskian-order-reformulation-mixed-list}, the dangerous mixed
models are exactly the order-pairs
\[
(\operatorname{ord}_0J_\lambda,\operatorname{ord}_0J_{u_5})
=(1,2),\ (1,4),\ (2,4).
\]
So the mixed low-order branch is already a finite canonical
Wronskian-ratio obstruction problem, captured in local mixed $x$-coordinates by
\[
\kappa_{1,1},\qquad \kappa_{1,3},\qquad \kappa_{2,2}.
\]

By the realization lemma, no identity involving only
\[
(c,v_5,u_5,\Delta_7)
\]
and their derivatives can eliminate these mixed patterns in general.

At the pair level, the centered fixed-sector quintic package
\[
A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S
\]
is now the natural object controlling whether any quintic patch opens at all.
By Corollary~\ref{cor:centered-quintic-fixed-sector-nontriviality},
\[
A_5^{\mathfrak f}(s)\not\equiv 0,
\]
so the centered branch cannot suffer total quintic collapse.

Near the centered base, however, the mixed-side local picture is now sharper
than a mere patch dichotomy. By
Corollary~\ref{cor:right-pincer-local-reduction-centered-base}, every
sufficiently small nearby genuinely new mixed $4$-point obstruction must lie
on the clean branch
\[
\operatorname{ord}_s v_5=1,
\]
while every late-$v_5$ branch is either locally sterile on the automatic
$u_5$-patch or already absorbed into the defect-free planar
quintic-circuit regime. Thus the genuinely new mixed local geometry near the
centered base has been reduced to the single clean branch $V_1\neq 0$.

Accordingly, the remaining mixed-side theorem is no longer another lifted jet
computation, nor a pointwise coefficient nonvanishing statement such as
$V_1\neq 0$ in isolation. It is the finite scalar descent on the clean branch,
namely
\[
c(-s)=c(s)\pmod{s^6},
\qquad\text{equivalently}\qquad
C_1=C_3=C_5=0,
\]
which makes the centered good-$v_5$-patch parity bridge formal. Beyond that,
any further mixed closure must come from global capture or from deeper
source-level corrected quotient-germ structure rather than from the present
lifted variables alone.
\end{remark}

\begin{remark}[What the new nonmixed/source-level machinery changes for the mixed side]
\label{rem:nonmixed-source-machinery-mixed-side}
The new repeated-source/source-determinant viewpoint and the no-go principle
excluding purely planar $(x,S)$-closure do not create a new mixed-local closure
theorem. Rather, they clarify the remaining mixed burden.

First, no argument using only planar $(x,S)$-geometry can close the $4$-point
branch, so any remaining mixed route must use either the centered scalar
descent or genuine coupled $Y$--$S$ source-level information.

Second, if a below-lifted backup route is needed, the natural mixed object is
not an $S$-only invariant, but a coupled source-minor ratio built from
$u_5$ and
\[
\lambda=\frac{\Delta_7}{v_5},
\]
i.e. a below-lifted avatar of
\[
\mathcal Z=\frac{J_{u_5}}{J_\lambda}.
\]

Thus the new nonmixed/source-level machinery functions primarily as a strategic
constraint and as a backup language for the mixed side, rather than as a
replacement for the local mixed exhaustion theorem near the centered base.
\end{remark}

\begin{remark}[Status of the lifted order-$7$ geometry]
\label{rem:wip-lifted-order7-zero-capture}
The lifted geometry is now substantially more stratified than a single
zero-capture problem.

First, shrinking exact lifted three-point and four-point circuits can accumulate
only at
\[
K_v=0
\qquad\text{and}\qquad
T_v=0,
\]
respectively, with uniform small-diameter exclusion away from those zero sets;
equivalently, they are rooted at the curvature- and torsion-type osculating
determinants of the corresponding lifted planar and space curves
(Lemma~\ref{lem:osculating-determinant-expansion},
Propositions~\ref{prop:shrinking-exact-lifted-three-point-circuits-force-Kv-zero}
and~\ref{prop:shrinking-exact-lifted-four-point-circuits-force-Tv-zero}).

Second, repeated-node limits are now explicit:
three-point collapse limits become tangent-line contacts for the
planar lifted curve $\Lambda_v=(x,S)$, and four-point collapse limits become
tangent-plane contacts for the lifted space curve $Q_v=(Y,x,S)$.

Third, the three-point side is now blockwise globally controlled on good
$v_5$-patches.
The curvature zero set $K_v=0$ has no infinite-order flat points; even-order
$K_v$-zeros are sterile; odd-order $K_v$-zeros carry exactly one local
opposite-side tangent-contact branch; and that branch continues uniquely on the
maximal right monotone-slope block, with no interior common-tangent event, no
source-side return, and no interior accumulation. Thus the three-point side is
no longer a live internal recurrence problem on such patches; only boundary exit
of the relevant source/target slope-overlap block can remain.

On the mixed four-point side, the right-pincer package now gives an analogous
local simplification near the centered base: every late-$v_5$ branch is either
locally sterile on the $u_5$-patch or already absorbed into the planar
quintic-circuit regime, so the only genuinely new mixed local branch left there
is the clean branch $\operatorname{ord}_s v_5=1$.

Fourth, the four-point side splits sharply into nonmixed and mixed regimes.
On the nonmixed side, finite-order odd $T_v$-zeros already support genuine
local exact branch sheets in the model geometry, so a blanket local sterility
theorem is false. On the mixed side, the dangerous low-order obstruction list is
finite and explicit:
\[
(m,n)=(3,4),\ (3,6),\ (4,6),
\]
equivalently
\[
(r,s)=(1,2),\ (1,4),\ (2,5),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3),\ (2,2),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal R)=(1,0),\ (1,2),\ (2,1).
\]

Fifth, below the lifted variables one has the exact Wronskian-ratio
reformulation
\[
\mathcal Z=\frac{J_{u_5}}{J_\lambda},
\qquad
\mathcal R=\frac{c^2}{M}\frac{d}{dh}\!\left(\frac{J_{u_5}}{J_\lambda}\right),
\qquad
\lambda=\frac{\Delta_7}{v_5},
\]
while the projective curvature ratio $\Theta$ yields no new independent local
obstruction beyond $(\mathcal Z,\mathcal R)$.

Sixth, the centered symmetric-placement Taylor package gives a strong local
collision-side parity picture:
\[
u_5,\ v_5,\ u_{7,K_1},\ v_{7,K_1}\ \text{odd in }s,
\qquad
\Delta_7\ \text{even in }s,
\]
with explicit septic coefficients $D_2,D_4,D_6$. In the diagonal-centered
odd/odd normal form
\[
Q(x)\sim (x^n,\ x,\ x^m),
\qquad
m,n\ \text{odd},\quad n>m\ge 3,
\]
one gets a punctured neighborhood free of $K_v=0$ and $T_v=0$ points.
Thus the explicit low-order dangerous $4$-point patterns do not arise at the
symmetric diagonal base itself.

So the missing global ingredient is no longer a generic local geometry theorem.
It is a combination of:
\begin{itemize}
\item source-level control of the multi-pair interaction defects
\[
E_{\ge2}^{(3)},\qquad E_{\ge2}^{(5)},\qquad \overline E_{\ge2}^{(7)};
\]

\item global continuation / recurrence control for the unique odd-order
three-point branch;

\item on the mixed side, no new local bridge theorem remains near the centered
base; what remains is only the finite scalar descent on the clean branch
together with any global capture needed to force bad mixed branches into the
local exhaustion theorem
\[
\text{Theorem~\ref{thm:local-exhaustion-mixed-four-point-centered-base}};
\]

\item and, on the still-live nonmixed side, a deeper RH-specific source- or
matrix-level identity imposing stronger parity / divisibility constraints on
\[
\mathcal R=\frac{T_v}{K_v^2}.
\]
\end{itemize}
\end{remark}

\begin{remark}[Live attack routes]
\label{rem:live-attack-routes}
At the present stage, the live routes are now quite sharply separated.

\begin{enumerate}
\item
\textbf{Two-point branch: three live conditional routes.}
The stronger finite-order route is still
Lemma~\ref{lem:minimal-source-level-two-point-criterion}: prove that the actual
corrected two-pair cubic/quintic/septic package is analytic on small two-atom
data and satisfies swap symmetry, one-amplitude collapse, and diagonal merger
\[
\mathfrak P_2(a_1,h;a_2,h)=(a_1+a_2)F_h.
\]
The weaker exact route is
Proposition~\ref{prop:conditional-exact-two-point-exclusion-qabs}, which would
already remove exact close two-point bad cores on compact subsets of
$\{c\neq 0\}$ from continuity and diagonal collapse of the actual corrected
two-atom quotient germ.

What is now ruled out is the naive source-summed corrected-block route: its
extracted one-atom finite-order coefficients are even in the source weight and
therefore cannot supply the required linear merger law. On the mixed side,
determinant-only and quotient-only arguments are likewise shear-blind. The
genuinely new derivative-geometric lane is the $\lambda$-shear route on a
good overlap patch, where
\[
\lambda=\frac{\Delta_7}{v_5}
\]
and an exact mixed branch generates moving shears
\[
(\eta_n,\xi_n,\gamma_n)
\]
for which
\[
A_n:=c-\eta_n\lambda,\qquad
B_n:=v_5-\xi_n\lambda,\qquad
F_n:=u_5-\gamma_n\lambda
\]
satisfy exact repeated-source transport along the branch. By
Proposition~\ref{prop:projective-compactness-moving-lambda-shear-two-point},
the automatic compactness is projective:
\[
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)]
\]
admits a convergent subsequence, and only on a subsequence whose limit lies in
the affine $\lambda$-chart does one obtain a convergent affine
$\lambda$-shear. Even then the frozen triple yields only asymptotic, not exact,
fixed-shear transport. The associated projective secant shadow can nevertheless
accumulate only on
\[
\{S=0\}\cup\{K_v=0\},
\qquad
S=\frac{\Delta_7}{c\,v_5}.
\]
So the remaining two-point work is either finite-order source-level merger,
quotient-diagonal continuity/diagonal collapse, or source-coupled control of
the mixed $\lambda$-shear exceptional loci. In the conditional exact
fixed-shear overlap lane,
Proposition~\ref{prop:fixed-shear-overlap-branch-off-Kv-forces-fold-at-S-zero}
shows that the slice
\[
\{S=0\}\cap\{K_v\neq 0\}
\]
is already forced into a fold-type projection regime. Thus the only clearly
genuinely mixed fixed-shear locus left on the overlap patch is
\[
K_v=0,
\]
while the missing step off $K_v=0$ is the identification of the resulting
second-coordinate parity with the existing nonmixed odd-zero
\[
\mathcal R=\frac{T_v}{K_v^2}
\]
package.

\item
\textbf{Three-point branch (derivative-geometric layer now stabilized).}
The lifted three-point side is now the most mature local branch. Shrinking
exact lifted $3$-point circuits are tied to the osculating determinant and
hence to
\[
K_v=0,
\]
the local branch structure at finite-order $K_v$-zeros is completely
classified by parity, and the odd-order branch is blockwise globally rigid on
good $v_5$-patches: infinite-order flatness is excluded, the branch continues
uniquely on the maximal right monotone-slope block, and there is no interior
common-tangent recurrence or source-side return. Inside the finite-core
program this stabilizes the lifted $k=3$ collinearity layer; any residual
issue there is only boundary exit of the relevant source/target slope-overlap
block, not an internal three-point propagation mechanism.

\item
\textbf{Four-point mixed branch: local route exhausted, global capture remains.}
Near the centered diagonal base, the mixed $4$-point branch is now locally
exhausted by
Theorem~\ref{thm:local-exhaustion-mixed-four-point-centered-base}: the clean
branch $V_1\neq 0$ is excluded by the canonical scalar descent and the
centered good-$v_5$-patch parity package, while every late-$v_5$ branch is
already removed on the $u_5$-patch as either locally sterile or
already-quintic. So the remaining mixed-side issue is no longer a new local jet
mechanism, but only any global capture needed to force bad mixed branches into
that centered-base local regime.

\item
\textbf{Route B backup degeneration tower.}
If the $v_5$-patch fails and $v_5$ starts late, the valuation form of the
septic transport constraint forces matching late vanishing of the septic
transport channel $v_{7,K_1}$. Thus failure of the $v_5$-route is not a
free local cancellation but a coupled quintic--septic degeneration scheme.

\item
\textbf{Four-point nonmixed branch via source-level control of odd $\mathcal W_{\mathrm{src}}$-zeros.}
The local nonmixed derivative geometry is now explicit: exact contacts force
zeros of $\mathcal R$, one-sign $\mathcal R$-intervals are sterile,
recurrent exact contacts force affine-planar collapse, and isolated zeros are
classified by parity. At source level, the same structure is encoded by the
canonical Wronskian
\[
\mathcal W_{\mathrm{src}}=J_\lambda J_{u_5}'-J_{u_5}J_\lambda',
\]
which differs from $\mathcal R$ only by a nonvanishing analytic factor on a
nonmixed arc.

For fixed source point $a$, repeated-source exact contacts are controlled by
the quadratic-envelope scalar
\[
\Gamma_a(x)=
\frac{Y(x)-Y(a)-Y'(a)(x-a)}
{S(x)-S(a)-S'(a)(x-a)},
\]
equivalently by the source quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)},
\]
with derivative governed by the osculatory $4\times 4$ determinant
$\mathfrak D(a,h)$. By
Proposition~\ref{prop:first-loss-is-diagonal-odd-zero-birth},
this repeated-source / first-loss mechanism is not an independent obstruction:
it occurs if and only if one diagonally approaches an odd-order zero of
$\mathcal R$, equivalently of $\mathcal W_{\mathrm{src}}$.

The remaining theorem-level task is therefore purely the global/source-level
exclusion of odd zeros of $\mathcal W_{\mathrm{src}}$ on opened nonmixed
arcs.
\end{enumerate}
\end{remark}

\begin{remark}[Stratified lifted local picture]
\label{rem:wip-stratified-lifted-local-picture}
The lifted local obstruction now splits into one closed regime and two genuinely
live regimes.

First, exact shrinking lifted $3$-point circuits concentrate into
\[
K_v=0.
\]
On good $v_5$-patches, this side is now blockwise globally controlled: there is no
infinite-order flatness, even-order $K_v$-zeros are sterile, odd-order
$K_v$-zeros seed exactly one local opposite-side branch, and that branch
continues uniquely on the maximal right monotone-slope block with no interior
common tangent, no source-side return, and no interior accumulation. So the
three-point side contributes only possible boundary exit, not an internal
recurrence mechanism.

Second, exact shrinking lifted $4$-point circuits concentrate into
\[
T_v=0.
\]
On the nonmixed side $K_v\neq 0$, the local derivative-side picture is now
explicit. Exact contacts force zeros of
\[
\mathcal R=\frac{T_v}{K_v^2},
\]
isolated zeros are classified by parity, one-sign $\mathcal R$-intervals are
exactly-contact sterile, and recurrent exact contacts force affine-planar
collapse. So the nonmixed $4$-point side is no longer a vague local
branching problem; what remains there is global/source-level control of which
odd zeros of $\mathcal R$ actually occur on genuine opened arcs.

Third, on the mixed side $K_v=T_v=0$, the low-order obstruction list is now
finite and explicit:
\[
(m,n)=(3,4),\ (3,6),\ (4,6),
\]
equivalently
\[
(r,s)=(1,2),\ (1,4),\ (2,5),
\]
equivalently
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3),\ (2,2).
\]
At the pair level, however, the centered quintic fixed-sector package
\[
A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S
\]
is now known not to vanish identically on the centered diagonal branch.
Near the centered base, the right-pincer package further reduces the mixed
local picture: every late-$v_5$ branch is either locally sterile on the
automatic $u_5$-patch or already absorbed into the planar quintic-circuit
regime, so the only genuinely new mixed local branch left there is the clean
branch
\[
\operatorname{ord}_s v_5=1.
\]

Thus the remaining lifted local issues are now:
the global/source-level control of odd zeros of $\mathcal R$ on the nonmixed
side, the finite scalar descent
\[
c(-s)=c(s)\pmod{s^6}
\]
on the clean mixed branch, and beyond that the global capture problem forcing
every relevant mixed branch into the centered-base local exhaustion theorem.
\end{remark}

\begin{remark}[Current geometric bottleneck]
\label{rem:current-geometric-bottleneck}
The remaining geometric bottleneck is now split into two qualitatively
different layers.

On the one-pair geometric layer, the obstruction is no longer bulk $W=0$
geometry, and it is no longer local adjacent pair-pair birth across a generic
turning boundary. On the $W=0,\ M\neq 0$ side,
Proposition~\ref{prop:no-W-flat-interval} excludes open-interval flatness and
Theorem~\ref{thm:finite-order-w-zero-local-sterility} shows that every
finite-order isolated $W=0$ boundary is locally sterile for pair-pair birth.
On the turning-boundary side,
Theorem~\ref{thm:adjacent-pair-pair-exclusion-turning} removes actual adjacent
pair-pair lines unconditionally.

At the lifted order-$7$ level, the canonical derivative-geometric determinants
\[
K_v
\qquad\text{and}\qquad
T_v
\]
govern shrinking exact lifted $3$- and $4$-point circuits on
$v_5\neq 0$ patches. On the $3$-point side, this layer is stabilized: shrinking
exact circuits concentrate into $\{K_v=0\}$, finite-order isolated zeros are
classified by parity, and the odd-order branch is blockwise globally rigid on
good $v_5$-patches.

On the $4$-point side, exact shrinking lifted $4$-point circuits concentrate
into
\[
\{T_v=0\},
\]
again with uniform small-diameter exclusion away from that zero set.

On the nonmixed side $K_v\neq 0$, generic odd-order $T_v$-zeros can still
carry preexisting close branches, so the nonmixed branch remains genuinely
live and now asks for global/source-level control of which odd zeros of
\[
\mathcal R=\frac{T_v}{K_v^2}
\]
actually arise on opened arcs.

By contrast, on the mixed side $K_v=T_v=0$, the local geometry near the
centered base is no longer the main bottleneck. There the right-pincer package
shows that every late-$v_5$ branch is either locally sterile on the automatic
$u_5$-patch or already absorbed into the defect-free planar quintic-circuit
regime, so the only genuinely new mixed local branch left is the clean branch
\[
V_1\neq 0.
\]
Accordingly, the mixed bottleneck is no longer a diffuse local codimension-two
analysis but the finite scalar descent
\[
c(-s)=c(s)\pmod{s^6}
\]
on that clean branch, together with the global capture problem of forcing every
relevant mixed branch into this centered-base local regime.

So the missing lifted ingredient is no longer another generic local geometric
exclusion theorem. It is: global/source-level control of odd zeros of
$\mathcal R$ on the nonmixed side; finite scalar descent on the clean mixed
branch; and beyond that the global/nonlocal capture problem linking the finite-core
endgame to this local exhaustion package.
\end{remark}

\begin{remark}[Current state of the argument]
\label{rem:current-state-of-argument}
The local one-pair analysis now consists of the canonical triple
\[
(c(h),\,v_5(h),\,\Delta_7(h)),
\]
together with the derived quantities
\[
M(h)=c(h)v_5'(h)-c'(h)v_5(h),
\qquad
N(h)=c(h)\Delta_7'(h)-c'(h)\Delta_7(h),
\]
\[
L(h)=v_5(h)\Delta_7'(h)-v_5'(h)\Delta_7(h),
\qquad
W(h)=\det(F(h),F'(h),F''(h)).
\]

On the region where $v_5M\neq 0$, the projective graph variables
\[
\mu=\frac{c}{v_5},
\qquad
\lambda=\frac{\Delta_7}{v_5}
\]
identify the normalized curve with a graph $\lambda=\lambda(\mu)$, and
\[
\lambda_{\mu\mu}=\frac{v_5^3}{M^3}W,
\qquad
\beta:=\lambda_\mu=-\frac{L}{M},
\qquad
T(h)=\left(-\frac{L(h)}{M(h)},\frac{N(h)}{M(h)}\right).
\]
Thus the global line-incidence problem is equivalently a problem about the
recurrence of tangent slopes $\beta$, or about vertical-line re-entry on the
dual tangent-line curve $T$.

Locally, both generic boundary types are now under control. At finite-order
$W=0,\ M\neq 0$ boundaries there is no local pair-pair birth, while at
generic turning boundaries actual adjacent pair-pair lines are excluded
unconditionally. The stronger symmetric directional-kernel theorem remains
available only conditionally on zero-capture and now serves as a sharper but
nonessential alternative route.

Accordingly, the remaining gap is no longer local boundary geometry. It is the
global propagation theorem linking these local facts: no fixed finite-slope line
should be able to leave and later re-enter the tangent-slope / tangent-line
data on nonadjacent branches. On the highest-new slice, this is the same as a
no-reentry theorem for the scalar graph
\[
\phi=\lambda^{[1]},
\qquad
\beta^{[1]}=\phi_\mu,
\qquad
m^{[1]}=\phi-\mu\phi_\mu.
\]

On the lifted $4$-point side, the mixed low-order obstruction list is now both
finite and canonical:
\[
(r,\operatorname{ord}_0\mathcal Z)\in\{(1,1),(1,3),(2,2)\},
\]
equivalently
\[
(r,s)=(1,2),(1,4),(2,5),
\]
or
\[
(m,n)=(3,4),(3,6),(4,6).
\]
The centered Taylor package already provides the explicit coefficients
\[
U_j,\ V_j,\ \widehat U_j,\ \widehat V_j,\ D_2,\ D_4,\ D_6,
\]
and the tagged quintic witness now shows that
\[
A_5^{\mathfrak f}(s)\not\equiv 0
\]
on the centered diagonal branch.

On the mixed side, however, the local theorem picture is now sharper than a
mere punctured-arc patch dichotomy. Near the centered base, the late-$v_5$
sector is already removed by the $u_5$-patch right-pincer package as either
locally sterile or planar-lift and hence already absorbed into the
defect-free quintic-circuit regime. The only genuinely new mixed local branch
there is the clean branch $V_1\neq 0$, and that branch is excluded by the
canonical scalar descent together with the centered good-$v_5$-patch parity
package. Consequently, any remaining mixed $4$-point issue is no longer a new
local mixed septic mechanism, but only a possible global/nonlocal escape from
the centered-base local exhaustion theorem.

In parallel, the finite-core endgame now splits into three layers.

First, on the two-pair side, the strengthened invariant
\[
\widehat\Psi(h)=
\left(
\frac{u_5(h)}{c(h)},
\frac{v_5(h)}{c(h)},
\frac{\Delta_7(h)}{c(h)^2}
\right)
\]
still gives the correct algebraic bridge, and on good $M\neq 0$ patches the
quantitative two-pair coincidence theorem forces bad two-point cores into a
defect-scale close regime. The minimal finite-order source criterion
\ref{lem:minimal-source-level-two-point-criterion} still isolates the exact
swap / one-amplitude / diagonal-merger package that would imply the desired
quadratic interaction factorization. However, the naive source-summed corrected
block model does not prove this criterion: along a weighted one-atom path its
extracted finite-order coefficients are even analytic in the source weight, so
the required linear merger law cannot come from that model alone.

At present the two-point side therefore splits into three conditional lanes:
the finite-order source-level merger route of
Lemma~\ref{lem:minimal-source-level-two-point-criterion}, the weaker
quotient-diagonal exact exclusion route of
Proposition~\ref{prop:conditional-exact-two-point-exclusion-qabs}, and the
mixed $\lambda$-shear / projective-shadow route on good overlap patches. In the
last route, an exact mixed branch generates moving $\lambda$-shears through
\[
\lambda=\frac{\Delta_7}{v_5},
\]
and
Proposition~\ref{prop:projective-compactness-moving-lambda-shear-two-point}
shows that the automatic compactness is projective:
\[
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)]
\]
admits a convergent subsequence. Only when the projective limit lies in the
affine $\lambda$-chart does one obtain a convergent affine $\lambda$-shear
subsequence, and even then the frozen triple gives only asymptotic, not exact,
fixed-shear transport. The associated projective secant shadow can nevertheless
accumulate only on
\[
\{S=0\}\cup\{K_v=0\},
\qquad
S=\frac{\Delta_7}{c\,v_5}.
\]
So the remaining structural issue on the two-point side is either verification
of the finite-order merger criterion or source-coupled control of these
explicit mixed exceptional loci.

Second, on the lifted three-point side, shrinking exact circuits now
concentrate into $K_v=0$, and this concentration is explicitly
derivative-geometric: by the osculating-determinant expansion, repeated-node
limits become tangent-line contacts for the planar lifted curve
\[
\Lambda_v=(x,S).
\]
On good $v_5$-patches this side is now blockwise globally controlled:
$K_v$ has no infinite-order zeros; even-order zeros are sterile; odd-order
zeros carry exactly one local branch; and that branch continues uniquely on
the maximal right monotone-slope block with no interior common-tangent event
or source-side return. So the three-point side is reduced to boundary exit of
the relevant slope-overlap block, not an internal recurrence mechanism.
Inside the finite-core reduction, this is exactly the stabilization of the
lifted $k=3$ collinearity layer.

Third, on the lifted four-point side, shrinking exact circuits now
concentrate into $T_v=0$, repeated-node limits become tangent-plane
contacts, and the local geometry splits into a nonmixed and a mixed regime.

On the nonmixed side, the local derivative-side theory is now explicit:
exact contacts force zeros of $\mathcal R=T_v/K_v^2$, isolated zeros are
classified by parity, one-sign $\mathcal R$-intervals are exactly-contact
sterile, and recurrent exact contacts force affine-planar collapse. At source
level, the same structure is encoded by the gauge-invariant Wronskian
\[
\mathcal W_{\mathrm{src}}=J_\lambda J_{u_5}'-J_{u_5}J_\lambda',
\]
which differs from $\mathcal R$ only by a nonvanishing analytic factor on a
nonmixed arc. For fixed source point $a$, repeated-source exact contacts
factor through the quadratic-envelope scalar
\[
\Gamma_a(x)=
\frac{Y(x)-Y(a)-Y'(a)(x-a)}
{S(x)-S(a)-S'(a)(x-a)},
\]
equivalently through the source quotient
\[
\Psi_a(h)=\frac{D_{u_5}(a,h)}{D_\lambda(a,h)},
\]
with derivative governed by the osculatory source determinant
$\mathfrak D(a,h)$. So the remaining nonmixed burden is global/source-level
control of which odd zeros of $\mathcal W_{\mathrm{src}}$, equivalently of
$\mathcal R$, occur on a genuine opened nonmixed arc.

On the mixed side, the dangerous low-order obstruction list is the finite
canonical set
\[
\kappa_{1,1},\qquad \kappa_{1,3},\qquad \kappa_{2,2},
\]
equivalently the order patterns
\[
(r,\operatorname{ord}_0\mathcal Z)=(1,1),\ (1,3),\ (2,2).
\]
The remaining theorem-level task there is no longer local patch classification.
It is the finite scalar descent
\[
c(-s)=c(s)\pmod{s^6}
\]
on the clean centered branch, together with the global capture problem forcing
every relevant mixed branch into the centered-base local exhaustion theorem.
Any further local mixed closure must therefore come from this scalar descent
together with deeper RH-specific source-/matrix-level structure, not from the
current lifted variables alone.
\end{remark}

\begin{remark}[Post-draft findings: established, provisional, and live]
\label{rem:post-draft-findings-established-provisional-live}
Since this draft state, six additional conclusions have emerged.

First, on the two-point branch, the exact finite-order source criterion remains
the clean algebraic route, but the naive source-summed corrected block model
cannot prove it: along a weighted one-atom path the extracted finite-order
coefficients are even analytic in the source weight. So the remaining two-point
issue now splits into three conditional lanes: the finite-order source-level
merger route, the weaker quotient-diagonal exact exclusion route, and the mixed
$\lambda$-shear / projective-shadow route on good overlap patches. In the last
route, a close exact mixed two-point bad branch generates moving shears through
\[
\lambda=\frac{\Delta_7}{v_5},
\]
and
Proposition~\ref{prop:projective-compactness-moving-lambda-shear-two-point}
shows that the automatic compactness is projective:
\[
[\delta_n(c):\delta_n(v_5):\delta_n(u_5):\delta_n(\lambda)]
\]
admits a convergent subsequence. Only when the projective limit lies in the
affine $\lambda$-chart does one obtain a convergent affine $\lambda$-shear
subsequence, and even then the limiting triple yields only asymptotic, not
exact, fixed-shear transport. The associated projective secant shadow can
nevertheless accumulate only on
\[
\{S=0\}\cup\{K_v=0\},
\qquad
S=\frac{\Delta_7}{c\,v_5}.
\]
So the remaining two-point issue is no longer a single broad interaction
ansatz, but a choice among these three explicit closure mechanisms.

Second, on the lifted four-point branch, the explicit low-order obstruction
list has been reduced to the six coefficients
\[
z_2,\ z_4,\ z_6,\ \kappa_{1,1},\ \kappa_{1,3},\ \kappa_{2,2},
\]
or equivalently to the order patterns
\[
\operatorname{ord}_0\mathcal R\in\{1,3,5\},
\qquad
(r,\operatorname{ord}_0\mathcal Z)\in\{(1,1),(1,3),(2,2)\}.
\]

Third, the centered symmetric-placement Taylor package now gives explicit septic
coefficients
\[
D_2,\qquad D_4,\qquad D_6,
\]
explicit bridge coefficients
\[
X_1,X_3,X_5,\qquad L_1,L_3,L_5,
\]
and a punctured-neighborhood exclusion at the diagonal base.

Fourth, the centered fixed-sector quintic package
\[
A_5^{\mathfrak f}(s)=u_5(s)I+v_5(s)S
\]
is now firmly established as the correct pair-level object on the mixed side.
The centered tagged witness survives specialization strongly enough to show
\[
U_1\neq 0,
\qquad
u_5(s)\not\equiv 0,
\qquad
A_5^{\mathfrak f}(s)\not\equiv 0,
\]
so the centered quintic pair cannot totally collapse.

Fifth, the right-pincer package now sharpens the mixed local picture near the
centered base: every late-$v_5$ branch is either locally sterile on the
automatic $u_5$-patch or already absorbed into the planar defect-free
quintic-circuit regime. So the only genuinely new mixed local branch left there
is the clean branch
\[
V_1\neq 0.
\]

Sixth, on that clean branch the remaining theorem has become very small:
the finite scalar descent
\[
c(-s)=c(s)\pmod{s^6},
\qquad\text{equivalently}\qquad
C_1=C_3=C_5=0.
\]
Once this holds, the centered good-$v_5$-patch bridge becomes formal:
\[
Y=\frac{u_5}{c},
\qquad
S=\frac{\Delta_7}{cv_5}
\]
are odd through the required order, and the entire explicit mixed low-order
bad list
\[
(r,\operatorname{ord}_0\mathcal Z)\in\{(1,1),(1,3),(2,2)\}
\]
is excluded there.

So the present frontier is no longer a generic local geometry problem. It is
the combination of either a source-level or quotient-diagonal two-point closure
theorem, or else a source-coupled $\lambda$-shear control on the explicit mixed
exceptional loci
\[
\{S=0\}\cup\{K_v=0\},
\qquad
S=\frac{\Delta_7}{c\,v_5},
\]
together with a finite scalar descent theorem on the clean mixed four-point
branch and a deeper RH-specific identity on the nonmixed four-point branch.
\end{remark}

\section{Endgame architecture and remaining global propagation problem}

The remaining endgame is now a global propagation problem for the normalized
line-incidence geometry rather than a local boundary-creation problem.

\begin{remark}[Equivalent formulations of the remaining global problem]
\label{rem:equivalent-global-propagation-problem}
On a generic component, the remaining missing theorem may be formulated in any
of the following equivalent ways:
\begin{enumerate}
\item no finite-slope affine line in the chart
\[
x=\frac{v_5}{c},
\qquad
y=\frac{\Delta_7}{c}
\]
is $2$-secant to two nonadjacent ECT intervals;

\item the slope function
\[
\beta(h):=-\frac{L(h)}{M(h)},
\qquad
L=v_5\Delta_7'-v_5'\Delta_7,
\]
does not revisit a level on nonadjacent branches;

\item the dual tangent-line curve
\[
T(h)=\left(-\frac{L(h)}{M(h)},\frac{N(h)}{M(h)}\right)
\]
has no nonadjacent same-parity re-entry against a vertical line in the
$(b,m)$-plane;

\item on the highest-new slice, the scalar graph
\[
\phi=\lambda^{[1]}
\]
has no nonadjacent re-entry of its slope $\phi_\mu$.
\end{enumerate}
The results proved above resolve the local behavior at finite-order
$W=0,\ M\neq 0$ boundaries and at generic turning boundaries. Thus the
remaining theorem target is not local boundary geometry but global non-recurrence:
a fixed finite slope should not leave and later re-enter the tangent-slope /
tangent-line data on nonadjacent branches. In the three equivalent languages
above, this is a theorem about the level sets of $\beta$, about vertical-line
re-entry for the dual curve $T$, or about nonadjacent slope re-entry for the
highest-new scalar graph $\phi$.
\end{remark}

\begin{remark}[Warning: what the current local theory does \emph{not} imply]
\label{rem:warning-no-easy-globalization}
Several tempting globalization statements suggested by the local theory are too
strong in generic models and should not be assumed without further RH-specific
input.

\begin{enumerate}
\item Naive support propagation is not enough: exclusion of adjacent pair-pair
lines does not by itself force exclusion for nonadjacent pairs.

\item Local convexity of the dual tangent-line curve, even together with the
shared asymptote structure of
Proposition~\ref{prop:dual-asymptote-turning-boundary}, is not by itself enough
to forbid nonadjacent same-parity re-entry in the dual $(\beta,m)$-plane.

\item The direct highest-new septic coefficient is explicit enough to prove
noncancellation, but not generically one-signed. Thus no trivial sign theorem
for the scalar graph $\phi=\lambda^{[1]}$ should be expected without further
RH-specific structure.
\end{enumerate}

Accordingly, the remaining gap is now a genuinely global special-structure
theorem, not a missing local lemma.
\end{remark}

\begin{lemma}[Crude polynomial bound for the local value scale]
\label{lem:crude-S-bound}
Let
\[
S(m)=\sum_\rho f_{\beta_\rho,\gamma_\rho}(m),
\]
where
\[
f_{\beta,\gamma}(m)
=
\frac{1-\beta}{(1-\beta)^2+(2m-\gamma)^2}
+
\frac{\beta}{\beta^2+(2m-\gamma)^2}.
\]
Then
\[
S(m)\ll Q^2,
\qquad Q\asymp \log|m|.
\]
Consequently
\[
L(m)\ll Q
\]
and
\[
B_\zeta(m)L(m)S(m)\ll Q^4.
\]
\end{lemma}

\begin{proof}
By the zero-free region, for zeros at relevant height one has
\[
\min(\beta,1-\beta)\gg \frac1Q.
\]
Hence
\[
f_{\beta,\gamma}(m)\ll \frac{Q}{1+(2m-\gamma)^2}.
\]
Partition the zeros into unit shells
\[
\mathcal S_k:=\{\rho: k\le |2m-\gamma_\rho|<k+1\},
\qquad k=0,1,2,\dots
\]
Standard zero counting gives
\[
\#\mathcal S_k\ll Q
\]
for each unit shell near height $m$. Therefore
\[
S(m)
\ll
\sum_{k\ge 0}\#\mathcal S_k\frac{Q}{1+k^2}
\ll
Q\sum_{k\ge 0}\frac{Q}{1+k^2}
\ll
Q^2.
\]
Since
\[
L(m)=\log\!\Bigl(3+|m|+\frac1{S(m)}\Bigr),
\]
we trivially have $L(m)\ll Q$, and the last estimate follows from
$B_\zeta(m)\asymp Q$.
\end{proof}

The following remark records the present status of the endgame before the
final contradiction theorem.

\begin{remark}[Work in progress: current endgame status]
\label{rem:wip-final-endgame-status}
The contradiction argument in the next theorem is presently written in the
\emph{pair-like branch} of the local model analysis. More precisely, the
current endgame is fully aligned with the case in which the actual same-scale
local core is perturbatively pair-like, so that the toy-model first-odd-jet
obstruction continues to govern the corrected transverse scalar.

The fixed-core analysis developed earlier in the draft shows, however, that
a more general finite-core branch is also possible: the first odd
coefficient may cancel while a genuine corrected anomaly survives at a
higher odd order. Thus the fully general finite-core endgame would need to
be formulated in terms of the \emph{first nonzero odd jet} of the corrected
transverse scalar, rather than specifically the first one.

Accordingly, the theorem below should presently be read together with the
preceding work-in-progress remarks on the pair-like versus finite-core fork.
In particular, the pair-based contradiction is the intended endgame under
the pair-like branch, while the genuinely finite-core branch remains to be
completed in full detail.

At the local algebraic level, the canonical quotient-level order-$7$
fixed-sector package is now closed via
Theorem~\ref{thm:quotient-septic-closure}: the remaining order-$7$ ambiguity is
only the choice of a raw representative inside
$A_{7,K_1}^{\mathfrak f}+\mathbf C A_5^{\mathfrak f}$, equivalently a local
gauge-fixing of $(u_7,v_7)$, and does not affect the quotient class
$[A_7^{\mathfrak f}]$ or the canonical second residual determinant
$\Delta_7$.
\end{remark}

\begin{remark}[Work in progress: asymptotic contradiction versus full $\RH$]
\label{rem:wip-high-height-only}
As presently written, the final contradiction is only asymptotic in the height
parameter $Q$: the comparison closes after reaching a regime in which the
zeta-side upper bound is dominated by the toy-side lower bound, schematically
because
\[
Q^4 e^{-\delta Q}\to 0
\qquad (Q\to\infty).
\]
Accordingly, the current argument excludes sufficiently large pair-like
off-line anomalies, but does not yet by itself rule out a hypothetical
low-lying off-line zero.  In particular, the present proof does not furnish a
uniform-in-height contradiction, nor does it presently prove that a single
off-line zero at one height would force corresponding bad local anomalies at
arbitrarily large heights.

A plausible repair is to split the endgame into an effective high-height
theorem plus a separate finite low-height bridge.

\smallskip

\noindent
\emph{Effective high-height step.}
One should first replace the soft asymptotic comparison by an explicit
inequality.  Concretely, the final contradiction compares a toy-side lower
bound of the form
\[
|\Xi_{\toy}^{(N)}(u,d)|
\ge
c_{\toy}\,\mathcal{L}(m)
\]
against a zeta-side upper bound of the form
\[
|\Xi_{\zeta}^{(N)}(m)|
\le
C_{\zeta}(\rho_0,\alpha)\,
\frac{\mathcal{U}(m)}{Q}\,
e^{-\delta_*(\alpha,\rho_0)Q},
\]
where in the present draft one has schematically
\[
\mathcal{L}(m)\asymp \frac{x}{B_\zeta(m)}S(m)
\]
(or its variable-$x$ replacement from
Remark~\ref{rem:wip-calibration-small-u}),
and
\[
\mathcal{U}(m)\asymp L(m)S(m)^2.
\]
To extract an actual threshold, every use of $O(\cdot)$, $\ll$, and
$\asymp$ in the final comparison must be replaced by explicit constants.
After substituting explicit bounds such as
\[
B_\zeta(m)\le C_B Q,\qquad
L(m)\le C_L Q,\qquad
S(m)\le C_S Q^2,
\]
the contradiction should reduce to an explicit scalar inequality of the form
\[
C_*(\rho_0,\alpha)\,Q^3 e^{-\delta_*(\alpha,\rho_0)Q}<1
\qquad (Q\ge Q_*),
\]
for some computable constant $C_*>0$.  Any explicit $Q_*$ satisfying this
inequality would then yield an \emph{effective} theorem excluding pair-like
off-line anomalies for all $Q\ge Q_*$.

\smallskip

\noindent
\emph{Height extraction.}
Once $Q_*$ is known explicitly, one must convert it into an actual height
threshold.  Since the draft works with a midpoint parameter $m$ satisfying
\[
Q\asymp \log |m|,
\]
this requires making the logarithmic comparability effective, for example in
the form
\[
c_Q \log(3+|m|)\le Q\le C_Q \log(3+|m|).
\]
From such inequalities one obtains an explicit midpoint threshold $m_*$, and
hence an explicit zero-height threshold $T_*$, since the local points under
consideration satisfy
\[
t_\pm = m \pm \frac{\sigma}{2}
\]
with $|\sigma|$ microscopic relative to the height scale.  Thus one would
arrive at a statement of the form:
\[
\text{no pair-like off-line zero can occur for } |\Im \rho|>T_*.
\]

\smallskip

\noindent
\emph{Finite low-height bridge.}
The effective high-height theorem alone still does not imply the full Riemann
Hypothesis unless one also excludes all potential off-line zeros below the
threshold $T_*$.  A natural way to do this is to combine the structural
argument above height $T_*$ with a rigorous finite verification of $\RH$
up to height $T_*$.  Accordingly, if one can arrange that the explicit
threshold $T_*$ lies below a rigorously verified range, then the final step
would be:
\[
\text{high-height exclusion above }T_*
\quad+\quad
\text{rigorous verification below }T_*
\quad\Longrightarrow\quad
\RH.
\]
This would still be an unconditional proof, albeit a computer-assisted one
rather than a purely internal asymptotic contradiction.

\smallskip

\noindent
\emph{What still needs to be made explicit.}
To implement this repair rigorously, the draft must still supply all of the
following ingredients in effective form:
\begin{enumerate}
\item an explicit toy-side lower constant on the admissible compact
$d$-range and microscopic $u$-range;
\item an explicit zeta-side upper constant in the $N$-point cancellation
estimate, including the exponential decay rate $\delta$;
\item explicit growth bounds for the auxiliary quantities appearing in the
final comparison, including $B_\zeta(m)$, $L(m)$, and $S(m)$;
\item an explicit conversion between the logarithmic parameter $Q$ and the
actual height variable;
\item a final theorem stated as an effective exclusion above a concrete
threshold $T_*$, rather than merely ``for $Q$ sufficiently large'';
\item a separate low-height bridge, either by citing a rigorous finite
verification result covering the range up to $T_*$, or by proving an
alternative uniform-in-height contradiction.
\end{enumerate}

\smallskip

\noindent
There is, in principle, a second possible repair: prove a propagation theorem
showing that any off-line zero at one height would force corresponding bad
local anomalies at arbitrarily large heights, so that the asymptotic
contradiction would automatically apply.  However, no such propagation
principle is currently established in the draft, and at present this appears
to be a substantially stronger theorem than the effective-threshold route
described above.

Accordingly, the current endgame should be read as an asymptotic contradiction
theorem in the pair-like branch.  A plausible route to a complete proof of
$\RH$ is available, but it requires an effective extraction of the height
threshold together with a finite low-height bridge, neither of which has yet
been written out in the draft.
\end{remark}

\begin{theorem}[Final calibrated $N$-point contradiction in the pair-like branch]
\label{thm:final-contradiction}
No fixed off-line toy anomaly can occur in the pair-like branch. Consequently,
under the pair-like branch hypothesis, the calibrated contradiction closes.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:calibration-remainder-cutoff} and the canonical
calibration theorem, in the fixed small-$x_0$ regime one has
\[
u^2\asymp \frac{x_0}{B_\zeta(m)}S(m).
\]

On the toy side, Proposition~\ref{prop:toy-n-point-direct} gives
\[
\Xi_{\toy}^{(N)}(u,d)=u^2\Phi_K(M(d))+O(u^4),
\]
hence on compact $d$-ranges,
\[
|\Xi_{\toy}^{(N)}(u,d)|\asymp u^2
\asymp
\frac{x_0}{B_\zeta(m)}S(m).
\]

On the zeta side, Corollary~\ref{cor:optimized-zeta-cancellation-depth} gives
\[
|\Xi_\zeta^{(N)}(m)|
\ll_{\rho_0,\alpha}
\frac{L(m)S(m)^2}{Q}\,
e^{-\delta_*(\alpha,\rho_0)Q}.
\]

By Lemma~\ref{lem:crude-S-bound}, one has $S(m)\ll Q^2$, $L(m)\ll Q$, and
$B_\zeta(m)L(m)S(m)\ll Q^4$. Therefore
\[
\frac{(L(m)S(m)^2/Q)e^{-\delta_*(\alpha,\rho_0)Q}}
{(x_0/B_\zeta(m))S(m)}
=
\frac{B_\zeta(m)}{x_0}\,\frac{L(m)S(m)}{Q}\,
e^{-\delta_*(\alpha,\rho_0)Q}
\ll
Q^3 e^{-\delta_*(\alpha,\rho_0)Q}\to 0.
\]
Hence for $Q$ sufficiently large,
\[
|\Xi_\zeta^{(N)}(m)|<|\Xi_{\toy}^{(N)}(u,d)|.
\]

This is impossible if the corrected local zeta deformation realizes the local
off-line toy anomaly with parameter $d\in D$, because the calibrated $N$-point
construction was set up so that the toy model is the jet-limit local avatar of
an off-line zero configuration. Thus no off-line zero can occur. Since every
violation of the Riemann Hypothesis would produce such an off-line local
anomaly, all nontrivial zeros must lie on the critical line. Hence $\RH$
holds.
\end{proof}

\appendix

\section{Toy microscopic expansion}
\label{app:toy-microscopic-expansion}

\begin{lemma}[Uniform microscopic expansion of the toy local deformation]
\label{lem:toy-microscopic-expansion}
Fix a compact interval
\[
D=[d_-,d_+]\subset(0,\infty),
\]
and let
\[
\Delta_{\toy}(u,d;s)
\]
denote the toy local deformation matrix in the symmetric microscopic regime,
with off-line parameter $u$, separation parameter $d$, and microscopic node
$s$.

Then there exist constants $\rho_{\toy}>0$ and $u_0(D)>0$ such that for all
\[
d\in D,
\qquad
|s|<\rho_{\toy},
\qquad
|u|<u_0(D),
\]
one has the expansion
\[
\Delta_{\toy}(u,d;s)=u^2M(d)+u^4E(u,d;s),
\]
where $M(d)$ is the toy anomaly matrix, $E(u,d;s)$ is analytic in $s$
for $|s|<\rho_{\toy}$, and
\[
\sup_{\substack{d\in D\\ |s|<\rho_{\toy}\\ |u|<u_0(D)}} \|E(u,d;s)\|\ll 1.
\]
In particular, for the microscopic nodes
\[
s_j=\frac{j}{Q^2},
\qquad
j=1,\dots,N,
\]
with $N\le \rho_{\toy}Q^2$, one has uniformly
\[
\Delta_{\toy}(u,d;s_j)=u^2M(d)+u^4E_j(u,d),
\qquad
\sup_j \|E_j(u,d)\|\ll 1.
\]
\end{lemma}

\begin{proof}
The toy local deformation is obtained from an explicit finite-dimensional
off-line perturbation of the toy block. By construction it depends smoothly
(in fact analytically) on the parameters $(u,s,d)$ in a neighborhood of
\[
(u,s,d)=(0,0,d_0),
\qquad d_0\in D.
\]
At $u=0$, the deformation vanishes, and by the even symmetry of the off-line
split there is no linear term in $u$. Hence the first nontrivial term is
quadratic:
\[
\Delta_{\toy}(u,d;s)=u^2M(d,s)+O(u^4),
\]
uniformly on compact $d$-ranges and for $|s|$ in a fixed microscopic disk.

By the jet-limit computation for the toy model, the leading quadratic
coefficient is independent of the microscopic node $s$ and equals the toy
anomaly matrix $M(d)$. Thus
\[
M(d,s)\equiv M(d),
\]
and the expansion becomes
\[
\Delta_{\toy}(u,d;s)=u^2M(d)+u^4E(u,d;s),
\]
with $E$ analytic in $s$ and uniformly bounded on compact parameter
ranges. Restricting to the microscopic nodes $s_j=j/Q^2$ gives the stated
uniform bound for $E_j(u,d)$.
\end{proof}

\begin{remark}[Work in progress: toy microscopic expansion]
\label{rem:wip-toy-microscopic-expansion}
The proof above is schematic: it uses smoothness in $(u,s,d)$, vanishing at
$u=0$, and even symmetry in the off-line split to obtain the quadratic
leading term, and invokes the jet-limit computation to identify the
coefficient as the toy anomaly matrix $M(d)$. A later pass should make the
analyticity and uniform-bound steps quantitative by recording an explicit
Taylor remainder with a constant depending only on $D$.
\end{remark}

\begin{thebibliography}{99}

\bibitem{Riemann1859}
B.~Riemann,
\newblock Ueber die Anzahl der Primzahlen unter einer gegebenen Gr\"osse,
\newblock \emph{Monatsberichte der Berliner Akademie}, 1859, 671--680.

\bibitem{Bombieri2000}
E.~Bombieri,
\newblock \emph{Problems of the Millennium: The Riemann Hypothesis},
\newblock Clay Mathematics Institute, 2000.

\bibitem{Conrey2003}
J.~B.~Conrey,
\newblock The Riemann Hypothesis,
\newblock \emph{Notices of the American Mathematical Society} \textbf{50} (2003), no.~3, 341--353.

\bibitem{Edwards2001}
H.~M.~Edwards,
\newblock \emph{Riemann's Zeta Function},
\newblock Dover Publications, Mineola, NY, 2001.

\bibitem{Titchmarsh1986}
E.~C.~Titchmarsh,
\newblock \emph{The Theory of the Riemann Zeta-Function},
\newblock 2nd ed., revised by D.~R.~Heath-Brown,
\newblock Oxford University Press, Oxford, 1986.

\bibitem{Speiser1935}
A.~Speiser,
\newblock Geometrisches zur Riemannschen Zetafunktion,
\newblock \emph{Mathematische Annalen} \textbf{110} (1935), 514--521.

\bibitem{LevinsonMontgomery1974}
N.~Levinson and H.~L.~Montgomery,
\newblock Zeros of the derivatives of the Riemann zeta-function,
\newblock \emph{Acta Mathematica} \textbf{133} (1974), 49--65.

\bibitem{deBranges1986}
L.~de~Branges,
\newblock The Riemann hypothesis for Hilbert spaces of entire functions,
\newblock \emph{Bulletin of the American Mathematical Society (N.S.)}
\textbf{15} (1986), no.~1, 1--17.

\bibitem{ConreyLi2000}
J.~B.~Conrey and X.-J.~Li,
\newblock A note on some positivity conditions related to zeta and L-functions,
\newblock \emph{International Mathematics Research Notices} \textbf{2000}
(2000), no.~18, 929--940.

\bibitem{Connes1997}
A.~Connes,
\newblock Trace formula in noncommutative geometry and the zeros of the Riemann zeta function,
\newblock \emph{Journ\'ees \'Equations aux d\'eriv\'ees partielles} (1997), Art.~No.~4, 1--28.

\bibitem{ConnesConsani2021}
A.~Connes and C.~Consani,
\newblock Weil positivity and trace formula: the archimedean place,
\newblock arXiv:2006.13771, 2021.

\end{thebibliography}

\end{document}
